### 2013-11-29 paper.tex
First commit

%%%% Various options for document class.
\documentclass[usenatbib, a4paper]{mn2e}
%%\documentclass[preprint2, a4paper, 11pt]{aastex}
%%\documentclass[twocolum]{revtex4}
%%\documentclass{report}
% \documentclass[useAMS,usenatbib,referee]{mn2e}

%\usepackage{psfig,morefloats,url}
%use preprint2 for 2 columns paper.

%% declare any packages used
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{color}
\usepackage{pdfpages}
\usepackage{appendix}
%\usepackage{epsfig}
%\usepackage[dvips]{color}
%\usepackage{aabib}

%\marginparwidth = 25pt
\citestyle{aa}
\addtolength{\topmargin}{-.5in}
%% This command added as margins are wrong in mn2e, it appears. 
%% Not needed for other classes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%% define bibstyle and other definitions
\bibliographystyle{aabib}
%% renew commands
\renewcommand{\labelitemi}{$-$}
\def\la{Ly-$\alpha$ }
\def\py{\textsc{Python} }
\def\civ{C~\textsc{iv} }
\def\araa{ARAA}
\def\nat{Nature}
\def\apjl{ApJ Letters}
\def\aapr{AAPR}
\def\ssr{SSR}
\def\apj{ApJ}
\def\pasp{PASP}
\def\aap{A\&A}
\def\mnras{MNRAS}
\def\aj{AJ}
\def\rmxaa{RMXAA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          TITLE AND AUTHORS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{The Disk Wind Contribution to Optical Lines in Cataclysmic Variables}
\author{J. H.
  Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}
%%\altaffiltext{1}{School of Physics \& Astronomy, University of Southampton,
  %%Southampton, SO17 1BJ, UK}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          ABSTRACT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{abstract}
Disk-dominated High-State Cataclysmic Variable systems (CVs) exhibit strong emission in optical recombination lines.
Here we present results obtained by improving a Monte Carlo radiative transfer code originally used
to model UV resonance lines in CVs, which show the potential contribution to these optical lines
from a line driven accretion disk wind.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          INTRODUCTION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Cataclysmic Variables (CVs), are systems in which a white dwarf accretes matter from a donor star
via Roche-lobe overflow. In Disk-dominated CVs, this accretion is mediated by an accretion disk which forms 
around the white dwarf, and it has been shown that the spectra of high state CVs
exhibit absorption features believed to be caused by an outflow, potentially line-drive,
rising from the accretion disk.

The ultraviolet spectra of CVs, in particular, exhibity P-Cygni like profiles in resonance lines such as 
NV, OVI and, most commonly, CIV.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          CODE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Description of the code}

\py is a Monte Carlo radiative transfer code which uses the Sobolev approximation. It is originally
introduced by Long \& Knigge (2002), and a more up-to-date description is provided by
Higginbottom et al. (2013).

\subsection{Macro-atoms}
In its standard operating mode, \py uses a two-level atom approximation (see e.g Mihalas 1982\nocite{mihalas}, Ch. 11) for its treatment of lines. This approximation works well when treating so-called `resonance lines' (such as \civ, O\textsc{vi}), in which the excited electron is strongly coupled to the ground state, but breaks down for more complex situations such as recombination cascades. To properly model recombination lines, including the Lyman and Balmer series, a more complete treatment of line transfer is required.

Lucy (2002, 2003\nocite{lucy2002, lucy2003}; hereafter L02, L03) showed that by quantising matter into `macro-atoms', and radiant and kinetic energy into energy packets, it is possible to asymptotically reproduce the emisssivity of a gas in statistical equilibrium without simplifying line transfer. Macro-atoms are finite volume elements with internal transition probabilities that are `activated' by packets of radiant (r-packets) or kinetic (k-packets) energy. A typical activation and deactivation sequence is shown in figure~\ref{macro}.
A full description is far beyond the scope of this report- consult L02 and L03.

The macro-atom scheme has been used with \py before, in a Hydrogen-only mode with application to YSOs \citep{simmacro2005}, but has not yet been applied to AGN or CV problems. With some improvements, the current scheme will enable \py to model H and He recombination lines, for example. The fast, simple treatment of resonance lines 
can be retained, as the \py implementation allows for non-macro atom treatment for certain ions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          MATOM TESTING
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Testing the macro atom scheme}

Before proceeding with modeling of CV systems, we need to be sure that our scheme fulfils Lucy's (2002) 
statement that it will `asymptotically reproduce the emissivity of a gas in statistical equilibrium'.
For our tests, we use a Hydrogen only `thin shell' mode in \py, in which a single macro atom is created as a spherical 
shell with a thickness of 1cm. We construct the situation such that all opacities other than 
bound-free absorption are negligible, and the only cooling process available to the gas is that of
recombination line emission. This is a mathematical pathology, commonly known as `Case A', and allows
us to test against analytical calculations.

As \py normally models dense environments, it assumes each principal quantum number level is
well `l-mixed' - that is each subshell of a given level is populated according to statistical weight by
inelastic collisions. It is therefore not possible to compare with non-L mixed calculations such as 
those presented in Osterbrock (1989\nocite{oster}). Seaton (1959; S59\nocite{seaton}) carried out calculations
for Case A in the l-mixed case, and is thus a better comparison. Figure 1 shows a comparison between S59
and \py, showing excellent agreement. Figure 2 shows the Case B comparison, in which the escape probabilities
for the Lyman lines have been explicitly zeroed.

\begin{figure}
\includegraphics[width=0.5\textwidth]{caseA.png}
\caption{Case A comparison between S59 and \py at 10000K and 20000K}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{caseB.png}
\caption{Case B comparison between S59 and \py at 10000K and 20000K}
\end{figure}

This test verifies the treatment of recombination lines in Hydrogen only models, but it is also necessary to test the implementation
of macro-atoms when other elements are treated as so-called `simple ions'. In this mode, the user can select which species to treat as
macro atoms, meaning that the other species are still treated with a two-level approximation. This means that the fast treatment of
resonance lines can be maintained without sacrificing the necessity that all energy packets are indivisible. It is important to verify that 
this still produces the correct ionization state for the wind. We can test this by comparing against both {\textsc Cloudy} and LK02.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          MATOM TESTING
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The CV Model}
As in LK02, we follow the prescription of SV93 in both our fundamental biconical wind model and velocity law

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          RESULTS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results from Simulations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          DISCUSSION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}

%% Balmer jump

\subsection{Future Work}

In addition to this project, we plan to apply the macro atom scheme to QSOs in order to build on the work of Higginbottom et al. (2013),
in which a benchmark biconical disk wind model was presented. In particular, we hope that the macro-atom scheme will enable the
model to produce significant Lyman-$\alpha$ emission, as is observed in QSOs.

\bibliography{mybib.bib}

\end{document}

### 2013-11-29 paper.tex
Edited makefile and title

@@
 
-\title{The Disk Wind Contribution to Optical Lines in Cataclysmic Variables}
-\author{J. H.
-  Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}
-%%\altaffiltext{1}{School of Physics \& Astronomy, University of Southampton,
-  %%Southampton, SO17 1BJ, UK}
+\title[Optical Lines from CV Disk Winds]
+{The Disk Wind Contribution to Optical Lines in Cataclysmic Variables}
+
+\author[Matthews et al.]{J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk},C.~Knigge,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and N.~Higginbottom$^1$
+\medskip  
+\\$^1$School of Physics and Astronomy, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom
+\\$^2$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD, 21218
+\\$^3$School of Mathematics and Physics, Queens University Belfast, University Road, Belfast, BT7 1NN, Northern Ireland, UK}
+
+\date{\today}
 
@@
 \end{abstract}
+
+\begin{keywords}
+Cataclysmic Variables - quasars: absorption lines - radiative transfer - 
+methods: numerical.
+\end{keywords}
 

### 2014-02-10 paper.tex
Figures subdirectory
Some changes, new figures

--- 2013-11-29 paper.tex
@@
 %%%% Various options for document class.
-\documentclass[usenatbib, a4paper]{mn2e}
-%%\documentclass[preprint2, a4paper, 11pt]{aastex}
+%\documentclass[usenatbib, a4paper]{preprint}
+%\documentclass[preprint, a4paper, 11pt]{aastex}
 %%\documentclass[twocolum]{revtex4}
 %%\documentclass{report}
-% \documentclass[useAMS,usenatbib,referee]{mn2e}
+\documentclass[useAMS,usenatbib, onecolumn]{mn2ejm}
 
@@
 %% Not needed for other classes
+
+%% This is the end of the preamble.  Indicate the beginning of the
+%% paper itself with \begin{document}.
 
@@
 
-\title{The Disk Wind Contribution to Optical Lines in Cataclysmic Variables}
+\title{The Disk Wind Contribution to the Optical Spectra of Cataclysmic Variables}
 \author{J. H.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \maketitle
 
-%% This is the end of the preamble.  Indicate the beginning of the
-%% paper itself with \begin{document}.
-
 \begin{abstract}
-Disk-dominated High-State Cataclysmic Variable systems (CVs) exhibit strong emission in optical recombination lines.
-Here we present results obtained by improving a Monte Carlo radiative transfer code originally used
-to model UV resonance lines in CVs, which show the potential contribution to these optical lines
-from a line driven accretion disk wind.
+High-State non-magnetic Cataclysmic Variable systems (CVs) exhibit strong emission in Hydrogen \& Helium 
+optical recombination lines. Here we present results obtained by encorporating a macro atom treatment into
+our Monte Carlo radiative transfer code originally used
+to model UV resonance lines in CVs, \py. Our benchmark CV model is capable of producing
+all of the notable optical lines (e.g. He II 4686, H${\alpha}$, He I), as well as
+enchanced emission in the Ly-$\alpha$ and He II $1640$ UV lines.
+In addition, the improved treatment of recombination means that the bound-free continuum
+emission is sufficient to mask the so-called `Balmer jump' photoabsorption edge, 
+suggesting a potential solution to a longstanding problem. 
 \end{abstract}
 
+%%\maketitle
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Cataclysmic Variables (CVs), are systems in which a white dwarf accretes matter from a donor star
-via Roche-lobe overflow. In Disk-dominated CVs, this accretion is mediated by an accretion disk which forms 
-around the white dwarf, and it has been shown that the spectra of high state CVs
-exhibit absorption features believed to be caused by an outflow, potentially line-drive,
-rising from the accretion disk.
+Non-magnetic Cataclysmic Variables (CVs), are systems in which a white dwarf accretes matter from a donor star
+through Roche-lobe overflow onto an accretion disk. It has been shown that the spectra of high state CVs
+exhibit absorption features believed to be caused by an outflow, potentially line-driven,
+rising from the accretion disk \citep{cordova1982}. 
+The ultraviolet spectra of CVs, in particular, exhibit P-Cygni like profiles in resonance lines such as 
+NV, OVI and, most commonly, CIV. This hints at the possibility of the wind being line driven, 
+as these resonance lines must experience a line force if they are photoionised by a disk or other photon source
+close to the centre of the system.
 
-The ultraviolet spectra of CVs, in particular, exhibity P-Cygni like profiles in resonance lines such as 
-NV, OVI and, most commonly, CIV.
+Multiple attempts have been made to model UV wind spectra by treating the wind
+as a biconical flow arising from the accretion disk, and conducting radiative transfer simulations to attempt
+to reproduce the resonance lines that appear in the spectra. The first generation of models
+applied knowledge gleaned from stellar wind modeling to the problem (Mauche \& Raymond
+1987; Drew 1987; Vitello \& Shlosman 1988), showing that mass loss rates of $\sim10\%$ of the accretion rate
+ were required to produce the required line strengths.
+Shlosman \& Vitello (1993; hereafter SV93) describe a radiative transfer code which first computes
+an ionization structure based on constant wind temperature, and then used the Sobolev approximation
+for line transfer.
+
+%% reorganise, mention SW Sex, UX UMa systems?
 
@@
 
-\py is a Monte Carlo radiative transfer code which uses the Sobolev approximation. It is originally
-introduced by Long \& Knigge (2002), and a more up-to-date description is provided by
-Higginbottom et al. (2013).
+\py is a Monte Carlo radiative transfer code which uses the Sobolev approximation.  
+It expands on the work of SV93 and also incorporates techniques described by
+Lucy (1999a, 1999b, 2002, 2003). The code is first described by Long \& Knigge (2002),
+who synthesized the UV spectra of CVs, successfully reproducing P-Cygni resonance line profiles
+whilst solving self-consistently for the thermal balance and ionization structure in the wind
+according to the method of Mazzali \& Lucy (1993). \py has since been used with application
+to QSO wind modeling \citep{higginbottom2013}, which involved a new ionization scheme to deal with the
+more complex power-law spectrum, and encorporation os processes such as Compton scattering in order
+to correctly treat X-ray radiation transfer. In addition, \citep{simmacro2005} modeled
+Brackett and Pfund line profiles in YSOs using \py, using the macro atom scheme outlined by Lucy (2002, 2003) applied
+to a Hydrogen-only model.
+
+Here, we 
+model the UV resonance lines in much the same way as LK02, using the 
+fast two-level atom approximation which is appropriate for treating transitions with strong
+coupling to the ground state. However, our model has one crucial difference to LK02, as we use
+the macro atom scheme in tandem with this method. Hydrogen and Helium are treated
+as macro atoms in an attempt to provide a better treatment of optical recombination lines (e.g. the Balmer series, He II 4686, He I lines),
+Lyman-$\alpha$, and the recombination continuum which is suspected to play a key role in `filling-in' the Balmer
+photoionization edge (see e.g. Knigge \& Drew 1998).
 
 \subsection{Macro-atoms}
-In its standard operating mode, \py uses a two-level atom approximation (see e.g Mihalas 1982\nocite{mihalas}, Ch.
-11) for its treatment of lines.
+In its standard operating mode, \py uses a two-level atom approximation \cite[see e.g.][]{mihalas} for its treatment of lines.
 This approximation works well when treating so-called `resonance lines' (such as \civ, O\textsc{vi}), in which the excited electron is strongly coupled to the ground state, but breaks down for more complex situations such as recombination cascades.
@@
 
+\subsection{Atomic Data}
+
+Atomic data is obtained from the same sources described in LK02 and updated in H13. 
+The additional level and line information required to treat Helium as macro atom was 
+obtained from \textsc{Topbase} \citep{topbase2005}. We treat Hydrogen as a 20-level atom as in S05, where 
+each level is defined by the principal quantum number n, which is appropriate due to
+the degeneracy of each level in the Hydrogen atom. Helium II is treated in much the same way,
+with 10 levels, but He I has larger energy differentials between different l subshells
+and triplet and singlet states. Thus, we still include levels up to n=10 but explicitly 
+treat the l-subshells as distinct levels instead of assuming they are perfectly `l-mixed',
+which will have the pleasant side effect having the potential to produce triplet lines.
+
+\subsection{Ionization scheme}
+
+Although H13 developed a new ionization scheme which approximates the 
+SED in a cell with a broken power law, here we follow LK02 in using the
+ionization scheme presented by Mazzali \& Lucy (1993), who specifically
+present the formula 
+\begin{equation}
+\frac{n_{j+1} n_e}{n_j} = W [\xi + W(1-\xi)]
+\left(\frac{T_e}{T_R}\right)^{1/2}
+\left(\frac{n_{j+1}n_e}{n_j}\right)^*_{T_R}, \label{ionization}
+\end{equation}
+which, in principle, accounts for ionizations from and
+recombinations to all levels of an ion. In this equation, the last
+(``starred'') term on the right hand side refers to the Saha
+abundances, $W$ is an effective dilution factor, $\xi$ is the
+fraction of recombinations going directly to the ground state, and
+$T_R$ and $T_e$ are the radiation and electron temperature
+respectively. LK02 provide a full description of our implementation.
+
+The reason for using this scheme 
+is twofold; First, the SED can be approximated well by a Blackbody due to the 
+absence of an X-ray source, and therefore the blackbody treament is appropriate; 
+Second, this provides continuity from LK02 and allows us to do a like-for-like comparison,
+which is especially useful in assessing the improvement in Hydrogen line emission, and any changes
+that might occur in the ionization stages of the resonance line species such as CIV.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Testing the macro atom scheme}
+\section{Code Validation and Testing}
+\subsection{Ionization}
+
+LK02 presented comparisons of between \py and the widely used photoionization code Cloudy, showing good agreement 
+of calculated ion fractions between the code. In addition, \cite{tardis} present a code for 
+spectral synthesis of Supernova (\textsc{TARDIS}) which compares spectra from a homologous spherical model with
+the ML92 ionization scheme. We are therefore confident that our treatment for so-called `simple ions' is correct.
+
+To verify that the macro atom treatment is correct, it is important to compare level population tests 
+fro Hydrogen and Helium with that expected from literature. In addition, we check that the dual macro atom/simple ion
+implementation still shows good agreement with Cloudy.
+
+\subsection{Non-LTE Level Populations}
 
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{caseA.png}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/seaton_emissiv.png}
 \caption{Case A comparison between S59 and \py at 10000K and 20000K}
+\label{seaton}
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{caseB.png}
-\caption{Case B comparison between S59 and \py at 10000K and 20000K}
-\end{figure}
+%\begin{figure}
+%\includegraphics[width=0.5\textwidth]{figures/caseA.png}
+%\caption{Case A comparison between S59 and \py at 10000K and 20000K}
+%\end{figure}
+
+%\begin{figure}
+%\includegraphics[width=0.5\textwidth]{figures/caseB.png}
+%\caption{Case B comparison between S59 and \py at 10000K and 20000K}
+%\end{figure}
 
@@
 
+Figure 3 shows a comparison between the macro atom mode and standard mode of the code using the SV93 model. The ionization state is remarkably similar.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
-%          MATOM TESTING
+%          THE MODEL
 %
@@
 
-\section{The CV Model}
-As in LK02, we follow the prescription of SV93 in both our fundamental biconical wind model and velocity law
+\section{The Benchmark CV Model}
+\subsection{Description of Model: Geometry and Kinematics}
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/fig1.eps}
+\caption{Cartoon illustrating the three broad classes of sightline discussed in the text.}
+\label{cartoon}
+\end{figure}
+
+As in LK02, we follow the prescription of SV93 in both our fundamental biconical wind model and velocity law. 
+The poloidal velocity, $v_l$, along a streamline in our model is given
+by 
+\begin{equation}
+v_l=v_0+\left[v_{\infty}(r_0)-v_0\right]\frac{\left(l/R_v\right)^{\alpha}}{\left(l/R_v\right)^{\alpha}+1},
+\label{v_law}
+\end{equation}
+where $l$ is distance measured along a poloidal streamline. This
+power-law velocity profile was adopted by SV93 in order to give a 
+continuous variation in the derivative of the velocity and a 
+realistic spread of Doppler-shifted frequencies in the outer portion
+of the wind (${l > R_v})$. We have similar requirements.
+The initial poloidal velocity of the wind, $v_0$ is (somewhat
+arbitrarily) set to $6~\rm{km~s^{-1}}$ for all streamlines, comparable
+to the sound speed in the disk photosphere. The
+wind then speeds up on a characteristic scale length $R_v$, 
+defined as the position along the poloidal streamline at which the
+wind reaches half its terminal velocity, $v_{\infty}$.
+The terminal poloidal velocity along each streamline is set to a fixed
+multiple of the escape velocity at the streamline foot point, 
+\begin{equation}
+v_{\infty}=fv_{esc},
+\label{v_infty}
+\end{equation}
+so the
+innermost streamlines reach the highest velocities.
+The power-law index $\alpha$ controls the shape of the velocity
+law: as $\alpha$ increases, the acceleration is increasingly
+concentrated around $l = R_v$ along each streamline. 
+For large $\alpha$, the initial poloidal velocity
+stays low near the disk and then increases quickly through $R_v$ to 
+values near $v_\infty$.
+
+Table~\ref{wind_param} shows the parameters used in the wind model, and Figure~\ref{cartoon}
+shows a sketch of the geometry of our model, with the key parameters labeled.
+
+\begin{table}
+\centering
+\begin{tabular}{p{3cm}p{4cm}}
+\hline Free Parameters 	&	 Value \\ 
+\hline \hline 
+$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
+$\dot{M}_{acc}$ 	 &	 $3.16\times 10^-9~M_{\odot}yr^{-1}$\\ 
+$\dot{M}_{wind}$  &	$3.16\times 10^-8~M_{\odot}yr^{-1}$\\ 
+$r_{min}$ 	&	 $4 R_{WD}$\\ 
+$r_{max}$ 	&	 $12 R_{WD}$ \\ 
+$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
+$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
+$\lambda$ 	&	 $0$ \\ 
+$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
+$R_v$ 	        &	 $7\times10^{11}$cm \\ 
+$\alpha$ 	&	 $1.5$ \\
+\end{tabular}
+\centering
+\caption{Wind geometry parameters used in the benchmark CV model.}
+\label{wind_param}
+\end{table}
+
+\subsection{Disk Treatment}
+\py has has some flexibility when treating the accretion disk as a source of photons, in which the disk is broken down into annuli 
+such that each annulus contributes an equal amount to the bolometric luminosity. Each annulus can 
+be treated either as a blackbody with the corresponding temperature or as a Kurucz stellar atmosphere model (REF)
+with the appropriate surface gravity and temperature. Both of these methods have flaws. It is known
+from studies of CV accretion disks that they exhibit absorption cores, which can inpact the overall spectrum 
+even if a wind is present (REF), so the blackbody treatment is not complete. However, the stellar atmosphere
+models also have problems \cite{wadedisk}, and there are clear inconsistencies with using a stellar atmosphere beneath a dense
+wind region which itself goes some way to simulating the disk atmosphere. Here we use the Kurucz models,
+partly because they provide the most pessimistic prediction due to the strong absorption beyong the Balmer edge, 
+which is required to be filled in by the recombination emission in the wind (see Section~\ref{balmerjump}).
+
+\subsubsection{Boundary Layer}
+Whether we include one, why why not, referring to He II and ionization.
+
+\subsection{Synthetic Spectra}
+Present the spectra.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{figures/smplot.pdf}
+\caption{Synthetic Spectra computed for sightlines of 22.5, 25, 62.5 and 80 degrees.}
+\end{figure}
+
+\subsection{Ionization State}
+Present the ionization state with wind plots showing dominant ions.
 
@@
 
-\section{Results from Simulations}
+\section{Discussion of Results}
+
+\subsection{The Balmer Series}
+
+\subsection{UV Resonance Lines}
+\subsubsection{OVI and the Auger effect}
+
+\subsection{The Balmer Jump}
+\label{balmerjump}
+
+\subsection{Helium Lines}
+
+\subsection{The Line Force}
 
@@
 
-\section{Discussion}
+\section{Conclusions and Future Work}
 
@@
 
+\subsection{Acknowledgements}
+%The work of NH, JHM and CK is supported by the Science and Technology Facilities Council (STFC), via studentships and a consolidated grant, respectively.
+In particular, we would like to thank Juan Hernandez Santisteban for useful conversations, and for his help extracting SDSS spectra.
+%The authors acknowledge the use of the IRIDIS High Performance Computing Facility, and associated support services at the University of Southampton, in the completion of this work.
+
 \bibliography{mybib.bib}

### 2014-08-15 scripts/mnras.py
A draft version

@@ -10,14 +10,28 @@ texfile =  open(filename, "r")
 outfile = open(outfilename, "w")
 
 
-outfile.write("\documentclass[useAMS,usenatbib]{mn2ejm}\n")
+outfile.write("\documentclass[useAMS,usenatbib]{mn2e}\n")
+
+fig_env = False
 
 for line in texfile:
 	if "begin{abstract}" in line:
 		outfile.write("\maketitle\n")
 		outfile.write(line)
 
+	elif "fullpage" in line and "begin{figure}" in line:
+		if fig_env == False:
+			outfile.write("\\begin{figure*}\n")
+			fig_env = True 
+
+	elif fig_env and "end{figure}" in line:
+		outfile.write("\end{figure*}")
+		outfile.write("\n")
+		fig_env = False 
+
 	elif "documentclass" not in line and "maketitle" not in line:
 		outfile.write(line)
+
+
 
 outfile.close()

### 2014-08-15 draft.tex
Draft version, 150814

%%%% Various options for document class.
%\documentclass[usenatbib, a4paper]{preprint}
\documentclass[preprint, a4paper, 11pt]{aastex}
%%\documentclass[twocolum]{revtex4}
%%\documentclass{report}
%%\documentclass[useAMS,usenatbib, onecolumn]{mn2ejm}

%\usepackage{psfig,morefloats,url}
%use preprint2 for 2 columns paper.

%% declare any packages used
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{color}
\usepackage{pdfpages}
\usepackage{appendix}
\usepackage{subfigure}
%\usepackage{epsfig}
%\usepackage[dvips]{color}
%\usepackage{aabib}

%\marginparwidth = 25pt
\citestyle{aa}
\addtolength{\topmargin}{-.5in}
%% This command added as margins are wrong in mn2e, it appears. 
%% Not needed for other classes

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%% define bibstyle and other definitions
\bibliographystyle{aabib}
%% renew commands
\renewcommand{\labelitemi}{$-$}
\def\py{\textsc{Python} }
\def\tar{\textsc{Tardis} }
\def\cld{\textsc{Cloudy} }
\def\civ{C~\textsc{iv} }
\def\araa{ARAA}
\def\nat{Nature}
\def\apjl{ApJ Letters}
\def\aapr{AAPR}
\def\ssr{SSR}
\def\apj{ApJ}
\def\pasp{PASP}
\def\aap{A\&A}
\def\mnras{MNRAS}
\def\aj{AJ}
\def\rmxaa{RMXAA}

%% define some control sequences for lines
\def\heiiopt{He~\textsc{ii}~$\lambda4686{\rm \AA}$}
\def\heiiuv{He~\textsc{ii}~$\lambda1640{\rm \AA}$}
\def\heiioptnew{He~\textsc{ii}~$\lambda3202{\rm \AA}$}
\def\la{Ly-$\alpha$}
\def\ha{H$\alpha$}
\def\hb{H$\beta$}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          TITLE AND AUTHORS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\title{Modeling the Optical Spectra of Cataclysmic Variables: The Importance of Disk Winds}
\title{Disk Winds Matter: Simulating the Optical Spectra of Cataclysmic Variables}
\author{J. H. Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}
%%\altaffiltext{1}{School of Physics \& Astronomy, University of Southampton,
  %%Southampton, SO17 1BJ, UK}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          ABSTRACT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
High-State non-magnetic Cataclysmic Variables (CVs) 
exhibit strong Hydrogen \& Helium recombination lines in their optical 
spectra. These lines can be single peaked, and may be formed 
in the same bipolar outflow that is responsible for the
blue-shifted absorption lines seen in the Ultraviolet (UV).
Here we present results obtained by incorporating a `macro-atom' treatment into
our Monte Carlo radiative transfer code, which was
originally used to synthesize the UV spectrum of a disk-dominated CV 
with a simple biconical wind. Using an identical model, we show that the wind leaves a noticeable imprint 
on the optical spectrum, producing He II 4686 and H${\alpha}$ as well as
enhanced emission in the Ly-$\alpha$ and He II $1640$ UV lines.
In addition, the improved treatment of recombination means that the bound-free continuum
emission is enhanced, albeit by a modest amount.
A short exploration of a 3-variable kinematic parameter space leads to models with higher densities 
that are able to produce single-peaked line emission, and also generate sufficient recombination emission
to fill in the Balmer jump photoabsorption edge. 
Finally, we present a synthetic spectrum of a next generation model in and out of eclipse,
and identify the strengths and shortcomings of the model in the context of the high inclination
Nova-like variable RW Tri.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          INTRODUCTION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Outflows are
close to ubiquitous  in accreting systems across many order of magnitude in mass,
from young stellar objects \citep{bunn1995} right up 
to quasi-stellar objects \citep[QSOs;][]{ganguly2008}. Outflows can take the form of jets, such as those
seen in X-ray binaries \citep{fender2006} or active galactic nuclei \citep[AGN;][]{marscher2006}, but can also manifest as `winds' emanating from
the accretion disk.
Understanding the impact of accretion disk winds on spectral features has far-reaching implications. 
They provide a feedback mechanism to limit the growth of black holes in AGN \citep{silkrees1998},
and their ever-present nature implies a deep connection with the accretion process. This connection
is important to understand in order to probe the universality of accretion \citep{mchardy2006, SKUK2012}, 
and to determine the true extent to which
accretion disks conform to the `$\alpha$-disk' model proposed by 
\cite{shakurasunyaev1973}. 
Despite this, in many types of systems the impact of winds on observational
features is somewhat unknown, and many theoretical questions relating to their origin 
and driving mechanism remain unanswered.

Cataclysmic variables (CVs) are systems in which a white dwarf accretes matter from a donor
star via Roche-lobe overflow. In non-magnetic, disk-dominated systems this accretion
is mediated by an accretion disk which forms around the white dwarf. 
Nova-like (NL) variables are a particular subclass of object in which the accretion disk
is in a permanent state of relatively high accretion rate 
($\dot{M} \sim 10^{-8}$~M$_{\odot}$~yr$^{-1}$),
making them the perfect laboratories to test the $\alpha$-disk model.
For over three decades, it has been known that winds emanating from the accretion disk
are important in shaping the ultraviolet (UV) spectra of high-state CVs (Heap 1978), 
the most spectacular evidence being the P-Cygni like profiles of resonance lines such as 
C${\textsc {iv}}$ (see e.g. Cordova \& Mason 1982\nocite{cordova1982}).

While the effect of the wind on the UV is at least partially clear, it may also have more subtle 
effects across the spectral range. It has been proposed that an accretion disk wind
can cause single-peaked emission line profiles in the optical (Murray \& Chiang 1996), 
such as those seen in Nova-like variables and SW Sex stars (Honeycutt, Schlegel,
\& Kaitchuck 1986; Dhillon \& Rutten 1995). It is particularly telling that single-peaked 
lines can be seen even in eclipse, suggesting 
that a spatially extensive wind may be the source of emission (see figure~\ref{novalikes}).
%%(Honeycutt, Schlegel, \& Kaitchuck 1986; Dhillon \& Rutten 1995). 
Further evidence of the influence of winds in the optical can be seen in P-Cygni like signatures,
observed in lines such as H$_{\alpha}$ and He \textsc{i} $\lambda5876$ \citep{RN98}.
In addition, \cite{KLWB98} suggested
that recombination continuum emission from a disk wind or atmosphere
could be responsible for filling in the Balmer absorption edge. This provides
a potential explanation for
the absence of a pronounced `Balmer jump' in optical spectra of CVs, which has never been adequately produced 
by theoretical models or spectral synthesis.
This dense disk atmosphere or wind transition region
necessary to produce the required recombination emission
could also explain the Fe~\textsc{ii} `curtain'
seen in near-UV observations of the high inclination dwarf nova OY Car in queiscence 
\citep{horne1994}.

\begin{figure}	%fullpage
\centering
\includegraphics[width=0.8\textwidth]{figures/fig1.eps}
\caption{Optical spectra of three nova-like variables: 
RW Sex (Top; Beuermann et al. 1992),
IX Vel (Middle; Beuermann \& Thomas 1990)
and RW Tri in eclipse (Bottom; Groot et al. 2004).
The data have been digitized from the respective publications. 
These systems have inclinations of $30^\circ$, $60^\circ$ and $70^\circ$ 
respectively.
The trend of increasing Balmer line emission with inclination can be seen.
In RW Tri strong single-peaked emission in the Balmer lines is seen even
in eclipse, indicating that the lines may be formed in a spatially extensive disk wind, and there is even a suggestion
of a (potentially wind-formed) recombination continuum in the eclipsed spectrum.}
\label{novalikes}
\end{figure}

The first attempts to model disk winds in CVs applied techniques used in stellar
wind modeling to an accretion disk geometry (Mauche \& Raymond
1987; Drew 1987; Vitello \& Shlosman 1988), and showed that mass loss rates of
$\sim10\%$ of the accretion rate
were required to produce the observed line strengths.
Using spectral synthesis codes to model resonance scattering,
Shlosman \& Vitello (1993; hereafter SV93) and Knigge, Woods \& Drew (1995; hereafter KWD95)
were both successful in reproducing the observed spectra such as the P-Cygni like
profiles in C\textsc{iv}~$\lambda1549$\AA.
Long \& Knigge (2002) expanded on the above work by presenting our code, which
solved self-consistently for thermal and ionization balance in the wind
according to the methods of Mazzali \& Lucy (1993; ML93). They successfully reproduced
UV resonance lines profiles and presented a synthesized spectrum of Z Cam
that agreed well with the observed features. Noebauer et al. (2010) expanded on this
by carrying out more detailed comparisons to RW Tri and UX UMa. In addition to these 
radiative transfer calculations, some work has also been done using Hydrodynamic wind models, 
such as that by \cite{pkdh2002}, and more recently by \cite{kusterer2014} with application to
AM Canum Venaticorum stars.

Here we present work using the same Monte Carlo radiative transfer code as LK02, but incorporating additional 
`macro-atom' techniques suggested by Lucy (2002, 2003) to improve our treatment of the Hydrogen and Helium
optical lines, as well as recombination continuum emission. 
In section 2 we present the code
and provide a brief description of macro-atoms and the radiative transfer methods we employ. 
We describe the kinematics and geometry of our biconical wind model in section 3.
In section 4 we present a benchmark model, which is discussed in section 5 with particular attention 
devoted to a small-scale parameter search.
Finally, in section 6, we summarise our findings, and outline areas for future work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          THE CODE, RADIATIVE TRANSFER
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Radiative Transfer}

\py is a Monte Carlo (MC) radiative transfer code which uses
the Sobolev approximation to treat line transfer. It operates 
in two distinct cycles. First, the ionization state, level populations
and temperature structure are calculated. This is done by
flying MC energy quanta through a pre-defined wind geometry and recording
the relevant estimators, before choosing  a new electron temperature 
in an attempt to balance heating and cooling in the plasma.
This process is repeated until the code converges on a 
solution. Second, the spectrum is synthesized by tracking
the energy packets through the wind and computing the 
emergent spectra at a number of user-specified viewing angles.

The code is capable of operating in a number of different
regimes, both in terms of the scale of the system, and the 
shape and characteristic energies of the illuminating spectrum. It is 
first described by LK02, who initially developed a biconical CV 
wind model to synthesize UV spectra. 
Higginbottom et al.\nocite{higginbottom2013} (2013; hereafter H13) presented a 
benchmark model for broad absorption line (BAL) QSOs.
As part of this effort, the ionization scheme was improved so that 
the code was capable of treating the power-law X-ray spectrum
exhibited by AGN.
This involved using a spectral model the mean intensity in a cell
computed from MC estimators for, instead of using a dilute blackbody
approximation. Compton processes
were also incorporated into the heating and cooling balance.
In addition, \cite{simmacro2005} modeled
Brackett and Pfund line profiles in YSOs using \textsc{Python,} which included
implementing a `macro-atom' mode in order to correctly treat the more
complex transition matrix involved in recombination.

\subsection{Macro-atoms}

Previously, \py used a two-level atom approximation \cite[see e.g.][]{mihalas}. This approximation is 
fast, and works well as a first approximation when treating so-called `resonance lines' (such as C\textsc{iv}) 
in which the excited electron is strongly coupled to the ground state.
However, in a number of situations, for example, when a level is primarily populated from above then,
this becomes a poor representation. 
To reproduce recombination lines and lines in which the lower level is not the ground state, 
it is therefore important to use an improved line transfer technique and level population solver.

By quantising matter into `macro-atoms', and radiant and kinetic 
energy into indivisible energy packets (r- and k- packets respectively), 
Lucy (2002, 2003\nocite{lucy2002, lucy2003}; hereafter L02, L03) showed that it is possible 
to asymptotically reproduce the emissivity of a gas in statistical equilibrium 
without simplifying the treatment of line transfer. 
It allows all possible transition paths from a given level and a full non-Local 
Thermodynamic Equilibrium (NLTE) solution for the level populations based on MC estimators. 
For a full description consult L02 and L03.

Macro-atoms have been used to model astrophysical plasmas in 
Wolf-Rayet star winds \cite{sim2004}, AGN disk winds \citep{simlong2008, tatum2012}
and Supernovae \citep{kasen2006, kerzendorfsim}.
Sim et al. (2005) used \py itself to apply this technique to
a Hydrogen-only model. We are now able to adopt a hybrid scheme. 
Any species in which have their level populations determined by
more complex interactions than resonance transitions
can be treated as full macro-atoms. The other species are treated as so-called `simple-ions',
where they still follow the indivisible packet constraint but use the two-level atom approximation.
This allows one to preserve the fast treatment of resonance lines while providing 
an improved representation of, for example, recombination, which is important when modeling features 
such as the Balmer lines and also recombination {\sl continuum} emission. 
Recombination is expected to be an important process in the optical
spectra of CVs, and they thus make a perfect application for Lucy's 
advances in MC methods.

\subsection{Ionization and Excitation}

In our hybrid ionization and excitation scheme, 
simple-ions have their ionization fractions
calculated using a modified Saha equation, and internal level populations are
calculated from LTE. For macro-atoms, we solve the equations of statistical 
equilibrium using MC estimators for the radiation field. This enables us to 
determine the ionization and excitation state of the ions in question.

\subsubsection{Macro-atoms}
% In order to correctly model lines in which the lower level is not the ground state 
% (such as H$\alpha$ \& H$\beta$), and improve the treatment of recombination,
% we treat H \& He as macro-atoms. This is because 
% the levels responsible for the line emission are populated mostly from above.
% Therefore, 
we treat H \& He as macro-atoms. 
Macro-atom NLTE level populations and ion fractions are calculated by solving 
the statistical equilbrium equations between each pair of levels. The rate
between a lower level $l$ and upper level $u$ in an atom is given by

\begin{eqnarray}
{\cal R}_{ul} &= & \beta_{lu} A_{ul} n_l + \beta_{lu} B_{ul} n_l J_{lu}^b + C_{ul} n_u n_e\label{eq:nlte_rul}\\
{\cal R}_{lu} &= & \beta_{lu} B_{lu} n_l J_{lu}^b + C_{lu} n_l n_e,
\end{eqnarray}

where $A$ and $B$ are Einstein coefficients, $C$ is the collisional rate coefficient and
$\beta_{lu}$ is the probability that a given line photon will escape the Sobolev
region. $J^b$ is the MC estimator for mean intensity at the blue wing of the line as 
recorded during the photon propagation. In the context of 
bound-free, we consider rates between the continuum state (or, in the case of ions with more than one 
bound electron, the ground state of the upper ion), $\kappa$,
and lower level $l$,

\begin{eqnarray}
{\cal R}_{\kappa l} &= & \alpha_{\kappa l} n_{\kappa} n_e \\
{\cal R}_{l \kappa} &= & n_l \int_{\nu_0}^{\infty} \frac{ 4 \pi J_{\nu} \sigma_{\nu}}{h \nu} d\nu,
\end{eqnarray}

where $\sigma_{\nu}$ is the photoioniziation cross section, $\alpha_{\kappa l}$ is the recombination
coefficient to level $l$ and $J_{\nu}$ is the mean intensity.
This treatment means that radiative and collisional rates to and from all 
levels are considered when calculating both the ionization state, and the level populations, 
although we neglect photoionization to excited levels of the upper ion. 
The \cite{vanregemorter} approximation is used for collisional transitions,
and thus we assume collisions between radiatively forbidden collisions are
negligible, a reasonable approximation in the regime where levels are mainly populated
by recombination. 
%{2002A&A...384..725L}.  source for beta sobolevs
%$\beta_{lu}=\frac{1}{\tau_{lu}}[1-\exp(-\tau_{lu})]$

\subsubsection{Simple-ions}

C, O, N, Ne, Na, Mg, Al, Si, S, Ar, Ca \& Fe are all included as simple-ions. 
The two-level atom is a first order approximation here, which is appropriate 
when treating resonance lines in which the lower level is at or close to the 
ground state. 
For these elements, we follow LK02 in using the ionization scheme presented by Mazzali \& Lucy (1993). 
Specifically, we use the formula
\begin{equation}
\frac{n_{j+1} n_e}{n_j} = W [\xi + W(1-\xi)]
\left(\frac{T_e}{T_R}\right)^{1/2}
\left(\frac{n_{j+1}n_e}{n_j}\right)^*_{T_R} \label{ionization}
\end{equation}
to solve for the relative ionization fractions. In this equation, the `starred' term on 
the right represents the Saha abundances, in accordance with the notation of Mihalas (1982). 
$W$ is an effective dilution factor, $\xi$ is the
fraction of recombinations going directly to the ground state, and
$T_R$ and $T_e$ are the radiation and electron temperature
respectively. LK02 provide a full description of our implementation.

The reason for using this scheme 
is twofold; First, unlike in H13, the SED can be approximated well by a dilute blackbody due to the 
absence of a power-law X-ray source, and therefore the above modification to the Saha equation
is appropriate; Second, this provides continuity from LK02 and allows us to do a like-for-like comparison,
which is especially useful in assessing the improvement in Hydrogen line emission, and any changes
that might occur in the ionization stages of the resonance line species such as CIV. 
Excitation is then calculated from LTE approximations. 
%This is because the 
% level populations are only important in working out the resonance scattering 
% opacity through the wind when modeling resonance lines.

\subsection{Atomic Data}
Atomic data is obtained from the same sources described in LK02 and updated in H13. 
The additional level and line information required to treat He as macro atom was 
obtained from \textsc{Topbase} \citep{topbase2005}. We treat H as a 20-level atom as in S05, where 
each level is defined by the principal quantum number n, which is appropriate due to
the degeneracy of each level in the H atom. He~\textsc{II} is treated in much the same way,
with 10 levels, but He~\textsc{I} has larger energy differentials between different l subshells
and triplet and singlet states. Thus, we still include levels up to $n=10$ but explicitly 
treat the $l$ and $s$ sub-orbitals as distinct levels instead of assuming they are perfectly `l-mixed',
which also allows the model to produce singlet and 
triplet lines, as seen in optical CV spectra.

\subsection{Code Validation and Testing}

\py has previously been tested against a number of radiative transfer and
photoionization codes. Comparisons of ionization balance with \cld \citep{cloudy2013} 
can be found in LK02 and H13 showing excellent agreement. We have also conducted comparisons
of ionization and spectral synthesis with the supernova code \textsc{Tardis.} \tar is described by
\cite{kerzendorfsim}, and the spectral comparisons can be found therein.
In addition to these code validation efforts, we have also conducted tests of
the macro atom scheme in \py to verify that it does indeed solve for level populations correctly
and produces the correct level emissivities. We have been able to show good agreement with 
Case A and Case B calculations by \cite{seaton1959}, and have tested our level
population solver against \textsc{Tardis.}

%% include figure here

% The left panel of figure~\ref{seaton} shows a comparison
% between our level emissivities for the Balmer series compared with analytic calculations
% by \cite{seaton1959}, showing good agreement in both the Case A and Case B limits 
% (see Osterbrock 1989 for a discussion of these two commonly used approximations\nocite{osterbrock}).
% The right panel of figure~\ref{seaton} shows a comparison of Helium I level populations (the most
% complex ion we currently treat as a macro-atom) between \py~and \tar~models. Considering the 
% two codes use different atomic data and \textsc{Tardis,} unlike \textsc{Python,} currently has a complete treatment of
% collisions between radiatively forbidden transitions, the factor of $<2$ agreement is 
% encouraging.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          THE MODEL
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{A Biconical Wind CV Model}

Here we describe some of the features of our biconical wind model. Our aim here is not
to provide a `best fit' model to the data, but rather to use as a starting point
the types of models which have already been successful in explaining UV spectra of CVs,
and examine their effect on the optical features when the treatment of line transfer
is improved.

\subsection{Description of Model: Geometry and Kinematics}

Our model follows the prescription outlined by Schlosman \& Vitello (1993; SV93). A schematic is shown
in figure~\ref{cartoon}. A smooth, biconical
disk wind rises from the accretion disk between radii $r_{min}$ and $r_{max}$. The covering fraction of the wind is 
controlled by the opening angles of the wind, $\theta_{min}$ and $\theta_{max}$, and the launch angle of
the other streamlines is given by

\begin{equation}
\theta(r_0) = \theta_{min} + (\theta_{max} - \theta_{min}) \left(\frac{r_0 - r_{min}}{r_{max} - r_{min}} \right)^{\gamma},
\label{theta}
\end{equation}

where $r_0$ is the launch radius of the streamline.
As in LK02, we follow SV93's power law
velocity profile. The poloidal velocity, $v_l$, in our model is given by

\begin{equation}
v_l=v_0+\left[v_{\infty}(r_0)-v_0\right]\frac{\left(l/R_v\right)^{\alpha}}{\left(l/R_v\right)^{\alpha}+1},
\label{v_law}
\end{equation}

where $l$ is distance measured along a  streamline. $v_{\infty}$, the 
terminal velocity, is set to a fixed multiple of the escape velocity at the bottom
of a streamline, and $v_0$ is a constant launch velocity (set to $6$~km~s$^{-1}$).
Once the wind is launched, it accelerates with a characteristic acceleration
length $R_v$, and $\alpha$ is an exponent which controls how quickly the 
wind accelerates. Larger values of $\alpha$ cause the main region of 
acceleration to occur close to $R_v$, whereas smaller values will lead
to a fast acceleration close to the disk (see figure~\ref{acc_law}).
SV93 chose this velocity law so as to give a 
velocity gradient that varied continuously along a streamline, as well
as producing line profiles with realistic velocity spreads.
In addition to these motivations, adopting a consistent velocity law 
allows for direct comparison with models which have already been successful in 
simulating UV resonance line profiles, such as those presented by LK02 and SV93.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/fig2_cartoon.eps}
\caption{Cartoon illustrating the geometry and kinematics of the benchmark CV wind model.}
\label{cartoon}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/acc_law.eps}
\caption{
The velocity law in our model for various values of
the acceleration exponent.
}
\label{acc_law}
\end{figure}

\begin{table}
\centering
\begin{tabular}{p{3cm}p{4cm}}
Model A \\
\hline Free Parameters 	&	 Value \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
$\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
$r_{min}$ 	&	 $4 R_{WD}$\\ 
$r_{max}$ 	&	 $12 R_{WD}$ \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
$\gamma$ 	&	 $1$ \\ 
$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
$R_v$ 	        &	 $7\times10^{10}$cm \\ 
$\alpha$ 	&	 $1.5$ \\
\end{tabular}
\centering
\caption{
Wind geometry parameters used in the benchmark CV model.}
\label{wind_param}
\end{table}

The principle of mass conservation means that the velocity law also 
controls the density, $\rho$, of the wind, which can be expressed in terms
of radial and vertical position $(r,z)$ as

\begin{equation}
\rho(r,z) = \frac{r}{r_0} \frac{dr}{dr_0} \frac{\phi(r_0)}{v_z(r,z)},
\label{density}
\end{equation}

where $\phi$ here is the mass loss rate per unit area at $r_0$
and $v_z$ is the vertical velocity component. In this model, we
adopt a uniform value for $\phi$.

\subsection{Photon Sources}

MC quanta originate from an accretion disk and a central WD in our model. It is also possible to include
a boundary layer with user-defined temperature and emitting area. Emission from the wind is dealt with
by reprocessing of the indivisible energy packets originally produced in the disk or central WD.

\subsubsection{Disk Treatment}

\py has has some flexibility when treating the accretion disk as a source of photons. 
The disk is broken down into annuli 
such that each annulus contributes an equal amount to the bolometric luminosity. 
We adopt the temperature profile of a standard \cite{shakurasunyaev1973} $\alpha$-disk.
%shown in figure 1.
An annulus can then
be treated either as a blackbody with the corresponding effective temperature or as a stellar atmosphere model
with the appropriate surface gravity and effective temperature. 
Both of these methods have limitations. It is known
from studies of CV accretion disks that they exhibit absorption cores 
formed in an optically thick disk atmosphere.
This can impact the overall spectrum even if a wind is present 
\citep[see e.g.][]{dhillon1996}.
However, the stellar atmosphere models
have had difficulties reproducing the required spectral shape \citep{wade1988}, 
and there are inconsistencies when using a 
stellar atmosphere beneath a dense
wind region that itself goes some way to simulating the disk atmosphere. 
In addition, \cite{linnell2010} found that deviations from the predicted 
$T\propto r^{-3/4}$ temperature profile are required to fit the data
in certain cases.

We hope that future simulations, coupled with a comparison to data, will 
actually address some of these problems, particularly since
the filtering effect of the wind may cause noteiceable effects
on the colour of the emergent spectrum \citep{hassall}. 
Here we use a blackbody illuminating spectrum
for the ionization cycles (see figure~\ref{sed}) and to compute our MC estimators.
During the spectral synthesis stage of the simulation we use stellar atmosphere models.
This is partly because they provide the most pessimistic prediction in terms of whether recombination emission in the 
wind can fill in the Balmer jump, due to the strong absorption beyond the Balmer edge.
For low temperatures, we use stellar atmospheres computed 
by Kurucz (reference), and for $T>50,000$~K we use models computed with 
\textsc{TLUSTY} \citep{tlusty}. The input spectra are created from these model
atmospheres using \textsc{Synspec}\footnote{http://nova.astro.umd.edu/Synspec43/synspec.html}.
%The temperature profile of our disk,
%with $\dot{M}_{acc} = 10^{-8}~M_{\odot}yr^{-1}$ can be seen in figure~\ref{t_profile}.

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/sed_figure.eps}
\caption{
The spectral energy distribution of the blackbody accretion
disk used in the ionization calculation (thick black line), 
with two boundary layer spectra also plotted.
The positions of the Hydrogen and Helium ionization edges 
are marked with dashed vertical lines.
%The effective temperature of the accretion disk
%in our model, as a function of radius.
}
\label{sed}
\end{figure}

\subsubsection{Boundary Layer}
The existence of a boundary layer in CVs arises naturally from the boundary condition
of the \cite{shakurasunyaev1973} model, since the material at the inner disk
edge must lose angular momentum in order to be deposited on
the surface of the compact object \cite[see e.g.][]{lyndenbell1974}.
Boundary layers are a possible source of
high energy photons which may be responsible for the photoionization of 
He~\textsc{ii}. 
\cite{pringlesavonije1979} predict temperatures of 
$200,000-500,000{\rm K}$ for the boundary layer,
but a number of studies have found difficulties
in producing the required ionization state of the wind
with such a hot, luminous boundary layer 
\citep[see e.g.][]{maucheraymond1987, drewverbunt1985}.
\cite{hoare1991}
use the Zanstra method to find boundary layer temperatures of
$\sim80,000{\rm K}$

It is possible to include a boundary layer in our model which emits 
as a blackbody with the effective temperature

\begin{equation}
T_{bl} = \left[ \frac{L_{acc}}{8 \pi R_* H \sigma} ( 1 - \omega_*/\omega_k)^2 \right]^{1/4},
\label{bl}
\end{equation}

where $L_{acc}$ is the accretion luminosity, $R_*$ is the WD radius, $H$ is the boundary layer height
above the disk plane
and $\omega_*$ and $\omega_k$ are the angular velocities at the WD surface and inner disk edge respectively
\citep{fkrbook}. Note that we assume a cylindrical geometry such that the effective emitting
area is $4 \pi R_* H$. 
In the benchmark model, we follow LK02 in setting the boundary layer
luminosity to zero, and then investigate the effect
of boundary layers with temperatures of $80,000{\rm K}$ and $200,000{\rm K}$ 
on the ionization state of the wind and resulting
spectrum. See section 5 for a discussion.

%Whether we include one, why why not, referring to He II and ionization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          RESULTS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results \& Analysis from a Benchmark Model}

The results in this section were obtained using the geometry described
in section 3. The kinematics and mass loss rate of the wind are identical
to LK02. Photon sources are identical, except that when synthesizing the
spectrum we treat the accretion disk 
as an ensemble of Kurucz and TLUSTY stellar atmosphere models to better 
interpret the behaviour of the Balmer jump. The aim here is to 
take a successful UV wind model, and examine it's effect 
when one utilises the better treatment of lines provided
by the macro-atom scheme.

\subsection{Synthetic Spectra}

\begin{figure} %fullpage
\includegraphics[width=\textwidth]{figures/fig5_uv_opt.eps}
\caption{
UV (left) and Optical synthetic spectra for model B computed at
sightlines of 10,27.5, 45, 62.5 and 80 degrees.	
The inset plots show zoomed-in line profiles for 
\heiiuv and \ha. Double-peaked line emission can be seen in 
\heiiuv, \heiiopt, \ha and some He I lines, but the 
line emission is not always sufficient to overcome the absorption
cores from the stellar atmosphere models.
}
\label{spec}
\end{figure} %fullpage\

Figure~\ref{spec} shows optical synthetic spectra for the benchmark 
model for 5 different sightlines. The first thing to note is that the 
model produces some lines which are strong enough to overcome
the absorption cores lines from the disk. These lines are generally double peaked, 
implying they were formed near the base of the wind where rotational velocity
can still dominate over the slowly increasing poloidal velocity. A Balmer 
jump is present at all inclinations. This is present
in the stellar atmosphere models used to model the disk,
and is not a result of photoabsorption through the wind.
%%%% SAY BALMER JUMP CASUED BY SAs

In fact, the wind has a Balmer jump in emission, but it is not prominent enough
to overcome the intrinsic absorption in the illuminating spectrum. 
Figure~\ref{cont} shows the total escaping spectrum, integrated
over all viewing angles, with the contribution from the disk and wind
also plotted. It shows that the lines are produced in the wind,
and also that the wind is producing a Balmer recombination
continuum, but one which is not yet sufficient to mask the absorption 
intrinsic to the disk SED. This offers a tantalising hint
that modest changes to the kinematics of the wind
may be sufficient to boost the continuum emission of the wind.
Furthermore, it confirms our suspicions that the improved
radiative transfer would cause enhanced recombination emission,
suggesting that, where possible, up to date treatments of
NLTE line transfer should be used in codes such as this.

The prominent P-Cygni profiles in e.g., C\textsc{iv} are still seen
in the UV spectra (see figure~\ref{spec}). In addition, the wind 
now contributes significant Lyman-$\alpha$ and
He~\textsc{ii}~$\lambda1640{\rm \AA}$  emission. 
We note that the ionization state of the wind 
is such that recombination to He~\textsc{ii} is significant, even
without a boundary layer source of higher energy photons.

\begin{figure} 
\includegraphics[width=0.45\textwidth]{figures/fig6_opt_cont.eps}
\caption{Synthetic optical spectra computed for sightlines of 22.5, 25, 62.5 and 80 degrees.}
\label{spec_continuum}
\end{figure}

Clearly, this particular model cannot explain all
the features seen in the optical spectra of Nova-like variables. However,
the wind has a clear effect on the spectral features, and cannot be ignored as 
a both source of line and continuum emission and as a reprocessing `filter'
of the underlying disk spectral energy distribution (SED).

\begin{figure} 
\includegraphics[width=0.5\textwidth]{figures/fig4.eps}
\caption{Total packet-binned spectra across all viewing angles. The top panel shows the total 
integrated escaping spectrum, while the other panels show the contributions from photons that originate
in the disk and wind respectively. Recombination continuum emission blueward of the Balmer 
edge is already prominent relative to other wind continuum processes, but is not sufficient
to fill in the Balmer jump in this specific model}
\label{cont}
\end{figure}

\subsection{Ionization and Temperature Structure}

In addition to producing synthetic spectra, we are also able to 
analyse the physical properties of the outflow.
Figure~\ref{wind} shows various physical properties
of the wind geometry. The ionization structure of the wind
is very similar to the original LK02 model, as one might expect.
He is mostly ionized throughout the wind except for a small region near
the disk which is shielded from the photons produced by the hot inner disk.

C\textsc{iv} is the dominant Carbon ion throughout the wind, allowing
for an absorbing column which covers a large range of velocitieis, and is thus
sufficient to produce the required broad, deep and blue-shifted absorption lines
we expect to see in a large fraction of Nova-likes.

\begin{figure} %fullpage
\includegraphics[width=\textwidth]{figures/fig5.eps}
\caption{Various properties of the wind.}
\label{wind}
\end{figure} %fullpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          DISCUSSION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion of Results}

The benchmark model presented above shows that a wind with the properties
of Model A, a model that successfully reproduces the UV spectral features,
would leave a clear imprint on the optical spectrum. It is important
to understand how changing the kinematics of the wind impacts this
effect. We can therefore examine the evolution
of the spectrum with a few key parameters. In particular, this
will help shed light on the predictions of, e.g., Murray \& Chiang (1996)
and Knigge et al. (1998) regarding the single peaked H$\alpha$ emission
and absence of a pronounced Balmer absorption edge respectively.

\subsection{Exploring Parameter Space}

The amount of line and recombination continuum
emission produced by given ion, $i$, in a plasma of volume $V$
depends on the emission measure, $EM$, defined as

\begin{equation}
EM=\int^V_0 n_e n_i \,dV,
\end{equation}

where $n_i$ is the number density of the ion in question. 
The emission reaching an observer 
also depends on the optical depth along 
the line of sight, which can also significantly affect line profile shapes.
Therefore, any quantity which controls the density profile of the wind
will have a profound impact on both the 
amount of emission and the shape of the escaping line profiles.

As described in section 3, we can alter the density in the wind by 
adjusting the velocity law. We have therefore conducted a limited parameter 
sweep, exploring the effect of changing $R_v$, $\alpha$ and $\dot{M}_W$.

\subsection{The Balmer Lines}

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_alpha.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_beta.eps}}   
}
\caption{
% How the H$\alpha$ and H$\beta$ lines in our model change with the kinematic properties
% of the wind. The three separate panels show three different values of $\dot{M}_W$, 
% while $\alpha$ and $R_v$ are all gradually increased from top to bottom and left to right respectively.
% Larger values of these quantities increase the density at the base of the wind. There is a clear transition
% from double peaked to single peaked behaviour, and at the highest densities the wind
% essentially becomes neutral as the optically thick regions self-shield the wind from photoionizing radiation.
\bf{Each of these figures will highlight the next gen model in bold.
and contain a grid like the above showing a pair of spectral features in
the left and right panels. The grey shaded line will show the benchmark model
for easy comparison.  
The most promising parameters at the moment are acceleration exponent and launch radii.}
}
\label{halpha}
\end{figure} %fullpage

Figure~\ref{halpha} shows how the H$\alpha$ line changes with the kinematics 
of the wind at an inclination of $80^\circ$. For models with lower densities, the
line is double peaked, but we see a transition to a single peaked line when 
a high enough density is reach such that the line becomes optically thick.
This reproduces the behaviour predicted by \cite{MC96}, who suggested that
the poloidal velocity gradient in the wind can be larger than the gradient of 
the Keplerian velocity. This gradient can therefore modify the line profile shape
but requires the line to be optically thick.

\subsection{The Balmer Jump}

\label{balmerjump}
\begin{itemize}
\item that we are able to fill in the Balmer jump with the recombination continuum from the wind
if the EM is high enough
\item How this changes with inclination
\item Comparison to literature
\item Discussion of disk atmosphere treatment and its effect.
\end{itemize}

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_1640.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_4686.eps}}   
}
%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
\caption{
The evolution of the He II lines with the kinematic properties
of the wind. 
% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
% when the wind becomes a neutral absorbing column.
}
\label{jump}
\end{figure}

\subsection{Helium Lines}
Discussion of Helium lines in the spectrum.
\begin{itemize}
\item He II 4686, He II 1640 strengths
\item Make the prediction that if 4686 is strong we might expect strong He II 3202. 
\item Discuss why it wouldn't have been seen yet (spectral coverage)
\item Helium I lines
\end{itemize}

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_balmer.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_uv.eps}}   
}
%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
\caption{The evolution of the Balmer jump and C~\textsc{iv} line with the kinematic properties
of the wind. 
% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
% when the wind becomes a neutral absorbing column.
}
\label{jump}
\end{figure}

\subsection{UV Resonance Lines}
Compare spectra to LK02 and other models. Are the spectral features preserved, has anything significant changed.
Lyman alpha?

\subsection{Boundary Layer}
\begin{itemize}
\item discuss the effect of 80000K and 200000K Boundary layers
\item Particularly referring to He II and CIV
\item Our findings support idea that 200000K BL would over ionize the wind- 
we favour 80,000K
\item I'd like to do a hypothetical Zanstra calculation here- state what
temperature our model would predict from the Zanstra method
\end{itemize}

%\subsubsection{The Line Force}
%\begin{itemize}
%\item Can this wind be radiatively driven? 
%\item Why/why not?
%\item Figure showing line force throughout the wind as a fraction of some critical value?
%\end{itemize}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          Comparison with real spectra
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{A Next-Generation Model}

\begin{table}
\centering
\begin{tabular}{p{3cm}p{4cm}}
Model B \\
\hline Free Parameters 	&	 Value \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
$\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
$r_{min}$ 	&	 $4 R_{WD}$\\ 
$r_{max}$ 	&	 $12 R_{WD}$ \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
$\gamma$ 	&	 $1$ \\ 
$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
$R_v$ 	        &	 $1\times10^{11}$cm \\ 
$\alpha$ 	&	 $4$ \\
\end{tabular}
\centering
\caption{Wind geometry parameters used in the next-generation CV model.}
\label{modelb}
\end{table}

With modest changes to the kinematics of the benchmark CV model,
it is possible to produce a `next generation model' with enhanced
line emission that comes closer to reproducing the observed optical spectrum
of a Nova-like variables. The parameters for this model (imaginatively dubbed Model B)
are show in table~\ref{modelb}, and the synthetic spectrum
is shown in figure~\ref{uvoptb}. An in and out of eclipse comparison 
between the synthetic spectrum
at an angle of $80^\circ$ and the high-inclination nova-like RW Tri 
is also shown in figure~\ref{rwtricomp}.

The similarity with the observed spectrum is striking. 
Model B produces strong emission in all the Balmer lines, 
with line to continuum ratios
comparable to those in RW Tri. 
The line to continuum ratio increases during eclipse,
as one expects if the emission is produced in a disk wind, 
thereby mimicking the behaviour of SW Sex stars.
The single-peaked $H\alpha$ line is produced by our models with a 
very similar width to the observed spectrum, although it is perhaps slightly more
`flat-topped' in the synthesized data.

One of the limitations of the model is that, apart 
from in $H\alpha$, the lines are in general double-peaked. 
The lack of high-resolution data in this regard makes detailed analysis difficult,
but it would appear that understanding how single-peaked 
line emission forms and the kinematics and densities required to
modify the line profile is still an open question. 
The major fallback of the next-generation model, however, lies
in the ultraviolet. To get the required emission in the optical lines
and recombination continuum the densities required are very high.
This causes a significant collisionally excited contribution
to the UV lines, meaning that the red wing of the 
resonance species such as C\textsc{iv} no longer matches the
observed profiles.

\begin{figure} %fullpage
\includegraphics[width=\textwidth]{figures/fig14_uv_opt.eps}
\caption{
UV (left) and Optical synthetic spectra for model B computed at
sightlines of 10,27.5, 45, 62.5 and 80 degrees.	
The inset plots show zoomed-in line profiles for 
\heiiuv and \ha. The \ha line 
is single peaked, but higher order lines in the Balmer series
are double-peaked, albeit with narrower profiles.
Strong \heiiopt emission can be seen
}
\label{uvoptb}
\end{figure} %fullpage

\begin{figure} %fullpage
\includegraphics[width=0.8\textwidth]{figures/fig13_eclipse.eps}
\caption{{\sl Top Panel:} In and out of eclipse spectra of the high
inclination Nova-like RW Tri. {\sl Bottom Panel:} In and out of eclipse synthetic
spectra from Model B.}
\label{rwtricomp}
\end{figure} %fullpage

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          Conclusions and Future Work
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}

By taking an already successful model
for the UV wavelength regime of CVs and treating 
it with an improved line transfer scheme, we have shown
that the wind does produce some recombination lines
and continuum emission blueward of the Balmer edge.
We have confirmed a number of the expected trends
by exploring a limited number of parameters governing the
kinematics and geometry of the wind. These include:

\renewcommand{\labelitemi}{$\bullet$}
\begin{itemize}
	\item The `filling-in' of the Balmer jump \citep{elitzur1983} by recombination 
	continuum emission from a disk wind
	\item Single peaked line emission in H alpha produced by 
	the introduction of a poloidal velocity gradient \citep{MC96}
	\item A Balmer decrement consistent with optically thick emission \citep{elitzur1983}.
\end{itemize}
\smallskip

\noindent We also make a number of predictions:

\begin{itemize}
	\item The depth of the Balmer absorption edge decreases with increasing inclination,
or alternatively that the Balmer recombination emission
is enhanced at higher inclinations, {\sl relative to the disk continuum}.
	\item The He~\textsc{ii}~$\lambda3202{\rm \AA}$ line should be
prominent in cases where He~\textsc{ii}~$\lambda1640{\rm \AA}$ \& 
\heiiopt are seen. 
	\item A Balmer jump in emission during eclipse.
\end{itemize}

\smallskip
We have presented a next-generation model
which produces all the prominent lines in and out of eclipse, and
shown that the model exhibits verisimilitude with the optical spectrum of RW Tri.
However, this model does not produce a complete unified CV model, as
the emission lines in the UV are somewhat unrealistic in strength.
This is a shortcoming which must be understood if it is true that
disk winds modify line profiles to become single peaked, as the 
densities required produce a large amount of collisionally excited emission
in UV resonance lines.

Our work demonstrates that, if nothing else,
{\sl disk winds matter}. At a minimum,
they can act as a spectral filter
for the disk spectrum. At a maximum, they may be responsible
for the majority of spectral features of high-state CVs,
and could dominate the appearance of both UV and optical
spectra of these systems.

%% Balmer jump

% \subsection{Future Work}

% To further investigate the true effect of the wind
% we hope that high quality, broadband spectra of 
% Nova-like variables at a range of inclinations 
% will be taken to examine

% In addition to this project, we have started to apply the macro atom scheme to QSOs in order to build on the work of Higginbottom et al. (2013). In particular, we hope that the macro-atom scheme will enable the
% model to produce significant Lyman-$\alpha$ emission, as is observed in QSOs.

\subsection*{Acknowledgements}
The work of JHM, NH and CK is supported by the Science and Technology Facilities Council (STFC), 
via studentships and a consolidated grant, respectively. We would like to thank Juan Hernandez Santisteban and Ivan Hubeny 
for useful discussions. We acknowledge the use of the IRIDIS High Performance Computing Facility, 
and associated support services at the University of Southampton, in the completion of this work.

\newpage
\newpage
\bibliography{mybib.bib}

\end{document}

### 2014-08-19 draft.tex
Version with some bullets, 19/08

@@
 %% renew commands
-\renewcommand{\labelitemi}{$-$}
+\renewcommand{\labelitemi}{$\bullet$}
 \def\py{\textsc{Python} }
@@
 were also incorporated into the heating and cooling balance.
-In addition, \cite{simmacro2005} modeled
+In addition, \cite[][SDL05]{simmacro2005} modeled
 Brackett and Pfund line profiles in YSOs using \textsc{Python,} which included
@@
 in which the excited electron is strongly coupled to the ground state.
-However, in a number of situations, for example, when a level is primarily populated from above then,
+However, in a number of situations, for example, when a level is primarily populated from above, then
 this becomes a poor representation. 
@@
 without simplifying the treatment of line transfer. 
-It allows all possible transition paths from a given level and a full non-Local 
+His macro-atom scheme allows all possible transition paths from a given level and a full non-Local 
 Thermodynamic Equilibrium (NLTE) solution for the level populations based on MC estimators. 
@@
 Macro-atoms have been used to model astrophysical plasmas in 
-Wolf-Rayet star winds \cite{sim2004}, AGN disk winds \citep{simlong2008, tatum2012}
+Wolf-Rayet star winds \citep{sim2004}, AGN disk winds \citep{simlong2008, tatum2012}
 and Supernovae \citep{kasen2006, kerzendorfsim}.
-Sim et al. (2005) used \py itself to apply this technique to
+SDL05 used \py itself to apply this technique to
 a Hydrogen-only model. We are now able to adopt a hybrid scheme. 
@@
 the statistical equilbrium equations between each pair of levels. The rate
-between a lower level $l$ and upper level $u$ in an atom is given by
+between a lower level $l$ and upper level $u$ in an ion is given by
 
@@
 The additional level and line information required to treat He as macro atom was 
-obtained from \textsc{Topbase} \citep{topbase2005}. We treat H as a 20-level atom as in S05, where 
+obtained from \textsc{Topbase} \citep{topbase2005}. We treat H as a 20-level atom as in SDL05, where 
 each level is defined by the principal quantum number n, which is appropriate due to
@@
 $M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
+$R_{WD}$ 	 &	 $7\times10^{8}$cm\\ 
 $\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
@@
 $v_{\infty}$ 	&	 $3v_{esc}$ \\ 
-$R_v$ 	        &	 $7\times10^{10}$cm \\ 
+%%$R_v$ 	        &	 $7\times10^{10}$cm \\ 
+$R_v$ 	        &	 $100 R_{WD}$ \\ 
 $\alpha$ 	&	 $1.5$ \\
@@
 actually address some of these problems, particularly since
-the filtering effect of the wind may cause noteiceable effects
+the filtering effect of the wind may cause noticeable effects
 on the colour of the emergent spectrum \citep{hassall}. 
@@
 %with $\dot{M}_{acc} = 10^{-8}~M_{\odot}yr^{-1}$ can be seen in figure~\ref{t_profile}.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{figures/sed_figure.eps}
-\caption{
-The spectral energy distribution of the blackbody accretion
-disk used in the ionization calculation (thick black line), 
-with two boundary layer spectra also plotted.
-The positions of the Hydrogen and Helium ionization edges 
-are marked with dashed vertical lines.
-%The effective temperature of the accretion disk
-%in our model, as a function of radius.
-}
-\label{sed}
-\end{figure}
 
@@
 \citep[see e.g.][]{maucheraymond1987, drewverbunt1985}.
-\cite{hoare1991}
+Hoare \& Drew (1991; HD91) \nocite{hoare1991}
 use the Zanstra method to find boundary layer temperatures of
@@
 \begin{equation}
-T_{bl} = \left[ \frac{L_{acc}}{8 \pi R_* H \sigma} ( 1 - \omega_*/\omega_k)^2 \right]^{1/4},
+T_{bl} = \left[ \frac{L_{acc}}{8 \pi R_{WD} H \sigma} ( 1 - \omega_*/\omega_k)^2 \right]^{1/4},
 \label{bl}
@@
 
-where $L_{acc}$ is the accretion luminosity, $R_*$ is the WD radius, $H$ is the boundary layer height
+where $L_{acc}$ is the accretion luminosity, $R_{WD}$ is the WD radius, $H$ is the boundary layer height
 above the disk plane
 and $\omega_*$ and $\omega_k$ are the angular velocities at the WD surface and inner disk edge respectively
-\citep{fkrbook}. Note that we assume a cylindrical geometry such that the effective emitting
+\citep{fkrbook}. Note that we adopt a cylindrical geometry such that the effective emitting
 area is $4 \pi R_* H$. 
@@
 spectrum. See section 5 for a discussion.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{figures/sed_figure.eps}
+\caption{
+The spectral energy distribution (SED) of the blackbody accretion
+disk used in the ionization calculation (thick black line), 
+with two boundary layer spectra also plotted.
+The SED for an accretion disk
+with the parameters used by HD91 in their Zanstra method calculations is shown in grey. 
+It still assumes a Shakura-Sunyaev temperature profile, but uses
+of $\dot{M}_{acc}= 5\times10^{-9}~M_{\odot}$yr$^{-1}$, and a slightly lower mass
+white dwarf with $M_{WD}=0.7 M_{\odot}$ and $R_{WD} = 7\times10^{8}$cm.
+The positions of the Hydrogen and Helium ionization edges 
+are marked with dashed vertical lines.
+%The effective temperature of the accretion disk
+%in our model, as a function of radius.
+}
+\label{sed}
+\end{figure}
 
@@
 NLTE line transfer should be used in codes such as this.
-
 The prominent P-Cygni profiles in e.g., C\textsc{iv} are still seen
@@
 He~\textsc{ii}~$\lambda1640{\rm \AA}$  emission. 
-We note that the ionization state of the wind 
-is such that recombination to He~\textsc{ii} is significant, even
-without a boundary layer source of higher energy photons.
+% We note that the ionization state of the wind 
+% is such that recombination to He~\textsc{ii} is significant, even
+% without a boundary layer as a source of higher energy photons.
+
+In addition to producing synthetic spectra, we are also able to 
+analyse the physical properties of the outflow.
+Figure~\ref{wind} shows various physical properties
+of the wind geometry. The ionization structure of the wind
+is very similar to the original LK02 model, as one might expect.
+He is mostly ionized throughout the wind except for a small region near
+the disk which is shielded from the photons produced by the hot inner disk.
+C\textsc{iv} is the dominant Carbon ion throughout the wind, allowing
+for an absorbing column which covers a large range of velocitieis, and is thus
+sufficient to produce the required broad, deep and blue-shifted absorption lines
+we expect to see in a large fraction of Nova-likes.
 
@@
 \includegraphics[width=0.45\textwidth]{figures/fig6_opt_cont.eps}
-\caption{Synthetic optical spectra computed for sightlines of 22.5, 25, 62.5 and 80 degrees.}
+\caption{Synthetic optical spectra computed for 
+sightlines of 22.5, 25, 62.5 and 80 degrees.}
 \label{spec_continuum}
@@
 
-In addition to producing synthetic spectra, we are also able to 
-analyse the physical properties of the outflow.
-Figure~\ref{wind} shows various physical properties
-of the wind geometry. The ionization structure of the wind
-is very similar to the original LK02 model, as one might expect.
-He is mostly ionized throughout the wind except for a small region near
-the disk which is shielded from the photons produced by the hot inner disk.
-
-C\textsc{iv} is the dominant Carbon ion throughout the wind, allowing
-for an absorbing column which covers a large range of velocitieis, and is thus
-sufficient to produce the required broad, deep and blue-shifted absorption lines
-we expect to see in a large fraction of Nova-likes.
-
 \begin{figure} %fullpage
@@
 where $n_i$ is the number density of the ion in question.    
-The emission reaching an observer 
-also depends on the optical depth along 
-the line of sight, which can also significantly affect line profile shapes.
 Therefore, any quantity which controls the density profile of the wind
@@
 amount of emission and the shape of the escaping line profiles.
-
+The emission reaching an observer at a given frequency
+also depends on the sobolev optical depth it experiences, which depends on both
+the density and the velocity gradient projected
+along the line of sight. This can also significantly affect line profile shapes.       
 As described in section 3, we can alter the density in the wind by 
-adjusting the velocity law. We have therefore conducted a limited parameter 
-sweep, exploring the effect of changing $R_v$, $\alpha$ and $\dot{M}_W$.
-
-\subsection{The Balmer Lines}
+adjusting the velocity law (which also determines the velocity gradient).
+
+We have therefore conducted a limited parameter 
+sweep, exploring the effect of changing a few key parameters.  We focus on 
+4 variables in order to explore the trends in our model. These are:
+
+\begin{itemize}
+ 	\item  The acceleration length, $R_v$, which controls the characteristic scale
+ 	over which the wind accelerates.
+ 	\item The acceleration exponent, $\alpha$, which focuses the acceleration
+ 	around $R_v$. A higher value of $\alpha$ therefore leads to a slowly accelerating 
+ 	wind with a dense base.
+ 	\item The launch radii of the wind, $r_{min}$ \& $r_{max}$.
+ 	\item The temperature of the boundary layer, $T_{bl}$.
+ \end{itemize}
+
+We have found these to be important parameters in modifying 
+the spectral features and ionization state of the wind.
+In general, quantities which cause a denser wind base increase
+the overal emission, although optical depth effects can clearly cause 
+the relationship to become more complicated.
+
+\subsection{Line Profiles: Shapes and Intensities}
+
+\noindent\rule{16cm}{0.4pt}
+
+{\bf
+\noindent key points here:
+
+\begin{itemize}
+	\item producing single peaked line profiles is difficult to say the least
+	\item with our high density models we can produce some single peaked line emission,
+	mostly in Halpha and beta. the other lines seem to stay double peaked.
+	\item this higher density causes (too much) collisionally excited line emission from CIV
+	\item if the wind was more equatorial then this might help, but this isn't really supported by observations.
+	\item we can definitely reproduce the behaviour predicted by Murray and Chiang
+	\item Comment on the observed Balmer decrement being fairly flat, as is observed. Point out that
+	this is necessary if H alpha is to be single peaked, as you need significant optical depths.
+\end{itemize}
+}
+
+\noindent\rule{16cm}{0.4pt}
 
@@
 \mbox{
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_alpha.eps}}
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_alpha_0.eps}}
 \quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_beta.eps}}   
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_beta_0.eps}}   
 }
@@
 
-Figure~\ref{halpha} shows how the H$\alpha$ line changes with the kinematics 
-of the wind at an inclination of $80^\circ$. For models with lower densities, the
+Figure~\ref{halpha} shows how the H$\alpha$ and H$\beta$ lines change with the kinematics 
+of the wind at an inclination of $80^\circ$. For H$\alpha$, in models with lower densities, the
 line is double peaked, but we see a transition to a single peaked line when 
@@
 the poloidal velocity gradient in the wind can be larger than the gradient of 
-the Keplerian velocity. This gradient can therefore modify the line profile shape
-but requires the line to be optically thick.
+the Keplerian velocity. This gradient can therefore modify the line profile shape.
+It is clear from the behaviour of H$\beta$
+
+In order to produce single-peaked line emission at high inclinations,
+it is clear that a higher line opacity is needed at the red and blue wings relative to
+the opacity at line centre. This can be achieved in a number of ways. A more equatorial 
+wind would cause the line opacity at line centre to decrease
+relative to the the wings of the line due to the increased radial component 
+of the velocity gradient.
+
+Our difficulty in producing single-peaked line emission from a full 
+radiative transfer calculation has been encountered before. SDL05 found that a 
+biconical disk geometry similar to that adopted here could not reproduce 
+the observed single peaked profiles in YSOs.
 
@@
 \label{balmerjump}
+
+\noindent\rule{16cm}{0.4pt}
+
+{\bf
+\noindent key points here:
+
 \begin{itemize}
-\item that we are able to fill in the Balmer jump with the recombination continuum from the wind
-if the EM is high enough
-\item How this changes with inclination
-\item Comparison to literature
-\item Discussion of disk atmosphere treatment and its effect.
+	\item there is always recombination continuum emission from the wind, but it
+	only because significant w.r.t disk when the wind accelerates more slowly.
+	\item This higher density causes (too much) collisionally excited line emission from CIV
+	\item supports findings from the line profile shapes conclusions above...suggests
+	we need to alter the geometry in some respect, or find someway to suppress
+	collisionally excited line emission from UV lines?
+	\item perhaps one should increase the volume of the emitting area rather than the density,
+	although this will also cause more thermal line emission...
+	\item Bottom lines: filling in the Balmer jump can be done, and at the very minimum recombination
+	emission from the wind can matter, especially if we believe that the lines come from the wind. 
+	But to properly fill in the edge, one requires very high, possibly unrealistic, densities.
+	\item make clear that the edge originally comes from the stellar atmosphere, and that
+	the model we have used here is perhaps a little pessimistic.
+	\item We predict that the Balmer jump becomes deeper relative to the continuum 
+	\item This is probably due to foreshortening of the disk continuum but a fairly constant
+	escaping Balmer continuum.
 \end{itemize}
+}
+
+\noindent\rule{16cm}{0.4pt}
 
@@
 \mbox{
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_1640.eps}}
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_1640_0.eps}}
 \quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_4686.eps}}   
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_4686_0.eps}}   
 }
@@
 
-\subsection{Helium Lines}
-Discussion of Helium lines in the spectrum.
+\subsection{The Boundary Layer and Ionization State of the wind}
+
+\noindent\rule{16cm}{0.4pt}
+
+% important points from Hoare and Drew paper
+% Zanstra method requires optically thick in He II Lyman continuum
+% recombination lines are optically thin
+% they note that He II n=2 edge opacity would cause more stringent limits. relevant to our edges.
+% %
+
+{\bf 
+\noindent key points here:
+
 \begin{itemize}
-\item He II 4686, He II 1640 strengths
-\item Make the prediction that if 4686 is strong we might expect strong He II 3202. 
-\item Discuss why it wouldn't have been seen yet (spectral coverage)
-\item Helium I lines
+	\item we don't necessarily need a Boundary layer to ionize Helium II
+	\item a Boundary layer of 200,000K overionizes Carbon IV
+	\item we therefore favour lower boundary layer temperatures, as supported
+	by the upper limits of Hoare and Drew 1991.
+	\item we expect a boundary layer to matter more in lower accretion
+	rate systems.
 \end{itemize}
+}
+
+\noindent\rule{16cm}{0.4pt}
+
+We find in all our models that He II line emission is significant, and that 
+in most cases He  III is the dominant Helium ion in the wind, making recombination
+to He II an important process. This occurs without the presence of a boundary 
+layer. However, as a boundary layer is theoretically predicted 
+it is still important to investigate the effects of introducing
+one on the ionization state of the wind, and in particular
+the resultant line emission from \heiiuv, \heiiuv and \civ.
+
+We introduce boundary layers with temperatures of 80,000K and 200,000K,
+commonly proposed values in the literature. We find that
+
+It is also instructive here to conduct a hypothetical 
+Zanstra method calculation, following the method of \cite{hoare1991}. 
+We adopt their definitions of the Zanstra ratios in the Helium lines (equations 5 and 6 
+in their paper),
+
+\begin{equation}
+G (\lambda228, 1800 \AA) = 2.4\times 10^{-3} \frac{f(\lambda1640)}{f_*(1800\AA)}
+\end{equation}
+and
+
+\begin{equation}
+G (\lambda228, 1800 \AA) = 1.3\times 10^{-3} \frac{f(\lambda4686)}{f_*(1800\AA)}.\\
+\end{equation}
+
+Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$.
+
+% Discussion of Helium lines in the spectrum.
+% \begin{itemize}
+% \item He II 4686, He II 1640 strengths
+% \item Make the prediction that if 4686 is strong we might expect strong He II 3202. 
+% \item Discuss why it wouldn't have been seen yet (spectral coverage)
+% \item Helium I lines
+% \end{itemize}
 
@@
 \mbox{
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_balmer.eps}}
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_balmer_0.eps}}
 \quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_uv.eps}}   
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_uv_0.eps}}   
 }
@@
 
-\subsection{Boundary Layer}
-\begin{itemize}
-\item discuss the effect of 80000K and 200000K Boundary layers
-\item Particularly referring to He II and CIV
-\item Our findings support idea that 200000K BL would over ionize the wind- 
-we favour 80,000K
-\item I'd like to do a hypothetical Zanstra calculation here- state what
-temperature our model would predict from the Zanstra method
-\end{itemize}
+% \subsection{Boundary Layer}
+% \begin{itemize}
+% \item discuss the effect of 80000K and 200000K Boundary layers
+% \item Particularly referring to He II and CIV
+% \item Our findings support idea that 200000K BL would over ionize the wind- 
+% we favour 80,000K
+% \item I'd like to do a hypothetical Zanstra calculation here- state what
+% temperature our model would predict from the Zanstra method
+% \end{itemize}
 
@@
 thereby mimicking the behaviour of SW Sex stars.
-The single-peaked $H\alpha$ line is produced by our models with a 
+The single-peaked \ha line is produced by our models with a 
 very similar width to the observed spectrum, although it is perhaps slightly more
@@
 One of the limitations of the model is that, apart 
-from in $H\alpha$, the lines are in general double-peaked. 
+from in H$\alpha$, the lines are in general double-peaked. 
 The lack of high-resolution data in this regard makes detailed analysis difficult,
@@
 The inset plots show zoomed-in line profiles for 
-\heiiuv and \ha. The \ha line 
+\heiiuv \ and \ha. The \ha line 
 is single peaked, but higher order lines in the Balmer series
@@
 they can act as a spectral filter
-for the disk spectrum. At a maximum, they may be responsible
+for the disk spectrum, and the properties of the plasma
+is an important tracer for the disk and boundary layer SEDs. 
+At a maximum, they may be responsible
 for the majority of spectral features of high-state CVs,

### 2014-08-20 draft.tex
Some small changes to typos, abstracts and inclusion of more notes

@@
 on the optical spectrum, producing He II 4686 and H${\alpha}$ as well as
-enhanced emission in the Ly-$\alpha$ and He II $1640$ UV lines.
+enhanced emission in the Ly-$\alpha$ and He II $1640$ UV lines. We find that 
+a boundary layer is not essential to produce significant recombination to 
+He II, and if one is present we favour temperatures of $<10^5$K to avoid
+overionizing the UV resonance line species such as CIV. We also conduct Zanstra method
+calculations and estimate that one would infer a boundary layer temperature of around 80,000K
+from our benchmark model, which does not include one. This suggests that previous calculations
+done using this method are strongly dependent on both the assumed geometry and disk
+spectrum.
+We also note that
+the presence of a boundary layer becomes more noticeable in lower accretion rate systems.
 In addition, the improved treatment of recombination means that the bound-free continuum
@@
 Outflows are
-close to ubiquitous  in accreting systems across many order of magnitude in mass,
+close to ubiquitous  in accreting systems across many orders of magnitude in mass,
 from young stellar objects \citep{bunn1995} right up 
@@
 Further evidence of the influence of winds in the optical can be seen in P-Cygni like signatures,
-observed in lines such as H$_{\alpha}$ and He \textsc{i} $\lambda5876$ \citep{RN98}.
+observed in lines such as \ha and He \textsc{i} $\lambda5876$ \citep{RN98}.
 In addition, \cite{KLWB98} suggested
@@
 
-Here we present work using the same Monte Carlo radiative transfer code as LK02, but incorporating additional 
+Here we present work using the same Monte Carlo radiative transfer code as LK02, \py, but incorporating additional 
 `macro-atom' techniques suggested by Lucy (2002, 2003) to improve our treatment of the Hydrogen and Helium
@@
 In section 4 we present a benchmark model, which is discussed in section 5 with particular attention 
-devoted to a small-scale parameter search.
-Finally, in section 6, we summarise our findings, and outline areas for future work.
+devoted to a small-scale parameter search. In section 6 we present a `next generation'
+model which better reproduces the spectral features observed in NLs, and 
+finally, in section 7, we summarise our findings.
+
+% {\bf
+% \noindent Fairly happy with this as an introduction. Could maybe
+% discuss the boundary layer background here instead of in section 2.
+% }
 
@@
 % encouraging.
+
+% \noindent\rule{16cm}{0.4pt}
+
+% {\bf
+% \noindent Notes on Section 2:
+
+% \begin{itemize}
+% 	\item Should this section go after section 3, so that we've got the reader hooked with the model description first?
+% 	\item 
+% 	\item Would appreciate feedback on whether explanation of macro-atoms 
+% 	is sufficient.
+
+% \noindent Potential Additional Figures:
+
+% \begin{itemize}
+% 	\item Include figure on Case A/ Case B and TARDIS comparison	
+% }
+%
+% \noindent\rule{16cm}{0.4pt}
 
@@
 This is partly because they provide the most pessimistic prediction in terms of whether recombination emission in the 
-wind can fill in the Balmer jump, due to the strong absorption beyond the Balmer edge.
+wind can fill in the Balmer jump, due to their intrinsic strong absorption beyond the Balmer edge.
 For low temperatures, we use stellar atmospheres computed 
-by Kurucz (reference), and for $T>50,000$~K we use models computed with 
+by Kurucz \citep{kurucz1991}, and for $T>50,000$~K we use models computed with 
 \textsc{TLUSTY} \citep{tlusty}. The input spectra are created from these model
@@
 %with $\dot{M}_{acc} = 10^{-8}~M_{\odot}yr^{-1}$ can be seen in figure~\ref{t_profile}.
+% more detail on why we use this hodge podge of atmosphere models?
 
@@
 
-%Whether we include one, why why not, referring to He II and ionization.
+% \noindent\rule{16cm}{0.4pt}
+%
+% {\bf
+% \noindent Notes on Section 3:
+
+% \begin{itemize}
+% 	\item
+
+% \noindent Potential Additional Figures:
+
+% \begin{itemize}
+% 	\item 	
+% }
+%
+% \noindent\rule{16cm}{0.4pt}
 
@@
 
-\subsection{Ionization and Temperature Structure}
+%\subsection{Ionization and Temperature Structure}
 
@@
 \end{figure} %fullpage
+
+% \noindent\rule{16cm}{0.4pt}
+
+% {\bf
+% \noindent Notes on Section 4:
+
+% \begin{itemize}
+% 	\item
+
+% \noindent Potential Additional Figures:
+
+% \begin{itemize}
+% 	\item 	
+% }
+
+% \noindent\rule{16cm}{0.4pt}
 
@@
 The amount of line and recombination continuum
-emission produced by given ion, $i$, in a plasma of volume $V$
+emission produced by a given ion, $i$, in a plasma of volume $V$
 depends on the emission measure, $EM$, defined as
@@
 \end{equation}
+
+%% Should I quote Optical depths or 'Q' here to motivate the parameter search?
 
@@
 	this is necessary if H alpha is to be single peaked, as you need significant optical depths.
+	\item \la needs to be discussed somewhere- potentially here. Personally I would like to point out
+	that recombination being important here suggests that it might also be in QSOs
 \end{itemize}
@@
 \noindent\rule{16cm}{0.4pt}
+
+Figure~\ref{halpha} shows how the H$\alpha$ and H$\beta$ lines change with the kinematics 
+of the wind at an inclination of $80^\circ$. For H$\alpha$, in models with lower densities, the
+line is double peaked, but we see a transition to a single peaked line when 
+a high enough density is reach such that the line becomes optically thick.
+This reproduces the behaviour predicted by \cite{MC96}, who suggested that
+the poloidal velocity gradient in the wind can be larger than the gradient of 
+the Keplerian velocity. This gradient can therefore modify the line profile shape.
+It is clear from the behaviour of H$\beta$
+
+In order to produce single-peaked line emission at high inclinations,
+it is clear that a higher line opacity is needed at the red and blue wings relative to
+the opacity at line centre. This can be achieved in a number of ways. A more equatorial 
+wind would cause the line opacity at line centre to decrease
+relative to the the wings of the line due to the increased radial component 
+of the velocity gradient.
+
+Our difficulty in producing single-peaked line emission from a full 
+radiative transfer calculation has been encountered before. SDL05 found that a 
+biconical disk geometry similar to that adopted here could not reproduce 
+the observed single peaked profiles in YSOs.
 
@@
 
-Figure~\ref{halpha} shows how the H$\alpha$ and H$\beta$ lines change with the kinematics 
-of the wind at an inclination of $80^\circ$. For H$\alpha$, in models with lower densities, the
-line is double peaked, but we see a transition to a single peaked line when 
-a high enough density is reach such that the line becomes optically thick.
-This reproduces the behaviour predicted by \cite{MC96}, who suggested that
-the poloidal velocity gradient in the wind can be larger than the gradient of 
-the Keplerian velocity. This gradient can therefore modify the line profile shape.
-It is clear from the behaviour of H$\beta$
-
-In order to produce single-peaked line emission at high inclinations,
-it is clear that a higher line opacity is needed at the red and blue wings relative to
-the opacity at line centre. This can be achieved in a number of ways. A more equatorial 
-wind would cause the line opacity at line centre to decrease
-relative to the the wings of the line due to the increased radial component 
-of the velocity gradient.
-
-Our difficulty in producing single-peaked line emission from a full 
-radiative transfer calculation has been encountered before. SDL05 found that a 
-biconical disk geometry similar to that adopted here could not reproduce 
-the observed single peaked profiles in YSOs.
-
 \subsection{The Balmer Jump}
@@
 We introduce boundary layers with temperatures of 80,000K and 200,000K,
-commonly proposed values in the literature. We find that
+commonly proposed values in the literature. We find that a boundary layer
 
@@
 Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$.
+
+% Possible figure: CIV line equivalent width or ionization fraction
+% as a function of boundary layer temperature?
 
@@
 
-\subsection{UV Resonance Lines}
-Compare spectra to LK02 and other models. Are the spectral features preserved, has anything significant changed.
-Lyman alpha?
+% \noindent\rule{16cm}{0.4pt}
+
+% {\bf
+% \noindent Notes on Section 5:
+
+% \begin{itemize}
+% 	\item
+
+% \noindent Potential Additional Figures:
+
+% \begin{itemize}
+% 	\item 	
+% }
+
+% \noindent\rule{16cm}{0.4pt}
+
+% \subsection{UV Resonance Lines}
+% Compare spectra to LK02 and other models. Are the spectral features preserved, has anything significant changed.
+% Lyman alpha?
 
@@
 
+% \noindent\rule{16cm}{0.4pt}
+
+% {\bf
+% \noindent Notes on Section 6:
+
+% \begin{itemize}
+% 	\item
+
+% \noindent Potential Additional Figures:
+
+% \begin{itemize}
+% 	\item 	
+% }
+
+% \noindent\rule{16cm}{0.4pt}
+
 \newpage
@@
 prominent in cases where He~\textsc{ii}~$\lambda1640{\rm \AA}$ \& 
-\heiiopt are seen. 
+\heiiopt\ are seen. 
 	\item A Balmer jump in emission during eclipse.
@@
 
+% {\bf
+% \noindent Notes on Section 7:
+
+% \begin{itemize}
+% 	\item
+
+% \noindent Potential Additional Figures:
+
+% \begin{itemize}
+% 	\item 	
+% }
+
 % \subsection{Future Work}

### 2014-08-20 scripts/mnras.py

@@ -19,6 +19,9 @@ for line in texfile:
 		outfile.write("\maketitle\n")
 		outfile.write(line)
 
+	elif "indent" in line and "rule" in line:
+		outfile.write("\\noindent\\rule{8cm}{0.4pt}\n")
+
 	elif "fullpage" in line and "begin{figure}" in line:
 		if fig_env == False:
 			outfile.write("\\begin{figure*}\n")

### 2014-08-20 draft.tex
First draft to send round

@@
 \def\aapr{AAPR}
+\def\actaa{ACTAA} 
 \def\ssr{SSR}
@@
 calculations and estimate that one would infer a boundary layer temperature of around 80,000K
-from our benchmark model, which does not include one. This suggests that previous calculations
+from our benchmark calculation, despite it not being present in the model itself. This suggests that previous calculations
 done using this method are strongly dependent on both the assumed geometry and disk
@@
 implying they were formed near the base of the wind where rotational velocity
-can still dominate over the slowly increasing poloidal velocity. A Balmer 
-jump is present at all inclinations. This is present
+can still dominate over the slowly increasing poloidal velocity. 
+We also see a general trend from absorption to emission in spectral lines
+with increasing inclination, as one would expect from our wind geometry.
+This is expected in CVs and can be seen clearly in figure 1. Note however
+that in our models the \heiiuv line does not exhibit this behaviour, which
+is somewhat surprising.
+
+A Balmer jump is present at all inclinations. This is present
 in the stellar atmosphere models used to model the disk,
 and is not a result of photoabsorption through the wind.
-%%%% SAY BALMER JUMP CASUED BY SAs
-
 In fact, the wind has a Balmer jump in emission, but it is not prominent enough
@@
 \begin{figure} 
-\includegraphics[width=0.5\textwidth]{figures/fig4.eps}
-\caption{Total packet-binned spectra across all viewing angles. The top panel shows the total 
-integrated escaping spectrum, while the other panels show the contributions from photons that originate
+\includegraphics[width=0.5\textwidth]{figures/fig7_escaping.eps}
+\caption{Total packet-binned spectra across all viewing angles. 
+The thick black line shows the total 
+integrated escaping spectrum, while green and red lines show the contributions from photons that originate
 in the disk and wind respectively. Recombination continuum emission blueward of the Balmer 
@@
 
-\noindent\rule{16cm}{0.4pt}
-
-{\bf
-\noindent key points here:
-
-\begin{itemize}
-	\item producing single peaked line profiles is difficult to say the least
-	\item with our high density models we can produce some single peaked line emission,
-	mostly in Halpha and beta. the other lines seem to stay double peaked.
-	\item this higher density causes (too much) collisionally excited line emission from CIV
-	\item if the wind was more equatorial then this might help, but this isn't really supported by observations.
-	\item we can definitely reproduce the behaviour predicted by Murray and Chiang
-	\item Comment on the observed Balmer decrement being fairly flat, as is observed. Point out that
-	this is necessary if H alpha is to be single peaked, as you need significant optical depths.
-	\item \la needs to be discussed somewhere- potentially here. Personally I would like to point out
-	that recombination being important here suggests that it might also be in QSOs
-\end{itemize}
-}
-
-\noindent\rule{16cm}{0.4pt}
+% \noindent\rule{16cm}{0.4pt}
+
+% {\bf
+% \noindent key points here:
+
+% \begin{itemize}
+% 	\item producing single peaked line profiles is difficult to say the least
+% 	\item with our high density models we can produce some single peaked line emission,
+% 	mostly in Halpha and beta. the other lines seem to stay double peaked.
+% 	\item this higher density causes (too much) collisionally excited line emission from CIV
+% 	\item if the wind was more equatorial then this might help, but this isn't really supported by observations.
+% 	\item we can definitely reproduce the behaviour predicted by Murray and Chiang
+% 	\item Comment on the observed Balmer decrement being fairly flat, as is observed. Point out that
+% 	this is necessary if H alpha is to be single peaked, as you need significant optical depths.
+% 	\item \la needs to be discussed somewhere- potentially here. Personally I would like to point out
+% 	that recombination being important here suggests that it might also be in QSOs
+% \end{itemize}
+% }
+
+% \noindent\rule{16cm}{0.4pt}
 
@@
 the poloidal velocity gradient in the wind can be larger than the gradient of 
-the Keplerian velocity. This gradient can therefore modify the line profile shape.
-It is clear from the behaviour of H$\beta$
+the Keplerian velocity. This velocity gradient can therefore modify the line profile shape
+by suppressing emission at the red and blue wings of the line, 
+providing that the line optical depth is high enough.
 
@@
 the opacity at line centre. This can be achieved in a number of ways. A more equatorial 
-wind would cause the line opacity at line centre to decrease
-relative to the the wings of the line due to the increased radial component 
-of the velocity gradient.
-
+wind would increase the radial velocity shear, but is not supported by observations (references 
+on collimated nature of CV winds).
 Our difficulty in producing single-peaked line emission from a full 
-radiative transfer calculation has been encountered before. SDL05 found that a 
-biconical disk geometry similar to that adopted here could not reproduce 
-the observed single peaked profiles in YSOs.
+radiative transfer calculation has been encountered before in a number of situations. 
+SDL05 found that a biconical disk geometry similar to that adopted here could not reproduce 
+the observed single peaked profiles in YSOs. We have shown
+that the mechanism proposed by \cite{MC96} does indeed produce 
+single-peaked line emission in our models, but for this to occur in the majority of
+spectral lines then very high densities are required.
 
@@
 \caption{
+Line profiles for \ha\ (right) and \hb\ (left) with varying kinematic 
+properties. The benchmark model is shown in the top panel, and also in grey in each 
+subsequent plot for comparison. The parameter that has been altered from the benchmark model 
+is marked on each panel. For the left and middle right columns, models lower down
+are more slowly accelerating and have denser wind bases. The middle right column
+shows the variation with wider launch radii, and the right hand column shows 
+how a boundary layer of increasing temperature affects the spectrum.
 % How the H$\alpha$ and H$\beta$ lines in our model change with the kinematic properties
@@
 % essentially becomes neutral as the optically thick regions self-shield the wind from photoionizing radiation.
-\bf{Each of these figures will highlight the next gen model in bold.
-and contain a grid like the above showing a pair of spectral features in
-the left and right panels. The grey shaded line will show the benchmark model
-for easy comparison.  
-The most promising parameters at the moment are acceleration exponent and launch radii.}
+% \bf{Each of these figures will highlight the next gen model in bold.
+% and contain a grid like the above showing a pair of spectral features in
+% the left and right panels. The grey shaded line will show the benchmark model
+% for easy comparison.  
+% The most promising parameters at the moment are acceleration exponent and launch radii.}
+% }
 }
@@
 
-\noindent\rule{16cm}{0.4pt}
-
-{\bf
-\noindent key points here:
-
-\begin{itemize}
-	\item there is always recombination continuum emission from the wind, but it
-	only because significant w.r.t disk when the wind accelerates more slowly.
-	\item This higher density causes (too much) collisionally excited line emission from CIV
-	\item supports findings from the line profile shapes conclusions above...suggests
-	we need to alter the geometry in some respect, or find someway to suppress
-	collisionally excited line emission from UV lines?
-	\item perhaps one should increase the volume of the emitting area rather than the density,
-	although this will also cause more thermal line emission...
-	\item Bottom lines: filling in the Balmer jump can be done, and at the very minimum recombination
-	emission from the wind can matter, especially if we believe that the lines come from the wind. 
-	But to properly fill in the edge, one requires very high, possibly unrealistic, densities.
-	\item make clear that the edge originally comes from the stellar atmosphere, and that
-	the model we have used here is perhaps a little pessimistic.
-	\item We predict that the Balmer jump becomes deeper relative to the continuum 
-	\item This is probably due to foreshortening of the disk continuum but a fairly constant
-	escaping Balmer continuum.
-\end{itemize}
-}
-
-\noindent\rule{16cm}{0.4pt}
+The left panel of figure~\ref{jump} shows the evolution
+of the Balmer jump with a number of key parameters. Higher density models
+produce sufficient recombination continuum emission to fill 
+in the Balmer jump. This offers a potential solution to a 
+longstanding problem when reconciling theoretical
+models of NL spectra with observations, as originally suggested by
+\cite{KLWB98}. The fact that this emission is very sensitive to the parameters
+that govern the density at the wind base also supports
+the idea that a transition region close to the disk plane is necessary
+to explain the emission features present \citep{kd1997}.
+
+% \noindent\rule{16cm}{0.4pt}
+
+% {\bf
+% \noindent key points here:
+
+% \begin{itemize}
+% 	\item there is always recombination continuum emission from the wind, but it
+% 	only because significant w.r.t disk when the wind accelerates more slowly.
+% 	\item This higher density causes (too much) collisionally excited line emission from CIV
+% 	\item supports findings from the line profile shapes conclusions above...suggests
+% 	we need to alter the geometry in some respect, or find someway to suppress
+% 	collisionally excited line emission from UV lines?
+% 	\item perhaps one should increase the volume of the emitting area rather than the density,
+% 	although this will also cause more thermal line emission...
+% 	\item Bottom lines: filling in the Balmer jump can be done, and at the very minimum recombination
+% 	emission from the wind can matter, especially if we believe that the lines come from the wind. 
+% 	But to properly fill in the edge, one requires very high, possibly unrealistic, densities.
+% 	\item make clear that the edge originally comes from the stellar atmosphere, and that
+% 	the model we have used here is perhaps a little pessimistic.
+% 	\item We predict that the Balmer jump becomes deeper relative to the continuum 
+% 	\item This is probably due to foreshortening of the disk continuum but a fairly constant
+% 	escaping Balmer continuum.
+% \end{itemize}
+% }
+
+% \noindent\rule{16cm}{0.4pt}
 
@@
 \caption{
-The evolution of the He II lines with the kinematic properties
-of the wind. 
+Line profiles for \heiiuv\ (right) and \heiiopt\  (left) with varying kinematic 
+properties, computed for an incliantion of $80^\circ$. 
+The panels are organised in the same way as figure~\ref{halpha}.
 % The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
@@
 }
-\label{jump}
+\label{heiifig}
 \end{figure}
@@
 
-\noindent\rule{16cm}{0.4pt}
+% fwoud
 
@@
 
-{\bf 
-\noindent key points here:
-
-\begin{itemize}
-	\item we don't necessarily need a Boundary layer to ionize Helium II
-	\item a Boundary layer of 200,000K overionizes Carbon IV
-	\item we therefore favour lower boundary layer temperatures, as supported
-	by the upper limits of Hoare and Drew 1991.
-	\item we expect a boundary layer to matter more in lower accretion
-	rate systems.
-\end{itemize}
-}
-
-\noindent\rule{16cm}{0.4pt}
+% {\bf 
+% \noindent key points here:
+
+% \begin{itemize}
+% 	\item we don't necessarily need a Boundary layer to ionize Helium II
+% 	\item a Boundary layer of 200,000K overionizes Carbon IV
+% 	\item we therefore favour lower boundary layer temperatures, as supported
+% 	by the upper limits of Hoare and Drew 1991.
+% 	\item we expect a boundary layer to matter more in lower accretion
+% 	rate systems.
+% \end{itemize}
+% }
+
+% \noindent\rule{16cm}{0.4pt}
 
@@
 
-We introduce boundary layers with temperatures of 80,000K and 200,000K,
-commonly proposed values in the literature. We find that a boundary layer
+We introduce blackbody boundary layers with temperatures of 80,000K and 200,000K,
+commonly proposed values in the literature, and adopt a scale height according to
+equation~\ref{bl}. We find that the strength of the C\textsc{iv} line decreases
+with increasing boundary layer temperature, as shown in figure~\ref{jump}.
+We note that a model boundary layer could produce a softer
+spectrum for a given effective temperature \citep[e.g.][]{suleimanov2014}, 
+meaning that our ionization constraints would
+allow for a higher value of $T_{bl}$. It is also
+possible that a flatter temperature profile in the disk,
+as suggested by some eclipse mapping observations of NLs (References),
+would cause a softer disk spectrum and allow a boundary layer 
+with $T_{bl} = 200,000$K to exist without over-ionizing the wind.
 
@@
 
-Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$.
+Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$. (I NEED TO DO THE CALCULATION!).
 
@@
 %%\includegraphics[width=0.5\textwidth]{figures/test.eps}
-\caption{The evolution of the Balmer jump and C~\textsc{iv} line with the kinematic properties
-of the wind. 
+\caption{The evolution of the Balmer jump and higher order Balmer lines (left) 
+and the \civ\ line profile (right)
+with the kinematic properties of the wind,
+computed for an incliantion of $80^\circ$. 
+the panels are organised in the same way as figure~\ref{halpha}.
 % The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
@@
 %\end{itemize}
-
-\newpage
 
@@
 $v_{\infty}$ 	&	 $3v_{esc}$ \\ 
-$R_v$ 	        &	 $1\times10^{11}$cm \\ 
+$R_v$ 	        &	 $142.9 R_{WD}$ \\ 
 $\alpha$ 	&	 $4$ \\
@@
 at an angle of $80^\circ$ and the high-inclination nova-like RW Tri 
-is also shown in figure~\ref{rwtricomp}.
+is also shown in figure~\ref{rwtricomp}. The inclination
+for RW Tri has been disputed, with claimed values of $75^\circ$ \citep{groot2004},
+$70.5^\circ$ \citep{smak1995}, $80^\circ$ \citep{longmore1981} and 
+$82^\circ$\citep{frankking1981}. A lower inclination
+would mean that our model would simply require lower densities 
+and smaller emission regions to produce the required continuum level
+and single peaked emission, so our conclusions from this comparison are
+not particular sensitive to the value chosen.
+We also emphasize that this is no sense a fit to the data. The model
+is designed to reproduce the general behaviour of Nova-likes
+and give an indication of the likely densities and kinematics 
+required in the wind, but we do not seek to provide robust parameter
+or precise parameters.
+%quotes a figure of , whereas  halevinhenden2008
 
@@
 thereby mimicking the behaviour of SW Sex stars.
-The single-peaked \ha line is produced by our models with a 
+The single-peaked \ha\ line is produced by our models with a 
 very similar width to the observed spectrum, although it is perhaps slightly more
@@
 in the ultraviolet. To get the required emission in the optical lines
-and recombination continuum the densities required are very high.
+and recombination continuum the densities required are very high 
+($n_e\sim10^{13}-10^{14}$ in the main emission region).
 This causes a significant collisionally excited contribution
@@
 
-\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-08-20 scripts/mnras.py

@@ -20,7 +20,8 @@ for line in texfile:
 		outfile.write(line)
 
 	elif "indent" in line and "rule" in line:
-		outfile.write("\\noindent\\rule{8cm}{0.4pt}\n")
+		if "%" not in line:
+			outfile.write("\\noindent\\rule{8cm}{0.4pt}\n")
 
 	elif "fullpage" in line and "begin{figure}" in line:
 		if fig_env == False:

### 2014-08-22 draft.tex
Added figure captions and a bit more text

@@
 \def\hb{H$\beta$}
+\def\civfull{C~\textsc{iv}~$\lambda1550{\rm \AA}$}
 
@@
 the macro atom scheme in \py to verify that it does indeed solve for level populations correctly
-and produces the correct level emissivities. We have been able to show good agreement with 
-Case A and Case B calculations by \cite{seaton1959}, and have tested our level
-population solver against \textsc{Tardis.}
+and produces the expected level emissivities. Figure~\ref{tests} shows good agreement with 
+Case B, l-mixed calculations by \cite{seaton1959}, and level
+population calcaultions with \textsc{Tardis.}
 
@@
 % encouraging.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/fig_caseb_tardis.eps}
+\caption{
+{\sl Top Panel:} Balmer decrements from \py compared with analytic calculations
+by Seaton (1959), showing good agreement when calculating level emissivities in Hydrogen
+in the Case B limit.
+(see Osterbrock 1989 for a discussion of this commonly used approximation).
+{\sl Bottom Panel:}  a comparison of Helium I level populations (the most complex ion we currently 
+treat as a macro-atom) between \py~and \tar~models. Considering the 
+two codes use different atomic data and \textsc{Tardis,} unlike \textsc{Python,} currently has 
+a complete treatment of collisions between radiatively forbidden transitions, the factor of 
+$<2$ agreement is encouraging. 
+}
+\label{tests}
+\end{figure}
+\nocite{osterbrock}
+\nocite{seaton1959}
 
@@
 The velocity law in our model for various values of
-the acceleration exponent.
+the acceleration exponent, $\alpha$.
 }
@@
 \caption{
-UV (left) and Optical synthetic spectra for model B computed at
-sightlines of 10,27.5, 45, 62.5 and 80 degrees.	
+UV (left) and Optical synthetic spectra for model A, our benchmark model,
+computed at sightlines of 10, 27.5, 45, 62.5 and 80 degrees.	
 The inset plots show zoomed-in line profiles for 
 \heiiuv and \ha. Double-peaked line emission can be seen in 
-\heiiuv, \heiiopt, \ha and some He I lines, but the 
+\heiiuv, \heiiopt, \ha\ and some He I lines, but the 
 line emission is not always sufficient to overcome the absorption
-cores from the stellar atmosphere models.
+cores from the stellar atmosphere models. The model
+also produces a prominent \heiioptnew\ line at high inclinations,
 }
@@
 \caption{Synthetic optical spectra computed for 
-sightlines of 22.5, 25, 62.5 and 80 degrees.}
+sightlines of 22.5, 25, 62.5 and 80 degrees. In these plots
+the flux is divided by a polynomial fit to the 
+underlying continuum redward of the Balmer edge, so that 
+line-to-continuum ratios and the true depth of the
+Balmer jump can be shown.}
 \label{spec_continuum}
@@
 \includegraphics[width=\textwidth]{figures/fig5.eps}
-\caption{Various properties of the wind.}
+\caption{
+The Physical Properties of the wind. Near
+the disk plane the wind is dense, with low poloidal velocities.
+As the wind accelerates it becomes less dense
+and more highly ionized. The dominant Helium ion
+is almost always He III, apart from in a small
+portion of the wind at the base, which is partially shielded
+from the inner disk.
+}
 \label{wind}
@@
 
-We find in all our models that He II line emission is significant, and that 
-in most cases He  III is the dominant Helium ion in the wind, making recombination
-to He II an important process. This occurs without the presence of a boundary 
-layer. However, as a boundary layer is theoretically predicted 
-it is still important to investigate the effects of introducing
-one on the ionization state of the wind, and in particular
-the resultant line emission from \heiiuv, \heiiuv and \civ.
-
-We introduce blackbody boundary layers with temperatures of 80,000K and 200,000K,
-commonly proposed values in the literature, and adopt a scale height according to
-equation~\ref{bl}. We find that the strength of the C\textsc{iv} line decreases
-with increasing boundary layer temperature, as shown in figure~\ref{jump}.
-We note that a model boundary layer could produce a softer
-spectrum for a given effective temperature \citep[e.g.][]{suleimanov2014}, 
-meaning that our ionization constraints would
-allow for a higher value of $T_{bl}$. It is also
-possible that a flatter temperature profile in the disk,
-as suggested by some eclipse mapping observations of NLs (References),
-would cause a softer disk spectrum and allow a boundary layer 
-with $T_{bl} = 200,000$K to exist without over-ionizing the wind.
-
-It is also instructive here to conduct a hypothetical 
-Zanstra method calculation, following the method of \cite{hoare1991}. 
-We adopt their definitions of the Zanstra ratios in the Helium lines (equations 5 and 6 
-in their paper),
-
-\begin{equation}
-G (\lambda228, 1800 \AA) = 2.4\times 10^{-3} \frac{f(\lambda1640)}{f_*(1800\AA)}
-\end{equation}
-and
-
-\begin{equation}
-G (\lambda228, 1800 \AA) = 1.3\times 10^{-3} \frac{f(\lambda4686)}{f_*(1800\AA)}.\\
-\end{equation}
-
-Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$. (I NEED TO DO THE CALCULATION!).
-
-% Possible figure: CIV line equivalent width or ionization fraction
-% as a function of boundary layer temperature?
-
-% Discussion of Helium lines in the spectrum.
-% \begin{itemize}
-% \item He II 4686, He II 1640 strengths
-% \item Make the prediction that if 4686 is strong we might expect strong He II 3202. 
-% \item Discuss why it wouldn't have been seen yet (spectral coverage)
-% \item Helium I lines
-% \end{itemize}
-
 \begin{figure} %fullpage
@@
 \label{jump}
+\end{figure}
+
+We find in all our models that He II line emission is significant, and that 
+in most cases He  III is the dominant Helium ion in the wind, making recombination
+to He II an important process. This occurs without the presence of a boundary 
+layer. However, as a boundary layer is theoretically predicted 
+it is still important to investigate the effects of introducing
+one on the ionization state of the wind, and in particular
+the resultant line emission from \heiiuv, \heiiuv and \civ.
+
+We introduce blackbody boundary layers with temperatures of 80,000K and 200,000K,
+commonly proposed values in the literature, and adopt a scale height according to
+equation~\ref{bl}. We find that the strength of the C\textsc{iv} line decreases
+with increasing boundary layer temperature, as shown in figure~\ref{jump}.
+We note that a model boundary layer could produce a softer
+spectrum for a given effective temperature \citep[e.g.][]{suleimanov2014}, 
+meaning that our ionization constraints would
+allow for a higher value of $T_{bl}$. It is also
+possible that a flatter temperature profile in the disk,
+as suggested by some eclipse mapping observations of NLs (References),
+would cause a softer disk spectrum and allow a boundary layer 
+with $T_{bl} = 200,000$K to exist without over-ionizing the wind.
+We note that there is an element of inconsistency with 
+requiring flatter disk temperature profiles in order to permit
+a hotter boundary layer,, as the theoretical argument 
+for the existence and likely temperature of a boundary layer has 
+mostly been put together assuming a Shakura-Sunyaev disk.  
+Radio emission has been seen in CVs, possibly implying the 
+existence of a radio jet \cite[see e.g.][]{kordingDNjet2008,kording2011}.
+A jet could extract some of the energy which is supposedly dissipated in the 
+boundary layer, causing $L_{bl} < L_{acc}/2$, although
+observations suggest the jet power would only be on the order
+of $10\%$ of the accretion power.
+
+It is also instructive here to conduct a hypothetical 
+Zanstra method calculation, following the method of \cite{hoare1991}. 
+We adopt their definitions of the Zanstra ratios in the Helium lines (equations 5 and 6 
+in their paper),
+
+\begin{equation}
+G (\lambda228, 1800 \AA) = 2.4\times 10^{-3} \frac{f(\lambda1640)}{f_*(1800\AA)}
+\end{equation}
+and
+
+\begin{equation}
+G (\lambda228, 1800 \AA) = 1.3\times 10^{-3} \frac{f(\lambda4686)}{f_*(1800\AA)}.\\
+\end{equation}
+
+Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$. (I NEED TO DO THE CALCULATION!).
+
+% Possible figure: CIV line equivalent width or ionization fraction
+% as a function of boundary layer temperature?
+
+% Discussion of Helium lines in the spectrum.
+% \begin{itemize}
+% \item He II 4686, He II 1640 strengths
+% \item Make the prediction that if 4686 is strong we might expect strong He II 3202. 
+% \item Discuss why it wouldn't have been seen yet (spectral coverage)
+% \item Helium I lines
+% \end{itemize}
+
+\begin{figure} 
+\mbox{
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/fig_EWt.eps}}
+
+}
+%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
+\caption{
+Equivalent widths of the \civfull\ and \heiiuv\ lines
+as a function of boundary layer temperature. The models used
+are identical to the benchmark model in geometry and kinematics.
+% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
+% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
+% when the wind becomes a neutral absorbing column.
+}
+\label{bl_grid}
 \end{figure}
@@
 UV (left) and Optical synthetic spectra for model B computed at
-sightlines of 10,27.5, 45, 62.5 and 80 degrees.	
+sightlines of 10, 27.5, 45, 62.5 and 80 degrees.	
 The inset plots show zoomed-in line profiles for 
@@
 are double-peaked, albeit with narrower profiles.
-Strong \heiiopt emission can be seen
+Strong \heiiopt emission can be seen, as well a trend
+of a deeper Balemr jump with decreasing inclination.
 }
@@
 	continuum emission from a disk wind
-	\item Single peaked line emission in H alpha produced by 
+	\item Single peaked line emission in \ha\ produced by 
 	the introduction of a poloidal velocity gradient \citep{MC96}

### 2014-09-02 draft.tex
implemented some of CK changes

@@
 \begin{abstract}
-High-State non-magnetic Cataclysmic Variables (CVs) 
-exhibit strong Hydrogen \& Helium recombination lines in their optical 
+High-state non-magnetic cataclysmic variables (CVs) 
+exhibit strong hydrogen \& helium recombination lines in their optical 
 spectra. These lines can be single peaked, and may be formed 
 in the same bipolar outflow that is responsible for the
-blue-shifted absorption lines seen in the Ultraviolet (UV).
-Here we present results obtained by incorporating a `macro-atom' treatment into
+blue-shifted absorption lines seen in the ultraviolet (UV).
+Here, we present results obtained by incorporating a `macro-atom' treatment into
 our Monte Carlo radiative transfer code, which was
-originally used to synthesize the UV spectrum of a disk-dominated CV 
-with a simple biconical wind. Using an identical model, we show that the wind leaves a noticeable imprint 
-on the optical spectrum, producing He II 4686 and H${\alpha}$ as well as
-enhanced emission in the Ly-$\alpha$ and He II $1640$ UV lines. We find that 
-a boundary layer is not essential to produce significant recombination to 
-He II, and if one is present we favour temperatures of $<10^5$K to avoid
-overionizing the UV resonance line species such as CIV. We also conduct Zanstra method
-calculations and estimate that one would infer a boundary layer temperature of around 80,000K
-from our benchmark calculation, despite it not being present in the model itself. This suggests that previous calculations
-done using this method are strongly dependent on both the assumed geometry and disk
-spectrum.
-We also note that
-the presence of a boundary layer becomes more noticeable in lower accretion rate systems.
-In addition, the improved treatment of recombination means that the bound-free continuum
-emission is enhanced, albeit by a modest amount.
+originally used to synthesize the UV spectra of disk-dominated CVs 
+with a simple biconical wind. 
+Using an identical model, we show that the same wind leaves a noticeable imprint 
+on the optical spectrum, producing \ha\ and \heiiopt\ as well as
+enhanced emission in the Ly-$\alpha$ and \heiiuv\ UV lines. 
+In addition, our improved treatment of recombination means that the bound-free continuum
+emission is significant, but does not yet overcome the intrinsic absorption edge
+present in the stellar atmosphere models used to treat the accretion disk.
+We find that a boundary layer is not essential for the production
+of He II recombination lines, but also explore the effect of boundary layers
+with temperatures of $80-200$kK on the ionization state of the wind
+and resulting spectrum.
 A short exploration of a 3-variable kinematic parameter space leads to models with higher densities 
@@
 Finally, we present a synthetic spectrum of a next generation model in and out of eclipse,
-and identify the strengths and shortcomings of the model in the context of the high inclination
-Nova-like variable RW Tri.
+which shows a striking similarity with the optical spectrum of the high inclination
+Nova-like variable RW Tri. The densities near the disk plane in this model
+are such that \civ\ has a large collisionally excited component, in 
+contrast to observations.
+% We find that 
+% a boundary layer is not essential to produce significant recombination to 
+% He II, and if one is present we favour temperatures of $<10^5$K to avoid
+% overionizing the UV resonance line species such as CIV. We also conduct Zanstra method
+% calculations and estimate that one would infer a boundary layer temperature of around 80,000K
+% from our benchmark calculation, despite it not being present in the model itself. This suggests that previous calculations
+%done using this method are strongly dependent on both the assumed geometry and disk
+%spectrum.
+%We also note that
+%the presence of a boundary layer becomes more noticeable in lower accretion rate systems.
 \end{abstract}
@@
 
-Outflows are
-close to ubiquitous  in accreting systems across many orders of magnitude in mass,
+Outflows are ubiquitous  in accreting systems across many orders of magnitude in mass,
 from young stellar objects \citep{bunn1995} right up 
 to quasi-stellar objects \citep[QSOs;][]{ganguly2008}. Outflows can take the form of jets, such as those
-seen in X-ray binaries \citep{fender2006} or active galactic nuclei \citep[AGN;][]{marscher2006}, but can also manifest as `winds' emanating from
-the accretion disk.
+seen in X-ray binaries \citep{fender2006} or active galactic nuclei \citep[AGN;][]{marscher2006}, 
+but can also manifest as `winds' emanating from the accretion disk (REFS).
 Understanding the impact of accretion disk winds on spectral features has far-reaching implications. 
@@
 and their ever-present nature implies a deep connection with the accretion process. This connection
-is important to understand in order to probe the universality of accretion \citep{mchardy2006, SKUK2012}, 
+is important to understand in order to probe the universality of accretion \citep{mchardy2006, SKUK2012} 
 and to determine the true extent to which
@@
 Despite this, in many types of systems the impact of winds on observational
-features is somewhat unknown, and many theoretical questions relating to their origin 
+features is essentially unknown, and many theoretical questions relating to their origin 
 and driving mechanism remain unanswered.
@@
 is mediated by an accretion disk which forms around the white dwarf. 
-Nova-like (NL) variables are a particular subclass of object in which the accretion disk
+nova-like (NL) variables are a particular subclass of objects in which the accretion disk
 is in a permanent state of relatively high accretion rate 
@@
 can cause single-peaked emission line profiles in the optical (Murray \& Chiang 1996), 
-such as those seen in Nova-like variables and SW Sex stars (Honeycutt, Schlegel,
+such as those seen in Nova-like variables and, especially, the SW Sex stars (Honeycutt, Schlegel,
 \& Kaitchuck 1986; Dhillon \& Rutten 1995). It is particularly telling that single-peaked 
-lines can be seen even in eclipse, suggesting 
+lines in high-inclination systems can be seen even in eclipse, suggesting 
 that a spatially extensive wind may be the source of emission (see figure~\ref{novalikes}).
 %%(Honeycutt, Schlegel, \& Kaitchuck 1986; Dhillon \& Rutten 1995). 
-Further evidence of the influence of winds in the optical can be seen in P-Cygni like signatures,
-observed in lines such as \ha and He \textsc{i} $\lambda5876$ \citep{RN98}.
+Further evidence of the influence of winds in the optical can occasionally 
+be seen in P-Cygni like signatures, observed in lines such as \ha\ 
+and He \textsc{i} $\lambda5876$ \citep{RN98}.
 In addition, \cite{KLWB98} suggested
@@
 could also explain the Fe~\textsc{ii} `curtain'
-seen in near-UV observations of the high inclination dwarf nova OY Car in queiscence 
+seen in near-UV observations of the high inclination dwarf nova OY Car in quiescence 
 \citep{horne1994}.
@@
 wind modeling to an accretion disk geometry (Mauche \& Raymond
-1987; Drew 1987; Vitello \& Shlosman 1988), and showed that mass loss rates of
+1987; Drew 1987; Vitello \& Shlosman 1988). These efforts showed that mass loss rates of
 $\sim10\%$ of the accretion rate
@@
 profiles in C\textsc{iv}~$\lambda1549$\AA.
-Long \& Knigge (2002) expanded on the above work by presenting our code, which
+Long \& Knigge (2002; LK02) presented a code that
 solved self-consistently for thermal and ionization balance in the wind
@@
 UV resonance lines profiles and presented a synthesized spectrum of Z Cam
-that agreed well with the observed features. Noebauer et al. (2010) expanded on this
-by carrying out more detailed comparisons to RW Tri and UX UMa. In addition to these 
-radiative transfer calculations, some work has also been done using Hydrodynamic wind models, 
+that agreed well with the observed features. Noebauer et al. (2010) used the same code 
+to carry out more detailed comparisons to RW Tri and UX UMa. In addition to these 
+radiative transfer calculations, some work has also been done using hydrodynamic wind models, 
 such as that by \cite{pkdh2002}, and more recently by \cite{kusterer2014} with application to
@@
 
-Here we present work using the same Monte Carlo radiative transfer code as LK02, \py, but incorporating additional 
-`macro-atom' techniques suggested by Lucy (2002, 2003) to improve our treatment of the Hydrogen and Helium
+Here, we present work using the same Monte Carlo radiative transfer code as LK02, 
+\py, but incorporating additional 
+`macro-atom' techniques suggested by Lucy (2002, 2003). 
+This improves our treatment of the Hydrogen and Helium
 optical lines, as well as recombination continuum emission. 
+Our goal is to investigate the effect of existing wind models
+on the optical spectra of CVs.
 In section 2 we present the code
@@
 We describe the kinematics and geometry of our biconical wind model in section 3.
-In section 4 we present a benchmark model, which is discussed in section 5 with particular attention 
-devoted to a small-scale parameter search. In section 6 we present a `next generation'
-model which better reproduces the spectral features observed in NLs, and 
+In section 4, we present a benchmark model, which is discussed in section 5 with particular attention 
+devoted to a small-scale parameter search. In section 6, we present a `next generation'
+model which better reproduces the spectral features observed in NLs, and, 
 finally, in section 7, we summarise our findings.
@@
 and temperature structure are calculated. This is done by
-flying MC energy quanta through a pre-defined wind geometry and recording
+flying MC energy quanta (`photons') through a pre-defined wind geometry and recording
 the relevant estimators, before choosing  a new electron temperature 
@@
 regimes, both in terms of the scale of the system, and the 
-shape and characteristic energies of the illuminating spectrum. It is 
-first described by LK02, who initially developed a biconical CV 
+shape and characteristic energies of the illuminating spectrum. 
+It was originally described by LK02, who developed a biconical CV 
 wind model to synthesize UV spectra. 
-Higginbottom et al.\nocite{higginbottom2013} (2013; hereafter H13) presented a 
-benchmark model for broad absorption line (BAL) QSOs.
+Higginbottom et al.\nocite{higginbottom2013} (2013; hereafter H13) used the same code to
+present a benchmark model for broad absorption line (BAL) QSOs.
 As part of this effort, the ionization scheme was improved so that 
-the code was capable of treating the power-law X-ray spectrum
-exhibited by AGN.
-This involved using a spectral model the mean intensity in a cell
-computed from MC estimators for, instead of using a dilute blackbody
-approximation. Compton processes
-were also incorporated into the heating and cooling balance.
+the code is now capable of treating arbritrary SEDs.
+%the power-law X-ray spectrum exhibited by AGN.
+% This involved using a spectral model the mean intensity in a cell
+% computed from MC estimators for, instead of using a dilute blackbody
+% approximation. Compton processes
+% were also incorporated into the heating and cooling balance.
 In addition, \cite[][SDL05]{simmacro2005} modeled
@@
 Wolf-Rayet star winds \citep{sim2004}, AGN disk winds \citep{simlong2008, tatum2012}
-and Supernovae \citep{kasen2006, kerzendorfsim}.
+and supernovae \citep{kasen2006, kerzendorfsim}.
 SDL05 used \py itself to apply this technique to
@@
 
-\subsubsection{Simple-ions}
-
-C, O, N, Ne, Na, Mg, Al, Si, S, Ar, Ca \& Fe are all included as simple-ions. 
-The two-level atom is a first order approximation here, which is appropriate 
+\subsubsection{Two-level atoms}
+
+C, O, N, Ne, Na, Mg, Al, Si, S, Ar, Ca \& Fe are all included as two-level atoms. 
+This is a first order approximation, which is appropriate 
 when treating resonance lines in which the lower level is at or close to the 
@@
 The reason for using this scheme 
-is twofold; First, unlike in H13, the SED can be approximated well by a dilute blackbody due to the 
+is twofold. First, unlike in H13, the SED can be approximated well by a dilute blackbody due to the 
 absence of a power-law X-ray source, and therefore the above modification to the Saha equation
-is appropriate; Second, this provides continuity from LK02 and allows us to do a like-for-like comparison,
-which is especially useful in assessing the improvement in Hydrogen line emission, and any changes
+is appropriate; Second, this provides continuity from LK02 and allows us to do a like-for-like comparison.
+This is especially useful in assessing the improvement in Hydrogen line emission, and any changes
 that might occur in the ionization stages of the resonance line species such as CIV. 
-Excitation is then calculated from LTE approximations. 
+Excitation is then calculated in LTE. 
 %This is because the 
@@
 Atomic data is obtained from the same sources described in LK02 and updated in H13. 
-The additional level and line information required to treat He as macro atom was 
+The additional level and line information required to treat He as a macro-atom was 
 obtained from \textsc{Topbase} \citep{topbase2005}. We treat H as a 20-level atom as in SDL05, where 
-each level is defined by the principal quantum number n, which is appropriate due to
+each level is defined by the principal quantum number, $n$, which is appropriate due to
 the degeneracy of each level in the H atom. He~\textsc{II} is treated in much the same way,
-with 10 levels, but He~\textsc{I} has larger energy differentials between different l subshells
+but with 10 levels. However, He~\textsc{I} has larger energy differentials between different l subshells
 and triplet and singlet states. Thus, we still include levels up to $n=10$ but explicitly 
 treat the $l$ and $s$ sub-orbitals as distinct levels instead of assuming they are perfectly `l-mixed',
-which also allows the model to produce singlet and 
-triplet lines, as seen in optical CV spectra.
+This also allows the model to produce singlet and 
+triplet lines, which are seen in optical CV spectra \citep[e.g.][]{dhillon1996}.
 
@@
 photoionization codes. Comparisons of ionization balance with \cld \citep{cloudy2013} 
-can be found in LK02 and H13 showing excellent agreement. We have also conducted comparisons
+can be found in LK02 and H13 and show excellent agreement. We have also conducted comparisons
 of ionization and spectral synthesis with the supernova code \textsc{Tardis.} \tar is described by
@@
 Here we describe some of the features of our biconical wind model. Our aim here is not
-to provide a `best fit' model to the data, but rather to use as a starting point
-the types of models which have already been successful in explaining UV spectra of CVs,
-and examine their effect on the optical features when the treatment of line transfer
+to provide a `best fit' model to match any particular dataset.
+Rather, we take as a starting point
+the types of models which have already been successful in explaining UV spectra of CVs.
+We can then examine the contribution of the wind to 
+the optical features when the treatment of line transfer
 is improved.
@@
 disk wind rises from the accretion disk between radii $r_{min}$ and $r_{max}$. The covering fraction of the wind is 
-controlled by the opening angles of the wind, $\theta_{min}$ and $\theta_{max}$, and the launch angle of
+also controlled by the opening angles of the wind, $\theta_{min}$ and $\theta_{max}$, and the launch angle of
 the other streamlines is given by
@@
 where $r_0$ is the launch radius of the streamline.
-As in LK02, we follow SV93's power law
-velocity profile. The poloidal velocity, $v_l$, in our model is given by
+%As in LK02, we follow SV93's power lawvelocity profile. 
+The poloidal velocity, $v_l$, in the SV93 model is given by
 
@@
 
-where $l$ is distance measured along a  streamline. $v_{\infty}$, the 
-terminal velocity, is set to a fixed multiple of the escape velocity at the bottom
+where $l$ is distance measured along a  streamline. The terminal velocity, 
+$v_{\infty}$, is set to a fixed multiple of the escape velocity at the bottom
 of a streamline, and $v_0$ is a constant launch velocity (set to $6$~km~s$^{-1}$).
@@
 $\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
-$\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
+$\dot{M}_{wind}$  &	fi\\ 
 $r_{min}$ 	&	 $4 R_{WD}$\\ 
@@
 
-The principle of mass conservation means that the velocity law also 
+%The principle of mass conservation 
+The mass continuity equation means that the velocity law also 
 controls the density, $\rho$, of the wind, which can be expressed in terms
@@
 
-where $\phi$ here is the mass loss rate per unit area at $r_0$
-and $v_z$ is the vertical velocity component. In this model, we
+where $\phi$ is the mass-loss rate per unit area at $r_0$
+and $v_z$ is the vertical velocity component. In our model, we
 adopt a uniform value for $\phi$.
@@
 
-MC quanta originate from an accretion disk and a central WD in our model. It is also possible to include
+MC quanta originate from the accretion disk and a central WD in our model. It is also possible to include
 a boundary layer with user-defined temperature and emitting area. Emission from the wind is dealt with
@@
 
-\subsubsection{Disk Treatment}
+\subsubsection{The Accretion Disk}
 
@@
 on the colour of the emergent spectrum \citep{hassall}. 
-Here we use a blackbody illuminating spectrum
+Here, we use a blackbody illuminating spectrum
 for the ionization cycles (see figure~\ref{sed}) and to compute our MC estimators.
@@
 but a number of studies have found difficulties
-in producing the required ionization state of the wind
+in producing the observed ionization state of the wind
 with such a hot, luminous boundary layer 
@@
 Hoare \& Drew (1991; HD91) \nocite{hoare1991}
-use the Zanstra method to find boundary layer temperatures of
-$\sim80,000{\rm K}$
+use the method of \cite{zanstra1929} to find upper limits on 
+boundary layer temperatures of $\sim80,000{\rm K}$.
 
@@
 area is $4 \pi R_* H$. 
-In the benchmark model, we follow LK02 in setting the boundary layer
-luminosity to zero, and then investigate the effect
-of boundary layers with temperatures of $80,000{\rm K}$ and $200,000{\rm K}$ 
+In our benchmark model, we follow LK02 in setting the boundary layer
+luminosity to zero. We investigate the effect
+of boundary layers with temperatures between $80,000{\rm K}$ and $200,000{\rm K}$ 
 on the ionization state of the wind and resulting
-spectrum. See section 5 for a discussion.
+spectrum in section 5.
 
@@
 are marked with dashed vertical lines.
+{\bf NOTE: CK thinks this figure needs more discussion}.
 %The effective temperature of the accretion disk
@@
 in section 3. The kinematics and mass loss rate of the wind are identical
-to LK02. Photon sources are identical, except that when synthesizing the
-spectrum we treat the accretion disk 
-as an ensemble of Kurucz and TLUSTY stellar atmosphere models to better 
-interpret the behaviour of the Balmer jump. The aim here is to 
-take a successful UV wind model, and examine it's effect 
+to LK02. 
+% Photon sources are identical, except that when synthesizing the
+% spectrum we treat the accretion disk 
+% as an ensemble of Kurucz and TLUSTY stellar atmosphere models to better 
+% interpret the behaviour of the Balmer jump.
+The aim here is to 
+take a successful UV wind model and examine its effect 
 when one utilises the better treatment of lines provided
@@
 \caption{
-UV (left) and Optical synthetic spectra for model A, our benchmark model,
+UV (left) and optical (right) synthetic spectra for model A, our benchmark model,
 computed at sightlines of 10, 27.5, 45, 62.5 and 80 degrees.	
@@
 Figure~\ref{spec} shows optical synthetic spectra for the benchmark 
-model for 5 different sightlines. The first thing to note is that the 
-model produces some lines which are strong enough to overcome
+model for 5 different sightlines.  
+The model produces some lines which are strong enough to overcome
 the absorption cores lines from the disk. These lines are generally double peaked, 
-implying they were formed near the base of the wind where rotational velocity
+implying that they were formed near the base of the wind where rotational velocity
 can still dominate over the slowly increasing poloidal velocity. 
@@
 with increasing inclination, as one would expect from our wind geometry.
-This is expected in CVs and can be seen clearly in figure 1. Note however
+This trend is also observed in CVs and can be seen clearly in figure 1. 
+Note, however,
 that in our models the \heiiuv line does not exhibit this behaviour, which
-is somewhat surprising.
-
-A Balmer jump is present at all inclinations. This is present
-in the stellar atmosphere models used to model the disk,
-and is not a result of photoabsorption through the wind.
-In fact, the wind has a Balmer jump in emission, but it is not prominent enough
-to overcome the intrinsic absorption in the illuminating spectrum. 
+is somewhat surprising. {\bf NOTE: we need to understand this!}.
+
+The Balmer jump is in absorption at all inclinations. This is 
+due to the stellar atmosphere models used to model the disk;
+it is not a result of photoabsorption in the wind.
+In fact, the wind spectrum has the Balmer jump in emission, 
+but this is not prominent enough
+to overcome the intrinsic absorption in the disk spectrum. 
 Figure~\ref{cont} shows the total escaping spectrum, integrated
 over all viewing angles, with the contribution from the disk and wind
-also plotted. It shows that the lines are produced in the wind,
+shown separately. This shows that the lines are produced in the wind,
 and also that the wind is producing a Balmer recombination
@@
 in the UV spectra (see figure~\ref{spec}). In addition, the wind 
-now contributes significant Lyman-$\alpha$ and
+now produces significant Lyman-$\alpha$ and
 He~\textsc{ii}~$\lambda1640{\rm \AA}$  emission. 
@@
 
-In addition to producing synthetic spectra, we are also able to 
+In addition to examining synthetic spectra, we are also able to 
 analyse the physical properties of the outflow.
@@
 C\textsc{iv} is the dominant Carbon ion throughout the wind, allowing
-for an absorbing column which covers a large range of velocitieis, and is thus
+for an absorbing column which covers a large range of velocities and is thus
 sufficient to produce the required broad, deep and blue-shifted absorption lines
-we expect to see in a large fraction of Nova-likes.
+we expect to see in a large fraction of nova-likes.
 
@@
 Clearly, this particular model cannot explain all
-the features seen in the optical spectra of Nova-like variables. However,
-the wind has a clear effect on the spectral features, and cannot be ignored as 
-a both source of line and continuum emission and as a reprocessing `filter'
+the features seen in the optical spectra of nova-like variables. However,
+the wind has a significant effect on the observed spectral features. 
+It cannot be ignored as a source of line and continuum emission and as a reprocessing `filter'
 of the underlying disk spectral energy distribution (SED).
@@
 The benchmark model presented above shows that a wind with the properties
-of Model A, a model that successfully reproduces the UV spectral features,
-would leave a clear imprint on the optical spectrum. It is important
-to understand how changing the kinematics of the wind impacts this
-effect. We can therefore examine the evolution
+of Model A, a model that successfully reproduces the observed UV spectral features
+of CVs,
+would also leave a clear imprint on the optical spectrum. It is important
+to understand how changing the kinematics of the wind impacts on this
+effect. A full parameter search is beyond the scope of this study, 
+but we can examine the evolution
 of the spectrum with a few key parameters. In particular, this
 will help shed light on the predictions of, e.g., Murray \& Chiang (1996)
-and Knigge et al. (1998) regarding the single peaked H$\alpha$ emission
+and Knigge et al. (1998) regarding the single-peaked H$\alpha$ emission
 and absence of a pronounced Balmer absorption edge respectively.
@@
 The emission reaching an observer at a given frequency
-also depends on the sobolev optical depth it experiences, which depends on both
+also depends on the Sobolev optical depth it experiences, which depends on both
 the density and the velocity gradient projected
@@
 \begin{itemize}
- 	\item  The acceleration length, $R_v$, which controls the characteristic scale
- 	over which the wind accelerates.
- 	\item The acceleration exponent, $\alpha$, which focuses the acceleration
+ 	\item the acceleration length, $R_v$, which controls the characteristic scale
+ 	over which the wind accelerates,
+ 	\item the acceleration exponent, $\alpha$, which focuses the acceleration
  	around $R_v$. A higher value of $\alpha$ therefore leads to a slowly accelerating 
- 	wind with a dense base.
- 	\item The launch radii of the wind, $r_{min}$ \& $r_{max}$.
- 	\item The temperature of the boundary layer, $T_{bl}$.
+ 	wind with a dense base,
+ 	\item the launch radii of the wind, $r_{min}$ \& $r_{max}$,
+ 	\item the temperature of the boundary layer, $T_{bl}$.
  \end{itemize}
@@
 In general, quantities which cause a denser wind base increase
-the overal emission, although optical depth effects can clearly cause 
+the overal emission, although optical depth effects can cause 
 the relationship to become more complicated.
@@
 SDL05 found that a biconical disk geometry similar to that adopted here could not reproduce 
-the observed single peaked profiles in YSOs. We have shown
+the observed single peaked profiles in YSOs. Here, we find
 that the mechanism proposed by \cite{MC96} does indeed produce 
 single-peaked line emission in our models, but for this to occur in the majority of
-spectral lines then very high densities are required.
+spectral lines very high densities are required.
 
@@
 Line profiles for \ha\ (right) and \hb\ (left) with varying kinematic 
-properties. The benchmark model is shown in the top panel, and also in grey in each 
+properties, computed for an inclination of $80^\circ$.
+The benchmark model is shown in the top panel, and also in grey in each 
 subsequent plot for comparison. The parameter that has been altered from the benchmark model 
@@
 Line profiles for \heiiuv\ (right) and \heiiopt\  (left) with varying kinematic 
-properties, computed for an incliantion of $80^\circ$. 
+properties, computed for an inclination of $80^\circ$. 
 The panels are organised in the same way as figure~\ref{halpha}.
@@
 with the kinematic properties of the wind,
-computed for an incliantion of $80^\circ$. 
+computed for an inclination of $80^\circ$. 
 the panels are organised in the same way as figure~\ref{halpha}.
@@
 one on the ionization state of the wind, and in particular
-the resultant line emission from \heiiuv, \heiiuv and \civ.
-
-We introduce blackbody boundary layers with temperatures of 80,000K and 200,000K,
+the resultant line emission from \heiiuv, \heiiopt\ and \civ. 
+We introduced blackbody boundary layers with temperatures between 80,000K and 200,000K,
 commonly proposed values in the literature, and adopt a scale height according to
 equation~\ref{bl}. We find that the strength of the C\textsc{iv} line decreases
-with increasing boundary layer temperature, as shown in figure~\ref{jump}.
+with increasing boundary layer temperature. This can be seen
+in figures~\ref{jump}, and also in figure~\ref{bl_grid}, which
+shows the equivalent width of the \civ\ and \heiiuv\ lines as 
+a function of $T_{bl}$.
 We note that a model boundary layer could produce a softer
@@
 meaning that our ionization constraints would
-allow for a higher value of $T_{bl}$. It is also
-possible that a flatter temperature profile in the disk,
+allow for a higher value of $T_{bl}$.
+
+Our findings
+are consistent with calculations carried out by
+\cite{hoaredrew1993}. They find that a high accretion rate 
+($\dot{M}_{acc} \sim 10^{-8}~M_{\odot}yr^{-1}$) 
+system does not necessarily require a boundary layer at all,
+and favour cool or underluminous boundary layers
+in order to explain the strengths of the \civ and N\textsc{v} 
+resonance lines.
+It is also possible that a flatter temperature profile in the disk,
 as suggested by some eclipse mapping observations of NLs (References),
@@
 with $T_{bl} = 200,000$K to exist without over-ionizing the wind.
-We note that there is an element of inconsistency with 
+There is an element of inconsistency with 
 requiring flatter disk temperature profiles in order to permit
-a hotter boundary layer,, as the theoretical argument 
+a hotter boundary layer, as the theoretical argument 
 for the existence and likely temperature of a boundary layer has 
@@
 of $10\%$ of the accretion power. 
-
-It is also instructive here to conduct a hypothetical 
-Zanstra method calculation, following the method of \cite{hoare1991}. 
-We adopt their definitions of the Zanstra ratios in the Helium lines (equations 5 and 6 
-in their paper),
-
-\begin{equation}
-G (\lambda228, 1800 \AA) = 2.4\times 10^{-3} \frac{f(\lambda1640)}{f_*(1800\AA)}
-\end{equation}
-and
-
-\begin{equation}
-G (\lambda228, 1800 \AA) = 1.3\times 10^{-3} \frac{f(\lambda4686)}{f_*(1800\AA)}.\\
-\end{equation}
-
-Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$. (I NEED TO DO THE CALCULATION!).
+It is clear that more work is needed to understand
+
+% It is also instructive here to conduct a hypothetical 
+% Zanstra method calculation, following the method of \cite{hoare1991}. 
+% We adopt their definitions of the Zanstra ratios in the Helium lines (equations 5 and 6 
+% in their paper),
+
+% \begin{equation}
+% G (\lambda228, 1800 \AA) = 2.4\times 10^{-3} \frac{f(\lambda1640)}{f_*(1800\AA)}
+% \end{equation}
+% and
+
+% \begin{equation}
+% G (\lambda228, 1800 \AA) = 1.3\times 10^{-3} \frac{f(\lambda4686)}{f_*(1800\AA)}.\\
+% \end{equation}
+
+% Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$. (I NEED TO DO THE CALCULATION!).
 
@@
 are identical to the benchmark model in geometry and kinematics.
+{\bf NOTE: The increase of He II line around 160kK is something we need to understand!}.
 % The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
@@
 
-\section{A Next-Generation Model}
+\section{An Improved Optical Model }
 
@@
 With modest changes to the kinematics of the benchmark CV model,
-it is possible to produce a `next generation model' with enhanced
-line emission that comes closer to reproducing the observed optical spectrum
+it is possible to produce a model
+that comes closer to reproducing the observed optical spectrum
 of a Nova-like variables. The parameters for this model (imaginatively dubbed Model B)
@@
 We also emphasize that this is no sense a fit to the data. The model
-is designed to reproduce the general behaviour of Nova-likes
+is purely designed to reproduce the general behaviour of nova-likes
 and give an indication of the likely densities and kinematics 
-required in the wind, but we do not seek to provide robust parameter
-or precise parameters.
+required in the wind.
 %quotes a figure of , whereas  halevinhenden2008
@@
 \begin{itemize}
-	\item The `filling-in' of the Balmer jump \citep{elitzur1983} by recombination 
+	\item The `filling-in' of the Balmer jump \citep{KLWB98} by recombination 
 	continuum emission from a disk wind
@@
 shown that the model exhibits verisimilitude with the optical spectrum of RW Tri.
-However, this model does not produce a complete unified CV model, as
-the emission lines in the UV are somewhat unrealistic in strength.
+However, this model does not produce a complete unified CV model. 
+The emission lines in the UV are somewhat unrealistic in strength,
+because the high densities needed to increase line opacity also produce
+a significant collisionally excited contribution..
 This is a shortcoming which must be understood if it is true that
-disk winds modify line profiles to become single peaked, as the 
-densities required produce a large amount of collisionally excited emission
-in UV resonance lines.
+disk winds modify line profiles to become single peaked.
+% as the 
+%densities required produce a large amount of collisionally excited emission
+%in UV resonance lines.
 
@@
 they can act as a spectral filter
-for the disk spectrum, and the properties of the plasma
-is an important tracer for the disk and boundary layer SEDs. 
+for the disk spectrum
+%and the properties of the plasma
+%is an important tracer for the disk and boundary layer SEDs. 
 At a maximum, they may be responsible

### 2014-09-02 draft.tex
Version to send first iteration

@@
 and produces the expected level emissivities. Figure~\ref{tests} shows good agreement with 
-Case B, l-mixed calculations by \cite{seaton1959}, and level
-population calcaultions with \textsc{Tardis.}
+l-mixed Balmer decrements in the Case B limit by \cite{seaton1959}, and 
+also compares He\textsc{i} level populations with \textsc{Tardis.}
 

### 2014-09-17 draft.tex
Lots of changes preparing for second draft

--- 2014-09-02 draft.tex
@@
 \def\apj{ApJ}
+\def\apss{AP\&SS}
 \def\pasp{PASP}
@@
 %\title{Modeling the Optical Spectra of Cataclysmic Variables: The Importance of Disk Winds}
-\title{Disk Winds Matter: Simulating the Optical Spectra of Cataclysmic Variables}
+%\title{Disk Winds Matter: Simulating the Optical Spectra of Cataclysmic Variables}
+\title{The Impact of Disk Winds on the Optical Spectra of Cataclysmic Variables}
 \author{J. H. Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}
@@
 High-state non-magnetic cataclysmic variables (CVs) 
-exhibit strong hydrogen \& helium recombination lines in their optical 
+exhibit strong hydrogen and helium recombination lines in their optical 
 spectra. These lines can be single peaked, and may be formed 
@@
 our Monte Carlo radiative transfer code, which was
-originally used to synthesize the UV spectra of disk-dominated CVs 
+originally used to synthesize the UV spectra of disk-dominated, high-state CVs 
 with a simple biconical wind. 
@@
 enhanced emission in the Ly-$\alpha$ and \heiiuv\ UV lines. 
-In addition, our improved treatment of recombination means that the bound-free continuum
-emission is significant, but does not yet overcome the intrinsic absorption edge
-present in the stellar atmosphere models used to treat the accretion disk.
+% In addition, our improved treatment of recombination means that the bound-free continuum
+% emission is significant, but does not yet overcome the intrinsic absorption edge
+% present in the stellar atmosphere models used to treat the accretion disk.
 We find that a boundary layer is not essential for the production
-of He II recombination lines, but also explore the effect of boundary layers
-with temperatures of $80-200$kK on the ionization state of the wind
-and resulting spectrum.
+of He II recombination lines.
+%  but also explore the effect of boundary layers
+% with temperatures of $80-200$kK on the ionization state of the wind
+% and resulting spectrum.
 A short exploration of a 3-variable kinematic parameter space leads to models with higher densities 
 that are able to produce single-peaked line emission, and also generate sufficient recombination emission
-to fill in the Balmer jump photoabsorption edge.
-Finally, we present a synthetic spectrum of a next generation model in and out of eclipse,
-which shows a striking similarity with the optical spectrum of the high inclination
+to fill in the Balmer jump photoabsorption edge intrinsic to our disk atmosphere spectra.
+Finally, we present a synthetic spectrum of an improved optical model in 
+and out of eclipse, which shows a striking similarity with 
+the optical spectrum of the high inclination
 Nova-like variable RW Tri. The densities near the disk plane in this model
-are such that \civ\ has a large collisionally excited component, in 
+are such that \civfull\ has a large collisionally excited component, in 
 contrast to observations.
@@
 
-Outflows are ubiquitous  in accreting systems across many orders of magnitude in mass,
-from young stellar objects \citep{bunn1995} right up 
-to quasi-stellar objects \citep[QSOs;][]{ganguly2008}. Outflows can take the form of jets, such as those
-seen in X-ray binaries \citep{fender2006} or active galactic nuclei \citep[AGN;][]{marscher2006}, 
-but can also manifest as `winds' emanating from the accretion disk (REFS).
-Understanding the impact of accretion disk winds on spectral features has far-reaching implications. 
-They provide a feedback mechanism to limit the growth of black holes in AGN \citep{silkrees1998},
-and their ever-present nature implies a deep connection with the accretion process. This connection
-is important to understand in order to probe the universality of accretion \citep{mchardy2006, SKUK2012} 
-and to determine the true extent to which
-accretion disks conform to the `$\alpha$-disk' model proposed by 
+% Outflows are ubiquitous  in accreting systems across many orders of magnitude in mass,
+% from young stellar objects \citep{bunn1995} right up 
+% to quasi-stellar objects \citep[QSOs;][]{ganguly2008}. Outflows can take the form of jets, such as those
+% seen in X-ray binaries \citep{fender2006} or active galactic nuclei \citep[AGN;][]{marscher2006}, 
+% but can also manifest as `winds' emanating from the accretion disk (REFS).
+% Understanding the impact of accretion disk winds on spectral features has far-reaching implications. 
+% They provide a feedback mechanism to limit the growth of black holes in AGN \citep{silkrees1998},
+% and their ever-present nature implies a deep connection with the accretion process. This connection
+% is important to understand in order to probe the universality of accretion \citep{mchardy2006, SKUK2012} 
+% and to determine the true extent to which
+% accretion disks conform to the `$\alpha$-disk' model proposed by 
+% \cite{shakurasunyaev1973}. 
+% Despite this, in many types of systems the impact of winds on observational
+% features is essentially unknown, and many theoretical questions relating to their origin 
+% and driving mechanism remain unanswered.
+
+Cataclysmic variables (CVs) are systems in which a white dwarf accretes matter from a donor
+star via Roche-lobe overflow. In non-magnetic, disk-dominated systems this accretion
+is mediated by an accretion disk which forms around the white dwarf. 
+Nova-like variables (NLs) are a particular subclass of objects in which the accretion disk
+is in a permanent state of relatively high accretion rate 
+($\dot{M} \sim 10^{-8}$~M$_{\odot}$~yr$^{-1}$),
+making them the perfect laboratories to test the widely-used 
+`$\alpha$-disk' model proposed by 
 \cite{shakurasunyaev1973}.
+
+For over three decades, it has been known that winds emanating from the accretion disk
+are important in shaping the ultraviolet (UV) spectra of high-state CVs (Heap 1978), 
+the most spectacular evidence being the P-Cygni like profiles of resonance lines such as 
+\civfull\ (see e.g. Cordova \& Mason 1982\nocite{cordova1982}).
 Despite this, in many types of systems the impact of winds on observational
@@
 
-Cataclysmic variables (CVs) are systems in which a white dwarf accretes matter from a donor
-star via Roche-lobe overflow. In non-magnetic, disk-dominated systems this accretion
-is mediated by an accretion disk which forms around the white dwarf. 
-nova-like (NL) variables are a particular subclass of objects in which the accretion disk
-is in a permanent state of relatively high accretion rate 
-($\dot{M} \sim 10^{-8}$~M$_{\odot}$~yr$^{-1}$),
-making them the perfect laboratories to test the $\alpha$-disk model.
-For over three decades, it has been known that winds emanating from the accretion disk
-are important in shaping the ultraviolet (UV) spectra of high-state CVs (Heap 1978), 
-the most spectacular evidence being the P-Cygni like profiles of resonance lines such as 
-C${\textsc {iv}}$ (see e.g. Cordova \& Mason 1982\nocite{cordova1982}).
-
 While the effect of the wind on the UV is at least partially clear, it may also have more subtle 
 effects across the spectral range. It has been proposed that an accretion disk wind
-can cause single-peaked emission line profiles in the optical (Murray \& Chiang 1996), 
-such as those seen in Nova-like variables and, especially, the SW Sex stars (Honeycutt, Schlegel,
-\& Kaitchuck 1986; Dhillon \& Rutten 1995). It is particularly telling that single-peaked 
+can provide a mechanism for single-peaked emission lines (Murray \& Chiang 1996), 
+such as those seen in Nova-like variables and, especially, the SW Sex stars \citep{HSK86, DR95}.
+It is particularly telling that single-peaked 
 lines in high-inclination systems can be seen even in eclipse, suggesting 
@@
 Further evidence of the influence of winds in the optical can occasionally 
-be seen in P-Cygni like signatures, observed in lines such as \ha\ 
+be occasionally seen in P-Cygni like profiles observed in lines such as \ha\ 
 and He \textsc{i} $\lambda5876$ \citep{RN98}.
-In addition, \cite{KLWB98} suggested
-that recombination continuum emission from a disk wind or atmosphere
-could be responsible for filling in the Balmer absorption edge. This provides
-a potential explanation for
-the absence of a pronounced `Balmer jump' in optical spectra of CVs, which has never been adequately produced 
-by theoretical models or spectral synthesis.
-This dense disk atmosphere or wind transition region
-necessary to produce the required recombination emission
-could also explain the Fe~\textsc{ii} `curtain'
-seen in near-UV observations of the high inclination dwarf nova OY Car in quiescence 
-\citep{horne1994}.
+
+% Somewhere, probably the introduction, we need to discuss alternatives for
+% explaining the Balmer Jump problem. The other major possibility is that
+% the disk atmospheres are not correct, see e.g Shaviv or that
+% backscattering fromt he wind changes the disk structure. This is the main
+% weakness in our model approach, because we cannot calculate the atmosphere
+% ourselves. (Christian and I have had some discussions with Hillier, who is
+% here in Aspen, and is the author of CMFGEN.  There was a paper on which he
+% was a co-author where 1-d models of winds were summed to ³make² a CV wind.
+% These used CMFGen and to calculate the structure of the wind, and so may
+% include the backr]reaction of the wind on the disk photosphere.  He said
+% he would check if these models had Balmer jumps, but you might want to
+% find the paper).
+
+It has also been proposed
+that recombination continuum emission from a disk wind or `transition region'
+could be responsible for filling in the Balmer absorption edge  \citep{KLWB98}. 
+This provides a potential explanation for
+the absence of a pronounced `Balmer jump' in optical spectra of CVs, 
+which has never been adequately produced by using stellar atmospheres 
+to model the accretion disk (see e.g. Haug 1987)\nocite{haug1987}. 
+However, it is also possible that accretion disks do not possess
+and intrinsic deep Balmer absorption edges.
+This depends to the optical depth at the edge
+and can change due to decrease due to less temperature variation with height
+near the disk photosphere (see e.g. Shaviv et al. 1991; 
+but also more recent work by Idan et al. 2010).
+\nocite{idanshaviv2010} \nocite{shaviv1991}
+
+% This dense disk atmosphere or wind transition region
+% necessary to produce the required recombination emission
+% could also explain the Fe~\textsc{ii} `curtain'
+% seen in near-UV observations of the high inclination dwarf nova OY Car in quiescence
+
+% In addition, \cite{KLWB98} suggested
+% that recombination continuum emission from a disk wind or atmosphere
+% could be responsible for filling in the Balmer absorption edge. This provides
+% a potential explanation for
+% the absence of a pronounced `Balmer jump' in optical spectra of CVs, which has never been adequately produced 
+% by theoretical models or spectral synthesis.
+% This dense disk atmosphere or wind transition region
+% necessary to produce the required recombination emission
+% could also explain the Fe~\textsc{ii} `curtain'
+% seen in near-UV observations of the high inclination dwarf nova OY Car in quiescence 
+% \citep{horne1994}.
 
@@
 Using spectral synthesis codes to model resonance scattering,
-Shlosman \& Vitello (1993; hereafter SV93) and Knigge, Woods \& Drew (1995; hereafter KWD95)
+Shlosman \& Vitello (1993; hereafter SV93)\nocite{SV93} and \cite{KWD95}
 were both successful in reproducing the observed spectra such as the P-Cygni like
 profiles in C\textsc{iv}~$\lambda1549$\AA.
-Long \& Knigge (2002; LK02) presented a code that
+Long \& Knigge (2002; hereafter LK02)\nocite{LK02} presented a code that
 solved self-consistently for thermal and ionization balance in the wind
-according to the methods of Mazzali \& Lucy (1993; ML93). They successfully reproduced
+according to the methods of Mazzali \& Lucy (1993; ML93)\nocite{ML93}. They successfully reproduced
 UV resonance lines profiles and presented a synthesized spectrum of Z Cam
@@
 Here, we present work using the same Monte Carlo radiative transfer code as LK02, 
-\py, but incorporating additional 
-`macro-atom' techniques suggested by Lucy (2002, 2003). 
-This improves our treatment of the Hydrogen and Helium
-optical lines, as well as recombination continuum emission. 
-Our goal is to investigate the effect of existing wind models
-on the optical spectra of CVs.
-In section 2 we present the code
-and provide a brief description of macro-atoms and the radiative transfer methods we employ. 
+but incorporating additional `macro-atom' techniques suggested by Lucy (2002, 2003). 
+Our aim is to model high-state CVs over a wide spectral range.
+In particular, we hope to assess the potential contribution
+to the optical spectrum from a disk wind model which preserves the UV features.
+It will then be possible to see how closely
+our models resemble the spectra in figure 1 as we change wind parameters.
+We will investigate whether a wind can produce significant
+recombination emission lines and whether the recombination
+continuum emission is sufficient to mask the Balmer jump from a disk atmosphere.
+We will also learn if the mechanism for single-peaked line emission
+proposed by \cite{MC96} works with plausible model parameters.
+In section 2 we present the code and provide a brief description of macro-atoms 
+and the radiative transfer methods we employ. 
 We describe the kinematics and geometry of our biconical wind model in section 3.
-In section 4, we present a benchmark model, which is discussed in section 5 with particular attention 
-devoted to a small-scale parameter search. In section 6, we present a `next generation'
-model which better reproduces the spectral features observed in NLs, and, 
+In section 4, we present a benchmark model, which is explored on in section 5 
+with a small-scale parameter search. In section 6, we present a
+model which better reproduces the optical spectrum of a NL, and, 
 finally, in section 7, we summarise our findings.
+
+% Here, we present work using the same Monte Carlo radiative transfer code as LK02, 
+% \py, but incorporating additional 
+% `macro-atom' techniques suggested by Lucy (2002, 2003). 
+% This improves our treatment of the Hydrogen and Helium
+% optical lines, as well as recombination continuum emission. 
+% Our goal is to investigate the effect of existing wind models
+% on the optical spectra of CVs.
 
@@
 shape and characteristic energies of the illuminating spectrum. 
-It was originally described by LK02, who developed a biconical CV 
-wind model to synthesize UV spectra. 
+It was originally developed by LK02 in order to model the UV spectra
+of CVs with a simple biconical disk wind model.. 
 Higginbottom et al.\nocite{higginbottom2013} (2013; hereafter H13) used the same code to
@@
 % were also incorporated into the heating and cooling balance.
-In addition, \cite[][SDL05]{simmacro2005} modeled
-Brackett and Pfund line profiles in YSOs using \textsc{Python,} which included
-implementing a `macro-atom' mode in order to correctly treat the more
-complex transition matrix involved in recombination.
+In addition, Sim et al. (2005; hereafter SDL05)\nocite{simmacro2005} modeled
+Brackett and Pfund line profiles in young-stellar objects (YSOs) using \textsc{Python,} which included
+implementing a `macro-atom' mode in order to correctly treat recombination lines.
 
@@
 
-Previously, \py used a two-level atom approximation \cite[see e.g.][]{mihalas}. This approximation is 
-fast, and works well as a first approximation when treating so-called `resonance lines' (such as C\textsc{iv}) 
+Previously to SDL05, \py used a two-level atom approximation \cite[see e.g.][]{mihalas}. This approximation is 
+fast, and works well as a first approximation when treating so-called `resonance lines' (such as \civfull) 
 in which the excited electron is strongly coupled to the ground state.
@@
 Lucy (2002, 2003\nocite{lucy2002, lucy2003}; hereafter L02, L03) showed that it is possible 
-to asymptotically reproduce the emissivity of a gas in statistical equilibrium 
-without simplifying the treatment of line transfer. 
+to `asymptotically reproduce the emissivity of a gas in statistical equilibrium 
+without simplifying the treatment of line transfer'. 
 His macro-atom scheme allows all possible transition paths from a given level and a full non-Local 
@@
 For a full description consult L02 and L03. 
-
 Macro-atoms have been used to model astrophysical plasmas in 
-Wolf-Rayet star winds \citep{sim2004}, AGN disk winds \citep{simlong2008, tatum2012}
-and supernovae \citep{kasen2006, kerzendorfsim}.
-SDL05 used \py itself to apply this technique to
-a Hydrogen-only model. We are now able to adopt a hybrid scheme. 
-Any species in which have their level populations determined by
-more complex interactions than resonance transitions
-can be treated as full macro-atoms. The other species are treated as so-called `simple-ions',
-where they still follow the indivisible packet constraint but use the two-level atom approximation.
+Wolf-Rayet star winds \citep{sim2004}, AGN disk winds \citep{simlong2008, tatum2012},
+supernovae \citep{kasen2006, kerzendorfsim} and YSOs (SDL05).
+% Recombination is expected to be an important process in the optical
+% spectra of CVs, and they thus make a perfect application for Lucy's 
+% advances in MC methods.
+
+\subsection{Ionization and Excitation}
+
+Whereas SDL05 used \py itself to apply the macro-atom 
+technique to a Hydrogen-only model, we
+adopt a hybrid ionization and excitation scheme. 
+Species can be treated as either full macro-atoms
+or using the two-level atom approximation.
+In the latter case, they still follow the indivisible packet constraint.
 This allows one to preserve the fast treatment of resonance lines while providing 
-an improved representation of, for example, recombination, which is important when modeling features 
+an improved representation of processes with more complex
+transition paths such as recombination. This is important when modeling features 
 such as the Balmer lines and also recombination {\sl continuum} emission.
-Recombination is expected to be an important process in the optical
-spectra of CVs, and they thus make a perfect application for Lucy's 
-advances in MC methods.
-
-\subsection{Ionization and Excitation}
-
-In our hybrid ionization and excitation scheme, 
-simple-ions have their ionization fractions
-calculated using a modified Saha equation, and internal level populations are
-calculated from LTE. For macro-atoms, we solve the equations of statistical 
-equilibrium using MC estimators for the radiation field. This enables us to 
-determine the ionization and excitation state of the ions in question.
+
+% In our hybrid ionization and excitation scheme, 
+% simple-ions have their ionization fractions
+% calculated using a modified Saha equation, and internal level populations are
+% calculated from LTE. For macro-atoms, we solve the equations of statistical 
+% equilibrium using MC estimators for the radiation field. This enables us to 
+% determine the ionization and excitation state of the ions in question.
 
@@
 % Therefore, 
-we treat H \& He as macro-atoms. 
+We treat H and He as macro-atoms. 
 Macro-atom NLTE level populations and ion fractions are calculated by solving 
-the statistical equilbrium equations between each pair of levels. The rate
-between a lower level $l$ and upper level $u$ in an ion is given by
-
-\begin{eqnarray}
-{\cal R}_{ul} &= & \beta_{lu} A_{ul} n_l + \beta_{lu} B_{ul} n_l J_{lu}^b + C_{ul} n_u n_e\label{eq:nlte_rul}\\
-{\cal R}_{lu} &= & \beta_{lu} B_{lu} n_l J_{lu}^b + C_{lu} n_l n_e,
-\end{eqnarray}
-
-where $A$ and $B$ are Einstein coefficients, $C$ is the collisional rate coefficient and
-$\beta_{lu}$ is the probability that a given line photon will escape the Sobolev
-region. $J^b$ is the MC estimator for mean intensity at the blue wing of the line as 
-recorded during the photon propagation. In the context of 
-bound-free, we consider rates between the continuum state (or, in the case of ions with more than one 
+the statistical equilbrium equations between each pair of levels. The bound-bound 
+de-excitation rate, ${\cal R}_{ul}$, in an ion is given by
+
+\begin{equation}
+{\cal R}_{ul} = \beta_{lu} A_{ul} n_u + \beta_{lu} B_{ul} n_u J_{lu} + C_{ul} n_u n_e,\label{eq:nlte_rul}
+\end{equation}
+
+where $u$ and $l$ denote the upper and lower levels, $C$ is the collisional rate coefficient
+and $A$ and $B$ are the Einstein coefficients. $\beta_{lu}$ is the probability that a 
+given line photon will escape the Sobolev region. $J$ is the MC estimator for the mean intensity in the line as 
+recorded during the photon propagation. The corresponding excitation rate is then
+
+\begin{equation}
+{\cal R}_{lu} = \beta_{lu} B_{lu} n_l J_{lu} + C_{lu} n_l n_e.
+\end{equation}
+
+We also calculate the photoionization rates between a lower level $l$,
+and the continuum state (or, in the case of ions with more than one 
 bound electron, the ground state of the upper ion), $\kappa$,
-and lower level $l$,
-
-\begin{eqnarray}
-{\cal R}_{\kappa l} &= & \alpha_{\kappa l} n_{\kappa} n_e \\
-{\cal R}_{l \kappa} &= & n_l \int_{\nu_0}^{\infty} \frac{ 4 \pi J_{\nu} \sigma_{\nu}}{h \nu} d\nu,
-\end{eqnarray}
-
-where $\sigma_{\nu}$ is the photoioniziation cross section, $\alpha_{\kappa l}$ is the recombination
-coefficient to level $l$ and $J_{\nu}$ is the mean intensity.
+
+\begin{equation}
+{\cal R}_{l \kappa}= n_l \int_{\nu_0}^{\infty} \frac{ 4 \pi J_{\nu} \sigma_{\nu}}{h \nu} d\nu,
+\end{equation}
+
+where $\sigma_{\nu}$ is the photoionization cross section and $J_{\nu}$ is the mean intensity. 
+The recombination rate is given by
+
+\begin{equation}
+{\cal R}_{\kappa l} = \alpha_{\kappa l} n_{\kappa} n_e, \\
+\end{equation}
+
+where $\alpha_{\kappa l}$ is the recombination
+coefficient to level $l$. 
 This treatment means that radiative and collisional rates to and from all 
@@
 The \cite{vanregemorter} approximation is used for collisional transitions,
-and thus we assume collisions between radiatively forbidden collisions are
-negligible, a reasonable approximation in the regime where levels are mainly populated
-by recombination. 
+and thus we assume collisions between radiatively forbidden transitions are
+not important in determining level populations.
+This is a reasonable approximation in the regimes considered here.
 %{2002A&A...384..725L}.  source for beta sobolevs
@@
 
-C, O, N, Ne, Na, Mg, Al, Si, S, Ar, Ca \& Fe are all included as two-level atoms. 
+Lines from all other elements are treated with the two-level atom approximation. 
 This is a first order approximation, which is appropriate 
@@
 respectively. LK02 provide a full description of our implementation.
-
-The reason for using this scheme 
-is twofold. First, unlike in H13, the SED can be approximated well by a dilute blackbody due to the 
-absence of a power-law X-ray source, and therefore the above modification to the Saha equation
-is appropriate; Second, this provides continuity from LK02 and allows us to do a like-for-like comparison.
-This is especially useful in assessing the improvement in Hydrogen line emission, and any changes
-that might occur in the ionization stages of the resonance line species such as CIV. 
-Excitation is then calculated in LTE. 
-%This is because the 
+This ionization scheme is appropriate here because
+the SED can be approximated well by a dilute blackbody due to the 
+absence of a power-law X-ray source, unlike with AGN (see e.g. H13).
+For two-level atoms, we assume LTE level populations.
+% This ionization scheme is appropriate here because, unlike with AGN,
+% the SED can be approximated well by a dilute blackbody due to the 
+% absence of a power-law X-ray source, and therefore the above modification to the Saha equation
+% is appropriate; Second, this provides continuity from LK02 and allows us to do a like-for-like comparison.
+% This is especially useful in assessing the improvement in Hydrogen line emission, and any changes
+% that might occur in the ionization stages of the resonance line species such as CIV. 
+% Excitation is then calculated in LTE. 
+% This is because the 
 % level populations are only important in working out the resonance scattering 
@@
 \subsection{Atomic Data}
-Atomic data is obtained from the same sources described in LK02 and updated in H13. 
-The additional level and line information required to treat He as a macro-atom was 
-obtained from \textsc{Topbase} \citep{topbase2005}. We treat H as a 20-level atom as in SDL05, where 
+Here we use the same atomic data as LK02 and updated by H13.
+We have obtained the additional level and line information required to treat He as a macro-atom 
+from \textsc{Topbase} \citep{topbase2005}. We treat H as a 20-level atom as in SDL05, where 
 each level is defined by the principal quantum number, $n$, which is appropriate due to
@@
 treat the $l$ and $s$ sub-orbitals as distinct levels instead of assuming they are perfectly `l-mixed',
-This also allows the model to produce singlet and 
+This also allows us to model singlet and 
 triplet lines, which are seen in optical CV spectra \citep[e.g.][]{dhillon1996}.
@@
 \py has previously been tested against a number of radiative transfer and
-photoionization codes. Comparisons of ionization balance with \cld \citep{cloudy2013} 
-can be found in LK02 and H13 and show excellent agreement. We have also conducted comparisons
+photoionization codes. LK02 and H13 conducted comparisons of ionization balance 
+with \cld \citep{cloudy2013}, demonstrating excellent agreement. 
+We have also carried out comparisons
 of ionization and spectral synthesis with the supernova code \textsc{Tardis.} \tar is described by
 \cite{kerzendorfsim}, and the spectral comparisons can be found therein.
-In addition to these code validation efforts, we have also conducted tests of
+In addition to these code validation efforts, we have carried out tests of
 the macro atom scheme in \py to verify that it does indeed solve for level populations correctly
 and produces the expected level emissivities. Figure~\ref{tests} shows good agreement with 
-Case B, l-mixed calculations by \cite{seaton1959}, and level
-population calcaultions with \textsc{Tardis.}
+l-mixed Balmer decrement calculations in the Case B limit by \cite{seaton1959}, and 
+also compares He \textsc{i} level populations with \textsc{Tardis.}
 
@@
 \caption{
-{\sl Top Panel:} Balmer decrements from \py compared with analytic calculations
+{\sl Top Panel:} Balmer decrements calculated with \py compared with analytic calculations
 by Seaton (1959), showing good agreement when calculating level emissivities in Hydrogen
@@
 
-Here we describe some of the features of our biconical wind model. Our aim here is not
-to provide a `best fit' model to match any particular dataset.
-Rather, we take as a starting point
-the types of models which have already been successful in explaining UV spectra of CVs.
-We can then examine the contribution of the wind to 
-the optical features when the treatment of line transfer
-is improved.
+Here we describe some of the features of our biconical wind model.
 
@@
 
-Our model follows the prescription outlined by Schlosman \& Vitello (1993; SV93). A schematic is shown
+For our kinematic wind model we use 
+the prescription outlined by Schlosman \& Vitello (1993; hereafter SV93). A schematic is shown
 in figure~\ref{cartoon}. A smooth, biconical
@@
 
-where $l$ is distance measured along a  streamline. The terminal velocity, 
+where $l$ is the poloidal distance. The terminal velocity, 
 $v_{\infty}$, is set to a fixed multiple of the escape velocity at the bottom
@@
 $R_{WD}$ 	 &	 $7\times10^{8}$cm\\ 
-$\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
-$\dot{M}_{wind}$  &	fi\\ 
+$\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$\\ 
+$\dot{M}_{wind}$  &	$10^{-9}~M_{\odot}yr^{-1}$å\\ 
 $r_{min}$ 	&	 $4 R_{WD}$\\ 
@@
 \caption{
-Wind geometry parameters used in the benchmark CV model.}
+Parameters used for the geometry and kinematics of the benchmark CV model.}
 \label{wind_param}
@@
 %The principle of mass conservation 
-The mass continuity equation means that the velocity law also 
+The mass continuity equation implies that the velocity law also 
 controls the density, $\rho$, of the wind, which can be expressed in terms
@@
 
-MC quanta originate from the accretion disk and a central WD in our model. It is also possible to include
+Photons originate from the accretion disk and a central WD in our model. It is also possible to include
 a boundary layer with user-defined temperature and emitting area. Emission from the wind is dealt with
@@
 the surface of the compact object \cite[see e.g.][]{lyndenbell1974}.
-Boundary layers are a possible source of
+Boundary layers are a source of
 high energy photons which may be responsible for the photoionization of 
-He~\textsc{ii}. 
-\cite{pringlesavonije1979} predict temperatures of 
-$200,000-500,000{\rm K}$ for the boundary layer,
-but a number of studies have found difficulties
+He~\textsc{ii}, so a disk wind can therefore be an important diagnostic
+tool for inferring boundary layer luminosities and temperatures. 
+The luminosity of the boundary layer, $L_{bl}$, is related to the accretion luminosity
+by
+
+\begin{equation}
+L_{bl} = \frac{1}{2} L_{acc} (1 - \omega_* / \omega_k)^2,
+\end{equation}
+
+where $\omega_k$ and $\omega_*$ are the angular momenta at the inner disk edge
+and WD surface respectively \citep{fkrbook}. A faster spinning white dwarf 
+will have a less luminous boundary layer.
+
+\cite{pringlesavonije1979} predict theoretical temperatures of 
+$200-500{\rm kK}$ for the boundary layer.
+This high temperature is supported by extreme UV observations \citep{mauche2004}
+and recent modeling \citep{suleimanov2014}, although these studies 
+find $L_{bl}/L_{acc}$ of $\sim0.05$ and $\sim0.2$ respectively in their
+model fits. A number of studies have found difficulties
 in producing the observed ionization state of the wind
@@
 \citep[see e.g.][]{maucheraymond1987, drewverbunt1985}.
-Hoare \& Drew (1991; HD91) \nocite{hoare1991}
+\cite{hoare1991}
 use the method of \cite{zanstra1929} to find upper limits on 
-boundary layer temperatures of $\sim80,000{\rm K}$.
+boundary layer temperatures of $\sim80{\rm kK}$.
 
 It is possible to include a boundary layer in our model which emits 
-as a blackbody with the effective temperature
-
-\begin{equation}
-T_{bl} = \left[ \frac{L_{acc}}{8 \pi R_{WD} H \sigma} ( 1 - \omega_*/\omega_k)^2 \right]^{1/4},
-\label{bl}
-\end{equation}
-
-where $L_{acc}$ is the accretion luminosity, $R_{WD}$ is the WD radius, $H$ is the boundary layer height
-above the disk plane
-and $\omega_*$ and $\omega_k$ are the angular velocities at the WD surface and inner disk edge respectively
-\citep{fkrbook}. Note that we adopt a cylindrical geometry such that the effective emitting
-area is $4 \pi R_* H$. 
-In our benchmark model, we follow LK02 in setting the boundary layer
+as a blackbody with a user-specified effective temperature and luminsoity.
+Boundary layer photons are then produced around the spherical surface of the 
+white dwarf. In our benchmark model, we follow LK02 in setting the boundary layer
 luminosity to zero. We investigate the effect
-of boundary layers with temperatures between $80,000{\rm K}$ and $200,000{\rm K}$ 
+of boundary layers with temperatures between $80{\rm kK}$ and $200{\rm kK}$ 
 on the ionization state of the wind and resulting
@@
 The spectral energy distribution (SED) of the blackbody accretion
-disk used in the ionization calculation (thick black line), 
-with two boundary layer spectra also plotted.
-The SED for an accretion disk
-with the parameters used by HD91 in their Zanstra method calculations is shown in grey. 
-It still assumes a Shakura-Sunyaev temperature profile, but uses
-of $\dot{M}_{acc}= 5\times10^{-9}~M_{\odot}$yr$^{-1}$, and a slightly lower mass
-white dwarf with $M_{WD}=0.7 M_{\odot}$ and $R_{WD} = 7\times10^{8}$cm.
+disk used in the ionization calculation (black line), 
+with two boundary layer blackbody spectra also plotted.
+% The SED for an accretion disk
+% with the parameters used by HD91 in their Zanstra method calculations is shown in grey. 
+% It still assumes a Shakura-Sunyaev temperature profile, but uses
+% of $\dot{M}_{acc}= 5\times10^{-9}~M_{\odot}$yr$^{-1}$, and a slightly lower mass
+% white dwarf with $M_{WD}=0.7 M_{\odot}$ and $R_{WD} = 7\times10^{8}$cm.
 The positions of the Hydrogen and Helium ionization edges 
@@
 
-The results in this section were obtained using the geometry described
-in section 3. The kinematics and mass loss rate of the wind are identical
-to LK02. 
+% The results in this section were obtained using the geometry described
+% in section 3. The kinematics and mass loss rate of the wind are identical
+% to LK02. 
 % Photon sources are identical, except that when synthesizing the
@@
 % interpret the behaviour of the Balmer jump.
-The aim here is to 
-take a successful UV wind model and examine its effect 
+
+Our aim here is not
+to provide a `best fit' model to match any particular dataset.
+Rather, we take
+a successful UV wind model as a starting point
+and examine its effect 
 when one utilises the better treatment of lines provided
 by the macro-atom scheme.
+
+% The specific model 
+% parameters are summarised in table 1, and follow LK02. 
+% They are motivated by a need to agree with typical observed values 
+% for NLs and the values required to reproduce the UV line profile
 
@@
 The inset plots show zoomed-in line profiles for 
-\heiiuv and \ha. Double-peaked line emission can be seen in 
+\heiiuv\ and \ha. Double-peaked line emission can be seen in 
 \heiiuv, \heiiopt, \ha\ and some He I lines, but the 
@@
 Figure~\ref{spec} shows optical synthetic spectra for the benchmark 
-model for 5 different sightlines.  
+model for five different inclination angles ranging from $10^\circ$ to $80^\circ$ 
+%5 different sightlines.  
 The model produces some lines which are strong enough to overcome
 the absorption cores lines from the disk. These lines are generally double peaked, 
-implying that they were formed near the base of the wind where rotational velocity
-can still dominate over the slowly increasing poloidal velocity. 
+as they are formed near the base of the wind where rotational velocity
+can still dominate over the slowly increasing poloidal velocity. The line 
+opacity is not yet high enough for the poloidal velocity gradient to 
+cause single-peaked profiles. 
 We also see a general trend from absorption to emission in spectral lines
 with increasing inclination, as one would expect from our wind geometry.
-This trend is also observed in CVs and can be seen clearly in figure 1. 
-Note, however,
-that in our models the \heiiuv line does not exhibit this behaviour, which
-is somewhat surprising. {\bf NOTE: we need to understand this!}.
+This trend is observed in CVs and can be seen clearly in figure 1. 
+% Note, however,
+% that in our models the \heiiuv\ line does not exhibit this behaviour, which
+% is somewhat surprising. {\bf NOTE: we need to understand this!}.
 
@@
 \caption{
-The Physical Properties of the wind. Near
-the disk plane the wind is dense, with low poloidal velocities.
+The physical properties of the wind- note the logarithmic scale. 
+Near the disk plane the wind is dense, with low poloidal velocities.
 As the wind accelerates it becomes less dense
@@
 
-\section{Discussion of Results}
+\section{Exploring Parameter Space}
 
@@
 
-\subsection{Exploring Parameter Space}
-
 The amount of line and recombination continuum
@@
 
+A full kinematic parameter search may prove instructive, but
+is beyond the scope of this particular study.
 We have therefore conducted a limited parameter 
-sweep, exploring the effect of changing a few key parameters.  We focus on 
-4 variables in order to explore the trends in our model. These are:
+search, where we focus on 
+two variables in order to explore the trends in our model. 
+These are:
 
@@
  	over which the wind accelerates,
- 	\item the acceleration exponent, $\alpha$, which focuses the acceleration
- 	around $R_v$. A higher value of $\alpha$ therefore leads to a slowly accelerating 
+ 	\item the acceleration exponent, $\alpha$, which controls the rate 
+ 	at which the velocity changes near $R_v$. 
+ 	A higher value of $\alpha$ therefore leads to a slowly accelerating 
  	wind with a dense base,
- 	\item the launch radii of the wind, $r_{min}$ \& $r_{max}$,
- 	\item the temperature of the boundary layer, $T_{bl}$.
+ 	% \item the launch radii of the wind, $r_{min}$ \& $r_{max}$,
+ 	%%\item the temperature of the boundary layer, $T_{bl}$.
  \end{itemize}
@@
 We have found these to be important parameters in modifying 
-the spectral features and ionization state of the wind.
+the emergent spectrum.
 In general, quantities which cause a denser wind base increase
-the overal emission, although optical depth effects can cause 
-the relationship to become more complicated.
+the overall emission, although optical depth effects can cause 
+the relationship to become more complicated. In addition to these 
+kinematic parameters, we also investigate the effect of 
+including a boundary layer on the equivalent widths of the 
+\civfull\ and \heiiuv\ lines (see section 5.3).
 
@@
 
-In order to produce single-peaked line emission at high inclinations,
+In order to produce single-peaked line emission in the majority of lines at high inclinations,
 it is clear that a higher line opacity is needed at the red and blue wings relative to
@@
 SDL05 found that a biconical disk geometry similar to that adopted here could not reproduce 
-the observed single peaked profiles in YSOs. Here, we find
+the observed single peaked profiles in YSOs. 
+Here, we find
 that the mechanism proposed by \cite{MC96} does indeed produce 
-single-peaked line emission in our models, but for this to occur in the majority of
+single-peaked line emission in our models with plausible wind parameters, 
+but for this to occur in the majority of
 spectral lines very high densities are required.
@@
 \mbox{
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_alpha_0.eps}}
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_alpha.eps}}
 \quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_beta_0.eps}}   
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_beta.eps}}   
 }
@@
 The left panel of figure~\ref{jump} shows the evolution
-of the Balmer jump with a number of key parameters. Higher density models
+of the Balmer jump with our kinematic parameters. Higher density models
 produce sufficient recombination continuum emission to fill 
@@
 \quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_4686_0.eps}}   
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_4686.eps}}   
 }
@@
 \caption{
-Line profiles for \heiiuv\ (right) and \heiiopt\  (left) with varying kinematic 
+Line profiles for \heiiuv\ (left) and \heiiopt\  (right) with varying kinematic 
 properties, computed for an inclination of $80^\circ$. 
@@
 \mbox{
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_balmer_0.eps}}
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_balmer.eps}}
 \quad
@@
 \caption{The evolution of the Balmer jump and higher order Balmer lines (left) 
-and the \civ\ line profile (right)
+and the \civfull\ line profile (right)
 with the kinematic properties of the wind,
@@
 one on the ionization state of the wind, and in particular
-the resultant line emission from \heiiuv, \heiiopt\ and \civ. 
+the resultant line emission from \heiiuv, \heiiopt\ and \civfull. 
 We introduced blackbody boundary layers with temperatures between 80,000K and 200,000K,
-commonly proposed values in the literature, and adopt a scale height according to
-equation~\ref{bl}. We find that the strength of the C\textsc{iv} line decreases
+commonly proposed values in the literature, and adopt a luminosity of
+$L_{acc} / 2$. We find that the strength of the C\textsc{iv} line decreases
 with increasing boundary layer temperature. This can be seen
 in figures~\ref{jump}, and also in figure~\ref{bl_grid}, which
-shows the equivalent width of the \civ\ and \heiiuv\ lines as 
+shows the equivalent width of the \civfull\ and \heiiuv\ lines as 
 a function of $T_{bl}$.
-We note that a model boundary layer could produce a softer
-spectrum for a given effective temperature \citep[e.g.][]{suleimanov2014}, 
-meaning that our ionization constraints would
-allow for a higher value of $T_{bl}$.
-
-Our findings
-are consistent with calculations carried out by
-\cite{hoaredrew1993}. They find that a high accretion rate 
+
+Our models favour cool or underluminous boundary layers,
+consistent with calculations carried out by
+\cite{hoaredrew1993}. However,
+it should be stressed that this result is extremely
+sensitive to the flux at the He \textsc{ii} and \civ\ 
+ionisation edges, so different disk or boundary layer
+SEDs would significantly impact this conclusion.
+For example, a slightly lower mass loss rate in the disk
+would permit a hotter boundary layer, and a modeled boundary layer
+would produce a softer spectrum for a given effective temperature
+(see e.g. Suleimanov 2014). Our main finding
+is therefore that a high accretion rate 
 ($\dot{M}_{acc} \sim 10^{-8}~M_{\odot}yr^{-1}$) 
-system does not necessarily require a boundary layer at all,
-and favour cool or underluminous boundary layers
-in order to explain the strengths of the \civ and N\textsc{v} 
-resonance lines.
-It is also possible that a flatter temperature profile in the disk,
-as suggested by some eclipse mapping observations of NLs (References),
-would cause a softer disk spectrum and allow a boundary layer 
-with $T_{bl} = 200,000$K to exist without over-ionizing the wind.
-There is an element of inconsistency with 
-requiring flatter disk temperature profiles in order to permit
-a hotter boundary layer, as the theoretical argument 
-for the existence and likely temperature of a boundary layer has 
-mostly been put together assuming a Shakura-Sunyaev disk.  
-Radio emission has been seen in CVs, possibly implying the 
-existence of a radio jet \cite[see e.g.][]{kordingDNjet2008,kording2011}.
-A jet could extract some of the energy which is supposedly dissipated in the 
-boundary layer, causing $L_{bl} < L_{acc}/2$, although
-observations suggest the jet power would only be on the order
-of $10\%$ of the accretion power. 
-It is clear that more work is needed to understand
+system does not necessarily require a boundary layer to produce
+He \textsc{ii} recombination lines, but we are not
+able to rule out any range of temperatures or
+luminosities without better understanding of
+the accretion disk.
+
+% Our findings
+% are consistent with calculations carried out by
+% \cite{hoaredrew1993}. They find that a high accretion rate 
+% ($\dot{M}_{acc} \sim 10^{-8}~M_{\odot}yr^{-1}$) 
+% system does not necessarily require a boundary layer at all,
+% and favour cool or underluminous boundary layers
+% in order to explain the strengths of the \civ\ and N \textsc{v} 
+% resonance lines.
+% It is also possible that a flatter temperature profile in the disk,
+% as suggested by some eclipse mapping observations of NLs (References),
+% would cause a softer disk spectrum and allow a boundary layer 
+% with $T_{bl} = 200,000$K to exist without over-ionizing the wind.
+% There is an element of inconsistency with 
+% requiring flatter disk temperature profiles in order to permit
+% a hotter boundary layer, as the theoretical argument 
+% for the existence and likely temperature of a boundary layer has 
+% mostly been put together assuming a Shakura-Sunyaev disk.  
+% Radio emission has been seen in CVs, possibly implying the 
+% existence of a radio jet \cite[see e.g.][]{kordingDNjet2008,kording2011}.
+% A jet could extract some of the energy which is supposedly dissipated in the 
+% boundary layer, causing $L_{bl} < L_{acc}/2$, although
+% observations suggest the jet power would only be on the order
+% of $10\%$ of the accretion power. 
+% It is clear that more work is needed to understand
 
@@
 Equivalent widths of the \civfull\ and \heiiuv\ lines
-as a function of boundary layer temperature. The models used
+as a function of boundary layer temperature, for a viewing angle of $80^\circ$. The models used
 are identical to the benchmark model in geometry and kinematics.
@@
 that comes closer to reproducing the observed optical spectrum
-of a Nova-like variables. The parameters for this model (imaginatively dubbed Model B)
+of a NLs. The parameters for this model (imaginatively dubbed Model B)
 are show in table~\ref{modelb}, and the synthetic spectrum
@@
 between the synthetic spectrum
-at an angle of $80^\circ$ and the high-inclination nova-like RW Tri 
+at an angle of $80^\circ$ and the high-inclination NL RW Tri 
 is also shown in figure~\ref{rwtricomp}. The inclination
@@
 We also emphasize that this is no sense a fit to the data. The model
-is purely designed to reproduce the general behaviour of nova-likes
+is purely designed to reproduce the general behaviour of NLs
 and give an indication of the likely densities and kinematics 
@@
 The inset plots show zoomed-in line profiles for 
-\heiiuv \ and \ha. The \ha line 
+\heiiuv\ and \ha. The \ha line 
 is single peaked, but higher order lines in the Balmer series
 are double-peaked, albeit with narrower profiles.
-Strong \heiiopt emission can be seen, as well a trend
-of a deeper Balemr jump with decreasing inclination.
+Strong \heiiopt\ emission can be seen, as well a trend
+of a deeper Balmer jump with decreasing inclination.
 }
@@
 \caption{{\sl Top Panel:} In and out of eclipse spectra of the high
-inclination Nova-like RW Tri. {\sl Bottom Panel:} In and out of eclipse synthetic
+inclination NL RW Tri. {\sl Bottom Panel:} In and out of eclipse synthetic
 spectra from Model B.}
@@
 and continuum emission blueward of the Balmer edge.
-We have confirmed a number of the expected trends
+We have confirmed a number of the expected behaviours
 by exploring a limited number of parameters governing the
@@
 \heiiopt\ are seen. 
-	\item A Balmer jump in emission during eclipse.
+	\item We expect Balmer jump in emission during eclipse.
 \end{itemize}
@@
 \smallskip
-We have presented a next-generation model
-which produces all the prominent lines in and out of eclipse, and
-shown that the model exhibits verisimilitude with the optical spectrum of RW Tri.
+Our improved optical model produces all the prominent lines in and out of eclipse, and
+exhibits verisimilitude with the optical spectrum of RW Tri.
 However, this model does not produce a complete unified CV model. 
@@
 Our work demonstrates that, if nothing else,
-{\sl disk winds matter}. At a minimum,
+{\sl disk winds matter} in the optical. At a minimum,
 they can act as a spectral filter
-for the disk spectrum
+for the disk spectrum.
 %and the properties of the plasma
@@
 At a maximum, they may be responsible
-for the majority of spectral features of high-state CVs,
+for the majority of optical spectral features of high-state CVs,
 and could dominate the appearance of both UV and optical

### 2014-09-18 draft.tex
Second draft version to send

@@
 and RW Tri in eclipse (Bottom; Groot et al. 2004).
-The data have been digitized from the respective publications. 
+The data have been digitized from the respective publications and a few of the more
+prominent emission and absorption lines are marked. 
 These systems have inclinations of $30^\circ$, $60^\circ$ and $70^\circ$ 
@@
 
+%The principle of mass conservation 
+The mass continuity equation implies that the velocity law also 
+controls the density, $\rho$, of the wind, which can be expressed in terms
+of radial and vertical position $(r,z)$ as
+
+\begin{equation}
+\rho(r,z) = \frac{r}{r_0} \frac{dr}{dr_0} \frac{\phi(r_0)}{v_z(r,z)},
+\label{density}
+\end{equation}
+
+where $\phi$ is the mass-loss rate per unit area at $r_0$
+and $v_z$ is the vertical velocity component. In our model, we
+adopt a uniform value for $\phi$.
+
+\subsection{Photon Sources}
+
+Photons originate from the accretion disk and a central WD in our model. It is also possible to include
+a boundary layer with user-defined temperature and emitting area. Emission from the wind is dealt with
+by reprocessing of the indivisible energy packets originally produced in the disk or central WD.
+
+\subsubsection{The Accretion Disk}
+
+\py has has some flexibility when treating the accretion disk as a source of photons. 
+The disk is broken down into annuli 
+such that each annulus contributes an equal amount to the bolometric luminosity. 
+We adopt the temperature profile of a standard \cite{shakurasunyaev1973} $\alpha$-disk.
+%shown in figure 1.
+An annulus can then
+be treated either as a blackbody with the corresponding effective temperature or as a stellar atmosphere model
+with the appropriate surface gravity and effective temperature. 
+Both of these methods have limitations. It is known
+from studies of CV accretion disks that they exhibit absorption cores 
+formed in an optically thick disk atmosphere.
+This can impact the overall spectrum even if a wind is present 
+\citep[see e.g.][]{dhillon1996}.
+However, the stellar atmosphere models
+have had difficulties reproducing the required spectral shape \citep{wade1988}, 
+and there are inconsistencies when using a 
+stellar atmosphere beneath a dense
+wind region that itself goes some way to simulating the disk atmosphere. 
+In addition, \cite{linnell2010} found that deviations from the predicted 
+$T\propto r^{-3/4}$ temperature profile are required to fit the data
+in certain cases.
+
+We hope that future simulations, coupled with a comparison to data, will 
+actually address some of these problems, particularly since
+the filtering effect of the wind may cause noticeable effects
+on the colour of the emergent spectrum \citep{hassall}. 
+Here, we use a blackbody illuminating spectrum
+for the ionization cycles (see figure~\ref{sed}) and to compute our MC estimators.
+During the spectral synthesis stage of the simulation we use stellar atmosphere models.
+This is partly because they provide the most pessimistic prediction in terms of whether recombination emission in the 
+wind can fill in the Balmer jump, due to their intrinsic strong absorption beyond the Balmer edge.
+For low temperatures, we use stellar atmospheres computed 
+by Kurucz \citep{kurucz1991}, and for $T>50,000$~K we use models computed with 
+\textsc{TLUSTY} \citep{tlusty}. The input spectra are created from these model
+atmospheres using \textsc{Synspec}\footnote{http://nova.astro.umd.edu/Synspec43/synspec.html}.
+%The temperature profile of our disk,
+%with $\dot{M}_{acc} = 10^{-8}~M_{\odot}yr^{-1}$ can be seen in figure~\ref{t_profile}.
+% more detail on why we use this hodge podge of atmosphere models?
+
+\subsubsection{Boundary Layer}
+The existence of a boundary layer in CVs arises naturally from the boundary condition
+of the \cite{shakurasunyaev1973} model, since the material at the inner disk
+edge must lose angular momentum in order to be deposited on
+the surface of the compact object \cite[see e.g.][]{lyndenbell1974}.
+Boundary layers are a source of
+high energy photons which may be responsible for the photoionization of 
+He~\textsc{ii}, so a disk wind can therefore be an important diagnostic
+tool for inferring boundary layer luminosities and temperatures. 
+The luminosity of the boundary layer, $L_{bl}$, is related to the accretion luminosity
+by
+
+\begin{equation}
+L_{bl} = \frac{1}{2} L_{acc} (1 - \omega_* / \omega_k)^2,
+\end{equation}
+
+where $\omega_k$ and $\omega_*$ are the angular momenta at the inner disk edge
+and WD surface respectively \citep{fkrbook}. A faster spinning white dwarf 
+will have a less luminous boundary layer.
+
+\cite{pringlesavonije1979} predict theoretical temperatures of 
+$200-500{\rm kK}$ for the boundary layer.
+This high temperature is supported by extreme UV observations \citep{mauche2004}
+and recent modeling \citep{suleimanov2014}, although these studies 
+find $L_{bl}/L_{acc}$ of $\sim0.05$ and $\sim0.2$ respectively in their
+model fits. A number of studies have found difficulties
+in producing the observed ionization state of the wind
+with such a hot, luminous boundary layer 
+\citep[see e.g.][]{maucheraymond1987, drewverbunt1985}.
+\cite{hoare1991}
+use the method of \cite{zanstra1929} to find upper limits on 
+boundary layer temperatures of $\sim80{\rm kK}$.
+
+It is possible to include a boundary layer in our model which emits 
+as a blackbody with a user-specified effective temperature and luminsoity.
+Boundary layer photons are then produced around the spherical surface of the 
+white dwarf. In our benchmark model, we follow LK02 in setting the boundary layer
+luminosity to zero. We investigate the effect
+of boundary layers with temperatures between $80{\rm kK}$ and $200{\rm kK}$ 
+on the ionization state of the wind and resulting
+spectrum in section 5.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{figures/sed_figure.eps}
+\caption{
+The spectral energy distribution (SED) of the blackbody accretion
+disk used in the ionization calculation (black line), 
+with two boundary layer blackbody spectra also plotted.
+% The SED for an accretion disk
+% with the parameters used by HD91 in their Zanstra method calculations is shown in grey. 
+% It still assumes a Shakura-Sunyaev temperature profile, but uses
+% of $\dot{M}_{acc}= 5\times10^{-9}~M_{\odot}$yr$^{-1}$, and a slightly lower mass
+% white dwarf with $M_{WD}=0.7 M_{\odot}$ and $R_{WD} = 7\times10^{8}$cm.
+The positions of the Hydrogen and Helium ionization edges 
+are marked with dashed vertical lines.
+{\bf NOTE: CK thinks this figure needs more discussion}.
+%The effective temperature of the accretion disk
+%in our model, as a function of radius.
+}
+\label{sed}
+\end{figure}
+
+% \noindent\rule{16cm}{0.4pt}
+%
+% {\bf
+% \noindent Notes on Section 3:
+
+% \begin{itemize}
+% 	\item
+
+% \noindent Potential Additional Figures:
+
+% \begin{itemize}
+% 	\item 	
+% }
+%
+% \noindent\rule{16cm}{0.4pt}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%          RESULTS
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{table}
@@
 
-%The principle of mass conservation 
-The mass continuity equation implies that the velocity law also 
-controls the density, $\rho$, of the wind, which can be expressed in terms
-of radial and vertical position $(r,z)$ as
-
-\begin{equation}
-\rho(r,z) = \frac{r}{r_0} \frac{dr}{dr_0} \frac{\phi(r_0)}{v_z(r,z)},
-\label{density}
-\end{equation}
-
-where $\phi$ is the mass-loss rate per unit area at $r_0$
-and $v_z$ is the vertical velocity component. In our model, we
-adopt a uniform value for $\phi$.
-
-\subsection{Photon Sources}
-
-Photons originate from the accretion disk and a central WD in our model. It is also possible to include
-a boundary layer with user-defined temperature and emitting area. Emission from the wind is dealt with
-by reprocessing of the indivisible energy packets originally produced in the disk or central WD.
-
-\subsubsection{The Accretion Disk}
-
-\py has has some flexibility when treating the accretion disk as a source of photons. 
-The disk is broken down into annuli 
-such that each annulus contributes an equal amount to the bolometric luminosity. 
-We adopt the temperature profile of a standard \cite{shakurasunyaev1973} $\alpha$-disk.
-%shown in figure 1.
-An annulus can then
-be treated either as a blackbody with the corresponding effective temperature or as a stellar atmosphere model
-with the appropriate surface gravity and effective temperature. 
-Both of these methods have limitations. It is known
-from studies of CV accretion disks that they exhibit absorption cores 
-formed in an optically thick disk atmosphere.
-This can impact the overall spectrum even if a wind is present 
-\citep[see e.g.][]{dhillon1996}.
-However, the stellar atmosphere models
-have had difficulties reproducing the required spectral shape \citep{wade1988}, 
-and there are inconsistencies when using a 
-stellar atmosphere beneath a dense
-wind region that itself goes some way to simulating the disk atmosphere. 
-In addition, \cite{linnell2010} found that deviations from the predicted 
-$T\propto r^{-3/4}$ temperature profile are required to fit the data
-in certain cases.
-
-We hope that future simulations, coupled with a comparison to data, will 
-actually address some of these problems, particularly since
-the filtering effect of the wind may cause noticeable effects
-on the colour of the emergent spectrum \citep{hassall}. 
-Here, we use a blackbody illuminating spectrum
-for the ionization cycles (see figure~\ref{sed}) and to compute our MC estimators.
-During the spectral synthesis stage of the simulation we use stellar atmosphere models.
-This is partly because they provide the most pessimistic prediction in terms of whether recombination emission in the 
-wind can fill in the Balmer jump, due to their intrinsic strong absorption beyond the Balmer edge.
-For low temperatures, we use stellar atmospheres computed 
-by Kurucz \citep{kurucz1991}, and for $T>50,000$~K we use models computed with 
-\textsc{TLUSTY} \citep{tlusty}. The input spectra are created from these model
-atmospheres using \textsc{Synspec}\footnote{http://nova.astro.umd.edu/Synspec43/synspec.html}.
-%The temperature profile of our disk,
-%with $\dot{M}_{acc} = 10^{-8}~M_{\odot}yr^{-1}$ can be seen in figure~\ref{t_profile}.
-% more detail on why we use this hodge podge of atmosphere models?
-
-\subsubsection{Boundary Layer}
-The existence of a boundary layer in CVs arises naturally from the boundary condition
-of the \cite{shakurasunyaev1973} model, since the material at the inner disk
-edge must lose angular momentum in order to be deposited on
-the surface of the compact object \cite[see e.g.][]{lyndenbell1974}.
-Boundary layers are a source of
-high energy photons which may be responsible for the photoionization of 
-He~\textsc{ii}, so a disk wind can therefore be an important diagnostic
-tool for inferring boundary layer luminosities and temperatures. 
-The luminosity of the boundary layer, $L_{bl}$, is related to the accretion luminosity
-by
-
-\begin{equation}
-L_{bl} = \frac{1}{2} L_{acc} (1 - \omega_* / \omega_k)^2,
-\end{equation}
-
-where $\omega_k$ and $\omega_*$ are the angular momenta at the inner disk edge
-and WD surface respectively \citep{fkrbook}. A faster spinning white dwarf 
-will have a less luminous boundary layer.
-
-\cite{pringlesavonije1979} predict theoretical temperatures of 
-$200-500{\rm kK}$ for the boundary layer.
-This high temperature is supported by extreme UV observations \citep{mauche2004}
-and recent modeling \citep{suleimanov2014}, although these studies 
-find $L_{bl}/L_{acc}$ of $\sim0.05$ and $\sim0.2$ respectively in their
-model fits. A number of studies have found difficulties
-in producing the observed ionization state of the wind
-with such a hot, luminous boundary layer 
-\citep[see e.g.][]{maucheraymond1987, drewverbunt1985}.
-\cite{hoare1991}
-use the method of \cite{zanstra1929} to find upper limits on 
-boundary layer temperatures of $\sim80{\rm kK}$.
-
-It is possible to include a boundary layer in our model which emits 
-as a blackbody with a user-specified effective temperature and luminsoity.
-Boundary layer photons are then produced around the spherical surface of the 
-white dwarf. In our benchmark model, we follow LK02 in setting the boundary layer
-luminosity to zero. We investigate the effect
-of boundary layers with temperatures between $80{\rm kK}$ and $200{\rm kK}$ 
-on the ionization state of the wind and resulting
-spectrum in section 5.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{figures/sed_figure.eps}
-\caption{
-The spectral energy distribution (SED) of the blackbody accretion
-disk used in the ionization calculation (black line), 
-with two boundary layer blackbody spectra also plotted.
-% The SED for an accretion disk
-% with the parameters used by HD91 in their Zanstra method calculations is shown in grey. 
-% It still assumes a Shakura-Sunyaev temperature profile, but uses
-% of $\dot{M}_{acc}= 5\times10^{-9}~M_{\odot}$yr$^{-1}$, and a slightly lower mass
-% white dwarf with $M_{WD}=0.7 M_{\odot}$ and $R_{WD} = 7\times10^{8}$cm.
-The positions of the Hydrogen and Helium ionization edges 
-are marked with dashed vertical lines.
-{\bf NOTE: CK thinks this figure needs more discussion}.
-%The effective temperature of the accretion disk
-%in our model, as a function of radius.
-}
-\label{sed}
-\end{figure}
-
-% \noindent\rule{16cm}{0.4pt}
-%
-% {\bf
-% \noindent Notes on Section 3:
-
-% \begin{itemize}
-% 	\item
-
-% \noindent Potential Additional Figures:
-
-% \begin{itemize}
-% 	\item 	
-% }
-%
-% \noindent\rule{16cm}{0.4pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%          RESULTS
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Results \& Analysis from a Benchmark Model}
@@
 by the macro-atom scheme.
-
+The model parameters are shown in table 1. 
+they are identical to LK02, and were chosen both to reflect typical
+values for NLs and reproduce realistic UV line profiles.
 % The specific model 
@@
 \caption{
-Line profiles for \ha\ (right) and \hb\ (left) with varying kinematic 
+Line profiles for \ha\ (left) and \hb\ (right) with varying kinematic 
 properties, computed for an inclination of $80^\circ$.
-The benchmark model is shown in the top panel, and also in grey in each 
-subsequent plot for comparison. The parameter that has been altered from the benchmark model 
-is marked on each panel. For the left and middle right columns, models lower down
-are more slowly accelerating and have denser wind bases. The middle right column
-shows the variation with wider launch radii, and the right hand column shows 
-how a boundary layer of increasing temperature affects the spectrum.
+The benchmark model is shown in the top left panel, and the improved optical
+model described in section 6 is highlighted in bold. 
+The parameter that has been altered from the benchmark model 
+is marked in each column and row. 
+Models towards the bottom right
+are have more slowly accelerating winds and denser wind bases. 
+% The middle right column
+% shows the variation with wider launch radii, and the right hand column shows 
+% how a boundary layer of increasing temperature affects the spectrum.
 % How the H$\alpha$ and H$\beta$ lines in our model change with the kinematic properties
@@
 The left panel of figure~\ref{jump} shows the evolution
-of the Balmer jump with our kinematic parameters. Higher density models
+of the Balmer jump with our kinematic parameters. 
+The `absorption' feature just redward of the Balmer jump
+is artificial. It is caused by line blanketing in the stellar atmospheres,
+which is not filled in by line emission from the wind
+due to the use of a 20-level Hydrogen atom.
+The higher density models
 produce sufficient recombination continuum emission to fill 
@@
 to explain the emission features present \citep{kd1997}.
-
 % \noindent\rule{16cm}{0.4pt}
@@
 \mbox{
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_1640_0.eps}}
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_1640.eps}}
 \quad
@@
 \quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_uv_0.eps}}   
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_uv.eps}}   
 }
@@
 inclination NL RW Tri. {\sl Bottom Panel:} In and out of eclipse synthetic
-spectra from Model B.}
+spectra from Model B.
+The artificial `absorption' feature just redward of the Balmer jump
+is caused for the reasons described in section 5.2.}
 \label{rwtricomp}

### 2014-10-13 draft.tex
updated to ksl version

@@
 exhibit strong hydrogen and helium recombination lines in their optical 
-spectra. These lines can be single peaked, and may be formed 
-in the same bipolar outflow that is responsible for the
-blue-shifted absorption lines seen in the ultraviolet (UV).
-Here, we present results obtained by incorporating a `macro-atom' treatment into
-our Monte Carlo radiative transfer code, which was
-originally used to synthesize the UV spectra of disk-dominated, high-state CVs 
-with a simple biconical wind. 
-Using an identical model, we show that the same wind leaves a noticeable imprint 
+spectra. These lines can be single peaked.  The Balmer jump observed in such systems
+is less pronounced than one would expect if the continuum in these systems arises solely from disk emission
+calculated by summing appropriately weighted stellar atmospheres.  Here we investigate the possibility that
+both of these effects are due to emission from the bipolar outflows that are known to be 
+  responsible for the
+blue-shifted absorption lines seen in the ultraviolet (UV).  For this study, we used an improved version of
+the Monte Carlo radiative transfer code that we used previously to show qualitatively that the UV spectra of disk-dominated,
+high state CVs could be reproduced from a relatively simple parameterization of a biconical wind with a mass loss rate about one-tenth of the mass accretion rate.
+%Here, we present results obtained by incorporating a `macro-atom' treatment into our Monte Carlo radiative transfer code, which was originally used to synthesize the UV spectra of disk-dominated, high-state CVs  with a simple biconical wind.
+We find that the same parameterized model leaves a noticeable imprint 
 on the optical spectrum, producing \ha\ and \heiiopt\ as well as
@@
 % present in the stellar atmosphere models used to treat the accretion disk.
-We find that a boundary layer is not essential for the production
-of He II recombination lines.
+A boundary layer is not essential for the production
+of He II recombination lines.  However, all of the optical lines produced from our original parameterization are double-peaked, and the effect on the Balmer line region is modest.
 %  but also explore the effect of boundary layers
@@
 % and resulting spectrum.
-A short exploration of a 3-variable kinematic parameter space leads to models with higher densities 
-that are able to produce single-peaked line emission, and also generate sufficient recombination emission
+Based on  a short exploration of a 3-variable kinematic parameter space, we conclude that  models with higher densities are needed 
+ to produce single-peaked line emission, and to generate sufficient recombination emission
 to fill in the Balmer jump photoabsorption edge intrinsic to our disk atmosphere spectra.
-Finally, we present a synthetic spectrum of an improved optical model in 
-and out of eclipse, which shows a striking similarity with 
+The  synthetic spectra using the revised set of parameters  shows  striking similarity with 
 the optical spectrum of the high inclination
-Nova-like variable RW Tri. The densities near the disk plane in this model
+Nova-like variable RW Tri, both in and out of eclipse. The densities near the disk plane in this model
 are such that \civfull\ has a large collisionally excited component, in 
-contrast to observations.
+contrast to observations. {\bf ksl - I am not sure what the last sentence here means.  How do we know from observations that CIV is collisionally excited}.   Nevertheless, it seems 
+quite possible that models with a different parameterization of the wind will ultimately be able to reproduce the spectra of high state, non-magnetic CVs from the UV through the visible.
 % We find that 
@@
 Cataclysmic variables (CVs) are systems in which a white dwarf accretes matter from a donor
-star via Roche-lobe overflow. In non-magnetic, disk-dominated systems this accretion
+star via Roche-lobe overflow. In non-magnetic systems this accretion
 is mediated by an accretion disk which forms around the white dwarf. 
@@
 is in a permanent state of relatively high accretion rate 
-($\dot{M} \sim 10^{-8}$~M$_{\odot}$~yr$^{-1}$),
-making them the perfect laboratories to test the widely-used 
-`$\alpha$-disk' model proposed by 
-\cite{shakurasunyaev1973}.
+($\dot{M} \sim 10^{-8}$~M$_{\odot}$~yr$^{-1}$).  This makes nova-like variables the obviousl
+laboratory for studying the properties of steady-state accretion disks.
+%making them the perfect laboratories to test the widely-used`$\alpha$-disk' model proposed by \cite{shakurasunyaev1973}.
 
@@
 the most spectacular evidence being the P-Cygni like profiles of resonance lines such as 
-\civfull\ (see e.g. Cordova \& Mason 1982\nocite{cordova1982}).
-Despite this, in many types of systems the impact of winds on observational
-features is essentially unknown, and many theoretical questions relating to their origin 
-and driving mechanism remain unanswered.
-
-While the effect of the wind on the UV is at least partially clear, it may also have more subtle 
-effects across the spectral range. It has been proposed that an accretion disk wind
-can provide a mechanism for single-peaked emission lines (Murray \& Chiang 1996), 
-such as those seen in Nova-like variables and, especially, the SW Sex stars \citep{HSK86, DR95}.
+\civfull\ (see e.g. Cordova \& Mason 1982\nocite{cordova1982}).  As discussed below, it is now possible to produce synthetic spectra 
+of CVs with winds that are qualitatively very similar to those observed.  However, less is known about the 
+the effects of the wind on the optical spectra of high state CVs, which are characterized by a relatively featureless 
+continuum and  emission from the
+Balmer lines of H, which in many cases are single peaked, especially, the SW Sex stars \citep{HSK86, DR95}, unlike the double-peaked lines one might expect from a disk.
+Some work has been carried out.
+% Despite this, in many types of systems the impact of winds on observational features is essentially unknown, and many theoretical questions relating to their origin  and driving mechanism remain unanswered.
+Murray \& Chiang (1996) have argued that the single peaked emission lines arise due to radiative transfer effects in the wnd
+% While the effect of the wind on the UV is at least partially clear, it may also have more subtle  effects across the spectral range.
+It has been proposed that an accretion disk wind can provide a mechanism for single-peaked emission lines (Murray \& Chiang 1996),  such as those seen in Nova-like variables and, especially, the SW Sex stars \citep{HSK86, DR95}.
 It is particularly telling that single-peaked 
@@
 
-It has also been proposed
-that recombination continuum emission from a disk wind or `transition region'
-could be responsible for filling in the Balmer absorption edge  \citep{KLWB98}. 
-This provides a potential explanation for
-the absence of a pronounced `Balmer jump' in optical spectra of CVs, 
-which has never been adequately produced by using stellar atmospheres 
-to model the accretion disk (see e.g. Haug 1987)\nocite{haug1987}. 
-However, it is also possible that accretion disks do not possess
-and intrinsic deep Balmer absorption edges.
-This depends to the optical depth at the edge
-and can change due to decrease due to less temperature variation with height
-near the disk photosphere (see e.g. Shaviv et al. 1991; 
+The continuum spectra of high disk-dominated CVs is generally assumed to be
+dominated by emission from the diskand and is often modeled in terms of a set of stellar atmospheres
+and/or disk models ({bf reference some of Linnells papers here}), using Hubeny's TLUSTY code {\cite{})
+The optical continua observed from  high-state, disk-dominated CVs lack pronounced ``Balmer jumps'', 
+spectra simulated from summed atmospheres.   One possible explanation for this problem is that disk atmospheres calculated
+with TLUSTY simply do not represent the physics of disks properly ((see e.g. Shaviv et al. 1991; 
 but also more recent work by Idan et al. 2010).
-\nocite{idanshaviv2010} \nocite{shaviv1991}
+\nocite{idanshaviv2010} \nocite{shaviv1991}.   An altenative suggested by \cite{KLWB98} is that recombination continuum emission from a disk wind or `transition region'
+fills  in the Balmer absorption edge.
+
+%It has also been proposed that recombination continuum emission from a disk wind or `transition region'could be responsible for filling in the Balmer absorption edge  \citep{KLWB98}.
+This provides a potential explanation for the absence of a pronounced `Balmer jump' in optical spectra of CVs,  which has never been adequately produced by using stellar atmospheres to model the accretion disk (see e.g.
+Haug 1987)\nocite{haug1987}.
+However, it is also possible that accretion disks do not possessand intrinsic deep Balmer absorption edges.
+This depends to the optical depth at the edge and can change due to decrease due to less temperature variation with height  near the disk photosphere (see e.g.
+Shaviv et al.
+1991;  but also more recent work by Idan et al.
+2010).\nocite{idanshaviv2010} \nocite{shaviv1991}
 
@@
 We will also learn if the mechanism for single-peaked line emission
-proposed by \cite{MC96} works with plausible model parameters.
+identified by \cite{MC96} operates  in  parameterized wind models capable of reproducing 
+other spectral features of observed CVs.  The remainder of this report is organized as followd
 In section 2 we present the code and provide a brief description of macro-atoms 
-and the radiative transfer methods we employ. 
-We describe the kinematics and geometry of our biconical wind model in section 3.
-In section 4, we present a benchmark model, which is explored on in section 5 
-with a small-scale parameter search. In section 6, we present a
+and the radiative transfer methods we employ.  In section 3, 
+We describe the kinematics and geometry of our biconical wind model.
+In section 4, we present spectra simulated from the benchmark model employed by LK02, and in section 5, we carry out 
+aparameter search to determine how spectra change as a function of several of the parmeters in the model. In section 6, we present a
 model which better reproduces the optical spectrum of a NL, and, 
@@
 flying MC energy quanta (`photons') through a pre-defined wind geometry and recording
-the relevant estimators, before choosing  a new electron temperature 
-in an attempt to balance heating and cooling in the plasma.
-This process is repeated until the code converges on a 
-solution. Second, the spectrum is synthesized by tracking
+estimators that characterize the radiation field in each cell of the grid, before choosing  a new electron temperature 
+that more closely balances heating and cooling in the plasma. Using the new electron temperature and the radiative estimators, we then
+revise the ionization state of the wind.  
+This process is repeated  a converged
+solution is reached with heating and cooling balanced throughout the wind. Second, the spectrum over the desired spectral range is synthesized by tracking
 the energy packets through the wind and computing the 
@@
 
-The code is capable of operating in a number of different
+\py is designed to operate in a number of different
 regimes, both in terms of the scale of the system, and the 
@@
 % were also incorporated into the heating and cooling balance.
-In addition, Sim et al. (2005; hereafter SDL05)\nocite{simmacro2005} modeled
-Brackett and Pfund line profiles in young-stellar objects (YSOs) using \textsc{Python,} which included
-implementing a `macro-atom' mode in order to correctly treat recombination lines.
+In addition, Sim et al. (2005; hereafter SDL05)\nocite{simmacro2005} used the code to model
+Brackett and Pfund line profiles of H in young-stellar objects (YSOs) using \textsc{Python,} and as part of this effort 
+implemented a `macro-atom' mode  in order to correctly treat recombination lines of H.
 
@@
 Previously to SDL05, \py used a two-level atom approximation \cite[see e.g.][]{mihalas}. This approximation is 
-fast, and works well as a first approximation when treating so-called `resonance lines' (such as \civfull) 
+fast, and works well as a first approximation when treating  `resonance lines' (such as \civfull) 
 in which the excited electron is strongly coupled to the ground state.
@@
 technique to a Hydrogen-only model, we
-adopt a hybrid ionization and excitation scheme. 
-Species can be treated as either full macro-atoms
-or using the two-level atom approximation.
-In the latter case, they still follow the indivisible packet constraint.
-This allows one to preserve the fast treatment of resonance lines while providing 
+adopt a hybrid ionization and excitation scheme to model the spectra of CVs. 
+Atomic pecies can be treated as either full macro-atoms
+or using the two-level atom approximation.  This is  important in our multi-dimensional code to balance the need to calculate certain transitions in detail and the desire to minimize the set of
+computational resources required.  For CVs, this allows us 
+%In the latter case, they still follow the indivisible packet constraint.This allows one 
+to preserve the fast treatment of the UV resonance lines while providing 
 an improved representation of processes with more complex
-transition paths such as recombination. This is important when modeling features 
-such as the Balmer lines and also recombination {\sl continuum} emission.
+transition paths such as recombination, H and He. %This is important when modeling features  such as the Balmer lines and also recombination {\sl continuum} emission.
 
@@
 \subsection{Atomic Data}
-Here we use the same atomic data as LK02 and updated by H13.
-We have obtained the additional level and line information required to treat He as a macro-atom 
-from \textsc{Topbase} \citep{topbase2005}. We treat H as a 20-level atom as in SDL05, where 
+Here we use the atomic data described by LK02 and updated by H13. We treat H as a 20-level atom as in SDL05, where 
 each level is defined by the principal quantum number, $n$, which is appropriate due to
-the degeneracy of each level in the H atom. He~\textsc{II} is treated in much the same way,
-but with 10 levels. However, He~\textsc{I} has larger energy differentials between different l subshells
+the degeneracy of each level in the H atom. For the macro-atom treatment of He, 
+we have added additional level and line information required 
+from \textsc{Topbase} \citep{topbase2005}.  He~\textsc{II} is treated in much the same way as H,
+but with 10 levels. He~\textsc{I} has larger energy differentials between different l subshells
 and triplet and singlet states. Thus, we still include levels up to $n=10$ but explicitly 
@@
 
-\py has previously been tested against a number of radiative transfer and
+We have previously compared \py to results obtained with  a number of radiative transfer and
 photoionization codes. LK02 and H13 conducted comparisons of ionization balance 
@@
 \cite{kerzendorfsim}, and the spectral comparisons can be found therein.
-In addition to these code validation efforts, we have carried out tests of
-the macro atom scheme in \py to verify that it does indeed solve for level populations correctly
+For the effort reported here, we have carried out tests of
+the macro-atom scheme in \py to verify that it does indeed solve for level populations correctly
 and produces the expected level emissivities. Figure~\ref{tests} shows good agreement with 
@@
 
-Here we describe some of the features of our biconical wind model.
+\py allows for several types of biconical wind models and various options for calculating the spectra of the components of the system.
+Here we describe some of the features of the  biconical wind models used in this study of CVs.
 
@@
 the prescription outlined by Schlosman \& Vitello (1993; hereafter SV93). A schematic is shown
-in figure~\ref{cartoon}. A smooth, biconical
+in figure~\ref{cartoon}. In this parametrization, a smooth, biconical
 disk wind rises from the accretion disk between radii $r_{min}$ and $r_{max}$. The covering fraction of the wind is 
@@
 the acceleration exponent, $\alpha$.
+{\bf ksl - I am not sure this figure is necessary and do not see where it is discussed.
+In light of the fact that our final claims are stated in terms of densisty, it might be interesting to see this expressed as a density rather than a velocity.}
 }
@@
 by reprocessing of the indivisible energy packets originally produced in the disk or central WD.
+{\bf ksl -Isn't the wind also allow to emit?
+If so, I think saying the wind is dealt with by reporcessing is misleading.}
 
@@
 $T\propto r^{-3/4}$ temperature profile are required to fit the data
-in certain cases.
+in certain cases.  {\bf ksl - I thought Wade said that both black bodies and stellar atmospheres had trouble reproducing the color of disks.  Please check}
 
@@
 wind can fill in the Balmer jump, due to their intrinsic strong absorption beyond the Balmer edge.
+{\bf - ksl - This seems like a mistatement.
+If we used BB for the detailed spectra there would be no balmer jump problem.}
 For low temperatures, we use stellar atmospheres computed 
@@
 edge must lose angular momentum in order to be deposited on
-the surface of the compact object \cite[see e.g.][]{lyndenbell1974}.
+the surface of the WD \cite[see e.g.][]{lyndenbell1974}.
 Boundary layers are a source of
@@
 as a blackbody with a user-specified effective temperature and luminsoity.
-Boundary layer photons are then produced around the spherical surface of the 
+In \py, boundary layer photons are then produced around the spherical surface of the 
 white dwarf. In our benchmark model, we follow LK02 in setting the boundary layer
@@
 
-Our aim here is not
-to provide a `best fit' model to match any particular dataset.
-Rather, we take
-a successful UV wind model as a starting point
-and examine its effect 
-when one utilises the better treatment of lines provided
-by the macro-atom scheme.
+As a starting point for our discussion of the effects of a wind on the optical spectra of a CV, we 
+take the fiducial model for an SV wind used by LK02 to simulate the UV spectrum of a typical high-state system,
+%Our aim here is not to provide a `best fit' model to match any particular dataset. Rather, we takea successful UV wind model as a starting point
+and examine the effect of using the better treatment of lines provided
+by the macro-atom scheme for H and He.
 The model parameters are shown in table 1. 
-they are identical to LK02, and were chosen both to reflect typical
-values for NLs and reproduce realistic UV line profiles.
+%they are identical to LK02, and were chosen both to reflect typical
+%values for NLs and reproduce realistic UV line profiles.
 % The specific model 
@@
 Figure~\ref{spec} shows optical synthetic spectra for the benchmark 
-model for five different inclination angles ranging from $10^\circ$ to $80^\circ$ 
+model for five inclination angles ranging from $10^\circ$ to $80^\circ$ .
 %5 different sightlines.  
-The model produces some lines which are strong enough to overcome
-the absorption cores lines from the disk. These lines are generally double peaked, 
+The spectra have some lines of H and He which have emission components that are strong enough to overcome
+the absorption cores in the underlying disk spectra. These emission lines are generally double peaked, 
 as they are formed near the base of the wind where rotational velocity
@@
 opacity is not yet high enough for the poloidal velocity gradient to 
-cause single-peaked profiles. 
+cause single-peaked profiles.  {\bf ksl - So this last statement is based on information that has not yet been submitted as evidence. Be careful of the flow of the paper here.}
 We also see a general trend from absorption to emission in spectral lines
@@
 In addition to examining synthetic spectra, we are also able to 
-analyse the physical properties of the outflow.
+analyse the physical properties of the outflow. {\bf ksl - A better opening sentence is needed.  We don't really provide much interpretation of this.}
 Figure~\ref{wind} shows various physical properties
@@
 
-Clearly, this particular model cannot explain all
+Clearly, the fiducial model used by LK02 to simulate the UV spectra of CVs does not  explain all
 the features seen in the optical spectra of nova-like variables. However,
-the wind has a significant effect on the observed spectral features. 
-It cannot be ignored as a source of line and continuum emission and as a reprocessing `filter'
+the wind in this mdoel has a significant effect on features in the synthetic spectrum. 
+It suggests that the wind  cannot be ignored as a source of line and continuum emission and as a reprocessing `filter'
 of the underlying disk spectral energy distribution (SED).
@@
 of CVs,  
-would also leave a clear imprint on the optical spectrum. It is important
+would also leave a clear imprint on the optical spectrum. {\bf ksl - why are we introducing the terminology of Model A at this point}. It is important
 to understand how changing the kinematics of the wind impacts on this
-effect. A full parameter search is beyond the scope of this study, 
+effect.   
+A full parameter search is beyond the scope of this study, 
 but we can examine the evolution
-of the spectrum with a few key parameters. In particular, this
+of the spectrum with a few key parameters. {\bf - ksl - I don't actually like the previous sentence.  We should some how say we want to study a few parameters that we think with help,
+without saying that something is beyond the scope}  In particular, this
 will help shed light on the predictions of, e.g., Murray \& Chiang (1996)
@@
 A full kinematic parameter search may prove instructive, but
-is beyond the scope of this particular study.
+is beyond the scope of this particular study. {\bf - ksl - you said this once already, and I don't think it should be explicitly stated at all}
 We have therefore conducted a limited parameter 
@@
 the overall emission, although optical depth effects can cause 
-the relationship to become more complicated. In addition to these 
+the relationship to become more complicated. {\bf - ksl - sure looks like a strong argument to study clumping} In addition to these 
 kinematic parameters, we also investigate the effect of 
@@
 \civfull\ and \heiiuv\ lines (see section 5.3).
+{\bf ksl - Not clear here why we do this.
+It would be nice to state why.
+Note, we did not comment on He II in the fiducial model.
+Note also.
+If the whole idea is to increase density, a referee is likely to ask why we did not simply increase the mass loss rate of the wind.}
 
@@
 spectral lines very high densities are required.
+{\bf - ksl - As we discussed it would be nice if we could really understand what is required for Murray and Chang to work, and relate it more directly to our models}
 
@@
 
+{\bf - ksl - We probably should have explained much earlier that He II 1640 is a recombination line and 
+because of this was not modeled by LK02.  Generally, it's unclear why we are concerned about this.}
+
+As we have noted earlier, the spectra produced LK02, using a simple two level approximation did not contain the He II emission that is observed in high state CVs, since they were
+unable to model lines produced primarily through recombination.  Our improved treatment now allows us to comment on this.
+
 We find in all our models that He II line emission is significant, and that 
@@
 observed profiles.
+{\bf ksl - I do not think it follows that because the red wing is strong, that this is due to collisional effects.
+I think your wind is now effectively just more extended and this produce more scattered radiation.
+Scttering goes like n(C), emission goes like ne*n(C).
+It would be interesting if we could figure out a way to show graphically where emission and absorption in a wind model are coming from.}
 
@@
 because the high densities needed to increase line opacity also produce
-a significant collisionally excited contribution..
+a significant collissionally excited contribution..
 This is a shortcoming which must be understood if it is true that

### 2014-11-06 draft.tex
Some changes and added fig1_nl_spectra generation folder

@@
 is in a permanent state of relatively high accretion rate 
-($\dot{M} \sim 10^{-8}$~M$_{\odot}$~yr$^{-1}$).  This makes nova-like variables the obviousl
+($\dot{M} \sim 10^{-8}$~M$_{\odot}$~yr$^{-1}$).  This makes nova-like variables the obvious
 laboratory for studying the properties of steady-state accretion disks.
@@
 the most spectacular evidence being the P-Cygni like profiles of resonance lines such as 
-\civfull\ (see e.g. Cordova \& Mason 1982\nocite{cordova1982}).  As discussed below, it is now possible to produce synthetic spectra 
-of CVs with winds that are qualitatively very similar to those observed.  However, less is known about the 
-the effects of the wind on the optical spectra of high state CVs, which are characterized by a relatively featureless 
-continuum and  emission from the
+\civfull\ (see e.g. Cordova \& Mason 1982\nocite{cordova1982}).  
+As discussed below, it is now possible to produce synthetic spectra 
+of CVs with winds that are qualitatively very similar to those observed.  
+However, less is known about the the effects of the wind on the optical spectra of high state CVs, 
+which are characterized by a relatively featureless continuum and  emission from the
 Balmer lines of H, which in many cases are single peaked, especially, the SW Sex stars \citep{HSK86, DR95}, unlike the double-peaked lines one might expect from a disk.
@@
 % Despite this, in many types of systems the impact of winds on observational features is essentially unknown, and many theoretical questions relating to their origin  and driving mechanism remain unanswered.
-Murray \& Chiang (1996) have argued that the single peaked emission lines arise due to radiative transfer effects in the wnd
+Murray \& Chiang (1996) have argued that the single peaked emission lines arise 
+due to radiative transfer effects in the wind.
 % While the effect of the wind on the UV is at least partially clear, it may also have more subtle  effects across the spectral range.
@@
 The continuum spectra of high disk-dominated CVs is generally assumed to be
-dominated by emission from the diskand and is often modeled in terms of a set of stellar atmospheres
+dominated by emission from the disk and and is often modeled in terms of a set of stellar atmospheres
 and/or disk models ({bf reference some of Linnells papers here}), using Hubeny's TLUSTY code {\cite{})
@@
 spectra simulated from summed atmospheres.  One possible explanation for this problem is that disk atmospheres calculated
-with TLUSTY simply do not represent the physics of disks properly ((see e.g. Shaviv et al. 1991; 
-but also more recent work by Idan et al. 2010).
-\nocite{idanshaviv2010} \nocite{shaviv1991}.   An altenative suggested by \cite{KLWB98} is that recombination continuum emission from a disk wind or `transition region'
-fills  in the Balmer absorption edge.
+with TLUSTY simply do not represent the physics of disks properly 
+((see e.g. Shaviv et al. 1991; but also more recent work by Idan et al. 2010).
+\nocite{idanshaviv2010} \nocite{shaviv1991}.   
+An alternative suggested by \cite{KLWB98} is that recombination continuum emission 
+from a disk wind or `transition region' fills  in the Balmer absorption edge.
 
@@
 identified by \cite{MC96} operates  in  parameterized wind models capable of reproducing 
-other spectral features of observed CVs.  The remainder of this report is organized as followd
+other spectral features of observed CVs.  The remainder of this report is organized as follows.
 In section 2 we present the code and provide a brief description of macro-atoms 
 and the radiative transfer methods we employ.  In section 3, 
-We describe the kinematics and geometry of our biconical wind model.
+we describe the kinematics and geometry of our biconical wind model.
 In section 4, we present spectra simulated from the benchmark model employed by LK02, and in section 5, we carry out 
@@
 revise the ionization state of the wind.  
-This process is repeated  a converged
-solution is reached with heating and cooling balanced throughout the wind. Second, the spectrum over the desired spectral range is synthesized by tracking
+This process is repeated until a converged
+solution is reached with heating and cooling balanced throughout the wind. 
+Second, the spectrum over the desired spectral range is synthesized by tracking
 the energy packets through the wind and computing the 
@@
 It was originally developed by LK02 in order to model the UV spectra
-of CVs with a simple biconical disk wind model.. 
+of CVs with a simple biconical disk wind model.
 Higginbottom et al.\nocite{higginbottom2013} (2013; hereafter H13) used the same code to
@@
 adopt a hybrid ionization and excitation scheme to model the spectra of CVs. 
-Atomic pecies can be treated as either full macro-atoms
+Atomic species can be treated as either full macro-atoms
 or using the two-level atom approximation.  This is  important in our multi-dimensional code to balance the need to calculate certain transitions in detail and the desire to minimize the set of
@@
 an improved representation of processes with more complex
-transition paths such as recombination, H and He. %This is important when modeling features  such as the Balmer lines and also recombination {\sl continuum} emission.
+transition paths such as recombination in H and He. 
+%This is important when modeling features  such as the Balmer lines and also recombination {\sl continuum} emission.
 
@@
 \py allows for several types of biconical wind models and various options for calculating the spectra of the components of the system.
-Here we describe some of the features of the  biconical wind models used in this study of CVs.
+Here we describe some of the features of the  biconical wind model used in this study of CVs.
 
@@
 by reprocessing of the indivisible energy packets originally produced in the disk or central WD. 
-{\bf ksl -Isn't the wind also allow to emit?
-If so, I think saying the wind is dealt with by reporcessing is misleading.}
+{\bf ksl -Isn't the wind also allow to emit?  If so, I think saying the wind is dealt with by reporcessing is misleading.
+jm - no- all energy packets are produced by the disk and central source, and thermal emission from 
+the wind would be produced by a r-packet to k-packet to r-packet path, possibly via activated macro-atoms.}
 
@@
 $T\propto r^{-3/4}$ temperature profile are required to fit the data
-in certain cases.  {\bf ksl - I thought Wade said that both black bodies and stellar atmospheres had trouble reproducing the color of disks.  Please check}
+in certain cases.
+{\bf ksl - I thought Wade said that both black bodies and stellar atmospheres had trouble reproducing the color of disks.
+Please check.
+jm- this is correct.
+it is still relevant but needs to be worded better,
+and this section needs to link with the earlier statements about e.g. Shaviv.}
 
@@
 \begin{tabular}{p{3cm}p{4cm}}
-Model A \\
+Benchmark Model \\
 \hline Free Parameters 	&	 Value \\ 
@@
 line emission is not always sufficient to overcome the absorption
-cores from the stellar atmosphere models. The model
+lines from the stellar atmosphere models. The model
 also produces a prominent \heiioptnew\ line at high inclinations,
@@
 The spectra have some lines of H and He which have emission components that are strong enough to overcome
-the absorption cores in the underlying disk spectra. These emission lines are generally double peaked, 
+the absorption lines in the underlying disk spectra. These emission lines are generally double peaked, 
 as they are formed near the base of the wind where rotational velocity
@@
 
-The benchmark model presented above shows that a wind with the properties
-of Model A, a model that successfully reproduces the observed UV spectral features
+The benchmark model presented above shows that a wind model
+ that successfully reproduces the observed UV spectral features
 of CVs,  
-would also leave a clear imprint on the optical spectrum. {\bf ksl - why are we introducing the terminology of Model A at this point}. It is important
+would also leave a clear imprint on the optical spectrum. 
+It is important
 to understand how changing the kinematics of the wind impacts on this
 effect.   
-A full parameter search is beyond the scope of this study, 
-but we can examine the evolution
-of the spectrum with a few key parameters. {\bf - ksl - I don't actually like the previous sentence.  We should some how say we want to study a few parameters that we think with help,
-without saying that something is beyond the scope}  In particular, this
+% {\bf - ksl - I don't actually like the previous sentence.  
+% We should some how say we want to study a few parameters that we think with help,
+% without saying that something is beyond the scope}  
+In particular, this
 will help shed light on the predictions of, e.g., Murray \& Chiang (1996)
@@
 
-A full kinematic parameter search may prove instructive, but
-is beyond the scope of this particular study. {\bf - ksl - you said this once already, and I don't think it should be explicitly stated at all}
-We have therefore conducted a limited parameter 
+% A full kinematic parameter search may prove instructive, but
+% is beyond the scope of this particular study. {\bf - ksl - you said this once already, and I don't think it should be explicitly stated at all}
+We have conducted a limited parameter 
 search, where we focus on 
@@
 \begin{tabular}{p{3cm}p{4cm}}
-Model B \\
+Improved Optical Model \\
 \hline Free Parameters 	&	 Value \\ 
@@
 that comes closer to reproducing the observed optical spectrum
-of a NLs. The parameters for this model (imaginatively dubbed Model B)
+of a NLs. The parameters for this model
 are show in table~\ref{modelb}, and the synthetic spectrum
@@
 The similarity with the observed spectrum is striking. 
-Model B produces strong emission in all the Balmer lines, 
+The improved optical model produces strong emission in all the Balmer lines, 
 with line to continuum ratios
@@
 inclination NL RW Tri. {\sl Bottom Panel:} In and out of eclipse synthetic
-spectra from Model B.
+spectra from the improved optical model.
 The artificial `absorption' feature just redward of the Balmer jump

### 2014-11-06 generate/fig1_nl_spectra/eclipse_compare.py

@@ -1,0 +1,204 @@
+from constants import *
+import numpy as np
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import read_output as rd
+rd.setpars()
+
+def gauss(sigma, x0, x):
+
+	term = 1.0 / (2.0*np.pi) / sigma
+
+	exp_term = ( (x - x0)**2 )  /  (2.0*sigma*sigma)
+
+	term *= np.exp(-exp_term)
+
+	return term
+
+# def convolve(FWHM, x, y, mode="gaussian"):
+
+# 	'''
+# 	convolve arrays
+# 	'''
+
+# 	sigma = FWHM / (np.sqrt(8.0*np.log(2.0)))
+
+# 	n_points = len(x)
+
+# 	for i in range(n_points):
+
+def get_linelist(filenames, ionreturn=False):
+
+	lines = np.array([])
+	z = np.array([])
+
+	for i in range(len(filenames)):
+
+		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
+
+		lines = np.concatenate((lines, x[1]))
+
+		z = np.concatenate((z, x[0]))
+
+	if ionreturn:
+		return lines, z
+	else:
+		return lines
+
+
+
+
+
+
+
+# some fontsizes for figure
+font1 = 16				# fontsize for x label
+font2 = 16				# fontsize for Y label
+font3 = 16				# fontsize for text on figures
+weight = 1.5
+
+
+
+# standard plot parameters for mnras
+fig_width_pt=120.0 #Figure parameters
+inches_per_pt=1.0/72.27
+golden_mean=(math.sqrt(5)-1.0)/2.0
+fig_width=fig_width_pt*inches_per_pt
+fig_height=fig_width*golden_mean
+fig_size=(fig_width*8, fig_height*8)
+params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
+plt.rcParams.update(params)
+matplotlib.rcParams['ps.useafm'] = True
+matplotlib.rcParams['pdf.use14corefonts'] = True
+matplotlib.rcParams['text.usetex'] = True
+
+
+figure(figsize=fig_size)
[…]

### 2014-11-06 generate/fig1_nl_spectra/plot2.py

@@ -1,0 +1,204 @@
+from constants import *
+import numpy as np
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import read_output as rd
+rd.setpars()
+
+def gauss(sigma, x0, x):
+
+	term = 1.0 / (2.0*np.pi) / sigma
+
+	exp_term = ( (x - x0)**2 )  /  (2.0*sigma*sigma)
+
+	term *= np.exp(-exp_term)
+
+	return term
+
+# def convolve(FWHM, x, y, mode="gaussian"):
+
+# 	'''
+# 	convolve arrays
+# 	'''
+
+# 	sigma = FWHM / (np.sqrt(8.0*np.log(2.0)))
+
+# 	n_points = len(x)
+
+# 	for i in range(n_points):
+
+def get_linelist(filenames, ionreturn=False):
+
+	lines = np.array([])
+	z = np.array([])
+
+	for i in range(len(filenames)):
+
+		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
+
+		lines = np.concatenate((lines, x[1]))
+
+		z = np.concatenate((z, x[0]))
+
+	if ionreturn:
+		return lines, z
+	else:
+		return lines
+
+
+
+
+
+
+
+# some fontsizes for figure
+font1 = 16				# fontsize for x label
+font2 = 16				# fontsize for Y label
+font3 = 16				# fontsize for text on figures
+weight = 1.5
+
+
+
+# standard plot parameters for mnras
+fig_width_pt=120.0 #Figure parameters
+inches_per_pt=1.0/72.27
+golden_mean=(math.sqrt(5)-1.0)/2.0
+fig_width=fig_width_pt*inches_per_pt
+fig_height=fig_width*golden_mean
+fig_size=(fig_width*8, fig_height*8)
+params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
+plt.rcParams.update(params)
+matplotlib.rcParams['ps.useafm'] = True
+matplotlib.rcParams['pdf.use14corefonts'] = True
+matplotlib.rcParams['text.usetex'] = True
+
+
+figure(figsize=fig_size)
[…]

### 2014-11-06 generate/fig1_nl_spectra/plot_nl_figure.py

@@ -1,0 +1,172 @@
+'''
+plot_nl_figure.py 
+
+This script creates the figure for the Nova like spectra
+in the 2014 CV paper. The data were scraped from Dexter.
+'''
+
+
+from constants import *
+import numpy as np
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import read_output as rd
+rd.setpars()
+
+# some fontsizes for figure
+font1 = 16				# fontsize for x label
+font2 = 12				# fontsize for Y label
+font3 = 16				# fontsize for text on figures
+weight = 2			# lineweight
+
+
+
+# standard plot parameters for mnras
+fig_width_pt=120.0 #Figure parameters
+inches_per_pt=1.0/72.27
+golden_mean=(math.sqrt(5)-1.0)/2.0
+fig_width=fig_width_pt*inches_per_pt
+fig_height=fig_width*golden_mean
+fig_size=(fig_width*8, fig_height*8)
+params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
+plt.rcParams.update(params)
+matplotlib.rcParams['ps.useafm'] = True
+matplotlib.rcParams['pdf.use14corefonts'] = True
+matplotlib.rcParams['text.usetex'] = True
+
+
+figure(figsize=fig_size)
+colour = "k"
+
+# read the RW Sex data
+x1,y1 = np.loadtxt("rwsex/data11.dat", unpack=True, comments="#", usecols=(0,1))
+
+# read the IX Vel daata
+x, y = np.loadtxt("ixvel/data2.dat", unpack=True, comments="#", usecols=(0,1))
+a,b = np.loadtxt("ixvel/data.dat", unpack=True, comments="#", usecols=(0,1))
+
+# read the RW Tri data 
+cc,dd = np.loadtxt("rwtri/new_eclipse.dat", unpack=True, comments="#", usecols=(0,1))
+cc_no, dd_no = np.loadtxt("rwtri/rwtri_opt_noeclipse.dat", unpack=True, comments="#", usecols=(0,1))
+
+
+
+
+
+
[…]

### 2014-12-01 draft_ck1.tex
another CK edit

%%%% Various options for document class.
%\documentclass[usenatbib, a4paper]{preprint}
\documentclass[preprint, a4paper, 11pt]{aastex}
%%\documentclass[twocolum]{revtex4}
%%\documentclass{report}
%%\documentclass[useAMS,usenatbib, onecolumn]{mn2ejm}

%\usepackage{psfig,morefloats,url}
%use preprint2 for 2 columns paper.

%% declare any packages used
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{color} 
\usepackage{pdfpages}
\usepackage{appendix}
\usepackage{subfigure}
%\usepackage{epsfig}
%\usepackage[dvips]{color}
%\usepackage{aabib}

%\marginparwidth = 25pt
\citestyle{aa}
\addtolength{\topmargin}{-.5in}
%% This command added as margins are wrong in mn2e, it appears. 
%% Not needed for other classes

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%% define bibstyle and other definitions
\bibliographystyle{aabib}
%% renew commands
\renewcommand{\labelitemi}{$\bullet$}
\def\py{\textsc{Python} }
\def\tar{\textsc{Tardis} }
\def\cld{\textsc{Cloudy} }
\def\civ{C~\textsc{iv} }
\def\araa{ARAA}
\def\nat{Nature}
\def\apjl{ApJ Letters}
\def\aapr{AAPR}
\def\actaa{ACTAA} 
\def\ssr{SSR}
\def\apj{ApJ}
\def\apss{AP\&SS}
\def\pasp{PASP}
\def\aap{A\&A}
\def\mnras{MNRAS}
\def\aj{AJ}
\def\rmxaa{RMXAA}

%% define some control sequences for lines
\def\heiiopt{He~\textsc{ii}~$\lambda4686{\rm \AA}$}
\def\heiiuv{He~\textsc{ii}~$\lambda1640{\rm \AA}$}
\def\heiioptnew{He~\textsc{ii}~$\lambda3202{\rm \AA}$}
\def\la{Ly-$\alpha$}
\def\ha{H$\alpha$}
\def\hb{H$\beta$}
\def\civfull{C~\textsc{iv}~$\lambda1550{\rm \AA}$}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          TITLE AND AUTHORS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables}
\author{J. H. Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          ABSTRACT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
Many high-state non-magnetic cataclysmic variables (CVs) exhibit
blue-shifted absorption or P-Cygni profiles in ultraviolet
(UV) resonance lines, such as C~{\sc iv}~1550\AA. These features
imply the existence of powerful accretion disk winds in
CVs, and considerable effort has gone into modelling UV line formation
in such outflows. By contrast, much less attention has been paid to
the potential impact of these disk winds on the {\em optical} spectra
of CVs. Here, we use an improved version of our Monte Carlo ionization
and radiative transfer code to investigate whether disk wind models that
produce realistic UV line profiles are also likely to generate
observationally significant recombination line and continuum emission
in the optical waveband. In particular, we test whether outflows may 
be responsible for the single-peaked emission line profiles often seen
in high-state CVs and for the weakness of the Balmer absorption edge
(relative to simple models of optically thick accretion disks).
We find that a standard disk wind model that is successful in
reproducing the UV spectra of CVs does leave a noticeable imprint on
the optical spectrum as well, particularly for systems viewed at high
inclination. The strongest optical wind-formed recombinations lines are \ha\ and
\heiiopt\ , although the outflow also produces emission in the Ly-$\alpha$
and \heiiuv\ UV lines. However, all of the optical lines produced by
this default wind model are double-peaked, and the effect of the wind
on the Balmer jump is modest. We carry out a limited exploration of
the disk wind parameter space, focusing on those parameters that affect the
density near the base of the wind. This shows that higher-density
outflows can produce both single-peaked emission lines and a
recombination continuum sufficient to fill in the Balmer
jump, although such models also tend to predict stronger-than-observed 
collisionally excited UV emission lines. Our main conclusion is that
disk wind emission is likely to have a significant impact on the
optical spectra of high-state CVs. 
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          INTRODUCTION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction} 
\label{sec:intro}

Cataclysmic variables (CVs) are systems in which a white dwarf
accretes matter from a donor star via Roche-lobe overflow. In
non-magnetic systems this accretion is mediated by a Keplerian disk
around the white dwarf (WD). Nova-like variables (NLs) are a subclass
of CVs in which the accretion disk is always in a relatively
high accretion rate state ($\dot{M} \sim
10^{-8}$~M$_{\odot}$~yr$^{-1}$).  This makes NLs an excellent
laboratory for studying the properties of steady-state accretion
disks.

It has been known for a long time that winds emanating from the
accretion disk are important in shaping the ultraviolet (UV) spectra
of high-state CVs (Heap 1978). The most spectacular evidence for such
outflows are the P-Cygni-like profiles seen in UV resonance lines such as
\civfull\ (see e.g. Cordova \& Mason
1982\nocite{cordova1982}). Considerable effort has been spent over the
years on understanding and modelling these UV features (e.g. Drew \&
Verbunt 1985; Mauche \& Raymond
1987; Drew 1987; Shlosman \& Vitello 1993; [hereafter
SV93]\nocite{SV93}; Knigge, Woods \& Drew 1995 [hereafter
KWD95]\nocite{KWD95}; Knigge \& Drew 1997; Knigge et al. 1997; Long \&
Knigge 2002 [hereafter LK02]\nocite{LK02}, Noebauer et al. 2010;
Puebla et al. 2011). The basic picture emerging from these efforts is
of a slowly accelerating, moderately collimated bipolar
outflow that carries away $\simeq 1\% - 10\%$ of the accreting
material. State-of-art-simulations of line formation in this type
of disk wind can produce UV line profiles that are remarkably similar
to observations.

Much less is known about the effect of these outflows on the optical
spectra of high-state CVs. These spectra are typically characterized
by H and He emissions superposed on a blue continuum. In many
cases, and particularly in the SW~Sex subclass of NLs
\citep{HSK86,DR95}, these lines are single-peaked. This is contrary to
theoretical expectations for lines formed in accretion disks, which
are predicted to be double-peaked (REF to Smak and Marsh \&
Horne). {\em Low-state} CVs (dwarf novae in quiescence) do, in fact,
exhibit such double-peaked lines (REF).

Murray \& Chiang (1996) have shown that the presence of disk winds may
offer a natural explanation for the single-peaked optical emission lines in
high-state CVs, since they can strongly affect the radiative transfer
of line photons. Strong support for a significant wind contribution to the
optical emission lines comes from observations of eclipsing
systems. There, the single-peaked lines are often only weakly
eclipsed, and a significant fraction of the line flux remains visible
even near mid-eclipse (REF). This points to line formation in a spatially
extended region, such as a disk wind (see figure~\ref{novalikes}).
%%(Honeycutt, Schlegel, \& Kaitchuck 1986; Dhillon \& Rutten 1995). 
Further evidence for a wind contribution to the optical lines comes
from isolated observations of P-Cygni-like line profiles even in optical
lines, such as \ha\ and He \textsc{i} $\lambda5876$ \citep{RN98}.

Could disk winds also have an impact on the UV/optical {\em continuum}
of high-state CVs? This continuum is usually thought to be dominated
by the accretion disk and modelled by splitting the disk into
a set of concentric, optically thick, non-interacting annuli following
the standard $T_{eff}(R) \propto R^{-3/4}$ radial temperature
distribution (Shakura \& Sunyaev REF). In such
models, each annulus is taken to emit either as a blackbody or,
perhaps more realistically, as a stellar/disk atmosphere model
(REF). In the latter case, the local surface gravity, $\log{g}(R)$, is
assumed to be set solely by the accreting WD, since self-gravity is
negligible in CV disks.

Attempts to fit the observed spectral energy distributions (SEDs) of
high-state CVs with such models have met with mixed success. In
particular, the SEDs predicted by most stellar/disk atmosphere models 
are too blue in the UV (REFs) and exhibit
stronger-than-observed Balmer jumps in absorption (REFs). One possible
explanation for these problems is that these models fail to capture
all of the relevant physics. Indeed, it has been argued that a
self-consistent treatment can 
produce better agreement with observational data (e.g. Shaviv et
al. 1991;  but also more recent work by Idan et al. 2010). 
\nocite{idanshaviv2010} \nocite{shaviv1991}. However, an alternative 
explanation, suggested by \cite{KLWB98}, is that recombination continuum
emission from the base of the disk wind might fill in the disk's
Balmer absorption edge and flatten the UV spectrum.

\begin{figure}	%fullpage
\centering
\includegraphics[width=0.8\textwidth]{figures/fig1.eps}
\caption{Optical spectra of three nova-like variables: 
RW Sex (Top; Beuermann et al. 1992),
IX Vel (Middle; Beuermann \& Thomas 1990)
and RW Tri in eclipse (Bottom; Groot et al. 2004).
The data have been digitized from the respective publications and a few of the more
prominent emission and absorption lines are marked. 
These systems have inclinations of $30^\circ$, $60^\circ$ and $70^\circ$ 
respectively.
The trend of increasing Balmer line emission with inclination can be seen.
In RW Tri strong single-peaked emission in the Balmer lines is seen even
in eclipse, indicating that the lines may be formed in a spatially
extensive disk wind, and there is even a suggestion 
of a (potentially wind-formed) recombination continuum in the eclipsed
spectrum.}
\label{novalikes}
\end{figure}

Here, we carry out Monte Carlo radiative transfer simulations in
order to assess the likely impact of accretion disk winds on the
optical spectra of high-state CVs. More specifically, our goal is to
test whether disk winds of the type developed to account for the UV
resonance lines would also naturally produce significant amounts of  
optical line and/or continuum emission. In order to achieve this, we
have implemented the `macro-atom' approach developed by Lucy
(2002, 2003) into the Monte Carlo ionization and radiative transfer
code described by LK02 (a process initiated by SDL05). With this
upgrade, the code is able to deal correctly with processes involving
excited levels, such as the recombination emission produced by CV
winds.

The remainder of this paper is organized as follows. In Section~2 we
briefly describe the code and and the newly implemented macro-atom
approach. In Section~3, we describe the kinematics and geometry of our
disk wind model. 
In Section~4, we present spectra simulated from the benchmark model
employed by LK02, and in Section~5, we carry out a limited sensitivity
study to explore how the predicted spectra change as a function of
some key parameters in our model. In Section~6, we summarize our
findings.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          THE CODE, RADIATIVE TRANSFER
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{{\sc python}: A Monte Carlo Ionization and Radiative Transfer Code}

\py is a Monte Carlo (MC) ionization and radiative transfer code which
uses the Sobolev approximation to treat line transfer. It has already
been described extensively in LK02, SDL05 and H13, so here we provide
only a brief summary of its operation, focusing particularly on new
aspects of our implementation of macro-atoms into the code.

\subsection{Basics}

\py operates in two distinct stages. First, the ionization state,
level populations and temperature structure are calculated. This is
done iteratively, by 
propagating several populations of MC energy quanta (`photons')
through a model wind. The geometric and kinemetic properties of the
outflow are specified on a pre-defined spatial grid. In each of these
iterations (``ionization cycles''), the code records estimators that 
characterize the radiation field in each grid cell. At the end 
of each ionization cycles, a new electron temperature is calculated
that more closely balances heating and cooling in the 
plasma. The radiative estimators and updated electron
temperature are then used to revise the ionization state of the wind,
and a new ionization cycle is started. The process is repeated until
heating and cooling are balanced throughout the wind.

This converged model is used as the basis for the second set of
iterations (``spectral cycles''). In these, the emergent spectrum over
the desired spectral range is synthesized by tracking populations of
energy packets through the wind and computing the emergent spectra at
a number of user-specified viewing angles.

\py is designed to operate in a number of different
regimes, both in terms of the scale of the system, and in terms of the
characteristics of the underlying radiation field.
It was originally developed by LK02 in order to model the UV spectra
of CVs with a simple biconical disk wind model. Sim et al. (2005;
hereafter SDL05)\nocite{simmacro2005} used the code to model Brackett
and Pfund line profiles of H in young-stellar objects (YSOs). As part
of this effort, they implemented a `macro-atom' mode (see below) in
order to correctly treat hydrogen recombination lines with
\py. Finally, Higginbottom et al.\nocite{higginbottom2013} (2013;
hereafter H13) used \py to model broad absorption line (BAL) QSOs. For
this application, an improved treatment of ionization was implemented,
so that the code is now capable of dealing with arbritrary
photo-ionizing SEDs, including non-thermal and multi-component ones.

\subsection{Ionization and Excitation: ``Simple Atoms''}

Prior to SDL05, the relative ionization fractions for all atomic
species were estimated via the modified Saha equation (Mazzali \&
Lucy 1993)  
\begin{equation}
\frac{n_{j+1} n_e}{n_j} = W [\xi + W(1-\xi)]
\left(\frac{T_e}{T_R}\right)^{1/2}
\left(\frac{n_{j+1}n_e}{n_j}\right)^*_{T_R}, \label{ionization}
\end{equation}
Here, the `starred' term on the right represents Saha
abundances computed at temperature $T_R$, but
using actual partition functions obtained 
from the dilute blackbody approximation.
This is in accordance with the notation of Mihalas (1982).  
%%JMTASK: in accordance with the notation of Mihalas (1982).  - check this!
$W$ is an effective dilution factor, $\xi$ is the
fraction of recombinations going directly to the ground state, and
$T_R$ and $T_e$ are the radiation and electron temperature
respectively. This simple ionization scheme produces reasonable
results when the photoionizing SED can be approximated by a dilute
blackbody. This is the case for high-state CVs. (As noted above, an
improved, but more complex treatment of ionization that is appropriate
for more complex SEDs is described in H13.)

Similarly, the relative excitation fractions within each ionization
stage of a given species were estimated via a modified Boltzmann
equation,
\begin{equation}
\frac{n_{jk}}{n_j} = W g_k \exp{-E_k/kT_R} / z_j(T_R),
\end{equation}
where $n_{jk}$ is the population of level $k$ in ionic stage $j$,
$E_k$ is the energy difference between level $k$ and the ground state,
and $z_j(T_R)$ is the partition function of ionic stage $j$.

Finally, \py modelled all bound-bound processes as transitions
within a simple two-level atom \cite[see e.g.][]{mihalas}. This
approach works reasonable well for resonance  
lines, such as \civfull, in which the lower level is the ground state.  
However, it is a poor approximation for many other
transitions, particularly those where the upper level is 
is primarily populated from above. Thus an improved method for
estimating excited level populations and simulating line transfer is
needed in order to model recombination lines and continua.

\subsection{Ionization and Excitation: Macro-Atoms}

Lucy (2002, 2003\nocite{lucy2002, lucy2003}; hereafter L02, L03) 
has shown that it is possible to calculate the emissivity of a gas in
statistical equilibrium accurately by quantising matter into
`macro-atoms', and radiant and kinetic energy into indivisible energy
packets (r- and k- packets, respectively). His macro-atom scheme
allows for all possible transition paths from a given level and
provides a full non-local thermodynamic equilibrium (NLTE) solution
for the level populations based on MC estimators. The macro-atom
technique has already been used to model Wolf-Rayet star
winds \citep{sim2004}, AGN disk winds \citep{simlong2008, tatum2012},
supernovae \citep{kasen2006, kerzendorfsim} and YSOs (SDL05). A full 
description of the scheme can be found in L02 and L03.

Briefly, macro-atom NLTE level populations and ionization fractions
are calculated by solving the statistical equilbrium equations between
each pair of levels. For example, the bound-bound de-excitation rate,
${\cal R}_{ul}$, in an ion is given by  
\begin{equation}
{\cal R}_{ul} = \beta_{lu} A_{ul} n_u + \beta_{lu} B_{ul} n_u J_{lu} +
C_{ul} n_u n_e,\label{eq:nlte_rul},
\end{equation}
where $u$ and $l$ denote the upper and lower levels, $C$ represents the
collisional rate coefficients and $A$ and $B$ represent the Einstein
coefficients. The quantity $\beta_{lu}$ is the probability that a
given line photon will escape the Sobolev region. Finally, $J$ is the
MC estimator for the mean intensity in the line, as recorded during
the photon propagation. The corresponding excitation rate is then 
\begin{equation}
{\cal R}_{lu} = \beta_{lu} B_{lu} n_l J_{lu} + C_{lu} n_l n_e,
\end{equation}
where we implicitly include a correction for stimulated emission in
our definition of the estimate for $J_{ul}$.

In our implementation of the macro-atom approach, we also explicitly
take into account the photoionization and collisional ionization rates
between a lower level, $l$, and the continuum (or, in the case of ions
with more than one bound electron, the ground state of the upper ion),
$\kappa$,
\begin{equation}
{\cal R}_{l \kappa}= n_l \int_{\nu_0}^{\infty} \frac{ 4 \pi J_{\nu}
  \sigma_{\nu}}{h \nu} d\nu + C_{l \kappa} n_l n_e.
\end{equation}

Here, $\sigma_{\nu}$ is the photoionization cross section, and $J_{\nu}$
is the mean intensity. The corresponding recombination rate is given
by 
\begin{equation}
{\cal R}_{\kappa l} = \alpha_{\kappa l} n_{\kappa} n_e + C_{\kappa l}
n_\kappa n_e, \\
\end{equation}
where $\alpha_{\kappa l}$ is the radiative recombination coefficient
to level $l$. This treatment means that radiative and collisional
rates to and from all levels are considered when calculating both the
ionization state and the level populations, although we neglect 
ionization directly to excited levels of the upper ion. The
\cite{vanregemorter} approximation is used for collisional
transitions, and thus we assume that collisions between radiatively
forbidden transitions are not important in determining level
populations. This is a reasonable approximation in the regimes
considered here.

\subsection{Ionization and Excitation: A Hybrid Approach}

SDL05 implemented a macro-atom treatment of Hydrogen in \py and used
this to predict the observable properties of a pure Hydrogen wind
model for YSOs. Our goal here is to simultaneously model the optical
and ultraviolet spectra of high-state CVs. Since the optical spectra
are dominated by H and He recombination lines, both of these species
need to be treated as macro-atoms. The UV spectra, on the other hand,
are dominated by resonance lines associated with metals. This means we
need to include these species in our models, but they can be treated 
with our (much faster) simple-atom approach. We have therefore
implemented a hybrid ionization and excitation scheme into \py. Any
atomic species can now be treated either in our simple-atom
approximation or with the full macro-atom machinery. For our CV
models, we treat H and He as macro-atoms and all metals as
simple-atoms.

\subsection{Atomic Data}

We generally use the same atomic data as H13, which is an updated
version of that described in LK02. In addition, we follow SDL05 in
treating Hydrogen as a 20-level atom, where each level is defined by
the principal quantum number, $n$. For the macro-atom treatment of
Helium,  we have added additional level and line information required 
from \textsc{Topbase} \citep{topbase2005}.  He~\textsc{II} is treated
in much the same way as H, but with 10 levels. He~\textsc{I} has
larger energy differentials between different l-subshells and triplet
and singlet states. Thus, we still include levels up to $n=10$ but
explicitly treat the $l$ and $s$ sub-orbitals as distinct levels
instead of assuming they are perfectly `l-mixed'. This allows us
to model the singlet and  triplet He~{\sc i} lines that are ubiquitous
in the optical spectra of CVs \citep[e.g.][]{dhillon1996}.

\subsection{Code Validation and Testing}

\py has been tested against a number of radiative transfer and
photoionization codes. LK02 and H13 conducted comparisons of 
ionization balance  with \cld \citep{cloudy2013}, demonstrating
excellent agreement. We have also carried out comparisons
of ionization and spectral synthesis with the supernova code
\textsc{Tardis.} \tar is described by 
\cite{kerzendorfsim}, and the spectral comparisons can be found
therein. For the effort reported here, we have additionally carried
out tests of the macro-atom scheme in \py. Figure~\ref{tests} shows
two of these tests. In the top panel, we compare the Balmer series 
emissivities as predicted by \py in the l-mixed Case~B limit against the
analytical calculations by \cite{seaton1959}. In the bottom panel, we
compare \py and \tar predictions of  He \textsc{i} level populations
for a particular test case. Agreement is excellent for both H and He.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/fig_caseb_tardis.eps}
\caption{
{\sl Top Panel:} Balmer decrements calculated with \py compared with analytic calculations
by Seaton (1959), showing good agreement when calculating level emissivities in Hydrogen
in the Case B limit.
(see Osterbrock 1989 for a discussion of this commonly used approximation).
{\sl Bottom Panel:}  a comparison of Helium I level populations (the most complex ion we currently 
treat as a macro-atom) between \py~and \tar~models. Considering the 
two codes use different atomic data and \textsc{Tardis,} unlike \textsc{Python,} currently has 
a complete treatment of collisions between radiatively forbidden transitions, the factor of 
$<2$ agreement is encouraging. 
{\bf CK: WHAT ARE THE PARTICULAR SETS OF PARAMETERS BEING ADOPTED HERE?}
}
\label{tests}
\end{figure}
\nocite{osterbrock}
\nocite{seaton1959}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          THE MODEL
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Describing the System and its Outflow}

\py includes several different kinematic models of accretion disk
winds, as well as different options for describing the physical and
radiative properties of the wind-driving system under
consideration. Most of these features have already been discussed in
LK02 and H13, so below we only briefly recount the key aspects of the
particular system and wind model used in the present study.

\subsection{Wind Geometry and Kinematics}

We adopt the kinematic disk wind model developed by Schlosman \&
Vitello (1993; hereafter SV93). A schematic of this model is shown in
figure~\ref{cartoon}. In this parametrization, a smooth, biconical
disk wind emanates from the accretion disk between radii $r_{min}$ and 
$r_{max}$. The covering fraction of the outflow is also controlled by the
inner and outer opening angles of the wind, $\theta_{min}$ and
$\theta_{max}$, and the launch angle of the other streamlines is given
by 
\begin{equation}
\theta(r_0) = \theta_{min} + (\theta_{max} - \theta_{min}) \left(\frac{r_0 - r_{min}}{r_{max} - r_{min}} \right)^{\gamma},
\label{theta}
\end{equation}
where $r_0$ is the launch radius of the streamline.

The poloidal (non-rotational) velocity field of the wind, $v_l$, is given by
\begin{equation}
v_l=v_0+\left[v_{\infty}(r_0)-v_0\right]\frac{\left(l/R_v\right)^{\alpha}}{\left(l/R_v\right)^{\alpha}+1},
\label{v_law}
\end{equation}
where $l$ is the poloidal distance along a particular wind
streamline. The terminal velocity along a streamline, $v_{\infty}$, is
set to a fixed multiple of the escape velocity at the launch
point. The launch velocity from the disk surface, $v_0$, is assumed to
be constant (set to $6$~km~s$^{-1}$). Once the wind is launched, it
accelerates, reaching half of its terminal velocity at $l = R_v$. The
velocity law exponent $\alpha$ controls how quickly the wind
accelerates. Larger values of $\alpha$ cause the main region of 
acceleration to occur close to $R_v$, whereas smaller values
correspond to fast acceleration close to the disk (see
figure~\ref{acc_law}).

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/fig2_cartoon.eps}
\caption{Cartoon illustrating the geometry and kinematics of the benchmark CV wind model.}
\label{cartoon}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/acc_law.eps}
\caption{
The adopted poloidal velocity law for various values of the
acceleration exponent, $\alpha$.
}
\label{acc_law}
\end{figure}

The density at position $(r,z)$ in the wind, $\rho(r,z)$, is
calculated from the mass continuity equation, yielding
\begin{equation}
\rho(r,z) = \frac{r}{r_0} \frac{dr}{dr_0} \frac{\phi(r_0)}{v_z(r,z)}.
\label{density}
\end{equation}
Here, $\phi(r_O)$ is the mass-loss rate per unit area at $r_0$, 
and $v_z$ is the vertical velocity component. We take $\phi(r_0)$ to be
uniform across the wind-launching area of the disk and normalize it by
matching its integral to the user-specified total mass-loss rate,
$\dot{M}_{wind}$. 
{\bf I'm still not sure I understand the formula
  SV93 use to define $\phi$, and hence that this description is
  actually strictly correct.... Not sure what to do about that
  though...}

\subsection{Sources and Sinks of Radiation}

The net photon sources in our CV model are the accretion disk, the
WD and, in principle, a boundary layer with user-defined temperature
and luminosity. All of these radiating bodies are taken to be
optically thick, and photons striking them are assumed to be destroyed
instantaneously. The secondary star is not included as a radiation
source, but is included as an occulting body. This allows us to model
eclipses. Finally, emission from the wind itself is also accounted for, but
note that we assume the outflow to be in radiative equilibrium. Thus all
of the heating of the wind, as well as its emission, is ultimately
powered by the radiation field of the net photon sources in the
simulation. In the following sections, we will describe our treatment
of these system components in slightly more detail.

\subsubsection{The Accretion Disk}

\py has has some flexibility when treating the accretion 
disk as a source of photons. The disk is broken down into annuli 
such that each annulus contributes an equal amount to the bolometric
luminosity. We take the disk to be geometrically thin, but optically
thick and thus adopt the temperature profile of a standard
\cite{shakurasunyaev1973} $\alpha$-disk. An annulus can then
be treated either as a blackbody with the corresponding effective
temperature or as a stellar atmosphere model with the appropriate
surface gravity and effective temperature. Here, we use blackbodies 
during the ionization cycles and to compute our MC
estimators. However, during the spectral synthesis stage of the 
simulation we use stellar atmosphere models. This produces more
realistic model spectra and allows us to test if recombination
emission from the wind base can fill in the Balmer jump, which is
always in absorption in these models. Our synthetic stellar atmosphere
spectra are calculated with
\textsc{Synspec}\footnote{http://nova.astro.umd.edu/Synspec43/synspec.html}
from either Kurucz \citep{kurucz1991} atmospheres (for $T_{eff} \leq
50,000$~K) or from \textsc{TLUSTY} models \citep{tlusty} (for $T_{eff} > 50,000$~K).

\subsubsection{The White Dwarf}

The WD at the center of the disk is always present as a spherical occulting
body with radius $R_{WD}$ in \py CV models, but it can also be included
as a source of radiation. In the models presented here, we treat the
WD as a blackbody radiator with temperature $T_{WD}$ and luminosity
$L_{WD} = 4\pi R_{WD}^2 \sigma T_{WD}^4$.

\subsubsection{The Boundary Layer}

It is possible to include radiation from a boundary layer (BL) between
the disk and the WD. In \py, the BL is described as
a blackbody with a user-specified effective temperature and
luminosity. In the models presented here, we have followed LK02 in setting
the BL luminosity to zero. However, we have confirmed that the addition of a
BL with $L_{BL} = 0.5 L_{acc}$ and temperatures in the range $80{\rm
kK} \leq T_{BL} \leq 200{\rm kK}$ would not change any of our main
conclusions. 
{\bf CK: Is this true? Do we want to say anything else, e.g. that we'll
     talk about this in a future paper?}

\subsubsection{The Secondary Star}

The donor star is included in the system as a pure radiation sink, 
i.e. it does not emit photons, but absorbs any photons that strike its
surface. The secondary is assumed to be Roche-lobe filling, so its
shape and size are defined by setting the mass ratio of the system, $q
= M_2/M_{WD}$. The inclusion of the donor star as an occulting body
allows us to model eclipses of the disk and the wind. For this
purpose, we define orbital phase such that $\Phi_{orb} = 0$ as the
inferior conjunction of the secondary (i.e. mid-eclipse for $i \simeq
90^o$).

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/sed_figure.eps}
\caption{
The spectral energy distribution (SED) of the blackbody accretion
disk used in the ionization calculation (black line), 
with two boundary layer blackbody spectra also plotted.
The positions of the Hydrogen and Helium ionization edges 
are marked with dashed vertical lines.
{\bf CK: this will need to be updated -- we want to show (just) the disk and
  WD spectra...}
}
%%JMTASK--CK: this will need to be updated -- we want to show (just) the disk and WD spectra...
\label{sed}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          RESULTS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}
\centering
\begin{tabular}{p{3cm}p{4cm}}
Model A \\
\hline Free Parameters 	&	 Value \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
$R_{WD}$ 	 &	 $7\times10^{8}$cm\\ 
$T_{WD}$ 	 &	 $40,000$K\\
$M_{2}$ 	 &	 $???? M_{\odot}$ \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$\\ 
$\dot{M}_{wind}$  &	$10^{-9}~M_{\odot}yr^{-1}$å\\ 
$r_{min}$ 	&	 $4 R_{WD}$\\ 
$r_{max}$ 	&	 $12 R_{WD}$ \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
$\gamma$ 	&	 $1$ \\ 
$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
%%$R_v$ 	        &	 $7\times10^{10}$cm \\ 
$R_v$ 	        &	 $100 R_{WD}$ \\ 
$\alpha$ 	&	 $1.5$ \\
\end{tabular}
\centering
\caption{
Parameters used for the geometry and kinematics of the benchmark CV model.}
\label{wind_param}
\end{table}

\section{A Benchmark CV Disk Wind Model}

Our main goal is to test whether the type of disk wind model that has
been successful in explaining the UV spectra of CVs could also have 
significant impact on the optical continuum and emission line spectra
of these systems. In order to set a benchmark, we therefore begin by
investigating one of the fiducial CV wind models that was used by SV93
and LK02 to simulate the UV spectrum of a typical high-state
system. The specific parameters for this model are listed in
Table~1. A key point is that the wind mass-loss rate in this model is
set to 10$\%$ of the accretion rate through the disk.

\subsection{Physical Structure and Ionization State}

Figure~\ref{wind} shows the physical and ionization structure 
of the benchmark disk wind model. There is an obvious drop-off in density
and temperature with distance away from the disk, so any line
formation process that scales as $n_e^2$ -- i.e. recombination and
collisionally excited emission -- should be expected to operate
primarily in the dense base of the outflow. Moreover, a comparison of
the rotational and poloidal velocity fields shows that rotation
dominates in the near-disk regime, while outflow dominates further out
in the wind.

The ionization equation used in the ``simple atom'' approach used in
LK02 (see Section~\ref{BLA}) should be a reasonable approximation to
the photoionization equilibrium in the benchmark wind model. Even
though the macro-atom treatment of H and He does affect the 
computation of the overall ionization equilibrium, we would expect the
resulting ionization state of the wind to be quite similar to that
found in LK02. The bottom panels in Figure~\ref{BL} confirm that this
is the case. In particular, Helium is fully ionized
throughout most of the outflow, except for a small region near the
base of the wind, which is shielded from the photons produced by the
hot inner disk. In line with the results shown in LK02, we also find
that C\textsc{iv} is the dominant Carbon ion throughout the wind,
resulting in a substantial absorbing column across a large range of
velocities. As we shall see, this produces the broad, deep and
blue-shifted C\textsc{iv}~$\lambda 1550{\rm \AA}$ absorption line that
is usually the most prominent wind-formed feature in the UV spectra of
low-inclination nova-like CVs.

\subsection{Synthetic Spectra}

We begin by verifying that the benchmark model still produces UV
spectra that resemble those observed in CVs. We do expect this to be
the case, since the ionization state of the wind has not changed
significantly from that computed in LK02 (see Section~\ref{BLA}). The
left column of panels in Figure~\ref{spec} shows that this expectation
is met: all of the strong metal resonance
lines -- notably N\textsc{v}~$\lambda 1240{\rm \AA}$,
Si\textsc{iv}~$\lambda 1400{\rm \AA}$ and C\textsc{iv}~$\lambda
1550{\rm \AA}$ -- are present and exhibit clear P-Cygni profiles
at intermediate inclinations. In addition, however, we now also find
that the wind produces significant Lyman-$\alpha$ and
He~\textsc{ii}~$\lambda1640{\rm \AA}$ emission lines.

\begin{figure} %fullpage
\includegraphics[width=\textwidth]{figures/fig5_uv_opt.eps}
\caption{
UV (left) and optical (right) synthetic spectra for model A, our benchmark model,
computed at sightlines of 10, 27.5, 45, 62.5 and 80 degrees.	
The inset plots show zoomed-in line profiles for 
\heiiuv\ and \ha. Double-peaked line emission can be seen in 
\heiiuv, \heiiopt, \ha\ and some He I lines, but the 
line emission is not always sufficient to overcome the absorption
cores from the stellar atmosphere models. The model
also produces a prominent \heiioptnew\ line at high inclinations,
}
\label{spec}
\end{figure} %fullpage\

Figure~\ref{spec} shows the corresponding optical spectra produced for
the benchmark model, and these do exhibit some emission lines
associated with H and He. Since the emissivity of these recombination 
features scales as $n_e^2$, they are formed almost entirely in the 
dense base of the wind, just above the accretion disk. Here, the
velocity field of the wind is still dominated by rotation, rather than
outflow, which accounts for the double-peaked shape of the lines. In
principle, lines formed in this region can still be single peaked,
since the existence of a poloidal velocity {\em gradient} changes the
local escape probabilities (Murray \& Chiang 1996). However, as
demonstrated explicitly in Section~\ref{BLA}, the line opacity in our
benchmark model is not high enough for this radiative transfer effect
to dominate the line shapes.

We also see a general trend from absorption lines to emission lines 
with increasing inclination, as one might expect from our wind
geometry. This trend is consistent with observations, as can be seen
in Figure~1.

The Balmer jump is in absorption at all inclinations for our benchmark
model. This is due to the stellar atmospheres we have used to
model the disk spectrum; it is not a result of photoabsorption in the
wind. In fact, the wind spectrum exhibits the Balmer jump in {\em
emission}, but this is not strong enough to overcome the intrinsic
absorption edge in the disk spectrum. This is illustrated in
Figure~\ref{cont}, which shows the angle-integrated spectrum of the system,
i.e. the spectrum formed by all escaping photons, separated into the
disk and wind contributions. Even though the wind-formed Balmer
recombination continuum does not completely fill in the Balmer
absorption edge in this model, it does already contribute
significantly to the total spectrum. This suggests that modest changes 
to the outflow kinematics might boost the wind continuum and produce
emergent spectra with weak or absent Balmer absorption edges.

\begin{figure} 
\includegraphics[width=0.45\textwidth]{figures/fig6_opt_cont.eps}
\caption{Synthetic optical spectra computed for 
sightlines of 22.5, 25, 62.5 and 80 degrees. In these plots
the flux is divided by a polynomial fit to the 
underlying continuum redward of the Balmer edge, so that 
line-to-continuum ratios and the true depth of the
Balmer jump can be shown.}
\label{spec_continuum}
\end{figure}

\begin{figure} 
\includegraphics[width=0.5\textwidth]{figures/fig7_escaping.eps}
\caption{Total packet-binned spectra across all viewing angles. 
The thick black line shows the total 
integrated escaping spectrum, while green and red lines show the contributions from photons that originate
in the disk and wind respectively. Recombination continuum emission blueward of the Balmer 
edge is already prominent relative to other wind continuum processes, but is not sufficient
to fill in the Balmer jump in this specific model}
\label{cont}
\end{figure}

\begin{figure} %fullpage
\includegraphics[width=\textwidth]{figures/fig5.eps}
\caption{
The physical properties of the wind- note the logarithmic scale. 
Near the disk plane the wind is dense, with low poloidal velocities.
As the wind accelerates it becomes less dense
and more highly ionized. The dominant Helium ion
is almost always He III, apart from in a small
portion of the wind at the base, which is partially shielded
from the inner disk.
}
\label{wind}
\end{figure} %fullpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          DISCUSSION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The Dependence of Wind Features on Outflow Parameters}

The results of Section~\ref{BLA} show that wind models that reproduce
the UV spectral features of CVs are likely to leave a clear imprint on
the optical spectrum. It is therefore important to understand the
sensitivity of optical (and UV) wind-formed features to the basic
properties of the outflow. In particular, there are two key questions
we would like to address: (i) under what conditions can disk winds
produce {\em single-peaked} Balmer emission lines (Murray \& Chiang
1996); (ii) can the wind-formed recombination continuum completely
fill in the disk's Balmer absorption edge for reasonable outflow
parameters?

The amount of recombination and collisionally excited emission
produced by a given ion, $i$, in a plasma of volume $V$ depends
primarily on the emission measure, $EM$, defined as 
\begin{equation}
EM=\int^V_0 n_e n_i \,dV,
\end{equation}
where $n_i$ is the number density of the ion in question.    
The emission reaching an observer at a given frequency also depends on
the Sobolev optical depth it experiences, which depends on both the
density and the velocity gradient projected along the line of
sight. This can also significantly affect line profile shapes.

The simplest way to simultaneously affect the density in the wind as
well as the velocity gradients is by modifying the poloidal velocity
law. We have therefore conducted a exploratory sensitivity study in
which we focus on just two kinematic variables (Section~\ref{BLA}):
\begin{itemize}
 	\item the acceleration length, $R_v$, which controls the
        distance over which the wind accelerates to $\frac{1}{2}v_{\infty}$;
 	\item the acceleration exponent, $\alpha$, which controls the rate 
 	at which the poloidal velocity changes near $R_v$.
\end{itemize} 
The general behaviour we might expect is that outflows with denser
regions near the wind base -- i.e. winds with larger $R_{v}$ and/or
larger $\alpha$ -- will produce stronger emission signatures. However,
this behaviour may be moderated by the effect of the increasing
optical depth through this region.

\subsection{Line Profiles: Shapes and Intensities}

Figure~\ref{halpha} shows how the H$\alpha$ and He~{\sc ii}~$\lambda
4686$ lines change with the kinematics of the wind for an inclination
of $80^\circ$. The width and strength of He~{\sc ii} clearly depend on
both $R_v$ and $\alpha$, but the overall line profile shape is always
double-peaked. This contrasts with the behaviour of H$\alpha$, which
becomes single-peaked in our densest models. The transition from
double-peaked to single-peaked occurs when the line becomes optically
thick. This reproduces the behaviour predicted by \cite{MC96}, who
showed that the poloidal velocity gradient in the wind can modify the
shape of optically thick emission lines even in the near-disk regime,
where the poloidal velocity itself is much smaller than the rotational
velocity. This has the effect of suppressing the line wings and
can therefore lead to the production of a single-peaked line profile
shape.

In order to produce single-peaked line emission in the majority of
lines at high inclinations, even higher opacity is needed in the
line wings. This difficulty in generating single-peaked line emission
from a rotating disk wind was also encountered by SDL05, who found
that an outflow geometry similar to that adopted here could not 
reproduce the observed single peaked profiles in YSOs. For the
parameters we have tested, the mechanism proposed by \cite{MC96} does
produce single-peaked profiles, but only for most optically thick
emission lines. In order for the same mechanism to affect the majority
of lines, even higher wind densities would be required.

{\bf CK: done up to here -- still need to edit discussion of Balmer
  jump and CIV, and then the ``next-gen'' model''}

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_alpha.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_beta.eps}}   
}
\caption{
Line profiles for \ha\ (left) and \hb\ (right) with varying kinematic 
properties, computed for an inclination of $80^\circ$.
The benchmark model is shown in the top left panel, and the improved optical
model described in section 6 is highlighted in bold. 
The parameter that has been altered from the benchmark model 
is marked in each column and row. 
Models towards the bottom right
are have more slowly accelerating winds and denser wind bases. }
\label{halpha}
\end{figure} %fullpage

\subsection{The Balmer Jump}

\label{balmerjump}

The left panel of figure~\ref{jump} shows the evolution
of the Balmer jump with our kinematic parameters. 
The `absorption' feature just redward of the Balmer jump
is artificial. It is caused by line blanketing in the stellar atmospheres,
which is not filled in by line emission from the wind
due to the use of a 20-level Hydrogen atom.
The higher density models
produce sufficient recombination continuum emission to fill 
in the Balmer jump. This offers a potential solution to a 
longstanding problem when reconciling theoretical
models of NL spectra with observations, as originally suggested by
\cite{KLWB98}. The fact that this emission is very sensitive to the parameters
that govern the density at the wind base also supports
the idea that a transition region close to the disk plane is necessary
to explain the emission features present \citep{kd1997}.

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_1640.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_4686.eps}}   
}
%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
\caption{
Line profiles for \heiiuv\ (left) and \heiiopt\  (right) with varying kinematic 
properties, computed for an inclination of $80^\circ$. 
The panels are organised in the same way as figure~\ref{halpha}.
% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
% when the wind becomes a neutral absorbing column.
}
\label{heiifig}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          Comparison with real spectra
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{An Improved Optical Model }

\begin{table}
\centering
\begin{tabular}{p{3cm}p{4cm}}
Model B \\
\hline Free Parameters 	&	 Value \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
$\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
$r_{min}$ 	&	 $4 R_{WD}$\\ 
$r_{max}$ 	&	 $12 R_{WD}$ \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
$\gamma$ 	&	 $1$ \\ 
$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
$R_v$ 	        &	 $142.9 R_{WD}$ \\ 
$\alpha$ 	&	 $4$ \\
\end{tabular}
\centering
\caption{Wind geometry parameters used in the next-generation CV model.}
\label{modelb}
\end{table}

With modest changes to the kinematics of the benchmark CV model,
it is possible to produce a model
that comes closer to reproducing the observed optical spectrum
of a NLs. The parameters for this model (imaginatively dubbed Model B)
are show in table~\ref{modelb}, and the synthetic spectrum
is shown in figure~\ref{uvoptb}. An in and out of eclipse comparison 
between the synthetic spectrum
at an angle of $80^\circ$ and the high-inclination NL RW Tri 
is also shown in figure~\ref{rwtricomp}. The inclination
for RW Tri has been disputed, with claimed values of $75^\circ$ \citep{groot2004},
$70.5^\circ$ \citep{smak1995}, $80^\circ$ \citep{longmore1981} and 
$82^\circ$\citep{frankking1981}. A lower inclination
would mean that our model would simply require lower densities 
and smaller emission regions to produce the required continuum level
and single peaked emission, so our conclusions from this comparison are
not particular sensitive to the value chosen.
We also emphasize that this is no sense a fit to the data. The model
is purely designed to reproduce the general behaviour of NLs
and give an indication of the likely densities and kinematics 
required in the wind.
%quotes a figure of , whereas  halevinhenden2008

The similarity with the observed spectrum is striking. 
Model B produces strong emission in all the Balmer lines, 
with line to continuum ratios
comparable to those in RW Tri. 
The line to continuum ratio increases during eclipse,
as one expects if the emission is produced in a disk wind, 
thereby mimicking the behaviour of SW Sex stars.
The single-peaked \ha\ line is produced by our models with a 
very similar width to the observed spectrum, although it is perhaps slightly more
`flat-topped' in the synthesized data.

One of the limitations of the model is that, apart 
from in H$\alpha$, the lines are in general double-peaked. 
The lack of high-resolution data in this regard makes detailed analysis difficult,
but it would appear that understanding how single-peaked 
line emission forms and the kinematics and densities required to
modify the line profile is still an open question. 
The major fallback of the next-generation model, however, lies
in the ultraviolet. To get the required emission in the optical lines
and recombination continuum the densities required are very high 
($n_e\sim10^{13}-10^{14}$ in the main emission region).
This causes a significant collisionally excited contribution
to the UV lines, meaning that the red wing of the 
resonance species such as C\textsc{iv} no longer matches the
observed profiles. {\bf ksl - I do not think it follows that because the red wing is strong, that this is due to collisional effects.  I think your wind is now effectively just more extended and this produce more scattered radiation. Scttering goes like n(C), emission goes like ne*n(C).  It would be interesting if we could figure out a way to show graphically where emission and absorption in a wind model are coming from.}

\begin{figure} %fullpage
\includegraphics[width=\textwidth]{figures/fig14_uv_opt.eps}
\caption{
UV (left) and Optical synthetic spectra for model B computed at
sightlines of 10, 27.5, 45, 62.5 and 80 degrees.	
The inset plots show zoomed-in line profiles for 
\heiiuv\ and \ha. The \ha line 
is single peaked, but higher order lines in the Balmer series
are double-peaked, albeit with narrower profiles.
Strong \heiiopt\ emission can be seen, as well a trend
of a deeper Balmer jump with decreasing inclination.
}
\label{uvoptb}
\end{figure} %fullpage

\begin{figure} %fullpage
\includegraphics[width=0.8\textwidth]{figures/fig13_eclipse.eps}
\caption{{\sl Top Panel:} In and out of eclipse spectra of the high
inclination NL RW Tri. {\sl Bottom Panel:} In and out of eclipse synthetic
spectra from Model B.
The artificial `absorption' feature just redward of the Balmer jump
is caused for the reasons described in section 5.2.}
\label{rwtricomp}
\end{figure} %fullpage

% \noindent\rule{16cm}{0.4pt}

% {\bf
% \noindent Notes on Section 6:

% \begin{itemize}
% 	\item

% \noindent Potential Additional Figures:

% \begin{itemize}
% 	\item 	
% }

% \noindent\rule{16cm}{0.4pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          Conclusions and Future Work
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}

By taking an already successful model
for the UV wavelength regime of CVs and treating 
it with an improved line transfer scheme, we have shown
that the wind does produce some recombination lines
and continuum emission blueward of the Balmer edge.
We have confirmed a number of the expected behaviours
by exploring a limited number of parameters governing the
kinematics and geometry of the wind. These include:

\renewcommand{\labelitemi}{$\bullet$}
\begin{itemize}
	\item The `filling-in' of the Balmer jump \citep{KLWB98} by recombination 
	continuum emission from a disk wind
	\item Single peaked line emission in \ha\ produced by 
	the introduction of a poloidal velocity gradient \citep{MC96}
	\item A Balmer decrement consistent with optically thick emission \citep{elitzur1983}.
\end{itemize}
\smallskip

\noindent We also make a number of predictions:

\begin{itemize}
	\item The depth of the Balmer absorption edge decreases with increasing inclination,
or alternatively that the Balmer recombination emission
is enhanced at higher inclinations, {\sl relative to the disk continuum}.
	\item The He~\textsc{ii}~$\lambda3202{\rm \AA}$ line should be
prominent in cases where He~\textsc{ii}~$\lambda1640{\rm \AA}$ \& 
\heiiopt\ are seen. 
	\item We expect Balmer jump in emission during eclipse.
\end{itemize}

\smallskip
Our improved optical model produces all the prominent lines in and out of eclipse, and
exhibits verisimilitude with the optical spectrum of RW Tri.
However, this model does not produce a complete unified CV model. 
The emission lines in the UV are somewhat unrealistic in strength,
because the high densities needed to increase line opacity also produce
a significant collissionally excited contribution..
This is a shortcoming which must be understood if it is true that
disk winds modify line profiles to become single peaked.
% as the 
%densities required produce a large amount of collisionally excited emission
%in UV resonance lines.

Our work demonstrates that, if nothing else,
{\sl disk winds matter} in the optical. At a minimum,
they can act as a spectral filter
for the disk spectrum.
%and the properties of the plasma
%is an important tracer for the disk and boundary layer SEDs. 
At a maximum, they may be responsible
for the majority of optical spectral features of high-state CVs,
and could dominate the appearance of both UV and optical
spectra of these systems.

%% Balmer jump

% {\bf
% \noindent Notes on Section 7:

% \begin{itemize}
% 	\item

% \noindent Potential Additional Figures:

% \begin{itemize}
% 	\item 	
% }

% \subsection{Future Work}

% To further investigate the true effect of the wind
% we hope that high quality, broadband spectra of 
% Nova-like variables at a range of inclinations 
% will be taken to examine

% In addition to this project, we have started to apply the macro atom scheme to QSOs in order to build on the work of Higginbottom et al. (2013). In particular, we hope that the macro-atom scheme will enable the
% model to produce significant Lyman-$\alpha$ emission, as is observed in QSOs.

\subsection*{Acknowledgements}
The work of JHM, NH and CK is supported by the Science and Technology Facilities Council (STFC), 
via studentships and a consolidated grant, respectively. We would like to thank Juan Hernandez Santisteban and Ivan Hubeny 
for useful discussions. We acknowledge the use of the IRIDIS High Performance Computing Facility, 
and associated support services at the University of Southampton, in the completion of this work.

\newpage
\newpage
\bibliography{mybib.bib}

\end{document}

### 2014-12-01 draft.tex
CK edit final, plus some references

--- 2014-09-18 draft.tex
@@
 
-%\title{Modeling the Optical Spectra of Cataclysmic Variables: The Importance of Disk Winds}
-%\title{Disk Winds Matter: Simulating the Optical Spectra of Cataclysmic Variables}
-\title{The Impact of Disk Winds on the Optical Spectra of Cataclysmic Variables}
+\title{The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables}
 \author{J. H. Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}
-%%\altaffiltext{1}{School of Physics \& Astronomy, University of Southampton,
-  %%Southampton, SO17 1BJ, UK}
 
@@
 \begin{abstract}
-High-state non-magnetic cataclysmic variables (CVs) 
-exhibit strong hydrogen and helium recombination lines in their optical 
-spectra. These lines can be single peaked, and may be formed 
-in the same bipolar outflow that is responsible for the
-blue-shifted absorption lines seen in the ultraviolet (UV).
-Here, we present results obtained by incorporating a `macro-atom' treatment into
-our Monte Carlo radiative transfer code, which was
-originally used to synthesize the UV spectra of disk-dominated, high-state CVs 
-with a simple biconical wind. 
-Using an identical model, we show that the same wind leaves a noticeable imprint 
-on the optical spectrum, producing \ha\ and \heiiopt\ as well as
-enhanced emission in the Ly-$\alpha$ and \heiiuv\ UV lines. 
-% In addition, our improved treatment of recombination means that the bound-free continuum
-% emission is significant, but does not yet overcome the intrinsic absorption edge
-% present in the stellar atmosphere models used to treat the accretion disk.
-We find that a boundary layer is not essential for the production
-of He II recombination lines.
-%  but also explore the effect of boundary layers
-% with temperatures of $80-200$kK on the ionization state of the wind
-% and resulting spectrum.
-A short exploration of a 3-variable kinematic parameter space leads to models with higher densities 
-that are able to produce single-peaked line emission, and also generate sufficient recombination emission
-to fill in the Balmer jump photoabsorption edge intrinsic to our disk atmosphere spectra.
-Finally, we present a synthetic spectrum of an improved optical model in 
-and out of eclipse, which shows a striking similarity with 
-the optical spectrum of the high inclination
-Nova-like variable RW Tri. The densities near the disk plane in this model
-are such that \civfull\ has a large collisionally excited component, in 
-contrast to observations.
-% We find that 
-% a boundary layer is not essential to produce significant recombination to 
-% He II, and if one is present we favour temperatures of $<10^5$K to avoid
-% overionizing the UV resonance line species such as CIV. We also conduct Zanstra method
-% calculations and estimate that one would infer a boundary layer temperature of around 80,000K
-% from our benchmark calculation, despite it not being present in the model itself. This suggests that previous calculations
-%done using this method are strongly dependent on both the assumed geometry and disk
-%spectrum.
-%We also note that
-%the presence of a boundary layer becomes more noticeable in lower accretion rate systems.
+Many high-state non-magnetic cataclysmic variables (CVs) exhibit
+blue-shifted absorption or P-Cygni profiles in ultraviolet
+(UV) resonance lines, such as C~{\sc iv}~1550\AA. These features
+imply the existence of powerful accretion disk winds in
+CVs, and considerable effort has gone into modelling UV line formation
+in such outflows. By contrast, much less attention has been paid to
+the potential impact of these disk winds on the {\em optical} spectra
+of CVs. Here, we use an improved version of our Monte Carlo ionization
+and radiative transfer code to investigate whether disk wind models that
+produce realistic UV line profiles are also likely to generate
+observationally significant recombination line and continuum emission
+in the optical waveband. In particular, we test whether outflows may 
+be responsible for the single-peaked emission line profiles often seen
+in high-state CVs and for the weakness of the Balmer absorption edge
+(relative to simple models of optically thick accretion disks).
+We find that a standard disk wind model that is successful in
+reproducing the UV spectra of CVs does leave a noticeable imprint on
+the optical spectrum as well, particularly for systems viewed at high
+inclination. The strongest optical wind-formed recombinations lines are \ha\ and
+\heiiopt\, although the outflow also produces emission in the Ly-$\alpha$
+and \heiiuv\ UV lines. However, all of the optical lines produced by
+this default wind model are double-peaked, and the effect of the wind
+on the Balmer jump is modest. We carry out a limited exploration of
+the disk wind parameter space, focusing on those parameters that affect the
+density near the base of the wind. This shows that higher-density
+outflows can produce both single-peaked emission lines and a
+recombination continuum sufficient to fill in the Balmer
+jump, although such models also tend to predict stronger-than-observed 
+collisionally excited UV emission lines. Our main conclusion is that
+disk wind emission is likely to have a significant impact on the
+optical spectra of high-state CVs. 
 \end{abstract}
@@
 \section{Introduction} 
-
-% Outflows are ubiquitous  in accreting systems across many orders of magnitude in mass,
-% from young stellar objects \citep{bunn1995} right up 
-% to quasi-stellar objects \citep[QSOs;][]{ganguly2008}. Outflows can take the form of jets, such as those
-% seen in X-ray binaries \citep{fender2006} or active galactic nuclei \citep[AGN;][]{marscher2006}, 
-% but can also manifest as `winds' emanating from the accretion disk (REFS).
-% Understanding the impact of accretion disk winds on spectral features has far-reaching implications. 
-% They provide a feedback mechanism to limit the growth of black holes in AGN \citep{silkrees1998},
-% and their ever-present nature implies a deep connection with the accretion process. This connection
-% is important to understand in order to probe the universality of accretion \citep{mchardy2006, SKUK2012} 
-% and to determine the true extent to which
-% accretion disks conform to the `$\alpha$-disk' model proposed by 
-% \cite{shakurasunyaev1973}. 
-% Despite this, in many types of systems the impact of winds on observational
-% features is essentially unknown, and many theoretical questions relating to their origin 
-% and driving mechanism remain unanswered.
-
-Cataclysmic variables (CVs) are systems in which a white dwarf accretes matter from a donor
-star via Roche-lobe overflow. In non-magnetic, disk-dominated systems this accretion
-is mediated by an accretion disk which forms around the white dwarf. 
-Nova-like variables (NLs) are a particular subclass of objects in which the accretion disk
-is in a permanent state of relatively high accretion rate 
-($\dot{M} \sim 10^{-8}$~M$_{\odot}$~yr$^{-1}$),
-making them the perfect laboratories to test the widely-used 
-`$\alpha$-disk' model proposed by 
-\cite{shakurasunyaev1973}.
-
-For over three decades, it has been known that winds emanating from the accretion disk
-are important in shaping the ultraviolet (UV) spectra of high-state CVs (Heap 1978), 
-the most spectacular evidence being the P-Cygni like profiles of resonance lines such as 
-\civfull\ (see e.g. Cordova \& Mason 1982\nocite{cordova1982}).
-Despite this, in many types of systems the impact of winds on observational
-features is essentially unknown, and many theoretical questions relating to their origin 
-and driving mechanism remain unanswered.
-
-While the effect of the wind on the UV is at least partially clear, it may also have more subtle 
-effects across the spectral range. It has been proposed that an accretion disk wind
-can provide a mechanism for single-peaked emission lines (Murray \& Chiang 1996), 
-such as those seen in Nova-like variables and, especially, the SW Sex stars \citep{HSK86, DR95}.
-It is particularly telling that single-peaked 
-lines in high-inclination systems can be seen even in eclipse, suggesting 
-that a spatially extensive wind may be the source of emission (see figure~\ref{novalikes}).
+\label{sec:intro}
+
+Cataclysmic variables (CVs) are systems in which a white dwarf
+accretes matter from a donor star via Roche-lobe overflow. In
+non-magnetic systems this accretion is mediated by a Keplerian disk
+around the white dwarf (WD). Nova-like variables (NLs) are a subclass
+of CVs in which the accretion disk is always in a relatively
+high accretion rate state ($\dot{M} \sim
+10^{-8}$~M$_{\odot}$~yr$^{-1}$).  This makes NLs an excellent
+laboratory for studying the properties of steady-state accretion
+disks.
+
+It has been known for a long time that winds emanating from the
+accretion disk are important in shaping the ultraviolet (UV) spectra
+of high-state CVs (Heap 1978). The most spectacular evidence for such
+outflows are the P-Cygni-like profiles seen in UV resonance lines such as
+\civfull\ (see e.g. Cordova \& Mason
+1982\nocite{cordova1982}). Considerable effort has been spent over the
+years on understanding and modelling these UV features (e.g. Drew \&
+Verbunt 1985; Mauche \& Raymond
+1987; Drew 1987; Shlosman \& Vitello 1993; [hereafter
+SV93]\nocite{SV93}; Knigge, Woods \& Drew 1995 [hereafter
+KWD95]\nocite{KWD95}; Knigge \& Drew 1997; Knigge et al. 1997; Long \&
+Knigge 2002 [hereafter LK02]\nocite{LK02}, Noebauer et al. 2010;
+Puebla et al. 2011). The basic picture emerging from these efforts is
+of a slowly accelerating, moderately collimated bipolar
+outflow that carries away $\simeq 1\% - 10\%$ of the accreting
+material. State-of-art-simulations of line formation in this type
+of disk wind can produce UV line profiles that are remarkably similar
+to observations.
+
+Much less is known about the effect of these outflows on the optical
+spectra of high-state CVs. These spectra are typically characterized
+by H and He emissions superposed on a blue continuum. In many
+cases, and particularly in the SW~Sex subclass of NLs
+\citep{HSK86,DR95}, these lines are single-peaked. This is contrary to
+theoretical expectations for lines formed in accretion disks, which
+are predicted to be double-peaked \citep{smak1981, hornemarsh1986}. 
+{\em Low-state} CVs (dwarf novae in quiescence) do, in fact,
+exhibit such double-peaked lines \citep{marshhorne1990}(MOREREF). 
+{\bf JM: Other things to consider; transition of line profiles
+from quiescence to outburst in DNe, emission lines in absorption cores
+trends of lines and continuum with inclination, flat
+Balmer decrement}.
+
+Murray \& Chiang (1996) have shown that the presence of disk winds may
+offer a natural explanation for the single-peaked optical emission lines in
+high-state CVs, since they can strongly affect the radiative transfer
+of line photons. Strong support for a significant wind contribution to the
+optical emission lines comes from observations of eclipsing
+systems. There, the single-peaked lines are often only weakly
+eclipsed, and a significant fraction of the line flux remains visible
+even near mid-eclipse (REF). This points to line formation in a spatially
+extended region, such as a disk wind (see figure~\ref{novalikes}).
 %%(Honeycutt, Schlegel, \& Kaitchuck 1986; Dhillon \& Rutten 1995). 
-Further evidence of the influence of winds in the optical can occasionally 
-be occasionally seen in P-Cygni like profiles observed in lines such as \ha\ 
-and He \textsc{i} $\lambda5876$ \citep{RN98}.
-
-% Somewhere, probably the introduction, we need to discuss alternatives for
-% explaining the Balmer Jump problem. The other major possibility is that
-% the disk atmospheres are not correct, see e.g Shaviv or that
-% backscattering fromt he wind changes the disk structure. This is the main
-% weakness in our model approach, because we cannot calculate the atmosphere
-% ourselves. (Christian and I have had some discussions with Hillier, who is
-% here in Aspen, and is the author of CMFGEN.  There was a paper on which he
-% was a co-author where 1-d models of winds were summed to ³make² a CV wind.
-% These used CMFGen and to calculate the structure of the wind, and so may
-% include the backr]reaction of the wind on the disk photosphere.  He said
-% he would check if these models had Balmer jumps, but you might want to
-% find the paper).
-
-It has also been proposed
-that recombination continuum emission from a disk wind or `transition region'
-could be responsible for filling in the Balmer absorption edge  \citep{KLWB98}. 
-This provides a potential explanation for
-the absence of a pronounced `Balmer jump' in optical spectra of CVs, 
-which has never been adequately produced by using stellar atmospheres 
-to model the accretion disk (see e.g. Haug 1987)\nocite{haug1987}. 
-However, it is also possible that accretion disks do not possess
-and intrinsic deep Balmer absorption edges.
-This depends to the optical depth at the edge
-and can change due to decrease due to less temperature variation with height
-near the disk photosphere (see e.g. Shaviv et al. 1991; 
-but also more recent work by Idan et al. 2010).
-\nocite{idanshaviv2010} \nocite{shaviv1991}
-
-% This dense disk atmosphere or wind transition region
-% necessary to produce the required recombination emission
-% could also explain the Fe~\textsc{ii} `curtain'
-% seen in near-UV observations of the high inclination dwarf nova OY Car in quiescence
-
-% In addition, \cite{KLWB98} suggested
-% that recombination continuum emission from a disk wind or atmosphere
-% could be responsible for filling in the Balmer absorption edge. This provides
-% a potential explanation for
-% the absence of a pronounced `Balmer jump' in optical spectra of CVs, which has never been adequately produced 
-% by theoretical models or spectral synthesis.
-% This dense disk atmosphere or wind transition region
-% necessary to produce the required recombination emission
-% could also explain the Fe~\textsc{ii} `curtain'
-% seen in near-UV observations of the high inclination dwarf nova OY Car in quiescence 
-% \citep{horne1994}.
+Further evidence for a wind contribution to the optical lines comes
+from isolated observations of P-Cygni-like line profiles even in optical
+lines, such as \ha\ and He \textsc{i} $\lambda5876$ \citep{RN98}.
+{\bf JM: need to mention this as pointed out by CK.}
+
+Could disk winds also have an impact on the UV/optical {\em continuum}
+of high-state CVs? This continuum is usually thought to be dominated
+by the accretion disk and modelled by splitting the disk into
+a set of concentric, optically thick, non-interacting annuli following
+the standard $T_{eff}(R) \propto R^{-3/4}$ radial temperature
+distribution \citep{shakurasunyaev1973}. In such
+models, each annulus is taken to emit either as a blackbody or,
+perhaps more realistically, as a stellar/disk atmosphere model
+(REF). In the latter case, the local surface gravity, $\log{g}(R)$, is
+assumed to be set solely by the accreting WD, since self-gravity is
+negligible in CV disks.
+
+Attempts to fit the observed spectral energy distributions (SEDs) of
+high-state CVs with such models have met with mixed success. In
+particular, the SEDs predicted by most stellar/disk atmosphere models 
+are too blue in the UV (REFs) and exhibit
+stronger-than-observed Balmer jumps in absorption (REFs). One possible
+explanation for these problems is that these models fail to capture
+all of the relevant physics. Indeed, it has been argued that a
+self-consistent treatment can 
+produce better agreement with observational data (e.g. Shaviv et
+al. 1991;  but also more recent work by Idan et al. 2010). 
+\nocite{idanshaviv2010} \nocite{shaviv1991}. However, an alternative 
+explanation, suggested by \cite{KLWB98}, is that recombination continuum
+emission from the base of the disk wind might fill in the disk's
+Balmer absorption edge and flatten the UV spectrum.
 
@@
 RW Sex (Top; Beuermann et al. 1992),
-IX Vel (Middle; Beuermann \& Thomas 1990)
+IX Vel (Middle; Beuermann \& Thomas 1990) %% CITE THESE
 and RW Tri in eclipse (Bottom; Groot et al. 2004).
@@
 In RW Tri strong single-peaked emission in the Balmer lines is seen even
-in eclipse, indicating that the lines may be formed in a spatially extensive disk wind, and there is even a suggestion
-of a (potentially wind-formed) recombination continuum in the eclipsed spectrum.}
+in eclipse, indicating that the lines may be formed in a spatially
+extensive disk wind, and there is even a suggestion 
+of a (potentially wind-formed) recombination continuum in the eclipsed
+spectrum.}
 \label{novalikes}
@@
 
-The first attempts to model disk winds in CVs applied techniques used in stellar
-wind modeling to an accretion disk geometry (Mauche \& Raymond
-1987; Drew 1987; Vitello \& Shlosman 1988). These efforts showed that mass loss rates of
-$\sim10\%$ of the accretion rate
-were required to produce the observed line strengths.
-Using spectral synthesis codes to model resonance scattering,
-Shlosman \& Vitello (1993; hereafter SV93)\nocite{SV93} and \cite{KWD95}
-were both successful in reproducing the observed spectra such as the P-Cygni like
-profiles in C\textsc{iv}~$\lambda1549$\AA.
-Long \& Knigge (2002; hereafter LK02)\nocite{LK02} presented a code that
-solved self-consistently for thermal and ionization balance in the wind
-according to the methods of Mazzali \& Lucy (1993; ML93)\nocite{ML93}. They successfully reproduced
-UV resonance lines profiles and presented a synthesized spectrum of Z Cam
-that agreed well with the observed features. Noebauer et al. (2010) used the same code 
-to carry out more detailed comparisons to RW Tri and UX UMa. In addition to these 
-radiative transfer calculations, some work has also been done using hydrodynamic wind models, 
-such as that by \cite{pkdh2002}, and more recently by \cite{kusterer2014} with application to
-AM Canum Venaticorum stars.
-
-Here, we present work using the same Monte Carlo radiative transfer code as LK02, 
-but incorporating additional `macro-atom' techniques suggested by Lucy (2002, 2003). 
-Our aim is to model high-state CVs over a wide spectral range.
-In particular, we hope to assess the potential contribution
-to the optical spectrum from a disk wind model which preserves the UV features.
-It will then be possible to see how closely
-our models resemble the spectra in figure 1 as we change wind parameters.
-We will investigate whether a wind can produce significant
-recombination emission lines and whether the recombination
-continuum emission is sufficient to mask the Balmer jump from a disk atmosphere.
-We will also learn if the mechanism for single-peaked line emission
-proposed by \cite{MC96} works with plausible model parameters.
-In section 2 we present the code and provide a brief description of macro-atoms 
-and the radiative transfer methods we employ. 
-We describe the kinematics and geometry of our biconical wind model in section 3.
-In section 4, we present a benchmark model, which is explored on in section 5 
-with a small-scale parameter search. In section 6, we present a
-model which better reproduces the optical spectrum of a NL, and, 
-finally, in section 7, we summarise our findings.
-
-% Here, we present work using the same Monte Carlo radiative transfer code as LK02, 
-% \py, but incorporating additional 
-% `macro-atom' techniques suggested by Lucy (2002, 2003). 
-% This improves our treatment of the Hydrogen and Helium
-% optical lines, as well as recombination continuum emission. 
-% Our goal is to investigate the effect of existing wind models
-% on the optical spectra of CVs.
-
-% {\bf
-% \noindent Fairly happy with this as an introduction. Could maybe
-% discuss the boundary layer background here instead of in section 2.
-% }
+%% CITATIONS FROM CAPTION
+\nocite{groot2004}
+
+Here, we carry out Monte Carlo radiative transfer simulations in
+order to assess the likely impact of accretion disk winds on the
+optical spectra of high-state CVs. More specifically, our goal is to
+test whether disk winds of the type developed to account for the UV
+resonance lines would also naturally produce significant amounts of  
+optical line and/or continuum emission. In order to achieve this, we
+have implemented the `macro-atom' approach developed by Lucy
+(2002, 2003) into the Monte Carlo ionization and radiative transfer
+code described by LK02 (a process initiated by SDL05). With this
+upgrade, the code is able to deal correctly with processes involving
+excited levels, such as the recombination emission produced by CV
+winds.
+
+The remainder of this paper is organized as follows. In Section~2 we
+briefly describe the code and and the newly implemented macro-atom
+approach. In Section~3, we describe the kinematics and geometry of our
+disk wind model. 
+In Section~4, we present spectra simulated from the benchmark model
+employed by LK02, and in Section~5, we carry out a limited sensitivity
+study to explore how the predicted spectra change as a function of
+some key parameters in our model. In Section~6, we summarize our
+findings.
 
@@
 
-\section{Radiative Transfer}
-
-\py is a Monte Carlo (MC) radiative transfer code which uses
-the Sobolev approximation to treat line transfer. It operates 
-in two distinct cycles. First, the ionization state, level populations
-and temperature structure are calculated. This is done by
-flying MC energy quanta (`photons') through a pre-defined wind geometry and recording
-the relevant estimators, before choosing  a new electron temperature 
-in an attempt to balance heating and cooling in the plasma.
-This process is repeated until the code converges on a 
-solution. Second, the spectrum is synthesized by tracking
-the energy packets through the wind and computing the 
-emergent spectra at a number of user-specified viewing angles.
-
-The code is capable of operating in a number of different
-regimes, both in terms of the scale of the system, and the 
-shape and characteristic energies of the illuminating spectrum. 
+\section{\sc{python}: A Monte Carlo Ionization and Radiative Transfer Code}
+
+\py is a Monte Carlo (MC) ionization and radiative transfer code which
+uses the Sobolev approximation to treat line transfer. It has already
+been described extensively in LK02, SDL05 and H13, so here we provide
+only a brief summary of its operation, focusing particularly on new
+aspects of our implementation of macro-atoms into the code.
+
+\subsection{Basics}
+
+\py operates in two distinct stages. First, the ionization state,
+level populations and temperature structure are calculated. This is
+done iteratively, by 
+propagating several populations of MC energy quanta (`photons')
+through a model wind. The geometric and kinemetic properties of the
+outflow are specified on a pre-defined spatial grid. In each of these
+iterations (``ionization cycles''), the code records estimators that 
+characterize the radiation field in each grid cell. At the end 
+of each ionization cycles, a new electron temperature is calculated
+that more closely balances heating and cooling in the 
+plasma. The radiative estimators and updated electron
+temperature are then used to revise the ionization state of the wind,
+and a new ionization cycle is started. The process is repeated until
+heating and cooling are balanced throughout the wind.
+
+This converged model is used as the basis for the second set of
+iterations (``spectral cycles''). In these, the emergent spectrum over
+the desired spectral range is synthesized by tracking populations of
+energy packets through the wind and computing the emergent spectra at
+a number of user-specified viewing angles.
+
+\py is designed to operate in a number of different
+regimes, both in terms of the scale of the system, and in terms of the
+characteristics of the underlying radiation field.
 It was originally developed by LK02 in order to model the UV spectra
-of CVs with a simple biconical disk wind model.. 
-Higginbottom et al.\nocite{higginbottom2013} (2013; hereafter H13) used the same code to
-present a benchmark model for broad absorption line (BAL) QSOs.
-As part of this effort, the ionization scheme was improved so that 
-the code is now capable of treating arbritrary SEDs.
-%the power-law X-ray spectrum exhibited by AGN.
-% This involved using a spectral model the mean intensity in a cell
-% computed from MC estimators for, instead of using a dilute blackbody
-% approximation. Compton processes
-% were also incorporated into the heating and cooling balance.
-In addition, Sim et al. (2005; hereafter SDL05)\nocite{simmacro2005} modeled
-Brackett and Pfund line profiles in young-stellar objects (YSOs) using \textsc{Python,} which included
-implementing a `macro-atom' mode in order to correctly treat recombination lines.
-
-\subsection{Macro-atoms}
-
-Previously to SDL05, \py used a two-level atom approximation \cite[see e.g.][]{mihalas}. This approximation is 
-fast, and works well as a first approximation when treating so-called `resonance lines' (such as \civfull) 
-in which the excited electron is strongly coupled to the ground state.
-However, in a number of situations, for example, when a level is primarily populated from above, then
-this becomes a poor representation. 
-To reproduce recombination lines and lines in which the lower level is not the ground state, 
-it is therefore important to use an improved line transfer technique and level population solver.
-
-By quantising matter into `macro-atoms', and radiant and kinetic 
-energy into indivisible energy packets (r- and k- packets respectively), 
-Lucy (2002, 2003\nocite{lucy2002, lucy2003}; hereafter L02, L03) showed that it is possible 
-to `asymptotically reproduce the emissivity of a gas in statistical equilibrium 
-without simplifying the treatment of line transfer'. 
-His macro-atom scheme allows all possible transition paths from a given level and a full non-Local 
-Thermodynamic Equilibrium (NLTE) solution for the level populations based on MC estimators. 
-For a full description consult L02 and L03. 
-Macro-atoms have been used to model astrophysical plasmas in 
-Wolf-Rayet star winds \citep{sim2004}, AGN disk winds \citep{simlong2008, tatum2012},
-supernovae \citep{kasen2006, kerzendorfsim} and YSOs (SDL05).
-% Recombination is expected to be an important process in the optical
-% spectra of CVs, and they thus make a perfect application for Lucy's 
-% advances in MC methods.
-
-\subsection{Ionization and Excitation}
-
-Whereas SDL05 used \py itself to apply the macro-atom 
-technique to a Hydrogen-only model, we
-adopt a hybrid ionization and excitation scheme. 
-Species can be treated as either full macro-atoms
-or using the two-level atom approximation.
-In the latter case, they still follow the indivisible packet constraint.
-This allows one to preserve the fast treatment of resonance lines while providing 
-an improved representation of processes with more complex
-transition paths such as recombination. This is important when modeling features 
-such as the Balmer lines and also recombination {\sl continuum} emission.
-
-% In our hybrid ionization and excitation scheme, 
-% simple-ions have their ionization fractions
-% calculated using a modified Saha equation, and internal level populations are
-% calculated from LTE. For macro-atoms, we solve the equations of statistical 
-% equilibrium using MC estimators for the radiation field. This enables us to 
-% determine the ionization and excitation state of the ions in question.
-
-\subsubsection{Macro-atoms}
-% In order to correctly model lines in which the lower level is not the ground state 
-% (such as H$\alpha$ \& H$\beta$), and improve the treatment of recombination,
-% we treat H \& He as macro-atoms. This is because 
-% the levels responsible for the line emission are populated mostly from above.
-% Therefore, 
-We treat H and He as macro-atoms. 
-Macro-atom NLTE level populations and ion fractions are calculated by solving 
-the statistical equilbrium equations between each pair of levels. The bound-bound 
-de-excitation rate, ${\cal R}_{ul}$, in an ion is given by
-
-\begin{equation}
-{\cal R}_{ul} = \beta_{lu} A_{ul} n_u + \beta_{lu} B_{ul} n_u J_{lu} + C_{ul} n_u n_e,\label{eq:nlte_rul}
-\end{equation}
-
-where $u$ and $l$ denote the upper and lower levels, $C$ is the collisional rate coefficient
-and $A$ and $B$ are the Einstein coefficients. $\beta_{lu}$ is the probability that a 
-given line photon will escape the Sobolev region. $J$ is the MC estimator for the mean intensity in the line as 
-recorded during the photon propagation. The corresponding excitation rate is then
-
-\begin{equation}
-{\cal R}_{lu} = \beta_{lu} B_{lu} n_l J_{lu} + C_{lu} n_l n_e.
-\end{equation}
-
-We also calculate the photoionization rates between a lower level $l$,
-and the continuum state (or, in the case of ions with more than one 
-bound electron, the ground state of the upper ion), $\kappa$,
-
-\begin{equation}
-{\cal R}_{l \kappa}= n_l \int_{\nu_0}^{\infty} \frac{ 4 \pi J_{\nu} \sigma_{\nu}}{h \nu} d\nu,
-\end{equation}
-
-where $\sigma_{\nu}$ is the photoionization cross section and $J_{\nu}$ is the mean intensity. 
-The recombination rate is given by
-
-\begin{equation}
-{\cal R}_{\kappa l} = \alpha_{\kappa l} n_{\kappa} n_e, \\
-\end{equation}
-
-where $\alpha_{\kappa l}$ is the recombination
-coefficient to level $l$. 
-This treatment means that radiative and collisional rates to and from all 
-levels are considered when calculating both the ionization state, and the level populations, 
-although we neglect photoionization to excited levels of the upper ion. 
-The \cite{vanregemorter} approximation is used for collisional transitions,
-and thus we assume collisions between radiatively forbidden transitions are
-not important in determining level populations.
-This is a reasonable approximation in the regimes considered here.
-%{2002A&A...384..725L}.  source for beta sobolevs
-%$\beta_{lu}=\frac{1}{\tau_{lu}}[1-\exp(-\tau_{lu})]$
-
-\subsubsection{Two-level atoms}
-
-Lines from all other elements are treated with the two-level atom approximation. 
-This is a first order approximation, which is appropriate 
-when treating resonance lines in which the lower level is at or close to the 
-ground state. 
-For these elements, we follow LK02 in using the ionization scheme presented by Mazzali \& Lucy (1993). 
-Specifically, we use the formula
+of CVs with a simple biconical disk wind model. Sim et al. (2005;
+hereafter SDL05)\nocite{simmacro2005} used the code to model Brackett
+and Pfund line profiles of H in young-stellar objects (YSOs). As part
+of this effort, they implemented a `macro-atom' mode (see below) in
+order to correctly treat hydrogen recombination lines with
+\py. Finally, Higginbottom et al.\nocite{higginbottom2013} (2013;
+hereafter H13) used \py to model broad absorption line (BAL) QSOs. For
+this application, an improved treatment of ionization was implemented,
+so that the code is now capable of dealing with arbritrary
+photo-ionizing SEDs, including non-thermal and multi-component ones.
+
+\subsection{Ionization and Excitation: ``Simple Atoms''}
+
+Prior to SDL05, the relative ionization fractions for all atomic
+species were estimated via the modified Saha equation (Mazzali \&
+Lucy 1993)  
 \begin{equation}
@@
 \left(\frac{T_e}{T_R}\right)^{1/2}
-\left(\frac{n_{j+1}n_e}{n_j}\right)^*_{T_R} \label{ionization}
+\left(\frac{n_{j+1}n_e}{n_j}\right)^*_{T_R}, \label{ionization}
 \end{equation}
-to solve for the relative ionization fractions. In this equation, the `starred' term on 
-the right represents the Saha abundances, in accordance with the notation of Mihalas (1982). 
+Here, the `starred' term on the right represents the Saha (LTE)
+abundances, in accordance with the notation of Mihalas (1982).  
 $W$ is an effective dilution factor, $\xi$ is the
@@
 $T_R$ and $T_e$ are the radiation and electron temperature
-respectively. LK02 provide a full description of our implementation.
-This ionization scheme is appropriate here because
-the SED can be approximated well by a dilute blackbody due to the 
-absence of a power-law X-ray source, unlike with AGN (see e.g. H13).
-For two-level atoms, we assume LTE level populations.
-% This ionization scheme is appropriate here because, unlike with AGN,
-% the SED can be approximated well by a dilute blackbody due to the 
-% absence of a power-law X-ray source, and therefore the above modification to the Saha equation
-% is appropriate; Second, this provides continuity from LK02 and allows us to do a like-for-like comparison.
-% This is especially useful in assessing the improvement in Hydrogen line emission, and any changes
-% that might occur in the ionization stages of the resonance line species such as CIV. 
-% Excitation is then calculated in LTE. 
-% This is because the 
-% level populations are only important in working out the resonance scattering 
-% opacity through the wind when modeling resonance lines.
+respectively. This simple ionization scheme produces reasonable
+results when the photoionizing SED can be approximated by a dilute
+blackbody. This is the case for high-state CVs. (As noted above, an
+improved, but more complex treatment of ionization that is appropriate
+for more complex SEDs is described in H13.)
+
+Similarly, the relative excitation fractions within each ionization
+stage of a given species were estimated via a modified Boltzmann
+equation,
+\begin{equation}
+\frac{n_{jk}}{n_j} = W g_k \exp{-E_k/kT_R} / z_j(T_R),
+\end{equation}
+where $n_{jk}$ is the population of level $k$ in ionic stage $j$,
+$E_k$ is the energy difference between level $k$ and the ground state,
+and $z_j(T_R)$ is the partition function of ionic stage $j$.
+
+Finally, \py modelled all bound-bound processes as transitions
+within a simple two-level atom \cite[see e.g.][]{mihalas}. This
+approach works reasonable well for resonance  
+lines, such as \civfull, in which the lower level is the ground state.  
+However, it is a poor approximation for many other
+transitions, particularly those where the upper level is 
+is primarily populated from above. Thus an improved method for
+estimating excited level populations and simulating line transfer is
+needed in order to model recombination lines and continua.
+
+\subsection{Ionization and Excitation: Macro-Atoms}
+
+Lucy (2002, 2003\nocite{lucy2002, lucy2003}; hereafter L02, L03) 
+has shown that it is possible to calculate the emissivity of a gas in
+statistical equilibrium accurately by quantising matter into
+`macro-atoms', and radiant and kinetic energy into indivisible energy
+packets (r- and k- packets, respectively). His macro-atom scheme
+allows for all possible transition paths from a given level and
+provides a full non-local thermodynamic equilibrium (NLTE) solution
+for the level populations based on MC estimators. The macro-atom
+technique has already been used to model Wolf-Rayet star
+winds \citep{sim2004}, AGN disk winds \citep{simlong2008, tatum2012},
+supernovae \citep{kasen2006, kerzendorfsim} and YSOs (SDL05). A full 
+description of the can be found in L02 and L03.
+
+Briefly, macro-atom NLTE level populations and ionization fractions
+are calculated by solving the statistical equilbrium equations between
+each pair of levels. For example, the bound-bound de-excitation rate,
+${\cal R}_{ul}$, in an ion is given by  
+\begin{equation}
+{\cal R}_{ul} = \beta_{lu} A_{ul} n_u + \beta_{lu} B_{ul} n_u J_{lu} +
+C_{ul} n_u n_e,\label{eq:nlte_rul},
+\end{equation}
+where $u$ and $l$ denote the upper and lower levels, $C$ represents the
+collisional rate coefficients and $A$ and $B$ represent the Einstein
+coefficients. The quantity $\beta_{lu}$ is the probability that a
+given line photon will escape the Sobolev region. Finally, $J$ is the
+MC estimator for the mean intensity in the line, as recorded during
+the photon propagation. The corresponding excitation rate is then 
+\begin{equation}
+{\cal R}_{lu} = \beta_{lu} B_{lu} n_l J_{lu} + C_{lu} n_l n_e,
+\end{equation}
+where we implicitly include a correction for stimulated emission in
+our definition of the estimate for $J_{ul}$.
+
+In our implementation of the macro-atom approach, we also explicitly
+take into account the photoionization and collisional ionization rates
+between a lower level, $l$, and the continuum (or, in the case of ions
+with more than one bound electron, the ground state of the upper ion),
+$\kappa$,
+\begin{equation}
+{\cal R}_{l \kappa}= n_l \int_{\nu_0}^{\infty} \frac{ 4 \pi J_{\nu}
+  \sigma_{\nu}}{h \nu} d\nu + C_{l \kappa} n_l n_e.
+\end{equation}
+
+Here, $\sigma_{\nu}$ is the photoionization cross section, and $J_{\nu}$
+is the mean intensity. The corresponding recombination rate is given
+by 
+\begin{equation}
+{\cal R}_{\kappa l} = \alpha_{\kappa l} n_{\kappa} n_e + C_{\kappa l}
+n_\kappa n_e, \\
+\end{equation}
+where $\alpha_{\kappa l}$ is the radiative recombination coefficient
+to level $l$. This treatment means that radiative and collisional
+rates to and from all levels are considered when calculating both the
+ionization state and the level populations, although we neglect 
+ionization directly to excited levels of the upper ion. The
+\cite{vanregemorter} approximation is used for collisional
+transitions, and thus we assume that collisions between radiatively
+forbidden transitions are not important in determining level
+populations. This is a reasonable approximation in the regimes
+considered here.
+
+\subsection{Ionization and Excitation: A Hybrid Approach}
+
+SDL05 implemented a macro-atom treatment of Hydrogen in \py and used
+this to predict the observable properties of a pure Hydrogen wind
+model for YSOs. Our goal here is to simultaneously model the optical
+and ultraviolet spectra of high-state CVs. Since the optical spectra
+are dominated by H and He recombination lines, both of these species
+need to be treated as macro-atoms. The UV spectra, on the other hand,
+are dominated by resonance lines associated with metals. This means we
+need to include these species in our models, but they can be treated 
+with our (much faster) simple-atom approach. We have therefore
+implemented a hybrid ionization and excitation scheme into \py. Any
+atomic species can now be treated either in our simple-atom
+approximation or with the full macro-atom machinery. For our CV
+models, we treat H and He as macro-atoms and all metals as
+simple-atoms.
 
 \subsection{Atomic Data}
-Here we use the same atomic data as LK02 and updated by H13.
-We have obtained the additional level and line information required to treat He as a macro-atom 
-from \textsc{Topbase} \citep{topbase2005}. We treat H as a 20-level atom as in SDL05, where 
-each level is defined by the principal quantum number, $n$, which is appropriate due to
-the degeneracy of each level in the H atom. He~\textsc{II} is treated in much the same way,
-but with 10 levels. However, He~\textsc{I} has larger energy differentials between different l subshells
-and triplet and singlet states. Thus, we still include levels up to $n=10$ but explicitly 
-treat the $l$ and $s$ sub-orbitals as distinct levels instead of assuming they are perfectly `l-mixed',
-This also allows us to model singlet and 
-triplet lines, which are seen in optical CV spectra \citep[e.g.][]{dhillon1996}.
+
+We generally use the same atomic data as H13, which is an updated
+version of that described in LK02. In addition, we follow SDL05 in
+treating Hydrogen as a 20-level atom, where each level is defined by
+the principal quantum number, $n$. For the macro-atom treatment of
+Helium,  we have added additional level and line information required 
+from \textsc{Topbase} \citep{topbase2005}.  He~\textsc{II} is treated
+in much the same way as H, but with 10 levels. He~\textsc{I} has
+larger energy differentials between different l-subshells and triplet
+and singlet states. Thus, we still include levels up to $n=10$ but
+explicitly treat the $l$ and $s$ sub-orbitals as distinct levels
+instead of assuming they are perfectly `l-mixed'. This allows us
+to model the singlet and  triplet He~\textsc{i} lines that are ubiquitous
+in the optical spectra of CVs \citep[e.g.][]{dhillon1996}.
 
@@
 
-\py has previously been tested against a number of radiative transfer and
-photoionization codes. LK02 and H13 conducted comparisons of ionization balance 
-with \cld \citep{cloudy2013}, demonstrating excellent agreement. 
-We have also carried out comparisons
-of ionization and spectral synthesis with the supernova code \textsc{Tardis.} \tar is described by
-\cite{kerzendorfsim}, and the spectral comparisons can be found therein.
-In addition to these code validation efforts, we have carried out tests of
-the macro atom scheme in \py to verify that it does indeed solve for level populations correctly
-and produces the expected level emissivities. Figure~\ref{tests} shows good agreement with 
-l-mixed Balmer decrement calculations in the Case B limit by \cite{seaton1959}, and 
-also compares He \textsc{i} level populations with \textsc{Tardis.}
-
-%% include figure here
-
-% The left panel of figure~\ref{seaton} shows a comparison
-% between our level emissivities for the Balmer series compared with analytic calculations
-% by \cite{seaton1959}, showing good agreement in both the Case A and Case B limits 
-% (see Osterbrock 1989 for a discussion of these two commonly used approximations\nocite{osterbrock}).
-% The right panel of figure~\ref{seaton} shows a comparison of Helium I level populations (the most
-% complex ion we currently treat as a macro-atom) between \py~and \tar~models. Considering the 
-% two codes use different atomic data and \textsc{Tardis,} unlike \textsc{Python,} currently has a complete treatment of
-% collisions between radiatively forbidden transitions, the factor of $<2$ agreement is 
-% encouraging.
+\py has been tested against a number of radiative transfer and
+photoionization codes. LK02 and H13 conducted comparisons of 
+ionization balance  with \cld \citep{cloudy2013}, demonstrating
+excellent agreement. We have also carried out comparisons
+of ionization and spectral synthesis with the supernova code
+\textsc{Tardis.} \tar is described by 
+\cite{kerzendorfsim}, and the spectral comparisons can be found
+therein. For the effort reported here, we have additionally carried
+out tests of the macro-atom scheme in \py. Figure~\ref{tests} shows
+two of these tests. In the top panel, we compare the Balmer series 
+emissivities as predicted by \py in the l-mixed Case~B limit against the
+analytical calculations by \cite{seaton1959}. In the bottom panel, we
+compare \py and \tar predictions of  He \textsc{i} level populations
+for a particular test case. Agreement is excellent for both H and He.
 
@@
 $<2$ agreement is encouraging. 
+{\bf CK: WHAT ARE THE PARTICULAR SETS OF PARAMETERS BEING ADOPTED HERE?}
 }
@@
 
-% \noindent\rule{16cm}{0.4pt}
-
-% {\bf
-% \noindent Notes on Section 2:
-
-% \begin{itemize}
-% 	\item Should this section go after section 3, so that we've got the reader hooked with the model description first?
-% 	\item 
-% 	\item Would appreciate feedback on whether explanation of macro-atoms 
-% 	is sufficient.
-
-% \noindent Potential Additional Figures:
-
-% \begin{itemize}
-% 	\item Include figure on Case A/ Case B and TARDIS comparison	
-% }
-%
-% \noindent\rule{16cm}{0.4pt}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{A Biconical Wind CV Model}
-
-Here we describe some of the features of our biconical wind model.
-
-\subsection{Description of Model: Geometry and Kinematics}
-
-For our kinematic wind model we use 
-the prescription outlined by Schlosman \& Vitello (1993; hereafter SV93). A schematic is shown
-in figure~\ref{cartoon}. A smooth, biconical
-disk wind rises from the accretion disk between radii $r_{min}$ and $r_{max}$. The covering fraction of the wind is 
-also controlled by the opening angles of the wind, $\theta_{min}$ and $\theta_{max}$, and the launch angle of
-the other streamlines is given by
-
+\section{Describing the System and its Outflow}
+
+\py includes several different kinematic models of accretion disk
+winds, as well as different options for describing the physical and
+radiative properties of the wind-driving system under
+consideration. Most of these features have already been discussed in
+LK02 and H13, so below we only briefly recount the key aspects of the
+particular system and wind model used in the present study.
+
+\subsection{Wind Geometry and Kinematics}
+
+We adopt the kinematic disk wind model developed by Schlosman \&
+Vitello (1993; hereafter SV93). A schematic of this model is shown in
+figure~\ref{cartoon}. In this parametrization, a smooth, biconical
+disk wind emanates from the accretion disk between radii $r_{min}$ and 
+$r_{max}$. The covering fraction of the outflow is also controlled by the
+inner and outer opening angles of the wind, $\theta_{min}$ and
+$\theta_{max}$, and the launch angle of the other streamlines is given
+by 
 \begin{equation}
@@
 \end{equation}
-
 where $r_0$ is the launch radius of the streamline.
-%As in LK02, we follow SV93's power lawvelocity profile. 
-The poloidal velocity, $v_l$, in the SV93 model is given by
-
+
+The poloidal (non-rotational) velocity field of the wind, $v_l$, is given by
 \begin{equation}
@@
 \end{equation}
-
-where $l$ is the poloidal distance. The terminal velocity, 
-$v_{\infty}$, is set to a fixed multiple of the escape velocity at the bottom
-of a streamline, and $v_0$ is a constant launch velocity (set to $6$~km~s$^{-1}$).
-Once the wind is launched, it accelerates with a characteristic acceleration
-length $R_v$, and $\alpha$ is an exponent which controls how quickly the 
-wind accelerates. Larger values of $\alpha$ cause the main region of 
-acceleration to occur close to $R_v$, whereas smaller values will lead
-to a fast acceleration close to the disk (see figure~\ref{acc_law}).
-SV93 chose this velocity law so as to give a 
-velocity gradient that varied continuously along a streamline, as well
-as producing line profiles with realistic velocity spreads.
-In addition to these motivations, adopting a consistent velocity law 
-allows for direct comparison with models which have already been successful in 
-simulating UV resonance line profiles, such as those presented by LK02 and SV93.
+where $l$ is the poloidal distance along a particular wind
+streamline. The terminal velocity along a streamline, $v_{\infty}$, is
+set to a fixed multiple of the escape velocity at the launch
+point. The launch velocity from the disk surface, $v_0$, is assumed to
+be constant (set to $6$~km~s$^{-1}$). Once the wind is launched, it
+accelerates, reaching half of its terminal velocity at $l = R_v$. The
+velocity law exponent $\alpha$ controls how quickly the wind
+accelerates. Larger values of $\alpha$ cause the main region of 
+acceleration to occur close to $R_v$, whereas smaller values
+correspond to fast acceleration close to the disk (see
+figure~\ref{acc_law}).
 
@@
 \caption{
-The velocity law in our model for various values of
-the acceleration exponent, $\alpha$.
-}
+The adopted poloidal velocity law for various values of the
+acceleration exponent, $\alpha$.} 
 \label{acc_law}
@@
 
-%The principle of mass conservation 
-The mass continuity equation implies that the velocity law also 
-controls the density, $\rho$, of the wind, which can be expressed in terms
-of radial and vertical position $(r,z)$ as
-
+The density at position $(r,z)$ in the wind, $\rho(r,z)$, is
+calculated from the mass continuity equation, yielding
 \begin{equation}
-\rho(r,z) = \frac{r}{r_0} \frac{dr}{dr_0} \frac{\phi(r_0)}{v_z(r,z)},
+\rho(r,z) = \frac{r}{r_0} \frac{dr}{dr_0} \frac{\phi(r_0)}{v_z(r,z)}.
 \label{density}
 \end{equation}
-
-where $\phi$ is the mass-loss rate per unit area at $r_0$
-and $v_z$ is the vertical velocity component. In our model, we
-adopt a uniform value for $\phi$.
-
-\subsection{Photon Sources}
-
-Photons originate from the accretion disk and a central WD in our model. It is also possible to include
-a boundary layer with user-defined temperature and emitting area. Emission from the wind is dealt with
-by reprocessing of the indivisible energy packets originally produced in the disk or central WD.
-
-\subsubsection{The Accretion Disk}
-
-\py has has some flexibility when treating the accretion disk as a source of photons. 
-The disk is broken down into annuli 
-such that each annulus contributes an equal amount to the bolometric luminosity. 
-We adopt the temperature profile of a standard \cite{shakurasunyaev1973} $\alpha$-disk.
-%shown in figure 1.
-An annulus can then
-be treated either as a blackbody with the corresponding effective temperature or as a stellar atmosphere model
-with the appropriate surface gravity and effective temperature. 
-Both of these methods have limitations. It is known
-from studies of CV accretion disks that they exhibit absorption cores 
-formed in an optically thick disk atmosphere.
-This can impact the overall spectrum even if a wind is present 
-\citep[see e.g.][]{dhillon1996}.
-However, the stellar atmosphere models
-have had difficulties reproducing the required spectral shape \citep{wade1988}, 
-and there are inconsistencies when using a 
-stellar atmosphere beneath a dense
-wind region that itself goes some way to simulating the disk atmosphere. 
-In addition, \cite{linnell2010} found that deviations from the predicted 
-$T\propto r^{-3/4}$ temperature profile are required to fit the data
-in certain cases.
-
-We hope that future simulations, coupled with a comparison to data, will 
-actually address some of these problems, particularly since
-the filtering effect of the wind may cause noticeable effects
-on the colour of the emergent spectrum \citep{hassall}. 
-Here, we use a blackbody illuminating spectrum
-for the ionization cycles (see figure~\ref{sed}) and to compute our MC estimators.
-During the spectral synthesis stage of the simulation we use stellar atmosphere models.
-This is partly because they provide the most pessimistic prediction in terms of whether recombination emission in the 
-wind can fill in the Balmer jump, due to their intrinsic strong absorption beyond the Balmer edge.
-For low temperatures, we use stellar atmospheres computed 
-by Kurucz \citep{kurucz1991}, and for $T>50,000$~K we use models computed with 
-\textsc{TLUSTY} \citep{tlusty}. The input spectra are created from these model
-atmospheres using \textsc{Synspec}\footnote{http://nova.astro.umd.edu/Synspec43/synspec.html}.
-%The temperature profile of our disk,
-%with $\dot{M}_{acc} = 10^{-8}~M_{\odot}yr^{-1}$ can be seen in figure~\ref{t_profile}.
-% more detail on why we use this hodge podge of atmosphere models?
+Here, $\phi(r_O)$ is the mass-loss rate per unit area at $r_0$, 
+and $v_z$ is the vertical velocity component. We take $\phi(r_0)$ to be
+uniform across the wind-launching area of the disk and normalize it by
+matching its integral to the user-specified total mass-loss rate,
+$\dot{M}_{wind}$. 
+{\bf CK: I'm still not sure I understand the formula
+  SV93 use to define $\phi$, and hence that this description is
+  actually strictly correct.... Not sure what to do about that
+  though...}
+
+\subsection{Sources and Sinks of Radiation}
+
+The net photon sources in our CV model are the accretion disk, the
+WD and, in principle, a boundary layer with user-defined temperature
+and luminosity. All of these radiating bodies are taken to be
+optically thick, and photons striking them are assumed to be destroyed
+instantaneously. The secondary star is not included as a radiation
+source, but is included as an occulting body. This allows us to model
+eclipses. Finally, emission from the wind itself is also accounted for, but
+note that we assume the outflow to be in radiative equilibrium. Thus all
+of the heating of the wind, as well as its emission, is ultimately
+powered by the radiation field of the net photon sources in the
+simulation. In the following sections, we will describe our treatment
+of these system components in slightly more detail.
+
+\subsubsection{Accretion Disk}
+
+\py has has some flexibility when treating the accretion 
+disk as a source of photons. The disk is broken down into annuli 
+such that each annulus contributes an equal amount to the bolometric
+luminosity. We take the disk to be geometrically thin, but optically
+thick and thus adopt the temperature profile of a standard
+\cite{shakurasunyaev1973} $\alpha$-disk. An annulus can then
+be treated either as a blackbody with the corresponding effective
+temperature or as a stellar atmosphere model with the appropriate
+surface gravity and effective temperature. Here, we use blackbodies 
+during the ionization cycles and to compute our MC
+estimators. However, during the spectral synthesis stage of the 
+simulation we use stellar atmosphere models. This produces more
+realistic model spectra and allows us to test if recombination
+emission from the wind base can fill in the Balmer jump, which is
+always in absorption in these models. Our synthetic stellar atmosphere
+spectra are calculated with
+\textsc{Synspec}\footnote{http://nova.astro.umd.edu/Synspec43/synspec.html}
+from either Kurucz \citep{kurucz1991} atmospheres (for $T_{eff} \leq
+50,000$~K) or from \textsc{TLUSTY} models \citep{tlusty} (for $T_{eff} > 50,000$~K).
+
+\subsubsection{White Dwarf}
+
+The WD at the center of the disk is always present as a spherical occulting
+body with radius $R_{WD}$ in \py CV models, but it can also be included
+as a source of radiation. In the models presented here, we treat the
+WD as a blackbody radiator with temperature $T_{WD}$ and luminosity
+$L_{WD} = 4\pi R_{WD}^2 \sigma T_{WD}^4$.
 
 \subsubsection{Boundary Layer}
-The existence of a boundary layer in CVs arises naturally from the boundary condition
-of the \cite{shakurasunyaev1973} model, since the material at the inner disk
-edge must lose angular momentum in order to be deposited on
-the surface of the compact object \cite[see e.g.][]{lyndenbell1974}.
-Boundary layers are a source of
-high energy photons which may be responsible for the photoionization of 
-He~\textsc{ii}, so a disk wind can therefore be an important diagnostic
-tool for inferring boundary layer luminosities and temperatures. 
-The luminosity of the boundary layer, $L_{bl}$, is related to the accretion luminosity
-by
-
-\begin{equation}
-L_{bl} = \frac{1}{2} L_{acc} (1 - \omega_* / \omega_k)^2,
-\end{equation}
-
-where $\omega_k$ and $\omega_*$ are the angular momenta at the inner disk edge
-and WD surface respectively \citep{fkrbook}. A faster spinning white dwarf 
-will have a less luminous boundary layer.
-
-\cite{pringlesavonije1979} predict theoretical temperatures of 
-$200-500{\rm kK}$ for the boundary layer.
-This high temperature is supported by extreme UV observations \citep{mauche2004}
-and recent modeling \citep{suleimanov2014}, although these studies 
-find $L_{bl}/L_{acc}$ of $\sim0.05$ and $\sim0.2$ respectively in their
-model fits. A number of studies have found difficulties
-in producing the observed ionization state of the wind
-with such a hot, luminous boundary layer 
-\citep[see e.g.][]{maucheraymond1987, drewverbunt1985}.
-\cite{hoare1991}
-use the method of \cite{zanstra1929} to find upper limits on 
-boundary layer temperatures of $\sim80{\rm kK}$.
-
-It is possible to include a boundary layer in our model which emits 
-as a blackbody with a user-specified effective temperature and luminsoity.
-Boundary layer photons are then produced around the spherical surface of the 
-white dwarf. In our benchmark model, we follow LK02 in setting the boundary layer
-luminosity to zero. We investigate the effect
-of boundary layers with temperatures between $80{\rm kK}$ and $200{\rm kK}$ 
-on the ionization state of the wind and resulting
-spectrum in section 5.
+
+It is possible to include radiation from a boundary layer (BL) between
+the disk and the WD. In \py, the BL is described as
+a blackbody with a user-specified effective temperature and
+luminosity. In the models presented here, we have followed LK02 in setting
+the BL luminosity to zero. However, we have confirmed that the addition of a
+BL with $L_{BL} = 0.5 L_{acc}$ and temperatures in the range $80{\rm
+kK} \leq T_{BL} \leq 200{\rm kK}$ would not change any of our main
+conclusions. 
+{\bf CK: Is this true? Do we want to say anything else, e.g. that we'll
+     talk about this in a future paper?}
+
+\subsubsection{Secondary Star}
+
+The donor star is included in the system as a pure radiation sink, 
+i.e. it does not emit photons, but absorbs any photons that strike its
+surface. The secondary is assumed to be Roche-lobe filling, so its
+shape and size are defined by setting the mass ratio of the system, $q
+= M_2/M_{WD}$. The inclusion of the donor star as an occulting body
+allows us to model eclipses of the disk and the wind. For this
+purpose, we define orbital phase such that $\Phi_{orb} = 0$ as the
+inferior conjunction of the secondary (i.e. mid-eclipse for $i \simeq
+90^o$).
 
@@
 with two boundary layer blackbody spectra also plotted.
-% The SED for an accretion disk
-% with the parameters used by HD91 in their Zanstra method calculations is shown in grey. 
-% It still assumes a Shakura-Sunyaev temperature profile, but uses
-% of $\dot{M}_{acc}= 5\times10^{-9}~M_{\odot}$yr$^{-1}$, and a slightly lower mass
-% white dwarf with $M_{WD}=0.7 M_{\odot}$ and $R_{WD} = 7\times10^{8}$cm.
 The positions of the Hydrogen and Helium ionization edges 
 are marked with dashed vertical lines.
-{\bf NOTE: CK thinks this figure needs more discussion}.
-%The effective temperature of the accretion disk
-%in our model, as a function of radius.
+{\bf CK: this will need to be updated -- we want to show (just) the disk and
+  WD spectra...}
  }
@@
 
-% \noindent\rule{16cm}{0.4pt}
-%
-% {\bf
-% \noindent Notes on Section 3:
-
-% \begin{itemize}
-% 	\item
-
-% \noindent Potential Additional Figures:
-
-% \begin{itemize}
-% 	\item 	
-% }
-%
-% \noindent\rule{16cm}{0.4pt}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{tabular}{p{3cm}p{4cm}}
-Model A \\
+Benchmark Model (Optimized for the UV Band) \\
 \hline Free Parameters 	&	 Value \\ 
@@
 $R_{WD}$ 	 &	 $7\times10^{8}$cm\\ 
+$T_{WD}$ 	 &	 $40,000$K\\
+$M_{2}$ 	 &	 $???? M_{\odot}$ \\ 
 $\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$\\ 
@@
 
-\section{Results \& Analysis from a Benchmark Model}
-
-% The results in this section were obtained using the geometry described
-% in section 3. The kinematics and mass loss rate of the wind are identical
-% to LK02. 
-% Photon sources are identical, except that when synthesizing the
-% spectrum we treat the accretion disk 
-% as an ensemble of Kurucz and TLUSTY stellar atmosphere models to better 
-% interpret the behaviour of the Balmer jump.
-
-Our aim here is not
-to provide a `best fit' model to match any particular dataset.
-Rather, we take
-a successful UV wind model as a starting point
-and examine its effect 
-when one utilises the better treatment of lines provided
-by the macro-atom scheme.
-The model parameters are shown in table 1. 
-they are identical to LK02, and were chosen both to reflect typical
-values for NLs and reproduce realistic UV line profiles.
-% The specific model 
-% parameters are summarised in table 1, and follow LK02. 
-% They are motivated by a need to agree with typical observed values 
-% for NLs and the values required to reproduce the UV line profile
+\section{A Benchmark Disk Wind Model}
+
+Our main goal is to test whether the type of disk wind model that has
+been successful in explaining the UV spectra of CVs could also have 
+significant impact on the optical continuum and emission line spectra
+of these systems. In order to set a benchmark, we therefore begin by
+investigating one of the fiducial CV wind models that was used by SV93
+and LK02 to simulate the UV spectrum of a typical high-state
+system. The specific parameters for this model are listed in
+Table~1. A key point is that the wind mass-loss rate in this model is
+set to 10$\%$ of the accretion rate through the disk.
+
+\subsection{Physical Structure and Ionization State}
+
+Figure~\ref{wind} shows the physical and ionization structure 
+of the benchmark disk wind model. There is an obvious drop-off in density
+and temperature with distance away from the disk, so any line
+formation process that scales as $n_e^2$ -- i.e. recombination and
+collisionally excited emission -- should be expected to operate
+primarily in the dense base of the outflow. Moreover, a comparison of
+the rotational and poloidal velocity fields shows that rotation
+dominates in the near-disk regime, while outflow dominates further out
+in the wind.
+
+The ionization equation used in the ``simple atom'' approach used in
+LK02 (see Section~\ref{BLA}) should be a reasonable approximation to
+the photoionization equilibrium in the benchmark wind model. Even
+though the macro-atom treatment of H and He does affect the 
+computation of the overall ionization equilibrium, we would expect the
+resulting ionization state of the wind to be quite similar to that
+found in LK02. The bottom panels in Figure~\ref{BL} confirm that this
+is the case. In particular, Helium is fully ionized
+throughout most of the outflow, except for a small region near the
+base of the wind, which is shielded from the photons produced by the
+hot inner disk. In line with the results shown in LK02, we also find
+that C\textsc{iv} is the dominant Carbon ion throughout the wind,
+resulting in a substantial absorbing column across a large range of
+velocities. As we shall see, this produces the broad, deep and
+blue-shifted C\textsc{iv}~$\lambda 1550{\rm \AA}$ absorption line that
+is usually the most prominent wind-formed feature in the UV spectra of
+low-inclination nova-like CVs.
 
 \subsection{Synthetic Spectra}
+
+We begin by verifying that the benchmark model still produces UV
+spectra that resemble those observed in CVs. We do expect this to be
+the case, since the ionization state of the wind has not changed
+significantly from that computed in LK02 (see Section~\ref{BLA}). The
+left column of panels in Figure~\ref{spec} shows that this expectation
+is met: all of the strong metal resonance
+lines - notably N\textsc{v}~$\lambda 1240{\rm \AA}$,
+Si\textsc{iv}~$\lambda 1400{\rm \AA}$ and C\textsc{iv}~$\lambda
+1550{\rm \AA}$ - are present and exhibit clear P-Cygni profiles
+at intermediate inclinations. In addition, however, we now also find
+that the wind produces significant Lyman-$\alpha$ and
+He~\textsc{ii}~$\lambda1640{\rm \AA}$ emission lines.
 
@@
 
-Figure~\ref{spec} shows optical synthetic spectra for the benchmark 
-model for five different inclination angles ranging from $10^\circ$ to $80^\circ$ 
-%5 different sightlines.  
-The model produces some lines which are strong enough to overcome
-the absorption cores lines from the disk. These lines are generally double peaked, 
-as they are formed near the base of the wind where rotational velocity
-can still dominate over the slowly increasing poloidal velocity. The line 
-opacity is not yet high enough for the poloidal velocity gradient to 
-cause single-peaked profiles. 
-We also see a general trend from absorption to emission in spectral lines
-with increasing inclination, as one would expect from our wind geometry.
-This trend is observed in CVs and can be seen clearly in figure 1. 
-% Note, however,
-% that in our models the \heiiuv\ line does not exhibit this behaviour, which
-% is somewhat surprising. {\bf NOTE: we need to understand this!}.
-
-The Balmer jump is in absorption at all inclinations. This is 
-due to the stellar atmosphere models used to model the disk;
-it is not a result of photoabsorption in the wind.
-In fact, the wind spectrum has the Balmer jump in emission, 
-but this is not prominent enough
-to overcome the intrinsic absorption in the disk spectrum. 
-Figure~\ref{cont} shows the total escaping spectrum, integrated
-over all viewing angles, with the contribution from the disk and wind
-shown separately. This shows that the lines are produced in the wind,
-and also that the wind is producing a Balmer recombination
-continuum, but one which is not yet sufficient to mask the absorption 
-intrinsic to the disk SED. This offers a tantalising hint
-that modest changes to the kinematics of the wind
-may be sufficient to boost the continuum emission of the wind.
-Furthermore, it confirms our suspicions that the improved
-radiative transfer would cause enhanced recombination emission,
-suggesting that, where possible, up to date treatments of
-NLTE line transfer should be used in codes such as this.
-The prominent P-Cygni profiles in e.g., C\textsc{iv} are still seen
-in the UV spectra (see figure~\ref{spec}). In addition, the wind 
-now produces significant Lyman-$\alpha$ and
-He~\textsc{ii}~$\lambda1640{\rm \AA}$  emission. 
-% We note that the ionization state of the wind 
-% is such that recombination to He~\textsc{ii} is significant, even
-% without a boundary layer as a source of higher energy photons.
-
-In addition to examining synthetic spectra, we are also able to 
-analyse the physical properties of the outflow.
-Figure~\ref{wind} shows various physical properties
-of the wind geometry. The ionization structure of the wind
-is very similar to the original LK02 model, as one might expect.
-He is mostly ionized throughout the wind except for a small region near
-the disk which is shielded from the photons produced by the hot inner disk.
-C\textsc{iv} is the dominant Carbon ion throughout the wind, allowing
-for an absorbing column which covers a large range of velocities and is thus
-sufficient to produce the required broad, deep and blue-shifted absorption lines
-we expect to see in a large fraction of nova-likes.
+Figure~\ref{spec} shows the corresponding optical spectra produced for
+the benchmark model, and these do exhibit some emission lines
+associated with H and He. Since the emissivity of these recombination 
+features scales as $n_e^2$, they are formed almost entirely in the 
+dense base of the wind, just above the accretion disk. Here, the
+velocity field of the wind is still dominated by rotation, rather than
+outflow, which accounts for the double-peaked shape of the lines. In
+principle, lines formed in this region can still be single peaked,
+since the existence of a poloidal velocity {\em gradient} changes the
+local escape probabilities (Murray \& Chiang 1996). However, as
+demonstrated explicitly in Section~\ref{BLA}, the line opacity in our
+benchmark model is not high enough for this radiative transfer effect
+to dominate the line shapes.
+
+We also see a general trend from absorption lines to emission lines 
+with increasing inclination, as one might expect from our wind
+geometry. This trend is consistent with observations, as can be seen
+in Figure~1.
+
+The Balmer jump is in absorption at all inclinations for our benchmark
+model. This is due to the stellar atmospheres we have used to
+model the disk spectrum; it is not a result of photoabsorption in the
+wind. In fact, the wind spectrum exhibits the Balmer jump in {\em
+emission}, but this is not strong enough to overcome the intrinsic
+absorption edge in the disk spectrum. This is illustrated in
+Figure~\ref{cont}, which shows the angle-integrated spectrum of the system,
+i.e. the spectrum formed by all escaping photons, separated into the
+disk and wind contributions. Even though the wind-formed Balmer
+recombination continuum does not completely fill in the Balmer
+absorption edge in this model, it does already contribute
+significantly to the total spectrum. This suggests that modest changes 
+to the outflow kinematics might boost the wind continuum and produce
+emergent spectra with weak or absent Balmer absorption edges.
 
@@
 
-Clearly, this particular model cannot explain all
-the features seen in the optical spectra of nova-like variables. However,
-the wind has a significant effect on the observed spectral features. 
-It cannot be ignored as a source of line and continuum emission and as a reprocessing `filter'
-of the underlying disk spectral energy distribution (SED).
-
 \begin{figure} 
@@
 \end{figure}
-
-%\subsection{Ionization and Temperature Structure}
 
@@
 
-% \noindent\rule{16cm}{0.4pt}
-
-% {\bf
-% \noindent Notes on Section 4:
-
-% \begin{itemize}
-% 	\item
-
-% \noindent Potential Additional Figures:
-
-% \begin{itemize}
-% 	\item 	
-% }
-
-% \noindent\rule{16cm}{0.4pt}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Exploring Parameter Space}
-
-The benchmark model presented above shows that a wind with the properties
-of Model A, a model that successfully reproduces the observed UV spectral features
-of CVs,
-would also leave a clear imprint on the optical spectrum. It is important
-to understand how changing the kinematics of the wind impacts on this
-effect. A full parameter search is beyond the scope of this study, 
-but we can examine the evolution
-of the spectrum with a few key parameters. In particular, this
-will help shed light on the predictions of, e.g., Murray \& Chiang (1996)
-and Knigge et al. (1998) regarding the single-peaked H$\alpha$ emission
-and absence of a pronounced Balmer absorption edge respectively.
-
-The amount of line and recombination continuum
-emission produced by a given ion, $i$, in a plasma of volume $V$
-depends on the emission measure, $EM$, defined as
-
+\section{The Dependence of Wind Features on Outflow Parameters}
+
+The results of Section~\ref{BLA} show that wind models that reproduce
+the UV spectral features of CVs are likely to leave a clear imprint on
+the optical spectrum. It is therefore important to understand the
+sensitivity of optical (and UV) wind-formed features to the basic
+properties of the outflow. In particular, there are two key questions
+we would like to address: (i) under what conditions can disk winds
+produce {\em single-peaked} Balmer emission lines (Murray \& Chiang
+1996); (ii) can the wind-formed recombination continuum completely
+fill in the disk's Balmer absorption edge for reasonable outflow
+parameters?
+
+The amount of recombination and collisionally excited emission
+produced by a given ion, $i$, in a plasma of volume $V$ depends
+primarily on the emission measure, $EM$, defined as 
 \begin{equation}
@@
 \end{equation}
-
-%% Should I quote Optical depths or 'Q' here to motivate the parameter search?
-
 where $n_i$ is the number density of the ion in question.    
-Therefore, any quantity which controls the density profile of the wind
-will have a profound impact on both the 
-amount of emission and the shape of the escaping line profiles.
-The emission reaching an observer at a given frequency
-also depends on the Sobolev optical depth it experiences, which depends on both
-the density and the velocity gradient projected
-along the line of sight. This can also significantly affect line profile shapes.       
-As described in section 3, we can alter the density in the wind by 
-adjusting the velocity law (which also determines the velocity gradient).
-
-A full kinematic parameter search may prove instructive, but
-is beyond the scope of this particular study.
-We have therefore conducted a limited parameter 
-search, where we focus on 
-two variables in order to explore the trends in our model. 
-These are:
-
+The emission reaching an observer at a given frequency also depends on
+the Sobolev optical depth it experiences, which depends on both the
+density and the velocity gradient projected along the line of
+sight. This can also significantly affect line profile shapes.
+
+The simplest way to simultaneously affect the density in the wind as
+well as the velocity gradients is by modifying the poloidal velocity
+law. We have therefore conducted a exploratory sensitivity study in
+which we focus on just two kinematic variables (Section~\ref{BLA}):
 \begin{itemize}
- 	\item the acceleration length, $R_v$, which controls the characteristic scale
- 	over which the wind accelerates,
+ 	\item the acceleration length, $R_v$, which controls the
+        distance over which the wind accelerates to $\frac{1}{2}v_{\infty}$;
  	\item the acceleration exponent, $\alpha$, which controls the rate 
- 	at which the velocity changes near $R_v$. 
- 	A higher value of $\alpha$ therefore leads to a slowly accelerating 
- 	wind with a dense base,
- 	% \item the launch radii of the wind, $r_{min}$ \& $r_{max}$,
- 	%%\item the temperature of the boundary layer, $T_{bl}$.
+ 	at which the poloidal velocity changes near $R_v$.
 \end{itemize} 
-
-We have found these to be important parameters in modifying 
-the emergent spectrum.
-In general, quantities which cause a denser wind base increase
-the overall emission, although optical depth effects can cause 
-the relationship to become more complicated. In addition to these 
-kinematic parameters, we also investigate the effect of 
-including a boundary layer on the equivalent widths of the 
-\civfull\ and \heiiuv\ lines (see section 5.3).
-
-\subsection{Line Profiles: Shapes and Intensities}
-
-% \noindent\rule{16cm}{0.4pt}
-
-% {\bf
-% \noindent key points here:
-
-% \begin{itemize}
-% 	\item producing single peaked line profiles is difficult to say the least
-% 	\item with our high density models we can produce some single peaked line emission,
-% 	mostly in Halpha and beta. the other lines seem to stay double peaked.
-% 	\item this higher density causes (too much) collisionally excited line emission from CIV
-% 	\item if the wind was more equatorial then this might help, but this isn't really supported by observations.
-% 	\item we can definitely reproduce the behaviour predicted by Murray and Chiang
-% 	\item Comment on the observed Balmer decrement being fairly flat, as is observed. Point out that
-% 	this is necessary if H alpha is to be single peaked, as you need significant optical depths.
-% 	\item \la needs to be discussed somewhere- potentially here. Personally I would like to point out
-% 	that recombination being important here suggests that it might also be in QSOs
-% \end{itemize}
-% }
-
-% \noindent\rule{16cm}{0.4pt}
-
-Figure~\ref{halpha} shows how the H$\alpha$ and H$\beta$ lines change with the kinematics 
-of the wind at an inclination of $80^\circ$. For H$\alpha$, in models with lower densities, the
-line is double peaked, but we see a transition to a single peaked line when 
-a high enough density is reach such that the line becomes optically thick.
-This reproduces the behaviour predicted by \cite{MC96}, who suggested that
-the poloidal velocity gradient in the wind can be larger than the gradient of 
-the Keplerian velocity. This velocity gradient can therefore modify the line profile shape
-by suppressing emission at the red and blue wings of the line, 
-providing that the line optical depth is high enough.
-
-In order to produce single-peaked line emission in the majority of lines at high inclinations,
-it is clear that a higher line opacity is needed at the red and blue wings relative to
-the opacity at line centre. This can be achieved in a number of ways. A more equatorial 
-wind would increase the radial velocity shear, but is not supported by observations (references 
-on collimated nature of CV winds).
-Our difficulty in producing single-peaked line emission from a full 
-radiative transfer calculation has been encountered before in a number of situations. 
-SDL05 found that a biconical disk geometry similar to that adopted here could not reproduce 
-the observed single peaked profiles in YSOs. 
-Here, we find
-that the mechanism proposed by \cite{MC96} does indeed produce 
-single-peaked line emission in our models with plausible wind parameters, 
-but for this to occur in the majority of
-spectral lines very high densities are required.
+The general behaviour we might expect is that outflows with denser
+regions near the wind base -- i.e. winds with larger $R_{v}$ and/or
+larger $\alpha$ -- will produce stronger optical emission signatures. 
+However, this behaviour may be moderated by the effect of the increasing
+optical depth through this region.
+
+\subsection{Optical Wind Signatures}
+
+Figures~\ref{halpha} and~\ref{heii} show how the H$\alpha$ and 
+He~{\sc ii}~$\lambda 
+4686$ lines change with the kinematics of the wind for an inclination
+of $80^\circ$. The width and strength of He~{\sc ii} clearly depend on
+both $R_v$ and $\alpha$, but the overall line profile shape is always
+double-peaked. This contrasts with the behaviour of H$\alpha$, which
+becomes single-peaked in our densest models. The transition from
+double-peaked to single-peaked occurs when the line becomes optically
+thick. This reproduces the behaviour predicted by \cite{MC96}, who
+showed that the poloidal velocity gradient in the wind can modify the
+shape of optically thick emission lines even in the near-disk regime,
+where the poloidal velocity itself is much smaller than the rotational
+velocity. This has the effect of suppressing the line wings and
+can therefore lead to the production of a single-peaked line profile
+shape.
+
+In order to produce single-peaked line emission in the majority of
+lines at high inclinations, even higher opacity is needed in the
+line wings. This difficulty in generating single-peaked line emission
+from a rotating disk wind was also encountered by SDL05, who found
+that an outflow geometry similar to that adopted here could not 
+reproduce the observed single peaked profiles in YSOs. For the
+parameters we have tested, the mechanism proposed by \cite{MC96} does
+produce single-peaked profiles, but only for most optically thick
+emission lines. In order for the same mechanism to affect the majority
+of lines, even higher wind densities would be required.
+
+Figure~\ref{jump} shows the behaviour of the Balmer jump region as a
+function of the kinematic wind parameters. Here, we clearly see the
+critical effect of the emission measure, with the densest winds
+filling in the disk's Balmer absorption edge most effectively.
+\footnote{Note that the apparent absorption feature 
+just redward of the Balmer jump in these models is artificial. It is
+caused by residual line blanketing in the stellar atmospheres, which
+our models cannot fill in since they employ a 20-level Hydrogen atom.}
+This offers a potential solution to a long-standing problem in
+understanding the spectral energy distribution of CVs, as
+originally suggested by \cite{KLWB98}.
+
+Two other features are worth noting in this part of the
+spectrum. First, the collisionally excited Ca~{\sc ii} H\&K 
+emission lines at 3969\AA 
+and (especially) 3934\AA become quite prominent in our densest
+models. Second, {\em all} of our models predict a detectable
+He~\textsc{ii} recombination line at 3202\AA. This is the Helium
+equivalent of Paschen$\beta$ and should be expected in all systems that
+feature a strong He~\textsc{ii}~4686\AA line (the Helium
+equivalent of Paschen$\alpha$). This line is unfamiliar observationally,
+but only because it lies bluewards of the atmospheric cut-off, but
+also redwards of most ultraviolet spectra. 
+{\bf JM: should we reference something for this paper here}
 
@@
 Models towards the bottom right
-are have more slowly accelerating winds and denser wind bases. 
-% The middle right column
-% shows the variation with wider launch radii, and the right hand column shows 
-% how a boundary layer of increasing temperature affects the spectrum.
-% How the H$\alpha$ and H$\beta$ lines in our model change with the kinematic properties
-% of the wind. The three separate panels show three different values of $\dot{M}_W$, 
-% while $\alpha$ and $R_v$ are all gradually increased from top to bottom and left to right respectively.
-% Larger values of these quantities increase the density at the base of the wind. There is a clear transition
-% from double peaked to single peaked behaviour, and at the highest densities the wind
-% essentially becomes neutral as the optically thick regions self-shield the wind from photoionizing radiation.
-% \bf{Each of these figures will highlight the next gen model in bold.
-% and contain a grid like the above showing a pair of spectral features in
-% the left and right panels. The grey shaded line will show the benchmark model
-% for easy comparison.  
-% The most promising parameters at the moment are acceleration exponent and launch radii.}
-% }
-}
+are have more slowly accelerating winds and denser wind bases. }
 \label{halpha}
@@
 
-\subsection{The Balmer Jump}
-
-\label{balmerjump}
-
-The left panel of figure~\ref{jump} shows the evolution
-of the Balmer jump with our kinematic parameters. 
-The `absorption' feature just redward of the Balmer jump
-is artificial. It is caused by line blanketing in the stellar atmospheres,
-which is not filled in by line emission from the wind
-due to the use of a 20-level Hydrogen atom.
-The higher density models
-produce sufficient recombination continuum emission to fill 
-in the Balmer jump. This offers a potential solution to a 
-longstanding problem when reconciling theoretical
-models of NL spectra with observations, as originally suggested by
-\cite{KLWB98}. The fact that this emission is very sensitive to the parameters
-that govern the density at the wind base also supports
-the idea that a transition region close to the disk plane is necessary
-to explain the emission features present \citep{kd1997}.
-% \noindent\rule{16cm}{0.4pt}
-
-% {\bf
-% \noindent key points here:
-
-% \begin{itemize}
-% 	\item there is always recombination continuum emission from the wind, but it
-% 	only because significant w.r.t disk when the wind accelerates more slowly.
-% 	\item This higher density causes (too much) collisionally excited line emission from CIV
-% 	\item supports findings from the line profile shapes conclusions above...suggests
-% 	we need to alter the geometry in some respect, or find someway to suppress
-% 	collisionally excited line emission from UV lines?
-% 	\item perhaps one should increase the volume of the emitting area rather than the density,
-% 	although this will also cause more thermal line emission...
-% 	\item Bottom lines: filling in the Balmer jump can be done, and at the very minimum recombination
-% 	emission from the wind can matter, especially if we believe that the lines come from the wind. 
-% 	But to properly fill in the edge, one requires very high, possibly unrealistic, densities.
-% 	\item make clear that the edge originally comes from the stellar atmosphere, and that
-% 	the model we have used here is perhaps a little pessimistic.
-% 	\item We predict that the Balmer jump becomes deeper relative to the continuum 
-% 	\item This is probably due to foreshortening of the disk continuum but a fairly constant
-% 	escaping Balmer continuum.
-% \end{itemize}
-% }
-
-% \noindent\rule{16cm}{0.4pt}
+\subsection{Ultraviolet Wind Signatures}
+
+The dependence of the ultraviolet C~{\sc iv} and He~{\sc ii} lines on
+the same kinematic wind parameters is illustrated in Figures~\ref{BLA}
+and~\ref{BLA}. As before, we focus on the predicted behaviour at $i =
+80^\circ$. In our benchmark model, the C~{\sc iv} emission
+line seen at high inclinations is almost entirely produced via
+resonance scattering. The angle-averaged flux integrated over the
+entire line profile -- accounting correctly for the blue-shifted
+absorption component seen at low inclinations -- would be
+approximately zero. However, as we increase the density and extent of
+the slow-moving part of the outflow near the disk plane, collisionally
+excited emission starts to contribute significantly to the C~{\sc iv}
+line profiles. This explains the much stronger line-to-continuum
+contrast seen in the $\alpha = 1.5$, $R_v = 2\times 10^{11}$~cm model,
+for example. For any given inclination, the trend is not necessarily
+monotonic, however, because the escape probabilities from the
+line-forming region can be highly anisotropic.  
+{\bf CK: I *think* this is the basic reason, but (a) can you check
+  this, James; (b) is it enough to just point this out?; (c) do we
+  understand why CIV is single-peaked but HeII, for example, is double-peaked?}
+
+The He~{\sc ii}~1640\AA recombination line is always double-peaked in
+our models, although the peak-to-peak separation decreases in the
+denser models. For double-peaked lines
+formed in rotating media -- in this case, the dense base of the wind
+-- the location of the peak(s) is roughly associated with the
+projected rotational velocity at the outer edge of the line-forming
+region. Thus the trend observed in He~{\sc ii} reflect the radial
+expansion of the line-forming region associated with an increase in
+the density at the base of the wind. The same trend is actually also
+seen in the optical He~{\sc ii}~4686\AA line. The strength of these
+features relative to their adjacent continua also track
+each other approximately. The reason for the non-monotonic behaviour
+in the line strengths as a function of the kinematic wind parameters
+is the same as for the C~{\sc iv} line.
+{\bf CK: again, can we check this is correct?}
 
@@
 
-\subsection{The Boundary Layer and Ionization State of the wind}
-
-% fwoud
-
-% important points from Hoare and Drew paper
-% Zanstra method requires optically thick in He II Lyman continuum
-% recombination lines are optically thin
-% they note that He II n=2 edge opacity would cause more stringent limits. relevant to our edges.
-% %
-
-% {\bf 
-% \noindent key points here:
-
-% \begin{itemize}
-% 	\item we don't necessarily need a Boundary layer to ionize Helium II
-% 	\item a Boundary layer of 200,000K overionizes Carbon IV
-% 	\item we therefore favour lower boundary layer temperatures, as supported
-% 	by the upper limits of Hoare and Drew 1991.
-% 	\item we expect a boundary layer to matter more in lower accretion
-% 	rate systems.
-% \end{itemize}
-% }
-
-% \noindent\rule{16cm}{0.4pt}
-
-\begin{figure} %fullpage
-\mbox{
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_balmer.eps}}
-\quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_uv.eps}}   
-}
-%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
-\caption{The evolution of the Balmer jump and higher order Balmer lines (left) 
-and the \civfull\ line profile (right)
-with the kinematic properties of the wind,
-computed for an inclination of $80^\circ$. 
-the panels are organised in the same way as figure~\ref{halpha}.
-% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
-% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
-% when the wind becomes a neutral absorbing column.
-}
-\label{jump}
-\end{figure}
-
-We find in all our models that He II line emission is significant, and that 
-in most cases He  III is the dominant Helium ion in the wind, making recombination
-to He II an important process. This occurs without the presence of a boundary 
-layer. However, as a boundary layer is theoretically predicted 
-it is still important to investigate the effects of introducing
-one on the ionization state of the wind, and in particular
-the resultant line emission from \heiiuv, \heiiopt\ and \civfull. 
-We introduced blackbody boundary layers with temperatures between 80,000K and 200,000K,
-commonly proposed values in the literature, and adopt a luminosity of
-$L_{acc} / 2$. We find that the strength of the C\textsc{iv} line decreases
-with increasing boundary layer temperature. This can be seen
-in figures~\ref{jump}, and also in figure~\ref{bl_grid}, which
-shows the equivalent width of the \civfull\ and \heiiuv\ lines as 
-a function of $T_{bl}$.
-
-Our models favour cool or underluminous boundary layers,
-consistent with calculations carried out by
-\cite{hoaredrew1993}. However,
-it should be stressed that this result is extremely
-sensitive to the flux at the He \textsc{ii} and \civ\ 
-ionisation edges, so different disk or boundary layer
-SEDs would significantly impact this conclusion.
-For example, a slightly lower mass loss rate in the disk
-would permit a hotter boundary layer, and a modeled boundary layer
-would produce a softer spectrum for a given effective temperature
-(see e.g. Suleimanov 2014). Our main finding
-is therefore that a high accretion rate 
-($\dot{M}_{acc} \sim 10^{-8}~M_{\odot}yr^{-1}$) 
-system does not necessarily require a boundary layer to produce
-He \textsc{ii} recombination lines, but we are not
-able to rule out any range of temperatures or
-luminosities without better understanding of
-the accretion disk.
-
-% Our findings
-% are consistent with calculations carried out by
-% \cite{hoaredrew1993}. They find that a high accretion rate 
-% ($\dot{M}_{acc} \sim 10^{-8}~M_{\odot}yr^{-1}$) 
-% system does not necessarily require a boundary layer at all,
-% and favour cool or underluminous boundary layers
-% in order to explain the strengths of the \civ\ and N \textsc{v} 
-% resonance lines.
-% It is also possible that a flatter temperature profile in the disk,
-% as suggested by some eclipse mapping observations of NLs (References),
-% would cause a softer disk spectrum and allow a boundary layer 
-% with $T_{bl} = 200,000$K to exist without over-ionizing the wind.
-% There is an element of inconsistency with 
-% requiring flatter disk temperature profiles in order to permit
-% a hotter boundary layer, as the theoretical argument 
-% for the existence and likely temperature of a boundary layer has 
-% mostly been put together assuming a Shakura-Sunyaev disk.  
-% Radio emission has been seen in CVs, possibly implying the 
-% existence of a radio jet \cite[see e.g.][]{kordingDNjet2008,kording2011}.
-% A jet could extract some of the energy which is supposedly dissipated in the 
-% boundary layer, causing $L_{bl} < L_{acc}/2$, although
-% observations suggest the jet power would only be on the order
-% of $10\%$ of the accretion power. 
-% It is clear that more work is needed to understand
-
-% It is also instructive here to conduct a hypothetical 
-% Zanstra method calculation, following the method of \cite{hoare1991}. 
-% We adopt their definitions of the Zanstra ratios in the Helium lines (equations 5 and 6 
-% in their paper),
-
-% \begin{equation}
-% G (\lambda228, 1800 \AA) = 2.4\times 10^{-3} \frac{f(\lambda1640)}{f_*(1800\AA)}
-% \end{equation}
-% and
-
-% \begin{equation}
-% G (\lambda228, 1800 \AA) = 1.3\times 10^{-3} \frac{f(\lambda4686)}{f_*(1800\AA)}.\\
-% \end{equation}
-
-% Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$. (I NEED TO DO THE CALCULATION!).
-
-% Possible figure: CIV line equivalent width or ionization fraction
-% as a function of boundary layer temperature?
-
-% Discussion of Helium lines in the spectrum.
-% \begin{itemize}
-% \item He II 4686, He II 1640 strengths
-% \item Make the prediction that if 4686 is strong we might expect strong He II 3202. 
-% \item Discuss why it wouldn't have been seen yet (spectral coverage)
-% \item Helium I lines
-% \end{itemize}
-
-\begin{figure} 
-\mbox{
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/fig_EWt.eps}}
-
-}
-%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
-\caption{
-Equivalent widths of the \civfull\ and \heiiuv\ lines
-as a function of boundary layer temperature, for a viewing angle of $80^\circ$. The models used
-are identical to the benchmark model in geometry and kinematics.
-{\bf NOTE: The increase of He II line around 160kK is something we need to understand!}.
-% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
-% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
-% when the wind becomes a neutral absorbing column.
-}
-\label{bl_grid}
-\end{figure}
-
-% \noindent\rule{16cm}{0.4pt}
-
-% {\bf
-% \noindent Notes on Section 5:
-
-% \begin{itemize}
-% 	\item
-
-% \noindent Potential Additional Figures:
-
-% \begin{itemize}
-% 	\item 	
-% }
-
-% \noindent\rule{16cm}{0.4pt}
-
-% \subsection{UV Resonance Lines}
-% Compare spectra to LK02 and other models. Are the spectral features preserved, has anything significant changed.
-% Lyman alpha?
-
-% \subsection{Boundary Layer}
-% \begin{itemize}
-% \item discuss the effect of 80000K and 200000K Boundary layers
-% \item Particularly referring to He II and CIV
-% \item Our findings support idea that 200000K BL would over ionize the wind- 
-% we favour 80,000K
-% \item I'd like to do a hypothetical Zanstra calculation here- state what
-% temperature our model would predict from the Zanstra method
-% \end{itemize}
-
-%\subsubsection{The Line Force}
-%\begin{itemize}
-%\item Can this wind be radiatively driven? 
-%\item Why/why not?
-%\item Figure showing line force throughout the wind as a fraction of some critical value?
-%\end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{An Improved Optical Model }
+\section{A Revised Model Optimized for Optical Wavelengths}
 
@@
 \begin{tabular}{p{3cm}p{4cm}}
-Model B \\
+Revised Model (Optimized for the Optical Band)\\
 \hline Free Parameters 	&	 Value \\ 
@@
 \centering
-\caption{Wind geometry parameters used in the next-generation CV model.}
+\caption{Wind geometry parameters used in the next-generation CV
+  model. {\bf CK: I actually think we should probably have a single
+    table with both sets of model pars}}
 \label{modelb}
@@
 
-With modest changes to the kinematics of the benchmark CV model,
-it is possible to produce a model
-that comes closer to reproducing the observed optical spectrum
-of a NLs. The parameters for this model (imaginatively dubbed Model B)
-are show in table~\ref{modelb}, and the synthetic spectrum
-is shown in figure~\ref{uvoptb}. An in and out of eclipse comparison 
-between the synthetic spectrum
-at an angle of $80^\circ$ and the high-inclination NL RW Tri 
-is also shown in figure~\ref{rwtricomp}. The inclination
-for RW Tri has been disputed, with claimed values of $75^\circ$ \citep{groot2004},
-$70.5^\circ$ \citep{smak1995}, $80^\circ$ \citep{longmore1981} and 
-$82^\circ$\citep{frankking1981}. A lower inclination
-would mean that our model would simply require lower densities 
-and smaller emission regions to produce the required continuum level
-and single peaked emission, so our conclusions from this comparison are
-not particular sensitive to the value chosen.
-We also emphasize that this is no sense a fit to the data. The model
-is purely designed to reproduce the general behaviour of NLs
-and give an indication of the likely densities and kinematics 
-required in the wind.
-%quotes a figure of , whereas  halevinhenden2008
-
-The similarity with the observed spectrum is striking. 
-Model B produces strong emission in all the Balmer lines, 
-with line to continuum ratios
-comparable to those in RW Tri. 
-The line to continuum ratio increases during eclipse,
-as one expects if the emission is produced in a disk wind, 
-thereby mimicking the behaviour of SW Sex stars.
-The single-peaked \ha\ line is produced by our models with a 
-very similar width to the observed spectrum, although it is perhaps slightly more
-`flat-topped' in the synthesized data.
-
-One of the limitations of the model is that, apart 
-from in H$\alpha$, the lines are in general double-peaked. 
-The lack of high-resolution data in this regard makes detailed analysis difficult,
-but it would appear that understanding how single-peaked 
-line emission forms and the kinematics and densities required to
-modify the line profile is still an open question. 
-The major fallback of the next-generation model, however, lies
-in the ultraviolet. To get the required emission in the optical lines
-and recombination continuum the densities required are very high 
-($n_e\sim10^{13}-10^{14}$ in the main emission region).
-This causes a significant collisionally excited contribution
-to the UV lines, meaning that the red wing of the 
-resonance species such as C\textsc{iv} no longer matches the
-observed profiles.
+The benchmark model discussed in Section~\ref{BLA} was originally
+designed to reproduce the wind-formed lines seen in the UV spectra of
+high-state CVs. As we have seen, this model does produce significant
+amounts of optical emission. However, with only relatively minor
+changes to the kinematics of the benchmark model, it is possible to
+construct a model that more closely matches the observed {\em optical}
+spectra of CVs. Guided by the results of the previous section, we
+adopt the parameters listed in Table~\ref{BLA} for this purpose.
+
+Figure~\ref{uvoptb} shows the predicted UV and optical spectra for this
+optically optimized model for the full range of inclinations, and
+Figure~\ref{rwtricomp} shows a qualitative comparison of the predicted
+out-of-eclipse and mid-eclipse spectra against observations of the
+high-inclination nova-like RW~Tri. The inclination of RW Tri is
+somewhat uncertain, with estimates including $70.5^\circ$
+\citep{smak1995}, $75^\circ$ \citep{groot2004}, $80^\circ$
+\citep{longmore1981} and $82^\circ$\citep{frankking1981}. Here, we
+adopt $i = 80^\circ$, but our qualitative conclusions are not
+particular sensitive to this particular value. We emphasize that this
+model is in no sense a fit to this -- or any other -- data set.
+{\bf CK: strictly speaking, we should be talking about q=M2/M1 and disk
+  radius here as well I think, since those parameters affect the
+  amount and nature of any uneclipsed light just as much (sort of) as
+  the inclination. We should probably quote M2, q and R2/a in the
+  table, and we may want to say that we've adopted a q that is in line
+  with the observed eclipse width of RW Tri. (In Roche geometry,the
+  eclipse width -- the half-width at half out-of-eclipse intensity,
+  say -- depends solely on q and i). See e.g. Horne's paper or various
+  Dhillon et al. papers.}
+
+The similarity between the synthetic and observed spectra is
+striking. In particular, the revised model produces strong emission in
+all the Balmer lines, with line-to-continuum ratios comparable to
+those seen in RW Tri. Moreover, the line-to-continuum contrast
+increases during eclipse, as expected for emission produced in a disk
+wind. This trend is in line with the observations of RW~Tri, and it
+has also been seen in other NLs, including members of the SW~Sex class
+(REF)
+{\bf CK: I'm pretty sure that we know this about UX Uma, e.g. from
+  eclipse mapping studies, and there ought to be mid-eclipse spectra
+  of some additional system}
+The revised model also produes a single-peaked \ha\ line, in line with
+the observational data.
+
+However, there are also interesting differences between the revised
+model and the RW Tri data set. For example, H$\alpha$ is the only line
+that is single-peaked in the model, in contrast to what is seen in the
+observations. (However, the relatively low resolution of the RW Tri
+spectra makes this comparison difficult.) Moreover, the model exhibits
+considerably stronger He~{\sc ii} features than the observations,
+which suggests that the overall ionization state of the model is
+somewhat too high.
+
+However, perhaps the most serious problem for this optically optimized
+model is associated with its predicted UV spectra. In order to
+generate strong optical wind signatures, we have adopted wind
+parameters that lead to very high densities at the base of the wind
+($n_e\sim10^{13}-10^{14}$ in the main emission region). This produces
+the desired optical recombination emission, but also increases the
+role of collisional excitation in the formation of the UV resonance
+lines. This explains the pronounced increase in the emission component 
+of the C\textsc{iv} 1550\AA resonance line, for example, relative to
+what was seen in the benchmark model (compare Figures~\ref{BLA} and
+\ref{BLA}). The strength of this component in the revised model --
+especially at low and intermediate inclinations -- is probably
+somewhat too high to be consistent with UV observations of high-state
+CVs (REF).
 
@@
 
-By taking an already successful model
-for the UV wavelength regime of CVs and treating 
-it with an improved line transfer scheme, we have shown
-that the wind does produce some recombination lines
-and continuum emission blueward of the Balmer edge.
-We have confirmed a number of the expected behaviours
-by exploring a limited number of parameters governing the
-kinematics and geometry of the wind. These include:
-
+We have investigated whether a disk wind model designed to reproduce
+the UV spectra of high-state CVs would also have a significant effect
+on the optical spectra of these systems. We find that this is indeed
+the case. In particular, the model wind produces H and He
+recombination lines, as well as a recombination continuum blueward of
+the Balmer edge.
+
+We have also explored the dependence of the optical (and UV) wind
+signatures on some key kinematic wind parameters. Based on this, we
+show that recombination emission from outflows with sufficiently high
+densities and/or optical depths might 
 \renewcommand{\labelitemi}{$\bullet$}
 \begin{itemize}
-	\item The `filling-in' of the Balmer jump \citep{KLWB98} by recombination 
-	continuum emission from a disk wind
-	\item Single peaked line emission in \ha\ produced by 
-	the introduction of a poloidal velocity gradient \citep{MC96}
-	\item A Balmer decrement consistent with optically thick emission \citep{elitzur1983}.
+	\item fill in the Balmer absorption edge in the spectrum of
+          the accretion, thus accounting for absence of this edge in
+          observed CV spectra\citep{KLWB98};
+	\item produce the commonly observed single-peaked optical line
+          profiles \citep{MC96}
+	\item generate a flat Balmer decrement consistent with
+          optically thick emission \citep{elitzur1983}. 
+{\bf CK: actually, I don't think this last point is ever discussed in
+  the paper. I'd suggest removing it here or mentioning it briefly
+  earlier. Will leave this to you, James.}
 \end{itemize}
@@
 
-\noindent We also make a number of predictions:
-
+\noindent Based on our modelling, we can also make a number of basic,
+testable predictions for wind-formed signatures:
 \begin{itemize}
-	\item The depth of the Balmer absorption edge decreases with increasing inclination,
-or alternatively that the Balmer recombination emission
-is enhanced at higher inclinations, {\sl relative to the disk continuum}.
-	\item The He~\textsc{ii}~$\lambda3202{\rm \AA}$ line should be
-prominent in cases where He~\textsc{ii}~$\lambda1640{\rm \AA}$ \& 
-\heiiopt\ are seen. 
-	\item We expect Balmer jump in emission during eclipse.
+	\item we expect the depth of the Balmer absorption edge in CV
+          spectra to decrease with increasing inclination (with the
+          Balmer jump possibly switching to emission at the highest
+          inclinations, if the flux in the wind-formed recombination
+          continuum exceeds that of the foreshortened disk spectrum);
+	\item we predict that a strong He~\textsc{ii}~$\lambda3202{\rm
+          \AA}$ line should be prominent in all cases where
+          He~\textsc{ii}~$\lambda1640{\rm \AA}$ \& \heiiopt\ are seen
+          (but note that this prediction is not restricted to lines
+          formed in disk winds);
+	\item we predict that the Balmer jump should be in emission
+          during mid-eclipse in high inclination systems.
 \end{itemize}
@@
 \smallskip
-Our improved optical model produces all the prominent lines in and out of eclipse, and
-exhibits verisimilitude with the optical spectrum of RW Tri.
-However, this model does not produce a complete unified CV model. 
-The emission lines in the UV are somewhat unrealistic in strength,
-because the high densities needed to increase line opacity also produce
-a significant collisionally excited contribution..
-This is a shortcoming which must be understood if it is true that
-disk winds modify line profiles to become single peaked.
-% as the 
-%densities required produce a large amount of collisionally excited emission
-%in UV resonance lines.
-
-Our work demonstrates that, if nothing else,
-{\sl disk winds matter} in the optical. At a minimum,
-they can act as a spectral filter
-for the disk spectrum.
-%and the properties of the plasma
-%is an important tracer for the disk and boundary layer SEDs. 
-At a maximum, they may be responsible
-for the majority of optical spectral features of high-state CVs,
-and could dominate the appearance of both UV and optical
-spectra of these systems.
+We have also constructed a revised benchmark model which is designed
+to more closely match the optical spectra of high-state CVs. This
+optically optimized model produces all the prominent optical lines in
+and out of eclipse, and achieves reasonable verisimilitude with the
+observed optical spectra of RW Tri. However, this model also has
+significant shortcomings. In particular, it predicts
+stronger-than-observed He~{\sc ii} lines in the optical region and too
+much of a collisionally excited contribution to the UV resonance lines
+that
+
+Overall, our work demonstrates that {\sl disk winds matter}. They are
+not just responsible for creating the blue-shifted absorption and
+P-Cygni profiles seen in the UV resonance lines of high-state CVs, but
+can also have a strong effect on the optical appearance of these
+systems. In fact, most of the optical features characteristic of CVs
+are likely to be affected -- and possibly even dominated -- by their disk
+winds. Given that optical spectroscopy plays the central role in
+observational studies of CVs, it is clearly critical to know 
+where and how these spectra are actually formed. We believe it is high
+time for a renewed effort to understand the formation of spectra in
+accretion disks and associated outflows.
+
+{\bf CK: I just realized that -- apart from the intro -- we never
+  actually discuss the issue of P Cyg profiles in the optical
+  lines. These have been observed -- e.g. in Halpha -- but I guess we
+  never produce these? Do we know why? We probably should at least
+  comment on this at some point in the text, and possibly even briefly
+  in the conclusions.}
 

### 2014-12-03 draft.tex
added some more CK changes

@@
 optical spectra of high-state CVs. 
+{\bf NOTE JM: This abstract is a few lines longer than I would like- 
+I think something punchier is required.}
 \end{abstract}
@@
 are predicted to be double-peaked \citep{smak1981, hornemarsh1986}. 
-{\em Low-state} CVs (dwarf novae in quiescence) do, in fact,
-exhibit such double-peaked lines \citep{marshhorne1990}(MOREREF). 
-{\bf JM: Other things to consider; transition of line profiles
-from quiescence to outburst in DNe, emission lines in absorption cores
-trends of lines and continuum with inclination, flat
-Balmer decrement}.
-
-Murray \& Chiang (1996) have shown that the presence of disk winds may
+{\em Low-state} CVs (dwarf novae in quiescence) can, in fact,
+exhibit such double-peaked lines \citep{marshhorne1990}. 
+{\bf NOTEJM: I've included a reference to a paper on IP Peg here
+which shows the transition from double peaked lines in 
+quiescence and a contrast to outburst spectra. I'm not sure
+of general trends in DNe. A lot seem to have weak emission cores
+embedded in absorption.}
+
+Murray \& Chiang (1996; hereafter MC96)\nocite{MC96} 
+have shown that the presence of disk winds may
 offer a natural explanation for the single-peaked optical emission lines in
@@
 \end{equation}
-Here, the `starred' term on the right represents the Saha (LTE)
-abundances, in accordance with the notation of Mihalas (1982).  
+Here, the `starred' term on the right represents abundances computed with
+the Saha equation at temperature $T_R$, but using actual partition functions
+from the dilute blackbody approximation. 
 $W$ is an effective dilution factor, $\xi$ is the
@@
 \begin{equation}
-\frac{n_{jk}}{n_j} = W g_k \exp{-E_k/kT_R} / z_j(T_R),
+\frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R),
 \end{equation}
@@
 $<2$ agreement is encouraging. 
-{\bf CK: WHAT ARE THE PARTICULAR SETS OF PARAMETERS BEING ADOPTED HERE?}
+{\bf NOTE CK: WHAT ARE THE PARTICULAR SETS OF PARAMETERS BEING ADOPTED HERE?}
 }
@@
 $\dot{M}_{wind}$. 
-{\bf CK: I'm still not sure I understand the formula
+{\bf NOTE CK: I'm still not sure I understand the formula
   SV93 use to define $\phi$, and hence that this description is
@@
 conclusions. 
-{\bf CK: Is this true? Do we want to say anything else, e.g. that we'll
-     talk about this in a future paper?}
+{\bf NOTE CK: Is this true? Do we want to say anything else, e.g. that we'll
+talk about this in a future paper? JM: This is true. Anything up to 200kK
+still has optical lines. The He II behaviour is not monotnic. CIV drops
+gradually and gets a little overionized- but this is a separate topic really.
+The issue of clumping and BL and their affect on ionization could be a 
+future paper.}
 
@@
 are marked with dashed vertical lines.
-{\bf CK: this will need to be updated -- we want to show (just) the disk and
-  WD spectra...}
+{\bf JM: do we want to show the stellar atmosphere spectrum here?
+we know it looks a bit crap around the He II edge, so perhaps not...
  }
@@
 since the existence of a poloidal velocity {\em gradient} changes the
-local escape probabilities (Murray \& Chiang 1996). However, as
+local escape probabilities (MC96). However, as
 demonstrated explicitly in Section~\ref{BLA}, the line opacity in our
@@
 we would like to address: (i) under what conditions can disk winds
-produce {\em single-peaked} Balmer emission lines (Murray \& Chiang
-1996); (ii) can the wind-formed recombination continuum completely
+produce {\em single-peaked} Balmer emission lines (MC96); (ii) can the wind-formed recombination continuum completely
 fill in the disk's Balmer absorption edge for reasonable outflow
@@
 He~\textsc{ii} recombination line at 3202\AA. This is the Helium
-equivalent of Paschen$\beta$ and should be expected in all systems that
-feature a strong He~\textsc{ii}~4686\AA line (the Helium
-equivalent of Paschen$\alpha$). This line is unfamiliar observationally,
+equivalent of Paschen~$\beta$ and should be expected in all systems that
+feature a strong He~\textsc{ii}~4686\AA\ line (the Helium
+equivalent of Paschen~$\alpha$). This line is unfamiliar observationally,
 but only because it lies bluewards of the atmospheric cut-off, but
@@
 \quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_beta.eps}}   
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_4686.eps}}   
 }
 \caption{
-Line profiles for \ha\ (left) and \hb\ (right) with varying kinematic 
+Line profiles plotted in veliocity space 
+for \ha\ (left) and \heiiopt\ (right) with varying kinematic 
 properties, computed for an inclination of $80^\circ$.
@@
 The parameter that has been altered from the benchmark model 
-is marked in each column and row. 
-Models towards the bottom right
+is marked in each column and row. Models towards the bottom right
 are have more slowly accelerating winds and denser wind bases. }
 \label{halpha}
+\end{figure} %fullpage
+
+\begin{figure} %fullpage
+\centering
+\includegraphics[width=0.8\textwidth]{figures/3by3_grid_balmer.eps}  
+%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
+\caption{
+Line profiles for \civ\ (left) and \heiiuv\  (right) with varying kinematic 
+properties, computed for an inclination of $80^\circ$. 
+The panels are organised in the same way as figure~\ref{halpha}.
+% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
+% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
+% when the wind becomes a neutral absorbing column.
+}
+\label{uvlines}
 \end{figure} %fullpage
@@
 resonance scattering. The angle-averaged flux integrated over the
-entire line profile -- accounting correctly for the blue-shifted
-absorption component seen at low inclinations -- would be
+entire line profile - accounting correctly for the blue-shifted
+absorption component seen at low inclinations - would be
 approximately zero. However, as we increase the density and extent of
@@
 \mbox{
+\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_uv.eps}}
+\quad
 \subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_1640.eps}}   
-\quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_4686.eps}}   
 }
@@
 \caption{
-Line profiles for \heiiuv\ (left) and \heiiopt\  (right) with varying kinematic 
+Line profiles for \civ\ (left) and \heiiuv\  (right) with varying kinematic 
 properties, computed for an inclination of $80^\circ$. 
@@
 }
-\label{heiifig}
+\label{uvlines}
 \end{figure}

### 2014-12-03 generate/fig1_nl_spectra/eclipse_compare.py

@@ -121,9 +121,9 @@ ylim(0.1,40)
 # plot model
 scale = 2.718 / 0.036
 subplot(212)
-s = rd.read_spec_file("cv_alpha4_r4r12_mdot1e9_rv2e11_opt")
-plot( s.wavelength, smooth(s.spec[-3], window_len=10)*1e11*scale,  c=colour, linewidth=weight)
-plot( s.wavelength, smooth(s.spec[-2], window_len=10)*1e11*scale,  c=colour, linewidth=weight)
+s = rd.read_spec_file("cv_alpha4_r4r12_mdot1e9_rv1e11_opt")
+plot( s.wavelength, smooth(s.spec[-3], window_len=20)*1e11*scale,  c=colour, linewidth=weight)
+plot( s.wavelength, smooth(s.spec[-2], window_len=20)*1e11*scale,  c=colour, linewidth=weight)
 xlim(3700,6900)
 
 

### 2014-12-03 draft.tex
updated some figures

@@
 optical spectra of high-state CVs. 
-{\bf NOTE JM: This abstract is a few lines longer than I would like- 
+{\bf JM: This abstract is a few lines longer than I would like- 
 I think something punchier is required.}
@@
 exhibit such double-peaked lines \citep{marshhorne1990}. 
-{\bf NOTEJM: I've included a reference to a paper on IP Peg here
+{\bf JM: I've included a reference to a paper on IP Peg here
 which shows the transition from double peaked lines in 
@@
 \subsection{Ionization and Excitation: ``Simple Atoms''}
+\label{simpleatoms}
 
@@
 \caption{
-{\sl Top Panel:} Balmer decrements calculated with \py compared with analytic calculations
-by Seaton (1959), showing good agreement when calculating level emissivities in Hydrogen
-in the Case B limit.
+{\sl Top Panel:} ``Case B'' Balmer decrements computed 
+with \textsc{Python} compared to analytic calculations
+by Seaton (1959). Both calculations are calculated at $T_e=10,000$K.
 (see Osterbrock 1989 for a discussion of this commonly used approximation).
 {\sl Bottom Panel:}  a comparison of Helium I level populations (the most complex ion we currently 
-treat as a macro-atom) between \py~and \tar~models. Considering the 
-two codes use different atomic data and \textsc{Tardis,} unlike \textsc{Python,} currently has 
-a complete treatment of collisions between radiatively forbidden transitions, the factor of 
+treat as a macro-atom) between \py~and \tar~models. 
+The calculation is conducted with physical parameters of $n_e=5.96\times10^4$~cm$^{-3}$,
+$T_e=30,600$K, $T_R=43,482$K and $W=9.65\times10^{-5}$. 
+Considering the two codes use different atomic data and \textsc{Tardis,} unlike \textsc{Python,} currently has a complete treatment of collisions between 
+radiatively forbidden transitions, the factor of 
 $<2$ agreement is encouraging. 
-{\bf NOTE CK: WHAT ARE THE PARTICULAR SETS OF PARAMETERS BEING ADOPTED HERE?}
 }
@@
 \end{figure}
+
 \nocite{osterbrock}
@@
 \subsection{Wind Geometry and Kinematics}
+\label{kinematics}
 
@@
 $\dot{M}_{wind}$. 
-{\bf NOTE CK: I'm still not sure I understand the formula
+{\bf CK: I'm still not sure I understand the formula
   SV93 use to define $\phi$, and hence that this description is
@@
 \subsection{Sources and Sinks of Radiation}
+\label{radsources}
 
@@
 conclusions. 
-{\bf NOTE CK: Is this true? Do we want to say anything else, e.g. that we'll
+{\bf CK: Is this true? Do we want to say anything else, e.g. that we'll
 talk about this in a future paper? JM: This is true. Anything up to 200kK
@@
 \caption{
-The spectral energy distribution (SED) of the blackbody accretion
-disk used in the ionization calculation (black line), 
-with two boundary layer blackbody spectra also plotted.
+The spectral energy distribution (SED) of the 
+White Dwarf (dashed line) and blackbody accretion
+disk used in the ionization calculation (black solid line).
 The positions of the Hydrogen and Helium ionization edges 
-are marked with dashed vertical lines.
+are marked with vertical lines.
 {\bf JM: do we want to show the stellar atmosphere spectrum here?
 we know it looks a bit crap around the He II edge, so perhaps not...
+ }
  }
@@
 $T_{WD}$ 	 &	 $40,000$K\\
-$M_{2}$ 	 &	 $???? M_{\odot}$ \\ 
+$M_{2}$ 	 &	 $0.4 M_{\odot}$ \\ 
 $\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$\\ 
@@
 \caption{
-Parameters used for the geometry and kinematics of the benchmark CV model.}
+Parameters used for the geometry and kinematics of the benchmark CV model.
+{\bf JM: this needs some stuff adding, as is mentioned in certain places}}
 \label{wind_param}
@@
 \section{A Benchmark Disk Wind Model}
+\label{modela}
 
@@
 \subsection{Physical Structure and Ionization State}
+\label{modela_ionization}
+
+\begin{figure} %fullpage
+\includegraphics[width=\textwidth]{figures/fig5.eps}
+\caption{
+The physical properties of the wind- note the logarithmic scale. 
+Near the disk plane the wind is dense, with low poloidal velocities.
+As the wind accelerates it becomes less dense
+and more highly ionized. The dominant Helium ion
+is almost always He III, apart from in a small
+portion of the wind at the base, which is partially shielded
+from the inner disk.
+}
+\label{wind}
+\end{figure} %fullpage
 
@@
 and temperature with distance away from the disk, so any line
-formation process that scales as $n_e^2$ -- i.e. recombination and
-collisionally excited emission -- should be expected to operate
+formation process that scales as $n_e^2$ - i.e. recombination and
+collisionally excited emission - should be expected to operate
 primarily in the dense base of the outflow. Moreover, a comparison of
@@
 The ionization equation used in the ``simple atom'' approach used in
-LK02 (see Section~\ref{BLA}) should be a reasonable approximation to
+LK02 (see section~\ref{simpleatoms}) should be a reasonable approximation to
 the photoionization equilibrium in the benchmark wind model. Even
@@
 resulting ionization state of the wind to be quite similar to that
-found in LK02. The bottom panels in Figure~\ref{BL} confirm that this
+found in LK02. The bottom panels in figure~\ref{wind} confirm that this
 is the case. In particular, Helium is fully ionized
@@
 \subsection{Synthetic Spectra}
+\label{modela_spectrum}
 
@@
 the case, since the ionization state of the wind has not changed
-significantly from that computed in LK02 (see Section~\ref{BLA}). The
-left column of panels in Figure~\ref{spec} shows that this expectation
+significantly from that computed in LK02 (see section~\ref{modela_ionization}). 
+The left column of panels in figure~\ref{spec} shows that this expectation
 is met: all of the strong metal resonance
@@
 local escape probabilities (MC96). However, as
-demonstrated explicitly in Section~\ref{BLA}, the line opacity in our
+demonstrated explicitly in section~\ref{modelb}, the line opacity in our
 benchmark model is not high enough for this radiative transfer effect
@@
 
-\begin{figure} %fullpage
-\includegraphics[width=\textwidth]{figures/fig5.eps}
-\caption{
-The physical properties of the wind- note the logarithmic scale. 
-Near the disk plane the wind is dense, with low poloidal velocities.
-As the wind accelerates it becomes less dense
-and more highly ionized. The dominant Helium ion
-is almost always He III, apart from in a small
-portion of the wind at the base, which is partially shielded
-from the inner disk.
-}
-\label{wind}
-\end{figure} %fullpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{The Dependence of Wind Features on Outflow Parameters}
-
-The results of Section~\ref{BLA} show that wind models that reproduce
+\label{modelb}
+
+The results of section~\ref{modela} show that wind models that reproduce
 the UV spectral features of CVs are likely to leave a clear imprint on
@@
 law. We have therefore conducted a exploratory sensitivity study in
-which we focus on just two kinematic variables (Section~\ref{BLA}):
+which we focus on just two kinematic variables (section~\ref{kinematics}):
+
 \begin{itemize}
@@
 \subsection{Optical Wind Signatures}
-
-Figures~\ref{halpha} and~\ref{heii} show how the H$\alpha$ and 
+\label{modelb_opt}
+
+Figure~\ref{halpha} shows how the H$\alpha$ and 
 He~{\sc ii}~$\lambda 
@@
 also redwards of most ultraviolet spectra. 
-{\bf JM: should we reference something for this paper here}
+{\bf JM: we should we reference something here for the 3202 line. 
+I blieve CK found a paper which shows it in an IP? I'll try and find it.}
 
@@
 properties, computed for an inclination of $80^\circ$.
-The benchmark model is shown in the top left panel, and the improved optical
-model described in section 6 is highlighted in bold. 
+The benchmark model and the improved optical
+model described in section 6 are labeled as A and B respectively. 
+The $x$-axis limits correspond to the Keplerian velocity at 
+$4R_{WD}$, the inner edge of the wind.
 The parameter that has been altered from the benchmark model 
 is marked in each column and row. Models towards the bottom right
-are have more slowly accelerating winds and denser wind bases. }
+are have more slowly accelerating winds and denser wind bases. 
+{\bf JM: Need to discuss the `single-peaked-ness' of line profiles
+in our telecon.}
+}
 \label{halpha}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figures/3by3_grid_balmer.eps}  
+\includegraphics[width=1.0\textwidth]{figures/3by3_grid_balmer.eps}  
 %%\includegraphics[width=0.5\textwidth]{figures/test.eps}
 \caption{
-Line profiles for \civ\ (left) and \heiiuv\  (right) with varying kinematic 
+The evolution of the Balmer jump with varying kinematic 
 properties, computed for an inclination of $80^\circ$. 
@@
 }
-\label{uvlines}
+\label{jump}
 \end{figure} %fullpage
@@
 \subsection{Ultraviolet Wind Signatures}
+\label{modelb_uv}
 
 The dependence of the ultraviolet C~{\sc iv} and He~{\sc ii} lines on
-the same kinematic wind parameters is illustrated in Figures~\ref{BLA}
-and~\ref{BLA}. As before, we focus on the predicted behaviour at $i =
+the same kinematic wind parameters is illustrated in figures~\ref{uvlines}
+and~\ref{uvlines}. As before, we focus on the predicted behaviour at $i =
 80^\circ$. In our benchmark model, the C~{\sc iv} emission
@@
   this, James; (b) is it enough to just point this out?; (c) do we
-  understand why CIV is single-peaked but HeII, for example, is double-peaked?}
+  understand why CIV is single-peaked but HeII, for example, is double-peaked?
+  JM: There are still a few tests I want to do here- we can discuss in the telecon.
+  I believe He II v CIV shape is just due to CIV being produced in an extended region,
+  and generally scattered, whereas He II is produced close to the disk, and there's probably
+  also a line opacity effect.
+  I can check this.}
 
@@
 The panels are organised in the same way as figure~\ref{halpha}.
+{\bf JM: I need to adjust the smoothing here so for all plots I smooth
+in terms of Wavelength rather than bins. Linked to single-peaked discussion. 
+Note also CK may want a Lyman alpha plot, which I might put here}
 % The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
@@
     table with both sets of model pars}}
-\label{modelb}
+\label{modelb_table}
 \end{table}
 
-The benchmark model discussed in Section~\ref{BLA} was originally
+The benchmark model discussed in section~\ref{modela} was originally
 designed to reproduce the wind-formed lines seen in the UV spectra of
@@
 spectra of CVs. Guided by the results of the previous section, we
-adopt the parameters listed in Table~\ref{BLA} for this purpose.
+adopt the parameters listed in table~\ref{modelb_table} for this purpose.
 
@@
 of the C\textsc{iv} 1550\AA resonance line, for example, relative to
-what was seen in the benchmark model (compare Figures~\ref{BLA} and
-\ref{BLA}). The strength of this component in the revised model --
+what was seen in the benchmark model (compare figures~\ref{spec} and
+\ref{uvoptb}). The strength of this component in the revised model --
 especially at low and intermediate inclinations -- is probably
@@
           profiles \citep{MC96}
-	\item generate a flat Balmer decrement consistent with
-          optically thick emission \citep{elitzur1983}. 
-{\bf CK: actually, I don't think this last point is ever discussed in
-  the paper. I'd suggest removing it here or mentioning it briefly
-  earlier. Will leave this to you, James.}
 \end{itemize}
 \smallskip
+
+{\bf JM: I originally also had a note about the flat Balmer decrement here.
+it's potentially interesting and could be included, but would need a discussion
+earlier in the text.}
 

### 2014-12-04 draft.tex
Some more CK suggested changes, added refs, option to add Ly alpha figure

@@
 years on understanding and modelling these UV features (e.g. Drew \&
-Verbunt 1985; Mauche \& Raymond
-1987; Drew 1987; Shlosman \& Vitello 1993; [hereafter
+Verbunt 1985\nocite{drewverbunt1985}; Mauche \& Raymond
+1987\nocite{maucheraymond1987}; Drew 1987; Shlosman \& Vitello 1993; [hereafter
 SV93]\nocite{SV93}; Knigge, Woods \& Drew 1995 [hereafter
-KWD95]\nocite{KWD95}; Knigge \& Drew 1997; Knigge et al. 1997; Long \&
+KWD95]\nocite{KWD95}; Knigge \& Drew 1997\nocite{kd1997}; 
+Knigge et al. 1997\nocite{knigge1997}; Long \&
 Knigge 2002 [hereafter LK02]\nocite{LK02}, Noebauer et al. 2010;
-Puebla et al. 2011). The basic picture emerging from these efforts is
+Puebla et al. 2011\nocite{puebla2011}). The basic picture emerging from these efforts is
 of a slowly accelerating, moderately collimated bipolar
@@
 from isolated observations of P-Cygni-like line profiles even in optical
-lines, such as \ha\ and He \textsc{i} $\lambda5876$ \citep{RN98}.
-{\bf JM: need to mention this as pointed out by CK.}
+lines, such as \ha\ and He \textsc{i} $\lambda5876$ \citep{RN98, kafka2004}.
+{\bf JM: need to mention this later as pointed out by CK- both in discussion
+and conclusion sections.}
 
@@
 perhaps more realistically, as a stellar/disk atmosphere model
-(REF). In the latter case, the local surface gravity, $\log{g}(R)$, is
+(REF). 
+In the latter case, the local surface gravity, $\log{g}(R)$, is
 assumed to be set solely by the accreting WD, since self-gravity is
@@
 particular, the SEDs predicted by most stellar/disk atmosphere models 
-are too blue in the UV (REFs) and exhibit
-stronger-than-observed Balmer jumps in absorption (REFs). One possible
+are too blue in the UV \citep{wade1988,long1991,long1994}(Other refs here?) and exhibit
+stronger-than-observed Balmer jumps in absorption \cite{wade1984,haug1987,ladous1989b,knigge1998}(Other refs here?). One possible
 explanation for these problems is that these models fail to capture
@@
 \caption{Optical spectra of three nova-like variables: 
-RW Sex (Top; Beuermann et al. 1992),
-IX Vel (Middle; Beuermann \& Thomas 1990) %% CITE THESE
-and RW Tri in eclipse (Bottom; Groot et al. 2004).
+RW Sex (top; Beuermann et al. 1992),
+IX Vel (top middle; Beuermann \& Thomas 1990) 
+and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
 The data have been digitized from the respective publications and a few of the more
@@
 \nocite{groot2004}
+\nocite{beuermann1990}
+\nocite{beuermann1992}
 
@@
 and LK02 to simulate the UV spectrum of a typical high-state
-system. The specific parameters for this model are listed in
+system. The specific parameters for this model (Model A) are listed in
 Table~1. A key point is that the wind mass-loss rate in this model is
@@
 The thick black line shows the total 
-integrated escaping spectrum, while green and red lines show the contributions from photons that originate
-in the disk and wind respectively. Recombination continuum emission blueward of the Balmer 
+integrated escaping spectrum, while green and red lines show the contributions from photons that originate in the disk and wind respectively. 
+Recombination continuum emission blueward of the Balmer 
 edge is already prominent relative to other wind continuum processes, but is not sufficient
@@
 The panels are organised in the same way as figure~\ref{halpha}.
+{\bf JM: Mark lines here?}
 % The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
@@
 \mbox{
+% \subfigure{\includegraphics[width=0.33\textwidth]{figures/3by3_grid_lyman.eps}}  
+% \quad
 \subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_uv.eps}}
@@
 \begin{tabular}{p{3cm}p{4cm}}
-Revised Model (Optimized for the Optical Band)\\
+Model B\\
 \hline Free Parameters 	&	 Value \\ 
@@
 \centering
-\caption{Wind geometry parameters used in the next-generation CV
-  model. {\bf CK: I actually think we should probably have a single
+\caption{Wind geometry parameters used in the revised CV model, Model B,
+which is {\em optimized for the optical band}
+{\bf CK: I actually think we should probably have a single
 table with both sets of model pars}}
@@
 construct a model that more closely matches the observed {\em optical}
-spectra of CVs. Guided by the results of the previous section, we
+spectra of CVs (imaginatively dubbed `Model B'). Guided by the results of the previous section, we
 adopt the parameters listed in table~\ref{modelb_table} for this purpose.
@@
 has also been seen in other NLs, including members of the SW~Sex class
-(REF)
-{\bf CK: I'm pretty sure that we know this about UX Uma, e.g. from
+(REF) {\bf CK: I'm pretty sure that we know this about UX Uma, e.g. from
   eclipse mapping studies, and there ought to be mid-eclipse spectra

### 2014-12-04 draft.tex
MErged into one table

@@
 \centering
-\begin{tabular}{p{3cm}p{4cm}}
-Benchmark Model (Optimized for the UV Band) \\
-\hline Free Parameters 	&	 Value \\ 
+\begin{tabular}{p{2cm}p{2cm}p{2cm}}
+Model Parameters \\
+\hline Parameter 	&	 Model A  & Model B \\ 
 \hline \hline 
-$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
-$R_{WD}$ 	 &	 $7\times10^{8}$cm\\ 
-$T_{WD}$ 	 &	 $40,000$K\\
-$M_{2}$ 	 &	 $0.4 M_{\odot}$ \\ 
-$\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$\\ 
-$\dot{M}_{wind}$  &	$10^{-9}~M_{\odot}yr^{-1}$å\\ 
-$r_{min}$ 	&	 $4 R_{WD}$\\ 
-$r_{max}$ 	&	 $12 R_{WD}$ \\ 
-$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
-$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
-$\gamma$ 	&	 $1$ \\ 
-$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
+$M_{WD}$ 	 &	 $0.8 M_{\odot}$  &     \\ 
+$R_{WD}$ 	 &	 $7\times10^{8}$cm  & \\ 
+$T_{WD}$ 	 &	 $40,000$K        &  \\
+$M_{2}$ 	 &	 $0.6 M_{\odot}$  &   \\ 
+$\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$  &\\ 
+$\dot{M}_{wind}$  &	$10^{-9}~M_{\odot}yr^{-1}$å  & \\ 
+$r_{min}$ 	&	 $4 R_{WD}$ &  \\ 
+$r_{max}$ 	&	 $12 R_{WD}$  &  \\ 
+$\theta_{min}$ 	&	 $20.0^{\circ}$  &  \\ 
+$\theta_{max}$ 	&	 $65.0^{\circ}$  &  \\ 
+$\gamma$ 	&	 $1$  &  \\ 
+$v_{\infty}$ 	&	 $3v_{esc}$  &  \\ 
 %%$R_v$ 	        &	 $7\times10^{10}$cm \\ 
-$R_v$ 	        &	 $100 R_{WD}$ \\ 
-$\alpha$ 	&	 $1.5$ \\
+$R_v$ 	        &	 $100 R_{WD}$  &  $142.9 R_{WD}$  \\ 
+$\alpha$ 	&	 $1.5$   &   $4$\\
 \end{tabular}
@@
 \caption{
-Parameters used for the geometry and kinematics of the benchmark CV model.
+Parameters used for the geometry and kinematics of the benchmark 
+CV model (Model A), which is optimized for the UV band, and a model
+which is optimized for the optical band and described in section 6 (Model B).
+For Model B, only parameters which are altered are given - otherwise the
+Model A parameter is used.
 {\bf JM: this needs some stuff adding, as is mentioned in certain places}}
 \label{wind_param}
+\label{modelb_table}
 \end{table}
@@
 
-\begin{table}
-\centering
-\begin{tabular}{p{3cm}p{4cm}}
-Model B\\
-\hline Free Parameters 	&	 Value \\ 
-\hline \hline 
-$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
-$\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
-$\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
-$r_{min}$ 	&	 $4 R_{WD}$\\ 
-$r_{max}$ 	&	 $12 R_{WD}$ \\ 
-$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
-$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
-$\gamma$ 	&	 $1$ \\ 
-$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
-$R_v$ 	        &	 $142.9 R_{WD}$ \\ 
-$\alpha$ 	&	 $4$ \\
-\end{tabular}
-\centering
-\caption{Wind geometry parameters used in the revised CV model, Model B,
-which is {\em optimized for the optical band}
-{\bf CK: I actually think we should probably have a single
-table with both sets of model pars}}
-\label{modelb_table}
-\end{table}
+% \begin{table}
+% \centering
+% \begin{tabular}{p{3cm}p{4cm}}
+% Model B\\
+% \hline Free Parameters 	&	 Value \\ 
+% \hline \hline 
+% $M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
+% $\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
+% $\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
+% $r_{min}$ 	&	 $4 R_{WD}$\\ 
+% $r_{max}$ 	&	 $12 R_{WD}$ \\ 
+% $\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
+% $\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
+% $\gamma$ 	&	 $1$ \\ 
+% $v_{\infty}$ 	&	 $3v_{esc}$ \\ 
+% $R_v$ 	        &	 $142.9 R_{WD}$ \\ 
+% $\alpha$ 	&	 $4$ \\
+% \end{tabular}
+% \centering
+% \caption{Wind geometry parameters used in the revised CV model, Model B,
+% which is {\em optimized for the optical band}
+% {\bf CK: I actually think we should probably have a single
+% table with both sets of model pars}}
+% \label{modelb_table}
+% \end{table}
 

### 2014-12-08 draft.tex
restructured version a la KSL

@@
 imply the existence of powerful accretion disk winds in
-CVs, and considerable effort has gone into modelling UV line formation
-in such outflows. By contrast, much less attention has been paid to
-the potential impact of these disk winds on the {\em optical} spectra
-of CVs. Here, we use an improved version of our Monte Carlo ionization
+CVs.
+% and considerable effort has gone into modelling UV line formation
+% in such outflows. By contrast, much less attention has been paid to
+% the potential impact of these disk winds on the {\em optical} spectra
+% of CVs. 
+Here, we use an improved version of our Monte Carlo ionization
 and radiative transfer code to investigate whether disk wind models that
@@
 observationally significant recombination line and continuum emission
-in the optical waveband. In particular, we test whether outflows may 
+in the {\em optical} waveband.   
+In particular, we test whether outflows may 
 be responsible for the single-peaked emission line profiles often seen
@@
 We find that a standard disk wind model that is successful in
-reproducing the UV spectra of CVs does leave a noticeable imprint on
-the optical spectrum as well, particularly for systems viewed at high
+reproducing the UV spectra of CVs also leaves a noticeable imprint on
+the optical spectrum, particularly for systems viewed at high
 inclination. The strongest optical wind-formed recombinations lines are \ha\ and
@@
 this default wind model are double-peaked, and the effect of the wind
-on the Balmer jump is modest. We carry out a limited exploration of
-the disk wind parameter space, focusing on those parameters that affect the
-density near the base of the wind. This shows that higher-density
-outflows can produce both single-peaked emission lines and a
-recombination continuum sufficient to fill in the Balmer
-jump, although such models also tend to predict stronger-than-observed 
-collisionally excited UV emission lines. Our main conclusion is that
-disk wind emission is likely to have a significant impact on the
-optical spectra of high-state CVs. 
-{\bf JM: This abstract is a few lines longer than I would like- 
-I think something punchier is required.}
+on the Balmer jump is modest. 
+We demonstrate that a higher-density outflow model 
+displays reasonable verisimilitude with the optical spectrum of RW Trianguli,
+producing all the observed lines. In addition, this model
+can produce both single-peaked \ha\ emission and a
+recombination continuum sufficient to fill in the Balmer jump,
+although it also predicts stronger-than-observed 
+collisionally excited UV emission lines. 
+Our revised model also significantly
+alters the spectral shape of the continuum and displays
+a strong inclination dependence in its emission properties. 
+We explicitly demonstrate that the radial velocity shear 
+is responsible for single-peaked emission in our models, as predicted.
+On the basis of these results, we suggest that winds can 
+modify, and perhaps even dominate, the line and continuum emission
+from accreting systems.
+% We carry out a limited exploration of
+% the disk wind parameter space, focusing on those parameters that affect the
+% density near the base of the wind. This shows that higher-density
+% outflows can produce both single-peaked emission lines and a
+% recombination continuum sufficient to fill in the Balmer
+% jump, although such models also tend to predict stronger-than-observed 
+% collisionally excited UV emission lines. Our main conclusion is that
+% disk wind emission is likely to have a significant impact on the
+% optical spectra of high-state CVs. 
+% {\bf JM: This abstract is a few lines longer than I would like- 
+% I think something punchier is required.}
 \end{abstract}
@@
 \begin{figure} %fullpage
-\includegraphics[width=\textwidth]{figures/fig5_uv_opt.eps}
+\includegraphics[width=0.9\textwidth]{figures/modela_uv_opt.eps}
 \caption{
@@
 the benchmark model, and these do exhibit some emission lines
-associated with H and He. Since the emissivity of these recombination 
-features scales as $n_e^2$, they are formed almost entirely in the 
+associated with H and He. 
+We see a general trend from absorption lines to emission lines 
+with increasing inclination, as one might expect from our wind
+geometry. This trend is consistent with observations, as can be seen
+in Figure~1. However, it is clear that this particular model
+does not produce all the lines seen in observations of high-state CVs.
+The higher order Balmer series lines too weak
+to overcome the intrinsic absorption from the disk atmosphere, and the wind 
+fails to produce any emission at intermediate inclinations, 
+which contrasts with (for example) the observed behaviour of IX Vel
+\citep{beuermann1990}.
+
+The emissivity of these recombination 
+features scales as $n_e^2$, meaning that they form almost entirely in the 
 dense base of the wind, just above the accretion disk. Here, the
@@
 to dominate the line shapes.
-
-We also see a general trend from absorption lines to emission lines 
-with increasing inclination, as one might expect from our wind
-geometry. This trend is consistent with observations, as can be seen
-in Figure~1.
 
@@
 \begin{figure} 
-\includegraphics[width=0.45\textwidth]{figures/fig6_opt_cont.eps}
+\includegraphics[width=0.45\textwidth]{figures/modela_opt_cont.eps}
 \caption{Synthetic optical spectra computed for 
-sightlines of 22.5, 25, 62.5 and 80 degrees. In these plots
+sightlines of 10, 27.5, 45, 62.5 and 80 degrees. In these plots
 the flux is divided by a polynomial fit to the 
@@
 \begin{figure} 
-\includegraphics[width=0.5\textwidth]{figures/fig7_escaping.eps}
+\includegraphics[width=0.5\textwidth]{figures/modela_escaping.eps}
 \caption{Total packet-binned spectra across all viewing angles. 
@@
 
+\newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
-%          DISCUSSION
+%          REVISED MODEL
 %
@@
 
-\section{The Dependence of Wind Features on Outflow Parameters}
-\label{modelb}
-
-The results of section~\ref{modela} show that wind models that reproduce
-the UV spectral features of CVs are likely to leave a clear imprint on
-the optical spectrum. It is therefore important to understand the
-sensitivity of optical (and UV) wind-formed features to the basic
-properties of the outflow. In particular, there are two key questions
-we would like to address: (i) under what conditions can disk winds
-produce {\em single-peaked} Balmer emission lines (MC96); (ii) can the wind-formed recombination continuum completely
-fill in the disk's Balmer absorption edge for reasonable outflow
-parameters?
+\section{A Revised Model Optimized for Optical Wavelengths}
+
+The benchmark model discussed in section~\ref{modela} was originally
+designed to reproduce the wind-formed lines seen in the UV spectra of
+high-state CVs. As we have seen, this model does produce significant
+amounts of optical emission. However, with only relatively minor
+changes to the kinematics of the benchmark model, it is possible to
+construct a model that more closely matches the observed optical
+spectra of CVs (imaginatively dubbed `Model B').
+
+Specifically, we aim to assess a whether a revised model can:
+
+\begin{itemize}
+ 	\item account for all of the lines we see in optical spectra of CVs while preserving
+the UV behaviour;
+ 	\item produce {\em single-peaked} Balmer emission lines (MC96); 
+ 	\item generate enough of a wind-formed recombination continuum 
+to completely fill in the disk's Balmer absorption edge for 
+reasonable outflow parameters.
+\end{itemize}
 
@@
 primarily on the emission measure, $EM$, defined as
+
 \begin{equation}
@@
 \end{equation}
+
 where $n_i$ is the number density of the ion in question.    
@@
 \end{itemize}
+
 The general behaviour we might expect is that outflows with denser
-regions near the wind base -- i.e. winds with larger $R_{v}$ and/or
-larger $\alpha$ -- will produce stronger optical emission signatures. 
+regions near the wind base - i.e. winds with larger $R_{v}$ and/or
+larger $\alpha$ - will produce stronger optical emission signatures. 
 However, this behaviour may be moderated by the effect of the increasing
@@
 
-\subsection{Optical Wind Signatures}
-\label{modelb_opt}
-
-Figure~\ref{halpha} shows how the H$\alpha$ and 
-He~{\sc ii}~$\lambda 
-4686$ lines change with the kinematics of the wind for an inclination
-of $80^\circ$. The width and strength of He~{\sc ii} clearly depend on
-both $R_v$ and $\alpha$, but the overall line profile shape is always
-double-peaked. This contrasts with the behaviour of H$\alpha$, which
-becomes single-peaked in our densest models. The transition from
-double-peaked to single-peaked occurs when the line becomes optically
-thick. This reproduces the behaviour predicted by \cite{MC96}, who
-showed that the poloidal velocity gradient in the wind can modify the
-shape of optically thick emission lines even in the near-disk regime,
-where the poloidal velocity itself is much smaller than the rotational
-velocity. This has the effect of suppressing the line wings and
-can therefore lead to the production of a single-peaked line profile
-shape.
-
-In order to produce single-peaked line emission in the majority of
-lines at high inclinations, even higher opacity is needed in the
-line wings. This difficulty in generating single-peaked line emission
-from a rotating disk wind was also encountered by SDL05, who found
-that an outflow geometry similar to that adopted here could not 
-reproduce the observed single peaked profiles in YSOs. For the
-parameters we have tested, the mechanism proposed by \cite{MC96} does
-produce single-peaked profiles, but only for most optically thick
-emission lines. In order for the same mechanism to affect the majority
-of lines, even higher wind densities would be required.
-
-Figure~\ref{jump} shows the behaviour of the Balmer jump region as a
-function of the kinematic wind parameters. Here, we clearly see the
-critical effect of the emission measure, with the densest winds
-filling in the disk's Balmer absorption edge most effectively.
-\footnote{Note that the apparent absorption feature 
-just redward of the Balmer jump in these models is artificial. It is
-caused by residual line blanketing in the stellar atmospheres, which
-our models cannot fill in since they employ a 20-level Hydrogen atom.}
-This offers a potential solution to a long-standing problem in
-understanding the spectral energy distribution of CVs, as
-originally suggested by \cite{KLWB98}.
-
-Two other features are worth noting in this part of the
-spectrum. First, the collisionally excited Ca~{\sc ii} H\&K 
-emission lines at 3969\AA 
-and (especially) 3934\AA become quite prominent in our densest
-models. Second, {\em all} of our models predict a detectable
-He~\textsc{ii} recombination line at 3202\AA. This is the Helium
-equivalent of Paschen~$\beta$ and should be expected in all systems that
-feature a strong He~\textsc{ii}~4686\AA\ line (the Helium
-equivalent of Paschen~$\alpha$). This line is unfamiliar observationally,
-but only because it lies bluewards of the atmospheric cut-off, but
-also redwards of most ultraviolet spectra. 
-{\bf JM: we should we reference something here for the 3202 line. 
-I blieve CK found a paper which shows it in an IP? I'll try and find it.}
+We adopt the parameters listed in table~\ref{modelb_table}
+for our model, which best matches the observed optical spectra
+of high-state CVs. Some of the trends we observe in our 
+parameter search are discussed in section 6.
+Here, we discuss our revised model.
+
+\subsection{Synthetic Spectra}
 
 \begin{figure} %fullpage
-\mbox{
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_alpha.eps}}
-\quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_4686.eps}}   
-}
-\caption{
-Line profiles plotted in veliocity space 
-for \ha\ (left) and \heiiopt\ (right) with varying kinematic 
-properties, computed for an inclination of $80^\circ$.
-The benchmark model and the improved optical
-model described in section 6 are labeled as A and B respectively. 
-The $x$-axis limits correspond to the Keplerian velocity at 
-$4R_{WD}$, the inner edge of the wind.
-The parameter that has been altered from the benchmark model 
-is marked in each column and row. Models towards the bottom right
-are have more slowly accelerating winds and denser wind bases. 
-{\bf JM: Need to discuss the `single-peaked-ness' of line profiles
-in our telecon.}
-}
-\label{halpha}
-\end{figure} %fullpage
-
-\begin{figure} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/3by3_grid_balmer.eps}  
-%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
-\caption{
-The evolution of the Balmer jump with varying kinematic 
-properties, computed for an inclination of $80^\circ$. 
-The panels are organised in the same way as figure~\ref{halpha}.
-{\bf JM: Mark lines here?}
-% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
-% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
-% when the wind becomes a neutral absorbing column.
-}
-\label{jump}
-\end{figure} %fullpage
-
-\subsection{Ultraviolet Wind Signatures}
-\label{modelb_uv}
-
-The dependence of the ultraviolet C~{\sc iv} and He~{\sc ii} lines on
-the same kinematic wind parameters is illustrated in figures~\ref{uvlines}
-and~\ref{uvlines}. As before, we focus on the predicted behaviour at $i =
-80^\circ$. In our benchmark model, the C~{\sc iv} emission
-line seen at high inclinations is almost entirely produced via
-resonance scattering. The angle-averaged flux integrated over the
-entire line profile - accounting correctly for the blue-shifted
-absorption component seen at low inclinations - would be
-approximately zero. However, as we increase the density and extent of
-the slow-moving part of the outflow near the disk plane, collisionally
-excited emission starts to contribute significantly to the C~{\sc iv}
-line profiles. This explains the much stronger line-to-continuum
-contrast seen in the $\alpha = 1.5$, $R_v = 2\times 10^{11}$~cm model,
-for example. For any given inclination, the trend is not necessarily
-monotonic, however, because the escape probabilities from the
-line-forming region can be highly anisotropic.  
-{\bf CK: I *think* this is the basic reason, but (a) can you check
-  this, James; (b) is it enough to just point this out?; (c) do we
-  understand why CIV is single-peaked but HeII, for example, is double-peaked?
-  JM: There are still a few tests I want to do here- we can discuss in the telecon.
-  I believe He II v CIV shape is just due to CIV being produced in an extended region,
-  and generally scattered, whereas He II is produced close to the disk, and there's probably
-  also a line opacity effect.
-  I can check this.}
-
-The He~{\sc ii}~1640\AA recombination line is always double-peaked in
-our models, although the peak-to-peak separation decreases in the
-denser models. For double-peaked lines
-formed in rotating media -- in this case, the dense base of the wind
--- the location of the peak(s) is roughly associated with the
-projected rotational velocity at the outer edge of the line-forming
-region. Thus the trend observed in He~{\sc ii} reflect the radial
-expansion of the line-forming region associated with an increase in
-the density at the base of the wind. The same trend is actually also
-seen in the optical He~{\sc ii}~4686\AA line. The strength of these
-features relative to their adjacent continua also track
-each other approximately. The reason for the non-monotonic behaviour
-in the line strengths as a function of the kinematic wind parameters
-is the same as for the C~{\sc iv} line.
-{\bf CK: again, can we check this is correct?}
-
-\begin{figure} %fullpage
-\mbox{
-% \subfigure{\includegraphics[width=0.33\textwidth]{figures/3by3_grid_lyman.eps}}  
-% \quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_uv.eps}}
-\quad
-\subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_1640.eps}}  
-}
-%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
-\caption{
-Line profiles for \civ\ (left) and \heiiuv\  (right) with varying kinematic 
-properties, computed for an inclination of $80^\circ$. 
-The panels are organised in the same way as figure~\ref{halpha}.
-{\bf JM: I need to adjust the smoothing here so for all plots I smooth
-in terms of Wavelength rather than bins. Linked to single-peaked discussion. 
-Note also CK may want a Lyman alpha plot, which I might put here}
-% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
-% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
-% when the wind becomes a neutral absorbing column.
-}
-\label{uvlines}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%          Comparison with real spectra
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{A Revised Model Optimized for Optical Wavelengths}
-
-% \begin{table}
-% \centering
-% \begin{tabular}{p{3cm}p{4cm}}
-% Model B\\
-% \hline Free Parameters 	&	 Value \\ 
-% \hline \hline 
-% $M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
-% $\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
-% $\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
-% $r_{min}$ 	&	 $4 R_{WD}$\\ 
-% $r_{max}$ 	&	 $12 R_{WD}$ \\ 
-% $\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
-% $\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
-% $\gamma$ 	&	 $1$ \\ 
-% $v_{\infty}$ 	&	 $3v_{esc}$ \\ 
-% $R_v$ 	        &	 $142.9 R_{WD}$ \\ 
-% $\alpha$ 	&	 $4$ \\
-% \end{tabular}
-% \centering
-% \caption{Wind geometry parameters used in the revised CV model, Model B,
-% which is {\em optimized for the optical band}
-% {\bf CK: I actually think we should probably have a single
-% table with both sets of model pars}}
-% \label{modelb_table}
-% \end{table}
-
-The benchmark model discussed in section~\ref{modela} was originally
-designed to reproduce the wind-formed lines seen in the UV spectra of
-high-state CVs. As we have seen, this model does produce significant
-amounts of optical emission. However, with only relatively minor
-changes to the kinematics of the benchmark model, it is possible to
-construct a model that more closely matches the observed {\em optical}
-spectra of CVs (imaginatively dubbed `Model B'). Guided by the results of the previous section, we
-adopt the parameters listed in table~\ref{modelb_table} for this purpose.
-
-Figure~\ref{uvoptb} shows the predicted UV and optical spectra for this
-optically optimized model for the full range of inclinations, and
-Figure~\ref{rwtricomp} shows a qualitative comparison of the predicted
-out-of-eclipse and mid-eclipse spectra against observations of the
-high-inclination nova-like RW~Tri. The inclination of RW Tri is
-somewhat uncertain, with estimates including $70.5^\circ$
-\citep{smak1995}, $75^\circ$ \citep{groot2004}, $80^\circ$
-\citep{longmore1981} and $82^\circ$\citep{frankking1981}. Here, we
-adopt $i = 80^\circ$, but our qualitative conclusions are not
-particular sensitive to this particular value. We emphasize that this
-model is in no sense a fit to this -- or any other -- data set.
-{\bf CK: strictly speaking, we should be talking about q=M2/M1 and disk
-  radius here as well I think, since those parameters affect the
-  amount and nature of any uneclipsed light just as much (sort of) as
-  the inclination. We should probably quote M2, q and R2/a in the
-  table, and we may want to say that we've adopted a q that is in line
-  with the observed eclipse width of RW Tri. (In Roche geometry,the
-  eclipse width -- the half-width at half out-of-eclipse intensity,
-  say -- depends solely on q and i). See e.g. Horne's paper or various
-  Dhillon et al. papers.}
-
-The similarity between the synthetic and observed spectra is
-striking. In particular, the revised model produces strong emission in
-all the Balmer lines, with line-to-continuum ratios comparable to
-those seen in RW Tri. Moreover, the line-to-continuum contrast
-increases during eclipse, as expected for emission produced in a disk
-wind. This trend is in line with the observations of RW~Tri, and it
-has also been seen in other NLs, including members of the SW~Sex class
-(REF) {\bf CK: I'm pretty sure that we know this about UX Uma, e.g. from
-  eclipse mapping studies, and there ought to be mid-eclipse spectra
-  of some additional system}
-The revised model also produes a single-peaked \ha\ line, in line with
-the observational data.
-
-However, there are also interesting differences between the revised
-model and the RW Tri data set. For example, H$\alpha$ is the only line
-that is single-peaked in the model, in contrast to what is seen in the
-observations. (However, the relatively low resolution of the RW Tri
-spectra makes this comparison difficult.) Moreover, the model exhibits
-considerably stronger He~{\sc ii} features than the observations,
-which suggests that the overall ionization state of the model is
-somewhat too high.
-
-However, perhaps the most serious problem for this optically optimized
-model is associated with its predicted UV spectra. In order to
-generate strong optical wind signatures, we have adopted wind
-parameters that lead to very high densities at the base of the wind
-($n_e\sim10^{13}-10^{14}$ in the main emission region). This produces
-the desired optical recombination emission, but also increases the
-role of collisional excitation in the formation of the UV resonance
-lines. This explains the pronounced increase in the emission component 
-of the C\textsc{iv} 1550\AA resonance line, for example, relative to
-what was seen in the benchmark model (compare figures~\ref{spec} and
-\ref{uvoptb}). The strength of this component in the revised model --
-especially at low and intermediate inclinations -- is probably
-somewhat too high to be consistent with UV observations of high-state
-CVs (REF).
-
-\begin{figure} %fullpage
-\includegraphics[width=\textwidth]{figures/fig14_uv_opt.eps}
+\includegraphics[width=0.9\textwidth]{figures/modelb_uv_opt.eps}
 \caption{
@@
 
+\begin{figure} 
+\includegraphics[width=0.45\textwidth]{figures/modelb_opt_cont.eps}
+\caption{
+Synthetic optical spectra computed for 
+sightlines of 10, 27.5, 45, 62.5 and 80 degrees. In these plots
+the flux is divided by a polynomial fit to the 
+underlying continuum redward of the Balmer edge, so that 
+line-to-continuum ratios and the true depth of the
+Balmer jump can be shown.
+}
+\label{continuumb}
+\end{figure}
+
+\begin{figure} 
+\includegraphics[width=0.5\textwidth]{figures/modelb_escaping.eps}
+\caption{Total packet-binned spectra across all viewing angles. 
+The thick black line shows the total 
+integrated escaping spectrum, while green and red lines show the contributions from photons that originate in the disk and wind respectively. 
+Recombination continuum emission blueward of the Balmer 
+edge is already prominent relative to other wind continuum processes, but is not sufficient
+to fill in the Balmer jump in this specific model}
+\label{modelb_escape}
+\end{figure}
+
+Figure~\ref{uvoptb} shows the predicted UV and optical spectra for this
+optically optimized model for the full range of inclinations. 
+As expected, the trend from absorption to emission 
+in the optical is again present, but in this improved model we produce emission
+lines in the entire Balmer series at high inclinations, as well as the observed lines 
+in He~\textsc{ii} and He~\textsc{i}. This can be seen more clearly in the 
+continuum-divided spectrum in figure~\ref{continuumb}, with the lines marked
+(NOTE, mark these).
+
+Two other features are worth noting in the optical
+spectrum. First, the collisionally excited Ca~{\sc ii} H\&K 
+emission lines at 3969\AA\ and (especially) 3934\AA\ 
+become quite prominent in our densest models. Second, our model predicts a detectable
+He~\textsc{ii} recombination line at 3202\AA. This is the Helium
+equivalent of Paschen~$\beta$ and should be expected in all systems that
+feature a strong He~\textsc{ii}~4686\AA\ line (the Helium
+equivalent of Paschen~$\alpha$). Although it has been observed (REF),
+this line is somewhat unfamiliar observationally,
+but only because it lies bluewards of the atmospheric cut-off, but
+also redwards of most ultraviolet spectra. 
+% {\bf JM: we should we reference something here for the 3202 line. 
+% I blieve CK found a paper which shows it in an IP? I'll try and find it.}
+
+The wind now also has a clear effect on the continuum shape,
+as shown by figure~\ref{modelb_escape}. The majority of the
+escaping spectrum has now been reprocessed in some way by the wind,
+either by electron scattering (the wind is now moderately Thompson-thick),
+or by bound-free processes. This is demonstrated by the flatter spectral shape
+and the slight Helum photoabsorption edges present in the optical spectrum.
+In addition, figures~11 and 12 clearly demonstrate that the wind produces
+a recombination continuum sufficient to completely fill in the Balmer jump
+at high inclinations. \footnote{Note that the apparent absorption feature 
+just redward of the Balmer jump in these models is artificial. It is
+caused by residual line blanketing in the stellar atmospheres, which
+our models cannot fill in since they employ a 20-level Hydrogen atom.}
+This offers a potential solution to a long-standing problem in
+understanding the spectral energy distribution of CVs, as
+originally suggested by \cite{KLWB98}.
+
+In the UV, the model still produces all the observed lines, 
+and deep P-Cygni profiles are produced in the normal resonance lines,
+as discussed in section ??. However, the UV spectra also
+display what is perhaps the biggest problem with this revised model,
+namely the strength of resonance line emission 
+at low and intermediate inclinations.
+In order to generate strong optical wind signatures, we have adopted wind
+parameters that lead to very high densities at the base of the wind
+($n_e\sim10^{13}-10^{14}$ in the main emission region). This produces
+the desired optical recombination emission, but also increases the
+role of collisional excitation in the formation of the UV resonance
+lines. This explains the pronounced increase in the emission component 
+of the C\textsc{iv} 1550\AA resonance line, for example, relative to
+what was seen in the benchmark model (compare figures~\ref{spec} and
+\ref{uvoptb}). The strength of this component in the revised model 
+is probably somewhat too high to be consistent with UV observations 
+of high-state CVs (REF).
+
+\subsection{Comparison to RW Tri}
+
 \begin{figure} %fullpage
@@
 
-% \noindent\rule{16cm}{0.4pt}
-
-% {\bf
-% \noindent Notes on Section 6:
+Figure~\ref{rwtricomp} shows a qualitative comparison of the predicted
+out-of-eclipse and mid-eclipse spectra against observations of the
+high-inclination nova-like RW~Tri. The inclination of RW Tri is
+somewhat uncertain, with estimates including $70.5^\circ$
+\citep{smak1995}, $75^\circ$ \citep{groot2004}, $80^\circ$
+\citep{longmore1981} and $82^\circ$\citep{frankking1981}. Here, we
+adopt $i = 80^\circ$, but our qualitative conclusions are not
+particular sensitive to this particular value. We emphasize that this
+model is in no sense a fit to this - or any other - data set.
+
+% {\bf CK: strictly speaking, we should be talking about q=M2/M1 and disk
+%   radius here as well I think, since those parameters affect the
+%   amount and nature of any uneclipsed light just as much (sort of) as
+%   the inclination. We should probably quote M2, q and R2/a in the
+%   table, and we may want to say that we've adopted a q that is in line
+%   with the observed eclipse width of RW Tri. (In Roche geometry,the
+%   eclipse width -- the half-width at half out-of-eclipse intensity,
+%   say -- depends solely on q and i). See e.g. Horne's paper or various
+%   Dhillon et al. papers.}
+
+The similarity between the synthetic and observed spectra is
+striking. In particular, the revised model produces strong emission in
+all the Balmer lines, with line-to-continuum ratios comparable to
+those seen in RW Tri. Moreover, the line-to-continuum contrast
+increases during eclipse, as expected for emission produced in a disk
+wind. This trend is in line with the observations of RW~Tri, and it
+has also been seen in other NLs, including members of the SW~Sex class
+(REF) 
+% {\bf CK: I'm pretty sure that we know this about UX Uma, e.g. from
+%   eclipse mapping studies, and there ought to be mid-eclipse spectra
+%   of some additional system}
+The revised model also produes a single-peaked \ha\ line, in line with
+the observational data.
+
+There are also interesting differences between the revised
+model and the RW Tri data set. For example, H$\alpha$ is the only line
+that is single-peaked in the model, in contrast to what is seen in the
+observations. (However, the relatively low resolution of the RW Tri
+spectra makes this comparison difficult.) Moreover, the model exhibits
+considerably stronger He~{\sc ii} features than the observations,
+which suggests that the overall ionization state of the model is
+somewhat too high.
+
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%          DISCUSSION
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{The Dependence of Wind Features on Outflow Parameters}
+ Here we could discuss single-peaked emission and trends with parameters.
+% \label{modelb}
+
+% The results of section~\ref{modela} show that wind models that reproduce
+% the UV spectral features of CVs are likely to leave a clear imprint on
+% the optical spectrum. It is therefore important to understand the
+% sensitivity of optical (and UV) wind-formed features to the basic
+% properties of the outflow. In particular, there are three key questions
+% we would like to address: (i) can a modified wind model account 
+% for all of the lines we see in optical spectra of CVs while preserving
+% the UV behaviour;
+% (ii) under what conditions can disk winds
+% produce {\em single-peaked} Balmer emission lines (MC96); 
+% (ii) can the wind-formed recombination continuum completely
+% fill in the disk's Balmer absorption edge for reasonable outflow
+% parameters?
+
+% The amount of recombination and collisionally excited emission
+% produced by a given ion, $i$, in a plasma of volume $V$ depends
+% primarily on the emission measure, $EM$, defined as 
+% \begin{equation}
+% EM=\int^V_0 n_e n_i \,dV,
+% \end{equation}
+% where $n_i$ is the number density of the ion in question.    
+% The emission reaching an observer at a given frequency also depends on
+% the Sobolev optical depth it experiences, which depends on both the
+% density and the velocity gradient projected along the line of
+% sight. This can also significantly affect line profile shapes.
+
+% The simplest way to simultaneously affect the density in the wind as
+% well as the velocity gradients is by modifying the poloidal velocity
+% law. We have therefore conducted a exploratory sensitivity study in
+% which we focus on just two kinematic variables (section~\ref{kinematics}):
 
 % \begin{itemize}
-% 	\item
-
-% \noindent Potential Additional Figures:
-
-% \begin{itemize}
-% 	\item 	
+%  	\item the acceleration length, $R_v$, which controls the
+%         distance over which the wind accelerates to $\frac{1}{2}v_{\infty}$;
+%  	\item the acceleration exponent, $\alpha$, which controls the rate 
+%  	at which the poloidal velocity changes near $R_v$.
+% \end{itemize} 
+% The general behaviour we might expect is that outflows with denser
+% regions near the wind base -- i.e. winds with larger $R_{v}$ and/or
+% larger $\alpha$ -- will produce stronger optical emission signatures. 
+% However, this behaviour may be moderated by the effect of the increasing
+% optical depth through this region.
+
+% \subsection{Optical Wind Signatures}
+% \label{modelb_opt}
+
+% Figure~\ref{halpha} shows how overall spectrum
+% changes with the kinematics of the wind for an inclination
+% of $80^\circ$. The width and strength of He~{\sc ii} clearly depend on
+% both $R_v$ and $\alpha$, but the overall line profile shape is always
+% double-peaked. This contrasts with the behaviour of H$\alpha$, which
+% becomes single-peaked in our densest models. The transition from
+% double-peaked to single-peaked occurs when the line becomes optically
+% thick. This reproduces the behaviour predicted by \cite{MC96}, who
+% showed that the poloidal velocity gradient in the wind can modify the
+% shape of optically thick emission lines even in the near-disk regime,
+% where the poloidal velocity itself is much smaller than the rotational
+% velocity. This has the effect of suppressing the line wings and
+% can therefore lead to the production of a single-peaked line profile
+% shape.
+
+% Figure~\ref{halpha} shows how the H$\alpha$ and 
+% He~{\sc ii}~$\lambda 
+% 4686$ lines change with the kinematics of the wind for an inclination
+% of $80^\circ$. The width and strength of He~{\sc ii} clearly depend on
+% both $R_v$ and $\alpha$, but the overall line profile shape is always
+% double-peaked. This contrasts with the behaviour of H$\alpha$, which
+% becomes single-peaked in our densest models. The transition from
+% double-peaked to single-peaked occurs when the line becomes optically
+% thick. This reproduces the behaviour predicted by \cite{MC96}, who
+% showed that the poloidal velocity gradient in the wind can modify the
+% shape of optically thick emission lines even in the near-disk regime,
+% where the poloidal velocity itself is much smaller than the rotational
+% velocity. This has the effect of suppressing the line wings and
+% can therefore lead to the production of a single-peaked line profile
+% shape.
+
+% In order to produce single-peaked line emission in the majority of
+% lines at high inclinations, even higher opacity is needed in the
+% line wings. This difficulty in generating single-peaked line emission
+% from a rotating disk wind was also encountered by SDL05, who found
+% that an outflow geometry similar to that adopted here could not 
+% reproduce the observed single peaked profiles in YSOs. For the
+% parameters we have tested, the mechanism proposed by \cite{MC96} does
+% produce single-peaked profiles, but only for most optically thick
+% emission lines. In order for the same mechanism to affect the majority
+% of lines, even higher wind densities would be required.
+
+% Figure~\ref{jump} shows the behaviour of the Balmer jump region as a
+% function of the kinematic wind parameters. Here, we clearly see the
+% critical effect of the emission measure, with the densest winds
+% filling in the disk's Balmer absorption edge most effectively.
+% \footnote{Note that the apparent absorption feature 
+% just redward of the Balmer jump in these models is artificial. It is
+% caused by residual line blanketing in the stellar atmospheres, which
+% our models cannot fill in since they employ a 20-level Hydrogen atom.}
+% This offers a potential solution to a long-standing problem in
+% understanding the spectral energy distribution of CVs, as
+% originally suggested by \cite{KLWB98}.
+
+% Two other features are worth noting in this part of the
+% spectrum. First, the collisionally excited Ca~{\sc ii} H\&K 
+% emission lines at 3969\AA\ 
+% and (especially) 3934\AA\ become quite prominent in our densest
+% models. Second, {\em all} of our models predict a detectable
+% He~\textsc{ii} recombination line at 3202\AA. This is the Helium
+% equivalent of Paschen~$\beta$ and should be expected in all systems that
+% feature a strong He~\textsc{ii}~4686\AA\ line (the Helium
+% equivalent of Paschen~$\alpha$). This line is unfamiliar observationally,
+% but only because it lies bluewards of the atmospheric cut-off, but
+% also redwards of most ultraviolet spectra. 
+% {\bf JM: we should we reference something here for the 3202 line. 
+% I blieve CK found a paper which shows it in an IP? I'll try and find it.}
+
+% \begin{figure} %fullpage
+% \mbox{
+% \subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_alpha.eps}}
+% \quad
+% \subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_4686.eps}}   
 % }
-
-% \noindent\rule{16cm}{0.4pt}
+% \caption{
+% Line profiles plotted in veliocity space 
+% for \ha\ (left) and \heiiopt\ (right) with varying kinematic 
+% properties, computed for an inclination of $80^\circ$.
+% The benchmark model and the improved optical
+% model described in section 6 are labeled as A and B respectively. 
+% The $x$-axis limits correspond to the Keplerian velocity at 
+% $4R_{WD}$, the inner edge of the wind.
+% The parameter that has been altered from the benchmark model 
+% is marked in each column and row. Models towards the bottom right
+% are have more slowly accelerating winds and denser wind bases. 
+% {\bf JM: Need to discuss the `single-peaked-ness' of line profiles
+% in our telecon.}
+% }
+% \label{halpha}
+% \end{figure} %fullpage
+
+% \begin{figure} %fullpage
+% \centering
+% \includegraphics[width=1.0\textwidth]{figures/3by3_grid_balmer.eps}  
+% %%\includegraphics[width=0.5\textwidth]{figures/test.eps}
+% \caption{
+% The evolution of the Balmer jump with varying kinematic 
+% properties, computed for an inclination of $80^\circ$. 
+% The panels are organised in the same way as figure~\ref{halpha}.
+% {\bf JM: Mark lines here?}
+% % The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
+% % lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
+% % when the wind becomes a neutral absorbing column.
+% }
+% \label{jump}
+% \end{figure} %fullpage
+
+% \subsection{Ultraviolet Wind Signatures}
+% \label{modelb_uv}
+
+% The dependence of the ultraviolet C~{\sc iv} and He~{\sc ii} lines on
+% the same kinematic wind parameters is illustrated in figures~\ref{uvlines}
+% and~\ref{uvlines}. As before, we focus on the predicted behaviour at $i =
+% 80^\circ$. In our benchmark model, the C~{\sc iv} emission
+% line seen at high inclinations is almost entirely produced via
+% resonance scattering. The angle-averaged flux integrated over the
+% entire line profile - accounting correctly for the blue-shifted
+% absorption component seen at low inclinations - would be
+% approximately zero. However, as we increase the density and extent of
+% the slow-moving part of the outflow near the disk plane, collisionally
+% excited emission starts to contribute significantly to the C~{\sc iv}
+% line profiles. This explains the much stronger line-to-continuum
+% contrast seen in the $\alpha = 1.5$, $R_v = 2\times 10^{11}$~cm model,
+% for example. For any given inclination, the trend is not necessarily
+% monotonic, however, because the escape probabilities from the
+% line-forming region can be highly anisotropic.  
+% {\bf CK: I *think* this is the basic reason, but (a) can you check
+%   this, James; (b) is it enough to just point this out?; (c) do we
+%   understand why CIV is single-peaked but HeII, for example, is double-peaked?
+%   JM: There are still a few tests I want to do here- we can discuss in the telecon.
+%   I believe He II v CIV shape is just due to CIV being produced in an extended region,
+%   and generally scattered, whereas He II is produced close to the disk, and there's probably
+%   also a line opacity effect.
+%   I can check this.}
+
+% The He~{\sc ii}~1640\AA recombination line is always double-peaked in
+% our models, although the peak-to-peak separation decreases in the
+% denser models. For double-peaked lines
+% formed in rotating media -- in this case, the dense base of the wind
+% -- the location of the peak(s) is roughly associated with the
+% projected rotational velocity at the outer edge of the line-forming
+% region. Thus the trend observed in He~{\sc ii} reflect the radial
+% expansion of the line-forming region associated with an increase in
+% the density at the base of the wind. The same trend is actually also
+% seen in the optical He~{\sc ii}~4686\AA line. The strength of these
+% features relative to their adjacent continua also track
+% each other approximately. The reason for the non-monotonic behaviour
+% in the line strengths as a function of the kinematic wind parameters
+% is the same as for the C~{\sc iv} line.
+% {\bf CK: again, can we check this is correct?}
+
+% \begin{figure} %fullpage
+% \mbox{
+% % \subfigure{\includegraphics[width=0.33\textwidth]{figures/3by3_grid_lyman.eps}}  
+% % \quad
+% \subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_uv.eps}}
+% \quad
+% \subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_1640.eps}}  
+% }
+% %%\includegraphics[width=0.5\textwidth]{figures/test.eps}
+% \caption{
+% Line profiles for \civ\ (left) and \heiiuv\  (right) with varying kinematic 
+% properties, computed for an inclination of $80^\circ$. 
+% The panels are organised in the same way as figure~\ref{halpha}.
+% {\bf JM: I need to adjust the smoothing here so for all plots I smooth
+% in terms of Wavelength rather than bins. Linked to single-peaked discussion. 
+% Note also CK may want a Lyman alpha plot, which I might put here}
+% % The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
+% % lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
+% % when the wind becomes a neutral absorbing column.
+% }
+% \label{uvlines}
+% \end{figure}
 

### 2014-12-09 draft.tex
version sent to CK and KSL 141209

@@
 conclusions.
-{\bf CK: Is this true? Do we want to say anything else, e.g. that we'll
-talk about this in a future paper? JM: This is true. Anything up to 200kK
-still has optical lines. The He II behaviour is not monotnic. CIV drops
-gradually and gets a little overionized- but this is a separate topic really.
-The issue of clumping and BL and their affect on ionization could be a 
-future paper.}
 
@@
 and temperature with distance away from the disk, so any line
-formation process that scales as $n_e^2$ - i.e. recombination and
+formation process that scales as $\rho^2$ - i.e. recombination and
 collisionally excited emission - should be expected to operate
@@
 The emissivity of these recombination 
-features scales as $n_e^2$, meaning that they form almost entirely in the 
+features scales as $\rho^2$, meaning that they form almost entirely in the 
 dense base of the wind, just above the accretion disk. Here, the
@@
 equivalent of Paschen~$\alpha$). Although it has been observed (REF),
-this line is somewhat unfamiliar observationally,
-but only because it lies bluewards of the atmospheric cut-off, but
+this line is somewhat unfamiliar observationally. 
+This is because it lies bluewards of the atmospheric cut-off, but
 also redwards of most ultraviolet spectra. 
@@
 % I blieve CK found a paper which shows it in an IP? I'll try and find it.}
+
+In the UV, the model still produces all the observed lines, 
+and deep P-Cygni profiles are produced in the normal resonance lines,
+as discussed in section ??. However, the UV spectra also
+display what is perhaps the biggest problem with this revised model,
+namely the strength of resonance line emission 
+at low and intermediate inclinations.
+In order to generate strong optical wind signatures, we have adopted wind
+parameters that lead to very high densities at the base of the wind
+($n_e\sim10^{13}-10^{14}$ in the main emission region). This produces
+the desired optical recombination emission, but also increases the
+role of collisional excitation in the formation of the UV resonance
+lines. This explains the pronounced increase in the emission component 
+of the C\textsc{iv} 1550\AA\ resonance line, for example, relative to
+what was seen in the benchmark model (compare figures~\ref{spec} and
+\ref{uvoptb}). The strength of this component in the revised model 
+is probably somewhat too high to be consistent with UV observations 
+of high-state CVs (REF).
+
+\subsection{Continuum Shape and the Balmer Jump}
 
@@
 
-In the UV, the model still produces all the observed lines, 
-and deep P-Cygni profiles are produced in the normal resonance lines,
-as discussed in section ??. However, the UV spectra also
-display what is perhaps the biggest problem with this revised model,
-namely the strength of resonance line emission 
-at low and intermediate inclinations.
-In order to generate strong optical wind signatures, we have adopted wind
-parameters that lead to very high densities at the base of the wind
-($n_e\sim10^{13}-10^{14}$ in the main emission region). This produces
-the desired optical recombination emission, but also increases the
-role of collisional excitation in the formation of the UV resonance
-lines. This explains the pronounced increase in the emission component 
-of the C\textsc{iv} 1550\AA resonance line, for example, relative to
-what was seen in the benchmark model (compare figures~\ref{spec} and
-\ref{uvoptb}). The strength of this component in the revised model 
-is probably somewhat too high to be consistent with UV observations 
-of high-state CVs (REF).
+It has been noted by \cite{ladous1989, ladous1989b}
+that the Balmer jump in high-state CVs would naturally weaken at
+high inclinations due to limb darkening effects. 
+Although we include a simple limb darkening law which affects 
+the {\em total flux} seen at each incliantion, we cannot
+include it as an effect on the {\em opacities} in our model.
+As a result, the efficiency of filling in the Balmer jump
+should really be judged at low and medium inclinations, 
+where, although prominent, the recombination continuum does
+not overcome the disk atmosphere absorption. 
+In addition, this effect 
+could mean that any model which successfully fills in the 
+jump at low inclinations could lead to a Balmer jump 
+in emission at high inclinations.
+To understand this phenomenon, a fully self-consistent
+radiative transfer calculation of both the disk atmosphere
+and connected wind is required.
+
+\subsection{Line Profile Shapes: Producing Single-Peaked Emission}
+
+% Although \ha\ is single-peaked in our model, the majority of the
+% lines are double-peaked, particularly  
+Figure~\ref{halpha} shows how the H$\alpha$ and 
+% He~{\sc ii}~$\lambda 4686$ 
+line changes with the kinematics of the wind 
+for an inclination of $80^\circ$. The width and strength of He~{\sc ii} 
+clearly depend on both $R_v$ and $\alpha$, but the overall line profile 
+shape is always double-peaked. This contrasts with the behaviour of 
+H$\alpha$, which becomes single-peaked in our densest models. The transition from
+double-peaked to single-peaked occurs when the line becomes optically
+thick. This reproduces the behaviour predicted by \cite{MC96}, who
+showed that the poloidal velocity gradient in the wind can modify the
+shape of optically thick emission lines even in the near-disk regime,
+where the poloidal velocity itself is much smaller than the rotational
+velocity. This has the effect of suppressing the line wings and
+can therefore lead to the production of a single-peaked line profile
+shape.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figures/mc.eps}
+\caption{
+\ha\ line profiles, normalised to 1, plotted in veliocity space 
+for three models with varying kinematic 
+properties, computed at an inclination of $80^\circ$.
+The benchmark model and the improved optical
+model described in section 6 are labeled as A and B respectively,
+and a third model (X) which has an increased acceleration length of 
+$R_V = 283.8~R_{WD}$, and $\alpha=4$ is also shown. 
+The $x$-axis limits correspond to the Keplerian velocity at 
+$4R_{WD}$, the inner edge of the wind.
+We observe a transition from double to singl-peaked lines
+as the emission region becomes more optically thick.
+% The parameter that has been altered from the benchmark model 
+% is marked in each column and row. Models towards the bottom right
+% are have more slowly accelerating winds and denser wind bases. 
+% {\bf JM: Need to discuss the `single-peaked-ness' of line profiles
+% in our telecon.}
+}
+\label{halpha}
+\end{figure} %fullpage
 
@@
 \begin{figure} %fullpage
-\includegraphics[width=0.8\textwidth]{figures/fig13_eclipse.eps}
+\includegraphics[width=0.9\textwidth]{figures/fig13_eclipse.eps}
 \caption{{\sl Top Panel:} In and out of eclipse spectra of the high
@@
 %   of some additional system}
-The revised model also produes a single-peaked \ha\ line, in line with
-the observational data.
+% The revised model also produes a single-peaked \ha\ line, in line with
+% the observational data.
 
 There are also interesting differences between the revised
-model and the RW Tri data set. For example, H$\alpha$ is the only line
-that is single-peaked in the model, in contrast to what is seen in the
-observations. (However, the relatively low resolution of the RW Tri
-spectra makes this comparison difficult.) Moreover, the model exhibits
+model and the RW Tri data set. For example, the model exhibits
 considerably stronger He~{\sc ii} features than the observations,
@@
 somewhat too high. 
+As discussed in section 5.3, H$\alpha$ is the only line
+that is single-peaked in the model. This is
+in contrast to what is seen in the observations,
+although the relatively low resolution of the RW Tri
+spectra makes this comparison difficult.
 
@@
 
-\section{The Dependence of Wind Features on Outflow Parameters}
- Here we could discuss single-peaked emission and trends with parameters.
+% \section{The Dependence of Wind Features on Outflow Parameters}
+%  Here we could discuss single-peaked emission and trends with parameters.
 % \label{modelb}
@@
 % I blieve CK found a paper which shows it in an IP? I'll try and find it.}
-
-% \begin{figure} %fullpage
-% \mbox{
-% \subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_alpha.eps}}
-% \quad
-% \subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_4686.eps}}   
-% }
-% \caption{
-% Line profiles plotted in veliocity space 
-% for \ha\ (left) and \heiiopt\ (right) with varying kinematic 
-% properties, computed for an inclination of $80^\circ$.
-% The benchmark model and the improved optical
-% model described in section 6 are labeled as A and B respectively. 
-% The $x$-axis limits correspond to the Keplerian velocity at 
-% $4R_{WD}$, the inner edge of the wind.
-% The parameter that has been altered from the benchmark model 
-% is marked in each column and row. Models towards the bottom right
-% are have more slowly accelerating winds and denser wind bases. 
-% {\bf JM: Need to discuss the `single-peaked-ness' of line profiles
-% in our telecon.}
-% }
-% \label{halpha}
-% \end{figure} %fullpage
 
@@
 
-We have also explored the dependence of the optical (and UV) wind
-signatures on some key kinematic wind parameters. Based on this, we
+We have also constructed a revised benchmark model which is designed
+to more closely match the optical spectra of high-state CVs. This
+optically optimized model produces all the prominent optical lines in
+and out of eclipse, and achieves reasonable verisimilitude with the
+observed optical spectra of RW Tri. However, this model also has
+significant shortcomings. In particular, it predicts
+stronger-than-observed He~{\sc ii} lines in the optical region and too
+much of a collisionally excited contribution to the UV resonance lines
+that
+
+Based on this, we
 show that recombination emission from outflows with sufficiently high
 densities and/or optical depths might
+
 \renewcommand{\labelitemi}{$\bullet$}
@@
           the accretion, thus accounting for absence of this edge in
-          observed CV spectra\citep{KLWB98};
+          observed CV spectra \citep{KLWB98};
 	\item produce the commonly observed single-peaked optical line
@@
 
-{\bf JM: I originally also had a note about the flat Balmer decrement here.
-it's potentially interesting and could be included, but would need a discussion
-earlier in the text.}
-
-\noindent Based on our modelling, we can also make a number of basic,
+Although we note that limb darkening effects on disk atmosphere opacities
+would affect the Balmer jump. We can also make a number of basic,
+testable predictions for wind-formed signatures:
+
+% {\bf JM: I originally also had a note about the flat Balmer decrement here.
+% it's potentially interesting and could be included, but would need a discussion
+% earlier in the text.}
+
+\noindent We can also make a number of basic,
 testable predictions for wind-formed signatures:
@@
 \smallskip
-We have also constructed a revised benchmark model which is designed
-to more closely match the optical spectra of high-state CVs. This
-optically optimized model produces all the prominent optical lines in
-and out of eclipse, and achieves reasonable verisimilitude with the
-observed optical spectra of RW Tri. However, this model also has
-significant shortcomings. In particular, it predicts
-stronger-than-observed He~{\sc ii} lines in the optical region and too
-much of a collisionally excited contribution to the UV resonance lines
-that
 
@@
 
-{\bf CK: I just realized that -- apart from the intro -- we never
-actually discuss the issue of P Cyg profiles in the optical
-lines. These have been observed -- e.g. in Halpha -- but I guess we
-never produce these? Do we know why? We probably should at least
-comment on this at some point in the text, and possibly even briefly
-in the conclusions.}
+% {\bf CK: I just realized that -- apart from the intro -- we never
+% actually discuss the issue of P Cyg profiles in the optical
+% lines. These have been observed -- e.g. in Halpha -- but I guess we
+% never produce these? Do we know why? We probably should at least
+% comment on this at some point in the text, and possibly even briefly
+% in the conclusions.}
 
@@
 \subsection*{Acknowledgements}
-The work of JHM, NH and CK is supported by the Science and Technology Facilities Council (STFC), 
-via studentships and a consolidated grant, respectively. We would like to thank Juan Hernandez Santisteban and Ivan Hubeny 
-for useful discussions. We acknowledge the use of the IRIDIS High Performance Computing Facility, 
+The work of JHM and CK is supported by the Science and Technology Facilities Council (STFC), 
+via studentships and a consolidated grant, respectively. We would like to thank Juan Hernandez Santisteban, Samuel Mangham and Ivan Hubeny for useful discussions. 
+We acknowledge the use of the IRIDIS High Performance Computing Facility, 
 and associated support services at the University of Southampton, in the completion of this work.
 
-\newpage
-\newpage
 \bibliography{mybib.bib}

### 2014-12-16 draft.tex
about to change conclusions on single peaked lines

@@
 Knigge et al. 1997\nocite{knigge1997}; Long \&
-Knigge 2002 [hereafter LK02]\nocite{LK02}, Noebauer et al. 2010;
+Knigge 2002 [hereafter LK02]\nocite{LK02}, Noebauer et al. 2010\nocite{noebauer};
 Puebla et al. 2011\nocite{puebla2011}). The basic picture emerging from these efforts is
@@
 exhibit such double-peaked lines \citep{marshhorne1990}. 
-{\bf JM: I've included a reference to a paper on IP Peg here
-which shows the transition from double peaked lines in 
-quiescence and a contrast to outburst spectra. I'm not sure
-of general trends in DNe. A lot seem to have weak emission cores
-embedded in absorption.}
-
-Murray \& Chiang (1996; hereafter MC96)\nocite{MC96} 
+% {\bf JM: I've included a reference to a paper on IP Peg here
+% which shows the transition from double peaked lines in 
+% quiescence and a contrast to outburst spectra. I'm not sure
+% of general trends in DNe. A lot seem to have weak emission cores
+% embedded in absorption.}
+
+Murray \& Chiang (1996, 1997; hereafter MC96, MC97)\nocite{MC96, MC97} 
 have shown that the presence of disk winds may
@@
 perhaps more realistically, as a stellar/disk atmosphere model
-(REF). 
-In the latter case, the local surface gravity, $\log{g}(R)$, is
+(REF). In the latter case, the local surface gravity, $\log{g}(R)$, is
 assumed to be set solely by the accreting WD, since self-gravity is
@@
 are too blue in the UV \citep{wade1988,long1991,long1994}(Other refs here?) and exhibit
-stronger-than-observed Balmer jumps in absorption \cite{wade1984,haug1987,ladous1989b,knigge1998}(Other refs here?). One possible
+stronger-than-observed Balmer jumps in absorption 
+\citep{wade1984,haug1987,ladous1989b,knigge1998}. One possible
 explanation for these problems is that these models fail to capture
@@
 al. 1991;  but also more recent work by Idan et al. 2010).
-\nocite{idanshaviv2010} \nocite{shaviv1991}. However, an alternative 
-explanation, suggested by \cite{KLWB98}, is that recombination continuum
-emission from the base of the disk wind might fill in the disk's
+\nocite{idanshaviv2010} \nocite{shaviv1991}
+However, an alternative explanation, suggested by \cite{KLWB98}, 
+is that recombination continuum emission from the base of the 
+disk wind might fill in the disk's
 Balmer absorption edge and flatten the UV spectrum.
@@
 since the existence of a poloidal velocity {\em gradient} changes the
-local escape probabilities (MC96). However, as
+local escape probabilities (MC96, MC97). However, as
 demonstrated explicitly in section~\ref{modelb}, the line opacity in our
@@
 feature a strong He~\textsc{ii}~4686\AA\ line (the Helium
-equivalent of Paschen~$\alpha$). Although it has been observed (REF),
-this line is somewhat unfamiliar observationally. 
-This is because it lies bluewards of the atmospheric cut-off, but
+equivalent of Paschen~$\alpha$). 
+%%Although it has been observed (REF),
+This line is somewhat unfamiliar observationally, because it 
+lies bluewards of the atmospheric cut-off, but
 also redwards of most ultraviolet spectra. 
@@
 is probably somewhat too high to be consistent with UV observations 
-of high-state CVs (REF).
+of high-state CVs (see e.g. Long et al. 1991, 1994; Noebauer et al. 2010).
+\nocite{long1991,long1994, noebauer}
 
@@
 a recombination continuum sufficient to completely fill in the Balmer jump
-at high inclinations. \footnote{Note that the apparent absorption feature 
+at high inclinations.\footnote{Note that the apparent absorption feature 
 just redward of the Balmer jump in these models is artificial. It is
@@
 Although we include a simple limb darkening law which affects 
-the {\em total flux} seen at each incliantion, we cannot
-include it as an effect on the {\em opacities} in our model.
+the seen at each inclination, we cannot
+include it as a {\em frequency dependent} opacity in our model.
 As a result, the efficiency of filling in the Balmer jump
@@
 % lines are double-peaked, particularly  
-Figure~\ref{halpha} shows how the H$\alpha$ and 
+Figure~\ref{halpha} shows how the H$\alpha$
 % He~{\sc ii}~$\lambda 4686$ 
 line changes with the kinematics of the wind
-for an inclination of $80^\circ$. The width and strength of He~{\sc ii} 
-clearly depend on both $R_v$ and $\alpha$, but the overall line profile 
-shape is always double-peaked. This contrasts with the behaviour of 
-H$\alpha$, which becomes single-peaked in our densest models. The transition from
-double-peaked to single-peaked occurs when the line becomes optically
-thick. This reproduces the behaviour predicted by \cite{MC96}, who
+for an inclination of $80^\circ$. 
+% The width and strength of He~{\sc ii} 
+% clearly depend on both $R_v$ and $\alpha$, but the overall line profile 
+% shape is always double-peaked. This contrasts with the behaviour of 
+The line becomes single-peaked in our densest models. 
+The transition from double-peaked to single-peaked occurs when the 
+line becomes optically thick. This reproduces the behaviour predicted by MC96, who
 showed that the poloidal velocity gradient in the wind can modify the
@@
 $4R_{WD}$, the inner edge of the wind.
-We observe a transition from double to singl-peaked lines
+We observe a transition from double to single-peaked lines
 as the emission region becomes more optically thick.
@@
 has also been seen in other NLs, including members of the SW~Sex class
-(REF) 
+\citep{neustroev2011}.
 % {\bf CK: I'm pretty sure that we know this about UX Uma, e.g. from

### 2014-12-22 draft.tex
added pdf version to repo

@@
 Figure~\ref{wind} shows the physical and ionization structure 
-of the benchmark disk wind model. There is an obvious drop-off in density
+of the benchmark disk wind model. The ionization parameter shown in the bottom
+right panel is given by
+
+\begin{eqnarray}
+U&=&\frac{Q_H}{4\pi R^2 n_{H} c}\\ 
+  &=& \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}
+\end{eqnarray}
+
+where $\rm{Q_H}$ is the number of hydrogen-ionizing photons emitted by
+the illuminating source per second, $R$ is the distance to the source,
+$\rm{n_H}$ is the local hydrogen number density and $c$ is the speed of
+light. $J_\nu$ is the MC estimator for the mean intensity in the cell. 
+The ionization parameter is a useful measure
+of the ionization state of a plasma, as it evaluates the ratio 
+of the integrated ionizing radiation field and the local Hydrogen density.
+
+There is an obvious drop-off in density
 and temperature with distance away from the disk, so any line
@@
 	\item fill in the Balmer absorption edge in the spectrum of
-          the accretion, thus accounting for absence of this edge in
+          the accretion, thus accounting for the absence of a strong edge in
           observed CV spectra \citep{KLWB98};
 	\item produce the commonly observed single-peaked optical line
-          profiles \citep{MC96}
+          profiles (MC96)
 \end{itemize}

### 2014-12-22 generate/fig1_nl_spectra/plot_nl_figure.py

@@ -12,14 +12,18 @@ from pylab import *
 import os, sys
 from cobra_sub import smooth
 import read_output as rd
+import py_plot_util as util 
+
+util.parse_rcparams("../params.rc")
 rd.setpars()
 
 # some fontsizes for figure
 font1 = 16				# fontsize for x label
-font2 = 12				# fontsize for Y label
+font2 = 16				# fontsize for Y label
 font3 = 16				# fontsize for text on figures
 weight = 2			# lineweight
 
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
 
 
 # standard plot parameters for mnras
@@ -73,7 +77,7 @@ subplot(411)
 plot(x1,y1, c=colour ,linewidth=weight)
 semilogy()
 
-ylabel("Flux ($10^{-13}$~erg s$^{-1}$ cm$^{-3}$ \AA$^{-1}$)", fontsize = font2)
+ylabel("Flux\n($10^{-13}$~erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$)", fontsize = 12)
 text( 6000, 3.5,"RW Sex", fontsize = font3)
 
 lines = [5879,6680,
@@ -83,15 +87,27 @@ labels = [r"He~\textsc{i}",r"He~\textsc{i}",
           r"He~\textsc{ii}",r"He~\textsc{ii}",
           r"H$\alpha$",r"H$\beta$", r"H$\gamma$", r"H$\delta$"]
 
-vlines(lines,4.5,5, linewidth=2)
 
-i = 0
-for l in lines:
-	text(l+20, 5, labels[i])
-	i+=1
+gca().set_xticklabels([])
 
-ylim(1,6)
+# vlines(lines,4.5,5, linewidth=2)
+# i = 0
+# for l in lines:
+# 	text(l+20, 5, labels[i])
+# 	i+=1
+
+ylim(0.9,6.3)
+vlines([3646], 0.9,6.3, linestyle="--")
 xlim(3500,6900)
+
+majorFormatter = FormatStrFormatter('%d')
+majorLocator   = MultipleLocator(1)
+minorFormatter = FormatStrFormatter('%d')
+
+# ax.yaxis.set_major_locator(majorLocator)
+ax = gca()
+ax.yaxis.set_major_formatter(majorFormatter)
+ax.yaxis.set_major_locator(majorLocator)
 
 ##############
[…]

### 2014-12-22 generate/fig1_nl_spectra/plot2.py
removed generate to solve page build issue

@@ -1,204 +1,0 @@
-from constants import *
-import numpy as np
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import read_output as rd
-rd.setpars()
-
-def gauss(sigma, x0, x):
-
-	term = 1.0 / (2.0*np.pi) / sigma
-
-	exp_term = ( (x - x0)**2 )  /  (2.0*sigma*sigma)
-
-	term *= np.exp(-exp_term)
-
-	return term
-
-# def convolve(FWHM, x, y, mode="gaussian"):
-
-# 	'''
-# 	convolve arrays
-# 	'''
-
-# 	sigma = FWHM / (np.sqrt(8.0*np.log(2.0)))
-
-# 	n_points = len(x)
-
-# 	for i in range(n_points):
-
-def get_linelist(filenames, ionreturn=False):
-
-	lines = np.array([])
-	z = np.array([])
-
-	for i in range(len(filenames)):
-
-		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
-
-		lines = np.concatenate((lines, x[1]))
-
-		z = np.concatenate((z, x[0]))
-
-	if ionreturn:
-		return lines, z
-	else:
-		return lines
-
-
-
-
-
-
-
-# some fontsizes for figure
-font1 = 16				# fontsize for x label
-font2 = 16				# fontsize for Y label
-font3 = 16				# fontsize for text on figures
-weight = 1.5
-
-
-
-# standard plot parameters for mnras
-fig_width_pt=120.0 #Figure parameters
-inches_per_pt=1.0/72.27
-golden_mean=(math.sqrt(5)-1.0)/2.0
-fig_width=fig_width_pt*inches_per_pt
-fig_height=fig_width*golden_mean
-fig_size=(fig_width*8, fig_height*8)
-params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
-plt.rcParams.update(params)
-matplotlib.rcParams['ps.useafm'] = True
-matplotlib.rcParams['pdf.use14corefonts'] = True
-matplotlib.rcParams['text.usetex'] = True
-
-
-figure(figsize=fig_size)
[…]

### 2014-12-22 generate/fig1_nl_spectra/plot_nl_figure.py

@@ -1,240 +1,0 @@
-'''
-plot_nl_figure.py 
-
-This script creates the figure for the Nova like spectra
-in the 2014 CV paper. The data were scraped from Dexter.
-'''
-
-
-from constants import *
-import numpy as np
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import read_output as rd
-import py_plot_util as util 
-
-util.parse_rcparams("../params.rc")
-rd.setpars()
-
-# some fontsizes for figure
-font1 = 16				# fontsize for x label
-font2 = 16				# fontsize for Y label
-font3 = 16				# fontsize for text on figures
-weight = 2			# lineweight
-
-from matplotlib.ticker import MultipleLocator, FormatStrFormatter
-
-
-# standard plot parameters for mnras
-fig_width_pt=120.0 #Figure parameters
-inches_per_pt=1.0/72.27
-golden_mean=(math.sqrt(5)-1.0)/2.0
-fig_width=fig_width_pt*inches_per_pt
-fig_height=fig_width*golden_mean
-fig_size=(fig_width*8, fig_height*8)
-params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
-plt.rcParams.update(params)
-matplotlib.rcParams['ps.useafm'] = True
-matplotlib.rcParams['pdf.use14corefonts'] = True
-matplotlib.rcParams['text.usetex'] = True
-
-
-figure(figsize=fig_size)
-colour = "k"
-
-# read the RW Sex data
-x1,y1 = np.loadtxt("rwsex/data11.dat", unpack=True, comments="#", usecols=(0,1))
-
-# read the IX Vel daata
-x, y = np.loadtxt("ixvel/data2.dat", unpack=True, comments="#", usecols=(0,1))
-a,b = np.loadtxt("ixvel/data.dat", unpack=True, comments="#", usecols=(0,1))
-
-# read the RW Tri data 
-cc,dd = np.loadtxt("rwtri/new_eclipse.dat", unpack=True, comments="#", usecols=(0,1))
[…]

### 2014-12-22 generate/fig1_nl_spectra/salt.py

@@ -1,207 +1,0 @@
-from constants import *
-import numpy as np
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import read_output as rd
-rd.setpars()
-
-def gauss(sigma, x0, x):
-
-	term = 1.0 / (2.0*np.pi) / sigma
-
-	exp_term = ( (x - x0)**2 )  /  (2.0*sigma*sigma)
-
-	term *= np.exp(-exp_term)
-
-	return term
-
-# def convolve(FWHM, x, y, mode="gaussian"):
-
-# 	'''
-# 	convolve arrays
-# 	'''
-
-# 	sigma = FWHM / (np.sqrt(8.0*np.log(2.0)))
-
-# 	n_points = len(x)
-
-# 	for i in range(n_points):
-
-def get_linelist(filenames, ionreturn=False):
-
-	lines = np.array([])
-	z = np.array([])
-
-	for i in range(len(filenames)):
-
-		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
-
-		lines = np.concatenate((lines, x[1]))
-
-		z = np.concatenate((z, x[0]))
-
-	if ionreturn:
-		return lines, z
-	else:
-		return lines
-
-
-
-
-
-
-
-# some fontsizes for figure
-font1 = 16				# fontsize for x label
-font2 = 16				# fontsize for Y label
-font3 = 16				# fontsize for text on figures
-weight = 1.5
-
-
-
-# standard plot parameters for mnras
-fig_width_pt=120.0 #Figure parameters
-inches_per_pt=1.0/72.27
-golden_mean=(math.sqrt(5)-1.0)/2.0
-fig_width=fig_width_pt*inches_per_pt
-fig_height=fig_width*golden_mean
-fig_size=(fig_width*8, fig_height*8)
-params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
-plt.rcParams.update(params)
-matplotlib.rcParams['ps.useafm'] = True
-matplotlib.rcParams['pdf.use14corefonts'] = True
-matplotlib.rcParams['text.usetex'] = True
-
-
-figure(figsize=fig_size)
[…]

### 2015-01-13 draft.tex
added some generate folders, some text edits for line profiles and a git ignore

@@
 producing all the observed lines. In addition, this model
-can produce both single-peaked \ha\ emission and a
-recombination continuum sufficient to fill in the Balmer jump,
+produces recombination continuum sufficient to fill in the Balmer jump,
 although it also predicts stronger-than-observed 
@@
 a strong inclination dependence in its emission properties. 
-We explicitly demonstrate that the radial velocity shear 
-is responsible for single-peaked emission in our models, as predicted.
+No single-peaked emission is seen, although we observe a 
+narrowing of the double-peaked emission lines from the base of the wind. 
+We suggest that a non-homogenous, `clumpy' wind may provide a possible
+solution.
 On the basis of these results, we suggest that winds can 
@@
 accretion disk are important in shaping the ultraviolet (UV) spectra
-of high-state CVs (Heap 1978). The most spectacular evidence for such
+of high-state CVs \citep{heap1978, greensteinoke1982}. The most spectacular evidence for such
 outflows are the P-Cygni-like profiles seen in UV resonance lines such as
@@
 
-Murray \& Chiang (1996, 1997; hereafter MC96, MC97)\nocite{MC96, MC97} 
+Murray \& Chiang (1996, 1997; hereafter referred to collectively as MC96)\nocite{MC96, MC97} 
 have shown that the presence of disk winds may
@@
 from isolated observations of P-Cygni-like line profiles even in optical
-lines, such as \ha\ and He \textsc{i} $\lambda5876$ \citep{RN98, kafka2004}.
-{\bf JM: need to mention this later as pointed out by CK- both in discussion
-and conclusion sections.}
+lines, such as \ha\ and He \textsc{i} $\lambda5876$ \citep{patterson1996, RN98, kafka2004}.
 
@@
 of a (potentially wind-formed) recombination continuum in the eclipsed
-spectrum.}
+spectrum. We have attempted to show each spectrum over a similar dynamic range.
+}
 \label{novalikes}
@@
 
-\py is a Monte Carlo (MC) ionization and radiative transfer code which
+\py is a Monte Carlo  ionization and radiative transfer code which
 uses the Sobolev approximation to treat line transfer. It has already
@@
 done iteratively, by 
-propagating several populations of MC energy quanta (`photons')
+propagating several populations of Monte Carlo energy quanta (`photons')
 through a model wind. The geometric and kinemetic properties of the
@@
 provides a full non-local thermodynamic equilibrium (NLTE) solution
-for the level populations based on MC estimators. The macro-atom
+for the level populations based on Monte Carlo estimators. The macro-atom
 technique has already been used to model Wolf-Rayet star
@@
 given line photon will escape the Sobolev region. Finally, $J$ is the
-MC estimator for the mean intensity in the line, as recorded during
+Monte Carlo estimator for the mean intensity in the line, as recorded during
 the photon propagation. The corresponding excitation rate is then 
@@
 The adopted poloidal velocity law for various values of the
-acceleration exponent, $\alpha$.} 
+acceleration exponent, $\alpha$.
+{\bf JM: KSL has suggested we ditch this}
+} 
 \label{acc_law}
@@
 surface gravity and effective temperature. Here, we use blackbodies 
-during the ionization cycles and to compute our MC
+during the ionization cycles and to compute our Monte Carlo
 estimators. However, during the spectral synthesis stage of the 
@@
 are marked with vertical lines.
-{\bf JM: do we want to show the stellar atmosphere spectrum here?
-we know it looks a bit crap around the He II edge, so perhaps not...
- }
+{\bf JM: KSL has suggested we ditch this}
  }
@@
 $\rm{n_H}$ is the local hydrogen number density and $c$ is the speed of
-light. $J_\nu$ is the MC estimator for the mean intensity in the cell. 
+light. $J_\nu$ is the Monte Carlo estimator for the mean intensity in the cell. 
 The ionization parameter is a useful measure
@@
 
+Our models do not exhibit P-Cygni profiles in the optical lines.
+This is perhaps not surprising. LK02 and SV93 originally designed such models
+to reproduce the UV line profiles. Thus, most of the wind
+has an ionization parameter of $\log U \sim 2$ (see figure 6).
+This means Hydrogen and Helium are fully ionized throughout 
+much of the wind and is successful in producing recombination features.
+However, it leads to absorbing columns in \ha\ of $N_H\sim ??$ - far too
+low to produce noticeable blue shifted absorption. 
+While we suspect that the winds that exhibit such profiles must 
+lie in a different ionization regime, requiring 
+significantly different disk SEDs or mass-loss rates to a 
+`standard' high-state CV. However, we note it is difficult for this
+idea to exist within a line-driven wind framework.
+
 The emissivity of these recombination 
@@
 since the existence of a poloidal velocity {\em gradient} changes the
-local escape probabilities (MC96, MC97). However, as
-demonstrated explicitly in section~\ref{modelb}, the line opacity in our
-benchmark model is not high enough for this radiative transfer effect
+local escape probabilities (MC96). However, as
+discussed further in section~\ref{modelb}, the 
+radial velocity shear in our
+models is not high enough for this radiative transfer effect
 to dominate the line shapes.
@@
 and deep P-Cygni profiles are produced in the normal resonance lines,
-as discussed in section ??. However, the UV spectra also
+as discussed in section 4.2. However, the UV spectra also
 display what is perhaps the biggest problem with this revised model,
@@
 
+Figure~\ref{halpha} shows how the H$\alpha$
+line changes with the kinematics of the wind
+for an inclination of $80^\circ$. 
+The line narrows as the models move towards denser,
+more slowly accelerating winds. 
+This is due
+the base of the wind becoming optically thick such 
+that line emission cannot escape. This means
+what is effectively a photosphere for the line moves 
+to a greater vertical distance from the disk plane,
+where rotational velocities drop off as $1/r$. 
+The narrowing of the line is {\em not} due to the radial velocity shear
+mechanism proposed by MC96.
+The main criterion for this mechanism is
+
+\begin{equation}
+\frac{dv_p}{dr} > \frac{dv_\phi}{ds}\,
+\end{equation}
+
+where $v_p$ is the poloidal velocity and $v_\phi$
+is the Keplerian velocity.
+This criterion is simply not satisfied in the emission region of our models.
+
+There are two possible ways in which the model
+could be altered to better reproduce single-peaked
+lines as a result of radial velocity shear. First,
+one could adopt a more equatorial wind geometry. 
+This would increase the velocity gradient in the radial 
+direction. However, CV winds are known to be moderately collimated.
+This is demonstrated by the fact that blue-shifted resonance line 
+absorption is seen in low inclination systems such as RW Sex \citep{greensteinoke1982},
+but not in eclipsing systems \citep{cordovamason1985}.
+Furthermore, the main reason for adopting this type of 
+wind geometry is that it already successfully models the 
+P-Cygni resonance lines seen in the UV (LK02, Noebauer et al. 2010),
+We note that equatorial winds are expected in AGN and X-ray binaries 
+\citep{ponti2012}, and that these winds may be more likely
+to exhibit the required kinematics.
+Second, one could adopt velocity laws with higher 
+velocity gradients in the line emission region. 
+However, this poses problems for a smooth biconical wind. 
+We have already demonstrated that high densities are required 
+to produce significant emission. In a smooth model, which
+satisfies the mass continuity condition (see section 3.1), 
+it is therefore difficult to reconcile 
+these high densities with the high velocity gradients required.
+
+We suggest that clumping
+in CV winds provides a possible solution.
+Non-homogeneity could allow higher density pockets 
+of emission to exist with radial velocity shear still being high.
+Line-driven winds are expected to be unstable (REFS),
+and a number of implementations have been used in the stellar wind
+community (REFS). We therefore hope that further investigation of
+clumped winds could help solve the current `mystery' of single-peaked 
+line emission in high inclination systems.
+
 % Although \ha\ is single-peaked in our model, the majority of the
 % lines are double-peaked, particularly  
-Figure~\ref{halpha} shows how the H$\alpha$
-% He~{\sc ii}~$\lambda 4686$ 
-line changes with the kinematics of the wind
-for an inclination of $80^\circ$. 
-% The width and strength of He~{\sc ii} 
-% clearly depend on both $R_v$ and $\alpha$, but the overall line profile 
-% shape is always double-peaked. This contrasts with the behaviour of 
-The line becomes single-peaked in our densest models. 
-The transition from double-peaked to single-peaked occurs when the 
-line becomes optically thick. This reproduces the behaviour predicted by MC96, who
-showed that the poloidal velocity gradient in the wind can modify the
-shape of optically thick emission lines even in the near-disk regime,
-where the poloidal velocity itself is much smaller than the rotational
-velocity. This has the effect of suppressing the line wings and
-can therefore lead to the production of a single-peaked line profile
-shape.
+% Figure~\ref{halpha} shows how the H$\alpha$
+% % He~{\sc ii}~$\lambda 4686$ 
+% line changes with the kinematics of the wind
+% for an inclination of $80^\circ$. 
+% % The width and strength of He~{\sc ii} 
+% % clearly depend on both $R_v$ and $\alpha$, but the overall line profile 
+% % shape is always double-peaked. This contrasts with the behaviour of 
+% The line becomes single-peaked in our densest models. 
+% The transition from double-peaked to single-peaked occurs when the 
+% line becomes optically thick. This reproduces the behaviour predicted by fsingle-pe96, who
+% showed that the poloidal velocity gradient in the wind can modify the
+% shape of optically thick emission lines even in the near-disk regime,
+% where the poloidal velocity itself is much smaller than the rotational
+% velocity. This has the effect of suppressing the line wings and
+% can therefore lead to the production of a single-peaked line profile
+% shape.
 
@@
 $4R_{WD}$, the inner edge of the wind.
-We observe a transition from double to single-peaked lines
-as the emission region becomes more optically thick.
+We observe a narrowing of the lines
+but this is not due to the radial velocity shear mechanism (see section 5.3
+for a discussion).
 % The parameter that has been altered from the benchmark model 
@@
 somewhat too high. 
-As discussed in section 5.3, H$\alpha$ is the only line
-that is single-peaked in the model. This is
-in contrast to what is seen in the observations,
-although the relatively low resolution of the RW Tri
-spectra makes this comparison difficult.
+As discussed in section 5.3, the optical lines are
+narrow. This is in contrast to what is generally seen in observations
+of NLs, although the relatively low resolution of the RW Tri
+spectra makes a specific comparison difficult.
 
@@
 recombination lines, as well as a recombination continuum blueward of
-the Balmer edge.
+the Balmer edge. We do not produce P-Cygni profiles
+in the optical H and He lines, 
+which are seen in a small fraction of CV optical spectra.
+Possible reasons for this are briefly discussed in section 
+4.2.
 
@@
 
-Based on this, we
-show that recombination emission from outflows with sufficiently high
-densities and/or optical depths might
+Based on this, we show that recombination emission 
+from outflows with sufficiently high densities and/or optical depths might
 
@@
           observed CV spectra \citep{KLWB98};
-	\item produce the commonly observed single-peaked optical line
-          profiles (MC96)
+	\item produce the optical lines observed in CVs.
 \end{itemize}
@@
 Although we note that limb darkening effects on disk atmosphere opacities
-would affect the Balmer jump. We can also make a number of basic,
-testable predictions for wind-formed signatures:
+would affect the Balmer jump (see section 5.2). In section 5.3, we demonstrate that
+although single-peaked emission can be formed in our densest models, 
+it is not due to the radial velocity shear mechanism proposed by MC96.
+The emission in our models which produce single-peaked lines comes from
+approximately $10^{11}$~cm above the disk plane, which is not supported
+by eclipse-mapping observations (REFS). We suggest
+that non-homogenous, 
+`clumpy' line-driven winds may offer a potential solution.
 

### 2015-01-13 generate/fig1_nl_spectra1/eclipse_compare.py

@@ -1,0 +1,204 @@
+from constants import *
+import numpy as np
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import read_output as rd
+rd.setpars()
+
+def gauss(sigma, x0, x):
+
+	term = 1.0 / (2.0*np.pi) / sigma
+
+	exp_term = ( (x - x0)**2 )  /  (2.0*sigma*sigma)
+
+	term *= np.exp(-exp_term)
+
+	return term
+
+# def convolve(FWHM, x, y, mode="gaussian"):
+
+# 	'''
+# 	convolve arrays
+# 	'''
+
+# 	sigma = FWHM / (np.sqrt(8.0*np.log(2.0)))
+
+# 	n_points = len(x)
+
+# 	for i in range(n_points):
+
+def get_linelist(filenames, ionreturn=False):
+
+	lines = np.array([])
+	z = np.array([])
+
+	for i in range(len(filenames)):
+
+		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
+
+		lines = np.concatenate((lines, x[1]))
+
+		z = np.concatenate((z, x[0]))
+
+	if ionreturn:
+		return lines, z
+	else:
+		return lines
+
+
+
+
+
+
+
+# some fontsizes for figure
+font1 = 16				# fontsize for x label
+font2 = 16				# fontsize for Y label
+font3 = 16				# fontsize for text on figures
+weight = 1.5
+
+
+
+# standard plot parameters for mnras
+fig_width_pt=120.0 #Figure parameters
+inches_per_pt=1.0/72.27
+golden_mean=(math.sqrt(5)-1.0)/2.0
+fig_width=fig_width_pt*inches_per_pt
+fig_height=fig_width*golden_mean
+fig_size=(fig_width*8, fig_height*8)
+params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
+plt.rcParams.update(params)
+matplotlib.rcParams['ps.useafm'] = True
+matplotlib.rcParams['pdf.use14corefonts'] = True
+matplotlib.rcParams['text.usetex'] = True
+
+
+figure(figsize=fig_size)
[…]

### 2015-01-13 generate/fig1_nl_spectra1/photons.py

@@ -1,0 +1,87 @@
+from constants import *
+import numpy as np
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import read_output as rd
+
+
+def planck_l (T, lamb):
+
+	''' 
+	The planck function for wavelength lamb at temperature T
+
+	Takes lambda in ANGSTROMS and return ergs cm^-2 s^-2 sr^-1 AA^-1
+	'''
+
+	# convert to cm for planck equation
+	lamb2 = lamb*ANGSTROM
+
+	x = H_OVER_K * C / (T * lamb2)
+	Bnu = (2. * H * C**2.0) /  (lamb2**5.) / (np.exp(x) - 1.)
+
+	# convert back to ANGSTROM
+    
+	return Bnu*ANGSTROM
+
+
+
+x = np.arange(2000,5000,50)
+
+# create a blackbody
+y = planck_l(10000,x)
+
+total = np.sum(y)
+
+
+
+
+
+#generate photons
+NPHOT = int (sys.argv[1])
+photon_bins = np.zeros(len(y))
+
+#weight = lum / NPHOT
+
+weight = 1
+
+binsize = 50
+
+for i in range(NPHOT):
+
+
+	# generate photon and locate in cdf
+	z = np.random.random() * total
+
+	j = -1
+	c_sum = 0.0
+	while c_sum < z:
+
+		j += 1 
+		c_sum += y[j]
+
+	wave = x[j]
+	
+
+	photon_bins[j] += weight
+
+
+
+
+
+
+
+#plot(x,yc)
+scatter(x,photon_bins)
+
+show()
+
+
+
+
+
+
+
+
+
+

### 2015-01-13 generate/fig1_nl_spectra1/plot2.py

@@ -1,0 +1,204 @@
+from constants import *
+import numpy as np
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import read_output as rd
+rd.setpars()
+
+def gauss(sigma, x0, x):
+
+	term = 1.0 / (2.0*np.pi) / sigma
+
+	exp_term = ( (x - x0)**2 )  /  (2.0*sigma*sigma)
+
+	term *= np.exp(-exp_term)
+
+	return term
+
+# def convolve(FWHM, x, y, mode="gaussian"):
+
+# 	'''
+# 	convolve arrays
+# 	'''
+
+# 	sigma = FWHM / (np.sqrt(8.0*np.log(2.0)))
+
+# 	n_points = len(x)
+
+# 	for i in range(n_points):
+
+def get_linelist(filenames, ionreturn=False):
+
+	lines = np.array([])
+	z = np.array([])
+
+	for i in range(len(filenames)):
+
+		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
+
+		lines = np.concatenate((lines, x[1]))
+
+		z = np.concatenate((z, x[0]))
+
+	if ionreturn:
+		return lines, z
+	else:
+		return lines
+
+
+
+
+
+
+
+# some fontsizes for figure
+font1 = 16				# fontsize for x label
+font2 = 16				# fontsize for Y label
+font3 = 16				# fontsize for text on figures
+weight = 1.5
+
+
+
+# standard plot parameters for mnras
+fig_width_pt=120.0 #Figure parameters
+inches_per_pt=1.0/72.27
+golden_mean=(math.sqrt(5)-1.0)/2.0
+fig_width=fig_width_pt*inches_per_pt
+fig_height=fig_width*golden_mean
+fig_size=(fig_width*8, fig_height*8)
+params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
+plt.rcParams.update(params)
+matplotlib.rcParams['ps.useafm'] = True
+matplotlib.rcParams['pdf.use14corefonts'] = True
+matplotlib.rcParams['text.usetex'] = True
+
+
+figure(figsize=fig_size)
[…]

### 2015-01-13 generate/fig1_nl_spectra1/plot_dex.py

@@ -1,0 +1,136 @@
+'''
+plot_nl_figure.py 
+
+This script creates the figure for the Nova like spectra
+in the 2014 CV paper. The data were scraped from Dexter.
+'''
+
+
+from constants import *
+import numpy as np
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import read_output as rd
+rd.setpars()
+
+# some fontsizes for figure
+font1 = 16				# fontsize for x label
+font2 = 12				# fontsize for Y label
+font3 = 16				# fontsize for text on figures
+weight = 1.5			# lineweight
+
+
+
+# standard plot parameters for mnras
+fig_width_pt=120.0 #Figure parameters
+inches_per_pt=1.0/72.27
+golden_mean=(math.sqrt(5)-1.0)/2.0
+fig_width=fig_width_pt*inches_per_pt
+fig_height=fig_width*golden_mean
+fig_size=(fig_width*8, fig_height*8)
+params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
+plt.rcParams.update(params)
+matplotlib.rcParams['ps.useafm'] = True
+matplotlib.rcParams['pdf.use14corefonts'] = True
+matplotlib.rcParams['text.usetex'] = True
+
+
+figure(figsize=fig_size)
+colour = "b"
+
+# read the RW Sex data
+x1,y1 = np.loadtxt("rwsex/data11.dat", unpack=True, comments="#", usecols=(0,1))
+
+# read the IX Vel daata
+x, y = np.loadtxt("ixvel/data2.dat", unpack=True, comments="#", usecols=(0,1))
+a,b = np.loadtxt("ixvel/data.dat", unpack=True, comments="#", usecols=(0,1))
+
+# read the RW Tri data 
+cc,dd = np.loadtxt("rwtri/new_eclipse.dat", unpack=True, comments="#", usecols=(0,1))
+cc_no, dd_no = np.loadtxt("rwtri/rwtri_opt_noeclipse.dat", unpack=True, comments="#", usecols=(0,1))
+
+
+
+
+
+
+# adjust RW Tri from MJy to F_lambda in CGS units
+nus = (C) / (cc*ANGSTROM)
[…]

### 2015-01-13 generate/fig1_nl_spectra1/plot_nl_figure.py

@@ -1,0 +1,240 @@
+'''
+plot_nl_figure.py 
+
+This script creates the figure for the Nova like spectra
+in the 2014 CV paper. The data were scraped from Dexter.
+'''
+
+
+from constants import *
+import numpy as np
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import read_output as rd
+import py_plot_util as util 
+
+util.parse_rcparams("../params.rc")
+rd.setpars()
+
+# some fontsizes for figure
+font1 = 16				# fontsize for x label
+font2 = 16				# fontsize for Y label
+font3 = 16				# fontsize for text on figures
+weight = 2			# lineweight
+
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+
+
+# standard plot parameters for mnras
+fig_width_pt=120.0 #Figure parameters
+inches_per_pt=1.0/72.27
+golden_mean=(math.sqrt(5)-1.0)/2.0
+fig_width=fig_width_pt*inches_per_pt
+fig_height=fig_width*golden_mean
+fig_size=(fig_width*8, fig_height*8)
+params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
+plt.rcParams.update(params)
+matplotlib.rcParams['ps.useafm'] = True
+matplotlib.rcParams['pdf.use14corefonts'] = True
+matplotlib.rcParams['text.usetex'] = True
+
+
+figure(figsize=fig_size)
+colour = "k"
+
+# read the RW Sex data
+x1,y1 = np.loadtxt("rwsex/data11.dat", unpack=True, comments="#", usecols=(0,1))
+
+# read the IX Vel daata
+x, y = np.loadtxt("ixvel/data2.dat", unpack=True, comments="#", usecols=(0,1))
+a,b = np.loadtxt("ixvel/data.dat", unpack=True, comments="#", usecols=(0,1))
+
+# read the RW Tri data 
+cc,dd = np.loadtxt("rwtri/new_eclipse.dat", unpack=True, comments="#", usecols=(0,1))
[…]

### 2015-01-13 generate/fig1_nl_spectra1/salt.py

@@ -1,0 +1,207 @@
+from constants import *
+import numpy as np
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import read_output as rd
+rd.setpars()
+
+def gauss(sigma, x0, x):
+
+	term = 1.0 / (2.0*np.pi) / sigma
+
+	exp_term = ( (x - x0)**2 )  /  (2.0*sigma*sigma)
+
+	term *= np.exp(-exp_term)
+
+	return term
+
+# def convolve(FWHM, x, y, mode="gaussian"):
+
+# 	'''
+# 	convolve arrays
+# 	'''
+
+# 	sigma = FWHM / (np.sqrt(8.0*np.log(2.0)))
+
+# 	n_points = len(x)
+
+# 	for i in range(n_points):
+
+def get_linelist(filenames, ionreturn=False):
+
+	lines = np.array([])
+	z = np.array([])
+
+	for i in range(len(filenames)):
+
+		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
+
+		lines = np.concatenate((lines, x[1]))
+
+		z = np.concatenate((z, x[0]))
+
+	if ionreturn:
+		return lines, z
+	else:
+		return lines
+
+
+
+
+
+
+
+# some fontsizes for figure
+font1 = 16				# fontsize for x label
+font2 = 16				# fontsize for Y label
+font3 = 16				# fontsize for text on figures
+weight = 1.5
+
+
+
+# standard plot parameters for mnras
+fig_width_pt=120.0 #Figure parameters
+inches_per_pt=1.0/72.27
+golden_mean=(math.sqrt(5)-1.0)/2.0
+fig_width=fig_width_pt*inches_per_pt
+fig_height=fig_width*golden_mean
+fig_size=(fig_width*8, fig_height*8)
+params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
+plt.rcParams.update(params)
+matplotlib.rcParams['ps.useafm'] = True
+matplotlib.rcParams['pdf.use14corefonts'] = True
+matplotlib.rcParams['text.usetex'] = True
+
+
+figure(figsize=fig_size)
[…]

### 2015-01-13 generate/fig2_cartoon/SV_cartoon.py
some reorganisation

@@ -1,0 +1,95 @@
+'''
+SV_cartoon.py 
+
+This script creates the cartoon figure for 
+the 2014 CV paper. The data were scraped from Dexter.
+'''
+
+import matplotlib.mlab as mlab
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+
+mpl.rcParams['pdf.use14corefonts'] = True
+mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+mpl.rc('text', usetex=True)
+
+thetamin=72.0
+thetamax=80.0
+diskmax=25.0
+xmin=10.0
+xmax=18.0
+rstar=2.0
+
+xwindmax=40.0
+zwindmax=(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))
+
+
+posx=np.arange(xmin,xwindmax,(xmax-xmin)/10.0)
+ymin1=[]
+ymax1=[]
+
+x=np.array([xmin,xmax,xwindmax])
+y1=np.array([0.0,(xmax-xmin)*np.tan(np.radians(90.0-thetamin)),(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))])
+y2=np.array([0.0,0.0,(xwindmax-xmax)*np.tan(np.radians(90.0-thetamax))])
+
+lsize=14
+tsize=16 
+
+fig=plt.figure()
+ax=fig.add_subplot(1,1,1)
+ax.plot(x,y1,x,y2,color='black')
+ax.plot(-1.0*x,y1,-1.0*x,y2,color='black')
+ax.plot(-1.0*x,-1.0*y1,-1.0*x,-1.0*y2,color='black')
+ax.plot(x,-1.0*y1,x,-1.0*y2,color='black')
+ax.set_xlim([-1.0*xwindmax,xwindmax])
+plt.fill_between(x,y1, y2, facecolor='0.9', interpolate=True)
+plt.fill_between(-1.0*x,y1, y2, facecolor='0.9', interpolate=True)
+plt.fill_between(x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
+plt.fill_between(-1.0*x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
[…]

### 2015-01-13 generate/fig3_acc_law/acc.py

@@ -1,0 +1,68 @@
+'''
+acc.py 
+
+Created the plot of the velocity law 
+for CV paper 2014
+'''
+
+import py_plot_util as util 
+util.parse_rcparams()
+
+
+from pylab import *
+
+figure()
+
+import read_output as rd 
+rd.setpars()
+import matplotlib.pyplot as plt 
+plt.rcParams["lines.linewidth"] = 2 
+
+plt.rcParams['ps.useafm'] = True
+plt.rcParams['pdf.use14corefonts'] = True
+
+
+def vel_law (l, R_v, alpha):
+
+	v0 = 6
+	v_inf=10000
+
+	v = (v_inf - v0) * (l / R_v)**alpha 
+
+	v /= 1.0 + (l / R_v)**alpha 
+
+	v += v0
+
+	return v
+
+
+alphas = [0.2,0.5,1, 1.5, 3,5,10]
+
+R_v = 7e10
+
+l = np.logspace(7,12,num=100000)
+
+colors = ["b", "g", "r", "k", "y", "c", "m"]
+
+i=0
+
+for alpha in alphas:
+
+	print alpha, np.log10(alpha)
+
+	plot(l/R_v, vel_law(l, R_v, alpha)/10000, label="$\\alpha=%.1f$" % alpha, c=colors[i])
+
+	i+=1
+
+
+
+xlim(0,2.0)
+legend(loc=4)
+
+xlabel("$l/R_v$", fontsize=16)
+ylabel("$v/v_{\infty}$", fontsize=16)
+
+savefig("acc_law.png")
+savefig("acc_law.eps", facecolor='w',edgecolor='w',bbox_inches='tight')
+
+

### 2015-01-13 generate/fig4_sed/bl_seds.py

@@ -1,0 +1,116 @@
+'''
+sed.py
+
+Create the plot of disk and BL seds for the
+CV paper 2014.
+
+Requireds JAMES's disk subtourines
+'''
+import disk
+from pylab import *
+import numpy as np 
+import os, sys
+from constants import *
+from cosmolopy.magnitudes import *
+from read_output import *
+
+# set some matplotlib parameters
+setpars()
+
+# minimum and max wavelengths for rings
+lmin = (C / 1e12) / ANGSTROM
+lmax = (C / 1e19) / ANGSTROM
+
+
+# make nr rings in a disk
+nr = 100	# number of rings
+r = disk.make_rings(lmin, lmax,0.8,1e-8,7e8,2.4e10, nrings = nr, mode="bb2")
+r2 = disk.make_rings(lmin, lmax,0.7,5e-9,8e8,2.4e10, nrings = nr, mode="bb2")
+
+
+
+
+# frequency resolution
+nfreq = 10000
+
+
+# create arrays for nu and fnu
+nu = np.logspace(np.log10(1e9), np.log10(1e19), num = nfreq)
+fnu = np.zeros(len(nu))
+fnu2 = np.zeros(len(nu))
+
+
+for j in range(nr - 1):
+	Bnu = disk.planck_nu (r.T[j], nu)
+	Bnu2 = disk.planck_nu (r2.T[j], nu)
+	print r.T[j]
+	for i in range(len(nu)):
+		fnu[i] += Bnu[i] * r.area[j] * PI
+		fnu2[i] += Bnu2[i] * r2.area[j] * PI
+
+
+
+
+L_acc = 0.5 * G * 0.8 * MSOL * 1e-8 * MSOL / YR / 7e8
+
+dnu = nu[1:] - nu[:-1]
+dnu = np.append(dnu, dnu[-1])
+
+Lacc = 2.0*np.sum(fnu*dnu)
+# L8 = np.sum(f8*dnu)
+# L20 = np.sum(f20*dnu)
+# print L_acc, Lacc, L8, L20
+#figure(figsize=(8,8))
+#loglog(nu, nu*fnu, label="Disk, HD91", linewidth=2.5, c="k")
+#loglog(nu, nu*fnu2, label=r"Disk, LK02", linewidth=2.5, c="#839096")
[…]

### 2015-01-13 generate/fig4_sed/sed.py

@@ -1,0 +1,129 @@
+'''
+sed.py
+
+Create the plot of disk and BL seds for the
+CV paper 2014.
+
+Requireds JAMES's disk subtourines
+'''
+import disk
+from pylab import *
+import numpy as np 
+import os, sys
+from constants import *
+from cosmolopy.magnitudes import *
+from read_output import *
+from py_plot_util import *
+
+# set some matplotlib parameters
+setpars()
+parse_rcparams()
+
+# minimum and max wavelengths for rings
+lmin = (C / 1e12) / ANGSTROM
+lmax = (C / 1e19) / ANGSTROM
+
+
+# make nr rings in a disk
+nr = 100	# number of rings
+r = disk.make_rings(lmin, lmax,0.8,1e-8,7e8,2.4e10, nrings = nr, mode="bb2")
+r2 = disk.make_rings(lmin, lmax,0.7,5e-9,8e8,2.4e10, nrings = nr, mode="bb2")
+
+
+
+
+# frequency resolution
+nfreq = 10000
+
+
+# create arrays for nu and fnu
+nu = np.logspace(np.log10(1e9), np.log10(1e19), num = nfreq)
+fnu = np.zeros(len(nu))
+fnu2 = np.zeros(len(nu))
+
+
+for j in range(nr - 1):
+	Bnu = disk.planck_nu (r.T[j], nu)
+	Bnu2 = disk.planck_nu (r2.T[j], nu)
+	print r.T[j]
+	for i in range(len(nu)):
+		fnu[i] += Bnu[i] * r.area[j] * PI
+		fnu2[i] += Bnu2[i] * r2.area[j] * PI
+
+
+
+
+L_acc = 0.5 * G * 0.8 * MSOL * 1e-8 * MSOL / YR / 7e8
+
+dnu = nu[1:] - nu[:-1]
+dnu = np.append(dnu, dnu[-1])
+
+Lacc = 2.0*np.sum(fnu*dnu)
+
+
+
+
+area8 = L_acc / STEFAN_BOLTZMANN / 80000.0**4
+area20 = L_acc / STEFAN_BOLTZMANN / 200000.0**4
+
+
+f8 = disk.planck_nu(80000,nu) * area8 * PI
+f20 = disk.planck_nu(200000,nu) * area20 * PI
+
+
+L8 = np.sum(f8*dnu)
+L20 = np.sum(f20*dnu)
+
+print L_acc, Lacc, L8, L20
+
+
[…]

### 2015-01-13 generate/fig5_uv_opt/fig5_uv_plus_opt_sidebyside.py

@@ -1,0 +1,150 @@
+import numpy as numpy
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import py_read_output as rd
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import py_plot_util as util 
+
+util.parse_rcparams()
+
+fname = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_uv"
+fname2 = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_opt"
+
+rd.setpars()
+
+nx = 2
+
+ratio = 8.27 / 11.02
+figure(figsize=(8.27,12))
+incs = ("10", "17.5", "45", "62.5", "80")
+
+s = rd.read_spectrum(fname)
+
+subplot(111)
+#xlabel("Wavelength [\AA]", fontsize=20)
+nspec = 5
+
+grids = [1,3,5,7,9]
+
+dticks = [10,10,10,5,5]
+
+for i in range(nspec):
+
+	subplot(nspec,2,grids[i])
+	xlim(1000,2000)
+
+	plot(s["Lambda"], 1e12*smooth(s[s.colnames[9+i]] ), c="k")
+
+	if i == 2: ylabel("Flux at 100pc ($10^{-12}$~erg s$^{-1}$ cm$^{-3}$ \AA$^{-1}$)", fontsize=20)
+
+	#text(6100, 0.7*1e12*(np.max(s.spec[i])), "$i=%s^{\circ}$" % incs[i])
+	ax = gca()
+	
+
+	print grids[i]
+	#if grids[i] < 8: ax.set_xticklabels([])
+	if i<4:ax.set_xticklabels([])
+
+
+	start, end = ax.get_ylim()
+
+	if i == 4:
+		start, end = 0,35
+	ax.yaxis.set_ticks(np.arange(start, end, dticks[i]))
+	ylim(start,end)
+
+
+
+
+#ylim(0,49)
+labels = [r"Ly-$\alpha$", r"C\textsc{iv}", r"He~\textsc{ii}~$\lambda1640$"]
+lines = [1215,1550, 1640]
+vlines(lines, 27,30)
+
+offs = [-90,0,0]
+for i in range(len(labels)):
+	text(lines[i]+offs[i],31,labels[i], fontsize=10)
+
+
+#ax is name of original plot so change this to whatever your plot is called, 
+#loc is where in graph you want box containing zoomed plot, mess with numbers
[…]

### 2015-01-13 generate/fig6_opt_cont/fig6_opt_continuum.py

@@ -1,0 +1,112 @@
+import numpy as numpy
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+from plot_norm import *
+import py_read_output as rd
+import py_plot_util as util 
+
+util.parse_rcparams()
+
+fname = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_opt"
+fname2 = "specs/cv_alpha4_r4r12_mdot1e9_rv1e11_opt"
+
+rd.setpars()
+
+mode = sys.argv[1]
+
+atomic_filenames = [ "data/atomic_macro/h10_lines.py", "data/atomic73/lines_linked_ver_2.py", 
+	                     "data/atomic_macro/he_top_lines.py" ]
+lines = get_linelist(atomic_filenames)
+
+nx = 2
+
+figure(figsize=(8.3,11.6))
+incs = ("10", "17.5", "45", "62.5", "80")
+
+s = rd.read_spectrum(fname)
+s2 = rd.read_spectrum(fname2)
+
+subplot(111)
+xlabel("Wavelength (\AA)", fontsize=20)
+nspec = 5
+
+
+
+for i in range(nspec):
+
+	subplot(nspec,1,i+1)
+	xlim(3040,6900)
+
+	a = get_continuum(s["Lambda"], s[s.colnames[9+i]], lines)
+
+	if mode == 'a':
+		plot(s["Lambda"], smooth(s[s.colnames[9+i]] /make_f(a, s["Lambda"]) ), c="k")
+
+	elif mode == "b":
+		plot(s["Lambda"], smooth(s[s.colnames[9+i]] /make_f(a, s["Lambda"]) ), c="#d3d3d3", label="A")
+		a = get_continuum(s2["Lambda"], s2[s2.colnames[9+i]], lines)
+		plot(s2["Lambda"], smooth(s2[s2.colnames[9+i]] /make_f(a, s2["Lambda"]) ), c="k", label="B")
+	
+
+	if i == 2: ylabel("Flux/Continuum", fontsize=20)
+
+	if i == 0 and mode == "b":
+		legend()
+
+	#text(6100, 0.7*1e12*(np.max(s[s.colnames[9+i]])), "$i=%s^{\circ}$" % incs[i])
+	ax = gca()
+	ylim(0.4,1.95)
+
+	print i
[…]

### 2015-01-13 generate/fig7_escaping/fig7.py

@@ -1,0 +1,49 @@
+#from plot_norm import *
+import numpy as numpy
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+from plot_norm import *
+from constants import *
+from scipy import interp
+import py_plot_util as util
+import py_read_output as rd
+
+
+rd.setpars()
+util.parse_rcparams()
+
+mode = sys.argv[1]
+
+
+fname = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_opt"
+
+fname2 = "specs/cv_alpha4_r4r12_mdot1e9_rv1e11_opt"
+
+s = rd.read_spectrum(fname)
+s2 = rd.read_spectrum(fname2)
+
+if mode=="a":
+	plot(s["Lambda"], 1e12*smooth(s["Emitted"]), linewidth=2, label="Total", c="k")
+	plot(s["Lambda"], 1e12*smooth(s["Disk"]), label="Disk")
+	plot(s["Lambda"], 1e12*smooth(s["Wind"]), label="Wind")
+
+else:
+	# plot(s["Lambda"], 1e12*smooth(s["Emitted"]), linewidth=2, c="k", alpha=0.7)
+	# plot(s["Lambda"], 1e12*smooth(s["Disk"]), c="g", alpha=0.7)
+	# plot(s["Lambda"], 1e12*smooth(s["Wind"]), c="r", alpha=0.7))
+
+	plot(s2["Lambda"], 1e12*smooth(s2["Emitted"]), linewidth=2, label="Total", c="k")
+	plot(s2["Lambda"], 1e12*smooth(s2["Disk"]),  linewidth=1, c="g", label="Disk")
+	plot(s2["Lambda"], 1e12*smooth(s2["Wind"]),  linewidth=1, c="r", label="Wind")
+
+xlabel("Wavelength (\AA)", fontsize=16)
+ylabel("$\log [$Flux at 100pc $(10^{-12}$~erg s$^{-1}$ cm$^{-3}$ \AA$^{-1})]$", fontsize=16)
+semilogy()
+legend()
+xlim(3050,6800)
+
+savefig('../../figures/model%s_escaping.eps' % (mode),facecolor='w',edgecolor='w',bbox_inches='tight')
+savefig('model%s_escaping.png' % (mode))

### 2015-01-13 generate/fig_levels/level_tests.py

@@ -1,0 +1,140 @@
+'''
+James Matthews, 30/04/14
+
+plotting script for comparing Tardis and Python level populations
+'''
+
+#import modules
+import sys, os
+from tardis.io import config_reader
+from tardis import model, simulation
+import numpy as np
+import logging
+import warnings
+from numpy import exp
+from pylab import *
+from astropy import units
+
+
+def run_tardis(yml_file="basic.yml"):
+	'''
+	runs a tardis model and returns a class instance of Radial1dModel type
+	'''
+	#read the config file and create a model
+	tardis_config = config_reader.TARDISConfiguration.from_yaml(yml_file)
+	radial1d = model.Radial1DModel(tardis_config)
+	simulation.run_radial1d(radial1d)
+
+	return radial1d
+
+
+def set_model_params(radial1d, t_r, w, t_e, ne, tau):
+	'''
+	set the model parameters in tardis, returns model 
+	of same type as input
+	'''
+	radial1d.t_rads[:] = t_r * units.K
+	radial1d.ws[:] = w
+	radial1d.plasma_array.electron_densities.values[:] = ne
+
+	##interfere with any details - e.g. electron temperature - like this ...can also do electron density etc.
+	frac_te = t_e / t_r
+	radial1d.plasma_array.link_t_rad_to_t_electron = frac_te
+	##might want to set tau_sobolev optical depths to zero (or some other set of values) for ease of comparison
+	radial1d.plasma_array.tau_sobolevs.values[:] = tau
+
+	#calculate the mean intensities in the lines for chosen conditions
+	radial1d.calculate_j_blues()
+
+	#propagate rad field settings to plasma
+	radial1d.plasma_array.j_blues = radial1d.j_blues
+	radial1d.plasma_array.t_rads = radial1d.t_rads.value
+
+	return radial1d
+
+
+def get_tardis_pops(radial1d, t_r, w, t_e, ne, tau):
+
+	'''
+	takes a tardis model and calculates the level populations 
+	in these physical conditions (t_r, w, t_e, ne, tau)
+
[…]

### 2015-01-13 generate/fig_levels/make_fig_caseb_and_tardis.py

@@ -1,0 +1,188 @@
+'''
+James Matthews, 30/04/14
+
+plotting script for comparing Tardis and Python level populations
+'''
+
+#import modules
+import sys, os
+from tardis.io import config_reader
+from tardis import model, simulation
+import numpy as np
+import logging
+import warnings
+from numpy import exp
+from pylab import *
+from astropy import units
+import read_output as rd
+import py_plot_util as util 
+
+
+def run_tardis(yml_file="basic.yml"):
+	'''
+	runs a tardis model and returns a class instance of Radial1dModel type
+	'''
+	#read the config file and create a model
+	tardis_config = config_reader.TARDISConfiguration.from_yaml(yml_file)
+	radial1d = model.Radial1DModel(tardis_config)
+	simulation.run_radial1d(radial1d)
+
+	return radial1d
+
+
+def set_model_params(radial1d, t_r, w, t_e, ne, tau):
+	'''
+	set the model parameters in tardis, returns model 
+	of same type as input
+	'''
+	radial1d.t_rads[:] = t_r * units.K
+	radial1d.ws[:] = w
+	radial1d.plasma_array.electron_densities.values[:] = ne
+
+	##interfere with any details - e.g. electron temperature - like this ...can also do electron density etc.
+	frac_te = t_e / t_r
+	radial1d.plasma_array.link_t_rad_to_t_electron = frac_te
+	##might want to set tau_sobolev optical depths to zero (or some other set of values) for ease of comparison
+	radial1d.plasma_array.tau_sobolevs.values[:] = tau
+
+	#calculate the mean intensities in the lines for chosen conditions
+	radial1d.calculate_j_blues()
+
+	#propagate rad field settings to plasma
+	radial1d.plasma_array.j_blues = radial1d.j_blues
+	radial1d.plasma_array.t_rads = radial1d.t_rads.value
+
+	return radial1d
+
+
+def get_tardis_pops(radial1d, t_r, w, t_e, ne, tau):
+
+	'''
[…]

### 2015-01-13 generate/murray/plotmc.py

@@ -1,0 +1,60 @@
+#!/usr/bin/env python
+import py_plot_util as util
+import py_plot_output as plt
+import py_read_output as rd 
+import numpy as np
+from pylab import * 
+import os, sys
+from astropy.io import ascii
+import plot_norm as norm
+from constants import C
+
+util.parse_rcparams()
+rd.setpars()
+
+alphas = [15,4,4]
+alphas_actual = [1.5,4,1.5,4]
+RV = ["7e10", "1e11", "2e11"]
+
+colours = ["#d3d3d3", "k", "r","b","g"]
+labels=["A","B","X","Y"]
+
+atomic_filenames = [ "data/atomic_macro/h10_lines.py", "data/atomic73/lines_linked_ver_2.py", 
+                             "data/atomic_macro/he_top_lines.py" ]
+lines = norm.get_linelist(atomic_filenames)
+
+for i in range(len(alphas)):
+
+
+
+	fname = "specs/cv_alpha%i_r4r12_mdot1e9_rv%s_opt" % (alphas[i], RV[i])
+
+	s = rd.read_spectrum(fname)
+
+	select = (s["Lambda"] > 6513)*(s["Lambda"] < 6613)
+
+	a = norm.get_continuum(s["Lambda"], s["A80P0.50"], lines, lmin=5600,lmax=6700, deg = 1)
+	ff = norm.make_f(a, s["Lambda"])
+	f = s["A80P0.50"]-ff
+
+	fmax = np.max(util.smooth(f[select],window_len=5))
+	f = f / fmax
+
+	XTOPLOT = C* 1e-7 *(s["Lambda"] - 6563) / 6563
+
+	plot(XTOPLOT, util.smooth(f,window_len=5), c=colours[i], label=labels[i], linewidth=2)
+
+
+legend()
+xlim(-19.469118,19.469118)
+ylim(0,1)
+xlabel("Velocity (100 km/s)", fontsize=16)
+ylabel("Normalised Flux", fontsize=16)
+
+
+
+
+savefig("mc.png")
+savefig("../../figures/mc.eps")
+
+

### 2015-01-13 generate/spec_uv_opt/spec_uv_opt.py

@@ -1,0 +1,199 @@
+import numpy as numpy
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import read_output as rd
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import py_plot_util as util 
+
+util.parse_rcparams()
+
+fname = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_uv"
+fname2 = "specs/cv_alpha4_r4r12_mdot1e9_rv1e11_uv"
+
+rd.setpars()
+
+mode = sys.argv[1]
+
+
+nx = 2
+
+textwidth = 0.8
+ratio = 8.27 / 11.02
+figure(figsize=(8.27,12))
+incs = ("10", "27.5", "45", "62.5", "80")
+
+s = rd.read_spec_file(fname)
+s2 = rd.read_spec_file(fname2)
+
+subplot(111)
+#xlabel("Wavelength [\AA]", fontsize=20)
+nspec = 5
+
+grids = [1,3,5,7,9]
+dticks = [10,10,10,5,5]
+
+for i in range(nspec):
+
+	subplot(nspec,2,grids[i])
+	xlim(1000,2000)
+
+
+	if mode == "a":
+		plot(s.wavelength, 1e12*smooth(s.spec[i] ), c="k", label="A")
+
+	else:
+		plot(s.wavelength, 1e12*smooth(s.spec[i] ), c="#d3d3d3", label="A")
+		plot(s2.wavelength, 1e12*smooth(s2.spec[i] ), c="k", label="B")
+
+	if i == 2: ylabel("Flux at 100pc ($10^{-12}$~erg s$^{-1}$ cm$^{-3}$ \AA$^{-1}$)", fontsize=20)
+
+	#text(6100, 0.7*1e12*(np.max(s.spec[i])), "$i=%s^{\circ}$" % incs[i])
+	ax = gca()
+	
+	if i == 0 and mode == "b":
+		legend()
+
+	print grids[i]
+	#if grids[i] < 8: ax.set_xticklabels([])
+	if i<4:ax.set_xticklabels([])
+	start, end = ax.get_ylim()
+	ax.yaxis.set_ticks(np.arange(start, end, dticks[i]))
+	ylim(start,end)
+
+#ylim(0,49)
+labels = [r"Ly-$\alpha$", r"C\textsc{iv}", r"He~\textsc{ii}~$\lambda1640$"]
[…]

### 2015-01-13 generate/wind_plot/for_Sam/classes.py

@@ -1,0 +1,177 @@
+'''
+	University of Southampton -- JM -- 30 September 2013
+
+				classes.py
+
+Synopsis:
+	classes
+    
+    This is a set of classes for use with the radiative transfer code python
+
+Usage:
+	
+
+Arguments:
+'''
+
+
+
+
+class spectotclass:
+    '''This is a class for storing any values read from a Python spec_tot file'''	
+    def __init__(self, fre, wave, emi, cen, dis, win, sca, hit):
+        self.freq = fre
+        self.wavelength = wave
+        self.emitted = emi
+        self.censrc = cen
+        self.disk = dis
+        self.wind = win
+        self.scattered = sca
+        self.hitSurf = hit
+
+
+
+class specclass:
+    '''This is a class for storing any values read from a Python spec file'''	
+    def __init__(self, fre, wave, emi, cen, dis, win, sca, hit, spe):
+        self.freq = fre
+        self.wavelength = wave
+        self.emitted = emi
+        self.censrc = cen
+        self.disk = dis
+        self.wind = win
+        self.scattered = sca
+        self.hitSurf = hit
+        self.spec = spe
+
+class macroclass:
+    '''This is a class for storing any values read from a Python macro atom spec file'''	
+    def __init__(self, fre, wave, emi, cen, dis, win, l, hit, spe):
+        self.freq = fre
+        self.wavelength = wave
+        self.emitted = emi
+        self.censrc = cen
+        self.disk = dis
+        self.wind = win
+        self.lines = l
+        self.hitSurf = hit
+        self.spec = spe
+
+
+class topbase_class:
+	'''This is a class for topbase photoionization data'''	
+	def __init__(self, nz, ne, islp_init, E0_init, linit, np_init, energies, cross_sections):
+		self.Z = nz
+		self.ion = ne
+		self.islp = islp_init
+		self.l = linit
+		self.E0 = E0_init 
+		self.np = np_init
+		self.energy = energies
+		self.XS = cross_sections
+        
+        
+#mode class: sets mode from command line
+class modeclass:
+	'''The mode class: for reading arguments from command line'''
[…]

### 2015-01-13 generate/wind_plot/for_Sam/make_windplot.py

@@ -1,0 +1,278 @@
+import matplotlib.pyplot as plt 
+from pylab import * 
+import numpy as np 
+import csv, sys, os, array, warnings, subprocess
+import pywind_sub as ps
+import matplotlib as mpl
+from matplotlib.mlab import bivariate_normal
+from matplotlib.colors import LogNorm
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib as mpl
+import time
+import read_output as rd
+
+
+def run_py_wind (vers, fname, cmds=None, ilv=None):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	if cmds == None:
+		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i","0", "1","1","1","2","2","2","2","1","2","3","6", \
+			          "3","6","4","6","5","0","q"])
+
+	x = cmds
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+
+
+
+def run_pydc (vers, fname, nplasma = 1):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	x = np.array(["1","M","4",str(nplasma),"1","-1","r","n","t","w", "q"])
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+#ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
+
+
+
+#nplasmas = ps.pywind_read(fname+'.pnum.dat',ix,iz)
+
+def read_pywind_smart(filename, return_inwind=False):
+	'''
+	read a py_wind file using np array reshaping and manipulation
+	'''
+
+	# first, simply load the filename 
[…]

### 2015-01-13 generate/wind_plot/for_Sam/plot_output.py

@@ -1,0 +1,60 @@
+import read_sub as sub
+from pylab import * 
+import numpy as np 
+import sys
+
+'''
+usage
+ e.g. python plot_output.py sv 
+'''
+ 
+
+fname = sys.argv[1]
+
+
+
+##### MAKING A WIND PLOT
+# run py_wind- only need to runt his to create the files
+sub.run_py_wind("77a_dev", fname)
+
+# read electron density from the file - could also try e.g. te or ionC4
+x, z, value = sub.read_pywind_smart(fname + ".ne.dat")
+
+# make a contour plot- note that z and x are in a weird order here
+# take the log with np.log10
+contourf(z,x,np.log10(value) )
+
+
+# make the y and x axes log!
+semilogy()
+semilogx()
+
+# add a colorbar
+colorbar()
+
+# add a title and axes labels
+#title("Title")
+#xlabel("X")
+#ylabel("Y")
+#edit xlims and ylims with xlim(30,40)
+
+show()		# show the figure
+
+#save with 
+#savefig("filename.png")
+
+#clear figure
+clf() 
+
+
+
+##### MAKING A SPECTRUM PLOT
+
+# read spec file
+s = sub.read_spec_file(fname)
+
+# plot the 0th element of the array which is the first viewing angle
+# use the function smooth to smooth the data
+plot(s.wavelength, sub.smooth(s.spec[0]) )
+show()
+

### 2015-01-13 generate/wind_plot/for_Sam/read_output.py

@@ -1,0 +1,328 @@
+'''
+	University of Southampton -- JM -- 30 September 2013
+
+				read_output.py
+
+Synopsis:
+	this enables one to read outputs from the Python radiative transfer code
+
+Usage:
+	
+
+Arguments:
+'''
+
+# we need the classes and numpy modules 
+import classes as cls
+import numpy as np
+import matplotlib.pyplot as plt
+import subprocess
+
+
+def read_spec_file (filename):
+    
+    '''reads a Python .spec file and places in specclass array,
+       which is returned'''
+    
+    if not '.spec' in filename: 
+        filename = filename + '.spec'
+        
+    
+    # initialise the spectrum array with blank arrays
+    spectrum = cls.specclass ([],[],[],[],[],[], [], [], []) 
+    
+    # first read the file into a temporary storage array
+    spectrum_temp = np.loadtxt (filename, comments ='#', unpack=True)
+    
+    # now set the correct elements of the class to be the temporary array
+    spectrum.freq = spectrum_temp[0]
+    spectrum.wavelength = spectrum_temp[1]
+    spectrum.emitted = spectrum_temp[2]
+    spectrum.censrc = spectrum_temp[3]
+    spectrum.disk = spectrum_temp[4]
+    spectrum.wind = spectrum_temp[5] 
+    spectrum.scattered = spectrum_temp[7]
+    spectrum.hitsurf = spectrum_temp[6]
+    spectrum.spec = spectrum_temp[8:]
+        
+     #finally, return the spectrum class which is a series of named arrays      
+    return spectrum
+
+
+def macro_spec (filename):
+    
+    '''reads a Python .spec file and places in specclass array,
+       which is returned'''
+    
+    if not '.spec' in filename: 
+        filename = filename + '.spec'
+        
+    
+    # initialise the spectrum array with blank arrays
+    spectrum = cls.macroclass ([],[],[],[],[],[], [], [], []) 
+    
+    # first read the file into a temporary storage array
+    spectrum_temp = np.loadtxt (filename, comments ='#', unpack=True)
+    
+    # now set the correct elements of the class to be the temporary array
+    spectrum.freq = spectrum_temp[0]
+    spectrum.wavelength = spectrum_temp[1]
+    spectrum.emitted = spectrum_temp[2]
+    spectrum.censrc = spectrum_temp[3]
+    spectrum.disk = spectrum_temp[4]
+    spectrum.wind = spectrum_temp[5] 
[…]

### 2015-01-13 generate/wind_plot/for_Sam/read_sub.py

@@ -1,0 +1,200 @@
+import numpy as np
+import time
+import sys
+import os
+
+
+class specclass:
+    '''This is a class for storing any values read from a Python spec file'''	
+    def __init__(self, fre, wave, emi, cen, dis, win, sca, hit, spe):
+        self.freq = fre
+        self.wavelength = wave
+        self.emitted = emi
+        self.censrc = cen
+        self.disk = dis
+        self.wind = win
+        self.scattered = sca
+        self.hitSurf = hit
+        self.spec = spe
+
+
+def read_spec_file (filename):
+    
+    '''reads a Python .spec file and places in specclass array,
+       which is returned'''
+    
+    if not '.spec' in filename: 
+        filename = filename + '.spec'
+        
+    
+    # initialise the spectrum array with blank arrays
+    spectrum = specclass ([],[],[],[],[],[], [], [], []) 
+    
+    # first read the file into a temporary storage array
+    spectrum_temp = np.loadtxt (filename, comments ='#', unpack=True)
+    
+    # now set the correct elements of the class to be the temporary array
+    spectrum.freq = spectrum_temp[0]
+    spectrum.wavelength = spectrum_temp[1]
+    spectrum.emitted = spectrum_temp[2]
+    spectrum.censrc = spectrum_temp[3]
+    spectrum.disk = spectrum_temp[4]
+    spectrum.wind = spectrum_temp[5] 
+    spectrum.scattered = spectrum_temp[7]
+    spectrum.hitsurf = spectrum_temp[6]
+    spectrum.spec = spectrum_temp[8:]
+        
+     #finally, return the spectrum class which is a series of named arrays      
+    return spectrum
+
+
+
+def run_py_wind (vers, fname, cmds=None, ilv=None):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	if cmds == None:
+		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i","0", "1","1","1","2","2","2","2","1","2","3","6", \
+			          "3","6","4","6","5","0","q"])
+
+	x = cmds
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+
+
+def read_pywind_smart(filename, return_inwind=False):
+	'''
[…]

### 2015-01-13 generate/wind_plot/he2_bl_plot.py

@@ -1,0 +1,229 @@
+import matplotlib.pyplot as plt 
+from pylab import * 
+import numpy as np 
+import csv, sys, os, array, warnings, subprocess
+import pywind_sub as ps
+import matplotlib as mpl
+from matplotlib.mlab import bivariate_normal
+from matplotlib.colors import LogNorm
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib as mpl
+import time
+import read_output as rd
+import matplotlib.gridspec as gridspec
+
+
+def run_py_wind (vers, fname, cmds=None, ilv=None):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	if cmds == None:
+		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i","0", "1","1","1","2","2","2","2","1","2","3","6", \
+			          "3","6","4","6","5","0","q"])
+
+	x = cmds
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+
+
+
+def run_pydc (vers, fname, nplasma = 1):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	x = np.array(["1","M","4",str(nplasma),"1","-1","r","n","t","w", "q"])
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+#ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
+
+
+
+#nplasmas = ps.pywind_read(fname+'.pnum.dat',ix,iz)
+
+def read_pywind_smart(filename, return_inwind=False):
+	'''
+	read a py_wind file using np array reshaping and manipulation
+	'''
+
+	# first, simply load the filename 
[…]

### 2015-01-13 generate/wind_plot/make_windplot.py

@@ -1,0 +1,202 @@
+import matplotlib.pyplot as plt 
+from pylab import * 
+import numpy as np 
+import csv, sys, os, array, warnings, subprocess
+import pywind_sub as ps
+import matplotlib as mpl
+from matplotlib.mlab import bivariate_normal
+from matplotlib.colors import LogNorm
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib as mpl
+import time
+import py_read_output as r
+import read_output as rd
+
+
+def run_py_wind (vers, fname, cmds=None, ilv=None):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	if cmds == None:
+		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i", "1","1","1","2","0","i","0", "1","1","1","2","2","2","2","1","2","3","6", \
+			          "3","6","4","6","5","0","q"])
+
+	x = cmds
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+
+
+
+def run_pydc (vers, fname, nplasma = 1):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	x = np.array(["1","M","4",str(nplasma),"1","-1","r","n","t","w", "q"])
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+#ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
+
+
+
+def read_pywind_logspace(filename):
+
+	'''
+	convert to logspace coordinates
+	'''
+
+	x,z,s = r.read_pywind(filename)
+
[…]

### 2015-01-13 generate/wind_plot/pywind_summary_paper.py

@@ -1,0 +1,218 @@
+#! /Library/Frameworks/EPD64.framework/Versions/Current/bin/python -i
+
+import csv, sys, os, array, warnings, subprocess
+import matplotlib.pyplot as plt
+import numpy as np
+import pywind_sub as ps
+import matplotlib as mpl
+from matplotlib.mlab import bivariate_normal
+from matplotlib.colors import LogNorm
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib as mpl
+
+mpl.rcParams['text.usetex']='true'
+
+
+fname=sys.argv[1]
+
+#cmdline='py_wind78a '+fname+' < paper_pywindcmds'
+#subprocess.check_call(cmdline,shell=True)	
+
+x=[]
+z=[]
+x1=[]
+z1=[]
+lx=[]
+lz=[]
+lx1=[]
+lz1=[]
+
+data=[]
+IPtemp=[]
+tetemp=[]
+nhtemp=[]
+xtemp=[]
+ztemp=[]
+
+tetemp=[]
+trtemp=[]
+
+convtemp=[]
+
+vx=[]
+vz=[]
+
+H1=[]
+H2=[]
+C4temp=[]
+Si4temp=[]
+N5temp=[]
+O6temp=[]
+
+
+
+ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
+
+
+
+H1=ps.pywind_read(fname+'.ioncH1.dat',ix,iz)
+H2=ps.pywind_read(fname+'.ioncH2.dat',ix,iz)
+
+H=np.empty([ix,iz])
+for i in range(ix):
+	for j in range(iz):
+		H[i][j]=np.log10(H1[i][j]+H2[i][j])
+
+
+
+IP=ps.pywind_read(fname+'.IP.dat',ix,iz)
+te=ps.pywind_log_read(fname+'.te.dat',ix,iz)
+#tr=ps.pywind_log_read(fname+'.tr.dat',ix,iz)
+vx=ps.pywind_read(fname+'.vz.dat',ix,iz)
+vy=ps.pywind_read(fname+'.vy.dat',ix,iz)
+vz=ps.pywind_read(fname+'.vz.dat',ix,iz)
+#nagn=ps.pywind_log_read(fname+'.nphot.dat',ix,iz)
+
+
+
+
+
+vxz=np.empty([ix,iz])
+for i in range(ix):
+	for j in range(iz):
[…]

### 2015-01-13 generate/wind_plot/windplot_new.py

@@ -1,0 +1,253 @@
+import matplotlib.pyplot as plt 
+from pylab import * 
+import numpy as np 
+import csv, sys, os, array, warnings, subprocess
+import pywind_sub as ps
+import matplotlib as mpl
+from matplotlib.mlab import bivariate_normal
+from matplotlib.colors import LogNorm
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib as mpl
+import time
+import read_output as rd
+
+
+def run_py_wind (vers, fname, cmds=None, ilv=None):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	if cmds == None:
+		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i", "1","1","1","2","0","i","0", "1","1","1","2","2","2","2","1","2","3","6", \
+			          "3","6","4","6","5","0","q"])
+
+	x = cmds
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+
+
+
+def run_pydc (vers, fname, nplasma = 1):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	x = np.array(["1","M","4",str(nplasma),"1","-1","r","n","t","w", "q"])
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+#ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
+
+
+
+#nplasmas = ps.pywind_read(fname+'.pnum.dat',ix,iz)
+
+def read_pywind_smart(filename, return_inwind=False):
+	'''
+	read a py_wind file using np array reshaping and manipulation
+	'''
+
+	# first, simply load the filename 
[…]

### 2015-01-15 draft.tex
a few more changes discussion and runs for figs

@@
 narrowing of the double-peaked emission lines from the base of the wind. 
-We suggest that a non-homogenous, `clumpy' wind may provide a possible
+We suggest that a nonhomogenous, `clumpy' wind may provide a possible
 solution.
@@
 eclipsed, and a significant fraction of the line flux remains visible
-even near mid-eclipse (REF). This points to line formation in a spatially
+even near mid-eclipse \citep[e.g.][]{groot2004}. This points to line formation in a spatially
 extended region, such as a disk wind (see figure~\ref{novalikes}).
@@
 particular, the SEDs predicted by most stellar/disk atmosphere models 
-are too blue in the UV \citep{wade1988,long1991,long1994}(Other refs here?) and exhibit
+are too blue in the UV \citep{wade1988,long1991,long1994} and exhibit
 stronger-than-observed Balmer jumps in absorption 
@@
 
-We adopt the kinematic disk wind model developed by Schlosman \&
-Vitello (1993; hereafter SV93). A schematic of this model is shown in
+We adopt the kinematic disk wind model developed by SV93. 
+A schematic of this model is shown in
 figure~\ref{cartoon}. In this parametrization, a smooth, biconical
@@
 does not produce all the lines seen in observations of high-state CVs.
-The higher order Balmer series lines too weak
+The higher order Balmer series lines are too weak
 to overcome the intrinsic absorption from the disk atmosphere, and the wind 
@@
 \citep{beuermann1990}.
-
-Our models do not exhibit P-Cygni profiles in the optical lines.
-This is perhaps not surprising. LK02 and SV93 originally designed such models
-to reproduce the UV line profiles. Thus, most of the wind
-has an ionization parameter of $\log U \sim 2$ (see figure 6).
-This means Hydrogen and Helium are fully ionized throughout 
-much of the wind and is successful in producing recombination features.
-However, it leads to absorbing columns in \ha\ of $N_H\sim ??$ - far too
-low to produce noticeable blue shifted absorption. 
-While we suspect that the winds that exhibit such profiles must 
-lie in a different ionization regime, requiring 
-significantly different disk SEDs or mass-loss rates to a 
-`standard' high-state CV. However, we note it is difficult for this
-idea to exist within a line-driven wind framework.
 
@@
 spectrum. First, the collisionally excited Ca~{\sc ii} H\&K 
-emission lines at 3969\AA\ and (especially) 3934\AA\ 
-become quite prominent in our densest models. Second, our model predicts a detectable
+emission line at 3934\AA\ 
+becomes quite prominent in our densest models. Second, our model predicts a detectable
 He~\textsc{ii} recombination line at 3202\AA. This is the Helium
@@
 % I blieve CK found a paper which shows it in an IP? I'll try and find it.}
+
+Our models do not exhibit P-Cygni profiles in the optical lines.
+This is perhaps not surprising. LK02 and SV93 originally designed such models
+to reproduce the UV line profiles. Thus, most of the wind
+has an ionization parameter of $\log U \sim 2$ (see figure 6).
+This means Hydrogen and Helium are fully ionized throughout 
+much of the wind and is successful in producing recombination features.
+However, it leads to absorbing columns in H of $N_H\sim ??$ - far too
+low to produce noticeable blue shifted absorption. 
+We therefore suspect that the winds that exhibit such profiles must 
+possess a higher degree of ionization stratification.
+This could manifest as a clumpy flow, in which ionization changes
+due to small scale density fluctuations, or a stratification on acceleration 
+length scales such as the kind shown by figure 6.
+This idea is supported by the fact that \cite{prinja2000}
+found dwarf nova BZ Cam's outflow to be unsteady and highly mass-loaded in outburst,
+by observing the UV resonance lines in outburst with the {\sl Hubble Space Telescope}.
+This system has exhibited P-Cygni profiles in He~\textsc{i}~$\lambda5876{\rm \AA}$
+and \ha\ when in a high-state \cite{patterson1996,RN98}.
 
@@
 P-Cygni resonance lines seen in the UV (LK02, Noebauer et al. 2010),
-We note that equatorial winds are expected in AGN and X-ray binaries 
-\citep{ponti2012}, and that these winds may be more likely
-to exhibit the required kinematics.
+Equatorial winds are expected in AGN and X-ray binaries 
+\citep{weymann1991, ponti2012}, so these winds may be more likely
+to possess the required kinematics.
 Second, one could adopt velocity laws with higher 
@@
 in CV winds provides a possible solution.
-Non-homogeneity could allow higher density pockets 
-of emission to exist with radial velocity shear still being high.
-Line-driven winds are expected to be unstable (REFS),
-and a number of implementations have been used in the stellar wind
-community (REFS). We therefore hope that further investigation of
-clumped winds could help solve the current `mystery' of single-peaked 
+Inhomogeneity could allow higher density pockets 
+of emission to exist while still possessing a high radial velocity shear.
+Theory of line-driven winds predicts an unstable flow
+\citep{macgregor1979,owockirybicki1984,owockirybicki1985},
+and simulations of accretion disk winds find a nonhomogeneous 
+density structure \citep{proga1998,pkdh2002}.
+In addition, a number of implementations have been used in the stellar wind
+community \citep[e.g.][]{hamannkoesterke1998,oskinova2007}. 
+We therefore hope that further investigation of
+`clumpy' winds could help solve the current mystery of single-peaked 
 line emission in high inclination systems.
-
-% Although \ha\ is single-peaked in our model, the majority of the
-% lines are double-peaked, particularly  
-% Figure~\ref{halpha} shows how the H$\alpha$
-% % He~{\sc ii}~$\lambda 4686$ 
-% line changes with the kinematics of the wind
-% for an inclination of $80^\circ$. 
-% % The width and strength of He~{\sc ii} 
-% % clearly depend on both $R_v$ and $\alpha$, but the overall line profile 
-% % shape is always double-peaked. This contrasts with the behaviour of 
-% The line becomes single-peaked in our densest models. 
-% The transition from double-peaked to single-peaked occurs when the 
-% line becomes optically thick. This reproduces the behaviour predicted by fsingle-pe96, who
-% showed that the poloidal velocity gradient in the wind can modify the
-% shape of optically thick emission lines even in the near-disk regime,
-% where the poloidal velocity itself is much smaller than the rotational
-% velocity. This has the effect of suppressing the line wings and
-% can therefore lead to the production of a single-peaked line profile
-% shape.
 
@@
 \caption{
-\ha\ line profiles, normalised to 1, plotted in veliocity space 
+\ha\ line profiles, normalised to 1, plotted in velocity space 
 for three models with varying kinematic 
@@
 We observe a narrowing of the lines
-but this is not due to the radial velocity shear mechanism (see section 5.3
+but this is not due to radial velocity shear (see section 5.3
 for a discussion).
-% The parameter that has been altered from the benchmark model 
-% is marked in each column and row. Models towards the bottom right
-% are have more slowly accelerating winds and denser wind bases. 
-% {\bf JM: Need to discuss the `single-peaked-ness' of line profiles
-% in our telecon.}
 }
@@
 %
-%          DISCUSSION
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \section{The Dependence of Wind Features on Outflow Parameters}
-%  Here we could discuss single-peaked emission and trends with parameters.
-% \label{modelb}
-
-% The results of section~\ref{modela} show that wind models that reproduce
-% the UV spectral features of CVs are likely to leave a clear imprint on
-% the optical spectrum. It is therefore important to understand the
-% sensitivity of optical (and UV) wind-formed features to the basic
-% properties of the outflow. In particular, there are three key questions
-% we would like to address: (i) can a modified wind model account 
-% for all of the lines we see in optical spectra of CVs while preserving
-% the UV behaviour;
-% (ii) under what conditions can disk winds
-% produce {\em single-peaked} Balmer emission lines (MC96); 
-% (ii) can the wind-formed recombination continuum completely
-% fill in the disk's Balmer absorption edge for reasonable outflow
-% parameters?
-
-% The amount of recombination and collisionally excited emission
-% produced by a given ion, $i$, in a plasma of volume $V$ depends
-% primarily on the emission measure, $EM$, defined as 
-% \begin{equation}
-% EM=\int^V_0 n_e n_i \,dV,
-% \end{equation}
-% where $n_i$ is the number density of the ion in question.    
-% The emission reaching an observer at a given frequency also depends on
-% the Sobolev optical depth it experiences, which depends on both the
-% density and the velocity gradient projected along the line of
-% sight. This can also significantly affect line profile shapes.
-
-% The simplest way to simultaneously affect the density in the wind as
-% well as the velocity gradients is by modifying the poloidal velocity
-% law. We have therefore conducted a exploratory sensitivity study in
-% which we focus on just two kinematic variables (section~\ref{kinematics}):
-
-% \begin{itemize}
-%  	\item the acceleration length, $R_v$, which controls the
-%         distance over which the wind accelerates to $\frac{1}{2}v_{\infty}$;
-%  	\item the acceleration exponent, $\alpha$, which controls the rate 
-%  	at which the poloidal velocity changes near $R_v$.
-% \end{itemize} 
-% The general behaviour we might expect is that outflows with denser
-% regions near the wind base -- i.e. winds with larger $R_{v}$ and/or
-% larger $\alpha$ -- will produce stronger optical emission signatures. 
-% However, this behaviour may be moderated by the effect of the increasing
-% optical depth through this region.
-
-% \subsection{Optical Wind Signatures}
-% \label{modelb_opt}
-
-% Figure~\ref{halpha} shows how overall spectrum
-% changes with the kinematics of the wind for an inclination
-% of $80^\circ$. The width and strength of He~{\sc ii} clearly depend on
-% both $R_v$ and $\alpha$, but the overall line profile shape is always
-% double-peaked. This contrasts with the behaviour of H$\alpha$, which
-% becomes single-peaked in our densest models. The transition from
-% double-peaked to single-peaked occurs when the line becomes optically
-% thick. This reproduces the behaviour predicted by \cite{MC96}, who
-% showed that the poloidal velocity gradient in the wind can modify the
-% shape of optically thick emission lines even in the near-disk regime,
-% where the poloidal velocity itself is much smaller than the rotational
-% velocity. This has the effect of suppressing the line wings and
-% can therefore lead to the production of a single-peaked line profile
-% shape.
-
-% Figure~\ref{halpha} shows how the H$\alpha$ and 
-% He~{\sc ii}~$\lambda 
-% 4686$ lines change with the kinematics of the wind for an inclination
-% of $80^\circ$. The width and strength of He~{\sc ii} clearly depend on
-% both $R_v$ and $\alpha$, but the overall line profile shape is always
-% double-peaked. This contrasts with the behaviour of H$\alpha$, which
-% becomes single-peaked in our densest models. The transition from
-% double-peaked to single-peaked occurs when the line becomes optically
-% thick. This reproduces the behaviour predicted by \cite{MC96}, who
-% showed that the poloidal velocity gradient in the wind can modify the
-% shape of optically thick emission lines even in the near-disk regime,
-% where the poloidal velocity itself is much smaller than the rotational
-% velocity. This has the effect of suppressing the line wings and
-% can therefore lead to the production of a single-peaked line profile
-% shape.
-
-% In order to produce single-peaked line emission in the majority of
-% lines at high inclinations, even higher opacity is needed in the
-% line wings. This difficulty in generating single-peaked line emission
-% from a rotating disk wind was also encountered by SDL05, who found
-% that an outflow geometry similar to that adopted here could not 
-% reproduce the observed single peaked profiles in YSOs. For the
-% parameters we have tested, the mechanism proposed by \cite{MC96} does
-% produce single-peaked profiles, but only for most optically thick
-% emission lines. In order for the same mechanism to affect the majority
-% of lines, even higher wind densities would be required.
-
-% Figure~\ref{jump} shows the behaviour of the Balmer jump region as a
-% function of the kinematic wind parameters. Here, we clearly see the
-% critical effect of the emission measure, with the densest winds
-% filling in the disk's Balmer absorption edge most effectively.
-% \footnote{Note that the apparent absorption feature 
-% just redward of the Balmer jump in these models is artificial. It is
-% caused by residual line blanketing in the stellar atmospheres, which
-% our models cannot fill in since they employ a 20-level Hydrogen atom.}
-% This offers a potential solution to a long-standing problem in
-% understanding the spectral energy distribution of CVs, as
-% originally suggested by \cite{KLWB98}.
-
-% Two other features are worth noting in this part of the
-% spectrum. First, the collisionally excited Ca~{\sc ii} H\&K 
-% emission lines at 3969\AA\ 
-% and (especially) 3934\AA\ become quite prominent in our densest
-% models. Second, {\em all} of our models predict a detectable
-% He~\textsc{ii} recombination line at 3202\AA. This is the Helium
-% equivalent of Paschen~$\beta$ and should be expected in all systems that
-% feature a strong He~\textsc{ii}~4686\AA\ line (the Helium
-% equivalent of Paschen~$\alpha$). This line is unfamiliar observationally,
-% but only because it lies bluewards of the atmospheric cut-off, but
-% also redwards of most ultraviolet spectra. 
-% {\bf JM: we should we reference something here for the 3202 line. 
-% I blieve CK found a paper which shows it in an IP? I'll try and find it.}
-
-% \begin{figure} %fullpage
-% \centering
-% \includegraphics[width=1.0\textwidth]{figures/3by3_grid_balmer.eps}  
-% %%\includegraphics[width=0.5\textwidth]{figures/test.eps}
-% \caption{
-% The evolution of the Balmer jump with varying kinematic 
-% properties, computed for an inclination of $80^\circ$. 
-% The panels are organised in the same way as figure~\ref{halpha}.
-% {\bf JM: Mark lines here?}
-% % The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
-% % lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
-% % when the wind becomes a neutral absorbing column.
-% }
-% \label{jump}
-% \end{figure} %fullpage
-
-% \subsection{Ultraviolet Wind Signatures}
-% \label{modelb_uv}
-
-% The dependence of the ultraviolet C~{\sc iv} and He~{\sc ii} lines on
-% the same kinematic wind parameters is illustrated in figures~\ref{uvlines}
-% and~\ref{uvlines}. As before, we focus on the predicted behaviour at $i =
-% 80^\circ$. In our benchmark model, the C~{\sc iv} emission
-% line seen at high inclinations is almost entirely produced via
-% resonance scattering. The angle-averaged flux integrated over the
-% entire line profile - accounting correctly for the blue-shifted
-% absorption component seen at low inclinations - would be
-% approximately zero. However, as we increase the density and extent of
-% the slow-moving part of the outflow near the disk plane, collisionally
-% excited emission starts to contribute significantly to the C~{\sc iv}
-% line profiles. This explains the much stronger line-to-continuum
-% contrast seen in the $\alpha = 1.5$, $R_v = 2\times 10^{11}$~cm model,
-% for example. For any given inclination, the trend is not necessarily
-% monotonic, however, because the escape probabilities from the
-% line-forming region can be highly anisotropic.  
-% {\bf CK: I *think* this is the basic reason, but (a) can you check
-%   this, James; (b) is it enough to just point this out?; (c) do we
-%   understand why CIV is single-peaked but HeII, for example, is double-peaked?
-%   JM: There are still a few tests I want to do here- we can discuss in the telecon.
-%   I believe He II v CIV shape is just due to CIV being produced in an extended region,
-%   and generally scattered, whereas He II is produced close to the disk, and there's probably
-%   also a line opacity effect.
-%   I can check this.}
-
-% The He~{\sc ii}~1640\AA recombination line is always double-peaked in
-% our models, although the peak-to-peak separation decreases in the
-% denser models. For double-peaked lines
-% formed in rotating media -- in this case, the dense base of the wind
-% -- the location of the peak(s) is roughly associated with the
-% projected rotational velocity at the outer edge of the line-forming
-% region. Thus the trend observed in He~{\sc ii} reflect the radial
-% expansion of the line-forming region associated with an increase in
-% the density at the base of the wind. The same trend is actually also
-% seen in the optical He~{\sc ii}~4686\AA line. The strength of these
-% features relative to their adjacent continua also track
-% each other approximately. The reason for the non-monotonic behaviour
-% in the line strengths as a function of the kinematic wind parameters
-% is the same as for the C~{\sc iv} line.
-% {\bf CK: again, can we check this is correct?}
-
-% \begin{figure} %fullpage
-% \mbox{
-% % \subfigure{\includegraphics[width=0.33\textwidth]{figures/3by3_grid_lyman.eps}}  
-% % \quad
-% \subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_uv.eps}}
-% \quad
-% \subfigure{\includegraphics[width=0.5\textwidth]{figures/3by3_grid_1640.eps}}  
-% }
-% %%\includegraphics[width=0.5\textwidth]{figures/test.eps}
-% \caption{
-% Line profiles for \civ\ (left) and \heiiuv\  (right) with varying kinematic 
-% properties, computed for an inclination of $80^\circ$. 
-% The panels are organised in the same way as figure~\ref{halpha}.
-% {\bf JM: I need to adjust the smoothing here so for all plots I smooth
-% in terms of Wavelength rather than bins. Linked to single-peaked discussion. 
-% Note also CK may want a Lyman alpha plot, which I might put here}
-% % The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
-% % lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
-% % when the wind becomes a neutral absorbing column.
-% }
-% \label{uvlines}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
 %          Conclusions and Future Work
@@
 Possible reasons for this are briefly discussed in section 
-4.2.
+5.2.
 
@@
 by eclipse-mapping observations (REFS). We suggest
-that non-homogenous, 
-`clumpy' line-driven winds may offer a potential solution.
+that nonhomogenous, `clumpy' line-driven winds may offer a potential solution.
 

### 2015-01-15 generate/fig1_nl_spectra1/plot2.py

@@ -3,7 +3,7 @@ import numpy as np
 from pylab import *
 import os, sys
 from cobra_sub import smooth
-import read_output as rd
+import py_read_output as rd
 rd.setpars()
 
 def gauss(sigma, x0, x):
@@ -121,9 +121,12 @@ ylim(0.1,40)
 # plot model
 scale = 2.718 / 0.036
 subplot(212)
-s = rd.read_spec_file("cv_alpha4_r4r12_mdot1e9_rv1e11_opt")
-plot( s.wavelength, smooth(s.spec[-3], window_len=5)*1e11*scale,  c=colour, linewidth=weight)
-plot( s.wavelength, smooth(s.spec[-2], window_len=5)*1e11*scale,  c=colour, linewidth=weight)
+s = rd.read_spectrum("cv_alpha4_r4r12_mdot1e9_rv1e11_opt")
+s2 = rd.read_spectrum("../../latest_outputs/cv_alpha4_r4r12_mdot1e9_rv1e11_opt")
+plot( s["Lambda"], smooth(s["A80P0.50"], window_len=5)*1e11*scale,  c=colour, linewidth=weight)
+plot( s["Lambda"], smooth(s["A80P0.00"], window_len=5)*1e11*scale,  c=colour, linewidth=weight)
+plot( s2["Lambda"], smooth(s2["A80P0.50"], window_len=5)*1e11*scale,  c='r', linewidth=weight)
+plot( s2["Lambda"], smooth(s2["A80P0.00"], window_len=5)*1e11*scale,  c='r', linewidth=weight)
 xlim(3700,6900)
 
 

### 2015-01-15 draft.tex
tweaked figures and text

@@
 \includegraphics[width=0.8\textwidth]{figures/fig1.eps}
-\caption{Optical spectra of three nova-like variables: 
+% \caption{Optical spectra of three nova-like variables: 
+% RW Sex (top; Beuermann et al. 1992),
+% IX Vel (top middle; Beuermann \& Thomas 1990) 
+% and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
+% The data have been digitized from the respective publications and a few of the more
+% prominent emission and absorption lines are marked. 
+\caption{
+Optical spectra of three nova-like variables: 
 RW Sex (top; Beuermann et al. 1992),
-IX Vel (top middle; Beuermann \& Thomas 1990) 
+IX Vel (top middle; A. Pala \& B. Gaensicke, private communication) 
 and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
-The data have been digitized from the respective publications and a few of the more
-prominent emission and absorption lines are marked. 
-These systems have inclinations of $30^\circ$, $60^\circ$ and $70^\circ$ 
-respectively. 
+The data for RW Sex and RW Tri were digitized from the respective publications,
+and the IX Vel spectrum was obtained using XShooter on the VLT on the night of ??.
+These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $70^\circ$ 
+(see section 5.4) respectively. 
 The trend of increasing Balmer line emission with inclination can be seen.
@@
 $M_{2}$ 	 &	 $0.6 M_{\odot}$  &   \\ 
+$q$ 	 &	 $0.75 M_{\odot}$  &   \\ 
+$P_{orb}$ 	 &	 $5.57$~hr  &   \\ 
 $\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$  &\\ 
@@
 Parameters used for the geometry and kinematics of the benchmark 
-CV model (Model A), which is optimized for the UV band, and a model
-which is optimized for the optical band and described in section 6 (Model B).
-For Model B, only parameters which are altered are given - otherwise the
-Model A parameter is used.
+CV model (model A), which is optimized for the UV band, and a model
+which is optimized for the optical band and described in section 5 (model B).
+For model B, only parameters which are altered are given - otherwise the
+model A parameter is used.
 {\bf JM: this needs some stuff adding, as is mentioned in certain places}}
@@
 and LK02 to simulate the UV spectrum of a typical high-state
-system. The specific parameters for this model (Model A) are listed in
+system. The specific parameters for this model (model A) are listed in
 Table~1. A key point is that the wind mass-loss rate in this model is
@@
 \includegraphics[width=0.45\textwidth]{figures/modela_opt_cont.eps}
-\caption{Synthetic optical spectra computed for 
+\caption{Synthetic optical spectra from model A computed for 
 sightlines of 10, 27.5, 45, 62.5 and 80 degrees. In these plots
@@
 The thick black line shows the total 
-integrated escaping spectrum, while green and red lines show the contributions from photons that originate in the disk and wind respectively. 
+integrated escaping spectrum, 
+while the green line shows disk photons which escape without being reprocessed by
+the wind. The red line show the contributions from reprocessed photons. 
 Recombination continuum emission blueward of the Balmer 
@@
 construct a model that more closely matches the observed optical
-spectra of CVs (imaginatively dubbed `Model B').
+spectra of CVs.
 
@@
 \caption{
-Synthetic optical spectra computed for 
+Synthetic optical spectra from model B computed for 
 sightlines of 10, 27.5, 45, 62.5 and 80 degrees. In these plots
@@
 The thick black line shows the total 
-integrated escaping spectrum, while green and red lines show the contributions from photons that originate in the disk and wind respectively. 
-Recombination continuum emission blueward of the Balmer 
-edge is already prominent relative to other wind continuum processes, but is not sufficient
-to fill in the Balmer jump in this specific model}
+integrated escaping spectrum, 
+while the green line shows disk photons which escape without being reprocessed by
+the wind. The red line show the contributions from reprocessed 
+photons. 
+In this denser model the reprocessed contribution is significant compared
+to the escaping disk spectrum. The Balmer continuum emission is prominent, and
+we can see a clear effect on the overall spectral shape from the wind.}
 \label{modelb_escape}
@@
 wind geometry is that it already successfully models the 
-P-Cygni resonance lines seen in the UV (LK02, Noebauer et al. 2010),
+P-Cygni resonance lines seen in the UV (LK02; Noebauer et al. 2010),
 Equatorial winds are expected in AGN and X-ray binaries 
@@
 inclination NL RW Tri. {\sl Bottom Panel:} In and out of eclipse synthetic
-spectra from Model B.
+spectra from model B.
 The artificial `absorption' feature just redward of the Balmer jump

### 2015-01-15 generate/fig1_nl_spectra1/plot2.py

@@ -123,11 +123,17 @@ scale = 2.718 / 0.036
 subplot(212)
 s = rd.read_spectrum("cv_alpha4_r4r12_mdot1e9_rv1e11_opt")
 s2 = rd.read_spectrum("../../latest_outputs/cv_alpha4_r4r12_mdot1e9_rv1e11_opt")
+
+scale2 = scale / 1.7627659414
 plot( s["Lambda"], smooth(s["A80P0.50"], window_len=5)*1e11*scale,  c=colour, linewidth=weight)
 plot( s["Lambda"], smooth(s["A80P0.00"], window_len=5)*1e11*scale,  c=colour, linewidth=weight)
-plot( s2["Lambda"], smooth(s2["A80P0.50"], window_len=5)*1e11*scale,  c='r', linewidth=weight)
-plot( s2["Lambda"], smooth(s2["A80P0.00"], window_len=5)*1e11*scale,  c='r', linewidth=weight)
+plot( s2["Lambda"], smooth(s2["A80P0.50"], window_len=5)*1e11*scale2,  c='r', linewidth=weight)
+plot( s2["Lambda"], smooth(s2["A80P0.00"], window_len=5)*1e11*scale2,  c='r', linewidth=weight)
 xlim(3700,6900)
+
+print np.mean(s2["A80P0.50"]) / np.mean(s["A80P0.50"])
+print np.mean(s2["A80P0.50"]) / np.mean(s["A80P0.50"]) * 5
+print np.mean(s2["A80P0.50"]) / np.mean(s["A80P0.50"]) * 4
 
 
 # text and labels

### 2015-01-15 generate/fig1_nl_spectra1/plot_nl_figure.py

@@ -69,7 +69,6 @@ dd_no = dd_no * nus_no / cc_no
 
 
 
-
 ##############
 # plot RW Sex
 ##############
@@ -77,15 +76,10 @@ subplot(411)
 plot(x1,y1, c=colour ,linewidth=weight)
 semilogy()
 
-ylabel("Flux\n($10^{-13}$~erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$)", fontsize = 12)
+#ylabel("Flux\n($10^{-13}$~erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$)", fontsize = 12)
 text( 6000, 3.5,"RW Sex", fontsize = font3)
 
-lines = [5879,6680,
-         4686, 5410,
-         6563, 4861, 4341,	4102]
-labels = [r"He~\textsc{i}",r"He~\textsc{i}",
-          r"He~\textsc{ii}",r"He~\textsc{ii}",
-          r"H$\alpha$",r"H$\beta$", r"H$\gamma$", r"H$\delta$"]
+
 
 
 gca().set_xticklabels([])
@@ -112,42 +106,113 @@ ax.yaxis.set_major_locator(majorLocator)
 ##############
 # plot IX Vel
 ##############
+# subplot(412)
+# plot(x[(y > 0.92745)][20:-10],smooth(y[(y > 0.92745)][20:-10] , window_len=20), c=colour,linewidth=weight)
+
+# plot( a[45:], b[45:], c=colour, linewidth=weight)
+
+# gca().set_xticklabels([])
+# xlim(3500,6900)
+# ylim(0.7, 4.2)
+# vlines([3646], 0.7, 4.2, linestyle="--")
+# semilogy()
+
+# majorFormatter = FormatStrFormatter('%d')
+# majorLocator   = MultipleLocator(1)
+# minorFormatter = FormatStrFormatter('%d')
+
+# # ax.yaxis.set_major_locator(majorLocator)
+# ax = gca()
+# ax.yaxis.set_major_formatter(majorFormatter)
+# ax.yaxis.set_major_locator(majorLocator)
+
+# # text and labels
+# ylabel("Relative Flux", fontsize = 12)
+# text( 6000, 1.4, "IX Vel", fontsize =font3)
+
+# 
+import pyfits as py
+def get_lambda(fname, length):
+  
+  delta = py.getval(fname, "CDELT1")
[…]

### 2015-01-15 generate/fig2_cartoon/SV_cartoon.py

@@ -60,7 +60,7 @@ plt.plot(0.0,0.0,'o',color='w',ms=20.0)
 
 
 ''' This is for the radiating sources'''
-ax.annotate(r'$\rm{White~Dwarf}$', xy=(-0.5,0.6),xytext=(-20,7),fontsize=lsize,arrowprops=dict(arrowstyle="->"),)
+ax.annotate(r'$\rm{White~Dwarf}$', xy=(-0.5,0.6),xytext=(-17,8),fontsize=lsize,arrowprops=dict(arrowstyle="->"),)
 ax.annotate(r'$\rm{Accretion~Disk}$', xy=(-5.0,0.1),xytext=(-26,5.5),fontsize=lsize,arrowprops=dict(arrowstyle="->"),)
 plt.text(-35,5,r'$\rm{Biconical~wind}$',fontsize=lsize,rotation=-37.0)
 

### 2015-01-15 generate/fig_levels/make_fig_caseb_and_tardis.py

@@ -157,7 +157,7 @@ figure()
 
 subplot(211)
 
-scatter(n_array, matom_emiss / hbeta,  label = '\\textsc{Python}', s=100, edgecolors='k', facecolors='none')
+scatter(n_array, matom_emiss / hbeta,  label = '\\textsc{Python}', s=150, edgecolors='k', facecolors='none')
 scatter(n_array[2:10], seaton, label = 'Seaton (1959)',s=40, color='k')
 xlabel( "$n$", fontsize=20)
 ylabel( r"Balmer decrement ($F_n$ / $F_{\beta}$)" , fontsize=20)
@@ -170,7 +170,7 @@ legend()
 
 # relative to ground state in this example
 subplot(212)
-scatter(n[:nlevs_tardis], np.log10(levpops[:nlevs_tardis]/levpops[0]), label = '\\textsc{Python}', s = 100, facecolors="none", c="k")
+scatter(n[:nlevs_tardis], np.log10(levpops[:nlevs_tardis]/levpops[0]), label = '\\textsc{Python}', s = 150, facecolors="none", c="k")
 scatter(n[:nlevs_tardis], np.log10(tardis_levs/tardis_levs[0]), label = '\\textsc{Tardis}', s=40, c="k")
 xlabel("Helium level, $i$", fontsize=20)
 ylabel("$\log (n_i / n_0)$", fontsize=20)

### 2015-01-18 draft.tex
Some more edits- pushing for laptop

@@
 \usepackage{subfigure}
+\usepackage{amsmath}
+\usepackage{amssymb}
+%\usepackage{aastex}
 %\usepackage{epsfig}
@@
 uses the Sobolev approximation to treat line transfer. It has already
-been described extensively in LK02, SDL05 and H13, so here we provide
+been described extensively by LK02, SDL05 and H13, so here we provide
 only a brief summary of its operation, focusing particularly on new
@@
 We generally use the same atomic data as H13, which is an updated
-version of that described in LK02. In addition, we follow SDL05 in
+version of that described by LK02. In addition, we follow SDL05 in
 treating Hydrogen as a 20-level atom, where each level is defined by
@@
 radiative properties of the wind-driving system under
-consideration. Most of these features have already been discussed in
+consideration. Most of these features have already been discussed by
 LK02 and H13, so below we only briefly recount the key aspects of the
@@
 
-The ionization equation used in the ``simple atom'' approach used in
+The ionization equation used in the ``simple atom'' approach used by
 LK02 (see section~\ref{simpleatoms}) should be a reasonable approximation to
@@
 resulting ionization state of the wind to be quite similar to that
-found in LK02. The bottom panels in figure~\ref{wind} confirm that this
+found by LK02. The bottom panels in figure~\ref{wind} confirm that this
 is the case. In particular, Helium is fully ionized
@@
 base of the wind, which is shielded from the photons produced by the
-hot inner disk. In line with the results shown in LK02, we also find
+hot inner disk. In line with the results of LK02, we also find
 that C\textsc{iv} is the dominant Carbon ion throughout the wind,
@@
 the case, since the ionization state of the wind has not changed
-significantly from that computed in LK02 (see section~\ref{modela_ionization}). 
+significantly from that computed by LK02 (see section~\ref{modela_ionization}). 
 The left column of panels in figure~\ref{spec} shows that this expectation
@@
 fails to produce any emission at intermediate inclinations, 
-which contrasts with (for example) the observed behaviour of IX Vel
-\citep{beuermann1990}.
+which contrasts with (for example) the observed behaviour of V3885 Sgr \citep{hartley2005}
+and IX Vel \citep[][see also figure 1]{beuermann1990}.
 
@@
 local escape probabilities (MC96). However, as
-discussed further in section~\ref{modelb}, the 
+discussed further in section~5.3, the 
 radial velocity shear in our
@@
 to the escaping disk spectrum. The Balmer continuum emission is prominent, and
-we can see a clear effect on the overall spectral shape from the wind.}
+the wind has a clear effect on the overall spectral shape.}
 \label{modelb_escape}
@@
 much of the wind and is successful in producing recombination features.
-However, it leads to absorbing columns in H of $N_H\sim ??$ - far too
+However, the line opacity throughout the wind it too
 low to produce noticeable blue shifted absorption. 
-We therefore suspect that the winds that exhibit such profiles must 
-possess a higher degree of ionization stratification.
-This could manifest as a clumpy flow, in which ionization changes
-due to small scale density fluctuations, or a stratification on acceleration 
-length scales such as the kind shown by figure 6.
-This idea is supported by the fact that \cite{prinja2000}
+We suspect that the winds that exhibit such profiles must 
+possess a higher degree of ionization stratification, although the lack 
+of contemporary observations means it is not known for certain if the 
+P-Cygni profiles in UV resonance lines and optical H and He lines exist simultaneously.
+Ionization stratification could manifest as a clumpy flow, in which ionization changes
+due to small scale density fluctuations, or a stratification in density
+and ionizing radiation field over larger scales.
+Tentative evidence for clumping comes from the fact that \cite{prinja2000}
 found dwarf nova BZ Cam's outflow to be unsteady and highly mass-loaded in outburst,
-by observing the UV resonance lines in outburst with the {\sl Hubble Space Telescope}.
+by observing the UV resonance lines.
 This system has exhibited P-Cygni profiles in He~\textsc{i}~$\lambda5876{\rm \AA}$
 and \ha\ when in a high-state \cite{patterson1996,RN98}. 
+We also note that the degree of ionization and density variation and 
+subsequent line opacities may be affected by our model parameters
+and the specific parameterisation adopted.
 
@@
 or by bound-free processes. This is demonstrated by the flatter spectral shape
-and the slight Helum photoabsorption edges present in the optical spectrum.
+and the slight Helium photoabsorption edges present in the optical spectrum.
 In addition, figures~11 and 12 clearly demonstrate that the wind produces
@@
 
-Figure~\ref{halpha} shows how the H$\alpha$
+Figure~13 shows how the H$\alpha$
 line changes with the kinematics of the wind
@@
 more slowly accelerating winds. 
-This is due
-the base of the wind becoming optically thick such 
+This is due the base of the wind becoming optically thick such 
 that line emission cannot escape. This means
@@
 mechanism proposed by MC96.
-The main criterion for this mechanism is
+The main criterion for this mechanism to work is that
 
 \begin{equation}
-\frac{dv_p}{dr} > \frac{dv_\phi}{ds}\,
+\frac{dv_p}{dr} \gtrsim \frac{dv_\phi}{dr},
 \end{equation}
@@
 where $v_p$ is the poloidal velocity and $v_\phi$
-is the Keplerian velocity.
-This criterion is simply not satisfied in the emission region of our models.
-
-There are two possible ways in which the model
-could be altered to better reproduce single-peaked
-lines as a result of radial velocity shear. First,
-one could adopt a more equatorial wind geometry. 
-This would increase the velocity gradient in the radial 
-direction. However, CV winds are known to be moderately collimated.
-This is demonstrated by the fact that blue-shifted resonance line 
-absorption is seen in low inclination systems such as RW Sex \citep{greensteinoke1982},
-but not in eclipsing systems \citep{cordovamason1985}.
-Furthermore, the main reason for adopting this type of 
-wind geometry is that it already successfully models the 
-P-Cygni resonance lines seen in the UV (LK02; Noebauer et al. 2010),
-Equatorial winds are expected in AGN and X-ray binaries 
-\citep{weymann1991, ponti2012}, so these winds may be more likely
-to possess the required kinematics.
-Second, one could adopt velocity laws with higher 
-velocity gradients in the line emission region. 
-However, this poses problems for a smooth biconical wind. 
-We have already demonstrated that high densities are required 
-to produce significant emission. In a smooth model, which
-satisfies the mass continuity condition (see section 3.1), 
-it is therefore difficult to reconcile 
-these high densities with the high velocity gradients required.
-
-We suggest that clumping
-in CV winds provides a possible solution.
+is the Keplerian velocity. This criterion is simply 
+not satisfied in the emission region of our models.
+MC96 find values of $2-6.5$ for the ratio $(dv_p/dr)/(dv_\phi/dr)$
+in their simple model, but in even our fastest accelerating 
+wind we find ratios of $\lesssim0.1$ in the main \ha\ emission region.
+The relatively low poloidal gradients are required to produce high densities
+and observable emission lines, although 
+we stress that the velocity field may depend significantly 
+on the particular parameterisation used. 
+We also suggest investigating clumping in CV winds.
 Inhomogeneity could allow higher density pockets 
@@
 community \citep[e.g.][]{hamannkoesterke1998,oskinova2007}.
-We therefore hope that further investigation of
-`clumpy' winds could help solve the current mystery of single-peaked 
-line emission in high inclination systems.
+
+The emission in our models which produce single-peaked lines comes from
+approximately $10^{11}$~cm ($\sim150~R_{WD}$) above the disk plane.
+Most models for Balmer emission in CVs propose that the Balmer emission
+is more or less confined to the disk plane (e.g, MC96; REFs), 
+and one might naively expect that the size of the emission region
+is comparable to the size of the accretion disk, i.e., 10s-100s of WD radii.
+However, the true vertical extent of the emission region is not known,
+and it has been shown in multiple observations of eclipsing NLs that the 
+H$\alpha$ line is only moderately eclipsed compared to the continuum 
+(REFs, see also section 5.4).
+We do not necessarily proposed that the emitting region is this large,
+but it is a natural avenue to explore and a simple way in which to form
+single-peaked lines.
+
+% Alternatively, there are possible ways in which the model
+% could be altered to better reproduce single-peaked
+% lines as a result of radial velocity shear. First,
+% one could adopt a more equatorial wind geometry. 
+% This would increase the velocity gradient in the radial 
+% direction. However, CV winds are known to be moderately collimated.
+% This is demonstrated by the fact that blue-shifted resonance line 
+% absorption is seen in low inclination systems such as RW Sex \citep{greensteinoke1982},
+% but not in eclipsing systems \citep{cordovamason1985}.
+% Furthermore, the main reason for adopting this type of 
+% wind geometry is that it already successfully models the 
+% P-Cygni resonance lines seen in the UV (LK02; Noebauer et al. 2010),
+% Equatorial winds are expected in AGN and X-ray binaries 
+% \citep{weymann1991, ponti2012}, so these winds may be more likely
+% to possess the required kinematics.
+% Second, one could adopt velocity laws with higher 
+% velocity gradients in the line emission region. 
+% However, this poses problems for a smooth biconical wind. 
+% We have already demonstrated that high densities are required 
+% to produce significant emission. In a smooth model, which
+% satisfies the mass continuity condition (see section 3.1), 
+% it is therefore difficult to reconcile 
+% these high densities with the high velocity gradients required.
+
+% We suggest that clumping
+% in CV winds provides a possible solution.
+% Inhomogeneity could allow higher density pockets 
+% of emission to exist while still possessing a high radial velocity shear.
+% Theory of line-driven winds predicts an unstable flow
+% \citep{macgregor1979,owockirybicki1984,owockirybicki1985},
+% and simulations of accretion disk winds find a nonhomogeneous 
+% density structure \citep{proga1998,pkdh2002}.
+% In addition, a number of implementations have been used in the stellar wind
+% community \citep[e.g.][]{hamannkoesterke1998,oskinova2007}. 
+% We therefore hope that further investigation of
+% clumpy winds could help shed light on the formation of single-peaked 
+% line emission in high inclination systems.
+% It should be stressed again that these conclusions may, as mentioned in 
+% section 5.1, be dependent on our particular parameterisation.
+% By way of example, specific assumptions about the initial and 
+% terminal velocities may significantly affect velocity gradients
+% in regions dominated by rotational velocities.
 
@@
 adopt $i = 80^\circ$, but our qualitative conclusions are not
-particular sensitive to this particular value. We emphasize that this
+particularly sensitive to this value. We emphasize that this
 model is in no sense a fit to this - or any other - data set.
@@
 As discussed in section 5.3, the optical lines are
-narrow. This is in contrast to what is generally seen in observations
+narrow, but double-peaked. 
+This is in contrast to what is generally seen in observations
 of NLs, although the relatively low resolution of the RW Tri
-spectra makes a specific comparison difficult.
+spectrum makes a specific comparison difficult.
 
@@
 would affect the Balmer jump (see section 5.2). In section 5.3, we demonstrate that
-although single-peaked emission can be formed in our densest models, 
+although the double peaked lines narrow 
+single-peaked emission can be formed in our densest models, 
 it is not due to the radial velocity shear mechanism proposed by MC96.
-The emission in our models which produce single-peaked lines comes from
-approximately $10^{11}$~cm above the disk plane, which is not supported
-by eclipse-mapping observations (REFS). We suggest
-that nonhomogenous, `clumpy' line-driven winds may offer a potential solution.
+We suggest that nonhomogenous, `clumpy' line-driven winds may offer a 
+potential solution.
 
@@
 
-\noindent We can also make a number of basic,
+We can also make a number of basic,
 testable predictions for wind-formed signatures:

### 2015-01-19 draft.tex
version to send to collaborators

@@
 \renewcommand{\labelitemi}{$\bullet$}
-\def\py{\textsc{Python} }
+\def\py{\textsc{Python}}
 \def\tar{\textsc{Tardis} }
@@
 %% define some control sequences for lines
-\def\heiiopt{He~\textsc{ii}~$\lambda4686{\rm \AA}$}
-\def\heiiuv{He~\textsc{ii}~$\lambda1640{\rm \AA}$}
-\def\heiioptnew{He~\textsc{ii}~$\lambda3202{\rm \AA}$}
-\def\la{Ly-$\alpha$}
+\def\heiiopt{He~\textsc{ii}~$\lambda4686$}
+\def\heiiuv{He~\textsc{ii}~$\lambda1640$}
+\def\heiioptnew{He~\textsc{ii}~$\lambda3202$}
+\def\la{Ly$\alpha$}
 \def\ha{H$\alpha$}
 \def\hb{H$\beta$}
-\def\civfull{C~\textsc{iv}~$\lambda1550{\rm \AA}$}
+\def\civfull{C~\textsc{iv}~$\lambda1550$}
 
@@
 Many high-state non-magnetic cataclysmic variables (CVs) exhibit
-blue-shifted absorption or P-Cygni profiles in ultraviolet
-(UV) resonance lines, such as C~{\sc iv}~1550\AA. These features
+blue-shifted absorption or P-Cygni profiles associated with ultraviolet
+(UV) resonance lines, such as C~{\sc iv}~$\lambda1550$. These features
 imply the existence of powerful accretion disk winds in
@@
 in the {\em optical} waveband. 
-In particular, we test whether outflows may 
-be responsible for the single-peaked emission line profiles often seen
-in high-state CVs and for the weakness of the Balmer absorption edge
-(relative to simple models of optically thick accretion disks).
 We find that a standard disk wind model that is successful in
@@
 inclination. The strongest optical wind-formed recombinations lines are \ha\ and
-\heiiopt\, although the outflow also produces emission in the Ly-$\alpha$
+\heiiopt\, although the outflow also produces emission in the Ly$\alpha$
 and \heiiuv\ UV lines. However, all of the optical lines produced by
 this default wind model are double-peaked, and the effect of the wind
-on the Balmer jump is modest. 
-We demonstrate that a higher-density outflow model 
+on the Balmer jump is modest. We demonstrate that a higher-density outflow model 
 displays reasonable verisimilitude with the optical spectrum of RW Trianguli,
-producing all the observed lines. In addition, this model
+producing all the observed lines. This model
 produces recombination continuum sufficient to fill in the Balmer jump,
-although it also predicts stronger-than-observed 
+but it also predicts stronger-than-observed 
 collisionally excited UV emission lines. 
@@
 narrowing of the double-peaked emission lines from the base of the wind.
-We suggest that a nonhomogenous, `clumpy' wind may provide a possible
-solution.
-On the basis of these results, we suggest that winds can 
+We show that denser models can produce a single-peaked \ha\ line,
+but this is not due to radial velocity shear mechanism that
+has previously been proposed. On the basis of these results, we suggest that winds can 
 modify, and perhaps even dominate, the line and continuum emission
-from accreting systems.
+from CVs.
 % We carry out a limited exploration of
@@
 around the white dwarf (WD). Nova-like variables (NLs) are a subclass
-of CVs in which the accretion disk is always in a relatively
-high accretion rate state ($\dot{M} \sim
+of CVs in which the  disk is always in a relatively
+high-accretion-rate state ($\dot{M} \sim
 10^{-8}$~M$_{\odot}$~yr$^{-1}$).  This makes NLs an excellent
@@
 1987\nocite{maucheraymond1987}; Drew 1987; Shlosman \& Vitello 1993; [hereafter
-SV93]\nocite{SV93}; Knigge, Woods \& Drew 1995 [hereafter
-KWD95]\nocite{KWD95}; Knigge \& Drew 1997\nocite{kd1997}; 
-Knigge et al. 1997\nocite{knigge1997}; Long \&
-Knigge 2002 [hereafter LK02]\nocite{LK02}, Noebauer et al. 2010\nocite{noebauer};
+SV93]\nocite{SV93}; Knigge, Woods \& Drew 1995\nocite{KWD95}; 
+Knigge \& Drew 1997\nocite{kd1997}; 
+Knigge et al. 1997\nocite{knigge1997}; Long \& Knigge 2002 [hereafter LK02]\nocite{LK02}, 
+Noebauer et al. 2010\nocite{noebauer};
 Puebla et al. 2011\nocite{puebla2011}). The basic picture emerging from these efforts is
@@
 outflow that carries away $\simeq 1\% - 10\%$ of the accreting
-material. State-of-art-simulations of line formation in this type
+material. State-of-the-art simulations of line formation in this type
 of disk wind can produce UV line profiles that are remarkably similar
@@
 spectra of high-state CVs. These spectra are typically characterized
-by H and He emissions superposed on a blue continuum. In many
+by H and He emission lines superposed on a blue continuum. In many
 cases, and particularly in the SW~Sex subclass of NLs
@@
 % of general trends in DNe. A lot seem to have weak emission cores
-% embedded in absorption.}
-
-Murray \& Chiang (1996, 1997; hereafter referred to collectively as MC96)\nocite{MC96, MC97} 
-have shown that the presence of disk winds may
-offer a natural explanation for the single-peaked optical emission lines in
-high-state CVs, since they can strongly affect the radiative transfer
-of line photons. Strong support for a significant wind contribution to the
-optical emission lines comes from observations of eclipsing
-systems. There, the single-peaked lines are often only weakly
-eclipsed, and a significant fraction of the line flux remains visible
-even near mid-eclipse \citep[e.g.][]{groot2004}. This points to line formation in a spatially
-extended region, such as a disk wind (see figure~\ref{novalikes}).
-%%(Honeycutt, Schlegel, \& Kaitchuck 1986; Dhillon \& Rutten 1995). 
-Further evidence for a wind contribution to the optical lines comes
-from isolated observations of P-Cygni-like line profiles even in optical
-lines, such as \ha\ and He \textsc{i} $\lambda5876$ \citep{patterson1996, RN98, kafka2004}.
-
-Could disk winds also have an impact on the UV/optical {\em continuum}
-of high-state CVs? This continuum is usually thought to be dominated
-by the accretion disk and modelled by splitting the disk into
-a set of concentric, optically thick, non-interacting annuli following
-the standard $T_{eff}(R) \propto R^{-3/4}$ radial temperature
-distribution \citep{shakurasunyaev1973}. In such
-models, each annulus is taken to emit either as a blackbody or,
-perhaps more realistically, as a stellar/disk atmosphere model
-(REF). In the latter case, the local surface gravity, $\log{g}(R)$, is
-assumed to be set solely by the accreting WD, since self-gravity is
-negligible in CV disks.
-
-Attempts to fit the observed spectral energy distributions (SEDs) of
-high-state CVs with such models have met with mixed success. In
-particular, the SEDs predicted by most stellar/disk atmosphere models 
-are too blue in the UV \citep{wade1988,long1991,long1994} and exhibit
-stronger-than-observed Balmer jumps in absorption 
-\citep{wade1984,haug1987,ladous1989b,knigge1998}. One possible
-explanation for these problems is that these models fail to capture
-all of the relevant physics. Indeed, it has been argued that a
-self-consistent treatment can 
-produce better agreement with observational data (e.g. Shaviv et
-al. 1991;  but also more recent work by Idan et al. 2010).
-\nocite{idanshaviv2010} \nocite{shaviv1991}
-However, an alternative explanation, suggested by \cite{KLWB98}, 
-is that recombination continuum emission from the base of the 
-disk wind might fill in the disk's
-Balmer absorption edge and flatten the UV spectrum.
+% embedded in absorption.}\
 
@@
 
+Murray \& Chiang (1996, 1997; hereafter referred to collectively as MC96)\nocite{MC96, MC97} 
+have shown that the presence of disk winds may
+offer a natural explanation for the single-peaked optical emission lines in
+high-state CVs, since they can strongly affect the radiative transfer
+of line photons. Strong support for a significant wind contribution to the
+optical emission lines comes from observations of eclipsing
+systems. There, the single-peaked lines are often only weakly
+eclipsed, and a significant fraction of the line flux remains visible
+even near mid-eclipse \citep[e.g.][]{baptista2000,groot2004}. 
+This points to line formation in a spatially
+extended region, such as a disk wind (see Fig.~\ref{novalikes}).
+%%(Honeycutt, Schlegel, \& Kaitchuck 1986; Dhillon \& Rutten 1995). 
+Further evidence for a wind contribution to the optical lines comes
+from isolated observations of P-Cygni-like line profiles even in optical
+lines, such as \ha\ and He \textsc{i} $\lambda5876$ \citep{patterson1996, RN98, kafka2004}.
+
+Could disk winds also have an impact on the UV/optical {\em continuum}
+of high-state CVs? This continuum is usually thought to be dominated
+by the accretion disk and modelled by splitting the disk into
+a set of concentric, optically thick, non-interacting annuli following
+the standard $T_{eff}(R) \propto R^{-3/4}$ radial temperature
+distribution \citep{shakurasunyaev1973}. In such
+models, each annulus is taken to emit either as a blackbody or,
+perhaps more realistically, as a stellar/disk atmosphere model
+\citep{Schwarzenberg-Czerny1977,wade1984,wade1988}.
+In the latter case, the local surface gravity, $\log{g}(R)$, is
+assumed to be set solely by the accreting WD, since self-gravity is
+negligible in CV disks.
+
+Attempts to fit the observed spectral energy distributions (SEDs) of
+high-state CVs with such models have met with mixed success. In
+particular, the SEDs predicted by most stellar/disk atmosphere models 
+are too blue in the UV \citep{wade1988,long1991,long1994,knigge1998} and exhibit
+stronger-than-observed Balmer jumps in absorption 
+\citep{wade1984,haug1987,ladous1989b,knigge1998}. One possible
+explanation for these problems is that these models fail to capture
+all of the relevant physics. Indeed, it has been argued that a
+self-consistent treatment can 
+produce better agreement with observational data (e.g. Shaviv et
+al. 1991;  but see also Idan et al. 2010).
+\nocite{idanshaviv2010} \nocite{shaviv1991}
+However, an alternative explanation, suggested by Knigge et al.
+(1998b; see also Hassall et al. 1985)\nocite{KLWB98,hassall}, 
+is that recombination continuum emission from the base of the 
+disk wind might fill in the disk's
+Balmer absorption edge and flatten the UV spectrum.
+
 %% CITATIONS FROM CAPTION
@@
 (2002, 2003) into the Monte Carlo ionization and radiative transfer
-code described by LK02 (a process initiated by SDL05). With this
-upgrade, the code is able to deal correctly with processes involving
+code described by LK02 (a process initiated by Sim et al. 2005; hereafter SDL05). 
+With this upgrade, the code is able to deal correctly with processes involving
 excited levels, such as the recombination emission produced by CV
@@
 In Section~4, we present spectra simulated from the benchmark model
-employed by LK02, and in Section~5, we carry out a limited sensitivity
-study to explore how the predicted spectra change as a function of
-some key parameters in our model. In Section~6, we summarize our
+employed by LK02, and, in Section~5, we present a revised model
+optimized for the optical waveband. In Section~6, we summarize our
 findings.
@@
 
-\py is a Monte Carlo  ionization and radiative transfer code which
+\py\ is a Monte Carlo  ionization and radiative transfer code which
 uses the Sobolev approximation to treat line transfer. It has already
-been described extensively by LK02, SDL05 and H13, so here we provide
-only a brief summary of its operation, focusing particularly on new
+been described extensively by LK02, SDL05 and Higginbottom et al. (2013; hereafter H13), 
+so here we provide only a brief summary of its operation, focusing particularly on new
 aspects of our implementation of macro-atoms into the code.
@@
 
-\py operates in two distinct stages. First, the ionization state,
+\py\ operates in two distinct stages. First, the ionization state,
 level populations and temperature structure are calculated. This is
@@
 characterize the radiation field in each grid cell. At the end 
-of each ionization cycles, a new electron temperature is calculated
+of each ionization cycle, a new electron temperature is calculated
 that more closely balances heating and cooling in the 
@@
 
-This converged model is used as the basis for the second set of
+This converged model is then used as the basis for the second set of
 iterations (``spectral cycles''). In these, the emergent spectrum over
@@
 
-\py is designed to operate in a number of different
+\py\ is designed to operate in a number of different
 regimes, both in terms of the scale of the system, and in terms of the
@@
 It was originally developed by LK02 in order to model the UV spectra
-of CVs with a simple biconical disk wind model. Sim et al. (2005;
-hereafter SDL05)\nocite{simmacro2005} used the code to model Brackett
+of CVs with a simple biconical disk wind model. SDL05
+\nocite{simmacro2005} used the code to model Brackett
 and Pfund line profiles of H in young-stellar objects (YSOs). As part
@@
 order to correctly treat hydrogen recombination lines with
-\py. Finally, Higginbottom et al.\nocite{higginbottom2013} (2013;
-hereafter H13) used \py to model broad absorption line (BAL) QSOs. For
+\py. Finally, H13 used \py\ to model broad absorption line (BAL) QSOs. For
 this application, an improved treatment of ionization was implemented,
-so that the code is now capable of dealing with arbritrary
+so that the code is now capable of dealing with arbitrary
 photo-ionizing SEDs, including non-thermal and multi-component ones.
@@
 \left(\frac{T_e}{T_R}\right)^{1/2}
-\left(\frac{n_{j+1}n_e}{n_j}\right)^*_{T_R}, \label{ionization}
+\left(\frac{n_{j+1}n_e}{n_j}\right)^*_{T_R}. \label{ionization}
 \end{equation}
@@
 fraction of recombinations going directly to the ground state, and
-$T_R$ and $T_e$ are the radiation and electron temperature
+$T_R$ and $T_e$ are the radiation and electron temperatures,
 respectively. This simple ionization scheme produces reasonable
@@
 
-Finally, \py modelled all bound-bound processes as transitions
+Finally, \py\ modelled all bound-bound processes as transitions
 within a simple two-level atom \cite[see e.g.][]{mihalas}. This
-approach works reasonable well for resonance  
+approach works reasonably well for resonance  
 lines, such as \civfull, in which the lower level is the ground state.  
 However, it is a poor approximation for many other
-transitions, particularly those where the upper level is 
+transitions, particularly those where the upper level
 is primarily populated from above. Thus an improved method for
@@
 supernovae \citep{kasen2006, kerzendorfsim} and YSOs (SDL05). A full 
-description of the can be found in L02 and L03.
+description of the approach can be found in L02 and L03.
 
@@
 \begin{equation}
-{\cal R}_{ul} = \beta_{lu} A_{ul} n_u + \beta_{lu} B_{ul} n_u J_{lu} +
+{\cal R}_{ul} = \beta_{lu} A_{ul} n_u + \beta_{lu} B_{ul} n_u J_{ul} +
 C_{ul} n_u n_e,\label{eq:nlte_rul},
@@
 where $u$ and $l$ denote the upper and lower levels, $C$ represents the
-collisional rate coefficients and $A$ and $B$ represent the Einstein
+collisional rate coefficients, and $A$ and $B$ represent the Einstein
 coefficients. The quantity $\beta_{lu}$ is the probability that a
-given line photon will escape the Sobolev region. Finally, $J$ is the
-Monte Carlo estimator for the mean intensity in the line, as recorded during
-the photon propagation. The corresponding excitation rate is then 
+given line photon will escape the Sobolev region. Finally, $J_{lu}$ is the
+Monte Carlo estimator for the mean intensity in the line. 
+The corresponding excitation rate is then 
 \begin{equation}
@@
 where we implicitly include a correction for stimulated emission in
-our definition of the estimate for $J_{ul}$.
+our definition of $J_{lu}$.
 
@@
 \end{equation}
-
 Here, $\sigma_{\nu}$ is the photoionization cross section, and $J_{\nu}$
@@
 
-SDL05 implemented a macro-atom treatment of Hydrogen in \py and used
+SDL05 implemented a macro-atom treatment of Hydrogen in \py\ and used
 this to predict the observable properties of a pure Hydrogen wind
@@
 the principal quantum number, $n$. For the macro-atom treatment of
-Helium,  we have added additional level and line information required 
+Helium, we have added the additional level and line information required 
 from \textsc{Topbase} \citep{topbase2005}.  He~\textsc{II} is treated
@@
 larger energy differentials between different l-subshells and triplet
-and singlet states. Thus, we still include levels up to $n=10$ but
+and singlet states. Thus, we still include levels up to $n=10$, but
 explicitly treat the $l$ and $s$ sub-orbitals as distinct levels
@@
 
-\py has been tested against a number of radiative transfer and
+\py\ has been tested against a number of radiative transfer and
 photoionization codes. LK02 and H13 conducted comparisons of 
@@
 therein. For the effort reported here, we have additionally carried
-out tests of the macro-atom scheme in \py. Figure~\ref{tests} shows
+out tests of the macro-atom scheme in \py. Fig.~\ref{tests} shows
 two of these tests. In the top panel, we compare the Balmer series 
-emissivities as predicted by \py in the l-mixed Case~B limit against the
+emissivities as predicted by \py\ in the l-mixed Case~B limit against the
 analytical calculations by \cite{seaton1959}. In the bottom panel, we
-compare \py and \tar predictions of  He \textsc{i} level populations
+compare \py\ and \tar predictions of  He \textsc{i} level populations
 for a particular test case. Agreement is excellent for both H and He.
@@
 {\sl Bottom Panel:}  a comparison of Helium I level populations (the most complex ion we currently 
-treat as a macro-atom) between \py~and \tar~models. 
+treat as a macro-atom) between \py\ and \tar models. 
 The calculation is conducted with physical parameters of $n_e=5.96\times10^4$~cm$^{-3}$,
@@
 
-\py includes several different kinematic models of accretion disk
+\py\ includes several different kinematic models of accretion disk
 winds, as well as different options for describing the physical and
@@
 A schematic of this model is shown in
-figure~\ref{cartoon}. In this parametrization, a smooth, biconical
+Fig.~\ref{cartoon}. In this parametrization, a smooth, biconical
 disk wind emanates from the accretion disk between radii $r_{min}$ and 
@@
 correspond to fast acceleration close to the disk (see
-figure~\ref{acc_law}).
+Fig.~\ref{acc_law}). The rotational velocity $v_\phi$ is originally 
+Keplerian and is assumed to conserve its specific angular momentum
+such that
+\begin{equation}
+v_\phi r = v_{k} r_0,
+\label{v_law}
+\end{equation}
+where $v_{k}=(GM_{WD}/r_0)^{1/2}$.
 
@@
 acceleration exponent, $\alpha$.
-{\bf JM: KSL has suggested we ditch this}
+%%{\bf JM: KSL has suggested we ditch this}
 } 
@@
 \begin{equation}
-\rho(r,z) = \frac{r}{r_0} \frac{dr}{dr_0} \frac{\phi(r_0)}{v_z(r,z)}.
+\rho(r,z) = \frac{r_0}{r} \frac{dr_0}{dr} \frac{\phi(r_0)}{v_z(r,z)}.
 \label{density}
 \end{equation}
-Here, $\phi(r_O)$ is the mass-loss rate per unit area at $r_0$, 
-and $v_z$ is the vertical velocity component. We take $\phi(r_0)$ to be
+Here, $\phi(r_0)$ is the local mass-loss rate per unit area at $r_0$, in the direction 
+of a streamline (as defined by SV93). 
+$v_z$ is the vertical velocity component. We take $\phi(r_0)$ to be
 uniform across the wind-launching area of the disk and normalize it by
@@
 $\dot{M}_{wind}$. 
-{\bf CK: I'm still not sure I understand the formula
-  SV93 use to define $\phi$, and hence that this description is
-  actually strictly correct.... Not sure what to do about that
-  though...}
+% {\bf CK: I'm still not sure I understand the formula
+%   SV93 use to define $\phi$, and hence that this description is
+%   actually strictly correct.... Not sure what to do about that
+%   though...}
 
@@
 
-\py has has some flexibility when treating the accretion 
+\py\ has has some flexibility when treating the accretion 
 disk as a source of photons. The disk is broken down into annuli 
@@
 luminosity. We take the disk to be geometrically thin, but optically
-thick and thus adopt the temperature profile of a standard
+thick, and thus adopt the temperature profile of a standard
 \cite{shakurasunyaev1973} $\alpha$-disk. An annulus can then
@@
 the BL luminosity to zero. However, we have confirmed that the addition of a
-BL with $L_{BL} = 0.5 L_{acc}$ and temperatures in the range $80{\rm
-kK} \leq T_{BL} \leq 200{\rm kK}$ would not change any of our main
+BL with $L_{BL} = 0.5 L_{acc}$ and temperatures in the range $80~{\rm
+kK} \leq T_{BL} \leq 200~{\rm kK}$ would not change any of our main
 conclusions.
@@
 surface. The secondary is assumed to be Roche-lobe filling, so its
-shape and size are defined by setting the mass ratio of the system, $q
-= M_2/M_{WD}$. The inclusion of the donor star as an occulting body
+shape and relative size are defined by setting the mass ratio of the system, 
+$q = M_2/M_{WD}$. The inclusion of the donor star as an occulting body
 allows us to model eclipses of the disk and the wind. For this
-purpose, we define orbital phase such that $\Phi_{orb} = 0$ as the
+purpose, we assume a circular orbit with a semi-major axis $a$ and 
+specify orbital phase such that $\Phi_{orb} = 0$ as the
 inferior conjunction of the secondary (i.e. mid-eclipse for $i \simeq
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{figures/sed_figure.eps}
-\caption{
-The spectral energy distribution (SED) of the 
-White Dwarf (dashed line) and blackbody accretion
-disk used in the ionization calculation (black solid line).
-The positions of the Hydrogen and Helium ionization edges 
-are marked with vertical lines.
-{\bf JM: KSL has suggested we ditch this}
- }
-\label{sed}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=0.45\textwidth]{figures/sed_figure.eps}
+% \caption{
+% The spectral energy distribution (SED) of the 
+% White Dwarf (dashed line) and blackbody accretion
+% disk used in the ionization calculation (black solid line).
+% The positions of the Hydrogen and Helium ionization edges 
+% are marked with vertical lines.
+% {\bf JM: KSL has suggested we ditch this}
+%  }
+% \label{sed}
+% \end{figure}
 
@@
 \hline \hline 
-$M_{WD}$ 	 &	 $0.8 M_{\odot}$  &     \\ 
-$R_{WD}$ 	 &	 $7\times10^{8}$cm  & \\ 
-$T_{WD}$ 	 &	 $40,000$K        &  \\
-$M_{2}$ 	 &	 $0.6 M_{\odot}$  &   \\ 
-$q$ 	 &	 $0.75 M_{\odot}$  &   \\ 
-$P_{orb}$ 	 &	 $5.57$~hr  &   \\ 
+$M_{WD}$ 	 &	 $0.8~M_{\odot}$  &     \\ 
+$R_{WD}$ 	 &	 $7\times10^{8}$~cm  & \\ 
+$T_{WD}$ 	 &	 $40,000$~K        &  \\
+$M_{2}$ 	& -&	 $0.6~M_{\odot}$   \\ 
+$q$ 	&- &	 $0.75$   \\ 
+$P_{orb}$ 	&- &	 $5.57$~hr   \\ 
+$a$ 	& -&	 $194.4~R_{WD}$   \\ 
+$R_2$   &   -  &	 $69.0~R_{WD}$  \\ 
 $\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$  &\\ 
 $\dot{M}_{wind}$  &	$10^{-9}~M_{\odot}yr^{-1}$å  & \\ 
-$r_{min}$ 	&	 $4 R_{WD}$ &  \\ 
-$r_{max}$ 	&	 $12 R_{WD}$  &  \\ 
+$r_{min}$ 	&	 $4~R_{WD}$ &  \\ 
+$r_{max}$ 	&	 $12~R_{WD}$  &  \\ 
+$r_{disk} (max)$ 	&	 $34~R_{WD}$  &  \\ 
 $\theta_{min}$ 	&	 $20.0^{\circ}$  &  \\ 
@@
 $\gamma$ 	&	 $1$  &  \\ 
-$v_{\infty}$ 	&	 $3v_{esc}$  &  \\ 
-%%$R_v$ 	        &	 $7\times10^{10}$cm \\ 
-$R_v$ 	        &	 $100 R_{WD}$  &  $142.9 R_{WD}$  \\ 
+$v_{\infty}$ 	&	 $3~v_{esc}$  &  \\ 
+$R_v$ 	        &	 $100~R_{WD}$  &  $142.9~R_{WD}$  \\ 
 $\alpha$ 	&	 $1.5$   &   $4$\\
@@
 For model B, only parameters which are altered are given - otherwise the
-model A parameter is used.
-{\bf JM: this needs some stuff adding, as is mentioned in certain places}}
+model A parameter is used. $P_{orb}$ is the orbital period 
+(the value for RW Tri from ?? is adopted, see section 5.4) and 
+$R_2$ is the radius of a sphere with the volume of the secondary's Roche lobe. 
+Other quantities are defined in the text or Fig.~\ref{cartoon}.
+Secondary star parameters are only quoted for 
+model B as we do not show eclipses with the 
+benchmark model (see section 5.4).
+}
 \label{wind_param}
@@
 Our main goal is to test whether the type of disk wind model that has
-been successful in explaining the UV spectra of CVs could also have 
+been successful in explaining the UV spectra of CVs could also have a
 significant impact on the optical continuum and emission line spectra
@@
 
-Figure~\ref{wind} shows the physical and ionization structure 
+Fig.~\ref{wind} shows the physical and ionization structure 
 of the benchmark disk wind model. The ionization parameter shown in the bottom
@@
 
-\begin{eqnarray}
-U&=&\frac{Q_H}{4\pi R^2 n_{H} c}\\ 
-  &=& \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}
-\end{eqnarray}
-
-where $\rm{Q_H}$ is the number of hydrogen-ionizing photons emitted by
-the illuminating source per second, $R$ is the distance to the source,
-$\rm{n_H}$ is the local hydrogen number density and $c$ is the speed of
-light. $J_\nu$ is the Monte Carlo estimator for the mean intensity in the cell. 
-The ionization parameter is a useful measure
-of the ionization state of a plasma, as it evaluates the ratio 
-of the integrated ionizing radiation field and the local Hydrogen density.
+\begin{equation}
+U = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu},
+\end{equation}
+
+\noindent where $\rm{n_H}$ is the local hydrogen number density and $\nu$ denotes photon 
+frequency. The ionization parameter is a useful measure of the ionization state of a plasma, 
+as it evaluates the ratio of the number density of ionizing photons and the local 
+Hydrogen density.
 
@@
 resulting ionization state of the wind to be quite similar to that
-found by LK02. The bottom panels in figure~\ref{wind} confirm that this
+found by LK02. The bottom panels in Fig.~\ref{wind} confirm that this
 is the case. In particular, Helium is fully ionized
@@
 velocities. As we shall see, this produces the broad, deep and
-blue-shifted C\textsc{iv}~$\lambda 1550{\rm \AA}$ absorption line that
+blue-shifted C\textsc{iv}~$\lambda1550$ absorption line that
 is usually the most prominent wind-formed feature in the UV spectra of
@@
 significantly from that computed by LK02 (see section~\ref{modela_ionization}). 
-The left column of panels in figure~\ref{spec} shows that this expectation
+The left column of panels in Fig.~\ref{spec} shows that this expectation
 is met: all of the strong metal resonance
-lines - notably N\textsc{v}~$\lambda 1240{\rm \AA}$,
-Si\textsc{iv}~$\lambda 1400{\rm \AA}$ and C\textsc{iv}~$\lambda
-1550{\rm \AA}$ - are present and exhibit clear P-Cygni profiles
+lines - notably N\textsc{v}~$\lambda1240$,
+Si\textsc{iv}~$\lambda1400$ and C\textsc{iv}~$\lambda1550$ - 
+are present and exhibit clear P-Cygni profiles
 at intermediate inclinations. In addition, however, we now also find
 that the wind produces significant Lyman-$\alpha$ and
-He~\textsc{ii}~$\lambda1640{\rm \AA}$ emission lines.
+He~\textsc{ii}~$\lambda1640$ emission lines.
 
@@
 cores from the stellar atmosphere models. The model
-also produces a prominent \heiioptnew\ line at high inclinations,
+also produces a prominent \heiioptnew\ line at high inclinations.
 }
@@
 
-Figure~\ref{spec} shows the corresponding optical spectra produced for
+Fig.~\ref{spec} (right-hand panel) and Fig.~\ref{spec_continuum}
+show the corresponding optical spectra produced for
 the benchmark model, and these do exhibit some emission lines
-associated with H and He. 
-We see a general trend from absorption lines to emission lines 
+associated with H and He. We see a general trend from absorption lines to emission lines 
 with increasing inclination, as one might expect from our wind
 geometry. This trend is consistent with observations, as can be seen
-in Figure~1. However, it is clear that this particular model
+in Fig.~1. However, it is clear that this particular model
 does not produce all the lines seen in observations of high-state CVs.
-The higher order Balmer series lines are too weak
+The higher-order Balmer series lines are too weak
 to overcome the intrinsic absorption from the disk atmosphere, and the wind 
-fails to produce any emission at intermediate inclinations, 
+fails to produce any observable emission at intermediate inclinations, 
 which contrasts with (for example) the observed behaviour of V3885 Sgr \citep{hartley2005}
-and IX Vel \citep[][see also figure 1]{beuermann1990}.
+and IX Vel \citep[][see also Fig.~1]{beuermann1990}.
 
@@
 absorption edge in the disk spectrum. This is illustrated in
-Figure~\ref{cont}, which shows the angle-integrated spectrum of the system,
+Fig.~\ref{cont}, which shows the angle-integrated spectrum of the system,
 i.e. the spectrum formed by all escaping photons, separated into the
@@
 designed to reproduce the wind-formed lines seen in the UV spectra of
-high-state CVs. As we have seen, this model does produce significant
-amounts of optical emission. However, with only relatively minor
-changes to the kinematics of the benchmark model, it is possible to
-construct a model that more closely matches the observed optical
-spectra of CVs.
+high-state CVs. As we have seen, this model does produce some observable
+optical emission. We can now attempt to construct a model that more closely 
+matches the observed optical spectra of CVs.
 
@@
 the UV behaviour;
- 	\item produce {\em single-peaked} Balmer emission lines (MC96); 
+         \item produce single-peaked Balmer emission lines (MC96); 
          \item generate enough of a wind-formed recombination continuum
@@
 
-The amount of recombination and collisionally excited emission
-produced by a given ion, $i$, in a plasma of volume $V$ depends
-primarily on the emission measure, $EM$, defined as
-
-\begin{equation}
-EM=\int^V_0 n_e n_i \,dV,
-\end{equation}
-
-where $n_i$ is the number density of the ion in question.    
-The emission reaching an observer at a given frequency also depends on
-the Sobolev optical depth it experiences, which depends on both the
-density and the velocity gradient projected along the line of
-sight. This can also significantly affect line profile shapes.
-
-The simplest way to simultaneously affect the density in the wind as
-well as the velocity gradients is by modifying the poloidal velocity
+The emission measure of a plasma is directly proportional to its density.
+The simplest way to simultaneously affect the density in the wind (for fixed mass loss rate)
+as well as the velocity gradients is by modifying the poloidal velocity
 law. We have therefore conducted a exploratory sensitivity study in
@@
          \item the acceleration length, $R_v$, which controls the
-        distance over which the wind accelerates to $\frac{1}{2}v_{\infty}$;
+        distance over which the wind accelerates to $\frac{1}{2}~v_{\infty}$;
          \item the acceleration exponent, $\alpha$, which controls the rate 
@@
 However, this behaviour may be moderated by the effect of the increasing
-optical depth through this region.
-
-We adopt the parameters listed in table~\ref{modelb_table}
-for our model, which best matches the observed optical spectra
-of high-state CVs. Some of the trends we observe in our 
-parameter search are discussed in section 6.
-Here, we discuss our revised model.
+optical depth through this region, which will also affect the line profile shapes. 
+Having briefly explored a variety of models with different kinematics,
+we adopt the parameters listed in table~\ref{modelb_table}(model B) for our revised model,
+which is optimized for the optical waveband.
 
@@
 The inset plots show zoomed-in line profiles for 
-\heiiuv\ and \ha. The \ha line 
-is single peaked, but higher order lines in the Balmer series
+\heiiuv\ and \ha. The Balmer and Helium
 are double-peaked, albeit with narrower profiles.
-Strong \heiiopt\ emission can be seen, as well a trend
+Strong \heiiopt\ emission can be seen, as well as a trend
 of a deeper Balmer jump with decreasing inclination.
@@
 
-Figure~\ref{uvoptb} shows the predicted UV and optical spectra for this
+Fig.~\ref{uvoptb} shows the predicted UV and optical spectra for this
 optically optimized model for the full range of inclinations. 
@@
 in He~\textsc{ii} and He~\textsc{i}. This can be seen more clearly in the 
-continuum-divided spectrum in figure~\ref{continuumb}, with the lines marked
-(NOTE, mark these).
+continuum-divided spectrum in Fig.~\ref{continuumb}.
+%with the lines marked (NOTE, mark these).
 
 Two other features are worth noting in the optical
-spectrum. First, the collisionally excited Ca~{\sc ii} H\&K 
-emission line at 3934\AA\ 
+spectrum. First, the collisionally excited Ca~{\sc ii} emission line at 3934\AA\ 
 becomes quite prominent in our densest models. Second, our model predicts a detectable
@@
 equivalent of Paschen~$\beta$ and should be expected in all systems that
-feature a strong He~\textsc{ii}~4686\AA\ line (the Helium
+feature a strong He~\textsc{ii}~$\lambda4686$ line (the Helium
 equivalent of Paschen~$\alpha$). 
@@
 to reproduce the UV line profiles. Thus, most of the wind
-has an ionization parameter of $\log U \sim 2$ (see figure 6).
+has an ionization parameter of $\log U \sim 2$ (see Fig.~\ref{wind}).
 This means Hydrogen and Helium are fully ionized throughout 
@@
 by observing the UV resonance lines.
-This system has exhibited P-Cygni profiles in He~\textsc{i}~$\lambda5876{\rm \AA}$
+This system has exhibited P-Cygni profiles in He~\textsc{i}~$\lambda5876$
 and \ha\ when in a high-state \cite{patterson1996,RN98}. 
@@
 parameters that lead to very high densities at the base of the wind
-($n_e\sim10^{13}-10^{14}$ in the main emission region). This produces
+($n_e\sim10^{13}-10^{14}$~cm$^{-3}$). This produces
 the desired optical recombination emission, but also increases the
@@
 lines. This explains the pronounced increase in the emission component 
-of the C\textsc{iv} 1550\AA\ resonance line, for example, relative to
-what was seen in the benchmark model (compare figures~\ref{spec} and
+of the C\textsc{iv} $\lambda1550$ resonance line, for example, relative to
+what was seen in the benchmark model (compare Figures~\ref{spec} and
 \ref{uvoptb}). The strength of this component in the revised model 
@@
 The wind now also has a clear effect on the continuum shape,
-as shown by figure~\ref{modelb_escape}. The majority of the
-escaping spectrum has now been reprocessed in some way by the wind,
+as shown by Fig.~\ref{modelb_escape}. The majority of the
+escaping spectrum has been reprocessed in some way by the wind,
 either by electron scattering (the wind is now moderately Thompson-thick),
 or by bound-free processes. This is demonstrated by the flatter spectral shape
-and the slight Helium photoabsorption edges present in the optical spectrum.
-In addition, figures~11 and 12 clearly demonstrate that the wind produces
+and the slight Helium photoabsorption edge present in the optical spectrum 
+(marked in Fig.~\ref{continuumb}). This reprocessing is also
+responsible for the change in continuum level between models A and B.
+In addition, Figures~\ref{uvoptb}, \ref{continuumb} 
+and \ref{modelb_escape} clearly demonstrate that the wind produces
 a recombination continuum sufficient to completely fill in the Balmer jump
@@
 our models cannot fill in since they employ a 20-level Hydrogen atom.}
-This offers a potential solution to a long-standing problem in
-understanding the spectral energy distribution of CVs, as
-originally suggested by \cite{KLWB98}.
-
-It has been noted by \cite{ladous1989, ladous1989b}
+This suggests that Balmer continuum emission from a wind can be important 
+in shaping the Balmer jump region, as
+originally suggested by Knigge et al.
+(1998b; see also Hassall et al. 1985)\nocite{KLWB98,hassall}.
+
+It should be acknowledged, however,
 that the Balmer jump in high-state CVs would naturally weaken at
-high inclinations due to limb darkening effects. 
+high inclinations due to limb darkening effects \citep{ladous1989, ladous1989b}. 
 Although we include a simple limb darkening law which affects 
-the seen at each inclination, we cannot
+the seen at each inclination, we do not
 include it as a {\em frequency dependent} opacity in our model.
@@
 
-Figure~13 shows how the H$\alpha$
-line changes with the kinematics of the wind
-for an inclination of $80^\circ$. 
-The line narrows as the models move towards denser,
-more slowly accelerating winds. 
-This is due the base of the wind becoming optically thick such 
-that line emission cannot escape. This means
-what is effectively a photosphere for the line moves 
-to a greater vertical distance from the disk plane,
-where rotational velocities drop off as $1/r$. 
-The narrowing of the line is {\em not} due to the radial velocity shear
-mechanism proposed by MC96.
-The main criterion for this mechanism to work is that
-
-\begin{equation}
-\frac{dv_p}{dr} \gtrsim \frac{dv_\phi}{dr},
-\end{equation}
-
-where $v_p$ is the poloidal velocity and $v_\phi$
-is the Keplerian velocity. This criterion is simply 
-not satisfied in the emission region of our models.
-MC96 find values of $2-6.5$ for the ratio $(dv_p/dr)/(dv_\phi/dr)$
-in their simple model, but in even our fastest accelerating 
-wind we find ratios of $\lesssim0.1$ in the main \ha\ emission region.
-The relatively low poloidal gradients are required to produce high densities
-and observable emission lines, although 
-we stress that the velocity field may depend significantly 
-on the particular parameterisation used. 
-We also suggest investigating clumping in CV winds.
-Inhomogeneity could allow higher density pockets 
-of emission to exist while still possessing a high radial velocity shear.
-Theory of line-driven winds predicts an unstable flow
-\citep{macgregor1979,owockirybicki1984,owockirybicki1985},
-and simulations of accretion disk winds find a nonhomogeneous 
-density structure \citep{proga1998,pkdh2002}.
-In addition, a number of implementations have been used in the stellar wind
-community \citep[e.g.][]{hamannkoesterke1998,oskinova2007}.
-
-The emission in our models which produce single-peaked lines comes from
-approximately $10^{11}$~cm ($\sim150~R_{WD}$) above the disk plane.
-Most models for Balmer emission in CVs propose that the Balmer emission
-is more or less confined to the disk plane (e.g, MC96; REFs), 
-and one might naively expect that the size of the emission region
-is comparable to the size of the accretion disk, i.e., 10s-100s of WD radii.
-However, the true vertical extent of the emission region is not known,
-and it has been shown in multiple observations of eclipsing NLs that the 
-H$\alpha$ line is only moderately eclipsed compared to the continuum 
-(REFs, see also section 5.4).
-We do not necessarily proposed that the emitting region is this large,
-but it is a natural avenue to explore and a simple way in which to form
-single-peaked lines.
-
-% Alternatively, there are possible ways in which the model
-% could be altered to better reproduce single-peaked
-% lines as a result of radial velocity shear. First,
-% one could adopt a more equatorial wind geometry. 
-% This would increase the velocity gradient in the radial 
-% direction. However, CV winds are known to be moderately collimated.
-% This is demonstrated by the fact that blue-shifted resonance line 
-% absorption is seen in low inclination systems such as RW Sex \citep{greensteinoke1982},
-% but not in eclipsing systems \citep{cordovamason1985}.
-% Furthermore, the main reason for adopting this type of 
-% wind geometry is that it already successfully models the 
-% P-Cygni resonance lines seen in the UV (LK02; Noebauer et al. 2010),
-% Equatorial winds are expected in AGN and X-ray binaries 
-% \citep{weymann1991, ponti2012}, so these winds may be more likely
-% to possess the required kinematics.
-% Second, one could adopt velocity laws with higher 
-% velocity gradients in the line emission region. 
-% However, this poses problems for a smooth biconical wind. 
-% We have already demonstrated that high densities are required 
-% to produce significant emission. In a smooth model, which
-% satisfies the mass continuity condition (see section 3.1), 
-% it is therefore difficult to reconcile 
-% these high densities with the high velocity gradients required.
-
-% We suggest that clumping
-% in CV winds provides a possible solution.
-% Inhomogeneity could allow higher density pockets 
-% of emission to exist while still possessing a high radial velocity shear.
-% Theory of line-driven winds predicts an unstable flow
-% \citep{macgregor1979,owockirybicki1984,owockirybicki1985},
-% and simulations of accretion disk winds find a nonhomogeneous 
-% density structure \citep{proga1998,pkdh2002}.
-% In addition, a number of implementations have been used in the stellar wind
-% community \citep[e.g.][]{hamannkoesterke1998,oskinova2007}. 
-% We therefore hope that further investigation of
-% clumpy winds could help shed light on the formation of single-peaked 
-% line emission in high inclination systems.
-% It should be stressed again that these conclusions may, as mentioned in 
-% section 5.1, be dependent on our particular parameterisation.
-% By way of example, specific assumptions about the initial and 
-% terminal velocities may significantly affect velocity gradients
-% in regions dominated by rotational velocities.
+Fig.~\ref{halpha} shows how the H$\alpha$ profile changes with the kinematics of the wind for 
+an inclination of $80^\circ$. The main prediction is that dense, slowly accelerating 
+wind models produce narrower emission lines. This is {\em not} due to the radial 
+velocity shear mechanism proposed by MC96. That mechanism can only work if poloidal 
+and rotational velocity gradients satisfy $(dv_l/dr)/(dv_\phi/dr) \gtrsim 1$; in 
+our models, this ratio is always $\lesssim 0.1$. Instead, the narrow lines predicted 
+by our denser wind models can be traced to the base of the outflow becoming optically 
+thick to line photons. In such models, the `line photosphere'
+(the $\tau \simeq 1$ surface of the line-forming region) moves outwards, towards larger 
+vertical and cylindrical distances. This reduces the predicted line widths, since the 
+rotational velocities -- which normally provide the main line broadening mechanism at 
+high inclination -- drop off as $1/r$. This is not to say that the MC96 
+mechanism could not be at work in CV winds. For example, it would be worth investigating
+alternative prescriptions for the wind velocity field, as well as the possibility that the 
+outflows may be clumped. However, such an investigation is beyond the scope of the present paper.
+
+In our models, single-peaked line profiles are produced once the line forming region has been
+pushed up to $\sim 10^{11}$~cm ($\sim150~R_{WD}$) above the disk plane. 
+This number may seem unrealistically large, but the vertical extent of 
+the emission region is actually not well constrained observationally. 
+In fact, multiple observations of eclipsing NLs show that the H$\alpha$ 
+line is only moderately eclipsed compared to the continuum (e.g. Baptista et al. 2000;
+Groot et al. 2004; see also section 5.4), 
+implying a significant vertical extent for the line-forming 
+region. This type of model should therefore not be ruled out {\em a priori}.
 
@@
 and a third model (X) which has an increased acceleration length of 
-$R_V = 283.8~R_{WD}$, and $\alpha=4$ is also shown. 
+$R_v = 283.8~R_{WD}$, and $\alpha=4$ is also shown. 
 The $x$-axis limits correspond to the Keplerian velocity at 
 $4R_{WD}$, the inner edge of the wind.
-We observe a narrowing of the lines
-but this is not due to radial velocity shear (see section 5.3
-for a discussion).
+We observe a narrowing of the lines, and a single-peaked line in model X.
+This is not due to radial velocity shear (see section 5.3).
 }
@@
 
-Figure~\ref{rwtricomp} shows a qualitative comparison of the predicted
+Fig.~\ref{rwtricomp} shows a qualitative comparison of the predicted
 out-of-eclipse and mid-eclipse spectra against observations of the
@@
 adopt $i = 80^\circ$, but our qualitative conclusions are not
-particularly sensitive to this value. We emphasize that this
+particularly sensitive to this choice. We emphasize that this
 model is in no sense a fit to this - or any other - data set.
@@
 
-There are also interesting differences between the revised
+However, there are also interesting differences between the revised
 model and the RW Tri data set. For example, the model exhibits
@@
 
-Although we note that limb darkening effects on disk atmosphere opacities
+We note that limb darkening effects on disk atmosphere opacities
 would affect the Balmer jump (see section 5.2). In section 5.3, we demonstrate that
-although the double peaked lines narrow 
+although the double peaked lines narrow and 
 single-peaked emission can be formed in our densest models, 
 it is not due to the radial velocity shear mechanism proposed by MC96.
-We suggest that nonhomogenous, `clumpy' line-driven winds may offer a 
-potential solution.
+We suggest that nonhomogenous, `clumpy' line-driven winds or a different
+wind parameterization may allow this mechanism to work.
+We also note the possibility that, as in our denser models, 
+the single-peaked lines are formed well above the disk where 
+rotational velocities are lower.
 
@@
 
-We can also make a number of basic,
-testable predictions for wind-formed signatures:
+We can also make a couple of basic,
+testable predictions about the Balmer continuum emission
+from a simialr wind geometry:
 \begin{itemize}
@@
           continuum exceeds that of the foreshortened disk spectrum);
-	\item we predict that a strong He~\textsc{ii}~$\lambda3202{\rm
-          \AA}$ line should be prominent in all cases where
-          He~\textsc{ii}~$\lambda1640{\rm \AA}$ \& \heiiopt\ are seen
-          (but note that this prediction is not restricted to lines
-          formed in disk winds);
+	% \item we predict that a strong He~\textsc{ii}~$\lambda3202{\rm
+ %          \AA}$ line should be prominent in all cases where
+ %          He~\textsc{ii}~$\lambda1640{\rm \AA}$ \& \heiiopt\ are seen
+ %          (but note that this prediction is not restricted to lines
+ %          formed in disk winds);
 	\item we predict that the Balmer jump should be in emission
@@
 systems. In fact, most of the optical features characteristic of CVs
-are likely to be affected -- and possibly even dominated -- by their disk
+are likely to be affected - and possibly even dominated - by their disk
 winds. Given that optical spectroscopy plays the central role in
-observational studies of CVs, it is clearly critical to know 
+observational studies of CVs, it is critical to know 
 where and how these spectra are actually formed. We believe it is high

### 2015-01-19 generate/fig1_nl_spectra1/plot2.py

@@ -121,19 +121,18 @@ ylim(0.1,40)
 # plot model
 scale = 2.718 / 0.036
 subplot(212)
-s = rd.read_spectrum("cv_alpha4_r4r12_mdot1e9_rv1e11_opt")
-s2 = rd.read_spectrum("../../latest_outputs/cv_alpha4_r4r12_mdot1e9_rv1e11_opt")
+s = rd.read_spectrum("../../latest_outputs/cv_alpha4_r4r12_mdot1e9_rv1e11_opt")
 
-scale2 = scale / 1.7627659414
+
 plot( s["Lambda"], smooth(s["A80P0.50"], window_len=5)*1e11*scale,  c=colour, linewidth=weight)
 plot( s["Lambda"], smooth(s["A80P0.00"], window_len=5)*1e11*scale,  c=colour, linewidth=weight)
-plot( s2["Lambda"], smooth(s2["A80P0.50"], window_len=5)*1e11*scale2,  c='r', linewidth=weight)
-plot( s2["Lambda"], smooth(s2["A80P0.00"], window_len=5)*1e11*scale2,  c='r', linewidth=weight)
+# plot( s2["Lambda"], smooth(s2["A80P0.50"], window_len=5)*1e11*scale2,  c='r', linewidth=weight)
+# plot( s2["Lambda"], smooth(s2["A80P0.00"], window_len=5)*1e11*scale2,  c='r', linewidth=weight)
 xlim(3700,6900)
 
-print np.mean(s2["A80P0.50"]) / np.mean(s["A80P0.50"])
-print np.mean(s2["A80P0.50"]) / np.mean(s["A80P0.50"]) * 5
-print np.mean(s2["A80P0.50"]) / np.mean(s["A80P0.50"]) * 4
+# print np.mean(s2["A80P0.50"]) / np.mean(s["A80P0.50"])
+# print np.mean(s2["A80P0.50"]) / np.mean(s["A80P0.50"]) * 5
+# print np.mean(s2["A80P0.50"]) / np.mean(s["A80P0.50"]) * 4
 
 
 # text and labels

### 2015-01-19 generate/fig6_opt_cont/fig6_opt_continuum.py

@@ -43,12 +43,12 @@ for i in range(nspec):
 	a = get_continuum(s["Lambda"], s[s.colnames[9+i]], lines)
 
 	if mode == 'a':
-		plot(s["Lambda"], smooth(s[s.colnames[9+i]] /make_f(a, s["Lambda"]) ), c="k")
+		plot(s["Lambda"], smooth(s[s.colnames[9+i]] /make_f(a, s["Lambda"]), window_len=5  ), c="k")
 
 	elif mode == "b":
-		plot(s["Lambda"], smooth(s[s.colnames[9+i]] /make_f(a, s["Lambda"]) ), c="#d3d3d3", label="A")
+		plot(s["Lambda"], smooth(s[s.colnames[9+i]] /make_f(a, s["Lambda"]), window_len=5 ), c="#d3d3d3", label="A")
 		a = get_continuum(s2["Lambda"], s2[s2.colnames[9+i]], lines)
-		plot(s2["Lambda"], smooth(s2[s2.colnames[9+i]] /make_f(a, s2["Lambda"]) ), c="k", label="B")
+		plot(s2["Lambda"], smooth(s2[s2.colnames[9+i]] /make_f(a, s2["Lambda"]), window_len=5), c="k", label="B")
 	
 
 	if i == 2: ylabel("Flux/Continuum", fontsize=20)
@@ -63,6 +63,18 @@ for i in range(nspec):
 	print i
 	#if grids[i] < 8: ax.set_xticklabels([])
 	if i<4:ax.set_xticklabels([])
+
+	vlines([3646],0.4,1.95, linestyle="--")
+
+	if mode == "b":
+		vlines([5696],0.4,1.95, linestyle="--")
+
+	if i == 3:
+		text(3656, 1.6, "Balmer edge")
+		if mode == "b":
+			text(5706,0.6, r"He~\textsc{ii}, $n=5$ edge")
+
+
 
 
 #ax is name of original plot so change this to whatever your plot is called, 
@@ -86,14 +98,15 @@ for i in range(nspec):
 lines = [3202,4686,6563]
 subplot(515)
 vlines(lines,0.5,0.65, linewidth=2)
-labels = [r"He~\textsc{ii}~$\lambda3202$", r"He~\textsc{ii}~$\lambda4686$", r"H$\alpha$"]
[…]

### 2015-01-19 generate/murray/plotmc.py

@@ -27,7 +27,7 @@ for i in range(len(alphas)):
 
 
 
-	fname = "specs/cv_alpha%i_r4r12_mdot1e9_rv%s_opt" % (alphas[i], RV[i])
+	fname = "../../latest_outputs/cv_alpha%i_r4r12_mdot1e9_rv%s_opt" % (alphas[i], RV[i])
 
 	s = rd.read_spectrum(fname)
 
@@ -37,12 +37,12 @@ for i in range(len(alphas)):
 	ff = norm.make_f(a, s["Lambda"])
 	f = s["A80P0.50"]-ff
 
-	fmax = np.max(util.smooth(f[select],window_len=5))
+	fmax = np.max(util.smooth(f[select],window_len=8))
 	f = f / fmax
 
 	XTOPLOT = C* 1e-7 *(s["Lambda"] - 6563) / 6563
 
-	plot(XTOPLOT, util.smooth(f,window_len=5), c=colours[i], label=labels[i], linewidth=2)
+	plot(XTOPLOT, util.smooth(f,window_len=8), c=colours[i], label=labels[i], linewidth=2)
 
 
 legend()

### 2015-01-19 generate/spec_uv_opt/spec_uv_opt.py

@@ -2,17 +2,18 @@ import numpy as numpy
 from pylab import *
 import os, sys
 from cobra_sub import smooth
-import read_output as rd
+import read_output as r
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 import py_plot_util as util 
+import py_read_output as rd
 
 util.parse_rcparams()
 
 fname = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_uv"
 fname2 = "specs/cv_alpha4_r4r12_mdot1e9_rv1e11_uv"
 
-rd.setpars()
+r.setpars()
 
 mode = sys.argv[1]
 
@@ -24,8 +25,8 @@ ratio = 8.27 / 11.02
 figure(figsize=(8.27,12))
 incs = ("10", "27.5", "45", "62.5", "80")
 
-s = rd.read_spec_file(fname)
-s2 = rd.read_spec_file(fname2)
+s = rd.read_spectrum(fname)
+s2 = rd.read_spectrum(fname2)
 
 subplot(111)
 #xlabel("Wavelength [\AA]", fontsize=20)
@@ -41,15 +42,15 @@ for i in range(nspec):
 
 
 	if mode == "a":
-		plot(s.wavelength, 1e12*smooth(s.spec[i] ), c="k", label="A")
+		plot(s["Lambda"], 1e12*smooth(s[s.colnames[9+i]], window_len=5), c="k", label="A")
 
 	else:
-		plot(s.wavelength, 1e12*smooth(s.spec[i] ), c="#d3d3d3", label="A")
-		plot(s2.wavelength, 1e12*smooth(s2.spec[i] ), c="k", label="B")
+		plot(s["Lambda"], 1e12*smooth(s[s.colnames[9+i]], window_len=5), c="#d3d3d3", label="A")
+		plot(s2["Lambda"], 1e12*smooth(s2[s.colnames[9+i]], window_len=5), c="k", label="B")
 
 	if i == 2: ylabel("Flux at 100pc ($10^{-12}$~erg s$^{-1}$ cm$^{-3}$ \AA$^{-1}$)", fontsize=20)
 
-	#text(6100, 0.7*1e12*(np.max(s.spec[i])), "$i=%s^{\circ}$" % incs[i])
[…]

### 2015-01-19 generate/wind_plot/make_windplot.py

@@ -97,10 +97,10 @@ def masked_to_lin(masked_array, nplasmas, NPLASMA):
 
 
 
-fname = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_uv"
+fname = "../../latest_outputs/cv_alpha15_r4r12_mdot1e9_rv7e10_uv"
 
 
-#run_py_wind("78a", fname)
+run_py_wind("", fname)
 rd.setpars()
 
 

### 2015-01-19 generate/fig1_nl_spectra1/eclipse_compare.py
trimmed

@@ -1,204 +1,0 @@
-from constants import *
-import numpy as np
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import read_output as rd
-rd.setpars()
-
-def gauss(sigma, x0, x):
-
-	term = 1.0 / (2.0*np.pi) / sigma
-
-	exp_term = ( (x - x0)**2 )  /  (2.0*sigma*sigma)
-
-	term *= np.exp(-exp_term)
-
-	return term
-
-# def convolve(FWHM, x, y, mode="gaussian"):
-
-# 	'''
-# 	convolve arrays
-# 	'''
-
-# 	sigma = FWHM / (np.sqrt(8.0*np.log(2.0)))
-
-# 	n_points = len(x)
-
-# 	for i in range(n_points):
-
-def get_linelist(filenames, ionreturn=False):
-
-	lines = np.array([])
-	z = np.array([])
-
-	for i in range(len(filenames)):
-
-		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
-
-		lines = np.concatenate((lines, x[1]))
-
-		z = np.concatenate((z, x[0]))
-
-	if ionreturn:
-		return lines, z
-	else:
-		return lines
-
-
-
-
-
-
-
-# some fontsizes for figure
-font1 = 16				# fontsize for x label
-font2 = 16				# fontsize for Y label
-font3 = 16				# fontsize for text on figures
-weight = 1.5
-
-
-
-# standard plot parameters for mnras
-fig_width_pt=120.0 #Figure parameters
-inches_per_pt=1.0/72.27
-golden_mean=(math.sqrt(5)-1.0)/2.0
-fig_width=fig_width_pt*inches_per_pt
-fig_height=fig_width*golden_mean
-fig_size=(fig_width*8, fig_height*8)
-params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
-plt.rcParams.update(params)
-matplotlib.rcParams['ps.useafm'] = True
-matplotlib.rcParams['pdf.use14corefonts'] = True
-matplotlib.rcParams['text.usetex'] = True
-
-
-figure(figsize=fig_size)
[…]

### 2015-01-19 generate/fig1_nl_spectra1/photons.py

@@ -1,87 +1,0 @@
-from constants import *
-import numpy as np
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import read_output as rd
-
-
-def planck_l (T, lamb):
-
-	''' 
-	The planck function for wavelength lamb at temperature T
-
-	Takes lambda in ANGSTROMS and return ergs cm^-2 s^-2 sr^-1 AA^-1
-	'''
-
-	# convert to cm for planck equation
-	lamb2 = lamb*ANGSTROM
-
-	x = H_OVER_K * C / (T * lamb2)
-	Bnu = (2. * H * C**2.0) /  (lamb2**5.) / (np.exp(x) - 1.)
-
-	# convert back to ANGSTROM
-    
-	return Bnu*ANGSTROM
-
-
-
-x = np.arange(2000,5000,50)
-
-# create a blackbody
-y = planck_l(10000,x)
-
-total = np.sum(y)
-
-
-
-
-
-#generate photons
-NPHOT = int (sys.argv[1])
-photon_bins = np.zeros(len(y))
-
-#weight = lum / NPHOT
-
-weight = 1
-
-binsize = 50
-
-for i in range(NPHOT):
-
-
-	# generate photon and locate in cdf
-	z = np.random.random() * total
-
-	j = -1
-	c_sum = 0.0
-	while c_sum < z:
-
-		j += 1 
-		c_sum += y[j]
-
-	wave = x[j]
-	
-
-	photon_bins[j] += weight
-
-
-
-
-
-
-
-#plot(x,yc)
-scatter(x,photon_bins)
-
-show()
-
-
-
-
-
-
-
-
-
-

### 2015-01-19 generate/fig1_nl_spectra1/plot2.py

@@ -1,212 +1,0 @@
-from constants import *
-import numpy as np
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import py_read_output as rd
-rd.setpars()
-
-def gauss(sigma, x0, x):
-
-	term = 1.0 / (2.0*np.pi) / sigma
-
-	exp_term = ( (x - x0)**2 )  /  (2.0*sigma*sigma)
-
-	term *= np.exp(-exp_term)
-
-	return term
-
-# def convolve(FWHM, x, y, mode="gaussian"):
-
-# 	'''
-# 	convolve arrays
-# 	'''
-
-# 	sigma = FWHM / (np.sqrt(8.0*np.log(2.0)))
-
-# 	n_points = len(x)
-
-# 	for i in range(n_points):
-
-def get_linelist(filenames, ionreturn=False):
-
-	lines = np.array([])
-	z = np.array([])
-
-	for i in range(len(filenames)):
-
-		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
-
-		lines = np.concatenate((lines, x[1]))
-
-		z = np.concatenate((z, x[0]))
-
-	if ionreturn:
-		return lines, z
-	else:
-		return lines
-
-
-
-
-
-
-
-# some fontsizes for figure
-font1 = 16				# fontsize for x label
-font2 = 16				# fontsize for Y label
-font3 = 16				# fontsize for text on figures
-weight = 1.5
-
-
-
-# standard plot parameters for mnras
-fig_width_pt=120.0 #Figure parameters
-inches_per_pt=1.0/72.27
-golden_mean=(math.sqrt(5)-1.0)/2.0
-fig_width=fig_width_pt*inches_per_pt
-fig_height=fig_width*golden_mean
-fig_size=(fig_width*8, fig_height*8)
-params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
-plt.rcParams.update(params)
-matplotlib.rcParams['ps.useafm'] = True
-matplotlib.rcParams['pdf.use14corefonts'] = True
-matplotlib.rcParams['text.usetex'] = True
-
-
[…]

### 2015-01-19 generate/fig1_nl_spectra1/plot_dex.py

@@ -1,136 +1,0 @@
-'''
-plot_nl_figure.py 
-
-This script creates the figure for the Nova like spectra
-in the 2014 CV paper. The data were scraped from Dexter.
-'''
-
-
-from constants import *
-import numpy as np
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import read_output as rd
-rd.setpars()
-
-# some fontsizes for figure
-font1 = 16				# fontsize for x label
-font2 = 12				# fontsize for Y label
-font3 = 16				# fontsize for text on figures
-weight = 1.5			# lineweight
-
-
-
-# standard plot parameters for mnras
-fig_width_pt=120.0 #Figure parameters
-inches_per_pt=1.0/72.27
-golden_mean=(math.sqrt(5)-1.0)/2.0
-fig_width=fig_width_pt*inches_per_pt
-fig_height=fig_width*golden_mean
-fig_size=(fig_width*8, fig_height*8)
-params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
-plt.rcParams.update(params)
-matplotlib.rcParams['ps.useafm'] = True
-matplotlib.rcParams['pdf.use14corefonts'] = True
-matplotlib.rcParams['text.usetex'] = True
-
-
-figure(figsize=fig_size)
-colour = "b"
-
-# read the RW Sex data
-x1,y1 = np.loadtxt("rwsex/data11.dat", unpack=True, comments="#", usecols=(0,1))
-
-# read the IX Vel daata
-x, y = np.loadtxt("ixvel/data2.dat", unpack=True, comments="#", usecols=(0,1))
-a,b = np.loadtxt("ixvel/data.dat", unpack=True, comments="#", usecols=(0,1))
-
-# read the RW Tri data 
-cc,dd = np.loadtxt("rwtri/new_eclipse.dat", unpack=True, comments="#", usecols=(0,1))
-cc_no, dd_no = np.loadtxt("rwtri/rwtri_opt_noeclipse.dat", unpack=True, comments="#", usecols=(0,1))
-
-
-
-
-
-
-# adjust RW Tri from MJy to F_lambda in CGS units
-nus = (C) / (cc*ANGSTROM)
[…]

### 2015-01-19 generate/fig1_nl_spectra1/plot_nl_figure.py

@@ -1,307 +1,0 @@
-'''
-plot_nl_figure.py 
-
-This script creates the figure for the Nova like spectra
-in the 2014 CV paper. The data were scraped from Dexter.
-'''
-
-
-from constants import *
-import numpy as np
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import read_output as rd
-import py_plot_util as util 
-
-util.parse_rcparams("../params.rc")
-rd.setpars()
-
-# some fontsizes for figure
-font1 = 16				# fontsize for x label
-font2 = 16				# fontsize for Y label
-font3 = 16				# fontsize for text on figures
-weight = 2			# lineweight
-
-from matplotlib.ticker import MultipleLocator, FormatStrFormatter
-
-
-# standard plot parameters for mnras
-fig_width_pt=120.0 #Figure parameters
-inches_per_pt=1.0/72.27
-golden_mean=(math.sqrt(5)-1.0)/2.0
-fig_width=fig_width_pt*inches_per_pt
-fig_height=fig_width*golden_mean
-fig_size=(fig_width*8, fig_height*8)
-params={'font size' :10, 'axes.labelsize': 10, 'text.fontsize': 10, 'legend.fontsize': 10, 'xticks.labelsize': 8, 'yticks.labelsize': 8}
-plt.rcParams.update(params)
-matplotlib.rcParams['ps.useafm'] = True
-matplotlib.rcParams['pdf.use14corefonts'] = True
-matplotlib.rcParams['text.usetex'] = True
-
-
-figure(figsize=fig_size)
-colour = "k"
-
-# read the RW Sex data
-x1,y1 = np.loadtxt("rwsex/data11.dat", unpack=True, comments="#", usecols=(0,1))
-
-# read the IX Vel daata
-x, y = np.loadtxt("ixvel/data2.dat", unpack=True, comments="#", usecols=(0,1))
-a,b = np.loadtxt("ixvel/data.dat", unpack=True, comments="#", usecols=(0,1))
-
-# read the RW Tri data 
-cc,dd = np.loadtxt("rwtri/new_eclipse.dat", unpack=True, comments="#", usecols=(0,1))
[…]

### 2015-01-19 generate/fig2_cartoon/SV_cartoon.py

@@ -1,95 +1,0 @@
-'''
-SV_cartoon.py 
-
-This script creates the cartoon figure for 
-the 2014 CV paper. The data were scraped from Dexter.
-'''
-
-import matplotlib.mlab as mlab
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-
-
-mpl.rcParams['pdf.use14corefonts'] = True
-mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
-## for Palatino and other serif fonts use:
-#rc('font',**{'family':'serif','serif':['Palatino']})
-mpl.rc('text', usetex=True)
-
-thetamin=72.0
-thetamax=80.0
-diskmax=25.0
-xmin=10.0
-xmax=18.0
-rstar=2.0
-
-xwindmax=40.0
-zwindmax=(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))
-
-
-posx=np.arange(xmin,xwindmax,(xmax-xmin)/10.0)
-ymin1=[]
-ymax1=[]
-
-x=np.array([xmin,xmax,xwindmax])
-y1=np.array([0.0,(xmax-xmin)*np.tan(np.radians(90.0-thetamin)),(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))])
-y2=np.array([0.0,0.0,(xwindmax-xmax)*np.tan(np.radians(90.0-thetamax))])
-
-lsize=14
-tsize=16 
-
-fig=plt.figure()
-ax=fig.add_subplot(1,1,1)
-ax.plot(x,y1,x,y2,color='black')
-ax.plot(-1.0*x,y1,-1.0*x,y2,color='black')
-ax.plot(-1.0*x,-1.0*y1,-1.0*x,-1.0*y2,color='black')
-ax.plot(x,-1.0*y1,x,-1.0*y2,color='black')
-ax.set_xlim([-1.0*xwindmax,xwindmax])
-plt.fill_between(x,y1, y2, facecolor='0.9', interpolate=True)
-plt.fill_between(-1.0*x,y1, y2, facecolor='0.9', interpolate=True)
-plt.fill_between(x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
-plt.fill_between(-1.0*x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
[…]

### 2015-01-19 generate/fig3_acc_law/acc.py

@@ -1,68 +1,0 @@
-'''
-acc.py 
-
-Created the plot of the velocity law 
-for CV paper 2014
-'''
-
-import py_plot_util as util 
-util.parse_rcparams()
-
-
-from pylab import *
-
-figure()
-
-import read_output as rd 
-rd.setpars()
-import matplotlib.pyplot as plt 
-plt.rcParams["lines.linewidth"] = 2 
-
-plt.rcParams['ps.useafm'] = True
-plt.rcParams['pdf.use14corefonts'] = True
-
-
-def vel_law (l, R_v, alpha):
-
-	v0 = 6
-	v_inf=10000
-
-	v = (v_inf - v0) * (l / R_v)**alpha 
-
-	v /= 1.0 + (l / R_v)**alpha 
-
-	v += v0
-
-	return v
-
-
-alphas = [0.2,0.5,1, 1.5, 3,5,10]
-
-R_v = 7e10
-
-l = np.logspace(7,12,num=100000)
-
-colors = ["b", "g", "r", "k", "y", "c", "m"]
-
-i=0
-
-for alpha in alphas:
-
-	print alpha, np.log10(alpha)
-
-	plot(l/R_v, vel_law(l, R_v, alpha)/10000, label="$\\alpha=%.1f$" % alpha, c=colors[i])
-
-	i+=1
-
-
-
-xlim(0,2.0)
-legend(loc=4)
-
-xlabel("$l/R_v$", fontsize=16)
-ylabel("$v/v_{\infty}$", fontsize=16)
-
-savefig("acc_law.png")
-savefig("acc_law.eps", facecolor='w',edgecolor='w',bbox_inches='tight')
-
-

### 2015-01-19 generate/fig4_sed/bl_seds.py

@@ -1,116 +1,0 @@
-'''
-sed.py
-
-Create the plot of disk and BL seds for the
-CV paper 2014.
-
-Requireds JAMES's disk subtourines
-'''
-import disk
-from pylab import *
-import numpy as np 
-import os, sys
-from constants import *
-from cosmolopy.magnitudes import *
-from read_output import *
-
-# set some matplotlib parameters
-setpars()
-
-# minimum and max wavelengths for rings
-lmin = (C / 1e12) / ANGSTROM
-lmax = (C / 1e19) / ANGSTROM
-
-
-# make nr rings in a disk
-nr = 100	# number of rings
-r = disk.make_rings(lmin, lmax,0.8,1e-8,7e8,2.4e10, nrings = nr, mode="bb2")
-r2 = disk.make_rings(lmin, lmax,0.7,5e-9,8e8,2.4e10, nrings = nr, mode="bb2")
-
-
-
-
-# frequency resolution
-nfreq = 10000
-
-
-# create arrays for nu and fnu
-nu = np.logspace(np.log10(1e9), np.log10(1e19), num = nfreq)
-fnu = np.zeros(len(nu))
-fnu2 = np.zeros(len(nu))
-
-
-for j in range(nr - 1):
-	Bnu = disk.planck_nu (r.T[j], nu)
-	Bnu2 = disk.planck_nu (r2.T[j], nu)
-	print r.T[j]
-	for i in range(len(nu)):
-		fnu[i] += Bnu[i] * r.area[j] * PI
-		fnu2[i] += Bnu2[i] * r2.area[j] * PI
-
-
-
-
-L_acc = 0.5 * G * 0.8 * MSOL * 1e-8 * MSOL / YR / 7e8
-
-dnu = nu[1:] - nu[:-1]
-dnu = np.append(dnu, dnu[-1])
-
-Lacc = 2.0*np.sum(fnu*dnu)
-# L8 = np.sum(f8*dnu)
-# L20 = np.sum(f20*dnu)
-# print L_acc, Lacc, L8, L20
-#figure(figsize=(8,8))
-#loglog(nu, nu*fnu, label="Disk, HD91", linewidth=2.5, c="k")
-#loglog(nu, nu*fnu2, label=r"Disk, LK02", linewidth=2.5, c="#839096")
[…]

### 2015-01-19 generate/fig4_sed/sed.py

@@ -1,129 +1,0 @@
-'''
-sed.py
-
-Create the plot of disk and BL seds for the
-CV paper 2014.
-
-Requireds JAMES's disk subtourines
-'''
-import disk
-from pylab import *
-import numpy as np 
-import os, sys
-from constants import *
-from cosmolopy.magnitudes import *
-from read_output import *
-from py_plot_util import *
-
-# set some matplotlib parameters
-setpars()
-parse_rcparams()
-
-# minimum and max wavelengths for rings
-lmin = (C / 1e12) / ANGSTROM
-lmax = (C / 1e19) / ANGSTROM
-
-
-# make nr rings in a disk
-nr = 100	# number of rings
-r = disk.make_rings(lmin, lmax,0.8,1e-8,7e8,2.4e10, nrings = nr, mode="bb2")
-r2 = disk.make_rings(lmin, lmax,0.7,5e-9,8e8,2.4e10, nrings = nr, mode="bb2")
-
-
-
-
-# frequency resolution
-nfreq = 10000
-
-
-# create arrays for nu and fnu
-nu = np.logspace(np.log10(1e9), np.log10(1e19), num = nfreq)
-fnu = np.zeros(len(nu))
-fnu2 = np.zeros(len(nu))
-
-
-for j in range(nr - 1):
-	Bnu = disk.planck_nu (r.T[j], nu)
-	Bnu2 = disk.planck_nu (r2.T[j], nu)
-	print r.T[j]
-	for i in range(len(nu)):
-		fnu[i] += Bnu[i] * r.area[j] * PI
-		fnu2[i] += Bnu2[i] * r2.area[j] * PI
-
-
-
-
-L_acc = 0.5 * G * 0.8 * MSOL * 1e-8 * MSOL / YR / 7e8
-
-dnu = nu[1:] - nu[:-1]
-dnu = np.append(dnu, dnu[-1])
-
-Lacc = 2.0*np.sum(fnu*dnu)
-
-
-
-
-area8 = L_acc / STEFAN_BOLTZMANN / 80000.0**4
-area20 = L_acc / STEFAN_BOLTZMANN / 200000.0**4
-
-
-f8 = disk.planck_nu(80000,nu) * area8 * PI
-f20 = disk.planck_nu(200000,nu) * area20 * PI
-
-
-L8 = np.sum(f8*dnu)
-L20 = np.sum(f20*dnu)
-
-print L_acc, Lacc, L8, L20
-
-
[…]

### 2015-01-19 generate/fig5_uv_opt/fig5_uv_plus_opt_sidebyside.py

@@ -1,150 +1,0 @@
-import numpy as numpy
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import py_read_output as rd
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-import py_plot_util as util 
-
-util.parse_rcparams()
-
-fname = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_uv"
-fname2 = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_opt"
-
-rd.setpars()
-
-nx = 2
-
-ratio = 8.27 / 11.02
-figure(figsize=(8.27,12))
-incs = ("10", "17.5", "45", "62.5", "80")
-
-s = rd.read_spectrum(fname)
-
-subplot(111)
-#xlabel("Wavelength [\AA]", fontsize=20)
-nspec = 5
-
-grids = [1,3,5,7,9]
-
-dticks = [10,10,10,5,5]
-
-for i in range(nspec):
-
-	subplot(nspec,2,grids[i])
-	xlim(1000,2000)
-
-	plot(s["Lambda"], 1e12*smooth(s[s.colnames[9+i]] ), c="k")
-
-	if i == 2: ylabel("Flux at 100pc ($10^{-12}$~erg s$^{-1}$ cm$^{-3}$ \AA$^{-1}$)", fontsize=20)
-
-	#text(6100, 0.7*1e12*(np.max(s.spec[i])), "$i=%s^{\circ}$" % incs[i])
-	ax = gca()
-	
-
-	print grids[i]
-	#if grids[i] < 8: ax.set_xticklabels([])
-	if i<4:ax.set_xticklabels([])
-
-
-	start, end = ax.get_ylim()
-
-	if i == 4:
-		start, end = 0,35
-	ax.yaxis.set_ticks(np.arange(start, end, dticks[i]))
-	ylim(start,end)
-
-
-
-
-#ylim(0,49)
-labels = [r"Ly-$\alpha$", r"C\textsc{iv}", r"He~\textsc{ii}~$\lambda1640$"]
-lines = [1215,1550, 1640]
-vlines(lines, 27,30)
-
-offs = [-90,0,0]
-for i in range(len(labels)):
-	text(lines[i]+offs[i],31,labels[i], fontsize=10)
-
-
-#ax is name of original plot so change this to whatever your plot is called, 
-#loc is where in graph you want box containing zoomed plot, mess with numbers
[…]

### 2015-01-19 generate/fig6_opt_cont/fig6_opt_continuum.py

@@ -1,125 +1,0 @@
-import numpy as numpy
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-from plot_norm import *
-import py_read_output as rd
-import py_plot_util as util 
-
-util.parse_rcparams()
-
-fname = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_opt"
-fname2 = "specs/cv_alpha4_r4r12_mdot1e9_rv1e11_opt"
-
-rd.setpars()
-
-mode = sys.argv[1]
-
-atomic_filenames = [ "data/atomic_macro/h10_lines.py", "data/atomic73/lines_linked_ver_2.py", 
-	                     "data/atomic_macro/he_top_lines.py" ]
-lines = get_linelist(atomic_filenames)
-
-nx = 2
-
-figure(figsize=(8.3,11.6))
-incs = ("10", "17.5", "45", "62.5", "80")
-
-s = rd.read_spectrum(fname)
-s2 = rd.read_spectrum(fname2)
-
-subplot(111)
-xlabel("Wavelength (\AA)", fontsize=20)
-nspec = 5
-
-
-
-for i in range(nspec):
-
-	subplot(nspec,1,i+1)
-	xlim(3040,6900)
-
-	a = get_continuum(s["Lambda"], s[s.colnames[9+i]], lines)
-
-	if mode == 'a':
-		plot(s["Lambda"], smooth(s[s.colnames[9+i]] /make_f(a, s["Lambda"]), window_len=5  ), c="k")
-
-	elif mode == "b":
-		plot(s["Lambda"], smooth(s[s.colnames[9+i]] /make_f(a, s["Lambda"]), window_len=5 ), c="#d3d3d3", label="A")
-		a = get_continuum(s2["Lambda"], s2[s2.colnames[9+i]], lines)
-		plot(s2["Lambda"], smooth(s2[s2.colnames[9+i]] /make_f(a, s2["Lambda"]), window_len=5), c="k", label="B")
-	
-
-	if i == 2: ylabel("Flux/Continuum", fontsize=20)
-
-	if i == 0 and mode == "b":
-		legend()
-
-	#text(6100, 0.7*1e12*(np.max(s[s.colnames[9+i]])), "$i=%s^{\circ}$" % incs[i])
-	ax = gca()
-	ylim(0.4,1.95)
-
-	print i
-	#if grids[i] < 8: ax.set_xticklabels([])
[…]

### 2015-01-19 generate/fig7_escaping/fig7.py

@@ -1,49 +1,0 @@
-#from plot_norm import *
-import numpy as numpy
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-from plot_norm import *
-from constants import *
-from scipy import interp
-import py_plot_util as util
-import py_read_output as rd
-
-
-rd.setpars()
-util.parse_rcparams()
-
-mode = sys.argv[1]
-
-
-fname = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_opt"
-
-fname2 = "specs/cv_alpha4_r4r12_mdot1e9_rv1e11_opt"
-
-s = rd.read_spectrum(fname)
-s2 = rd.read_spectrum(fname2)
-
-if mode=="a":
-	plot(s["Lambda"], 1e12*smooth(s["Emitted"]), linewidth=2, label="Total", c="k")
-	plot(s["Lambda"], 1e12*smooth(s["Disk"]), label="Disk")
-	plot(s["Lambda"], 1e12*smooth(s["Wind"]), label="Wind")
-
-else:
-	# plot(s["Lambda"], 1e12*smooth(s["Emitted"]), linewidth=2, c="k", alpha=0.7)
-	# plot(s["Lambda"], 1e12*smooth(s["Disk"]), c="g", alpha=0.7)
-	# plot(s["Lambda"], 1e12*smooth(s["Wind"]), c="r", alpha=0.7))
-
-	plot(s2["Lambda"], 1e12*smooth(s2["Emitted"]), linewidth=2, label="Total", c="k")
-	plot(s2["Lambda"], 1e12*smooth(s2["Disk"]),  linewidth=1, c="g", label="Disk")
-	plot(s2["Lambda"], 1e12*smooth(s2["Wind"]),  linewidth=1, c="r", label="Wind")
-
-xlabel("Wavelength (\AA)", fontsize=16)
-ylabel("$\log [$Flux at 100pc $(10^{-12}$~erg s$^{-1}$ cm$^{-3}$ \AA$^{-1})]$", fontsize=16)
-semilogy()
-legend()
-xlim(3050,6800)
-
-savefig('../../figures/model%s_escaping.eps' % (mode),facecolor='w',edgecolor='w',bbox_inches='tight')
-savefig('model%s_escaping.png' % (mode))

### 2015-01-19 generate/fig_levels/level_tests.py

@@ -1,140 +1,0 @@
-'''
-James Matthews, 30/04/14
-
-plotting script for comparing Tardis and Python level populations
-'''
-
-#import modules
-import sys, os
-from tardis.io import config_reader
-from tardis import model, simulation
-import numpy as np
-import logging
-import warnings
-from numpy import exp
-from pylab import *
-from astropy import units
-
-
-def run_tardis(yml_file="basic.yml"):
-	'''
-	runs a tardis model and returns a class instance of Radial1dModel type
-	'''
-	#read the config file and create a model
-	tardis_config = config_reader.TARDISConfiguration.from_yaml(yml_file)
-	radial1d = model.Radial1DModel(tardis_config)
-	simulation.run_radial1d(radial1d)
-
-	return radial1d
-
-
-def set_model_params(radial1d, t_r, w, t_e, ne, tau):
-	'''
-	set the model parameters in tardis, returns model 
-	of same type as input
-	'''
-	radial1d.t_rads[:] = t_r * units.K
-	radial1d.ws[:] = w
-	radial1d.plasma_array.electron_densities.values[:] = ne
-
-	##interfere with any details - e.g. electron temperature - like this ...can also do electron density etc.
-	frac_te = t_e / t_r
-	radial1d.plasma_array.link_t_rad_to_t_electron = frac_te
-	##might want to set tau_sobolev optical depths to zero (or some other set of values) for ease of comparison
-	radial1d.plasma_array.tau_sobolevs.values[:] = tau
-
-	#calculate the mean intensities in the lines for chosen conditions
-	radial1d.calculate_j_blues()
-
-	#propagate rad field settings to plasma
-	radial1d.plasma_array.j_blues = radial1d.j_blues
-	radial1d.plasma_array.t_rads = radial1d.t_rads.value
-
-	return radial1d
-
-
-def get_tardis_pops(radial1d, t_r, w, t_e, ne, tau):
-
-	'''
-	takes a tardis model and calculates the level populations 
-	in these physical conditions (t_r, w, t_e, ne, tau)
-
[…]

### 2015-01-19 generate/fig_levels/make_fig_caseb_and_tardis.py

@@ -1,188 +1,0 @@
-'''
-James Matthews, 30/04/14
-
-plotting script for comparing Tardis and Python level populations
-'''
-
-#import modules
-import sys, os
-from tardis.io import config_reader
-from tardis import model, simulation
-import numpy as np
-import logging
-import warnings
-from numpy import exp
-from pylab import *
-from astropy import units
-import read_output as rd
-import py_plot_util as util 
-
-
-def run_tardis(yml_file="basic.yml"):
-	'''
-	runs a tardis model and returns a class instance of Radial1dModel type
-	'''
-	#read the config file and create a model
-	tardis_config = config_reader.TARDISConfiguration.from_yaml(yml_file)
-	radial1d = model.Radial1DModel(tardis_config)
-	simulation.run_radial1d(radial1d)
-
-	return radial1d
-
-
-def set_model_params(radial1d, t_r, w, t_e, ne, tau):
-	'''
-	set the model parameters in tardis, returns model 
-	of same type as input
-	'''
-	radial1d.t_rads[:] = t_r * units.K
-	radial1d.ws[:] = w
-	radial1d.plasma_array.electron_densities.values[:] = ne
-
-	##interfere with any details - e.g. electron temperature - like this ...can also do electron density etc.
-	frac_te = t_e / t_r
-	radial1d.plasma_array.link_t_rad_to_t_electron = frac_te
-	##might want to set tau_sobolev optical depths to zero (or some other set of values) for ease of comparison
-	radial1d.plasma_array.tau_sobolevs.values[:] = tau
-
-	#calculate the mean intensities in the lines for chosen conditions
-	radial1d.calculate_j_blues()
-
-	#propagate rad field settings to plasma
-	radial1d.plasma_array.j_blues = radial1d.j_blues
-	radial1d.plasma_array.t_rads = radial1d.t_rads.value
-
-	return radial1d
-
-
-def get_tardis_pops(radial1d, t_r, w, t_e, ne, tau):
-
-	'''
[…]

### 2015-01-19 generate/murray/plotmc.py

@@ -1,60 +1,0 @@
-#!/usr/bin/env python
-import py_plot_util as util
-import py_plot_output as plt
-import py_read_output as rd 
-import numpy as np
-from pylab import * 
-import os, sys
-from astropy.io import ascii
-import plot_norm as norm
-from constants import C
-
-util.parse_rcparams()
-rd.setpars()
-
-alphas = [15,4,4]
-alphas_actual = [1.5,4,1.5,4]
-RV = ["7e10", "1e11", "2e11"]
-
-colours = ["#d3d3d3", "k", "r","b","g"]
-labels=["A","B","X","Y"]
-
-atomic_filenames = [ "data/atomic_macro/h10_lines.py", "data/atomic73/lines_linked_ver_2.py", 
-                             "data/atomic_macro/he_top_lines.py" ]
-lines = norm.get_linelist(atomic_filenames)
-
-for i in range(len(alphas)):
-
-
-
-	fname = "../../latest_outputs/cv_alpha%i_r4r12_mdot1e9_rv%s_opt" % (alphas[i], RV[i])
-
-	s = rd.read_spectrum(fname)
-
-	select = (s["Lambda"] > 6513)*(s["Lambda"] < 6613)
-
-	a = norm.get_continuum(s["Lambda"], s["A80P0.50"], lines, lmin=5600,lmax=6700, deg = 1)
-	ff = norm.make_f(a, s["Lambda"])
-	f = s["A80P0.50"]-ff
-
-	fmax = np.max(util.smooth(f[select],window_len=8))
-	f = f / fmax
-
-	XTOPLOT = C* 1e-7 *(s["Lambda"] - 6563) / 6563
-
-	plot(XTOPLOT, util.smooth(f,window_len=8), c=colours[i], label=labels[i], linewidth=2)
-
-
-legend()
-xlim(-19.469118,19.469118)
-ylim(0,1)
-xlabel("Velocity (100 km/s)", fontsize=16)
-ylabel("Normalised Flux", fontsize=16)
-
-
-
-
-savefig("mc.png")
-savefig("../../figures/mc.eps")
-
-

### 2015-01-19 generate/spec_uv_opt/spec_uv_opt.py

@@ -1,211 +1,0 @@
-import numpy as numpy
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import read_output as r
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-import py_plot_util as util 
-import py_read_output as rd
-
-util.parse_rcparams()
-
-fname = "specs/cv_alpha15_r4r12_mdot1e9_rv7e10_uv"
-fname2 = "specs/cv_alpha4_r4r12_mdot1e9_rv1e11_uv"
-
-r.setpars()
-
-mode = sys.argv[1]
-
-
-nx = 2
-
-textwidth = 0.8
-ratio = 8.27 / 11.02
-figure(figsize=(8.27,12))
-incs = ("10", "27.5", "45", "62.5", "80")
-
-s = rd.read_spectrum(fname)
-s2 = rd.read_spectrum(fname2)
-
-subplot(111)
-#xlabel("Wavelength [\AA]", fontsize=20)
-nspec = 5
-
-grids = [1,3,5,7,9]
-dticks = [10,10,10,5,5]
-
-for i in range(nspec):
-
-	subplot(nspec,2,grids[i])
-	xlim(1000,2000)
-
-
-	if mode == "a":
-		plot(s["Lambda"], 1e12*smooth(s[s.colnames[9+i]], window_len=5), c="k", label="A")
-
-	else:
-		plot(s["Lambda"], 1e12*smooth(s[s.colnames[9+i]], window_len=5), c="#d3d3d3", label="A")
-		plot(s2["Lambda"], 1e12*smooth(s2[s.colnames[9+i]], window_len=5), c="k", label="B")
-
-	if i == 2: ylabel("Flux at 100pc ($10^{-12}$~erg s$^{-1}$ cm$^{-3}$ \AA$^{-1}$)", fontsize=20)
-
-	#text(6100, 0.7*1e12*(np.max(s[s.colnames[9+i]])), "$i=%s^{\circ}$" % incs[i])
-	ax = gca()
-	
-	if i == 0 and mode == "b":
-		legend()
-
-	print grids[i]
-	#if grids[i] < 8: ax.set_xticklabels([])
-	if i<4:ax.set_xticklabels([])
-	start, end = ax.get_ylim()
-	if i == 4 and mode == "b":
-		start = 0
-		end = 45
[…]

### 2015-01-19 generate/wind_plot/for_Sam/classes.py

@@ -1,177 +1,0 @@
-'''
-	University of Southampton -- JM -- 30 September 2013
-
-				classes.py
-
-Synopsis:
-	classes
-    
-    This is a set of classes for use with the radiative transfer code python
-
-Usage:
-	
-
-Arguments:
-'''
-
-
-
-
-class spectotclass:
-    '''This is a class for storing any values read from a Python spec_tot file'''	
-    def __init__(self, fre, wave, emi, cen, dis, win, sca, hit):
-        self.freq = fre
-        self.wavelength = wave
-        self.emitted = emi
-        self.censrc = cen
-        self.disk = dis
-        self.wind = win
-        self.scattered = sca
-        self.hitSurf = hit
-
-
-
-class specclass:
-    '''This is a class for storing any values read from a Python spec file'''	
-    def __init__(self, fre, wave, emi, cen, dis, win, sca, hit, spe):
-        self.freq = fre
-        self.wavelength = wave
-        self.emitted = emi
-        self.censrc = cen
-        self.disk = dis
-        self.wind = win
-        self.scattered = sca
-        self.hitSurf = hit
-        self.spec = spe
-
-class macroclass:
-    '''This is a class for storing any values read from a Python macro atom spec file'''	
-    def __init__(self, fre, wave, emi, cen, dis, win, l, hit, spe):
-        self.freq = fre
-        self.wavelength = wave
-        self.emitted = emi
-        self.censrc = cen
-        self.disk = dis
-        self.wind = win
-        self.lines = l
-        self.hitSurf = hit
-        self.spec = spe
-
-
-class topbase_class:
-	'''This is a class for topbase photoionization data'''	
-	def __init__(self, nz, ne, islp_init, E0_init, linit, np_init, energies, cross_sections):
-		self.Z = nz
-		self.ion = ne
-		self.islp = islp_init
-		self.l = linit
-		self.E0 = E0_init 
-		self.np = np_init
-		self.energy = energies
-		self.XS = cross_sections
-        
-        
-#mode class: sets mode from command line
-class modeclass:
-	'''The mode class: for reading arguments from command line'''
[…]

### 2015-01-19 generate/wind_plot/for_Sam/make_windplot.py

@@ -1,278 +1,0 @@
-import matplotlib.pyplot as plt 
-from pylab import * 
-import numpy as np 
-import csv, sys, os, array, warnings, subprocess
-import pywind_sub as ps
-import matplotlib as mpl
-from matplotlib.mlab import bivariate_normal
-from matplotlib.colors import LogNorm
-from matplotlib.backends.backend_pdf import PdfPages
-import matplotlib as mpl
-import time
-import read_output as rd
-
-
-def run_py_wind (vers, fname, cmds=None, ilv=None):
-	'''
-	run version vers of py_wind on file fname.wind_save
-	'''
-
-	if cmds == None:
-		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i","0", "1","1","1","2","2","2","2","1","2","3","6", \
-			          "3","6","4","6","5","0","q"])
-
-	x = cmds
-	np.savetxt("_tempcmd.txt", x, fmt = "%s")
-
-
-	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
-	time.sleep(3)
-
-	# remove temporary file
-	#os.system("rm -f _tempcmd.txt")
-	return isys
-
-
-
-
-def run_pydc (vers, fname, nplasma = 1):
-	'''
-	run version vers of py_wind on file fname.wind_save
-	'''
-
-	x = np.array(["1","M","4",str(nplasma),"1","-1","r","n","t","w", "q"])
-	np.savetxt("_tempcmd.txt", x, fmt = "%s")
-
-
-	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt')
-	time.sleep(3)
-
-	# remove temporary file
-	#os.system("rm -f _tempcmd.txt")
-	return isys
-
-#ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
-
-
-
-#nplasmas = ps.pywind_read(fname+'.pnum.dat',ix,iz)
-
-def read_pywind_smart(filename, return_inwind=False):
-	'''
-	read a py_wind file using np array reshaping and manipulation
-	'''
-
-	# first, simply load the filename 
[…]

### 2015-01-19 generate/wind_plot/for_Sam/plot_output.py

@@ -1,60 +1,0 @@
-import read_sub as sub
-from pylab import * 
-import numpy as np 
-import sys
-
-'''
-usage
- e.g. python plot_output.py sv 
-'''
- 
-
-fname = sys.argv[1]
-
-
-
-##### MAKING A WIND PLOT
-# run py_wind- only need to runt his to create the files
-sub.run_py_wind("77a_dev", fname)
-
-# read electron density from the file - could also try e.g. te or ionC4
-x, z, value = sub.read_pywind_smart(fname + ".ne.dat")
-
-# make a contour plot- note that z and x are in a weird order here
-# take the log with np.log10
-contourf(z,x,np.log10(value) )
-
-
-# make the y and x axes log!
-semilogy()
-semilogx()
-
-# add a colorbar
-colorbar()
-
-# add a title and axes labels
-#title("Title")
-#xlabel("X")
-#ylabel("Y")
-#edit xlims and ylims with xlim(30,40)
-
-show()		# show the figure
-
-#save with 
-#savefig("filename.png")
-
-#clear figure
-clf() 
-
-
-
-##### MAKING A SPECTRUM PLOT
-
-# read spec file
-s = sub.read_spec_file(fname)
-
-# plot the 0th element of the array which is the first viewing angle
-# use the function smooth to smooth the data
-plot(s.wavelength, sub.smooth(s.spec[0]) )
-show()
-

### 2015-01-19 generate/wind_plot/for_Sam/read_output.py

@@ -1,328 +1,0 @@
-'''
-	University of Southampton -- JM -- 30 September 2013
-
-				read_output.py
-
-Synopsis:
-	this enables one to read outputs from the Python radiative transfer code
-
-Usage:
-	
-
-Arguments:
-'''
-
-# we need the classes and numpy modules 
-import classes as cls
-import numpy as np
-import matplotlib.pyplot as plt
-import subprocess
-
-
-def read_spec_file (filename):
-    
-    '''reads a Python .spec file and places in specclass array,
-       which is returned'''
-    
-    if not '.spec' in filename: 
-        filename = filename + '.spec'
-        
-    
-    # initialise the spectrum array with blank arrays
-    spectrum = cls.specclass ([],[],[],[],[],[], [], [], []) 
-    
-    # first read the file into a temporary storage array
-    spectrum_temp = np.loadtxt (filename, comments ='#', unpack=True)
-    
-    # now set the correct elements of the class to be the temporary array
-    spectrum.freq = spectrum_temp[0]
-    spectrum.wavelength = spectrum_temp[1]
-    spectrum.emitted = spectrum_temp[2]
-    spectrum.censrc = spectrum_temp[3]
-    spectrum.disk = spectrum_temp[4]
-    spectrum.wind = spectrum_temp[5] 
-    spectrum.scattered = spectrum_temp[7]
-    spectrum.hitsurf = spectrum_temp[6]
-    spectrum.spec = spectrum_temp[8:]
-        
-     #finally, return the spectrum class which is a series of named arrays      
-    return spectrum
-
-
-def macro_spec (filename):
-    
-    '''reads a Python .spec file and places in specclass array,
-       which is returned'''
-    
-    if not '.spec' in filename: 
-        filename = filename + '.spec'
-        
-    
-    # initialise the spectrum array with blank arrays
-    spectrum = cls.macroclass ([],[],[],[],[],[], [], [], []) 
-    
-    # first read the file into a temporary storage array
-    spectrum_temp = np.loadtxt (filename, comments ='#', unpack=True)
-    
-    # now set the correct elements of the class to be the temporary array
-    spectrum.freq = spectrum_temp[0]
-    spectrum.wavelength = spectrum_temp[1]
-    spectrum.emitted = spectrum_temp[2]
-    spectrum.censrc = spectrum_temp[3]
-    spectrum.disk = spectrum_temp[4]
-    spectrum.wind = spectrum_temp[5] 
[…]

### 2015-01-19 generate/wind_plot/for_Sam/read_sub.py

@@ -1,200 +1,0 @@
-import numpy as np
-import time
-import sys
-import os
-
-
-class specclass:
-    '''This is a class for storing any values read from a Python spec file'''	
-    def __init__(self, fre, wave, emi, cen, dis, win, sca, hit, spe):
-        self.freq = fre
-        self.wavelength = wave
-        self.emitted = emi
-        self.censrc = cen
-        self.disk = dis
-        self.wind = win
-        self.scattered = sca
-        self.hitSurf = hit
-        self.spec = spe
-
-
-def read_spec_file (filename):
-    
-    '''reads a Python .spec file and places in specclass array,
-       which is returned'''
-    
-    if not '.spec' in filename: 
-        filename = filename + '.spec'
-        
-    
-    # initialise the spectrum array with blank arrays
-    spectrum = specclass ([],[],[],[],[],[], [], [], []) 
-    
-    # first read the file into a temporary storage array
-    spectrum_temp = np.loadtxt (filename, comments ='#', unpack=True)
-    
-    # now set the correct elements of the class to be the temporary array
-    spectrum.freq = spectrum_temp[0]
-    spectrum.wavelength = spectrum_temp[1]
-    spectrum.emitted = spectrum_temp[2]
-    spectrum.censrc = spectrum_temp[3]
-    spectrum.disk = spectrum_temp[4]
-    spectrum.wind = spectrum_temp[5] 
-    spectrum.scattered = spectrum_temp[7]
-    spectrum.hitsurf = spectrum_temp[6]
-    spectrum.spec = spectrum_temp[8:]
-        
-     #finally, return the spectrum class which is a series of named arrays      
-    return spectrum
-
-
-
-def run_py_wind (vers, fname, cmds=None, ilv=None):
-	'''
-	run version vers of py_wind on file fname.wind_save
-	'''
-
-	if cmds == None:
-		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i","0", "1","1","1","2","2","2","2","1","2","3","6", \
-			          "3","6","4","6","5","0","q"])
-
-	x = cmds
-	np.savetxt("_tempcmd.txt", x, fmt = "%s")
-
-
-	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
-	time.sleep(3)
-
-	# remove temporary file
-	#os.system("rm -f _tempcmd.txt")
-	return isys
-
-
-
-def read_pywind_smart(filename, return_inwind=False):
-	'''
[…]

### 2015-01-19 generate/wind_plot/he2_bl_plot.py

@@ -1,229 +1,0 @@
-import matplotlib.pyplot as plt 
-from pylab import * 
-import numpy as np 
-import csv, sys, os, array, warnings, subprocess
-import pywind_sub as ps
-import matplotlib as mpl
-from matplotlib.mlab import bivariate_normal
-from matplotlib.colors import LogNorm
-from matplotlib.backends.backend_pdf import PdfPages
-import matplotlib as mpl
-import time
-import read_output as rd
-import matplotlib.gridspec as gridspec
-
-
-def run_py_wind (vers, fname, cmds=None, ilv=None):
-	'''
-	run version vers of py_wind on file fname.wind_save
-	'''
-
-	if cmds == None:
-		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i","0", "1","1","1","2","2","2","2","1","2","3","6", \
-			          "3","6","4","6","5","0","q"])
-
-	x = cmds
-	np.savetxt("_tempcmd.txt", x, fmt = "%s")
-
-
-	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
-	time.sleep(3)
-
-	# remove temporary file
-	#os.system("rm -f _tempcmd.txt")
-	return isys
-
-
-
-
-def run_pydc (vers, fname, nplasma = 1):
-	'''
-	run version vers of py_wind on file fname.wind_save
-	'''
-
-	x = np.array(["1","M","4",str(nplasma),"1","-1","r","n","t","w", "q"])
-	np.savetxt("_tempcmd.txt", x, fmt = "%s")
-
-
-	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt')
-	time.sleep(3)
-
-	# remove temporary file
-	#os.system("rm -f _tempcmd.txt")
-	return isys
-
-#ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
-
-
-
-#nplasmas = ps.pywind_read(fname+'.pnum.dat',ix,iz)
-
-def read_pywind_smart(filename, return_inwind=False):
-	'''
-	read a py_wind file using np array reshaping and manipulation
-	'''
-
-	# first, simply load the filename 
[…]

### 2015-01-19 generate/wind_plot/pywind_summary_paper.py

@@ -1,218 +1,0 @@
-#! /Library/Frameworks/EPD64.framework/Versions/Current/bin/python -i
-
-import csv, sys, os, array, warnings, subprocess
-import matplotlib.pyplot as plt
-import numpy as np
-import pywind_sub as ps
-import matplotlib as mpl
-from matplotlib.mlab import bivariate_normal
-from matplotlib.colors import LogNorm
-from matplotlib.backends.backend_pdf import PdfPages
-import matplotlib as mpl
-
-mpl.rcParams['text.usetex']='true'
-
-
-fname=sys.argv[1]
-
-#cmdline='py_wind78a '+fname+' < paper_pywindcmds'
-#subprocess.check_call(cmdline,shell=True)	
-
-x=[]
-z=[]
-x1=[]
-z1=[]
-lx=[]
-lz=[]
-lx1=[]
-lz1=[]
-
-data=[]
-IPtemp=[]
-tetemp=[]
-nhtemp=[]
-xtemp=[]
-ztemp=[]
-
-tetemp=[]
-trtemp=[]
-
-convtemp=[]
-
-vx=[]
-vz=[]
-
-H1=[]
-H2=[]
-C4temp=[]
-Si4temp=[]
-N5temp=[]
-O6temp=[]
-
-
-
-ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
-
-
-
-H1=ps.pywind_read(fname+'.ioncH1.dat',ix,iz)
-H2=ps.pywind_read(fname+'.ioncH2.dat',ix,iz)
-
-H=np.empty([ix,iz])
-for i in range(ix):
-	for j in range(iz):
-		H[i][j]=np.log10(H1[i][j]+H2[i][j])
-
-
-
-IP=ps.pywind_read(fname+'.IP.dat',ix,iz)
-te=ps.pywind_log_read(fname+'.te.dat',ix,iz)
-#tr=ps.pywind_log_read(fname+'.tr.dat',ix,iz)
-vx=ps.pywind_read(fname+'.vz.dat',ix,iz)
-vy=ps.pywind_read(fname+'.vy.dat',ix,iz)
-vz=ps.pywind_read(fname+'.vz.dat',ix,iz)
-#nagn=ps.pywind_log_read(fname+'.nphot.dat',ix,iz)
-
-
-
-
-
-vxz=np.empty([ix,iz])
-for i in range(ix):
-	for j in range(iz):
[…]

### 2015-01-19 generate/wind_plot/windplot_new.py

@@ -1,253 +1,0 @@
-import matplotlib.pyplot as plt 
-from pylab import * 
-import numpy as np 
-import csv, sys, os, array, warnings, subprocess
-import pywind_sub as ps
-import matplotlib as mpl
-from matplotlib.mlab import bivariate_normal
-from matplotlib.colors import LogNorm
-from matplotlib.backends.backend_pdf import PdfPages
-import matplotlib as mpl
-import time
-import read_output as rd
-
-
-def run_py_wind (vers, fname, cmds=None, ilv=None):
-	'''
-	run version vers of py_wind on file fname.wind_save
-	'''
-
-	if cmds == None:
-		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i", "1","1","1","2","0","i","0", "1","1","1","2","2","2","2","1","2","3","6", \
-			          "3","6","4","6","5","0","q"])
-
-	x = cmds
-	np.savetxt("_tempcmd.txt", x, fmt = "%s")
-
-
-	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
-	time.sleep(3)
-
-	# remove temporary file
-	#os.system("rm -f _tempcmd.txt")
-	return isys
-
-
-
-
-def run_pydc (vers, fname, nplasma = 1):
-	'''
-	run version vers of py_wind on file fname.wind_save
-	'''
-
-	x = np.array(["1","M","4",str(nplasma),"1","-1","r","n","t","w", "q"])
-	np.savetxt("_tempcmd.txt", x, fmt = "%s")
-
-
-	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt')
-	time.sleep(3)
-
-	# remove temporary file
-	#os.system("rm -f _tempcmd.txt")
-	return isys
-
-#ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
-
-
-
-#nplasmas = ps.pywind_read(fname+'.pnum.dat',ix,iz)
-
-def read_pywind_smart(filename, return_inwind=False):
-	'''
-	read a py_wind file using np array reshaping and manipulation
-	'''
-
-	# first, simply load the filename 
[…]

### 2015-01-21 draft.tex
trimmed
figure order
commit before fiddling with sobolev things

@@
 streamline. The terminal velocity along a streamline, $v_{\infty}$, is
-set to a fixed multiple of the escape velocity at the launch
+set to a fixed multiple of $v_{esc}$, the escape velocity at the launch
 point. The launch velocity from the disk surface, $v_0$, is assumed to
@@
 model A parameter is used. $P_{orb}$ is the orbital period 
-(the value for RW Tri from ?? is adopted, see section 5.4) and 
+(the value for RW Tri from Walker 1963 is adopted, see section 5.4) and 
 $R_2$ is the radius of a sphere with the volume of the secondary's Roche lobe. 
@@
 \end{table}
+
+\nocite{walker1963}
 
@@
 
-We begin by verifying that the benchmark model still produces UV
-spectra that resemble those observed in CVs. We do expect this to be
-the case, since the ionization state of the wind has not changed
-significantly from that computed by LK02 (see section~\ref{modela_ionization}). 
-The left column of panels in Fig.~\ref{spec} shows that this expectation
-is met: all of the strong metal resonance
-lines - notably N\textsc{v}~$\lambda1240$,
-Si\textsc{iv}~$\lambda1400$ and C\textsc{iv}~$\lambda1550$ - 
-are present and exhibit clear P-Cygni profiles
-at intermediate inclinations. In addition, however, we now also find
-that the wind produces significant Lyman-$\alpha$ and
-He~\textsc{ii}~$\lambda1640$ emission lines.
-
 \begin{figure} %fullpage
@@
 
+We begin by verifying that the benchmark model still produces UV
+spectra that resemble those observed in CVs. We do expect this to be
+the case, since the ionization state of the wind has not changed
+significantly from that computed by LK02 (see section~\ref{modela_ionization}). 
+The left column of panels in Fig.~\ref{spec} shows that this expectation
+is met: all of the strong metal resonance
+lines - notably N\textsc{v}~$\lambda1240$,
+Si\textsc{iv}~$\lambda1400$ and C\textsc{iv}~$\lambda1550$ - 
+are present and exhibit clear P-Cygni profiles
+at intermediate inclinations. In addition, however, we now also find
+that the wind produces significant Lyman-$\alpha$ and
+He~\textsc{ii}~$\lambda1640$ emission lines.
+
 Fig.~\ref{spec} (right-hand panel) and Fig.~\ref{spec_continuum}
@@
 \begin{figure} 
-\includegraphics[width=0.5\textwidth]{figures/modela_escaping.eps}
+\includegraphics[width=0.45\textwidth]{figures/modela_escaping.eps}
 \caption{Total packet-binned spectra across all viewing angles. 
@@
 as well as the velocity gradients is by modifying the poloidal velocity
-law. We have therefore conducted a exploratory sensitivity study in
-which we focus on just two kinematic variables (section~\ref{kinematics}):
+law. To do this, we focus on just two kinematic variables (section~\ref{kinematics}):
 
@@
 \end{figure} %fullpage
-
-\begin{figure} 
-\includegraphics[width=0.45\textwidth]{figures/modelb_opt_cont.eps}
-\caption{
-Synthetic optical spectra from model B computed for 
-sightlines of 10, 27.5, 45, 62.5 and 80 degrees. In these plots
-the flux is divided by a polynomial fit to the 
-underlying continuum redward of the Balmer edge, so that 
-line-to-continuum ratios and the true depth of the
-Balmer jump can be shown.
-}
-\label{continuumb}
-\end{figure}
-
-\begin{figure} 
-\includegraphics[width=0.5\textwidth]{figures/modelb_escaping.eps}
-\caption{Total packet-binned spectra across all viewing angles. 
-The thick black line shows the total 
-integrated escaping spectrum, 
-while the green line shows disk photons which escape without being reprocessed by
-the wind. The red line show the contributions from reprocessed 
-photons. 
-In this denser model the reprocessed contribution is significant compared
-to the escaping disk spectrum. The Balmer continuum emission is prominent, and
-the wind has a clear effect on the overall spectral shape.}
-\label{modelb_escape}
-\end{figure}
 
@@
 
-\subsection{Line Profile Shapes: Producing Single-Peaked Emission}
-
-Fig.~\ref{halpha} shows how the H$\alpha$ profile changes with the kinematics of the wind for 
-an inclination of $80^\circ$. The main prediction is that dense, slowly accelerating 
-wind models produce narrower emission lines. This is {\em not} due to the radial 
-velocity shear mechanism proposed by MC96. That mechanism can only work if poloidal 
-and rotational velocity gradients satisfy $(dv_l/dr)/(dv_\phi/dr) \gtrsim 1$; in 
-our models, this ratio is always $\lesssim 0.1$. Instead, the narrow lines predicted 
-by our denser wind models can be traced to the base of the outflow becoming optically 
-thick to line photons. In such models, the `line photosphere'
-(the $\tau \simeq 1$ surface of the line-forming region) moves outwards, towards larger 
-vertical and cylindrical distances. This reduces the predicted line widths, since the 
-rotational velocities -- which normally provide the main line broadening mechanism at 
-high inclination -- drop off as $1/r$. This is not to say that the MC96 
-mechanism could not be at work in CV winds. For example, it would be worth investigating
-alternative prescriptions for the wind velocity field, as well as the possibility that the 
-outflows may be clumped. However, such an investigation is beyond the scope of the present paper.
-
-In our models, single-peaked line profiles are produced once the line forming region has been
-pushed up to $\sim 10^{11}$~cm ($\sim150~R_{WD}$) above the disk plane. 
-This number may seem unrealistically large, but the vertical extent of 
-the emission region is actually not well constrained observationally. 
-In fact, multiple observations of eclipsing NLs show that the H$\alpha$ 
-line is only moderately eclipsed compared to the continuum (e.g. Baptista et al. 2000;
-Groot et al. 2004; see also section 5.4), 
-implying a significant vertical extent for the line-forming 
-region. This type of model should therefore not be ruled out {\em a priori}.
+\begin{figure} 
+\includegraphics[width=0.45\textwidth]{figures/modelb_opt_cont.eps}
+\caption{
+Synthetic optical spectra from model B computed for 
+sightlines of 10, 27.5, 45, 62.5 and 80 degrees. In these plots
+the flux is divided by a polynomial fit to the 
+underlying continuum redward of the Balmer edge, so that 
+line-to-continuum ratios and the true depth of the
+Balmer jump can be shown.
+}
+\label{continuumb}
+\end{figure}
+
+\begin{figure} 
+\includegraphics[width=0.45\textwidth]{figures/modelb_escaping.eps}
+\caption{Total packet-binned spectra across all viewing angles. 
+The thick black line shows the total 
+integrated escaping spectrum, 
+while the green line shows disk photons which escape without being reprocessed by
+the wind. The red line show the contributions from reprocessed 
+photons. 
+In this denser model the reprocessed contribution is significant compared
+to the escaping disk spectrum. The Balmer continuum emission is prominent, and
+the wind has a clear effect on the overall spectral shape.}
+\label{modelb_escape}
+\end{figure}
 
@@
 
-\subsection{Comparison to RW Tri}
+\subsection{Line Profile Shapes: Producing Single-Peaked Emission}
 
@@
 \end{figure} %fullpage
+
+Fig.~\ref{halpha} shows how the H$\alpha$ profile changes with the kinematics of the wind for 
+an inclination of $80^\circ$. The main prediction is that dense, slowly accelerating 
+wind models produce narrower emission lines. This is {\em not} due to the radial 
+velocity shear mechanism proposed by MC96. That mechanism can only work if poloidal 
+and rotational velocity gradients satisfy $(dv_l/dr)/(dv_\phi/dr) \gtrsim 1$; in 
+our models, this ratio is always $\lesssim 0.1$. Instead, the narrow lines predicted 
+by our denser wind models can be traced to the base of the outflow becoming optically 
+thick to line photons. In such models, the `line photosphere'
+(the $\tau \simeq 1$ surface of the line-forming region) moves outwards, towards larger 
+vertical and cylindrical distances. This reduces the predicted line widths, since the 
+rotational velocities -- which normally provide the main line broadening mechanism at 
+high inclination -- drop off as $1/r$. This is not to say that the MC96 
+mechanism could not be at work in CV winds. For example, it would be worth investigating
+alternative prescriptions for the wind velocity field, as well as the possibility that the 
+outflows may be clumped. However, such an investigation is beyond the scope of the present paper.
+
+In our models, single-peaked line profiles are produced once the line forming region has been
+pushed up to $\sim 10^{11}$~cm ($\sim150~R_{WD}$) above the disk plane. 
+This number may seem unrealistically large, but the vertical extent of 
+the emission region is actually not well constrained observationally. 
+In fact, multiple observations of eclipsing NLs show that the H$\alpha$ 
+line is only moderately eclipsed compared to the continuum (e.g. Baptista et al. 2000;
+Groot et al. 2004; see also section 5.4), 
+implying a significant vertical extent for the line-forming 
+region. This type of model should therefore not be ruled out {\em a priori}.
+
+\subsection{Comparison to RW Tri}
 

### 2015-01-22 draft.tex
corrected a number of errors, units and wording

@@
 the optical spectrum, particularly for systems viewed at high
-inclination. The strongest optical wind-formed recombinations lines are \ha\ and
-\heiiopt\, although the outflow also produces emission in the Ly$\alpha$
+inclination. The strongest optical wind-formed recombination lines are \ha\ and
+\heiiopt, although the outflow also produces emission in the Ly$\alpha$
 and \heiiuv\ UV lines. However, all of the optical lines produced by
@@
 collisionally excited UV emission lines. 
-Our revised model also significantly
-alters the spectral shape of the continuum and displays
-a strong inclination dependence in its emission properties. 
+The wind in our revised model also alters the spectral shape of the continuum, 
+and displays a strong inclination dependence in its emission properties. 
 No single-peaked emission is seen, although we observe a 
 narrowing of the double-peaked emission lines from the base of the wind.
-We show that denser models can produce a single-peaked \ha\ line,
-but this is not due to radial velocity shear mechanism that
-has previously been proposed. On the basis of these results, we suggest that winds can 
+We show that denser models can produce a single-peaked \ha\ line.
+The single-peaked line profile is due to the line emission originating from 
+$\sim10^11$~cm above the disk plane where rotational velocities are small, 
+and is not due to the radial velocity shear mechanism that
+has previously been proposed. 
+On the basis of our results, we suggest that winds can 
 modify, and perhaps even dominate, the line and continuum emission
@@
 RW Sex (top; Beuermann et al. 1992),
-IX Vel (top middle; A. Pala \& B. Gaensicke, private communication) 
+IX Vel (top middle; A. F. Pala \& B. T. Gaensicke, private communication) 
 and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
 The data for RW Sex and RW Tri were digitized from the respective publications,
-and the IX Vel spectrum was obtained using XShooter on the VLT on the night of ??.
-These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $70^\circ$ 
+and the IX Vel spectrum was obtained using the XSHOOTER spectrograph 
+on the Very Large Telescope on 2014 October 10.
+These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $75^\circ$ 
 (see section 5.4) respectively. 
@@
 \nocite{beuermann1992}
+\nocite{higginbottom2013}
 
@@
 \py\ is a Monte Carlo  ionization and radiative transfer code which
-uses the Sobolev approximation to treat line transfer. It has already
-been described extensively by LK02, SDL05 and Higginbottom et al. (2013; hereafter H13), 
-so here we provide only a brief summary of its operation, focusing particularly on new
+uses the Sobolev approximation to treat line transfer 
+\citep[e.g.][]{sobolev1957,sobolev1960,rybickihummer1978}. 
+The code has already been described extensively by LK02, SDL05 and Higginbottom et al. (2013; hereafter H13), so here we provide only a brief summary of its operation, 
+focusing particularly on new
 aspects of our implementation of macro-atoms into the code.
@@
 outflow are specified on a pre-defined spatial grid. In each of these
-iterations (``ionization cycles''), the code records estimators that 
+iterations (`ionization cycles'), the code records estimators that 
 characterize the radiation field in each grid cell. At the end 
@@
 This converged model is then used as the basis for the second set of
-iterations (``spectral cycles''). In these, the emergent spectrum over
+iterations (`spectral cycles'). In these, the emergent spectrum over
 the desired spectral range is synthesized by tracking populations of
@@
 of this effort, they implemented a `macro-atom' mode (see below) in
-order to correctly treat hydrogen recombination lines with
+order to correctly treat H recombination lines with
 \py. Finally, H13 used \py\ to model broad absorption line (BAL) QSOs. For
@@
 
-\subsection{Ionization and Excitation: ``Simple Atoms''}
+\subsection{Ionization and Excitation: `Simple Atoms'}
 \label{simpleatoms}
@@
 Here, the `starred' term on the right represents abundances computed with
-the Saha equation at temperature $T_R$, but using actual partition functions
+the Saha equation at temperature $T_R$, but using partition functions
 from the dilute blackbody approximation. 
@@
 $E_k$ is the energy difference between level $k$ and the ground state,
+$g_k$ is the statistical weight of level $k$
 and $z_j(T_R)$ is the partition function of ionic stage $j$.
@@
 Finally, \py\ modelled all bound-bound processes as transitions
-within a simple two-level atom \cite[see e.g.][]{mihalas}. This
+within a simple two-level atom \cite[e.g.][]{mihalas}. This
 approach works reasonably well for resonance  
@@
 winds \citep{sim2004}, AGN disk winds \citep{simlong2008, tatum2012},
-supernovae \citep{kasen2006, kerzendorfsim} and YSOs (SDL05). A full 
+supernovae \citep{kromersim, kerzendorfsim} and YSOs (SDL05). A full 
 description of the approach can be found in L02 and L03.
@@
 are calculated by solving the statistical equilbrium equations between
-each pair of levels. For example, the bound-bound de-excitation rate,
-${\cal R}_{ul}$, in an ion is given by  
+each pair of levels. In the framework of the Sobolev escape probability formalism (Rybicki \& Hummer 1978; L02; Sim 2004), 
+the bound-bound excitation rate, ${\cal R}_{lu}$, in an ion is given by 
 \begin{equation}
-{\cal R}_{ul} = \beta_{lu} A_{ul} n_u + \beta_{lu} B_{ul} n_u J_{ul} +
-C_{ul} n_u n_e,\label{eq:nlte_rul},
+{\cal R}_{lu} = B_{lu} n_l J_{est} + C_{lu} n_l n_e,
 \end{equation}
 where $u$ and $l$ denote the upper and lower levels, $C$ represents the
-collisional rate coefficients, and $A$ and $B$ represent the Einstein
-coefficients. The quantity $\beta_{lu}$ is the probability that a
-given line photon will escape the Sobolev region. Finally, $J_{lu}$ is the
-Monte Carlo estimator for the mean intensity in the line. 
-The corresponding excitation rate is then 
+collisional rate coefficients, and $B$ is the usual Einstein
+coefficient. $J_{est}$ is the Monte Carlo estimator for the mean intensity 
+impinging on the Sobolev region, weighted by an angle-dependent escape probability, 
+given by \citep{sim2004}
 \begin{equation}
-{\cal R}_{lu} = \beta_{lu} B_{lu} n_l J_{lu} + C_{lu} n_l n_e,
+J_{est} = \frac{c}{4 \pi \nu_0 V} \sum_{photons} w \frac{1 - e^{-\tau_s}}{\tau_s} \frac{1}{dv/ds}.
 \end{equation}
-where we implicitly include a correction for stimulated emission in
-our definition of $J_{lu}$.
+Here $w$ is the photon weight (in luminosity units), $\nu_0$
+is the line frequency, $dv/ds$ is the velocity gradient and
+$\tau_s$ is the Sobolev optical depth experienced by the photon in resonance.
+The sum is over all photons that come into resonance with the line.
+The corresponding de-excitation rate is then 
+\begin{equation}
+{\cal R}_{ul} = \beta_{lu} A_{ul} n_u + B_{ul} n_u J_{est} +
+C_{ul} n_u n_e,
+\label{eq:nlte_rul}
+\end{equation}
+where $A$ is the usual Einstein coefficient. 
+The quantity $\beta_{lu}$ is the {\em angle-averaged} probability 
+that a given line photon will escape the Sobolev region.
 
@@
 ionization directly to excited levels of the upper ion. The
-\cite{vanregemorter} approximation is used for collisional
+Van Regemorter (1962) approximation is used for collisional
 transitions, and thus we assume that collisions between radiatively
@@
 
-SDL05 implemented a macro-atom treatment of Hydrogen in \py\ and used
-this to predict the observable properties of a pure Hydrogen wind
+SDL05 implemented a macro-atom treatment of H in \py\ and used
+this to predict the observable properties of a pure H wind
 model for YSOs. Our goal here is to simultaneously model the optical
@@
 version of that described by LK02. In addition, we follow SDL05 in
-treating Hydrogen as a 20-level atom, where each level is defined by
+treating H as a 20-level atom, where each level is defined by
 the principal quantum number, $n$. For the macro-atom treatment of
-Helium, we have added the additional level and line information required 
-from \textsc{Topbase} \citep{topbase2005}.  He~\textsc{II} is treated
-in much the same way as H, but with 10 levels. He~\textsc{I} has
+He, we have added the additional level and line information required 
+from \textsc{Topbase} \citep{topbase2005}.  He~\textsc{ii} is treated
+in much the same way as H, but with 10 levels. He~\textsc{i} has
 larger energy differentials between different l-subshells and triplet
@@
 \caption{
-{\sl Top Panel:} ``Case B'' Balmer decrements computed 
+{\sl Top Panel:} `Case B' Balmer decrements computed 
 with \textsc{Python} compared to analytic calculations
@@
 (see Osterbrock 1989 for a discussion of this commonly used approximation).
-{\sl Bottom Panel:}  a comparison of Helium I level populations (the most complex ion we currently 
+{\sl Bottom Panel:}  a comparison of He I level populations (the most complex ion we currently 
 treat as a macro-atom) between \py\ and \tar models. 
@@
 \end{equation}
-Here, $\phi(r_0)$ is the local mass-loss rate per unit area at $r_0$, in the direction 
-of a streamline (as defined by SV93). 
-$v_z$ is the vertical velocity component. We take $\phi(r_0)$ to be
-uniform across the wind-launching area of the disk and normalize it by
-matching its integral to the user-specified total mass-loss rate,
-$\dot{M}_{wind}$. 
+Here, 
+$v_z$ is the vertical velocity component and $\phi(r_0)$ 
+is the local mass-loss rate per unit area at $r_0$, 
+%in the direction of a streamline (as defined by SV93), 
+such that 
+\begin{equation}
+\phi(r_0) \propto \dot{M}_{wind} R_0^\lambda \cos [\theta(r_0)].
+\label{density}
+\end{equation}
+We adopt $\lambda = 0$ and normalize $\phi(r_0)$ by 
+matching its integral over both sides of the disk
+to the user-specified total mass-loss rate, $\dot{M}_{wind}$. 
 % {\bf CK: I'm still not sure I understand the formula
@@
 
-\py\ has has some flexibility when treating the accretion 
+\py\ has some flexibility when treating the accretion 
 disk as a source of photons. The disk is broken down into annuli 
@@
 The WD at the center of the disk is always present as a spherical occulting
-body with radius $R_{WD}$ in \py CV models, but it can also be included
+body with radius $R_{WD}$ in \py\ CV models, but it can also be included
 as a source of radiation. In the models presented here, we treat the
@@
 % disk used in the ionization calculation (black solid line).
-% The positions of the Hydrogen and Helium ionization edges 
+% The positions of the H and He ionization edges 
 % are marked with vertical lines.
@@
 As the wind accelerates it becomes less dense
-and more highly ionized. The dominant Helium ion
+and more highly ionized. The dominant He ion
 is almost always He III, apart from in a small
@@
 
-\noindent where $\rm{n_H}$ is the local hydrogen number density and $\nu$ denotes photon 
+\noindent where $\rm{n_H}$ is the local number density of H and $\nu$ denotes photon 
 frequency. The ionization parameter is a useful measure of the ionization state of a plasma, 
 as it evaluates the ratio of the number density of ionizing photons and the local 
-Hydrogen density.
+H density.
 
@@
 
-The ionization equation used in the ``simple atom'' approach used by
+The ionization equation used in the `simple atom' approach used by
 LK02 (see section~\ref{simpleatoms}) should be a reasonable approximation to
@@
 found by LK02. The bottom panels in Fig.~\ref{wind} confirm that this
-is the case. In particular, Helium is fully ionized
+is the case. In particular, He is fully ionized
 throughout most of the outflow, except for a small region near the
@@
 hot inner disk. In line with the results of LK02, we also find
-that C\textsc{iv} is the dominant Carbon ion throughout the wind,
+that C\textsc{iv} is the dominant C ion throughout the wind,
 resulting in a substantial absorbing column across a large range of
@@
 
-Specifically, we aim to assess a whether a revised model can:
+Specifically, we aim to assess whether a revised model can:
 
@@
 the UV behaviour;
-         \item produce single-peaked Balmer emission lines (MC96); 
+         \item produce single-peaked Balmer emission lines; 
          \item generate enough of a wind-formed recombination continuum
@@
 However, this behaviour may be moderated by the effect of the increasing
-optical depth through this region, which will also affect the line profile shapes. 
+optical depth through this region, which can also affect the line profile shapes. 
+In addition, modifyin $R_v$ in particular also tends to increase the emission volume.
 Having briefly explored a variety of models with different kinematics,
-we adopt the parameters listed in table~\ref{modelb_table}(model B) for our revised model,
-which is optimized for the optical waveband.
+we adopt the parameters listed in table~\ref{modelb_table}
+for our revised model (model B), which is optimized for the optical waveband.
 
@@
 The inset plots show zoomed-in line profiles for 
-\heiiuv\ and \ha. The Balmer and Helium
+\heiiuv\ and \ha. The Balmer and He
 are double-peaked, albeit with narrower profiles.
@@
 
-Fig.~\ref{uvoptb} shows the predicted UV and optical spectra for this
+Fig.~\ref{uvoptb} shows the UV and optical spectra for this
 optically optimized model for the full range of inclinations. 
@@
 becomes quite prominent in our densest models. Second, our model predicts a detectable
-He~\textsc{ii} recombination line at 3202\AA. This is the Helium
+He~\textsc{ii} recombination line at 3202\AA. This is the He
 equivalent of Paschen~$\beta$ and should be expected in all systems that
-feature a strong He~\textsc{ii}~$\lambda4686$ line (the Helium
+feature a strong He~\textsc{ii}~$\lambda4686$ line (the He
 equivalent of Paschen~$\alpha$). 
@@
 has an ionization parameter of $\log U \sim 2$ (see Fig.~\ref{wind}).
-This means Hydrogen and Helium are fully ionized throughout 
-much of the wind and is successful in producing recombination features.
-However, the line opacity throughout the wind it too
+This means H and He are fully ionized throughout 
+much of the wind and are successful in producing recombination features.
+However, the line opacity throughout the wind is too
 low to produce noticeable blue shifted absorption. 
@@
 and ionizing radiation field over larger scales.
-Tentative evidence for clumping comes from the fact that \cite{prinja2000}
+Theory of line-driven winds expects them to be unsteady (REFs)
+and modelling of CV winds also predicts density inhomogeneities (REF).
+Tentative evidence for clumping being directly related to P-Cygni optical lines
+comes from the fact that \cite{prinja2000}
 found dwarf nova BZ Cam's outflow to be unsteady and highly mass-loaded in outburst,
@@
 This system has exhibited P-Cygni profiles in He~\textsc{i}~$\lambda5876$
-and \ha\ when in a high-state \cite{patterson1996,RN98}. 
+and \ha\ when in a high-state \citep{patterson1996,RN98}. 
 We also note that the degree of ionization and density variation and 
@@
 or by bound-free processes. This is demonstrated by the flatter spectral shape
-and the slight Helium photoabsorption edge present in the optical spectrum 
+and the slight He photoabsorption edge present in the optical spectrum 
 (marked in Fig.~\ref{continuumb}). This reprocessing is also
@@
 caused by residual line blanketing in the stellar atmospheres, which
-our models cannot fill in since they employ a 20-level Hydrogen atom.}
+our models cannot fill in since they employ a 20-level H atom.}
 This suggests that Balmer continuum emission from a wind can be important 
@@
 \begin{figure} %fullpage
-\includegraphics[width=0.9\textwidth]{figures/fig13_eclipse.eps}
+\includegraphics[width=0.9\textwidth]{figures/fig13.eps}
 \caption{{\sl Top Panel:} In and out of eclipse spectra of the high
@@
 an inclination of $80^\circ$. The main prediction is that dense, slowly accelerating 
-wind models produce narrower emission lines. This is {\em not} due to the radial 
-velocity shear mechanism proposed by MC96. That mechanism can only work if poloidal 
+wind models produce narrower emission lines. This is {\em not} due to radial 
+velocity shear. As stated by MC96, that mechanism can only work if poloidal 
 and rotational velocity gradients satisfy $(dv_l/dr)/(dv_\phi/dr) \gtrsim 1$; in 
@@
 by our denser wind models can be traced to the base of the outflow becoming optically 
-thick to line photons. In such models, the `line photosphere'
+thick in the continuum, such that the line emission from the base of the wind
+cannot escape to the observer. In such models, the `line photosphere'
 (the $\tau \simeq 1$ surface of the line-forming region) moves outwards, towards larger 
 vertical and cylindrical distances. This reduces the predicted line widths, since the 
-rotational velocities -- which normally provide the main line broadening mechanism at 
-high inclination -- drop off as $1/r$. This is not to say that the MC96 
+rotational velocities - which normally provide the main line broadening mechanism at 
+high inclination - drop off as $1/r$. This is not to say that the MC96 
 mechanism could not be at work in CV winds. For example, it would be worth investigating
 alternative prescriptions for the wind velocity field, as well as the possibility that the 
-outflows may be clumped. However, such an investigation is beyond the scope of the present paper.
+outflows may be clumped. A nonhomogenous flow 
+(which has been predicted in CVs; see section 5.2)
+might allow large radial velocity shears to exist while still 
+maintaining the high densities needed to produce the required level of emission.
+However, such an investigation is beyond the scope of the present paper.
 
@@
 implying a significant vertical extent for the line-forming 
-region. This type of model should therefore not be ruled out {\em a priori}.
+region. This type of model should therefore not be ruled out {\em a priori}, 
+but this specific model was not adopted as our optically optimized model
+due to an unrealistically high continuum level in eclipse.
 
@@
 which suggests that the overall ionization state of the model is
-somewhat too high. 
-As discussed in section 5.3, the optical lines are
-narrow, but double-peaked. 
-This is in contrast to what is generally seen in observations
+somewhat too high. As discussed in section 5.3, the optical lines are
+narrow, but double-peaked. This is in contrast to what is generally seen in observations
 of NLs, although the relatively low resolution of the RW Tri
-spectrum makes a specific comparison difficult.
+spectrum makes a specific comparison difficult. In order to demonstrate
+the double-peaked nature of the narrower lines, we choose not to 
+smooth the synthesized data to the resolution of the RW Tri dataset.
 
@@
           the accretion, thus accounting for the absence of a strong edge in
-          observed CV spectra \citep{KLWB98};
+          observed CV spectra;
 	\item produce the optical lines observed in CVs.
@@
 
-We can also make a couple of basic,
+It is not yet clear whether a wind model such as this can
+explain all of the observed optical features of high-state CVs-
+further effort is required both from the observational
+and modelling perspectives.
+However, we can make a couple of basic,
 testable predictions about the Balmer continuum emission
-from a simialr wind geometry:
+from similar wind geometries:
 \begin{itemize}
@@
 
-% {\bf CK: I just realized that -- apart from the intro -- we never
-% actually discuss the issue of P Cyg profiles in the optical
-% lines. These have been observed -- e.g. in Halpha -- but I guess we
-% never produce these? Do we know why? We probably should at least
-% comment on this at some point in the text, and possibly even briefly
-% in the conclusions.}
-
-%% Balmer jump
-
-% {\bf
-% \noindent Notes on Section 7:
-
-% \begin{itemize}
-% 	\item
-
-% \noindent Potential Additional Figures:
-
-% \begin{itemize}
-% 	\item 	
-% }
-
-% \subsection{Future Work}
-
-% To further investigate the true effect of the wind
-% we hope that high quality, broadband spectra of 
-% Nova-like variables at a range of inclinations 
-% will be taken to examine
-
-% In addition to this project, we have started to apply the macro atom scheme to QSOs in order to build on the work of Higginbottom et al.
-(2013).
-In particular, we hope that the macro-atom scheme will enable the
-% model to produce significant Lyman-$\alpha$ emission, as is observed in QSOs.
-
 \subsection*{Acknowledgements}
 The work of JHM and CK is supported by the Science and Technology Facilities Council (STFC), 
-via studentships and a consolidated grant, respectively. We would like to thank Juan Hernandez Santisteban, Samuel Mangham and Ivan Hubeny for useful discussions. 
-We acknowledge the use of the IRIDIS High Performance Computing Facility, 
+via studentships and a consolidated grant, respectively. The work of NSH is supported by NASA under Astrophysics Theory Program grants NNX11AI96G  and NNX14AK44G.
+We are very grateful to A.F. Palah and B.T. Gaensicke for the IX Vel XSHOOTER dataset.
+We would also like to thank J.V. Hernandez Santisteban, S.W. Mangham and I. Hubeny for useful discussions. We acknowledge the use of the IRIDIS High Performance Computing Facility, 
 and associated support services at the University of Southampton, in the completion of this work.

### 2015-01-22 draft.tex
approaching final draft

@@
 The single-peaked line profile is due to the line emission originating from 
-$\sim10^11$~cm above the disk plane where rotational velocities are small, 
+$\sim10^{11}$~cm above the disk plane where rotational velocities are small, 
 and is not due to the radial velocity shear mechanism that
@@
 winds \citep{sim2004}, AGN disk winds \citep{simlong2008, tatum2012},
-supernovae \citep{kromersim, kerzendorfsim} and YSOs (SDL05). A full 
+supernovae \citep{kromersim2009, kerzendorfsim} and YSOs (SDL05). A full 
 description of the approach can be found in L02 and L03.
@@
 ionization directly to excited levels of the upper ion. The
-Van Regemorter (1962) approximation is used for collisional
+\cite{vanregemorter} approximation is used for collisional
 transitions, and thus we assume that collisions between radiatively
@@
 Here, 
-$v_z$ is the vertical velocity component and $\phi(r_0)$ 
-is the local mass-loss rate per unit area at $r_0$, 
-%in the direction of a streamline (as defined by SV93), 
+$v_z$ is the vertical velocity component and, following SV93,
+$\phi(r_0)$ is the local mass-loss rate per unit area at $r_0$, 
 such that 
 \begin{equation}
-\phi(r_0) \propto \dot{M}_{wind} R_0^\lambda \cos [\theta(r_0)].
+\phi(r_0) \propto \dot{M}_{wind} r_0^\lambda \cos [\theta(r_0)].
 \label{density}
@@
 optical depth through this region, which can also affect the line profile shapes. 
-In addition, modifyin $R_v$ in particular also tends to increase the emission volume.
+In addition, modifying $R_v$ also increases the emission {\em volume}.
 Having briefly explored a variety of models with different kinematics,
@@
 equivalent of Paschen~$\alpha$). 
-%%Although it has been observed (REF),
 This line is somewhat unfamiliar observationally, because it 
@@
 also redwards of most ultraviolet spectra.
-% {\bf JM: we should we reference something here for the 3202 line. 
-% I blieve CK found a paper which shows it in an IP? I'll try and find it.}
 
@@
 and ionizing radiation field over larger scales.
-Theory of line-driven winds expects them to be unsteady (REFs)
-and modelling of CV winds also predicts density inhomogeneities (REF).
+Theory of line-driven winds expects them to be unsteady \citep{macgregor1979,owockirybicki1984,owockirybicki1985},
+simulations of CV disk winds also predict density inhomogeneities 
+\citep{proga1998,pkdh2002}.
 Tentative evidence for clumping being directly related to P-Cygni optical lines
@@
 \caption{
-\ha\ line profiles, normalised to 1, plotted in velocity space 
+\ha\ line profiles, normalized to 1, plotted in velocity space 
 for three models with varying kinematic 

### 2015-01-23 draft.tex
Nearly there

@@
 \usepackage{amssymb}
-%\usepackage{aastex}
-%\usepackage{epsfig}
-%\usepackage[dvips]{color}
-%\usepackage{aabib}
-
-%\marginparwidth = 25pt
+
 \citestyle{aa}
@@
 imply the existence of powerful accretion disk winds in
-CVs.
-% and considerable effort has gone into modelling UV line formation
-% in such outflows. By contrast, much less attention has been paid to
-% the potential impact of these disk winds on the {\em optical} spectra
-% of CVs. 
-Here, we use an improved version of our Monte Carlo ionization
+CVs. Here, we use an improved version of our Monte Carlo ionization
 and radiative transfer code to investigate whether disk wind models that
@@
 producing all the observed lines. This model
-produces recombination continuum sufficient to fill in the Balmer jump,
-but it also predicts stronger-than-observed 
-collisionally excited UV emission lines. 
+produces a recombination continuum that is strong enough to fill in the Balmer jump,
+but it also predicts stronger-than-observed collisionally excited UV emission lines. 
 The wind in our revised model also alters the spectral shape of the continuum, 
@@
 narrowing of the double-peaked emission lines from the base of the wind.
-We show that denser models can produce a single-peaked \ha\ line.
-The single-peaked line profile is due to the line emission originating from 
+We show that even denser models can produce a single-peaked \ha\ line.
+In this model, the single-peaked line profile is due to the line emission originating from 
 $\sim10^{11}$~cm above the disk plane where rotational velocities are small, 
 and is not due to the radial velocity shear mechanism that
-has previously been proposed. 
-On the basis of our results, we suggest that winds can 
+has previously been proposed. On the basis of our results, we suggest that winds can 
 modify, and perhaps even dominate, the line and continuum emission
 from CVs.
-% We carry out a limited exploration of
-% the disk wind parameter space, focusing on those parameters that affect the
-% density near the base of the wind. This shows that higher-density
-% outflows can produce both single-peaked emission lines and a
-% recombination continuum sufficient to fill in the Balmer
-% jump, although such models also tend to predict stronger-than-observed 
-% collisionally excited UV emission lines. Our main conclusion is that
-% disk wind emission is likely to have a significant impact on the
-% optical spectra of high-state CVs. 
-% {\bf JM: This abstract is a few lines longer than I would like- 
-% I think something punchier is required.}
 \end{abstract}
@@
 are predicted to be double-peaked \citep{smak1981, hornemarsh1986}. 
-{\em Low-state} CVs (dwarf novae in quiescence) can, in fact,
+{\em Low-state} CVs (dwarf novae in quiescence) do, in fact,
 exhibit such double-peaked lines \citep{marshhorne1990}.
-% {\bf JM: I've included a reference to a paper on IP Peg here
-% which shows the transition from double peaked lines in 
-% quiescence and a contrast to outburst spectra. I'm not sure
-% of general trends in DNe. A lot seem to have weak emission cores
-% embedded in absorption.}\
 
@@
 \includegraphics[width=0.8\textwidth]{figures/fig1.eps}
-% \caption{Optical spectra of three nova-like variables: 
-% RW Sex (top; Beuermann et al. 1992),
-% IX Vel (top middle; Beuermann \& Thomas 1990) 
-% and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
-% The data have been digitized from the respective publications and a few of the more
-% prominent emission and absorption lines are marked. 
 \caption{
@@
 
-%% CITATIONS FROM CAPTION
 \nocite{groot2004}
@@
 
-The remainder of this paper is organized as follows. In Section~2 we
+The remainder of this paper is organized as follows. In Section~2, we
 briefly describe the code and and the newly implemented macro-atom
@@
 \py\ is designed to operate in a number of different
-regimes, both in terms of the scale of the system, and in terms of the
+regimes, both in terms of the scale of the system and in terms of the
 characteristics of the underlying radiation field.
@@
 is the line frequency, $dv/ds$ is the velocity gradient and
-$\tau_s$ is the Sobolev optical depth experienced by the photon in resonance.
+$\tau_s$ is the Sobolev optical depth.
 The sum is over all photons that come into resonance with the line.
@@
 atomic species can now be treated either in our simple-atom
-approximation or with the full macro-atom machinery. For our CV
+approximation or with the full macro-atom machinery. In our CV
 models, we treat H and He as macro-atoms and all metals as
@@
 correspond to fast acceleration close to the disk (see
-Fig.~\ref{acc_law}). The rotational velocity $v_\phi$ is originally 
-Keplerian and is assumed to conserve its specific angular momentum
+Fig.~\ref{acc_law}). The rotational velocity $v_\phi$ is 
+Keplerian at the base of the streamline 
+and we assume conservation of specific angular momentum,
 such that
@@
 $\phi(r_0)$ is the local mass-loss rate per unit area at $r_0$, 
-such that 
+defined as
 \begin{equation}
@@
 to the user-specified total mass-loss rate, $\dot{M}_{wind}$.
-% {\bf CK: I'm still not sure I understand the formula
-%   SV93 use to define $\phi$, and hence that this description is
-%   actually strictly correct.... Not sure what to do about that
-%   though...}
 
@@
 from either Kurucz \citep{kurucz1991} atmospheres (for $T_{eff} \leq
-50,000$~K) or from \textsc{TLUSTY} models \citep{tlusty} (for $T_{eff} > 50,000$~K).
+50,000$~K) or from \textsc{TLUSTY} \citep{tlusty} models (for $T_{eff} > 50,000$~K).
 
@@
 luminosity. In the models presented here, we have followed LK02 in setting
-the BL luminosity to zero. However, we have confirmed that the addition of a
+the BL luminosity to zero. However, we have confirmed that the addition of an isotropic
 BL with $L_{BL} = 0.5 L_{acc}$ and temperatures in the range $80~{\rm
@@
 purpose, we assume a circular orbit with a semi-major axis $a$ and 
-specify orbital phase such that $\Phi_{orb} = 0$ as the
+specify orbital phase such that $\Phi_{orb} = 0$ is the
 inferior conjunction of the secondary (i.e. mid-eclipse for $i \simeq
@@
 
-% \begin{figure}
-% \centering
-% \includegraphics[width=0.45\textwidth]{figures/sed_figure.eps}
-% \caption{
-% The spectral energy distribution (SED) of the 
-% White Dwarf (dashed line) and blackbody accretion
-% disk used in the ionization calculation (black solid line).
-% The positions of the H and He ionization edges 
-% are marked with vertical lines.
-% {\bf JM: KSL has suggested we ditch this}
-%  }
-% \label{sed}
-% \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
-%          RESULTS
+%          BENCHMARK MODEL
 %
@@
 \begin{tabular}{p{2cm}p{2cm}p{2cm}}
+%%\multicolumn{2}{|l|}{Model Parameters}  \\
 Model Parameters \\
@@
 $r_{max}$ 	&	 $12~R_{WD}$  &  \\ 
-$r_{disk} (max)$ 	&	 $34~R_{WD}$  &  \\ 
+$r_{disk}$(max) 	&	 $34.3~R_{WD}$  &  \\ 
 $\theta_{min}$ 	&	 $20.0^{\circ}$  &  \\ 
@@
 \caption{
-The physical properties of the wind- note the logarithmic scale. 
+The physical properties of the wind -- note the logarithmic scale. 
 Near the disk plane the wind is dense, with low poloidal velocities.
@@
 
-\noindent where $\rm{n_H}$ is the local number density of H and $\nu$ denotes photon 
+\noindent where $\rm{n_H}$ is the local number density of H, and $\nu$ denotes photon 
 frequency. The ionization parameter is a useful measure of the ionization state of a plasma, 
-as it evaluates the ratio of the number density of ionizing photons and the local 
+as it evaluates the ratio of the number density of ionizing photons to the local 
 H density.
@@
 and temperature with distance away from the disk, so any line
-formation process that scales as $\rho^2$ - i.e. recombination and
-collisionally excited emission - should be expected to operate
+formation process that scales as $\rho^2$ -- i.e. recombination and
+collisionally excited emission -- should be expected to operate
 primarily in the dense base of the outflow. Moreover, a comparison of
@@
 is met: all of the strong metal resonance
-lines - notably N\textsc{v}~$\lambda1240$,
-Si\textsc{iv}~$\lambda1400$ and C\textsc{iv}~$\lambda1550$ - 
+lines -- notably N\textsc{v}~$\lambda1240$,
+Si\textsc{iv}~$\lambda1400$ and C\textsc{iv}~$\lambda1550$ -- 
 are present and exhibit clear P-Cygni profiles
 at intermediate inclinations. In addition, however, we now also find
-that the wind produces significant Lyman-$\alpha$ and
+that the wind produces significant Ly$\alpha$ and
 He~\textsc{ii}~$\lambda1640$ emission lines.
@@
 in Fig.~1. However, it is clear that this particular model
-does not produce all the lines seen in observations of high-state CVs.
+does not produce all of the lines seen in observations of high-state CVs.
 The higher-order Balmer series lines are too weak
 to overcome the intrinsic absorption from the disk atmosphere, and the wind 
-fails to produce any observable emission at intermediate inclinations, 
-which contrasts with (for example) the observed behaviour of V3885 Sgr \citep{hartley2005}
+fails to produce any observable emission at low and intermediate inclinations.
+This contrasts with the fact that emission lines are seen 
+in the optical spectra of (for example) V3885 Sgr \citep{hartley2005}
 and IX Vel \citep[][see also Fig.~1]{beuermann1990}.
@@
 \includegraphics[width=0.45\textwidth]{figures/modela_escaping.eps}
-\caption{Total packet-binned spectra across all viewing angles. 
+\caption{Total packet-binned spectra across all viewing angles, in units
+of monochromatic luminosity.
 The thick black line shows the total 
@@
 The emission measure of a plasma is directly proportional to its density.
-The simplest way to simultaneously affect the density in the wind (for fixed mass loss rate)
-as well as the velocity gradients is by modifying the poloidal velocity
-law. To do this, we focus on just two kinematic variables (section~\ref{kinematics}):
+The simplest way to simultaneously affect the density in the wind (for fixed mass loss rate),
+as well as the velocity gradients, is by modifying the poloidal velocity
+law. Therefore, we focus on just two kinematic variables (section~\ref{kinematics}):
 
@@
 The general behaviour we might expect is that outflows with denser
-regions near the wind base - i.e. winds with larger $R_{v}$ and/or
-larger $\alpha$ - will produce stronger optical emission signatures. 
+regions near the wind base -- i.e. winds with larger $R_{v}$ and/or
+larger $\alpha$ -- will produce stronger optical emission signatures. 
 However, this behaviour may be moderated by the effect of the increasing
@@
 In addition, modifying $R_v$ also increases the emission {\em volume}.
-Having briefly explored a variety of models with different kinematics,
+Based on a preliminary exploration of models with different kinematics,
 we adopt the parameters listed in table~\ref{modelb_table}
-for our revised model (model B), which is optimized for the optical waveband.
+for our `optically optimized' model (model B).
 
@@
 
-Fig.~\ref{uvoptb} shows the UV and optical spectra for this
+Fig.~\ref{uvoptb} shows the UV and optical spectra for the
 optically optimized model for the full range of inclinations. 
 As expected, the trend from absorption to emission 
-in the optical is again present, but in this improved model we produce emission
+in the optical is again present, but in this revised model we produce emission
 lines in the entire Balmer series at high inclinations, as well as the observed lines 
 in He~\textsc{ii} and He~\textsc{i}. This can be seen more clearly in the 
-continuum-divided spectrum in Fig.~\ref{continuumb}.
-%with the lines marked (NOTE, mark these).
+continuum-normalized spectrum in Fig.~\ref{continuumb}.
 
 Two other features are worth noting in the optical
-spectrum. First, the collisionally excited Ca~{\sc ii} emission line at 3934\AA\ 
+spectrum. First, the collisionally excited Ca~{\sc ii} emission line at 3934~\AA\ 
 becomes quite prominent in our densest models. Second, our model predicts a detectable
-He~\textsc{ii} recombination line at 3202\AA. This is the He
+He~\textsc{ii} recombination line at 3202~\AA. This is the He
 equivalent of Paschen~$\beta$ and should be expected in all systems that
@@
 low to produce noticeable blue shifted absorption. 
-We suspect that the winds that exhibit such profiles must 
+We suspect that the systems that exhibit such profiles must 
 possess a higher degree of ionization stratification, although the lack 
@@
 P-Cygni profiles in UV resonance lines and optical H and He lines exist simultaneously.
-Ionization stratification could manifest as a clumpy flow, in which ionization changes
-due to small scale density fluctuations, or a stratification in density
+Ionization stratification could be caused by a clumpy flow, in which the ionization state 
+changes due to small scale density fluctuations, or a stratification in density
 and ionizing radiation field over larger scales.
-Theory of line-driven winds expects them to be unsteady \citep{macgregor1979,owockirybicki1984,owockirybicki1985},
-simulations of CV disk winds also predict density inhomogeneities 
+Invoking clumpiness in these outflows is not an unreasonable
+hypothesis. Theories of line-driven winds predict an unstable flow
+\citep{macgregor1979,owockirybicki1984,owockirybicki1985}, and
+simulations of CV disk winds also produce density inhomogeneities 
 \citep{proga1998,pkdh2002}.
@@
 comes from the fact that \cite{prinja2000}
-found dwarf nova BZ Cam's outflow to be unsteady and highly mass-loaded in outburst,
-by observing the UV resonance lines.
-This system has exhibited P-Cygni profiles in He~\textsc{i}~$\lambda5876$
+found the dwarf nova BZ Cam's outflow to be unsteady and highly mass-loaded in outburst,
+based on observations of the UV resonance lines.
+This system has also exhibited P-Cygni profiles in He~\textsc{i}~$\lambda5876$
 and \ha\ when in a high-state \citep{patterson1996,RN98}. 
-We also note that the degree of ionization and density variation and 
+The degree of ionization and density variation and 
 subsequent line opacities may be affected by our model parameters
-and the specific parameterisation adopted.
+and the specific parameterisation we have adopted.
 
@@
 The wind now also has a clear effect on the continuum shape,
-as shown by Fig.~\ref{modelb_escape}. The majority of the
+as shown by Fig.~\ref{modelb_escape}. In fact, the majority of the
 escaping spectrum has been reprocessed in some way by the wind,
-either by electron scattering (the wind is now moderately Thompson-thick),
+either by electron scattering (the wind is now moderately Thomson-thick),
 or by bound-free processes. This is demonstrated by the flatter spectral shape
@@
 our models cannot fill in since they employ a 20-level H atom.}
-This suggests that Balmer continuum emission from a wind can be important 
+This might suggest that Balmer continuum emission from a wind can be important 
 in shaping the Balmer jump region, as
@@
 Although we include a simple limb darkening law which affects 
-the seen at each inclination, we do not
+the emergent flux at each inclination, we do not
 include it as a {\em frequency dependent} opacity in our model.
@@
 in emission at high inclinations.
-To understand this phenomenon, a fully self-consistent
+In any case, to properly understand this phenomenon, a fully self-consistent
 radiative transfer calculation of both the disk atmosphere
@@
 \includegraphics[width=0.45\textwidth]{figures/modelb_escaping.eps}
-\caption{Total packet-binned spectra across all viewing angles. 
+\caption{Total packet-binned spectra across all viewing angles, in units
+of monochromatic luminosity. 
 The thick black line shows the total 
@@
 vertical and cylindrical distances. This reduces the predicted line widths, since the 
-rotational velocities - which normally provide the main line broadening mechanism at 
-high inclination - drop off as $1/r$. This is not to say that the MC96 
+rotational velocities -- which normally provide the main line broadening mechanism at 
+high inclination -- drop off as $1/r$. This is not to say that the MC96 
 mechanism could not be at work in CV winds. For example, it would be worth investigating
 alternative prescriptions for the wind velocity field, as well as the possibility that the 
-outflows may be clumped. A nonhomogenous flow 
+outflows may be clumped. An inhomogeneous flow 
 (which has been predicted in CVs; see section 5.2)
@@
 but this specific model was not adopted as our optically optimized model
-due to an unrealistically high continuum level in eclipse.
+due to its unrealistically high continuum level in eclipse.
 
@@
 
-Fig.~\ref{rwtricomp} shows a qualitative comparison of the predicted
+Fig.~\ref{rwtricomp} shows a comparison of the predicted
 out-of-eclipse and mid-eclipse spectra against observations of the
@@
 adopt $i = 80^\circ$, but our qualitative conclusions are not
-particularly sensitive to this choice. We emphasize that this
-model is in no sense a fit to this - or any other - data set.
-
-% {\bf CK: strictly speaking, we should be talking about q=M2/M1 and disk
-%   radius here as well I think, since those parameters affect the
-%   amount and nature of any uneclipsed light just as much (sort of) as
-%   the inclination. We should probably quote M2, q and R2/a in the
-%   table, and we may want to say that we've adopted a q that is in line
-%   with the observed eclipse width of RW Tri. (In Roche geometry,the
-%   eclipse width -- the half-width at half out-of-eclipse intensity,
-%   say -- depends solely on q and i). See e.g. Horne's paper or various
-%   Dhillon et al. papers.}
+particularly sensitive to this choice. 
+We follow LK02 is setting the value of $r_{disk}$ (the maximum radius of the accretion disk)
+to $34.3~R_{WD}$. When compared to the semi-major axis of RW Tri,
+this value is perhaps lower than one might 
+typically expect for NLs \citep{harropallinwarner1996}. 
+However, it is consistent
+with values inferred by \cite{rutten1992}.
+We emphasize that this model is in no sense a fit to this -- or any other -- data set.
 
@@
 has also been seen in other NLs, including members of the SW~Sex class
-\citep{neustroev2011}.
-% {\bf CK: I'm pretty sure that we know this about UX Uma, e.g. from
-%   eclipse mapping studies, and there ought to be mid-eclipse spectra
-%   of some additional system}
-% The revised model also produes a single-peaked \ha\ line, in line with
-% the observational data.
+\citep{neustroev2011}. As noted in section 5.2, the majority
+of the escaping radiation has been reprocessed by the wind in some way
+(particularly the eclipsed light).
 
@@
 smooth the synthesized data to the resolution of the RW Tri dataset.
-
-\newpage
+If the data was smoothed, the \ha\ line would appear single-peaked.
 
@@
 %
-%          Conclusions and Future Work
+%          CONCLUSIONS
 %
@@
 stronger-than-observed He~{\sc ii} lines in the optical region and too
-much of a collisionally excited contribution to the UV resonance lines
-that
-
-Based on this, we show that recombination emission 
-from outflows with sufficiently high densities and/or optical depths might
-
-\renewcommand{\labelitemi}{$\bullet$}
-\begin{itemize}
-	\item fill in the Balmer absorption edge in the spectrum of
-          the accretion, thus accounting for the absence of a strong edge in
-          observed CV spectra;
-	\item produce the optical lines observed in CVs.
-\end{itemize}
-\smallskip
-
-We note that limb darkening effects on disk atmosphere opacities
-would affect the Balmer jump (see section 5.2). In section 5.3, we demonstrate that
+much of a collisionally excited contribution to the UV resonance lines.
+
+Based on this, we argue that recombination emission 
+from outflows with sufficiently high densities and/or optical depths 
+might produce the optical lines observed in CVs, and may also 
+fill in the Balmer absorption edge in the spectrum of the accretion disk, 
+thus accounting for the absence of a strong edge in observed CV spectra.
+In section 5.3, we demonstrate that
 although the double peaked lines narrow and 
 single-peaked emission can be formed in our densest models, 
-it is not due to the radial velocity shear mechanism proposed by MC96.
-We suggest that nonhomogenous, `clumpy' line-driven winds or a different
-wind parameterization may allow this mechanism to work.
+this is not due to the radial velocity shear mechanism proposed by MC96.
+We suggest that `clumpy' line-driven winds or a different
+wind parameterization may nevertheless allow this mechanism to work.
 We also note the possibility that, as in our denser models, 
-the single-peaked lines are formed well above the disk where 
+the single-peaked lines are formed well above the disk, where 
 rotational velocities are lower.
 
-% {\bf JM: I originally also had a note about the flat Balmer decrement here.
-% it's potentially interesting and could be included, but would need a discussion
-% earlier in the text.}
-
 It is not yet clear whether a wind model such as this can
-explain all of the observed optical features of high-state CVs-
-further effort is required both from the observational
-and modelling perspectives.
-However, we can make a couple of basic,
-testable predictions about the Balmer continuum emission
-from similar wind geometries:
-\begin{itemize}
-	\item we expect the depth of the Balmer absorption edge in CV
-          spectra to decrease with increasing inclination (with the
-          Balmer jump possibly switching to emission at the highest
-          inclinations, if the flux in the wind-formed recombination
-          continuum exceeds that of the foreshortened disk spectrum);
-	% \item we predict that a strong He~\textsc{ii}~$\lambda3202{\rm
- %          \AA}$ line should be prominent in all cases where
- %          He~\textsc{ii}~$\lambda1640{\rm \AA}$ \& \heiiopt\ are seen
- %          (but note that this prediction is not restricted to lines
- %          formed in disk winds);
-	\item we predict that the Balmer jump should be in emission
-          during mid-eclipse in high inclination systems.
-\end{itemize}
-
-\smallskip
-
-Overall, our work demonstrates that {\sl disk winds matter}. They are
+explain all of the observed optical features of high-state CVs --
+further effort is required on both the observational
+and modelling fronts.
+However, our work demonstrates that {\sl disk winds matter}. They are
 not just responsible for creating the blue-shifted absorption and
@@
 systems. In fact, most of the optical features characteristic of CVs
-are likely to be affected - and possibly even dominated - by their disk
+are likely to be affected -- and possibly even dominated -- by their disk
 winds. Given that optical spectroscopy plays the central role in

### 2015-01-26 scripts/mnras.py
correct keywords, affils, abstract wc as requested by mnras

@@ -10,7 +10,7 @@ texfile =  open(filename, "r")
 outfile = open(outfilename, "w")
 
 
-outfile.write("\documentclass[useAMS,usenatbib]{mn2e}\n")
+outfile.write("\documentclass[useAMS,usenatbib]{mn2e_x}\n")
 
 fig_env = False
 

### 2015-03-24 old.tex
starting to address referee comments

--- 2015-01-23 draft.tex
@@
 \title{The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables}
-\author{J. H. Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}
+
+\author[Matthews et al.]{J.~H.~Matthews,$^1$ C.~Knigge,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and N.~Higginbottom$^4$
+\medskip  
+\\$^1$School of Physics and Astronomy, University of Southampton, Highfield, Southampton, SO17 1BJ, UK
+\\$^2$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
+\\$^3$School of Mathematics and Physics, Queens University Belfast, University Road, Belfast, BT7 1NN, Northern Ireland, UK
+\\$^4$Department of Astronomy, University of Las Vegas, Las Vegas, NV 89119, USA}
+
+%%\author{J. H. Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}
 
@@
 \begin{abstract}
+% Many high-state non-magnetic cataclysmic variables (CVs) exhibit
+% blue-shifted absorption or P-Cygni profiles associated with ultraviolet
+% (UV) resonance lines, such as C~{\sc iv}~$\lambda1550$. These features
+% imply the existence of powerful accretion disk winds in
+% CVs. Here, we use an improved version of our Monte Carlo ionization
+% and radiative transfer code to investigate whether disk wind models that
+% produce realistic UV line profiles are also likely to generate
+% observationally significant recombination line and continuum emission
+% in the {\em optical} waveband. 
+% We also test whether outflows may be responsible for the single-peaked 
+% emission line profiles often seen
+% in high-state CVs and for the weakness of the Balmer absorption edge
+% (relative to simple models of optically thick accretion disks).
+% We find that a standard disk wind model that is successful in
+% reproducing the UV spectra of CVs also leaves a noticeable imprint on
+% the optical spectrum, particularly for systems viewed at high
+% inclination. The strongest optical wind-formed recombination lines are \ha\ and
+% \heiiopt, although the outflow also produces emission in the Ly$\alpha$
+% and \heiiuv\ UV lines. However, all of the optical lines produced by
+% this default wind model are double-peaked, and the effect of the wind
+% on the Balmer jump is modest. We demonstrate that a higher-density outflow model 
+% displays reasonable verisimilitude with the optical spectrum of RW Trianguli,
+% producing all the observed lines. This model
+% produces a recombination continuum that is strong enough to fill in the Balmer jump,
+% but it also predicts stronger-than-observed collisionally excited UV emission lines. 
+% The wind in our revised model also alters the spectral shape of the continuum, 
+% and displays a strong inclination dependence in its emission properties. 
+% No single-peaked emission is seen, although we observe a 
+% narrowing of the double-peaked emission lines from the base of the wind.
+% We show that even denser models can produce a single-peaked \ha\ line.
+% In this model, the single-peaked line profile is due to the line emission originating from 
+% $\sim10^{11}$~cm above the disk plane where rotational velocities are small, 
+% and is not due to the radial velocity shear mechanism that
+% has previously been proposed. On the basis of our results, we suggest that winds can 
+% modify, and perhaps even dominate, the line and continuum emission
+% from CVs.
 Many high-state non-magnetic cataclysmic variables (CVs) exhibit
 blue-shifted absorption or P-Cygni profiles associated with ultraviolet
-(UV) resonance lines, such as C~{\sc iv}~$\lambda1550$. These features
-imply the existence of powerful accretion disk winds in
-CVs. Here, we use an improved version of our Monte Carlo ionization
+(UV) resonance lines. These features imply the existence of 
+powerful accretion disk winds in CVs. Here, we use our Monte Carlo ionization
 and radiative transfer code to investigate whether disk wind models that
@@
 observationally significant recombination line and continuum emission
-in the {\em optical} waveband. 
+in the {\em optical} waveband. We also test whether outflows may be responsible for 
+the single-peaked emission line profiles often seen in high-state CVs and for the weakness
+of the Balmer absorption edge (relative to simple models of optically thick accretion disks).
 We find that a standard disk wind model that is successful in
@@
 inclination. The strongest optical wind-formed recombination lines are \ha\ and
-\heiiopt, although the outflow also produces emission in the Ly$\alpha$
-and \heiiuv\ UV lines. However, all of the optical lines produced by
-this default wind model are double-peaked, and the effect of the wind
-on the Balmer jump is modest. We demonstrate that a higher-density outflow model 
-displays reasonable verisimilitude with the optical spectrum of RW Trianguli,
-producing all the observed lines. This model
-produces a recombination continuum that is strong enough to fill in the Balmer jump,
-but it also predicts stronger-than-observed collisionally excited UV emission lines. 
-The wind in our revised model also alters the spectral shape of the continuum, 
-and displays a strong inclination dependence in its emission properties. 
-No single-peaked emission is seen, although we observe a 
+\heiiopt. We demonstrate that a higher-density outflow model produces 
+all the expected H and He lines and produces a recombination continuum that can 
+fill in the Balmer jump at high inclinations.
+This model displays reasonable verisimilitude with the optical spectrum of RW Trianguli. No single-peaked emission is seen, although we observe a 
 narrowing of the double-peaked emission lines from the base of the wind.
-We show that even denser models can produce a single-peaked \ha\ line.
-In this model, the single-peaked line profile is due to the line emission originating from 
-$\sim10^{11}$~cm above the disk plane where rotational velocities are small, 
-and is not due to the radial velocity shear mechanism that
-has previously been proposed. On the basis of our results, we suggest that winds can 
+Finally, we show that even denser models can produce a single-peaked \ha\ line.
+On the basis of our results, we suggest that winds can 
 modify, and perhaps even dominate, the line and continuum emission
@@
 
+\begin{keywords}
+{\sl (stars:)} novae, cataclysmic variables - accretion, accretion discs - stars: winds, outflows - line: profiles - radiative transfer - methods: numerical 
+\end{keywords}
+
 \maketitle
@@
 \label{sec:intro}
+
+\begin{figure}	%fullpage
+\centering
+\includegraphics[width=0.7\textwidth]{figures/fig1.eps}
+\caption{
+Optical spectra of three nova-like variables: 
+RW Sex (top; Beuermann et al. 1992),
+IX Vel (top middle; A. F. Pala \& B. T. Gaensicke, private communication) 
+and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
+The data for RW Sex and RW Tri were digitized from the respective publications,
+and the IX Vel spectrum was obtained using the XSHOOTER spectrograph 
+on the Very Large Telescope on 2014 October 10.
+These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $75^\circ$ 
+(see section 5.4) respectively. 
+The trend of increasing Balmer line emission with inclination can be seen.
+In RW Tri strong single-peaked emission in the Balmer lines is seen even
+in eclipse, indicating that the lines may be formed in a spatially
+extensive disk wind, and there is even a suggestion 
+of a (potentially wind-formed) recombination continuum in the eclipsed
+spectrum. We have attempted to show each spectrum over a similar dynamic range.
+}
+\label{novalikes}
+\end{figure}
 
@@
 exhibit such double-peaked lines \citep{marshhorne1990}.
-
-\begin{figure}	%fullpage
-\centering
-\includegraphics[width=0.8\textwidth]{figures/fig1.eps}
-\caption{
-Optical spectra of three nova-like variables: 
-RW Sex (top; Beuermann et al. 1992),
-IX Vel (top middle; A. F. Pala \& B. T. Gaensicke, private communication) 
-and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
-The data for RW Sex and RW Tri were digitized from the respective publications,
-and the IX Vel spectrum was obtained using the XSHOOTER spectrograph 
-on the Very Large Telescope on 2014 October 10.
-These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $75^\circ$ 
-(see section 5.4) respectively. 
-The trend of increasing Balmer line emission with inclination can be seen.
-In RW Tri strong single-peaked emission in the Balmer lines is seen even
-in eclipse, indicating that the lines may be formed in a spatially
-extensive disk wind, and there is even a suggestion 
-of a (potentially wind-formed) recombination continuum in the eclipsed
-spectrum. We have attempted to show each spectrum over a similar dynamic range.
-}
-\label{novalikes}
-\end{figure}
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/fig2_cartoon.eps}
+\includegraphics[width=0.45\textwidth]{figures/fig2_cartoon.eps}
 \caption{Cartoon illustrating the geometry and kinematics of the benchmark CV wind model.}
@@
 \begin{tabular}{p{2cm}p{2cm}p{2cm}}
-%%\multicolumn{2}{|l|}{Model Parameters}  \\
-Model Parameters \\
+\multicolumn{2}{|l|}{Model Parameters}  \\
+%%Model Parameters \\
 \hline Parameter 	&	 Model A  & Model B \\ 
@@
 \begin{figure} %fullpage
-\includegraphics[width=\textwidth]{figures/fig5.eps}
+\includegraphics[width=0.9\textwidth]{figures/fig5.eps}
 \caption{
@@
 
-\subsection{Synthetic Spectra}
-\label{modela_spectrum}
-
 \begin{figure} %fullpage
@@
 \end{figure} %fullpage\
+
+\subsection{Synthetic Spectra}
+\label{modela_spectrum}
 

### 2015-03-25 draft.tex
actual submit
working on response

@@
 
-\begin{figure}	%fullpage
-\centering
-\includegraphics[width=0.8\textwidth]{figures/fig1.eps}
-\caption{
-Optical spectra of three nova-like variables: 
-RW Sex (top; Beuermann et al. 1992),
-IX Vel (top middle; A. F. Pala \& B. T. Gaensicke, private communication) 
-and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
-The data for RW Sex and RW Tri were digitized from the respective publications,
-and the IX Vel spectrum was obtained using the XSHOOTER spectrograph 
-on the Very Large Telescope on 2014 October 10.
-These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $75^\circ$ 
-(see section 5.4) respectively. 
-The trend of increasing Balmer line emission with inclination can be seen.
-In RW Tri strong single-peaked emission in the Balmer lines is seen even
-in eclipse, indicating that the lines may be formed in a spatially
-extensive disk wind, and there is even a suggestion 
-of a (potentially wind-formed) recombination continuum in the eclipsed
-spectrum. We have attempted to show each spectrum over a similar dynamic range.
-}
-\label{novalikes}
-\end{figure}
-
 Murray \& Chiang (1996, 1997; hereafter referred to collectively as MC96)\nocite{MC96, MC97} 
@@
 Similarly, the relative excitation fractions within each ionization
-stage of a given species were estimated via a modified Boltzmann
+stage of a given species were estimated via a modified (dilute) Boltzmann
 equation,
@@
 
-Finally, \py\ modelled all bound-bound processes as transitions
-within a simple two-level atom \cite[e.g.][]{mihalas}. This
-approach works reasonably well for resonance  
+Finally, \py\ originally modelled all bound-bound processes as transitions
+within a simple two-level atom \cite[e.g.][]{mihalas}. 
+This framework was used for the treatment of line transfer and also
+for the line heating and cooling calculations. 
+The approximation works reasonably well for resonance  
 lines, such as \civfull, in which the lower level is the ground state.  
@@
 \cite{vanregemorter} approximation is used for collisional
-transitions, and thus we assume that collisions between radiatively
-forbidden transitions are not important in determining level
-populations. This is a reasonable approximation in the regimes
-considered here.
+transitions. This means that collisions between radiatively
+forbidden transitions are not taken into account when one 
+splits levels according to $l$ and $J$ quantum numbers, as well
+as principal quantum number, $n$ (as we have done with He~\textsc{i}; 
+see section~\ref{sec:data}).
+Although this is, in general, a poor approximation, 
+it is a second order effect in the physical regime where 
+recombination lines are formed. 
+This is because bound-free processes are 
+dominant in determining level populations and emissivities.
+We have verified that this is indeed the case in the He~\textsc{i}
+emission regions in our model.
 
@@
 models, we treat H and He as macro-atoms and all metals as
-simple-atoms.
+simple-atoms. Elements treated with either method
+are always present as sources of both bound-free opacity and line opacity, 
+and contribute to the heating and cooling balance of the plasma.
 
 \subsection{Atomic Data}
+\label{sec:data}
 
@@
 set to 10$\%$ of the accretion rate through the disk. 
+The sensitivity to some of these parameters is discussed further in
+section 5.
 
@@
 
+\subsection{Synthetic Spectra}
+\label{modela_spectrum}
+
 We begin by verifying that the benchmark model still produces UV
@@
 
+%It is possible that other parameters, such as the launching radii and angles
+
 \subsection{Synthetic Spectra}
@@
 \caption{
-UV (left) and Optical synthetic spectra for model B computed at
+UV (left) and optical (right) synthetic spectra for model B computed at
 sightlines of 10, 27.5, 45, 62.5 and 80 degrees. 
+Model A is shown in grey for comparison.	
 The inset plots show zoomed-in line profiles for 
@@
 Synthetic optical spectra from model B computed for 
-sightlines of 10, 27.5, 45, 62.5 and 80 degrees. In these plots
-the flux is divided by a polynomial fit to the 
+sightlines of 10, 27.5, 45, 62.5 and 80 degrees. 
+Model A is shown in grey for comparison.
+In these plots the flux is divided by a polynomial fit to the 
 underlying continuum redward of the Balmer edge, so that 
@@
 The work of JHM and CK is supported by the Science and Technology Facilities Council (STFC), 
-via studentships and a consolidated grant, respectively. The work of NSH is supported by NASA under Astrophysics Theory Program grants NNX11AI96G  and NNX14AK44G.
-We are very grateful to A.F. Palah and B.T. Gaensicke for the IX Vel XSHOOTER dataset.
-We would also like to thank J.V. Hernandez Santisteban, S.W. Mangham and I. Hubeny for useful discussions. We acknowledge the use of the IRIDIS High Performance Computing Facility, 
+via studentships and a consolidated grant, respectively. 
+The work of NSH is supported by NASA under Astrophysics Theory Program grants NNX11AI96G  and NNX14AK44G.
+We would like to thank the anonymous referee for a helpful and constructive report, and 
+we are  grateful to A.F. Palah and B.T. Gaensicke for the IX Vel XSHOOTER dataset.
+We would also like to thank J.V. Hernandez Santisteban, S.W. Mangham and I. Hubeny for useful discussions. 
+We acknowledge the use of the IRIDIS High Performance Computing Facility, 
 and associated support services at the University of Southampton, in the completion of this work.

### 2015-03-25 response/supplement_response.tex
working on response

--- 2015-01-23 draft.tex
@@
-%%%% Various options for document class.
-%\documentclass[usenatbib, a4paper]{preprint}
-\documentclass[preprint, a4paper, 11pt]{aastex}
-%%\documentclass[twocolum]{revtex4}
-%%\documentclass{report}
-%%\documentclass[useAMS,usenatbib, onecolumn]{mn2ejm}
-
-%\usepackage{psfig,morefloats,url}
-%use preprint2 for 2 columns paper.
-
+\documentclass{article}
 %% declare any packages used
@@
 
-\citestyle{aa}
-\addtolength{\topmargin}{-.5in}
-%% This command added as margins are wrong in mn2e, it appears. 
-%% Not needed for other classes
+\begin{document}
 
-%% This is the end of the preamble.  Indicate the beginning of the
-%% paper itself with \begin{document}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-%% define bibstyle and other definitions
-\bibliographystyle{aabib}
-%% renew commands
-\renewcommand{\labelitemi}{$\bullet$}
-\def\py{\textsc{Python}}
-\def\tar{\textsc{Tardis} }
-\def\cld{\textsc{Cloudy} }
-\def\civ{C~\textsc{iv} }
-\def\araa{ARAA}
-\def\nat{Nature}
-\def\apjl{ApJ Letters}
-\def\aapr{AAPR}
-\def\actaa{ACTAA} 
-\def\ssr{SSR}
-\def\apj{ApJ}
-\def\apss{AP\&SS}
-\def\pasp{PASP}
-\def\aap{A\&A}
-\def\mnras{MNRAS}
-\def\aj{AJ}
-\def\rmxaa{RMXAA}
-
-%% define some control sequences for lines
-\def\heiiopt{He~\textsc{ii}~$\lambda4686$}
-\def\heiiuv{He~\textsc{ii}~$\lambda1640$}
-\def\heiioptnew{He~\textsc{ii}~$\lambda3202$}
-\def\la{Ly$\alpha$}
-\def\ha{H$\alpha$}
-\def\hb{H$\beta$}
-\def\civfull{C~\textsc{iv}~$\lambda1550$}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%          TITLE AND AUTHORS
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title{The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables}
-\author{J. H. Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%          ABSTRACT
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{abstract}
-Many high-state non-magnetic cataclysmic variables (CVs) exhibit
-blue-shifted absorption or P-Cygni profiles associated with ultraviolet
-(UV) resonance lines, such as C~{\sc iv}~$\lambda1550$. These features
-imply the existence of powerful accretion disk winds in
-CVs. Here, we use an improved version of our Monte Carlo ionization
-and radiative transfer code to investigate whether disk wind models that
-produce realistic UV line profiles are also likely to generate
-observationally significant recombination line and continuum emission
-in the {\em optical} waveband. 
-We find that a standard disk wind model that is successful in
-reproducing the UV spectra of CVs also leaves a noticeable imprint on
-the optical spectrum, particularly for systems viewed at high
-inclination. The strongest optical wind-formed recombination lines are \ha\ and
-\heiiopt, although the outflow also produces emission in the Ly$\alpha$
-and \heiiuv\ UV lines. However, all of the optical lines produced by
-this default wind model are double-peaked, and the effect of the wind
-on the Balmer jump is modest. We demonstrate that a higher-density outflow model 
-displays reasonable verisimilitude with the optical spectrum of RW Trianguli,
-producing all the observed lines. This model
-produces a recombination continuum that is strong enough to fill in the Balmer jump,
-but it also predicts stronger-than-observed collisionally excited UV emission lines. 
-The wind in our revised model also alters the spectral shape of the continuum, 
-and displays a strong inclination dependence in its emission properties. 
-No single-peaked emission is seen, although we observe a 
-narrowing of the double-peaked emission lines from the base of the wind.
-We show that even denser models can produce a single-peaked \ha\ line.
-In this model, the single-peaked line profile is due to the line emission originating from 
-$\sim10^{11}$~cm above the disk plane where rotational velocities are small, 
-and is not due to the radial velocity shear mechanism that
-has previously been proposed. On the basis of our results, we suggest that winds can 
-modify, and perhaps even dominate, the line and continuum emission
-from CVs.
-\end{abstract}
-
+\title{Supplementary material for referee\\MNRAS: MN-15-0213-MJ}
 \maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%          INTRODUCTION
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction} 
-\label{sec:intro}
-
-Cataclysmic variables (CVs) are systems in which a white dwarf
-accretes matter from a donor star via Roche-lobe overflow. In
-non-magnetic systems this accretion is mediated by a Keplerian disk
-around the white dwarf (WD). Nova-like variables (NLs) are a subclass
-of CVs in which the  disk is always in a relatively
-high-accretion-rate state ($\dot{M} \sim
-10^{-8}$~M$_{\odot}$~yr$^{-1}$).  This makes NLs an excellent
-laboratory for studying the properties of steady-state accretion
-disks.
-
-It has been known for a long time that winds emanating from the
-accretion disk are important in shaping the ultraviolet (UV) spectra
-of high-state CVs \citep{heap1978, greensteinoke1982}. The most spectacular evidence for such
-outflows are the P-Cygni-like profiles seen in UV resonance lines such as
-\civfull\ (see e.g. Cordova \& Mason
-1982\nocite{cordova1982}). Considerable effort has been spent over the
-years on understanding and modelling these UV features (e.g. Drew \&
-Verbunt 1985\nocite{drewverbunt1985}; Mauche \& Raymond
-1987\nocite{maucheraymond1987}; Drew 1987; Shlosman \& Vitello 1993; [hereafter
-SV93]\nocite{SV93}; Knigge, Woods \& Drew 1995\nocite{KWD95}; 
-Knigge \& Drew 1997\nocite{kd1997}; 
-Knigge et al. 1997\nocite{knigge1997}; Long \& Knigge 2002 [hereafter LK02]\nocite{LK02}, 
-Noebauer et al. 2010\nocite{noebauer};
-Puebla et al. 2011\nocite{puebla2011}). The basic picture emerging from these efforts is
-of a slowly accelerating, moderately collimated bipolar
-outflow that carries away $\simeq 1\% - 10\%$ of the accreting
-material. State-of-the-art simulations of line formation in this type
-of disk wind can produce UV line profiles that are remarkably similar
-to observations.
-
-Much less is known about the effect of these outflows on the optical
-spectra of high-state CVs. These spectra are typically characterized
-by H and He emission lines superposed on a blue continuum. In many
-cases, and particularly in the SW~Sex subclass of NLs
-\citep{HSK86,DR95}, these lines are single-peaked. This is contrary to
-theoretical expectations for lines formed in accretion disks, which
-are predicted to be double-peaked \citep{smak1981, hornemarsh1986}. 
-{\em Low-state} CVs (dwarf novae in quiescence) do, in fact,
-exhibit such double-peaked lines \citep{marshhorne1990}.
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figures/fig1.eps}
+\includegraphics[width=1.0\textwidth]{pops.png}
 \caption{
-Optical spectra of three nova-like variables: 
-RW Sex (top; Beuermann et al. 1992),
-IX Vel (top middle; A. F. Pala \& B. T. Gaensicke, private communication) 
-and RW Tri in and out of eclipse (bottom two panels; Groot et al. 2004).
-The data for RW Sex and RW Tri were digitized from the respective publications,
-and the IX Vel spectrum was obtained using the XSHOOTER spectrograph 
-on the Very Large Telescope on 2014 October 10.
-These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $75^\circ$ 
-(see section 5.4) respectively. 
-The trend of increasing Balmer line emission with inclination can be seen.
-In RW Tri strong single-peaked emission in the Balmer lines is seen even
-in eclipse, indicating that the lines may be formed in a spatially
-extensive disk wind, and there is even a suggestion 
-of a (potentially wind-formed) recombination continuum in the eclipsed
-spectrum. We have attempted to show each spectrum over a similar dynamic range.
 }
@@
 
-Murray \& Chiang (1996, 1997; hereafter referred to collectively as MC96)\nocite{MC96, MC97} 
-have shown that the presence of disk winds may
-offer a natural explanation for the single-peaked optical emission lines in
-high-state CVs, since they can strongly affect the radiative transfer
-of line photons. Strong support for a significant wind contribution to the
-optical emission lines comes from observations of eclipsing
-systems. There, the single-peaked lines are often only weakly
-eclipsed, and a significant fraction of the line flux remains visible
-even near mid-eclipse \citep[e.g.][]{baptista2000,groot2004}. 
-This points to line formation in a spatially
-extended region, such as a disk wind (see Fig.~\ref{novalikes}).
-%%(Honeycutt, Schlegel, \& Kaitchuck 1986; Dhillon \& Rutten 1995). 
-Further evidence for a wind contribution to the optical lines comes
-from isolated observations of P-Cygni-like line profiles even in optical
-lines, such as \ha\ and He \textsc{i} $\lambda5876$ \citep{patterson1996, RN98, kafka2004}.
-
-Could disk winds also have an impact on the UV/optical {\em continuum}
-of high-state CVs? This continuum is usually thought to be dominated
-by the accretion disk and modelled by splitting the disk into
-a set of concentric, optically thick, non-interacting annuli following
-the standard $T_{eff}(R) \propto R^{-3/4}$ radial temperature
-distribution \citep{shakurasunyaev1973}. In such
-models, each annulus is taken to emit either as a blackbody or,
-perhaps more realistically, as a stellar/disk atmosphere model
-\citep{Schwarzenberg-Czerny1977,wade1984,wade1988}.
-In the latter case, the local surface gravity, $\log{g}(R)$, is
-assumed to be set solely by the accreting WD, since self-gravity is
-negligible in CV disks.
-
-Attempts to fit the observed spectral energy distributions (SEDs) of
-high-state CVs with such models have met with mixed success. In
-particular, the SEDs predicted by most stellar/disk atmosphere models 
-are too blue in the UV \citep{wade1988,long1991,long1994,knigge1998} and exhibit
-stronger-than-observed Balmer jumps in absorption 
-\citep{wade1984,haug1987,ladous1989b,knigge1998}. One possible
-explanation for these problems is that these models fail to capture
-all of the relevant physics. Indeed, it has been argued that a
-self-consistent treatment can 
-produce better agreement with observational data (e.g. Shaviv et
-al. 1991;  but see also Idan et al. 2010).
-\nocite{idanshaviv2010} \nocite{shaviv1991}
-However, an alternative explanation, suggested by Knigge et al.
-(1998b; see also Hassall et al. 1985)\nocite{KLWB98,hassall}, 
-is that recombination continuum emission from the base of the 
-disk wind might fill in the disk's
-Balmer absorption edge and flatten the UV spectrum.
-
-\nocite{groot2004}
-\nocite{beuermann1990}
-\nocite{beuermann1992}
-\nocite{higginbottom2013}
-
-Here, we carry out Monte Carlo radiative transfer simulations in
-order to assess the likely impact of accretion disk winds on the
-optical spectra of high-state CVs. More specifically, our goal is to
-test whether disk winds of the type developed to account for the UV
-resonance lines would also naturally produce significant amounts of  
-optical line and/or continuum emission. In order to achieve this, we
-have implemented the `macro-atom' approach developed by Lucy
-(2002, 2003) into the Monte Carlo ionization and radiative transfer
-code described by LK02 (a process initiated by Sim et al. 2005; hereafter SDL05). 
-With this upgrade, the code is able to deal correctly with processes involving
-excited levels, such as the recombination emission produced by CV
-winds.
-
-The remainder of this paper is organized as follows. In Section~2, we
-briefly describe the code and and the newly implemented macro-atom
-approach. In Section~3, we describe the kinematics and geometry of our
-disk wind model. 
-In Section~4, we present spectra simulated from the benchmark model
-employed by LK02, and, in Section~5, we present a revised model
-optimized for the optical waveband. In Section~6, we summarize our
-findings.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%          THE CODE, RADIATIVE TRANSFER
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{\sc{python}: A Monte Carlo Ionization and Radiative Transfer Code}
-
-\py\ is a Monte Carlo  ionization and radiative transfer code which
-uses the Sobolev approximation to treat line transfer 
-\citep[e.g.][]{sobolev1957,sobolev1960,rybickihummer1978}. 
-The code has already been described extensively by LK02, SDL05 and Higginbottom et al. (2013; hereafter H13), so here we provide only a brief summary of its operation, 
-focusing particularly on new
-aspects of our implementation of macro-atoms into the code.
-
-\subsection{Basics}
-
-\py\ operates in two distinct stages. First, the ionization state,
-level populations and temperature structure are calculated. This is
-done iteratively, by 
-propagating several populations of Monte Carlo energy quanta (`photons')
-through a model wind. The geometric and kinemetic properties of the
-outflow are specified on a pre-defined spatial grid. In each of these
-iterations (`ionization cycles'), the code records estimators that 
-characterize the radiation field in each grid cell. At the end 
-of each ionization cycle, a new electron temperature is calculated
-that more closely balances heating and cooling in the 
-plasma. The radiative estimators and updated electron
-temperature are then used to revise the ionization state of the wind,
-and a new ionization cycle is started. The process is repeated until
-heating and cooling are balanced throughout the wind.
-
-This converged model is then used as the basis for the second set of
-iterations (`spectral cycles'). In these, the emergent spectrum over
-the desired spectral range is synthesized by tracking populations of
-energy packets through the wind and computing the emergent spectra at
-a number of user-specified viewing angles.
-
-\py\ is designed to operate in a number of different
-regimes, both in terms of the scale of the system and in terms of the
-characteristics of the underlying radiation field.
-It was originally developed by LK02 in order to model the UV spectra
-of CVs with a simple biconical disk wind model. SDL05
-\nocite{simmacro2005} used the code to model Brackett
-and Pfund line profiles of H in young-stellar objects (YSOs). As part
-of this effort, they implemented a `macro-atom' mode (see below) in
-order to correctly treat H recombination lines with
-\py. Finally, H13 used \py\ to model broad absorption line (BAL) QSOs. For
-this application, an improved treatment of ionization was implemented,
-so that the code is now capable of dealing with arbitrary
-photo-ionizing SEDs, including non-thermal and multi-component ones.
-
-\subsection{Ionization and Excitation: `Simple Atoms'}
-\label{simpleatoms}
-
-Prior to SDL05, the relative ionization fractions for all atomic
-species were estimated via the modified Saha equation (Mazzali \&
-Lucy 1993)  
-\begin{equation}
-\frac{n_{j+1} n_e}{n_j} = W [\xi + W(1-\xi)]
-\left(\frac{T_e}{T_R}\right)^{1/2}
-\left(\frac{n_{j+1}n_e}{n_j}\right)^*_{T_R}. \label{ionization}
-\end{equation}
-Here, the `starred' term on the right represents abundances computed with
-the Saha equation at temperature $T_R$, but using partition functions
-from the dilute blackbody approximation. 
-$W$ is an effective dilution factor, $\xi$ is the
-fraction of recombinations going directly to the ground state, and
-$T_R$ and $T_e$ are the radiation and electron temperatures,
-respectively. This simple ionization scheme produces reasonable
-results when the photoionizing SED can be approximated by a dilute
-blackbody. This is the case for high-state CVs. (As noted above, an
-improved, but more complex treatment of ionization that is appropriate
-for more complex SEDs is described in H13.)
-
-Similarly, the relative excitation fractions within each ionization
-stage of a given species were estimated via a modified Boltzmann
-equation,
-\begin{equation}
-\frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R),
-\end{equation}
-where $n_{jk}$ is the population of level $k$ in ionic stage $j$,
-$E_k$ is the energy difference between level $k$ and the ground state,
-$g_k$ is the statistical weight of level $k$
-and $z_j(T_R)$ is the partition function of ionic stage $j$.
-
-Finally, \py\ modelled all bound-bound processes as transitions
-within a simple two-level atom \cite[e.g.][]{mihalas}. This
-approach works reasonably well for resonance  
-lines, such as \civfull, in which the lower level is the ground state.  
-However, it is a poor approximation for many other
-transitions, particularly those where the upper level
-is primarily populated from above. Thus an improved method for
-estimating excited level populations and simulating line transfer is
-needed in order to model recombination lines and continua.
-
-\subsection{Ionization and Excitation: Macro-Atoms}
-
-Lucy (2002, 2003\nocite{lucy2002, lucy2003}; hereafter L02, L03) 
-has shown that it is possible to calculate the emissivity of a gas in
-statistical equilibrium accurately by quantising matter into
-`macro-atoms', and radiant and kinetic energy into indivisible energy
-packets (r- and k- packets, respectively). His macro-atom scheme
-allows for all possible transition paths from a given level and
-provides a full non-local thermodynamic equilibrium (NLTE) solution
-for the level populations based on Monte Carlo estimators. The macro-atom
-technique has already been used to model Wolf-Rayet star
-winds \citep{sim2004}, AGN disk winds \citep{simlong2008, tatum2012},
-supernovae \citep{kromersim2009, kerzendorfsim} and YSOs (SDL05). A full 
-description of the approach can be found in L02 and L03.
-
-Briefly, macro-atom NLTE level populations and ionization fractions
-are calculated by solving the statistical equilbrium equations between
-each pair of levels. In the framework of the Sobolev escape probability formalism (Rybicki \& Hummer 1978; L02; Sim 2004), 
-the bound-bound excitation rate, ${\cal R}_{lu}$, in an ion is given by 
-\begin{equation}
-{\cal R}_{lu} = B_{lu} n_l J_{est} + C_{lu} n_l n_e,
-\end{equation}
-where $u$ and $l$ denote the upper and lower levels, $C$ represents the
-collisional rate coefficients, and $B$ is the usual Einstein
-coefficient. $J_{est}$ is the Monte Carlo estimator for the mean intensity 
-impinging on the Sobolev region, weighted by an angle-dependent escape probability, 
-given by \citep{sim2004}
-\begin{equation}
-J_{est} = \frac{c}{4 \pi \nu_0 V} \sum_{photons} w \frac{1 - e^{-\tau_s}}{\tau_s} \frac{1}{dv/ds}.
-\end{equation}
-Here $w$ is the photon weight (in luminosity units), $\nu_0$
-is the line frequency, $dv/ds$ is the velocity gradient and
-$\tau_s$ is the Sobolev optical depth.
-The sum is over all photons that come into resonance with the line.
-The corresponding de-excitation rate is then 
-\begin{equation}
-{\cal R}_{ul} = \beta_{lu} A_{ul} n_u + B_{ul} n_u J_{est} +
-C_{ul} n_u n_e,
-\label{eq:nlte_rul}
-\end{equation}
-where $A$ is the usual Einstein coefficient. 
-The quantity $\beta_{lu}$ is the {\em angle-averaged} probability 
-that a given line photon will escape the Sobolev region.
-
-In our implementation of the macro-atom approach, we also explicitly
-take into account the photoionization and collisional ionization rates
-between a lower level, $l$, and the continuum (or, in the case of ions
-with more than one bound electron, the ground state of the upper ion),
-$\kappa$,
-\begin{equation}
-{\cal R}_{l \kappa}= n_l \int_{\nu_0}^{\infty} \frac{ 4 \pi J_{\nu}
-  \sigma_{\nu}}{h \nu} d\nu + C_{l \kappa} n_l n_e.
-\end{equation}
-Here, $\sigma_{\nu}$ is the photoionization cross section, and $J_{\nu}$
-is the mean intensity. The corresponding recombination rate is given
-by 
-\begin{equation}
-{\cal R}_{\kappa l} = \alpha_{\kappa l} n_{\kappa} n_e + C_{\kappa l}
-n_\kappa n_e, \\
-\end{equation}
-where $\alpha_{\kappa l}$ is the radiative recombination coefficient
-to level $l$. This treatment means that radiative and collisional
-rates to and from all levels are considered when calculating both the
-ionization state and the level populations, although we neglect 
-ionization directly to excited levels of the upper ion. The
-\cite{vanregemorter} approximation is used for collisional
-transitions, and thus we assume that collisions between radiatively
-forbidden transitions are not important in determining level
-populations. This is a reasonable approximation in the regimes
-considered here.
-
-\subsection{Ionization and Excitation: A Hybrid Approach}
-
-SDL05 implemented a macro-atom treatment of H in \py\ and used
-this to predict the observable properties of a pure H wind
-model for YSOs. Our goal here is to simultaneously model the optical
-and ultraviolet spectra of high-state CVs. Since the optical spectra
-are dominated by H and He recombination lines, both of these species
-need to be treated as macro-atoms. The UV spectra, on the other hand,
-are dominated by resonance lines associated with metals. This means we
-need to include these species in our models, but they can be treated 
-with our (much faster) simple-atom approach. We have therefore
-implemented a hybrid ionization and excitation scheme into \py. Any
-atomic species can now be treated either in our simple-atom
-approximation or with the full macro-atom machinery. In our CV
-models, we treat H and He as macro-atoms and all metals as
-simple-atoms.
-
-\subsection{Atomic Data}
-
-We generally use the same atomic data as H13, which is an updated
-version of that described by LK02. In addition, we follow SDL05 in
-treating H as a 20-level atom, where each level is defined by
-the principal quantum number, $n$. For the macro-atom treatment of
-He, we have added the additional level and line information required 
-from \textsc{Topbase} \citep{topbase2005}.  He~\textsc{ii} is treated
-in much the same way as H, but with 10 levels. He~\textsc{i} has
-larger energy differentials between different l-subshells and triplet
-and singlet states. Thus, we still include levels up to $n=10$, but
-explicitly treat the $l$ and $s$ sub-orbitals as distinct levels
-instead of assuming they are perfectly `l-mixed'. This allows us
-to model the singlet and  triplet He~\textsc{i} lines that are ubiquitous
-in the optical spectra of CVs \citep[e.g.][]{dhillon1996}.
-
-\subsection{Code Validation and Testing}
-
-\py\ has been tested against a number of radiative transfer and
-photoionization codes. LK02 and H13 conducted comparisons of 
-ionization balance  with \cld \citep{cloudy2013}, demonstrating
-excellent agreement. We have also carried out comparisons
-of ionization and spectral synthesis with the supernova code
-\textsc{Tardis.} \tar is described by 
-\cite{kerzendorfsim}, and the spectral comparisons can be found
-therein. For the effort reported here, we have additionally carried
-out tests of the macro-atom scheme in \py. Fig.~\ref{tests} shows
-two of these tests. In the top panel, we compare the Balmer series 
-emissivities as predicted by \py\ in the l-mixed Case~B limit against the
-analytical calculations by \cite{seaton1959}. In the bottom panel, we
-compare \py\ and \tar predictions of  He \textsc{i} level populations
-for a particular test case. Agreement is excellent for both H and He.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/fig_caseb_tardis.eps}
-\caption{
-{\sl Top Panel:} `Case B' Balmer decrements computed 
-with \textsc{Python} compared to analytic calculations
-by Seaton (1959). Both calculations are calculated at $T_e=10,000$K.
-(see Osterbrock 1989 for a discussion of this commonly used approximation).
-{\sl Bottom Panel:}  a comparison of He I level populations (the most complex ion we currently 
-treat as a macro-atom) between \py\ and \tar models. 
-The calculation is conducted with physical parameters of $n_e=5.96\times10^4$~cm$^{-3}$,
-$T_e=30,600$K, $T_R=43,482$K and $W=9.65\times10^{-5}$. 
-Considering the two codes use different atomic data and \textsc{Tardis,} unlike \textsc{Python,} currently has a complete treatment of collisions between 
-radiatively forbidden transitions, the factor of 
-$<2$ agreement is encouraging. 
-}
-\label{tests}
-\end{figure}
-
-\nocite{osterbrock}
-\nocite{seaton1959}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%          THE MODEL
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Describing the System and its Outflow}
-
-\py\ includes several different kinematic models of accretion disk
-winds, as well as different options for describing the physical and
-radiative properties of the wind-driving system under
-consideration. Most of these features have already been discussed by
-LK02 and H13, so below we only briefly recount the key aspects of the
-particular system and wind model used in the present study.
-
-\subsection{Wind Geometry and Kinematics}
-\label{kinematics}
-
-We adopt the kinematic disk wind model developed by SV93. 
-A schematic of this model is shown in
-Fig.~\ref{cartoon}. In this parametrization, a smooth, biconical
-disk wind emanates from the accretion disk between radii $r_{min}$ and 
-$r_{max}$. The covering fraction of the outflow is also controlled by the
-inner and outer opening angles of the wind, $\theta_{min}$ and
-$\theta_{max}$, and the launch angle of the other streamlines is given
-by 
-\begin{equation}
-\theta(r_0) = \theta_{min} + (\theta_{max} - \theta_{min}) \left(\frac{r_0 - r_{min}}{r_{max} - r_{min}} \right)^{\gamma},
-\label{theta}
-\end{equation}
-where $r_0$ is the launch radius of the streamline.
-
-The poloidal (non-rotational) velocity field of the wind, $v_l$, is given by
-\begin{equation}
-v_l=v_0+\left[v_{\infty}(r_0)-v_0\right]\frac{\left(l/R_v\right)^{\alpha}}{\left(l/R_v\right)^{\alpha}+1},
-\label{v_law}
-\end{equation}
-where $l$ is the poloidal distance along a particular wind
-streamline. The terminal velocity along a streamline, $v_{\infty}$, is
-set to a fixed multiple of $v_{esc}$, the escape velocity at the launch
-point. The launch velocity from the disk surface, $v_0$, is assumed to
-be constant (set to $6$~km~s$^{-1}$). Once the wind is launched, it
-accelerates, reaching half of its terminal velocity at $l = R_v$. The
-velocity law exponent $\alpha$ controls how quickly the wind
-accelerates. Larger values of $\alpha$ cause the main region of 
-acceleration to occur close to $R_v$, whereas smaller values
-correspond to fast acceleration close to the disk (see
-Fig.~\ref{acc_law}). The rotational velocity $v_\phi$ is 
-Keplerian at the base of the streamline 
-and we assume conservation of specific angular momentum,
-such that
-\begin{equation}
-v_\phi r = v_{k} r_0,
-\label{v_law}
-\end{equation}
-where $v_{k}=(GM_{WD}/r_0)^{1/2}$.
-
-\begin{figure} 
-\centering
-\includegraphics[width=0.5\textwidth]{figures/fig2_cartoon.eps}
-\caption{Cartoon illustrating the geometry and kinematics of the benchmark CV wind model.}
-\label{cartoon}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{figures/acc_law.eps}
-\caption{
-The adopted poloidal velocity law for various values of the
-acceleration exponent, $\alpha$.
-%%{\bf JM: KSL has suggested we ditch this}
-} 
-\label{acc_law}
-\end{figure}
-
-The density at position $(r,z)$ in the wind, $\rho(r,z)$, is
-calculated from the mass continuity equation, yielding
-\begin{equation}
-\rho(r,z) = \frac{r_0}{r} \frac{dr_0}{dr} \frac{\phi(r_0)}{v_z(r,z)}.
-\label{density}
-\end{equation}
-Here, 
-$v_z$ is the vertical velocity component and, following SV93,
-$\phi(r_0)$ is the local mass-loss rate per unit area at $r_0$, 
-defined as
-\begin{equation}
-\phi(r_0) \propto \dot{M}_{wind} r_0^\lambda \cos [\theta(r_0)].
-\label{density}
-\end{equation}
-We adopt $\lambda = 0$ and normalize $\phi(r_0)$ by 
-matching its integral over both sides of the disk
-to the user-specified total mass-loss rate, $\dot{M}_{wind}$.
-
-\subsection{Sources and Sinks of Radiation}
-\label{radsources}
-
-The net photon sources in our CV model are the accretion disk, the
-WD and, in principle, a boundary layer with user-defined temperature
-and luminosity. All of these radiating bodies are taken to be
-optically thick, and photons striking them are assumed to be destroyed
-instantaneously. The secondary star is not included as a radiation
-source, but is included as an occulting body. This allows us to model
-eclipses. Finally, emission from the wind itself is also accounted for, but
-note that we assume the outflow to be in radiative equilibrium. Thus all
-of the heating of the wind, as well as its emission, is ultimately
-powered by the radiation field of the net photon sources in the
-simulation. In the following sections, we will describe our treatment
-of these system components in slightly more detail.
-
-\subsubsection{Accretion Disk}
-
-\py\ has some flexibility when treating the accretion 
-disk as a source of photons. The disk is broken down into annuli 
-such that each annulus contributes an equal amount to the bolometric
-luminosity. We take the disk to be geometrically thin, but optically
-thick, and thus adopt the temperature profile of a standard
-\cite{shakurasunyaev1973} $\alpha$-disk. An annulus can then
-be treated either as a blackbody with the corresponding effective
-temperature or as a stellar atmosphere model with the appropriate
-surface gravity and effective temperature. Here, we use blackbodies 
-during the ionization cycles and to compute our Monte Carlo
-estimators. However, during the spectral synthesis stage of the 
-simulation we use stellar atmosphere models. This produces more
-realistic model spectra and allows us to test if recombination
-emission from the wind base can fill in the Balmer jump, which is
-always in absorption in these models. Our synthetic stellar atmosphere
-spectra are calculated with
-\textsc{Synspec}\footnote{http://nova.astro.umd.edu/Synspec43/synspec.html}
-from either Kurucz \citep{kurucz1991} atmospheres (for $T_{eff} \leq
-50,000$~K) or from \textsc{TLUSTY} \citep{tlusty} models (for $T_{eff} > 50,000$~K).
-
-\subsubsection{White Dwarf}
-
-The WD at the center of the disk is always present as a spherical occulting
-body with radius $R_{WD}$ in \py\ CV models, but it can also be included
-as a source of radiation. In the models presented here, we treat the
-WD as a blackbody radiator with temperature $T_{WD}$ and luminosity
-$L_{WD} = 4\pi R_{WD}^2 \sigma T_{WD}^4$.
-
-\subsubsection{Boundary Layer}
-
-It is possible to include radiation from a boundary layer (BL) between
-the disk and the WD. In \py, the BL is described as
-a blackbody with a user-specified effective temperature and
-luminosity. In the models presented here, we have followed LK02 in setting
-the BL luminosity to zero. However, we have confirmed that the addition of an isotropic
-BL with $L_{BL} = 0.5 L_{acc}$ and temperatures in the range $80~{\rm
-kK} \leq T_{BL} \leq 200~{\rm kK}$ would not change any of our main
-conclusions.
-
-\subsubsection{Secondary Star}
-
-The donor star is included in the system as a pure radiation sink, 
-i.e. it does not emit photons, but absorbs any photons that strike its
-surface. The secondary is assumed to be Roche-lobe filling, so its
-shape and relative size are defined by setting the mass ratio of the system, 
-$q = M_2/M_{WD}$. The inclusion of the donor star as an occulting body
-allows us to model eclipses of the disk and the wind. For this
-purpose, we assume a circular orbit with a semi-major axis $a$ and 
-specify orbital phase such that $\Phi_{orb} = 0$ is the
-inferior conjunction of the secondary (i.e. mid-eclipse for $i \simeq
-90^o$).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%          BENCHMARK MODEL
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{table}
-\centering
-\begin{tabular}{p{2cm}p{2cm}p{2cm}}
-%%\multicolumn{2}{|l|}{Model Parameters}  \\
-Model Parameters \\
-\hline Parameter 	&	 Model A  & Model B \\ 
-\hline \hline 
-$M_{WD}$ 	 &	 $0.8~M_{\odot}$  &     \\ 
-$R_{WD}$ 	 &	 $7\times10^{8}$~cm  & \\ 
-$T_{WD}$ 	 &	 $40,000$~K        &  \\
-$M_{2}$ 	& -&	 $0.6~M_{\odot}$   \\ 
-$q$ 	&- &	 $0.75$   \\ 
-$P_{orb}$ 	&- &	 $5.57$~hr   \\ 
-$a$ 	& -&	 $194.4~R_{WD}$   \\ 
-$R_2$   &   -  &	 $69.0~R_{WD}$  \\ 
-$\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$  &\\ 
-$\dot{M}_{wind}$  &	$10^{-9}~M_{\odot}yr^{-1}$å  & \\ 
-$r_{min}$ 	&	 $4~R_{WD}$ &  \\ 
-$r_{max}$ 	&	 $12~R_{WD}$  &  \\ 
-$r_{disk}$(max) 	&	 $34.3~R_{WD}$  &  \\ 
-$\theta_{min}$ 	&	 $20.0^{\circ}$  &  \\ 
-$\theta_{max}$ 	&	 $65.0^{\circ}$  &  \\ 
-$\gamma$ 	&	 $1$  &  \\ 
-$v_{\infty}$ 	&	 $3~v_{esc}$  &  \\ 
-$R_v$ 	        &	 $100~R_{WD}$  &  $142.9~R_{WD}$  \\ 
-$\alpha$ 	&	 $1.5$   &   $4$\\
-\end{tabular}
-\centering
-\caption{
-Parameters used for the geometry and kinematics of the benchmark 
-CV model (model A), which is optimized for the UV band, and a model
-which is optimized for the optical band and described in section 5 (model B).
-For model B, only parameters which are altered are given - otherwise the
-model A parameter is used. $P_{orb}$ is the orbital period 
-(the value for RW Tri from Walker 1963 is adopted, see section 5.4) and 
-$R_2$ is the radius of a sphere with the volume of the secondary's Roche lobe. 
-Other quantities are defined in the text or Fig.~\ref{cartoon}.
-Secondary star parameters are only quoted for 
-model B as we do not show eclipses with the 
-benchmark model (see section 5.4).
-}
-\label{wind_param}
-\label{modelb_table}
-\end{table}
-
-\nocite{walker1963}
-
-\section{A Benchmark Disk Wind Model}
-\label{modela}
-
-Our main goal is to test whether the type of disk wind model that has
-been successful in explaining the UV spectra of CVs could also have a
-significant impact on the optical continuum and emission line spectra
-of these systems. In order to set a benchmark, we therefore begin by
-investigating one of the fiducial CV wind models that was used by SV93
-and LK02 to simulate the UV spectrum of a typical high-state
-system. The specific parameters for this model (model A) are listed in
-Table~1. A key point is that the wind mass-loss rate in this model is
-set to 10$\%$ of the accretion rate through the disk.
-
-\subsection{Physical Structure and Ionization State}
-\label{modela_ionization}
-
-\begin{figure} %fullpage
-\includegraphics[width=\textwidth]{figures/fig5.eps}
-\caption{
-The physical properties of the wind -- note the logarithmic scale. 
-Near the disk plane the wind is dense, with low poloidal velocities.
-As the wind accelerates it becomes less dense
-and more highly ionized. The dominant He ion
-is almost always He III, apart from in a small
-portion of the wind at the base, which is partially shielded
-from the inner disk.
-}
-\label{wind}
-\end{figure} %fullpage
-
-Fig.~\ref{wind} shows the physical and ionization structure 
-of the benchmark disk wind model. The ionization parameter shown in the bottom
-right panel is given by
-
-\begin{equation}
-U = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu},
-\end{equation}
-
-\noindent where $\rm{n_H}$ is the local number density of H, and $\nu$ denotes photon 
-frequency. The ionization parameter is a useful measure of the ionization state of a plasma, 
-as it evaluates the ratio of the number density of ionizing photons to the local 
-H density.
-
-There is an obvious drop-off in density
-and temperature with distance away from the disk, so any line
-formation process that scales as $\rho^2$ -- i.e. recombination and
-collisionally excited emission -- should be expected to operate
-primarily in the dense base of the outflow. Moreover, a comparison of
-the rotational and poloidal velocity fields shows that rotation
-dominates in the near-disk regime, while outflow dominates further out
-in the wind.
-
-The ionization equation used in the `simple atom' approach used by
-LK02 (see section~\ref{simpleatoms}) should be a reasonable approximation to
-the photoionization equilibrium in the benchmark wind model. Even
-though the macro-atom treatment of H and He does affect the 
-computation of the overall ionization equilibrium, we would expect the
-resulting ionization state of the wind to be quite similar to that
-found by LK02. The bottom panels in Fig.~\ref{wind} confirm that this
-is the case. In particular, He is fully ionized
-throughout most of the outflow, except for a small region near the
-base of the wind, which is shielded from the photons produced by the
-hot inner disk. In line with the results of LK02, we also find
-that C\textsc{iv} is the dominant C ion throughout the wind,
-resulting in a substantial absorbing column across a large range of
-velocities. As we shall see, this produces the broad, deep and
-blue-shifted C\textsc{iv}~$\lambda1550$ absorption line that
-is usually the most prominent wind-formed feature in the UV spectra of
-low-inclination nova-like CVs.
-
-\subsection{Synthetic Spectra}
-\label{modela_spectrum}
-
-\begin{figure} %fullpage
-\includegraphics[width=0.9\textwidth]{figures/modela_uv_opt.eps}
-\caption{
-UV (left) and optical (right) synthetic spectra for model A, our benchmark model,
-computed at sightlines of 10, 27.5, 45, 62.5 and 80 degrees.	
-The inset plots show zoomed-in line profiles for 
-\heiiuv\ and \ha. Double-peaked line emission can be seen in 
-\heiiuv, \heiiopt, \ha\ and some He I lines, but the 
-line emission is not always sufficient to overcome the absorption
-cores from the stellar atmosphere models. The model
-also produces a prominent \heiioptnew\ line at high inclinations.
-}
-\label{spec}
-\end{figure} %fullpage\
-
-We begin by verifying that the benchmark model still produces UV
-spectra that resemble those observed in CVs. We do expect this to be
-the case, since the ionization state of the wind has not changed
-significantly from that computed by LK02 (see section~\ref{modela_ionization}). 
-The left column of panels in Fig.~\ref{spec} shows that this expectation
-is met: all of the strong metal resonance
-lines -- notably N\textsc{v}~$\lambda1240$,
-Si\textsc{iv}~$\lambda1400$ and C\textsc{iv}~$\lambda1550$ -- 
-are present and exhibit clear P-Cygni profiles
-at intermediate inclinations. In addition, however, we now also find
-that the wind produces significant Ly$\alpha$ and
-He~\textsc{ii}~$\lambda1640$ emission lines.
-
-Fig.~\ref{spec} (right-hand panel) and Fig.~\ref{spec_continuum}
-show the corresponding optical spectra produced for
-the benchmark model, and these do exhibit some emission lines
-associated with H and He. We see a general trend from absorption lines to emission lines 
-with increasing inclination, as one might expect from our wind
-geometry. This trend is consistent with observations, as can be seen
-in Fig.~1. However, it is clear that this particular model
-does not produce all of the lines seen in observations of high-state CVs.
-The higher-order Balmer series lines are too weak
-to overcome the intrinsic absorption from the disk atmosphere, and the wind 
-fails to produce any observable emission at low and intermediate inclinations.
-This contrasts with the fact that emission lines are seen 
-in the optical spectra of (for example) V3885 Sgr \citep{hartley2005}
-and IX Vel \citep[][see also Fig.~1]{beuermann1990}.
-
-The emissivity of these recombination 
-features scales as $\rho^2$, meaning that they form almost entirely in the 
-dense base of the wind, just above the accretion disk. Here, the
-velocity field of the wind is still dominated by rotation, rather than
-outflow, which accounts for the double-peaked shape of the lines. In
-principle, lines formed in this region can still be single peaked,
-since the existence of a poloidal velocity {\em gradient} changes the
-local escape probabilities (MC96). However, as
-discussed further in section~5.3, the 
-radial velocity shear in our
-models is not high enough for this radiative transfer effect
-to dominate the line shapes.
-
-The Balmer jump is in absorption at all inclinations for our benchmark
-model. This is due to the stellar atmospheres we have used to
-model the disk spectrum; it is not a result of photoabsorption in the
-wind. In fact, the wind spectrum exhibits the Balmer jump in {\em
-emission}, but this is not strong enough to overcome the intrinsic
-absorption edge in the disk spectrum. This is illustrated in
-Fig.~\ref{cont}, which shows the angle-integrated spectrum of the system,
-i.e. the spectrum formed by all escaping photons, separated into the
-disk and wind contributions. Even though the wind-formed Balmer
-recombination continuum does not completely fill in the Balmer
-absorption edge in this model, it does already contribute
-significantly to the total spectrum. This suggests that modest changes 
-to the outflow kinematics might boost the wind continuum and produce
-emergent spectra with weak or absent Balmer absorption edges.
-
-\begin{figure} 
-\includegraphics[width=0.45\textwidth]{figures/modela_opt_cont.eps}
-\caption{Synthetic optical spectra from model A computed for 
-sightlines of 10, 27.5, 45, 62.5 and 80 degrees. In these plots
-the flux is divided by a polynomial fit to the 
-underlying continuum redward of the Balmer edge, so that 
-line-to-continuum ratios and the true depth of the
-Balmer jump can be shown.}
-\label{spec_continuum}
-\end{figure}
-
-\begin{figure} 
-\includegraphics[width=0.45\textwidth]{figures/modela_escaping.eps}
-\caption{Total packet-binned spectra across all viewing angles, in units
-of monochromatic luminosity.
-The thick black line shows the total 
-integrated escaping spectrum, 
-while the green line shows disk photons which escape without being reprocessed by
-the wind. The red line show the contributions from reprocessed photons. 
-Recombination continuum emission blueward of the Balmer 
-edge is already prominent relative to other wind continuum processes, but is not sufficient
-to fill in the Balmer jump in this specific model}
-\label{cont}
-\end{figure}
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%          REVISED MODEL
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{A Revised Model Optimized for Optical Wavelengths}
-
-The benchmark model discussed in section~\ref{modela} was originally
-designed to reproduce the wind-formed lines seen in the UV spectra of
-high-state CVs. As we have seen, this model does produce some observable
-optical emission. We can now attempt to construct a model that more closely 
-matches the observed optical spectra of CVs.
-
-Specifically, we aim to assess whether a revised model can:
-
-\begin{itemize}
-         \item account for all of the lines we see in optical spectra of CVs while preserving
-the UV behaviour;
-         \item produce single-peaked Balmer emission lines; 
-         \item generate enough of a wind-formed recombination continuum
-to completely fill in the disk's Balmer absorption edge for 
-reasonable outflow parameters.
-\end{itemize}
-
-The emission measure of a plasma is directly proportional to its density.
-The simplest way to simultaneously affect the density in the wind (for fixed mass loss rate),
-as well as the velocity gradients, is by modifying the poloidal velocity
-law. Therefore, we focus on just two kinematic variables (section~\ref{kinematics}):
-
-\begin{itemize}
-         \item the acceleration length, $R_v$, which controls the
-        distance over which the wind accelerates to $\frac{1}{2}~v_{\infty}$;
-         \item the acceleration exponent, $\alpha$, which controls the rate 
-         at which the poloidal velocity changes near $R_v$.
-\end{itemize}
-
-The general behaviour we might expect is that outflows with denser
-regions near the wind base -- i.e. winds with larger $R_{v}$ and/or
-larger $\alpha$ -- will produce stronger optical emission signatures. 
-However, this behaviour may be moderated by the effect of the increasing
-optical depth through this region, which can also affect the line profile shapes. 
-In addition, modifying $R_v$ also increases the emission {\em volume}.
-Based on a preliminary exploration of models with different kinematics,
-we adopt the parameters listed in table~\ref{modelb_table}
-for our `optically optimized' model (model B).
-
-\subsection{Synthetic Spectra}
-
-\begin{figure} %fullpage
-\includegraphics[width=0.9\textwidth]{figures/modelb_uv_opt.eps}
-\caption{
-UV (left) and Optical synthetic spectra for model B computed at
-sightlines of 10, 27.5, 45, 62.5 and 80 degrees.	
-The inset plots show zoomed-in line profiles for 
-\heiiuv\ and \ha. The Balmer and He
-are double-peaked, albeit with narrower profiles.
-Strong \heiiopt\ emission can be seen, as well as a trend
-of a deeper Balmer jump with decreasing inclination.
-}
-\label{uvoptb}
-\end{figure} %fullpage
-
-Fig.~\ref{uvoptb} shows the UV and optical spectra for the
-optically optimized model for the full range of inclinations. 
-As expected, the trend from absorption to emission 
-in the optical is again present, but in this revised model we produce emission
-lines in the entire Balmer series at high inclinations, as well as the observed lines 
-in He~\textsc{ii} and He~\textsc{i}. This can be seen more clearly in the 
-continuum-normalized spectrum in Fig.~\ref{continuumb}.
-
-Two other features are worth noting in the optical
-spectrum. First, the collisionally excited Ca~{\sc ii} emission line at 3934~\AA\ 
-becomes quite prominent in our densest models. Second, our model predicts a detectable
-He~\textsc{ii} recombination line at 3202~\AA. This is the He
-equivalent of Paschen~$\beta$ and should be expected in all systems that
-feature a strong He~\textsc{ii}~$\lambda4686$ line (the He
-equivalent of Paschen~$\alpha$). 
-This line is somewhat unfamiliar observationally, because it 
-lies bluewards of the atmospheric cut-off, but
-also redwards of most ultraviolet spectra.
-
-Our models do not exhibit P-Cygni profiles in the optical lines.
-This is perhaps not surprising. LK02 and SV93 originally designed such models
-to reproduce the UV line profiles. Thus, most of the wind
-has an ionization parameter of $\log U \sim 2$ (see Fig.~\ref{wind}).
-This means H and He are fully ionized throughout 
-much of the wind and are successful in producing recombination features.
-However, the line opacity throughout the wind is too
-low to produce noticeable blue shifted absorption. 
-We suspect that the systems that exhibit such profiles must 
-possess a higher degree of ionization stratification, although the lack 
-of contemporary observations means it is not known for certain if the 
-P-Cygni profiles in UV resonance lines and optical H and He lines exist simultaneously.
-Ionization stratification could be caused by a clumpy flow, in which the ionization state 
-changes due to small scale density fluctuations, or a stratification in density
-and ionizing radiation field over larger scales.
-Invoking clumpiness in these outflows is not an unreasonable
-hypothesis. Theories of line-driven winds predict an unstable flow
-\citep{macgregor1979,owockirybicki1984,owockirybicki1985}, and
-simulations of CV disk winds also produce density inhomogeneities 
-\citep{proga1998,pkdh2002}.
-Tentative evidence for clumping being directly related to P-Cygni optical lines
-comes from the fact that \cite{prinja2000}
-found the dwarf nova BZ Cam's outflow to be unsteady and highly mass-loaded in outburst,
-based on observations of the UV resonance lines.
-This system has also exhibited P-Cygni profiles in He~\textsc{i}~$\lambda5876$
-and \ha\ when in a high-state \citep{patterson1996,RN98}. 
-The degree of ionization and density variation and 
-subsequent line opacities may be affected by our model parameters
-and the specific parameterisation we have adopted.
-
-In the UV, the model still produces all the observed lines, 
-and deep P-Cygni profiles are produced in the normal resonance lines,
-as discussed in section 4.2. However, the UV spectra also
-display what is perhaps the biggest problem with this revised model,
-namely the strength of resonance line emission 
-at low and intermediate inclinations.
-In order to generate strong optical wind signatures, we have adopted wind
-parameters that lead to very high densities at the base of the wind
-($n_e\sim10^{13}-10^{14}$~cm$^{-3}$). This produces
-the desired optical recombination emission, but also increases the
-role of collisional excitation in the formation of the UV resonance
-lines. This explains the pronounced increase in the emission component 
-of the C\textsc{iv} $\lambda1550$ resonance line, for example, relative to
-what was seen in the benchmark model (compare Figures~\ref{spec} and
-\ref{uvoptb}). The strength of this component in the revised model 
-is probably somewhat too high to be consistent with UV observations 
-of high-state CVs (see e.g. Long et al. 1991, 1994; Noebauer et al. 2010).
-\nocite{long1991,long1994, noebauer}
-
-\subsection{Continuum Shape and the Balmer Jump}
-
-The wind now also has a clear effect on the continuum shape,
-as shown by Fig.~\ref{modelb_escape}. In fact, the majority of the
-escaping spectrum has been reprocessed in some way by the wind,
-either by electron scattering (the wind is now moderately Thomson-thick),
-or by bound-free processes. This is demonstrated by the flatter spectral shape
-and the slight He photoabsorption edge present in the optical spectrum 
-(marked in Fig.~\ref{continuumb}). This reprocessing is also
-responsible for the change in continuum level between models A and B.
-In addition, Figures~\ref{uvoptb}, \ref{continuumb} 
-and \ref{modelb_escape} clearly demonstrate that the wind produces
-a recombination continuum sufficient to completely fill in the Balmer jump
-at high inclinations.\footnote{Note that the apparent absorption feature 
-just redward of the Balmer jump in these models is artificial. It is
-caused by residual line blanketing in the stellar atmospheres, which
-our models cannot fill in since they employ a 20-level H atom.}
-This might suggest that Balmer continuum emission from a wind can be important 
-in shaping the Balmer jump region, as
-originally suggested by Knigge et al.
-(1998b; see also Hassall et al. 1985)\nocite{KLWB98,hassall}.
-
-It should be acknowledged, however,
-that the Balmer jump in high-state CVs would naturally weaken at
-high inclinations due to limb darkening effects \citep{ladous1989, ladous1989b}. 
-Although we include a simple limb darkening law which affects 
-the emergent flux at each inclination, we do not
-include it as a {\em frequency dependent} opacity in our model.
-As a result, the efficiency of filling in the Balmer jump
-should really be judged at low and medium inclinations, 
-where, although prominent, the recombination continuum does
-not overcome the disk atmosphere absorption. 
-In addition, this effect 
-could mean that any model which successfully fills in the 
-jump at low inclinations could lead to a Balmer jump 
-in emission at high inclinations.
-In any case, to properly understand this phenomenon, a fully self-consistent
-radiative transfer calculation of both the disk atmosphere
-and connected wind is required.
-
-\begin{figure} 
-\includegraphics[width=0.45\textwidth]{figures/modelb_opt_cont.eps}
-\caption{
-Synthetic optical spectra from model B computed for 
-sightlines of 10, 27.5, 45, 62.5 and 80 degrees. In these plots
-the flux is divided by a polynomial fit to the 
-underlying continuum redward of the Balmer edge, so that 
-line-to-continuum ratios and the true depth of the
-Balmer jump can be shown.
-}
-\label{continuumb}
-\end{figure}
-
-\begin{figure} 
-\includegraphics[width=0.45\textwidth]{figures/modelb_escaping.eps}
-\caption{Total packet-binned spectra across all viewing angles, in units
-of monochromatic luminosity. 
-The thick black line shows the total 
-integrated escaping spectrum, 
-while the green line shows disk photons which escape without being reprocessed by
-the wind. The red line show the contributions from reprocessed 
-photons. 
-In this denser model the reprocessed contribution is significant compared
-to the escaping disk spectrum. The Balmer continuum emission is prominent, and
-the wind has a clear effect on the overall spectral shape.}
-\label{modelb_escape}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figures/mc.eps}
-\caption{
-\ha\ line profiles, normalized to 1, plotted in velocity space 
-for three models with varying kinematic 
-properties, computed at an inclination of $80^\circ$.
-The benchmark model and the improved optical
-model described in section 6 are labeled as A and B respectively,
-and a third model (X) which has an increased acceleration length of 
-$R_v = 283.8~R_{WD}$, and $\alpha=4$ is also shown. 
-The $x$-axis limits correspond to the Keplerian velocity at 
-$4R_{WD}$, the inner edge of the wind.
-We observe a narrowing of the lines, and a single-peaked line in model X.
-This is not due to radial velocity shear (see section 5.3).
-}
-\label{halpha}
-\end{figure} %fullpage
-
-\subsection{Line Profile Shapes: Producing Single-Peaked Emission}
-
-\begin{figure} %fullpage
-\includegraphics[width=0.9\textwidth]{figures/fig13.eps}
-\caption{{\sl Top Panel:} In and out of eclipse spectra of the high
-inclination NL RW Tri. {\sl Bottom Panel:} In and out of eclipse synthetic
-spectra from model B.
-The artificial `absorption' feature just redward of the Balmer jump
-is caused for the reasons described in section 5.2.}
-\label{rwtricomp}
-\end{figure} %fullpage
-
-Fig.~\ref{halpha} shows how the H$\alpha$ profile changes with the kinematics of the wind for 
-an inclination of $80^\circ$. The main prediction is that dense, slowly accelerating 
-wind models produce narrower emission lines. This is {\em not} due to radial 
-velocity shear. As stated by MC96, that mechanism can only work if poloidal 
-and rotational velocity gradients satisfy $(dv_l/dr)/(dv_\phi/dr) \gtrsim 1$; in 
-our models, this ratio is always $\lesssim 0.1$. Instead, the narrow lines predicted 
-by our denser wind models can be traced to the base of the outflow becoming optically 
-thick in the continuum, such that the line emission from the base of the wind
-cannot escape to the observer. In such models, the `line photosphere'
-(the $\tau \simeq 1$ surface of the line-forming region) moves outwards, towards larger 
-vertical and cylindrical distances. This reduces the predicted line widths, since the 
-rotational velocities -- which normally provide the main line broadening mechanism at 
-high inclination -- drop off as $1/r$. This is not to say that the MC96 
-mechanism could not be at work in CV winds. For example, it would be worth investigating
-alternative prescriptions for the wind velocity field, as well as the possibility that the 
-outflows may be clumped. An inhomogeneous flow 
-(which has been predicted in CVs; see section 5.2)
-might allow large radial velocity shears to exist while still 
-maintaining the high densities needed to produce the required level of emission.
-However, such an investigation is beyond the scope of the present paper.
-
-In our models, single-peaked line profiles are produced once the line forming region has been
-pushed up to $\sim 10^{11}$~cm ($\sim150~R_{WD}$) above the disk plane. 
-This number may seem unrealistically large, but the vertical extent of 
-the emission region is actually not well constrained observationally. 
-In fact, multiple observations of eclipsing NLs show that the H$\alpha$ 
-line is only moderately eclipsed compared to the continuum (e.g. Baptista et al. 2000;
-Groot et al. 2004; see also section 5.4), 
-implying a significant vertical extent for the line-forming 
-region. This type of model should therefore not be ruled out {\em a priori}, 
-but this specific model was not adopted as our optically optimized model
-due to its unrealistically high continuum level in eclipse.
-
-\subsection{Comparison to RW Tri}
-
-Fig.~\ref{rwtricomp} shows a comparison of the predicted
-out-of-eclipse and mid-eclipse spectra against observations of the
-high-inclination nova-like RW~Tri. The inclination of RW Tri is
-somewhat uncertain, with estimates including $70.5^\circ$
-\citep{smak1995}, $75^\circ$ \citep{groot2004}, $80^\circ$
-\citep{longmore1981} and $82^\circ$\citep{frankking1981}. Here, we
-adopt $i = 80^\circ$, but our qualitative conclusions are not
-particularly sensitive to this choice. 
-We follow LK02 is setting the value of $r_{disk}$ (the maximum radius of the accretion disk)
-to $34.3~R_{WD}$. When compared to the semi-major axis of RW Tri,
-this value is perhaps lower than one might 
-typically expect for NLs \citep{harropallinwarner1996}. 
-However, it is consistent
-with values inferred by \cite{rutten1992}.
-We emphasize that this model is in no sense a fit to this -- or any other -- data set.
-
-The similarity between the synthetic and observed spectra is
-striking. In particular, the revised model produces strong emission in
-all the Balmer lines, with line-to-continuum ratios comparable to
-those seen in RW Tri. Moreover, the line-to-continuum contrast
-increases during eclipse, as expected for emission produced in a disk
-wind. This trend is in line with the observations of RW~Tri, and it
-has also been seen in other NLs, including members of the SW~Sex class
-\citep{neustroev2011}. As noted in section 5.2, the majority
-of the escaping radiation has been reprocessed by the wind in some way
-(particularly the eclipsed light).
-
-However, there are also interesting differences between the revised
-model and the RW Tri data set. For example, the model exhibits
-considerably stronger He~{\sc ii} features than the observations,
-which suggests that the overall ionization state of the model is
-somewhat too high. As discussed in section 5.3, the optical lines are
-narrow, but double-peaked. This is in contrast to what is generally seen in observations
-of NLs, although the relatively low resolution of the RW Tri
-spectrum makes a specific comparison difficult. In order to demonstrate
-the double-peaked nature of the narrower lines, we choose not to 
-smooth the synthesized data to the resolution of the RW Tri dataset.
-If the data was smoothed, the \ha\ line would appear single-peaked.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%          CONCLUSIONS
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusions}
-
-We have investigated whether a disk wind model designed to reproduce
-the UV spectra of high-state CVs would also have a significant effect
-on the optical spectra of these systems. We find that this is indeed
-the case. In particular, the model wind produces H and He
-recombination lines, as well as a recombination continuum blueward of
-the Balmer edge. We do not produce P-Cygni profiles
-in the optical H and He lines, 
-which are seen in a small fraction of CV optical spectra.
-Possible reasons for this are briefly discussed in section 
-5.2.
-
-We have also constructed a revised benchmark model which is designed
-to more closely match the optical spectra of high-state CVs. This
-optically optimized model produces all the prominent optical lines in
-and out of eclipse, and achieves reasonable verisimilitude with the
-observed optical spectra of RW Tri. However, this model also has
-significant shortcomings. In particular, it predicts
-stronger-than-observed He~{\sc ii} lines in the optical region and too
-much of a collisionally excited contribution to the UV resonance lines.
-
-Based on this, we argue that recombination emission 
-from outflows with sufficiently high densities and/or optical depths 
-might produce the optical lines observed in CVs, and may also 
-fill in the Balmer absorption edge in the spectrum of the accretion disk, 
-thus accounting for the absence of a strong edge in observed CV spectra.
-In section 5.3, we demonstrate that
-although the double peaked lines narrow and 
-single-peaked emission can be formed in our densest models, 
-this is not due to the radial velocity shear mechanism proposed by MC96.
-We suggest that `clumpy' line-driven winds or a different
-wind parameterization may nevertheless allow this mechanism to work.
-We also note the possibility that, as in our denser models, 
-the single-peaked lines are formed well above the disk, where 
-rotational velocities are lower.
-
-It is not yet clear whether a wind model such as this can
-explain all of the observed optical features of high-state CVs --
-further effort is required on both the observational
-and modelling fronts.
-However, our work demonstrates that {\sl disk winds matter}. They are
-not just responsible for creating the blue-shifted absorption and
-P-Cygni profiles seen in the UV resonance lines of high-state CVs, but
-can also have a strong effect on the optical appearance of these
-systems. In fact, most of the optical features characteristic of CVs
-are likely to be affected -- and possibly even dominated -- by their disk
-winds. Given that optical spectroscopy plays the central role in
-observational studies of CVs, it is critical to know 
-where and how these spectra are actually formed. We believe it is high
-time for a renewed effort to understand the formation of spectra in
-accretion disks and associated outflows.
-
-\subsection*{Acknowledgements}
-The work of JHM and CK is supported by the Science and Technology Facilities Council (STFC), 
-via studentships and a consolidated grant, respectively. The work of NSH is supported by NASA under Astrophysics Theory Program grants NNX11AI96G  and NNX14AK44G.
-We are very grateful to A.F. Palah and B.T. Gaensicke for the IX Vel XSHOOTER dataset.
-We would also like to thank J.V. Hernandez Santisteban, S.W. Mangham and I. Hubeny for useful discussions. We acknowledge the use of the IRIDIS High Performance Computing Facility, 
-and associated support services at the University of Southampton, in the completion of this work.
-
-\bibliography{mybib.bib}
-
 \end{document}

### 2015-03-26 draft.tex
made more corrections

@@
 This framework was used for the treatment of line transfer and also
-for the line heating and cooling calculations. 
+for the line heating and cooling calculations (see LK02). 
 The approximation works reasonably well for resonance  
@@
 forbidden transitions are not taken into account when one 
-splits levels according to $l$ and $J$ quantum numbers, as well
+splits levels according to $l$- and $s$-subshells, as well
 as principal quantum number, $n$ (as we have done with He~\textsc{i}; 
-see section~\ref{sec:data}).
-Although this is, in general, a poor approximation, 
-it is a second order effect in the physical regime where 
-recombination lines are formed. 
-This is because bound-free processes are 
+see section~\ref{sec:data}). Although this is, in general, 
+a poor approximation, it is a second order effect in the physical 
+regime where recombination lines are formed. This is because bound-free processes are 
 dominant in determining level populations and emissivities.
@@
 Table~1. A key point is that the wind mass-loss rate in this model is
-set to 10$\%$ of the accretion rate through the disk. 
-The sensitivity to some of these parameters is discussed further in
-section 5.
+set to 10$\%$ of the accretion rate through the disk. The inner edge of
+the wind ($r_{min}$) is set to $4~R_{WD}$ following SV93. 
+The sensitivity to some of these parameters is briefly discussed in
+section~5.
 
@@
 
+This model demonstrated that one can achieve a more
+realistic optical spectrum by altering just two kinematic parameters. 
+However, it may also be possible to achieve this with
+other free parameters such as $\dot{M}_{wind}$, the opening angles of the wind and the 
+inner and outer launch radii. For example, increasing the mass loss rate of the wind
+would increase the amount of wind emission, as well as lowering the ionization 
+parameter and increasing optical depth through the wind. 
+Wider launch radii and opening angles would lead to a larger emitting volume, but
+this would be moderated by the decrease in density for a fixed mass-loss rate. 
+We also note that the inner radius of $4~R_{WD}$ adopted by SV93 
+particularly affects the emergent spectrum seen at inclinations $<\theta_{min}$ as 
+the inner disk is uncovered. A wind which extends right up to the WD would therefore
+have more absorption in the resonance lines and a less pronounced Balmer absorption edge
+at low inclinations. We suggest that future work should incorporate a treatment of clumping
+and investigate the effect of these parameters in more detail. If a wind 
+really does produce the line and continuum emission seen in optical spectra of high-state CVs, then
+understanding the true mass loss rate and geometry of the outflow is clearly important.
+
 \subsection{Continuum Shape and the Balmer Jump}
@@
 
+% \section{Sensitivity to Free Parameters}
+% \label{sec:free_params}
+
+% We have demonstrated that one can achieve a more
+% realistic optical spectrum with small changes to the wind prescription; 
+% specifically by altering just two kinematic parameters which increase the emission measure
+% of the wind plasma. However, it may also be possible to achieve this by altering 
+% other free parameters such as $\dot{M}_W$, the opening angles of the wind and the 
+% inner and outer launch radii. Increasing the mass loss rate of the wind or volume of 
+% the emitting area would
+
+% We plan to explore the effect of these parameters
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-03-26 draft.tex
a few more slight changes

@@
 forbidden transitions are not taken into account when one 
-splits levels according to $l$- and $s$-subshells, as well
+splits levels ito $l$- and $s$-subshells, as well
 as principal quantum number, $n$ (as we have done with He~\textsc{i}; 
-see section~\ref{sec:data}). Although this is, in general, 
-a poor approximation, it is a second order effect in the physical 
-regime where recombination lines are formed. This is because bound-free processes are 
-dominant in determining level populations and emissivities.
-We have verified that this is indeed the case in the He~\textsc{i}
-emission regions in our model.
+see section~\ref{sec:data}). Although this approximation is, in general, 
+a poor one, the effect is second order in the physical 
+regime where recombination lines are formed in our models. 
+This is because bound-free processes are dominant in determining 
+level populations and emissivities. We have verified that this 
+is indeed the case in the He~\textsc{i} emission regions in our models.
 

### 2015-03-26 response/supplement_response.tex
a few more slight changes

@@
 
+This is a supplementary documenting which presents a few plots to justify the claims made in the response to
+referee for MNRAS submission MN-15-0213-MJ.
+
+Figure 1 shows the level populations of Helium 1. Levels are split according to TopBase, meaning that they are in 
+energy order and split by s and l quantum numbers.It demonstrates that in the dense regions of the wind in which He I emission tends to occur (Cell 10), the populations are already more or less distributed by statistical weight.
+The cells in the figure have the following properties:
+
+\begin{itemize}
+\item cell 10: $T_R=4.76e+04, T_e=3.43e+04, n_e=1.10e+14, W=3.49e-01$
+\item cell 96: $T_R=4.69e+04, T_e=1.96e+04, n_e=5.26e+10, W=6.02e-03$
+\item cell 200: $T_R=3.41e+04, T_e=1.49e+03, n_e=5.87e+07, W=1.41e-04$
+\end{itemize}
+Figure 2 shows a spectrum. One of the models has arbritrarily fast transitions added between forbidden transitions,
+to simulate the effect of dominant collisional transitions between these states. The other model is model B from the 
+paper, a model with significant He I emission. The effect on the overall spectrum is completely negligible.
+
 \begin{figure}	%fullpage
@@
 \includegraphics[width=1.0\textwidth]{pops.png}
+\caption
+{
+Top Panel: fractional level populations in He I.
+Bottom Panel: fractional level populations in He I divided by statistical weight.
+In dense regions the levels are already distributed more or less according to statistical weight.
+This
+is due to b-f processes dominating the level populations. As densities decrease, the triplet and singlet populations
+become somewhat decoupled. This does not affect the model as these cells have negligible line emissivities.
+}
+\label{f1}
+\end{figure}
+
+\begin{figure}	%fullpage
+\centering
 \caption{
+A spectrum will be shown here.
 }
-\label{novalikes}
+\label{f2}
 \end{figure}

### 2015-04-02 draft.tex
updated draft

@@
 \begin{equation}
-J_{est} = \frac{c}{4 \pi \nu_0 V} \sum_{photons} w \frac{1 - e^{-\tau_s}}{\tau_s} \frac{1}{dv/ds}.
+J_{est} = \frac{c}{4 \pi \nu_0 V} \sum_{i} w_i \frac{1 - e^{-\tau_{s,i}}}{\tau_{s,i}} \frac{1}{(dv/ds)_i}.
 \end{equation}
@@
 $\tau_s$ is the Sobolev optical depth.
-The sum is over all photons that come into resonance with the line.
+The sum is over all photons that come into resonance with the line,
+and thus represents an integral over solid angle.
 The corresponding de-excitation rate is then 
@@
 models, we treat H and He as macro-atoms and all metals as
-simple-atoms. Elements treated with either method
-are always present as sources of both bound-free opacity and line opacity, 
+simple-atoms. Species treated with either method
+are full taken into account as sources of both bound-free opacity and line opacity, 
 and contribute to the heating and cooling balance of the plasma.
@@
 is met: all of the strong metal resonance
-lines -- notably N\textsc{v}~$\lambda1240$,
-Si\textsc{iv}~$\lambda1400$ and C\textsc{iv}~$\lambda1550$ -- 
+lines -- notably N~\textsc{v}~$\lambda1240$,
+Si~\textsc{iv}~$\lambda1400$ and C~\textsc{iv}~$\lambda1550$ -- 
 are present and exhibit clear P-Cygni profiles
@@
 
-This model demonstrated that one can achieve a more
-realistic optical spectrum by altering just two kinematic parameters. 
-However, it may also be possible to achieve this with
-other free parameters such as $\dot{M}_{wind}$, the opening angles of the wind and the 
-inner and outer launch radii. For example, increasing the mass loss rate of the wind
-would increase the amount of wind emission, as well as lowering the ionization 
-parameter and increasing optical depth through the wind. 
-Wider launch radii and opening angles would lead to a larger emitting volume, but
-this would be moderated by the decrease in density for a fixed mass-loss rate. 
-We also note that the inner radius of $4~R_{WD}$ adopted by SV93 
-particularly affects the emergent spectrum seen at inclinations $<\theta_{min}$ as 
-the inner disk is uncovered. A wind which extends right up to the WD would therefore
-have more absorption in the resonance lines and a less pronounced Balmer absorption edge
-at low inclinations. We suggest that future work should incorporate a treatment of clumping
-and investigate the effect of these parameters in more detail. If a wind 
-really does produce the line and continuum emission seen in optical spectra of high-state CVs, then
-understanding the true mass loss rate and geometry of the outflow is clearly important.
-
 \subsection{Continuum Shape and the Balmer Jump}
@@
 
+\subsection{Sensitivity to Parameters}
+
+This revised model demonstrates that one can achieve a more
+realistic optical spectrum by altering just two kinematic parameters. 
+However, it may also be possible to achieve this with
+other free parameters such as $\dot{M}_{wind}$, the opening angles of the wind and the 
+inner and outer launch radii. For example, increasing the mass loss rate of the wind
+would increase the amount of wind emission, as well as lowering the ionization 
+parameter and increasing optical depth through the wind. In general, we expect
+scattering and ionization changes to scale as $\rho$, whereas recombination
+emission scales as $\rho^2$. Wider launch radii and opening angles would lead 
+to a larger emitting volume, but this would be moderated by a decrease in density for a fixed mass-loss rate. 
+We also note that the inner radius of $4~R_{WD}$ adopted by SV93 
+particularly affects the emergent spectrum seen at inclinations $<\theta_{min}$ as 
+the inner disk is uncovered. A wind which extends right up to the WD would therefore
+have more absorption in the resonance lines and a less pronounced Balmer absorption edge
+at low inclinations. We suggest that future work should incorporate a treatment of clumping
+and investigate the effect of these parameters in more detail. If a wind 
+really does produce the line and continuum emission seen in optical spectra of high-state CVs, then
+understanding the true mass loss rate and geometry of the outflow is clearly important.
+
 \subsection{Comparison to RW Tri}

### 2015-04-07 draft.tex
updated text

@@
 realistic optical spectrum by altering just two kinematic parameters. 
-However, it may also be possible to achieve this with
+However, it may also be possible to achieve this by modifying
 other free parameters such as $\dot{M}_{wind}$, the opening angles of the wind and the 
 inner and outer launch radii. For example, increasing the mass loss rate of the wind
-would increase the amount of wind emission, as well as lowering the ionization 
-parameter and increasing optical depth through the wind. In general, we expect
-scattering and ionization changes to scale as $\rho$, whereas recombination
-emission scales as $\rho^2$. Wider launch radii and opening angles would lead 
-to a larger emitting volume, but this would be moderated by a decrease in density for a fixed mass-loss rate. 
-We also note that the inner radius of $4~R_{WD}$ adopted by SV93 
-particularly affects the emergent spectrum seen at inclinations $<\theta_{min}$ as 
-the inner disk is uncovered. A wind which extends right up to the WD would therefore
-have more absorption in the resonance lines and a less pronounced Balmer absorption edge
-at low inclinations. We suggest that future work should incorporate a treatment of clumping
-and investigate the effect of these parameters in more detail. If a wind 
-really does produce the line and continuum emission seen in optical spectra of high-state CVs, then
+increases the amount of recombination emission (which scales as $\rho^2$), 
+as well as lowering the ionization parameter and increasing optical depth through the wind. 
+Wider launch radii and opening angles lead to a larger emitting volume, but this is moderated by a decrease in density 
+for a fixed mass-loss rate. We also note that the inner radius of $4~R_{WD}$ adopted by SV93 
+affects the emergent UV spectrum seen at inclinations $<\theta_{min}$ as 
+the inner disk is uncovered. This causes less absorption in the UV resonance lines,
+but the effect on the optical spectrum is negligible.
+We have verified this general behaviour, but
+we suggest that future work should investigate the effect of these parameters in more detail
+as well as incorporating a treatment of clumping.
+If a wind really does produce the line and continuum emission seen in optical spectra of high-state CVs, then
 understanding the true mass loss rate and geometry of the outflow is clearly important.

### 2015-04-08 draft.tex
bringing up to final submission

@@
 on the Very Large Telescope on 2014 October 10.
-These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $75^\circ$ 
+These systems have approximate inclinations of $30^\circ$, $60^\circ$ and $80^\circ$ 
 (see section 5.4) respectively. 
@@
 forbidden transitions are not taken into account when one 
-splits levels ito $l$- and $s$-subshells, as well
+splits levels into $l$- and $s$-subshells, as well
 as principal quantum number, $n$ (as we have done with He~\textsc{i}; 
@@
 simple-atoms. Species treated with either method
-are full taken into account as sources of both bound-free opacity and line opacity, 
+are fully taken into account as sources of both bound-free opacity and line opacity, 
 and contribute to the heating and cooling balance of the plasma.
@@
 Table~1. A key point is that the wind mass-loss rate in this model is
-set to 10$\%$ of the accretion rate through the disk. The inner edge of
-the wind ($r_{min}$) is set to $4~R_{WD}$ following SV93. 
+set to 10$\%$ of the accretion rate through the disk. We follow SV93
+in setting the inner edge of the wind ($r_{min}$) to $4~R_{WD}$. 
 The sensitivity to some of these parameters is briefly discussed in
@@
 
-\subsection{Sensitivity to Parameters}
+\subsection{Sensitivity to Model Parameters}
 
@@
 as well as lowering the ionization parameter and increasing optical depth through the wind. 
-Wider launch radii and opening angles lead to a larger emitting volume, but this is moderated by a decrease in density 
+Larger launching radii and covering factors tend to lead to a larger emitting volume, 
+but this is moderated by a decrease in density 
 for a fixed mass-loss rate. We also note that the inner radius of $4~R_{WD}$ adopted by SV93 
@@
 We have verified this general behaviour, but
-we suggest that future work should investigate the effect of these parameters in more detail
+we suggest that future work should investigate the effect of these parameters in more detail,
 as well as incorporating a treatment of clumping.

### 2015-04-08 draft.tex
wording

@@
 The emission measure of a plasma is directly proportional to its density.
-The simplest way to simultaneously affect the density in the wind (for fixed mass loss rate),
+The simplest way to simultaneously affect the density in the wind (for fixed mass-loss rate),
 as well as the velocity gradients, is by modifying the poloidal velocity
@@
 other free parameters such as $\dot{M}_{wind}$, the opening angles of the wind and the 
-inner and outer launch radii. For example, increasing the mass loss rate of the wind
+inner and outer launch radii. For example, increasing the mass-loss rate of the wind
 increases the amount of recombination emission (which scales as $\rho^2$), 
-as well as lowering the ionization parameter and increasing optical depth through the wind. 
-Larger launching radii and covering factors tend to lead to a larger emitting volume, 
+as well as lowering the ionization parameter and increasing the optical depth through the wind. 
+Larger launching regions and covering factors tend to lead to a larger emitting volume, 
 but this is moderated by a decrease in density 
@@
 If a wind really does produce the line and continuum emission seen in optical spectra of high-state CVs, then
-understanding the true mass loss rate and geometry of the outflow is clearly important.
+understanding the true mass-loss rate and geometry of the outflow is clearly important.
 

### 2015-04-08 scripts/mnras.py
trying to make final submitted zip

@@ -1,41 +1,0 @@
-
-
-import sys
-import numpy as np
-filename = sys.argv[1]
-outfilename = sys.argv[2]
-
-
-texfile =  open(filename, "r")
-outfile = open(outfilename, "w")
-
-
-outfile.write("\documentclass[useAMS,usenatbib]{mn2e_x}\n")
-
-fig_env = False
-
-for line in texfile:
-	if "begin{abstract}" in line:
-		outfile.write("\maketitle\n")
-		outfile.write(line)
-
-	elif "indent" in line and "rule" in line:
-		if "%" not in line:
-			outfile.write("\\noindent\\rule{8cm}{0.4pt}\n")
-
-	elif "fullpage" in line and "begin{figure}" in line:
-		if fig_env == False:
-			outfile.write("\\begin{figure*}\n")
-			fig_env = True 
-
-	elif fig_env and "end{figure}" in line:
-		outfile.write("\end{figure*}")
-		outfile.write("\n")
-		fig_env = False 
-
-	elif "documentclass" not in line and "maketitle" not in line:
-		outfile.write(line)
-
-
-
-outfile.close()

### 2015-04-08 draft_mnras.tex
trying to make final submitted zip
fiddled with orders. ArXix? would want email address

--- 2015-04-08 draft.tex
@@
+\documentclass[useAMS,usenatbib]{mn2e_x}
 %%%% Various options for document class.
-%\documentclass[usenatbib, a4paper]{preprint}
-\documentclass[preprint, a4paper, 11pt]{aastex}
-%%\documentclass[twocolum]{revtex4}
-%%\documentclass{report}
-%%\documentclass[useAMS,usenatbib, onecolumn]{mn2ejm}
 
@@
 
+\maketitle
 \begin{abstract}
-% Many high-state non-magnetic cataclysmic variables (CVs) exhibit
-% blue-shifted absorption or P-Cygni profiles associated with ultraviolet
-% (UV) resonance lines, such as C~{\sc iv}~$\lambda1550$. These features
-% imply the existence of powerful accretion disk winds in
-% CVs. Here, we use an improved version of our Monte Carlo ionization
-% and radiative transfer code to investigate whether disk wind models that
-% produce realistic UV line profiles are also likely to generate
-% observationally significant recombination line and continuum emission
-% in the {\em optical} waveband. 
-% We also test whether outflows may be responsible for the single-peaked 
-% emission line profiles often seen
-% in high-state CVs and for the weakness of the Balmer absorption edge
-% (relative to simple models of optically thick accretion disks).
-% We find that a standard disk wind model that is successful in
-% reproducing the UV spectra of CVs also leaves a noticeable imprint on
-% the optical spectrum, particularly for systems viewed at high
-% inclination. The strongest optical wind-formed recombination lines are \ha\ and
-% \heiiopt, although the outflow also produces emission in the Ly$\alpha$
-% and \heiiuv\ UV lines. However, all of the optical lines produced by
-% this default wind model are double-peaked, and the effect of the wind
-% on the Balmer jump is modest. We demonstrate that a higher-density outflow model 
-% displays reasonable verisimilitude with the optical spectrum of RW Trianguli,
-% producing all the observed lines. This model
-% produces a recombination continuum that is strong enough to fill in the Balmer jump,
-% but it also predicts stronger-than-observed collisionally excited UV emission lines. 
-% The wind in our revised model also alters the spectral shape of the continuum, 
-% and displays a strong inclination dependence in its emission properties. 
-% No single-peaked emission is seen, although we observe a 
-% narrowing of the double-peaked emission lines from the base of the wind.
-% We show that even denser models can produce a single-peaked \ha\ line.
-% In this model, the single-peaked line profile is due to the line emission originating from 
-% $\sim10^{11}$~cm above the disk plane where rotational velocities are small, 
-% and is not due to the radial velocity shear mechanism that
-% has previously been proposed. On the basis of our results, we suggest that winds can 
-% modify, and perhaps even dominate, the line and continuum emission
-% from CVs.
 Many high-state non-magnetic cataclysmic variables (CVs) exhibit
@@
 
-\maketitle
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{figure}	%fullpage
+\begin{figure*}
 \centering
@@
 \label{novalikes}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure} %fullpage
-\includegraphics[width=0.9\textwidth]{figures/fig5.eps}
+\begin{figure*}
+\includegraphics[width=0.8\textwidth]{figures/fig5.eps}
 \caption{
@@
 \label{wind}
-\end{figure} %fullpage
+\end{figure*}
 
@@
 
-\begin{figure} %fullpage
+\begin{figure*}
 \includegraphics[width=0.9\textwidth]{figures/modela_uv_opt.eps}
@@
 \label{spec}
-\end{figure} %fullpage\
+\end{figure*}
 
@@
 
-\begin{figure} %fullpage
+\begin{figure*}
 \includegraphics[width=0.9\textwidth]{figures/modelb_uv_opt.eps}
@@
 \label{uvoptb}
-\end{figure} %fullpage
+\end{figure*}
 
@@
 
-\begin{figure} %fullpage
-\includegraphics[width=0.9\textwidth]{figures/fig13.eps}
-\caption{{\sl Top Panel:} In and out of eclipse spectra of the high
-inclination NL RW Tri. {\sl Bottom Panel:} In and out of eclipse synthetic
-spectra from model B.
-The artificial `absorption' feature just redward of the Balmer jump
-is caused for the reasons described in section 5.2.}
-\label{rwtricomp}
-\end{figure} %fullpage
-
 Fig.~\ref{halpha} shows how the H$\alpha$ profile changes with the kinematics of the wind for 
@@
 
+\begin{figure*}
+\includegraphics[width=0.9\textwidth]{figures/fig13.eps}
+\caption{{\sl Top Panel:} In and out of eclipse spectra of the high
+inclination NL RW Tri. {\sl Bottom Panel:} In and out of eclipse synthetic
+spectra from model B.
+The artificial `absorption' feature just redward of the Balmer jump
+is caused for the reasons described in section 5.2.}
+\label{rwtricomp}
+\end{figure*}
+
 Fig.~\ref{rwtricomp} shows a comparison of the predicted

### 2015-04-16 draft_mnras_arxiv.tex
ready for arxiv hopefully

--- 2015-04-07 draft.tex
@@
+\documentclass[useAMS,usenatbib]{mn2e_arxiv_submit}
 %%%% Various options for document class.
-%\documentclass[usenatbib, a4paper]{preprint}
-\documentclass[preprint, a4paper, 11pt]{aastex}
-%%\documentclass[twocolum]{revtex4}
-%%\documentclass{report}
-%%\documentclass[useAMS,usenatbib, onecolumn]{mn2ejm}
 
@@
 
-\author[Matthews et al.]{J.~H.~Matthews,$^1$ C.~Knigge,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and N.~Higginbottom$^4$
+\author[Matthews et al.]{J.~H.~Matthews,$^1$\thanks{E-mail: jm8g08@soton.ac.uk} C.~Knigge,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and N.~Higginbottom$^4$
 \medskip  
@@
 
+\date{Accepted, 15 April 2015. Received, 8 April 2015; in original form, 26 January 2015.}
 %%\author{J. H. Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}
@@
 
-% \section{Sensitivity to Free Parameters}
-% \label{sec:free_params}
-
-% We have demonstrated that one can achieve a more
-% realistic optical spectrum with small changes to the wind prescription; 
-% specifically by altering just two kinematic parameters which increase the emission measure
-% of the wind plasma. However, it may also be possible to achieve this by altering 
-% other free parameters such as $\dot{M}_W$, the opening angles of the wind and the 
-% inner and outer launch radii. Increasing the mass loss rate of the wind or volume of 
-% the emitting area would
-
-% We plan to explore the effect of these parameters
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
